### 2017-08-08 Analysis/Norm_kids.Rmd
First commit

---
title: "WordRec Experiment"
author: "A. Fourtassi & M. Frank"
date: "January 13, 2017"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Libraries.

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
theme_set(theme_bw())
```

The following analysis is done using pilot data with 25 subjects.

We plan to collect data for 100 subjects

Data.

```{r}

#Skip the pre task trials 
#Filter subjects who had no technical problem
#Select subjects who got more than 50% correct answers on the pre task trials

d_norm <- read_delim("Norm_kids.txt", delim = " ") %>%
  filter(type == "Train") #%>%
  #filter(score > 0.5)

```

Process norming data

```{r}
concept <- d_norm %>%
  filter(condition == 'concept') %>%
  group_by(distance) %>%
  multi_boot_standard(col = "answer") #%>%
  #rename(concept_dist = conceptOrd,
      #   semDist=mean)

sound <- d_norm %>% 
  filter(condition == 'sound') %>%
  group_by(distance, sameDiff) %>%
  multi_boot_standard(col = "answer") #%>%
 # mutate(contrast= paste(phone1, "/", phone2, sep="")) %>%
  #select(-phone1) %>%
  #select(-phone2)

```
Norming plots

```{r}
plot_concept  <- ggplot(concept, aes(x = distance, y= mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .03), size=0.5) +

 xlab("distance") +ylab("% different")+ theme_bw()

plot_concept

sound$distance <- factor(sound$distance, levels = c('pl','in','ar1','ar2'))

plot_sound  <- ggplot(sound, aes(x = distance, y= mean, col=sameDiff)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .03), size=0.5) +

 xlab("distance") +ylab("% different")+ theme_bw()

plot_sound
```

Process Switch data

```{r}
#data <- d %>%
#  mutate(correct=ifelse(order==answer, 1, 0))%>%
#  mutate(soun_dist = sound_dist+1) %>%
#  select(-sound_dist) %>%
#  rename(sound_dist = soun_dist)  %>%
#  select(ID, concept_dist, sound_dist, correct, RT) %>%
#  left_join(sound0) %>%
#  left_join(concept0)

data_4 <- d_4 %>%
  mutate(correct=ifelse(order==answer, 1, 0))%>%
  mutate(soun_dist = sound_dist+1) %>%
  select(-sound_dist) %>%
  rename(sound_dist = soun_dist)  %>%
  select(ID, concept_dist, sound_dist, trial, correct, RT)

data_merge_4 <- data_4 %>%
  mutate(sound_level=ifelse((sound_dist==1 | sound_dist==2), 0.20, 0.75)) %>%
  mutate(concept_level=ifelse((concept_dist==1 | concept_dist==2), 0.37, 0.87)) %>%
  mutate(trial=ifelse((trial==0 | trial==1), 0, 1)) %>%
  select(-sound_dist) %>%
  select(-concept_dist) %>%
  rename(sound_dist=sound_level,
         concept_dist=concept_level)

data_5 <- d_5 %>%
  mutate(correct=ifelse(order==answer, 1, 0))%>%
  mutate(soun_dist = sound_dist+1) %>%
  select(-sound_dist) %>%
  rename(sound_dist = soun_dist)  %>%
  select(ID, concept_dist, sound_dist, trial, correct, RT)

data_merge_5 <- data_5 %>%
  mutate(sound_level=ifelse((sound_dist==1 | sound_dist==2), 0.20, 0.75)) %>%
  mutate(concept_level=ifelse((concept_dist==1 | concept_dist==2), 0.15, 0.75)) %>%
  mutate(trial=ifelse((trial==0 | trial==1), 0, 1)) %>%
  select(-sound_dist) %>%
  select(-concept_dist) %>%
  rename(sound_dist=sound_level,
         concept_dist=concept_level)

data_merge <- bind_rows(data_merge_4, data_merge_5)

#saveRDS(data, file="data_switch.Rda")

saveRDS(data_merge_4, file="data_switch_all.Rda")

#saveRDS(data_merge, file="data_switch_av.Rda")
```

```{r}
data_plot <- data %>%
  group_by(sound_dist, concept_dist, trial) %>%
  multi_boot_standard(col = "correct")

data_plot_4 <- data_4 %>%
  group_by(sound_dist, concept_dist, trial) %>%
  multi_boot_standard(col = "correct")

data_plot_5 <- data_5 %>%
  group_by(sound_dist, concept_dist, trial) %>%
  multi_boot_standard(col = "correct")

data_plot_merge_4 <- data_merge_4 %>%
  group_by(sound_dist, concept_dist, trial) %>%
  multi_boot_standard(col = "correct")

data_plot_merge_5 <- data_merge_5 %>%
  group_by(sound_dist, concept_dist, trial) %>%
  multi_boot_standard(col = "correct")

data_plot_all <- data_merge %>%
  group_by(sound_dist, concept_dist, trial) %>%
  multi_boot_standard(col = "correct")

data_plot_2 <- data %>%
  group_by(sound_dist, concept_dist) %>%
  multi_boot_standard(col = "correct")

data_plot_2_l <- data_merge %>%
  group_by(sound_dist, concept_dist) %>%
  multi_boot_standard(col = "correct")

data_plot_C0 <- data_plot %>%
  filter(trial=='0')

data_plot_C1 <- data_plot %>%
  filter(trial=='1')

data_plot_C2 <- data_plot %>%
  filter(trial=='2')

data_plot_C3 <- data_plot %>%
  filter(trial=='3')

#data_plotRT <- data %>%
#  group_by(acousDist, semDist, correct) %>%
#  multi_boot_standard(col = "RT")
```

initial plot
```{r}

ggplot(data_plot_merge_4, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8)) +
  facet_grid(. ~ trial)

ggplot(data_plot_merge_5, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8)) +
  facet_grid(. ~ trial)

ggplot(data_plot_4, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8)) +
  facet_grid(. ~ trial)

ggplot(data_plot_5, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8)) +
  facet_grid(. ~ trial)

```

```{r}

ggplot(data_plot_2_l, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  xlab("Auditory distance") +ylab("% different")+
  scale_colour_discrete(name="Visual Dist")+
theme(legend.title = element_text(size=8))

```

```{r}

ggplot(data_plot_l, 
       aes(x = concept_dist, y = mean, col = factor(sound_dist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  xlab("Visual distance") +ylab("% different")+
  scale_colour_discrete(name="Acoustic Dist")+
theme(legend.title = element_text(size=8)) +
  facet_grid(. ~ trial)

```

```{r}
ggplot(data_plot, 
       aes(x = semDist, y = mean, col = factor(acousDist))) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  scale_colour_solarized() +
  xlab("Visual distance") +ylab("% different")+
  scale_colour_discrete(name="Auditory Dist")+
theme(legend.title = element_text(size=8))

```

Fit the models.
```{r}

#Fit the uniomodal sound condition
sound_data <- d %>%
    filter(condition == "sound")

concept_data <- d %>%
    filter(condition == "concept")

joint_data <- d %>%
    filter(condition == "joint")

#Fit the uniomodal sound condition with a logistic regression
fit_sound <- glm(answer ~ sound_dist, data=sound_data, family = binomial())

##extract coefficient
s_coef <- coef(fit_sound)["sound_dist"]
s_inter <- coef(fit_sound)["(Intercept)"]

#prameters of the sound distribution
s_var=4/(s_coef)
s_sum=-1*s_inter/s_coef

#Fit the uniomodal visual conditon
fit_concept <- glm(answer ~ concept_dist, data=concept_data, family = binomial())

##extract coefficient
c_coef <- coef(fit_concept)["concept_dist"]
c_inter <- coef(fit_concept)["(Intercept)"]

#prameters of the sound distribution
v_var=4/(c_coef)
v_sum=-1*c_inter/c_coef

#Fit the bimodal conditon
fit_joint <- glm(answer ~ sound_dist+concept_dist, data=joint_data, family = binomial())

##extract coefficient
j_coef_a <- coef(fit_joint)["sound_dist"]
j_coef_v <- coef(fit_joint)["concept_dist"]
j_inter <- coef(fit_joint)["(Intercept)"]

#prameters of the sound distribution (approx: the average mean sum equal to 0+4/2=2)
j_var_a=4/(j_coef_a)
j_var_v=4/(j_coef_v)

```

Analysis of the unimodal cases.
```{r}

#Recogniton functions from the unimodal fit 
x <- seq(0, 4, 0.01)

y_sound <- predict(fit_sound, list(sound_dist = x), type="response")
y_concept <- predict(fit_concept, list(concept_dist = x), type="response")

uniS <- data.frame(xS=x,yS=y_sound)
uniV <- data.frame(xV=x,yV=y_concept)

#Recognition functions from the bimodal fit (marginal distributions)
Logistic_a = function (x, A = j_coef_a , B = 2*j_coef_a) {
    1 / (1 + exp(-1*(-B +A * x)))
}

Logistic_v = function (x, A = j_coef_v , B = 2*j_coef_v) {
    1 / (1 + exp(-1*(-B +A * x)))
}

#Plot all these functions in the same graph

##The auditory case
ggplot(sounds, 
       aes(x = sound_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(data=uniS,aes(x=xS, y=yS))+
  xlab("Auditory distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+
  stat_function(fun = Logistic_a, colour="red")

##The visual case
ggplot(concepts, 
       aes(x = concept_dist, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(data=uniV,aes(x=xV, y=yV))+
  xlab("Visual distance") +ylab("% different")+
  scale_y_continuous(limits = c(0, 1))+
  stat_function(fun = Logistic_v, colour="red")

```

The bimodal case
```{r}

# Bimodal recognition functions

##the bimodal fit 
model_fit <- function (x,y) {
   1/(1 + exp(-x*j_coef_a-y*j_coef_v+2*j_coef_a+2*j_coef_v))
}

##Values of the baseline
model_base <- function (x,y) {
   1/(1 + exp(-x*s_coef-y*c_coef+2*s_coef+2*c_coef))
}

# Add the fit the baeline to data

ms_all <- joint %>% 
  rename(joint = mean) %>%
  left_join(select(concepts, concept_dist, mean) %>% 
              rename(concepts = mean)) %>%
  left_join(select(sounds, sound_dist, mean) %>% 
              rename(sounds = mean)) %>%
  mutate(fit = model_fit(sound_dist, concept_dist)) %>%
  mutate(base = model_base(sound_dist, concept_dist)) %>%
  gather(model, pred, concepts, sounds, base, fit)

#Plot Heat map for the data
ggplot(data = ms_all, aes(x=sound_dist, y=concept_dist, fill=joint)) + 
  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")

#Plot Heatmap for the baseline
mybase <- ms_all %>%
  filter(model=="base")

ggplot(data = mybase, aes(x=sound_dist, y=concept_dist, fill=pred)) + 
  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")

myfilter <- ms_all %>%
  filter(model=="fit" | model=="base")

#Correlation models (baseline and fit) to bimodal data 
ggplot(myfilter, 
       aes(x = pred, y = joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) +
 geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_abline(slope = 1, lty = 2) +
  facet_grid(model~.)

```

The modality dominance
```{r}

#Modality dominance coeficent
a_fit=j_var_v/j_var_a
a_base=v_var/s_var
a_Vdom=2*a_base
a_Sdom=0.5*a_base

#Classification thresholds (prob=0.5) for:

##The basline (combination of the unimodal cases)
classif_base = function (x, A=a_base) {
    2*(A+1)-A*x
}

##Best bivariate fit 
classif_fit = function (x, A=a_fit) {
    2*(A+1)-A*x
}

##A baseline for visual domiance
classif_Vdom = function (x, A=a_Vdom) {
    2*(A+1)-A*x
}

##A baseline for auditory domiance
classif_Sdom = function (x, A=a_Sdom) {
    2*(A+1)-A*x
}

#Sample from the baseline bivariate distribution
Gaus_base <- data.frame(x=c(rnorm(1000,0,sqrt(s_var)),rnorm(1000,4,sqrt(s_var))),
          y=c(rnorm(1000,0,sqrt(v_var)),rnorm(1000,4,sqrt(v_var))))

#Plot samples from the bivariate distribution
ggplot(Gaus_base, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
  stat_function(fun = classif_base, colour = "red") +xlab("Auditory") +ylab("Visual")+ scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))

#Sample from the best bivariate fit 
Gaus_fit <- data.frame(x=c(rnorm(1000,0,sqrt(j_var_a)),rnorm(1000,4,sqrt(j_var_a))),
          y=c(rnorm(1000,0,sqrt(j_var_v)),rnorm(1000,4,sqrt(j_var_v))))

#Plot samples from the best bivariate fit
ggplot(Gaus_fit, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
  stat_function(fun = classif_fit, colour = "red") +xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))

#Modality dominance?
ggplot(Gaus_fit, aes(x,y)) +
  stat_function(fun = classif_base, colour = "red", lty=2) +
  stat_function(fun = classif_Vdom, colour = "blue", lty=2 )+
  stat_function(fun = classif_Sdom, colour = "blue", lty=2)+
  stat_function(fun = classif_fit, colour = "black")+
  xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+
  scale_y_continuous(limits = c(-6, 10))+theme(aspect.ratio = 1)

```

### 2017-08-08 Analysis/process_kids.py

@@ -1,0 +1,44 @@
+import os
+import sys
+import shutil
+import numpy
+from optparse import OptionParser
+import random
+from math import *
+import glob
+import pprint
+import json
+
+ExpN="Norming_kids"
+subjN=0
+myFiles= glob.glob("../Raw_data/"+ExpN+"/*json")
+for f in myFiles:
+    file_name=f.split('.')[0]
+    cur=open(f,'r')
+    cur_json=json.load(cur)
+    subjN=subjN+1
+
+#extract info
+    #kid_id=file_name
+    tri_type=cur_json["data"]["data"]["tri_type"]
+    condition=cur_json["data"]["data"]["condition"]
+    distance=cur_json["data"]["data"]["dist"]
+    item=cur_json["data"]["data"]["item"]
+    sameDiff=cur_json["data"]["data"]["sameDiff"]
+    answer=cur_json["data"]["data"]["answer"]
+    native=cur_json["data"]["brief"]["native"]
+    gender=cur_json["data"]["brief"]["gender"]
+    age=cur_json["data"]["brief"]["age"]
+
+    trials=cur_json["data"]["data"]["tri_number"]
+    for i in range(len(trials)):
+        if distance[i]=='':
+	    distance[i]='NA'
+	if item =='':
+	    item='NA'
+	if distance=='':
+	    distance='NA'
+
+        print 'subject_'+str(subjN), tri_type[i], condition[i], distance[i], item[i], sameDiff[i], answer[i], native[0], gender[0], age[0]
+
+    

### 2017-08-08 Analysis/process_kids_exp.py

@@ -1,0 +1,51 @@
+import os
+import sys
+import shutil
+import numpy
+from optparse import OptionParser
+import random
+from math import *
+import glob
+import pprint
+import json
+
+ExpN="rawdata_kids_pilot1"
+subjN=0
+myFiles= glob.glob("../Raw_data/"+ExpN+"/*json")
+for f in myFiles:
+    file_name=f.split('.')[0]
+    cur=open(f,'r')
+    cur_json=json.load(cur)
+    subjN=subjN+1
+
+#extract info
+    #kid_id=file_name
+    tri_type=cur_json["data"]["data"]["tri_type"]
+    experiment=cur_json["data"]["data"]["experiment"]
+    condition=cur_json["data"]["data"]["condition"]
+    sound_dist=cur_json["data"]["data"]["sound_val"]
+    concept_dist=cur_json["data"]["data"]["concept_val"]
+    item=cur_json["data"]["data"]["item"]
+    sameDiff=cur_json["data"]["data"]["sameDiff"]
+    answer=cur_json["data"]["data"]["answer"]
+    correct=cur_json["data"]["data"]["correct"]
+    native=cur_json["data"]["brief"]["native"]
+    gender=cur_json["data"]["brief"]["gender"]
+    age=cur_json["data"]["brief"]["age"]
+
+    trials=cur_json["data"]["data"]["trial"]
+    for i in range(len(trials)):
+        if concept_dist[i]=='':
+	    concept_dist[i]='NA'
+	if sound_dist[i]=='':
+            sound_dist[i]='NA'
+	if sameDiff[i] =='':
+	    sameDiff[i]='NA'
+	if correct[i]=='':
+	    correct[i]='NA'
+	if trials[i]=='':
+	    trials[i]='NA'
+
+        print 'subject_'+str(subjN), tri_type[i], condition[i], trials[i], sound_dist[i], concept_dist[i], item[i], sameDiff[i], answer[i], correct[i], native[0], gender[0], age[0]
+
+    

### 2017-08-08 extract.py

@@ -1,0 +1,59 @@
+from xml.dom import minidom
+import sys
+
+doc = minidom.parse(sys.argv[1])
+layers = [layer for layer in doc.getElementsByTagName('g')]
+for layer in layers:
+    layer_id = layer.getAttribute('inkscape:label')
+    print "\"" + layer_id + "\": {",
+    for path in layer.getElementsByTagName('path'):
+        piece = path.getAttribute('id').split("-")[0]
+        pathstring = path.getAttribute('d')
+        print "\"" + piece + "\":" + '"' + pathstring + '", \n',
+    print "},"
+doc.unlink()
+
+# def multiline(string, indent):
+#   cperline = 80 - indent - 4
+#   n_lines = len(string) / cperline + 1
+#   ret_string = '"' + string[0:cperline]
+#   for i in range(n_lines)[1:]:
+#     ret_string += '" + \n'+' '*indent+'"'
+#     ret_string +=string[i*cperline:(i+1)*cperline]
+#   return ret_string + '"'
+
+# identical = ['hair', 'bangs', #'bigreflect1', 'bigreflect2', 'smallreflect1',
+#              #'smallreflect2', 'pupil1', 'pupil2',
+#              'face', 'neck']
+
+# doc = minidom.parse("alice.svg")  # parseString also exists
+# layers = [ layer for layer in doc.getElementsByTagName('g')]
+# for layer in doc.getElementsByTagName('g'):
+#   layer_id = layer.getAttribute('inkscape:label')
+#   layer_indent = len(layer_id) + 9
+#   pieces = [ (path.getAttribute('d'), path.getAttribute('id') ) for path
+#              in layer.getElementsByTagName('path')]
+#   print "var", layer_id, '= {',
+#   for i in range(len(pieces)):
+#     piece = pieces[i]
+#     p_id = piece[1].split("-")[0]
+#     indent = len(p_id) + 4 + layer_indent
+#     if (i == 0):
+#       ind = ''
+#     else:
+#       ind = ' '*layer_indent
+#     if (i == len(pieces) - 1):
+#       print ind + '"' + p_id + '":',
+#       if (p_id in identical):
+#         print p_id,
+#       else:
+#         print multiline(piece[0], indent),
+#       print '};'
+#     else:
+#       print ind + '"' + p_id + '":',
+#       if (p_id in identical):
+#         print p_id + ','
+#       else:
+#         print multiline(piece[0], indent) + ','
+#   print
+# doc.unlink()

### 2017-08-08 switch_kids.js

@@ -1,0 +1,1342 @@
+//////////////////
+//Helper functions
+///////////////////
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+
+
+function showCurrent(event)
+{
+    //var duration = event.duration;
+    var duration = event.duration;
+   
+}
+
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+
+
+////////////////////////////////////////////////
+//Instructions for the Task and preTask training
+///////////////////////////////////////////////
+
+var MyInstruct = {
+  
+
+
+    "train_sound" :"Now you will be trained to trials on sound difference!",
+    
+    "PracticeObj":"<font size=6><b>Practice Object discrimination!</b></font>",
+    
+    "Obj":"<font size=6><b>Real Object discrimination!</b></font>",
+    
+    "PracticeSnd":"<font size=6><b>Practice Sound discrimination!</b></font>",
+    
+    "Snd":"<font size=6><b>Real Sound discrimination!</b></font>",
+    
+    "PracticeWord":"<font size=6><b>Practice Word learning!</b></font>",
+    
+    "Word":"<font size=6><b>Real Word learning</b></font>",
+    
+    "WordTest":"<font size=6><b>Now Test! </font></b><br><br><font size=4> Next time the test will appear immediately after object presenttion!</font>",
+    
+    "train_object" :"<font size=6><b>Now you will be trained to trials on object difference!</b></font>",
+    
+    "sound" :"Next are the real trials on sound difference!",
+    
+    "object" :"Next are the real trials on object difference!",
+    
+    
[…]

### 2017-08-09 switch_kids.js
new changes

@@ -159,18 +159,27 @@ var us_a_b_b_a = $('<audio>').attr('src','sounds/us_A_b_b_A.mp3').attr("preload"
 var us_a_b_a = $('<audio>').attr('src','sounds/us_A_b_A.mp3').attr("preload", "auto");
 
 
+var col = "#ffffff";
+var col1 = "#EC7063",
+    col2 = "#AF7AC5",
+    col3 = "#5499C7",
+    col4 = "#48C9B0";
 
-var bird = new Ecosystem.Genus('bird', {col1:col, col2:col, col3:col, tar1:1, tar2:0 });
-    
-var flower = new Ecosystem.Genus('flower', {col1:col, col2:col, col3:col, tar1:1, tar2:0 });
+var colors = shuffleArray([col1, col2, col3, col4]);
 
-var fish = new Ecosystem.Genus('fish', {col1:col, col2:col, col3:col, tar1:1, tar2:0 });
+var bird = new Ecosystem.Genus('bird', {col2:col, col3:col, col3:col, tar1:1, tar2:0 });
     
-var bug = new Ecosystem.Genus('bug', {col1:col, col2:col, col3:col, tar1:1, tar2:0 });
+var flower = new Ecosystem.Genus('flower', {col2:col, col3:col, col4: col,  tar1:1, tar2:0 });
+
+var fish = new Ecosystem.Genus('fish', {col2:col, col3:col, col4:col, tar1:1, tar2:0 });
+    
+var bug = new Ecosystem.Genus('bug', {col2:col, col3:col, col4:col, tar1:1, tar2:0 });
 
 var CatEx = randomElement(["bird", "flower", "fish", "bug"])
 
-var Concept_pre0 = [{category:CatEx, prop:0}, {category:CatEx, prop:1}]
+
+
+var Concept_pre0 = [{category:CatEx, prop:0, col1:col}, {category:CatEx, prop:1, col1:col1}]
 
 
 var Sound_pre0 = [us_a_d_b_a,
@@ -181,7 +190,7 @@ var Sound_pre0 = [us_a_d_b_a,
 //Preloading Task stim (0: left, 1: right)
 var rando=0;
 
-var col = "#ffffff";
+
 
 
 //Stimuli for discrimination
@@ -191,6 +200,13 @@ var col = "#ffffff";
 var category_discrim = shuffleArray(["bird", "flower", "fish", "bug"])
 //Concept stimuli
 
+var color ={
+    "bird":col1,
[…]

### 2017-08-29 Analysis/pilot_kids.Rmd
pilot 3

---
title: "WordRec Experiment"
author: "A. Fourtassi & M. Frank"
date: "January 13, 2017"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Libraries.

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
theme_set(theme_bw())
```

Data.

```{r}

d_word <- read_delim("pilot3_kids.txt", delim = " ") %>%
  filter(type == "Test") %>%
  filter(age != 6)

```

Process word learning data

```{r}
#Average

data <- d_word %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0)) %>%
  group_by(sound_dist, concept_dist) %>%
  multi_boot_standard(col = "iscorrect")

data$sound_dist <- factor(data$sound_dist, levels = c('similar','different', 'maximal'))

ggplot(data, 
       aes(x = sound_dist, y = mean, col = factor(concept_dist))) +
       #aes(x = concept_dist, y = mean)) + 
  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
                  position = position_dodge(width = .1)) + 
  geom_line(lty = 2) + 
  xlab("Aud distance") +ylab("% Accurate")+
  scale_colour_discrete(name="Vis Dist")+
theme(legend.title = element_text(size=8)) #+  facet_grid(. ~ item)

```

Process discrimianation data

```{r}
concept <- d_discrim %>%
  filter(condition == 'concept') %>%
  group_by( concept_dist) %>%
  multi_boot_standard(col = "answer") #%>%
  #rename(concept_dist = conceptOrd,
      #   semDist=mean)

sound <- d_discrim %>% 
  filter(condition == 'sound') %>%
  group_by(sound_dist, sameDiff) %>%
  multi_boot_standard(col = "answer") #%>%
 # mutate(contrast= paste(phone1, "/", phone2, sep="")) %>%
  #select(-phone1) %>%
  #select(-phone2)

```

plot discrimination data

```{r}
plot_concept  <- ggplot(concept, aes(x = concept_dist, y= mean)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .03), size=0.5) +

 xlab("distance") +ylab("% different")+ theme_bw()

plot_concept

#sound$distance <- factor(sound$distance, levels = c('pl','in','ar1','ar2'))

plot_sound  <- ggplot(sound, aes(x = sound_dist, y= mean, col=sameDiff)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(width = .03), size=0.5) +

 xlab("distance") +ylab("% different")+ theme_bw()

plot_sound
```

### 2017-08-29 switch_kids_2.js

@@ -56,8 +56,6 @@ var MyInstruct = {
 
     "train_sound" :"Now you will be trained to trials on sound difference!",
     
-    "refresh" :"<font size=6><b>Refresh!</b></font>",
-    
     "PracticeObj":"<font size=6><b>Practice Object discrimination!</b></font>",
     
     "Obj":"<font size=6><b>Real Object discrimination!</b></font>",
@@ -277,33 +275,28 @@ var ConceptStim=[
                
                   [{category:category[0], prop:0, col1:col},{category:category[0], prop:0.5, col1:col}, 'similar'],
                   [{category:category[1], prop:0, col1:col},{category:category[1], prop:0.5, col1:col}, 'similar'],
-                  [{category:category[3], prop:0, col1:col},{category:category[3], prop:0.5, col1:col}, 'similar'],
                   [{category:category[2], prop:0, col1:col},{category:category[2], prop:1, col1:col}, 'different'],
                   [{category:category[3], prop:0, col1:col},{category:category[3], prop:1, col1:col}, 'different'],
-                  [{category:category[0], prop:0, col1:col},{category:category[0], prop:1, col1:col}, 'different']
+    
                   ]
     
 
 //sound stimuli
-//
+//I should pick in random some
 
     
 var SoundLabels=[
                 ["ar_a_xx_G_a", "ar_a_G_xx_a", "similar"],
                 ["us_A_b_d_A", "us_A_d_b_A", "different"],
-                ["neem_lif", "lif_neem", "maximal"],
                 ["ar_a_xx_G_a", "ar_a_G_xx_a", "similar"],
-                ["us_A_b_d_A", "us_A_d_b_A", "different"],
-                ["neem_lif", "lif_neem", "maximal"]
+                ["us_A_b_d_A", "us_A_d_b_A", "different"]
                 ]
 
 var SoundLabels_test = [
                 ["ar_a_xx_a", "ar_a_G_a", "similar"],
                 ["us_A_b_A", "us_A_d_A", "different"],
-                ["neem", "lif", "maximal"],
                 ["ar_a_xx_a", "ar_a_G_a", "similar"],
-                ["us_A_b_A", "us_A_d_A", "different"],
-                ["neem", "lif", "maximal"]
+                ["us_A_b_A", "us_A_d_A", "different"]
                 ]
 
 
@@ -793,19 +786,17 @@ myTrial = {
 
 
[…]

### 2017-11-06 Analysis/analyses.Rmd
new modif

---
title: "Word Learning Experiment"
author: "A. Fourtassi & M. Frank"
date: "November 6, 2017"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Libraries.

```{r}
library(readr)
library(tidyr)
library(ggplot2)
library(langcog)
library(dplyr)
library(plyr)
library(dplyr)
library(pwr)
theme_set(theme_bw())
```

Here I filter the unsused info, which was collected in the pilot experiment but it is no more included in the final experiment.

Moreover, unlike the pilot Exp, the final Exp contains a catch condition. The catch condition is obvious, and will be used to exclude participants who did not pay attention or/did not understand the task
```{r}

d_real <- read_delim("pilot3_kids.txt", delim = " ") %>%
  filter(sound_dist != 'similar') %>%
  filter(age == 4)

d_real$sound_dist <- mapvalues(d_real$sound_dist, from = c("different", "maximal"), to = c("similar", "different"))

```

Population:
```{r}
# 4 to 5 years old recruted at Bing nursery school at Standord University
```

Sample size:

```{r}
# N = 60
#See power analysis below
```

Data.

```{r}

d_word <- d_real %>%
  filter(type == "Test") 
  #filter(sound_dist != 'similar')
```

Below, for the pilot data, exlusion is based on one of the experimental condition (i.e., sounds diff and meaning diff). In the final experiment, exlusion will be based on the catch condition, which is also maximal (i.e., sounds diff and meaning diff).

```{r}
data <- d_word %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0)) %>%
  group_by(ID, sound_dist, concept_dist) %>%
  multi_boot_standard(col = "iscorrect")

data_excl <- data %>%
  filter(sound_dist == 'different' & concept_dist == 'different') %>%
  ungroup() %>%
  select(ID, mean) %>%
  dplyr::rename(score = mean)
  #select(ID, score)

data_good <- d_word %>%
  left_join(data_excl) %>%
  filter(score >0.5)

```

Now analyse and plot data

```{r}
#Average

data_new <- data_good %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0)) %>%
  group_by(sound_dist, concept_dist) %>%
  multi_boot_standard(col = "iscorrect")

```

```{r }

data_new$concept_dist <- factor(data_new$concept_dist, levels = c("similar", "different"))
data_new$sound_dist <- factor(data_new$sound_dist, levels = c("similar", "different"))

ggplot(data_new, 
       aes(x = sound_dist, y = mean, group = factor(concept_dist), col = factor(concept_dist))) +

  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
                  position = position_dodge(width = .1)) +

  geom_hline(yintercept = .50, linetype="dashed") + 
  geom_line() +
  xlab("Sound condition") +ylab("Accuracy")+
  #scale_colour_manual(values = c("red", "blue"), name="Vis Dist")+
  scale_colour_discrete(name="Meaning condition")+

  #scale_y_continuous(limits = c(0.45, 0.9))+
theme(legend.title = element_text(size=8)) #+ facet_grid(. ~ ID)

```

Power analysis

```{r}

#Effect size estimates are based on pilot data above

#First we want to detect a difference in accuracy between the maximal trial (around .85) and the lower accuracy trials (sounds different but meanings similar, or vice versa), which are both around 0.65

p.out1 <- pwr.2p.test(h = ES.h(p1 = 0.85, p2 = 0.65),
                     sig.level = 0.05, 
                     power = 0.80, 
                     alternative = "greater")
plot(p.out1)

#Second we want points at 0.65 to be different from chance

p.out2 <- pwr.p.test(h = ES.h(p1 = 0.65, p2 = 0.5),
                     sig.level = 0.05, 
                     power = 0.80, 
                     alternative = "greater")

plot(p.out2)

# A reasonable final sample size is 60 participants

```

### 2017-11-06 switch_kids_v2.js

@@ -45,6 +45,14 @@ function shuffleArray(a) {
 }
 
 
+var code = '';
+
+$( "#nextButton_brief" ).click(function() {
+    code=$('#txt_code').val();
+  
+});
+
+
 
 ////////////////////////////////////////////////
 //Instructions for the Task and preTask training
@@ -343,27 +351,30 @@ var catch_test = [
                     ]
 
 
-var category = shuffleArray([bird, tree, fish, bug])
-//Concept stimuli
+var category = [bird, tree, fish, bug]
+var category_name = ["bird", "tree", "fish", "bug"]
 
+
+var catRand = shuffleArray([0,1,2,3])
 //define similar and different proportion
 
+var visDist = 0.35
 
 var concept_cluster1 = [
-    [{category:category[0], prop:0, col1:col},{category:category[0], prop:0.3, col1:col}, 'similar'],
-    [{category:category[1], prop:0, col1:col},{category:category[1], prop:1, col1:col}, 'different']
+    [{category:category[catRand[0]], prop:0, col1:col},{category:category[catRand[0]], prop:visDist, col1:col}, 'similar', category_name[catRand[0]]],
+    [{category:category[catRand[1]], prop:0, col1:col},{category:category[catRand[1]], prop:1, col1:col}, 'different', category_name[catRand[1]]]
 ]
 
 var concept_cluster2 =[
-    [{category:category[2], prop:0, col1:col},{category:category[2], prop:1, col1:col}, 'different'],
-    [{category:category[3], prop:0, col1:col},{category:category[3], prop:0.3, col1:col}, 'similar']
+    [{category:category[catRand[2]], prop:0, col1:col},{category:category[catRand[2]], prop:1, col1:col}, 'different', category_name[catRand[2]]],
+    [{category:category[catRand[3]], prop:0, col1:col},{category:category[catRand[3]], prop:visDist, col1:col}, 'similar', category_name[catRand[3]]]
 ]
 
 
 var concept_catch = [
     {category:flower, prop:0, col1:col},
     {category:flower, prop:1, col1:col},
-    'catch'
+    'catch', 'flower'
 ]
 
 //Now the main thing:
@@ -654,7 +665,7 @@ for (i=0; i<concept_all.length; i++){//iterate over all conditions
         condition: i,
         trial:k,
         trial_type: "Train",
-        item:concept_all[i][0].category,
+        item:'',
         concept_l:concept_all[i][0],
         concept_r:concept_all[i][1],
         sound:sound_train_all[i][m],
[…]

### 2017-11-06 switch_adults.js
adult experiment

@@ -1,0 +1,1176 @@
+//////////////////
+//Helper functions
+///////////////////
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+
+
+function showCurrent(event)
+{
+    //var duration = event.duration;
+    var duration = event.duration;
+   
+}
+
+function randomInteger(n) {
+	return Math.floor(Math.random()*n);
+}
+
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+
+
+////////////////////////////////////////////////
+//Instructions for the Task and preTask training
+///////////////////////////////////////////////
+
+var MyInstruct = {
+  
+
+
+    "train_sound" :"Now you will be trained to trials on sound difference!",
+    
+    "refresh" :"<font size=6><b>Refresh your memory!</b></font>",
+    
+    "refresh_pra" :"<font size=6><b>Refresh your memory!</b></font></br></br>To refresh your memory, you will see another learning trial. You will be tested again after this refreshment!",
+    
+    "PracticeObj":"<font size=6><b>Practice Object discrimination!</b></font>",
+    
+    "Obj":"<font size=6><b>Real Object discrimination!</b></font>",
+    
+    "PracticeSnd":"<font size=6><b>Practice Sound discrimination!</b></font>",
+    
+    "Snd":"<font size=6><b>Real Sound discrimination!</b></font>",
+    
+    "PracticeWord":"<font size=6><b>Practice</b></font> <br><br> This is a practice example. You will see 2 objects and hear their names. Listen carfully and try to remember the words!",
+    
[…]

### 2017-11-06 Analysis/process_kids.py
final pre registration for kids

@@ -1,44 +1,0 @@
-import os
-import sys
-import shutil
-import numpy
-from optparse import OptionParser
-import random
-from math import *
-import glob
-import pprint
-import json
-
-ExpN="Norming_kids"
-subjN=0
-myFiles= glob.glob("../Raw_data/"+ExpN+"/*json")
-for f in myFiles:
-    file_name=f.split('.')[0]
-    cur=open(f,'r')
-    cur_json=json.load(cur)
-    subjN=subjN+1
-
-#extract info
-    #kid_id=file_name
-    tri_type=cur_json["data"]["data"]["tri_type"]
-    condition=cur_json["data"]["data"]["condition"]
-    distance=cur_json["data"]["data"]["dist"]
-    item=cur_json["data"]["data"]["item"]
-    sameDiff=cur_json["data"]["data"]["sameDiff"]
-    answer=cur_json["data"]["data"]["answer"]
-    native=cur_json["data"]["brief"]["native"]
-    gender=cur_json["data"]["brief"]["gender"]
-    age=cur_json["data"]["brief"]["age"]
-
-    trials=cur_json["data"]["data"]["tri_number"]
-    for i in range(len(trials)):
-        if distance[i]=='':
-	    distance[i]='NA'
-	if item =='':
-	    item='NA'
-	if distance=='':
-	    distance='NA'
-
-        print 'subject_'+str(subjN), tri_type[i], condition[i], distance[i], item[i], sameDiff[i], answer[i], native[0], gender[0], age[0]
-
-    

### 2017-11-06 Analysis/process_kids_exp.py

@@ -1,51 +1,0 @@
-import os
-import sys
-import shutil
-import numpy
-from optparse import OptionParser
-import random
-from math import *
-import glob
-import pprint
-import json
-
-ExpN="rawdata_kids_pilot1"
-subjN=0
-myFiles= glob.glob("../Raw_data/"+ExpN+"/*json")
-for f in myFiles:
-    file_name=f.split('.')[0]
-    cur=open(f,'r')
-    cur_json=json.load(cur)
-    subjN=subjN+1
-
-#extract info
-    #kid_id=file_name
-    tri_type=cur_json["data"]["data"]["tri_type"]
-    experiment=cur_json["data"]["data"]["experiment"]
-    condition=cur_json["data"]["data"]["condition"]
-    sound_dist=cur_json["data"]["data"]["sound_val"]
-    concept_dist=cur_json["data"]["data"]["concept_val"]
-    item=cur_json["data"]["data"]["item"]
-    sameDiff=cur_json["data"]["data"]["sameDiff"]
-    answer=cur_json["data"]["data"]["answer"]
-    correct=cur_json["data"]["data"]["correct"]
-    native=cur_json["data"]["brief"]["native"]
-    gender=cur_json["data"]["brief"]["gender"]
-    age=cur_json["data"]["brief"]["age"]
-
-    trials=cur_json["data"]["data"]["trial"]
-    for i in range(len(trials)):
-        if concept_dist[i]=='':
-	    concept_dist[i]='NA'
-	if sound_dist[i]=='':
-            sound_dist[i]='NA'
-	if sameDiff[i] =='':
-	    sameDiff[i]='NA'
-	if correct[i]=='':
-	    correct[i]='NA'
-	if trials[i]=='':
-	    trials[i]='NA'
-
-        print 'subject_'+str(subjN), tri_type[i], condition[i], trials[i], sound_dist[i], concept_dist[i], item[i], sameDiff[i], answer[i], correct[i], native[0], gender[0], age[0]
-
-    

### 2017-11-06 switch_adults.js

@@ -1,1176 +1,0 @@
-//////////////////
-//Helper functions
-///////////////////
-
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-
-
-function showCurrent(event)
-{
-    //var duration = event.duration;
-    var duration = event.duration;
-   
-}
-
-function randomInteger(n) {
-	return Math.floor(Math.random()*n);
-}
-
-function randomElement(array) {
-  return array[randomInteger(array.length)];
-}
-
-function randomInt(min,max)
-{
-    return Math.floor(Math.random()*(max-min+1)+min);
-}
-
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-//shuffle an array
-function shuffleArray(a) {
-
-    for (var i = a.length - 1; i > 0; i--) {
-        var j = Math.floor(Math.random() * (i + 1));
-        var temp = a[i];
-        a[i] = a[j];
-        a[j] = temp;
-    }
-    return a;
-}
-
-
-
-////////////////////////////////////////////////
-//Instructions for the Task and preTask training
-///////////////////////////////////////////////
-
-var MyInstruct = {
-  
-
-
-    "train_sound" :"Now you will be trained to trials on sound difference!",
-    
-    "refresh" :"<font size=6><b>Refresh your memory!</b></font>",
-    
-    "refresh_pra" :"<font size=6><b>Refresh your memory!</b></font></br></br>To refresh your memory, you will see another learning trial. You will be tested again after this refreshment!",
-    
-    "PracticeObj":"<font size=6><b>Practice Object discrimination!</b></font>",
-    
-    "Obj":"<font size=6><b>Real Object discrimination!</b></font>",
-    
-    "PracticeSnd":"<font size=6><b>Practice Sound discrimination!</b></font>",
-    
-    "Snd":"<font size=6><b>Real Sound discrimination!</b></font>",
-    
-    "PracticeWord":"<font size=6><b>Practice</b></font> <br><br> This is a practice example. You will see 2 objects and hear their names. Listen carfully and try to remember the words!",
-    
[…]

### 2017-11-06 Analysis/Norm_concept_kids .Rmd
final pre registration for kids

--- 2017-08-08 Analysis/Norm_kids.Rmd
@@
 ```
-
-The following analysis is done using pilot data with 25 subjects.
-
-We plan to collect data for 100 subjects
 
@@
 
-sound <- d_norm %>% 
-  filter(condition == 'sound') %>%
-  group_by(distance, sameDiff) %>%
-  multi_boot_standard(col = "answer") #%>%
- # mutate(contrast= paste(phone1, "/", phone2, sep="")) %>%
-  #select(-phone1) %>%
-  #select(-phone2)
-
 ```
@@
 plot_concept  <- ggplot(concept, aes(x = distance, y= mean)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
+  geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
                   position = position_dodge(width = .03), size=0.5) +
@@
 
-sound$distance <- factor(sound$distance, levels = c('pl','in','ar1','ar2'))
-
-plot_sound  <- ggplot(sound, aes(x = distance, y= mean, col=sameDiff)) +
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .03), size=0.5) +
-
- xlab("distance") +ylab("% different")+ theme_bw()
-
-plot_sound
 ```
-
-Process Switch data
-
-```{r}
-#data <- d %>%
-#  mutate(correct=ifelse(order==answer, 1, 0))%>%
-#  mutate(soun_dist = sound_dist+1) %>%
-#  select(-sound_dist) %>%
-#  rename(sound_dist = soun_dist)  %>%
-#  select(ID, concept_dist, sound_dist, correct, RT) %>%
-#  left_join(sound0) %>%
-#  left_join(concept0)
-
-data_4 <- d_4 %>%
-  mutate(correct=ifelse(order==answer, 1, 0))%>%
-  mutate(soun_dist = sound_dist+1) %>%
-  select(-sound_dist) %>%
-  rename(sound_dist = soun_dist)  %>%
-  select(ID, concept_dist, sound_dist, trial, correct, RT)
-
-data_merge_4 <- data_4 %>%
-  mutate(sound_level=ifelse((sound_dist==1 | sound_dist==2), 0.20, 0.75)) %>%
-  mutate(concept_level=ifelse((concept_dist==1 | concept_dist==2), 0.37, 0.87)) %>%
-  mutate(trial=ifelse((trial==0 | trial==1), 0, 1)) %>%
-  select(-sound_dist) %>%
-  select(-concept_dist) %>%
-  rename(sound_dist=sound_level,
-         concept_dist=concept_level)
-
-data_5 <- d_5 %>%
-  mutate(correct=ifelse(order==answer, 1, 0))%>%
-  mutate(soun_dist = sound_dist+1) %>%
-  select(-sound_dist) %>%
-  rename(sound_dist = soun_dist)  %>%
-  select(ID, concept_dist, sound_dist, trial, correct, RT)
-
-data_merge_5 <- data_5 %>%
-  mutate(sound_level=ifelse((sound_dist==1 | sound_dist==2), 0.20, 0.75)) %>%
-  mutate(concept_level=ifelse((concept_dist==1 | concept_dist==2), 0.15, 0.75)) %>%
-  mutate(trial=ifelse((trial==0 | trial==1), 0, 1)) %>%
-  select(-sound_dist) %>%
-  select(-concept_dist) %>%
-  rename(sound_dist=sound_level,
-         concept_dist=concept_level)
-
-data_merge <- bind_rows(data_merge_4, data_merge_5)
-
-#saveRDS(data, file="data_switch.Rda")
-
-saveRDS(data_merge_4, file="data_switch_all.Rda")
-
-#saveRDS(data_merge, file="data_switch_av.Rda")
-```
-
-```{r}
-data_plot <- data %>%
-  group_by(sound_dist, concept_dist, trial) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_4 <- data_4 %>%
-  group_by(sound_dist, concept_dist, trial) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_5 <- data_5 %>%
-  group_by(sound_dist, concept_dist, trial) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_merge_4 <- data_merge_4 %>%
-  group_by(sound_dist, concept_dist, trial) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_merge_5 <- data_merge_5 %>%
-  group_by(sound_dist, concept_dist, trial) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_all <- data_merge %>%
-  group_by(sound_dist, concept_dist, trial) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_2 <- data %>%
-  group_by(sound_dist, concept_dist) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_2_l <- data_merge %>%
-  group_by(sound_dist, concept_dist) %>%
-  multi_boot_standard(col = "correct")
-
-data_plot_C0 <- data_plot %>%
-  filter(trial=='0')
-
-data_plot_C1 <- data_plot %>%
-  filter(trial=='1')
-
-data_plot_C2 <- data_plot %>%
-  filter(trial=='2')
-
-data_plot_C3 <- data_plot %>%
-  filter(trial=='3')
-
-#data_plotRT <- data %>%
-#  group_by(acousDist, semDist, correct) %>%
-#  multi_boot_standard(col = "RT")
-```
-
-initial plot
-```{r}
-
-ggplot(data_plot_merge_4, 
-       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(lty = 2) + 
-  xlab("Auditory distance") +ylab("% different")+
-  scale_colour_discrete(name="Visual Dist")+
-theme(legend.title = element_text(size=8)) +
-  facet_grid(. ~ trial)
-
-ggplot(data_plot_merge_5, 
-       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(lty = 2) + 
-  xlab("Auditory distance") +ylab("% different")+
-  scale_colour_discrete(name="Visual Dist")+
-theme(legend.title = element_text(size=8)) +
-  facet_grid(. ~ trial)
-
-ggplot(data_plot_4, 
-       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(lty = 2) + 
-  xlab("Auditory distance") +ylab("% different")+
-  scale_colour_discrete(name="Visual Dist")+
-theme(legend.title = element_text(size=8)) +
-  facet_grid(. ~ trial)
-
-ggplot(data_plot_5, 
-       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(lty = 2) + 
-  xlab("Auditory distance") +ylab("% different")+
-  scale_colour_discrete(name="Visual Dist")+
-theme(legend.title = element_text(size=8)) +
-  facet_grid(. ~ trial)
-
-```
-
-```{r}
-
-ggplot(data_plot_2_l, 
-       aes(x = sound_dist, y = mean, col = factor(concept_dist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(lty = 2) + 
-  xlab("Auditory distance") +ylab("% different")+
-  scale_colour_discrete(name="Visual Dist")+
-theme(legend.title = element_text(size=8))
-
-```
-
-```{r}
-
-ggplot(data_plot_l, 
-       aes(x = concept_dist, y = mean, col = factor(sound_dist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(lty = 2) + 
-  xlab("Visual distance") +ylab("% different")+
-  scale_colour_discrete(name="Acoustic Dist")+
-theme(legend.title = element_text(size=8)) +
-  facet_grid(. ~ trial)
-
-```
-
-```{r}
-ggplot(data_plot, 
-       aes(x = semDist, y = mean, col = factor(acousDist))) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(lty = 2) + 
-  scale_colour_solarized() +
-  xlab("Visual distance") +ylab("% different")+
-  scale_colour_discrete(name="Auditory Dist")+
-theme(legend.title = element_text(size=8))
-
-```
-
-Fit the models.
-```{r}
-
-#Fit the uniomodal sound condition
-sound_data <- d %>%
-    filter(condition == "sound")
-
-concept_data <- d %>%
-    filter(condition == "concept")
-
-joint_data <- d %>%
-    filter(condition == "joint")
-
-#Fit the uniomodal sound condition with a logistic regression
-fit_sound <- glm(answer ~ sound_dist, data=sound_data, family = binomial())
-
-##extract coefficient
-s_coef <- coef(fit_sound)["sound_dist"]
-s_inter <- coef(fit_sound)["(Intercept)"]
-
-#prameters of the sound distribution
-s_var=4/(s_coef)
-s_sum=-1*s_inter/s_coef
-
-#Fit the uniomodal visual conditon
-fit_concept <- glm(answer ~ concept_dist, data=concept_data, family = binomial())
-
-##extract coefficient
-c_coef <- coef(fit_concept)["concept_dist"]
-c_inter <- coef(fit_concept)["(Intercept)"]
-
-#prameters of the sound distribution
-v_var=4/(c_coef)
-v_sum=-1*c_inter/c_coef
-
-#Fit the bimodal conditon
-fit_joint <- glm(answer ~ sound_dist+concept_dist, data=joint_data, family = binomial())
-
-##extract coefficient
-j_coef_a <- coef(fit_joint)["sound_dist"]
-j_coef_v <- coef(fit_joint)["concept_dist"]
-j_inter <- coef(fit_joint)["(Intercept)"]
-
-#prameters of the sound distribution (approx: the average mean sum equal to 0+4/2=2)
-j_var_a=4/(j_coef_a)
-j_var_v=4/(j_coef_v)
-
-```
-
-Analysis of the unimodal cases.
-```{r}
-
-#Recogniton functions from the unimodal fit 
-x <- seq(0, 4, 0.01)
-
-y_sound <- predict(fit_sound, list(sound_dist = x), type="response")
-y_concept <- predict(fit_concept, list(concept_dist = x), type="response")
-
-uniS <- data.frame(xS=x,yS=y_sound)
-uniV <- data.frame(xV=x,yV=y_concept)
-
-#Recognition functions from the bimodal fit (marginal distributions)
-Logistic_a = function (x, A = j_coef_a , B = 2*j_coef_a) {
-    1 / (1 + exp(-1*(-B +A * x)))
-}
-
-Logistic_v = function (x, A = j_coef_v , B = 2*j_coef_v) {
-    1 / (1 + exp(-1*(-B +A * x)))
-}
-
-#Plot all these functions in the same graph
-
-##The auditory case
-ggplot(sounds, 
-       aes(x = sound_dist, y = mean)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(data=uniS,aes(x=xS, y=yS))+
-  xlab("Auditory distance") +ylab("% different")+
-  scale_y_continuous(limits = c(0, 1))+
-  stat_function(fun = Logistic_a, colour="red")
-
-##The visual case
-ggplot(concepts, 
-       aes(x = concept_dist, y = mean)) + 
-  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_line(data=uniV,aes(x=xV, y=yV))+
-  xlab("Visual distance") +ylab("% different")+
-  scale_y_continuous(limits = c(0, 1))+
-  stat_function(fun = Logistic_v, colour="red")
-
-```
-
-The bimodal case
-```{r}
-
-# Bimodal recognition functions
-
-##the bimodal fit 
-model_fit <- function (x,y) {
-   1/(1 + exp(-x*j_coef_a-y*j_coef_v+2*j_coef_a+2*j_coef_v))
-}
-
-##Values of the baseline
-model_base <- function (x,y) {
-   1/(1 + exp(-x*s_coef-y*c_coef+2*s_coef+2*c_coef))
-}
-
-# Add the fit the baeline to data
-
-ms_all <- joint %>% 
-  rename(joint = mean) %>%
-  left_join(select(concepts, concept_dist, mean) %>% 
-              rename(concepts = mean)) %>%
-  left_join(select(sounds, sound_dist, mean) %>% 
-              rename(sounds = mean)) %>%
-  mutate(fit = model_fit(sound_dist, concept_dist)) %>%
-  mutate(base = model_base(sound_dist, concept_dist)) %>%
-  gather(model, pred, concepts, sounds, base, fit)
-
-#Plot Heat map for the data
-ggplot(data = ms_all, aes(x=sound_dist, y=concept_dist, fill=joint)) + 
-  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")
-
-#Plot Heatmap for the baseline
-mybase <- ms_all %>%
-  filter(model=="base")
-
-ggplot(data = mybase, aes(x=sound_dist, y=concept_dist, fill=pred)) + 
-  geom_tile()+scale_fill_continuous(limits=c(0, 1))+xlab("Auditory distance") +ylab("Visual distance")
-
-myfilter <- ms_all %>%
-  filter(model=="fit" | model=="base")
-
-#Correlation models (baseline and fit) to bimodal data 
-ggplot(myfilter, 
-       aes(x = pred, y = joint, col = factor(concept_dist), 
-           shape = factor(sound_dist))) +
- geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
-                  position = position_dodge(width = .1)) + 
-  geom_abline(slope = 1, lty = 2) +
-  facet_grid(model~.)
-
-```
-
-The modality dominance
-```{r}
-
-#Modality dominance coeficent
-a_fit=j_var_v/j_var_a
-a_base=v_var/s_var
-a_Vdom=2*a_base
-a_Sdom=0.5*a_base
-
-#Classification thresholds (prob=0.5) for:
-
-##The basline (combination of the unimodal cases)
-classif_base = function (x, A=a_base) {
-    2*(A+1)-A*x
-}
-
-##Best bivariate fit 
-classif_fit = function (x, A=a_fit) {
-    2*(A+1)-A*x
-}
-
-##A baseline for visual domiance
-classif_Vdom = function (x, A=a_Vdom) {
-    2*(A+1)-A*x
-}
-
-##A baseline for auditory domiance
-classif_Sdom = function (x, A=a_Sdom) {
-    2*(A+1)-A*x
-}
-
-#Sample from the baseline bivariate distribution
-Gaus_base <- data.frame(x=c(rnorm(1000,0,sqrt(s_var)),rnorm(1000,4,sqrt(s_var))),
-          y=c(rnorm(1000,0,sqrt(v_var)),rnorm(1000,4,sqrt(v_var))))
-
-#Plot samples from the bivariate distribution
-ggplot(Gaus_base, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
-  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
-  stat_function(fun = classif_base, colour = "red") +xlab("Auditory") +ylab("Visual")+ scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))
-
-#Sample from the best bivariate fit 
-Gaus_fit <- data.frame(x=c(rnorm(1000,0,sqrt(j_var_a)),rnorm(1000,4,sqrt(j_var_a))),
-          y=c(rnorm(1000,0,sqrt(j_var_v)),rnorm(1000,4,sqrt(j_var_v))))
-
-#Plot samples from the best bivariate fit
-ggplot(Gaus_fit, aes(x,y)) +  stat_density2d(geom="contour",aes(alpha=..level..))+
-  scale_alpha_continuous(limits=c(0,0.03),breaks=1e-6*seq(0,10,by=2))+
-  stat_function(fun = classif_fit, colour = "red") +xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+scale_y_continuous(limits = c(-6, 10))
-
-#Modality dominance?
-ggplot(Gaus_fit, aes(x,y)) +
-  stat_function(fun = classif_base, colour = "red", lty=2) +
-  stat_function(fun = classif_Vdom, colour = "blue", lty=2 )+
-  stat_function(fun = classif_Sdom, colour = "blue", lty=2)+
-  stat_function(fun = classif_fit, colour = "black")+
-  xlab("Auditory") +ylab("Visual") + scale_x_continuous(limits = c(-6, 10))+
-  scale_y_continuous(limits = c(-6, 10))+theme(aspect.ratio = 1)
-
-```

### 2018-08-13 Analysis/process.Rmd
analysis

---
title: "WordRec Experiment"
date: "January 13, 2017"
output:
  html_document:
    number_sections: yes
    toc: yes
---

Libraries.

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(langcog)
theme_set(theme_bw())
```

Data.

```{r}

d_word_summer <- read_delim("data_summer_2.txt", delim = " ") %>%
  filter(type == "Test") %>%
  filter(age != 6) %>%
  filter(code != 'test',
         !is.na(code)) %>%
  filter(grepl('soph', code))

d_all <- d_word_summer %>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0))

```

Process data:

```{r}

data <- d_all %>%
  group_by(ID, sound_dist, concept_dist) %>%
  dplyr::summarise(mean = mean(iscorrect))
  #multi_boot_standard(col = "iscorrect")

#Catch
data_excl <- data %>%
  filter(sound_dist == 'catch') %>%
  ungroup() %>%
  select(ID, mean) %>%
  dplyr::rename(score = mean)

data_catch <- d_all %>%
  left_join(data_excl) %>%
  filter(score > 0.5) %>%
  filter(sound_dist != 'catch')

#Exclude items 
#item_excl <- (data %>%
#  filter(sound_dist != 'catch') %>%
#  filter(mean < 0.25) %>%
#  ungroup() %>%
#  distinct(ID))$ID

#data_reverse <- d_word %>%
# filter(!(ID %in% item_excl))

#data_catch_reverse <- d_word %>%
#  left_join(data_excl) %>%
#  filter(score >= 0.5) %>%
#  filter(!(ID %in% item_excl))

#data_final <- data_good %>%
#  mutate(age2 = ifelse(grepl('4',age), 4, 5))

```

Summary 
```{r }
#{r fig.width=2, fig.height=5}

sum_catch <- data_catch %>%
  group_by(sound_dist, concept_dist) %>%
  #group_by(sound_dist) %>%
  dplyr::summarise(mean = mean(iscorrect),
                   sd = sd(iscorrect),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se)

ggplot(sum_catch, 
      aes(x = sound_dist, y = mean, col = factor(concept_dist))) +
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                 position = position_dodge(width = .1)) + 
  #geom_line(lty = 2) + 
  geom_hline(yintercept = 0.50) +
  xlab("Aud distance") +ylab("% Accurate")+
  scale_colour_discrete(name="Vis Dist")+
theme(legend.title = element_text(size=8))

#Model
data_model <- data_catch %>%
  mutate(s_dist=ifelse(sound_dist=="similar", 0, 1),
         c_dist=ifelse(concept_dist=="similar", 0, 1))

model <- glmer(iscorrect ~ s_dist + c_dist + 
                 (1 | ID) + 
                 (1 | item_object) + 
                 (1 | item_sound), 
               data = data_model, family = binomial())

summary(model)

```

### 2018-12-15 cogsci/cogsci.Rmd
sim exp

---
title: "Word Learning as Network Growth: A Cross-linguistic Analysis"

bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

header-includes:
   - \usepackage[subtle]{savetrees}

author-information: > 
    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract:

    "Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages. We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."

keywords:
    "semantic network, phonological network, network growth, mechanism of word learning"

output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())

#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
#                      echo=F, warning=F, cache=F, message=F, sanitize = T)

knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)

```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
```

# Introduction

How do children acquire words? An important step consists in mapping a phonological form (e.g. the sound "cat") to a semantic referent (the concept CAT). A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008). However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998). Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.

We know that similarity affect word recognition in both adults and children. For example, exposure to a word such as "cat" influences subsequent recognition of phonologically and smantically similar words like "cab" and "dog" (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).

Crucially, similarity influences not only the recognition of know words, but also the learning of novel words. In the phonological domain, Swingley & Aslin (2007) showed that infants found it more challenging to learn a novel word such as "tog" (which is similar a the familiar word "dog") than to learn a word such as "shang" (which is not similar to any words children knew). When learning two novel words, Stager and Werker (1997) found that infatns were more likely to succeed when the words were phonologically distant (e.g., "lif"/"neem"), than when they were phonologcially simialr ("bin/"din"). In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).

That said, previous experimental work has studied the effect of phonological and semantic similarity separately. Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).  However, children  acquire a lexicon which is more richly structured than these special cases. In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains. Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.

One could imagine two learning scenarios. On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al. 1975). For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity. Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms. On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002). Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension. In this study, we explore these hypothesis, bla bla

A second goal of this work is to investigate how the learning mechanism develops over the life span. According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors. To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.  A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind. For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al. 2013; Pajak et al. 2016). Here we explore

Talk a bit about what we do

# Experiment 1
Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers). After training, children performed a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2). Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different. Our predictions were as follows. If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level. Finally, the pair of words that are similar on both levels should be the most difficult to learn.

## Methods

### Participants
We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus. So far, we collected data from N=47 children (mean age= months, F=). An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as specified in the pre-registration).

### Stimuli
The sound stimuli were generated using the MBROLA Speech Synthesizer (Cite) using an American English voice. We generated two similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof"). We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure).
As for the objects used as semantic referents, we used the Dynamic Categories Stimuli (Cite) which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish" (plus the additional category "flower" for the catch trial). These categories are supposed to be naturally occuring kinds that might be seen on an alien planet. In each category, we generated instances that varied in their similarity by manipuating a continuous property controling features of the category's shape. This property was the head fatness for the category "bug", the body strech for "bird", the tail size relative to the body fatness for "fish", the width of the trunk for "tree", and finally center size for "flower". All these continous properties varied on a scale from 0 to 1. We generated "similar" and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively. Examples of the resuting pairs are shown in Figure XX.

###Design 
The experiment consisted of 4 conditions which consisted, each, of a pair of sounds-objects associations. These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design. Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar to the previous ones. It involved different sounds and different objects, and it was used only to select participant who were able to follow the instructions and show minimal learning (not at chance level).

### Procedure
Children were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet. The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task. After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition. In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) follwoed by an additional four testing trials.

In the exposure trials, children saw two objects associated with their corresponding sounds. We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound. The second sound-object association followed on the other side of the screen after 500ms. For both objects, visual stimuli were present for the duration of the sound clip (∼800ms).  In the testing trials, children saw both objects simultaneousely and heard only one sound. They completed the trial by selecting which of the two objects corresponded to the sound. They responded by touching one of the pictures on the tablet.

The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence). We also randomized the on-screen position (left vs. right) of the two pictures on each testing trial. The experiment can be views online using this link XX.

### Results

```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first."}

img <- png::readPNG("figs/growth2.png")
grid::grid.raster(img)

```

Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].  The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT. Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process. Third, it tests the generality of the findings across eight languages.

```{r }

#Import data from saved
data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")

#tidy data
data_long <- data_all_scaled %>%
  gather(predictor, value, length:freq_mika)

data_long <- data_long %>%
  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))

data_long$predictor <- mapValues(data_long$predictor, 
                                 from = c("PAC_assoc", "PAC_phono_t2"), 
                                 to = c("Sem.", "Phono."))

#Compute the correlations 
correlations <-  data_long %>%
  group_by(language, predictor) %>%
  dplyr::summarise(cor = round(cor(AoA, value), 2))

plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)

```

```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}
plot_data_all
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

```

```{r }

#Import data from saved
degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
  dplyr::rename(Dimension = dimension)

plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
  facet_grid(. ~ language)+
  geom_point(size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme_few()+
  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
  xlab("degree") +ylab("probability")

ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)

```

```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power-law distribution should appear as a straight line in this graph."}
plot_dist
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

```

# Networks
## Data
We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
We used the *Words and Sentences* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months). Following previous studies [@storkel2009; @hills2009], we restricted our analysis to nouns. We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008], and we excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.

We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages. Table \ref{tab:stats} gives an overview of the data used. Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available. Note, however, that all languages have at least 60% of nouns translated.

```{r stats, results="asis", echo=FALSE}

statistics <- feather::read_feather("../saved_data/statistics.feather") 
rownames(statistics) <- NULL

tab <- xtable::xtable(statistics,
                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left). We included in our study the subset of these nouns that had available English translations (middle). The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")

print(tab, type="latex", comment = F, table.placement = "H")

#print(statistics, type="latex", comment = F, table.placement = "H")
```

## Semantic networks

We constructed semantic networks following the procedure outlined in @hills2009. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target. To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

## Phonological networks

We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance of 1 [e.g., @storkel2009]. However, in these previous studies the network was built using an adult vocabulary. In the current study, however, network growth models are based on the children's early vocabulary which contains very few word pairs with an edit distance of 1. When using this threshold, the resulting networks were too sparse and uninformative. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2. The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

<!--## Network growth

We tested two network growth scenarios discussed in @hills2009. The first one was *Preferential Attachment* (PAT). According to this mechanism, the network structure of known words predicts what words will be learned next. A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network. The second mechanism was *Preferential Acquisition* (PAC). In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.  Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network. For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to. Thus, according to PAT, the node N1 is more likely to enter the lexicon first. For PAC, each candidate node was characterized with its degree in the entire network. According th PAC, the node N3 is more likely to enter the lexicon first.

-->

# Analysis

## Static properties of the global network

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months). This global network is the end-state towards which both PAT and PAC should converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that are relevant to PAC and/or PAT.

###Connectivity predicts the age of acquisition

Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}). Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages. The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.

###Power-law degree distribution?
We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99]. If the network displays this property, this fact would suggest a PAT-like generative process. Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT. The log-log plots are shown in Figure \ref{fig:degree_distribution}. We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15]. In brief, the analysis consisted in two steps. First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$. Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model. Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we obtained  $p < 0.05$, suggesting that the power law can be ruled out in this particular case.

In sum, the static properties of the global network are *a priori* compatible with both PAT and PAC. In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
<!--
```{r }

#Import data from saved
post_combined <- feather::read_feather("../saved_data/combined_net.feather")

pred_comb <- ggplot(post_combined, aes(x = model, y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = model), size=0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_comb.png", plot = pred_comb, width = 8, height = 4)
```

```{r pred_comb_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language. Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\\% credible intervals (computed using the highest density intervals). "}
pred_comb
#img <- png::readPNG("figs/pred_comb.png")
#grid::grid.raster(img)
```
-->

```{r }

#Import data from saved
individual <- feather::read_feather("../saved_data/individual_both.feather") %>%
  filter(Evaluation =='Fit') %>%
  select(-Evaluation) %>%
  mutate(Test = 'Individual')

combined <- feather::read_feather("../saved_data/combined_net.feather") %>%
  dplyr::rename(lower = hdi_lower,
                upper = hdi_upper) %>%
  mutate(Test = 'Combined')

growth_all <- bind_rows(individual, combined)

pred_ind <- ggplot(growth_all, aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7, axis.text.x = element_text(size=8))

ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)

```

```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals). Positive values mean that learning proceeds according to the predictions of the growth scenario. Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}

pred_ind

#img <- png::readPNG("figs/pred_ind.png")
#grid::grid.raster(img)
```

## Network growth models

### How does each growth scenario predict noun development?

To test the network growth scenarios, we fit different growth models to the data.  We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function: 
\begin{equation}
 p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
\end{equation}

\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient). A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for an illustration of how growth values $d_i$ are defined in each growth scenario). The normalization includes all words that could be learned at that month.

We estimated the parameter $\beta$ using a Bayesian approach. The inference was performed using the probabilistic programming language  WebPPL [@dippl]. We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.

<!--Besides fitting a growth model to the data, we conducted a separate evaluation. This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.  For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.-->

<!--The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{We do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}-->For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT. Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.} The PAC model also fits better than PAT for phonological networks. We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).

### What is the relative contribution of each growth model?

Above we evaluated the network growth scenarios individually. As a next step, we analyzed their relative contribution to the learning process. This was done through adding more fitted parameters to the model, that is, by substituting $\beta d_i$ in formula (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC. Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both phonological and semantic networks contribute to lexical growth, but the phonological network appears to be stronger and more consistent across languages. In summary, the findings show that both semantic and phonological networks contribute to the learning process, and that they both grow primarily by PAC, relying on the external connectivity in the learning environment, rather than the internal connectivity in the acquired lexicon.

```{r }

#Import data from saved
regressions <- feather::read_feather("../saved_data/regressions_bis.feather")

pred_regressions <- ggplot(regressions, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor), size=0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=4)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_regressions.png", plot = pred_regressions, width = 8, height = 4)
```

```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA)."}

pred_regressions

#img <- png::readPNG("figs/pred_regressions.png")
#grid::grid.raster(img)
```

## Comparison to other predictors of age of acquisition

We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contributes to noun learning across languages. However, we know that other factors influence learning as well [e.g., @braginsky2016]. Next we investigated how semantic and phonological connectivity interact with two other factors. The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g. @goodman2008]. The second factor is word length, which correlates with phonological connectivity. <!-- [@pisoni1985].-->

Since PAT was uninformative, we dropped it from this analysis, keeping only PAC. This simplified the model because we no longer needed to fit growth month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.} A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.

We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.} For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g. "father" counts as "daddy"). For word length, we counted the number of phonemes in our generated IPA transcription.

We conducted two analyses. We fit a linear regression for each language, and we fit a linear mixed-effect model to all the data pooled across languages, with language as a random effect. Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and Figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled). The findings were as follows. Overall, frequency is the largest and most consistent predictor of age of acquisition, replicating results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015]. Word length predicts learning in some languages such as Croatian and Norwegian, but not in others (including English). It remains, however, a significant predictor in the global model. As for the factors of interest, i.e., semantic and phonological connectivity, we also found cross-linguistic differences. Phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but not in English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This contrasts with the original finding in Hills et al. 2009. However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates. Another important difference is the number of words tested: Our study uses a larger set of nouns.} Despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.

# Discussion

The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers. We compared two network growth scenarios and assessed their relative contributions across eight languages. One scenario, PAT, described a rich-get-richer network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.  Our findings largely replicate the results obtained by @hills2009: Semantic networks grow by preferential acquisition, not by preferential attachment. A novel finding is that phonological networks also grow primarily by preferential acquisition. Moreover, both semantic and phonological connectivity in the learning environment predict growth. These findings generalize well across languages. When pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others. Nevertheless, this cross-linguistic variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language. In fact, both phonological and semantic connectivity are significant predictors when data are pooled across languages.

```{r }

#Import data from saved
regression_all <- feather::read_feather("../saved_data/regression_all_bis.feather")
regression_all_noCov <- feather::read_feather("../saved_data/regression_all_bis_noCov.feather")

pred_regression_all <- ggplot(regression_all, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor), size=0.3)+
  geom_pointrange(data=regression_all_noCov,
                  aes(ymin = lower, ymax = upper, col = predictor),
                  position = position_dodge(width = .3),
                  linetype=1,
                  size = 0.7,
                  fatten = 1.5,
                  alpha = 0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_regression_all.png", plot = pred_regression_all, width = 4, height = 2)
```

```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect. Ranges indicate 95\\% confidence intervals. Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}

pred_regression_all

#img <- png::readPNG("figs/pred_regression_all.png")
#grid::grid.raster(img)
```

Children start by learning words that have high semantic and phonological similarity to a variety of other words in the learning environment, not in the child's available lexicon.  This result suggests that children are sensitive to connectivity even without having first acquired the connected words. How can children indirectly detect highly connected words, and why would such words be more readily learned?

In the semantic case, the networks are based on free association norms. These associations can be (partly) derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts. In a network structure, highly connected words would be the words that co-occur with many other words in various contexts. Why would such words be easier to learn? One possibility, suggested by @hills2010, is that the referents of these words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].

In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. Even infants show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994]. Moreover, phonotactic probability facilitates learning and recognition [e.g., @storkel2001]. 
In other words, children's sensitivity to local phonotactic regularities might lead them to learn higher-probability words more easily. This learning effect, in turn, would lead to an observed pattern of growth that would appear to follow the PAC growth model even though learners themselves would only be tracking local statistics.

Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms in both the semantic and phonological domains. One question for future experimental work is whether such patterns of growth can be produced in controlled behavioral experiments.
<!--Finally, this study shares a number of limitations with previous studies using similar research strategy and dataset.For instance, we used normative age of acquisition. However, individual children may follow different learning trajectories. The use of longitudinal data would allow us to assess how the aggregate behavior relates to these individual trajectories [e.g., typical vs. late talkers, @beckage2011]. Moreover,In particular, the results provide correlational but not causal evidence. Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments. -->

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}

# Acknowledgements

This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.

# References

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent

### 2018-12-15 cogsci/cogsci.tex
sim exp

--- 2018-12-15 cogsci/cogsci.Rmd
@@
----
-title: "Word Learning as Network Growth: A Cross-linguistic Analysis"
+% Template for Cogsci submission with R Markdown
 
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
+% Stuff changed from original Markdown PLOS Template
+\documentclass[10pt, letterpaper]{article}
 
-header-includes:
-   - \usepackage[subtle]{savetrees}
+\usepackage{cogsci}
+\usepackage{pslatex}
+\usepackage{float}
+\usepackage{caption}
 
-author-information: > 
-    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
-    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
-    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
 
-abstract:
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
 
-    "Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions.
-Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
-One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words.
-Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon.
-The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages.
-We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically.
-The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."
+% hyperref package, useful for hyperlinks
+\usepackage{hyperref}
 
-keywords:
-    "semantic network, phonological network, network growth, mechanism of word learning"
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
+\usepackage{graphicx}
 
-output: cogsci2016::cogsci_paper
----
+% Sweave(-like)
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
+\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
+\newenvironment{Schunk}{}{}
+\DefineVerbatimEnvironment{Code}{Verbatim}{}
+\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
+\newenvironment{CodeChunk}{}{}
 
-```{r global_options, include=FALSE}
-rm(list=ls())
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
 
-#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
-#                      echo=F, warning=F, cache=F, message=F, sanitize = T)
+\usepackage{color}
 
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, message=F, sanitize = T)
+% Use doublespacing - comment out for single spacing
+%\usepackage{setspace}
+%\doublespacing
 
-```
+% % Text layout
+% \topmargin 0.0cm
+% \oddsidemargin 0.5cm
+% \evensidemargin 0.5cm
+% \textwidth 16cm
+% \textheight 21cm
 
-```{r, libraries}
-library(png)
-library(grid)
-library(ggplot2)
-library(ggthemes)
-library(xtable)
-options(xtable.comment = FALSE)
-library(purrr)
-library(readr)
-library(ggplot2)
-library(langcog)
-library(boot)
-#library(lazyeval)
-library(dplyr)
-library(tidyr)
-library(wordbankr)
-library(directlabels)
-#library(scales)
-library(stringr)
-library(lmtest)
-library(rwebppl)
-library(jsonlite)
-library(nlme)
-library(feather)
-library(broom)
-library(HDInterval)
-library(BBmisc)
-```
+\title{Word Learning as Network Growth: A Cross-linguistic Analysis}
 
-# Introduction
+\usepackage[subtle]{savetrees}
 
-How do children acquire words?
-An important step consists in mapping a phonological form (e.g.
-the sound "cat") to a semantic referent (the concept CAT).
-A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008).
-However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998).
-Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.
+\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois \And {\large \bf Michael C.
+Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
 
-We know that similarity affect word recognition in both adults and children.
-For example, exposure to a word such as "cat" influences subsequent recognition of phonologically and smantically similar words like "cab" and "dog" (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
+\begin{document}
 
-Crucially, similarity influences not only the recognition of know words, but also the learning of novel words.
-In the phonological domain, Swingley & Aslin (2007) showed that infants found it more challenging to learn a novel word such as "tog" (which is similar a the familiar word "dog") than to learn a word such as "shang" (which is not similar to any words children knew).
-When learning two novel words, Stager and Werker (1997) found that infatns were more likely to succeed when the words were phonologically distant (e.g., "lif"/"neem"), than when they were phonologcially simialr ("bin/"din").
-In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).
+\maketitle
 
-That said, previous experimental work has studied the effect of phonological and semantic similarity separately.
-Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).
-However, children  acquire a lexicon which is more richly structured than these special cases.
-In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains.
-Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.
+\begin{abstract}
+Children tend to produce words earlier when they are connected to a
+variety of other words along both the phonological and semantic
+dimensions. Though this connectivity effect has been extensively
+documented, little is known about the underlying developmental
+mechanism. One view suggests that learning is primarily driven by a
+network growth model where highly connected words in the child's early
+lexicon attract similar words. Another view suggests that learning is
+driven by highly connected words in the external learning environment
+instead of highly connected words in the early internal lexicon. The
+present study tests both scenarios systematically in both the
+phonological and semantic domains, and across 8 languages. We show that
+external connectivity in the learning environment drives growth in both
+the semantic and the phonological networks, and that this pattern is
+consistent cross-linguistically. The findings suggest a word learning
+mechanism where children harness their statistical learning abilities to
+(indirectly) detect and learn highly connected words in the learning
+environment.
 
-One could imagine two learning scenarios.
-On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al.
-1975).
-For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity.
-Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms.
-On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002).
-Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension.
-In this study, we explore these hypothesis, bla bla
+\textbf{Keywords:}
+semantic network, phonological network, network growth, mechanism of
+word learning
+\end{abstract}
 
-A second goal of this work is to investigate how the learning mechanism develops over the life span.
-According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors.
-To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.
-A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind.
-For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al.
-2013; Pajak et al.
-2016).
-Here we explore
+\section{Introduction}\label{introduction}
+
+How do children acquire words? An important step consists in mapping a
+phonological form (e.g.~the sound ``cat'') to a semantic referent (the
+concept CAT). A large body of work has been devoted to explore the
+mechanism of this mapping (Quine, 1960; Markman, 1990; Smith and Yu,
+2008). However, words do not exist in a vacuum; they are organized into
+a strcuture based on both semantic and phonological similarity
+principles (e.g., Collins \& Loftus, 1975; Luce \& Pisoni, 1998). A more
+accurate understanding of word learning should account not only for how
+sounds are mapped to meanings, but also for how sound similarity and
+meaning similarity may influence the process of aqusition.
+
+We know that similarity affect word recognition in both adults and
+children. For example, exposure to a word such as ``cat'' influences
+subsequent recognition of phonologically and smantically similar words
+like ``cab'' and ``dog'' (Goldinger, Luce \& Pisoni, 1989; McNamara,
+2006; Arias-Trejo \& Plunkett, 2010; Mani \& Plunkett, 2011).
+
+Crucially, similarity influences not only the recognition of know words,
+but also the learning of novel words. For example, Swingley \& Aslin
+(2007) showed that infants found it more challenging to learn the
+meaning of a novel word such as ``tog'' (which is similar a the familiar
+word ``dog'') than to learn the meaning of a word such as ``shang''
+(which is not similar to any words children knew). When learning two
+novel words, Stager and Werker (1997) found that infatns were more
+likely to succeed when these words were phonologically distant (e.g.,
+``lif''/``neem''), than when they were phonologcially simialr
+(``bin/''din``). Besides, children learn the semantic relationship among
+newly learned words spontaneousely (Wojcik \& Saffran, 2013), and they
+prioritize the acquisition of words that are distinct in the semantic
+space (Engelthaler \& Hills, 2017).
+
+That said, previous experimental work has studied the effect of
+phonological and semantic similarity separately. Some studied the
+mechanism of word learning using a toy lexicon where only the
+phonological similarity varied (e.g., Stager and Werker, 1997), and
+others studied the learning of a toy lexicon where only the semantic
+similarity varied (e.g., Wojcik \& Saffran, 2013). However, children
+acquire a lexicon which is more richly structured than these special
+cases. In particular, as reviewed abvove, the end-state lexicon involves
+variability along both the phonological and semantic domains. Thus, to
+have a deeper understanding of word acquisition in the real world, it is
+crucial to study how learners acquire a lexicon that simulates this
+bi-dimensional variation.
+
+One could imagine two learning scenarios. On the first one, children's
+learning, at least in some challenging situations, is primarily
+determined by one dimension (Sloutsky \& Napolitano, 2003; Colavita et
+al. 1975). For example, it is possible that similar sounding words are
+confusable and hard to learn regardless of their semantic similarity.
+Vice-versa, similar meanings might be challenging to learn regardless of
+the phonological similarity of their forms. On the second scenario,
+learners combine cues from both dimensions to optimize their learning
+(Fourtassi and Frank, 2018; Ernst \& Banks, 2002). Thus, confusability
+that may arise from high similarity along one dimension can be mitigated
+via higher distance from the other dimension. In this study, we explore
+these hypothesis, bla bla
+
+A second goal of this work is to investigate how the learning mechanism
+develops over the life span. According to one hypothesis, adults use
+qualitatively distinct learning mechanisms than children, due, for
+example, to maturational factors. To illustrate, in the experimental
+setting used in Stager and Werker (1997), children's difficulty with
+learning similar sounding words--despite their ability to perceptually
+differentiate them--might be attributed to their inferior working
+memory, hindering their ability to attend simultaneously to the sound
+contrast and the meanings. A second hypothesis proposes that learners
+use fundamentally similar mechanisms across the life span, and that the
+difference might be one of degree, not kind. For example, though they
+have vastly greater working memory capacity, adults show patterns of
+word processing and learning which parallel results obtained with
+children in Stager and Werker's study (White et al. 2013; Pajak et al.
+2016). Here we explore
 
@@
 
-# Experiment 1
-Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
-After training, children performed a series of two-alternative forced choices.
-In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2).
-Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different.
-Our predictions were as follows.
-If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level.
-Finally, the pair of words that are similar on both levels should be the most difficult to learn.
+\section{Experiment 1}\label{experiment-1}
 
-## Methods
+Children were trained to learn the association between pairs of
+nonesense words (e.g., ``lif''/``neem'') and pairs of objects (e.g., two
+flowers). After training, children performed a series of two-alternative
+forced choices. In each testing trial, one of the two sounds is uttered
+(e.g., ``lif'') and participants choose the corresponding object from
+the two alternatives (e.g., flower 1 or flower 2). Each child learned an
+artificial lexicon where both the pairs of sounds and the pairs of
+objects can be similar or different. Our predictions were as follows. If
+the sound and meaning interact in word learning, then the pair of words
+that differ on both the meaning and sound levels should be the easiest
+to learn, followed by the pairs of words that are different on one
+level, but similar on another level. Finally, the pair of words that are
+similar on both levels should be the most difficult to learn.
 
-### Participants
-We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
-So far, we collected data from N=47 children (mean age= months, F=).
-An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as specified in the pre-registration).
+\subsection{Methods}\label{methods}
 
-### Stimuli
-The sound stimuli were generated using the MBROLA Speech Synthesizer (Cite) using an American English voice.
-We generated two similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof").
-We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure).
-As for the objects used as semantic referents, we used the Dynamic Categories Stimuli (Cite) which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish" (plus the additional category "flower" for the catch trial).
-These categories are supposed to be naturally occuring kinds that might be seen on an alien planet.
-In each category, we generated instances that varied in their similarity by manipuating a continuous property controling features of the category's shape.
-This property was the head fatness for the category "bug", the body strech for "bird", the tail size relative to the body fatness for "fish", the width of the trunk for "tree", and finally center size for "flower".
-All these continous properties varied on a scale from 0 to 1.
-We generated "similar" and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively.
-Examples of the resuting pairs are shown in Figure XX.
+\subsubsection{Participants}\label{participants}
 
-###Design 
-The experiment consisted of 4 conditions which consisted, each, of a pair of sounds-objects associations.
-These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design.
-Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar to the previous ones.
-It involved different sounds and different objects, and it was used only to select participant who were able to follow the instructions and show minimal learning (not at chance level).
+We planned to recruit a sample of 60 children ages 4-5 years from the
+Bing Nursery School on Stanford University's campus. So far, we
+collected data from N=47 children (mean age= months, F=). An additional
+28 children participated but were removed from analyses because they
+were not above chance on the catch trials (as specified in the
+pre-registration).
 
-### Procedure
-Children were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time.
-The experimenter explained that the game consisted in learning some words spoken in an alien planet.
-The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task.
-After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition.
-In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) follwoed by an additional four testing trials.
+\subsubsection{Stimuli}\label{stimuli}
 
-In the exposure trials, children saw two objects associated with their corresponding sounds.
-We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound.
-The second sound-object association followed on the other side of the screen after 500ms.
-For both objects, visual stimuli were present for the duration of the sound clip (∼800ms).
-In the testing trials, children saw both objects simultaneousely and heard only one sound.
-They completed the trial by selecting which of the two objects corresponded to the sound.
-They responded by touching one of the pictures on the tablet.
+The sound stimuli were generated using the MBROLA Speech Synthesizer
+(Cite) using an American English voice. We generated two similar sound
+pairs (``aka''/``ama'' and ``ada''/``aba'') and two different sound
+pairs (``lif''/``neem'' and ``zem''/``doof''). We generated a addtional
+pair (``nak''/``veep'') which we used in the catch trial (see
+Procedure). As for the objects used as semantic referents, we used the
+Dynamic Categories Stimuli (Cite) which allowed us to generate objects
+in four different categories: ``tree'', ``bird'', ``bug'', and ``fish''
+(plus the additional category ``flower'' for the catch trial). These
+categories are supposed to be naturally occuring kinds that might be
+seen on an alien planet. In each category, we generated instances that
+varied in their similarity by manipuating a continuous property
+controling features of the category's shape. This property was the head
+fatness for the category ``bug'', the body strech for ``bird'', the tail
+size relative to the body fatness for ``fish'', the width of the trunk
+for ``tree'', and finally center size for ``flower''. All these
+continous properties varied on a scale from 0 to 1. We generated
+``similar'' and ``different'' objects' pairs (whithin each category) by
+setting the values of this properties to 0 and 0.5, and to 0 and 1,
+respectively. Examples of the resuting pairs are shown in Figure XX.
 
-The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence).
-We also randomized the on-screen position (left vs.
-right) of the two pictures on each testing trial.
-The experiment can be views online using this link XX.
+\subsubsection{Design}\label{design}
 
-### Results
+The experiment consisted of 4 conditions which consisted, each, of a
+pair of sounds-objects associations. These conditions were constructed
+by crossing the sound's degree of similarity with the object's degree of
+similarity leading to a 2x2 factorial design. Besides the 4 conditions,
+we also tested participants on a fifth catch condition which was similar
+to the previous ones. It involved different sounds and different
+objects, and it was used only to select participant who were able to
+follow the instructions and show minimal learning (not at chance level).
 
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios.
+\subsubsection{Procedure}\label{procedure}
+
+Children were asked if they would be willing to play a game on a tablet
+with the experimenter and were informed that they could stop playing at
+any time. The experimenter explained that the game consisted in learning
+some words spoken in an alien planet. The experiment began with two
+simple examples (not included in the analysis), and in these examples
+children were given feedback from the experimenter so as to make sure
+they correctly understood the structure of the task. After the
+introduction and examples, children were tested in a sequence of five
+conditions: the four experimental conditions plus the catch condition.
+In each condition, participants saw a first block of four exposure
+trials followed by four testing trials, and a second block of two
+exposure trials (for memory refreshment) follwoed by an additional four
+testing trials.
+
+In the exposure trials, children saw two objects associated with their
+corresponding sounds. We presented the first object on the left side of
+the tablet's screen simultaneously with the corresponding sound. The
+second sound-object association followed on the other side of the screen
+after 500ms. For both objects, visual stimuli were present for the
+duration of the sound clip (∼800ms). In the testing trials, children saw
+both objects simultaneousely and heard only one sound. They completed
+the trial by selecting which of the two objects corresponded to the
+sound. They responded by touching one of the pictures on the tablet.
+
+The object-sound pairings were randomized across participants, as was
+the order of the conditions (except for the catch condition which was
+always placed in the middle of the testing sequence). We also randomized
+the on-screen position (left vs.~right) of the two pictures on each
+testing trial. The experiment can be views online using this link XX.
+
+\subsubsection{Results}\label{results}
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/growth-1}
+
+}
+
+\caption{\label{fig:growth}Illustration of the growth scenarios.
 Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
@@
 For PAC, the utility of a candidate node is its degree in the entire network.
-According to PAC, the node E2 is more likely to enter the lexicon first."}
+According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
+\end{figure}
+\end{CodeChunk}
 
-img <- png::readPNG("figs/growth2.png")
-grid::grid.raster(img)
+Studies that investigate lexical network growth have focused on semantic
+networks using English data (Hills, Maouene, Riordan, \& Smith, 2010;
+Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Steyvers \& Tenenbaum,
+2005). The novelty of the current study is threefold: First, it
+investigates whether phonological networks, like semantic networks, grow
+by PAC, or if they rather grow by PAT. Second, it provides a systematic
+comparison of both network growth scenarios in the phonological and the
+semantic domains and assesses their relative contribution to the
+learning process. Third, it tests the generality of the findings across
+eight languages.
 
-```
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].
-The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
-Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process.
-Third, it tests the generality of the findings across eight languages.
+{\centering \includegraphics{figs/all_data-1}
 
-```{r }
+}
 
-#Import data from saved
-data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")
+\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
+\end{figure*}
+\end{CodeChunk}
 
-#tidy data
-data_long <- data_all_scaled %>%
-  gather(predictor, value, length:freq_mika)
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-data_long <- data_long %>%
-  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
-  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))
+{\centering \includegraphics{figs/degree_distribution-1}
 
-data_long$predictor <- mapValues(data_long$predictor, 
-                                 from = c("PAC_assoc", "PAC_phono_t2"), 
-                                 to = c("Sem.", "Phono."))
+}
 
-#Compute the correlations 
-correlations <-  data_long %>%
-  group_by(language, predictor) %>%
-  dplyr::summarise(cor = round(cor(AoA, value), 2))
+\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
+A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
+\end{figure*}
+\end{CodeChunk}
 
-plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
-  facet_grid(predictor ~ language)+#, scales = "free") +
-  geom_jitter(#aes(colour = lexical_class),
-    colour = solarized_palette(1),
-    size = 0.5, alpha = 0.5) +
-  geom_abline(slope = -1)+
-  coord_cartesian(xlim=c(-1,5))+
-  #scale_x_continuous(limits=c(-2,5))+
-  scale_y_continuous(breaks =c(15,25,35))+
-  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
-  scale_colour_solarized(name = "") +
-  theme_few()+
-  #theme_bw()+
-  theme(aspect.ratio = 0.7, 
-        plot.margin=grid::unit(c(0,0,0,0), "mm")
-        )+
-  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
-  xlab("degree z-score") +ylab("AoA")
+\section{Networks}\label{networks}
 
-ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
+\subsection{Data}\label{data}
 
-```
+We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
+2017), an open repository aggregating cross-linguistic language
+developmental data of the MacArthur-Bates Communicative Development
+Inventory (CDI), a parent report vocabulary checklist. Parent report is
+a reliable and valid measure of children's vocabulary that allows for
+the cost-effective collection of datasets large enough to test
+network-based models of acquisition (Fenson et al., 1994). We used the
+\emph{Words and Sentences} version of the CDI which contains the
+productive vocabulary of toddlers (age varied between 16 to 36 months).
+Following previous studies (Hills et al., 2009; Storkel, 2009), we
+restricted our analysis to nouns. We defined the age of acquisition of a
+given word by the month at which this word was produced by at least 50\%
+of children (J. C. Goodman, Dale, \& Li, 2008), and we excluded nouns
+that have not been learned (according to this criterion) by the last
+month for which we have CDI data.
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits."}
-plot_data_all
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
+We obtained these nouns in eight languages: Croatian, Danish, English,
+Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
+nouns that had entries in the Florida Association Norms (see below).
+Since these norms are available only in English, we used the
+hand-checked translation equivalents provided by Braginsky, Yurovsky,
+Marchman, \& Frank (2016), allowing us to use the English association
+norms across languages. Table \ref{tab:stats} gives an overview of the
+data used. Translation equivalents were originally constructed for a
+subset of words appearing on the toddler CDI form, and so not all words
+are currently available. Note, however, that all languages have at least
+60\% of nouns translated.
 
-```
+\begin{table}[H]
+\centering
+\begin{tabular}{rlrrr}
+  \hline
+ & language & total & translated & normed \\ 
+  \hline
+1 & Croatian & 253 & 177 & 170 \\ 
+  2 & Danish & 295 & 198 & 187 \\ 
+  3 & English & 296 & 296 & 274 \\ 
+  4 & Italian & 311 & 203 & 194 \\ 
+  5 & Norwegian & 305 & 193 & 186 \\ 
+  6 & Russian & 311 & 311 & 285 \\ 
+  7 & Spanish & 240 & 173 & 163 \\ 
+  8 & Turkish & 293 & 175 & 164 \\ 
+   \hline
+\end{tabular}
+\caption{\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
+We included in our study the subset of these nouns that had available English translations (middle).
+The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).}
+\end{table}
 
-```{r }
+\subsection{Semantic networks}\label{semantic-networks}
 
-#Import data from saved
-degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
-  dplyr::rename(Dimension = dimension)
+We constructed semantic networks following the procedure outlined in
+Hills et al. (2009). We used as an index of semantic relatedness the
+Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
+This dataset was collected by giving adult participants a word (the
+cue), and asking them to write the first word that comes to mind (the
+target). For example, when given the word ``ball'', they might answer
+with the word ``game''. A pair of nodes were connected by a directed
+link from the cue to the target if there was a cue-target relationship
+between these nodes in the association norms. The connectivity of a
+given node was characterized by its \emph{indegree}: the number of links
+for which the word was the target. To model growth from month to month,
+we constructed a different network at each month, based on the words
+that have been acquired by that month.
 
-plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
-  facet_grid(. ~ language)+
-  geom_point(size = 0.5, alpha = 0.5) +
-  scale_y_log10() + scale_x_log10() +
-  theme_few()+
-  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
-  xlab("degree") +ylab("probability")
+\subsection{Phonological networks}\label{phonological-networks}
 
-ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)
+We generated approximate International Phonetic Alphabet (IPA)
+transcriptions from the orthographic transcription, across languages,
+using the open source text-to-speech software
+\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
+the Levenshtein distance (also known as edit distance) as a measure of
+phonological relatedness between two nodes. The measure counts the
+minimum number of operations (insertions, deletions, substitutions)
+required to change one string into another.
 
-```
+In previous studies, two nodes were linked if they had an edit distance
+of 1 (e.g., Storkel, 2009). However, in these previous studies the
+network was built using an adult vocabulary. In the current study,
+however, network growth models are based on the children's early
+vocabulary which contains very few word pairs with an edit distance of
+1. When using this threshold, the resulting networks were too sparse and
+uninformative. Thus, we increased the threshold from 1 to 2, that is,
+two nodes were related if their edit distance was equal to 1 or 2. The
+connectivity of a given node was characterized with its \emph{degree}:
+the number of links it shares with other words.
 
-```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
-A perfect power-law distribution should appear as a straight line in this graph."}
-plot_dist
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
+\section{Analysis}\label{analysis}
 
-```
-
-# Networks
-## Data
-We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist.
-Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
-We used the *Words and Sentences* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies [@storkel2009; @hills2009], we restricted our analysis to nouns.
-We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008], and we excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.
-
-We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish.
-We used the subset of nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages.
-Table \ref{tab:stats} gives an overview of the data used.
-Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available.
-Note, however, that all languages have at least 60% of nouns translated.
-
-```{r stats, results="asis", echo=FALSE}
-
-statistics <- feather::read_feather("../saved_data/statistics.feather") 
-rownames(statistics) <- NULL
-
-tab <- xtable::xtable(statistics,
-                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
-We included in our study the subset of these nouns that had available English translations (middle).
-The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")
-
-print(tab, type="latex", comment = F, table.placement = "H")
-
-#print(statistics, type="latex", comment = F, table.placement = "H")
-```
-
-## Semantic networks
-
-We constructed semantic networks following the procedure outlined in @hills2009.
-We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
-This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
-For example, when given the word "ball", they might answer with the word "game".
-A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
-The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.
-To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.
-
-## Phonological networks
-
-We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
-The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
-
-In previous studies, two nodes were linked if they had an edit distance of 1 [e.g., @storkel2009].
-However, in these previous studies the network was built using an adult vocabulary.
-In the current study, however, network growth models are based on the children's early vocabulary which contains very few word pairs with an edit distance of 1.
-When using this threshold, the resulting networks were too sparse and uninformative.
-Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.
-The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
-
-<!--## Network growth
-
-We tested two network growth scenarios discussed in @hills2009.
-The first one was *Preferential Attachment* (PAT).
-According to this mechanism, the network structure of known words predicts what words will be learned next.
-A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network.
-The second mechanism was *Preferential Acquisition* (PAC).
-In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.
-Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
-For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to.
-Thus, according to PAT, the node N1 is more likely to enter the lexicon first.
-For PAC, each candidate node was characterized with its degree in the entire network.
-According th PAC, the node N3 is more likely to enter the lexicon first.
-
--->
-
-# Analysis
-
-## Static properties of the global network
+\subsection{Static properties of the global
+network}\label{static-properties-of-the-global-network}
 
 We start by analyzing word connectivity in the global (static) network.
-We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months).
-This global network is the end-state towards which both PAT and PAC should converge by the last month of learning.
-Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment.
-Below we analyze properties of this global networks that are relevant to PAC and/or PAT.
+We constructed this network using nouns learned by the oldest age for
+which we have CDI data (e.g., in English this corresponds to the network
+by 30 months). This global network is the end-state towards which both
+PAT and PAC should converge by the last month of learning. Moreover,
+following Hills et al. (2009), we used this end-state network as a proxy
+for the external connectivity in the learning environment. Below we
+analyze properties of this global networks that are relevant to PAC
+and/or PAT.
 
-###Connectivity predicts the age of acquisition
+\subsubsection{Connectivity predicts the age of
+acquisition}\label{connectivity-predicts-the-age-of-acquisition}
 
-Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}).
-Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
+Connectivity in the global network is directly related to PAC as it
+represents the explicit criterion PAC uses to determine what words
+should be learned first (Figure \ref{fig:growth}). Therefore, a direct
+consequence of a PAC-like growth scenario is a correlation between
+connectivity in the global network and the age of
+acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
 Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
-For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
-The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.
+Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
+Figure \ref{fig:data_all} shows how the age of acquisition for each word
+varies as a function of its degree (or indegree for the semantic
+network). For ease of visual comparison, the predictor (i.e., the
+degree) was centered and scaled across languages. The plots show,
+overall, a negative correlation between the month of acquisition and the
+degree, indicating that nouns with higher degrees are generally learned
+earlier.
 
-###Power-law degree distribution?
-We also analyzed the global network's degree distribution.
-The shape of this distribution is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
-If the network displays this property, this fact would suggest a PAT-like generative process.
-Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT.
-The log-log plots are shown in Figure \ref{fig:degree_distribution}.
-We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
-In brief, the analysis consisted in two steps.
-First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$.
-Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
-Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we obtained  $p < 0.05$, suggesting that the power law can be ruled out in this particular case.
+\subsubsection{Power-law degree
+distribution?}\label{power-law-degree-distribution}
 
-In sum, the static properties of the global network are *a priori* compatible with both PAT and PAC.
-In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
-<!--
-```{r }
+We also analyzed the global network's degree distribution. The shape of
+this distribution is particularly relevant to PAT as this growth
+scenario is known to generate networks with a power-law degree
+distribution (i.e., a distribution of the form
+\(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
+network displays this property, this fact would suggest a PAT-like
+generative process. Conversely, if the degree distribution does not
+follow a power law, this fact would weaken the case for PAT. The log-log
+plots are shown in Figure \ref{fig:degree_distribution}. We fit a power
+law to each empirical degree distribution following the procedure
+outlined in Clauset, Shalizi, \& Newman (2009) and using the related R
+package (poweRlaw, Gillespie, 2015). In brief, the analysis consisted in
+two steps. First, we derived the optimal cut-off, \(k_{min}\), above
+which the distribution is more likely to follow a power
+law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
+and we estimate the corresponding scaling parameter \(\alpha\). Second
+we calculated the goodness-to-fit, which resulted in a \(p\)-value
+quantifying the plausibility of the model. Overall, we could not reject
+the null hypothesis of a power-law distribution: the \(p\)-value was
+generally above 0.1, except for the Italian phonological network where
+we obtained \(p < 0.05\), suggesting that the power law can be ruled out
+in this particular case.
 
-#Import data from saved
-post_combined <- feather::read_feather("../saved_data/combined_net.feather")
+In sum, the static properties of the global network are \emph{a priori}
+compatible with both PAT and PAC. In order to decide between these two
+developmental scenarios, we need to fit explicit growth models to the
+data.
 
-pred_comb <- ggplot(post_combined, aes(x = model, y = mean)) +
-  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = model), size=0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-ggsave("figs/pred_comb.png", plot = pred_comb, width = 8, height = 4)
-```
+{\centering \includegraphics{figs/pred_ind_img-1}
 
-```{r pred_comb_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language.
-Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\\% credible intervals (computed using the highest density intervals).
-"}
-pred_comb
-#img <- png::readPNG("figs/pred_comb.png")
-#grid::grid.raster(img)
-```
--->
+}
 
-```{r }
+\caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
+Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).
+Positive values mean that learning proceeds according to the predictions of the growth scenario.
+Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:pred_ind_img}
+\end{figure*}
+\end{CodeChunk}
 
-#Import data from saved
-individual <- feather::read_feather("../saved_data/individual_both.feather") %>%
-  filter(Evaluation =='Fit') %>%
-  select(-Evaluation) %>%
-  mutate(Test = 'Individual')
+\subsection{Network growth models}\label{network-growth-models}
 
-combined <- feather::read_feather("../saved_data/combined_net.feather") %>%
-  dplyr::rename(lower = hdi_lower,
-                upper = hdi_upper) %>%
-  mutate(Test = 'Combined')
+\subsubsection{How does each growth scenario predict noun
+development?}\label{how-does-each-growth-scenario-predict-noun-development}
 
-growth_all <- bind_rows(individual, combined)
+To test the network growth scenarios, we fit different growth models to
+the data. We calculated the probability that a word \(w_i\), with a
+growth value \(d_i\) would enter the lexicon at a given month, using a
+softmax function:
 
-pred_ind <- ggplot(growth_all, aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Test),
-                  position = position_dodge(width = .5),
-                  size = 0.5,
-                  fatten = 0.5)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7, axis.text.x = element_text(size=8))
-
-ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)
-
-```
-
-```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
-Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals).
-Positive values mean that learning proceeds according to the predictions of the growth scenario.
-Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}
-
-pred_ind
-
-#img <- png::readPNG("figs/pred_ind.png")
-#grid::grid.raster(img)
-```
-
-## Network growth models
-
-### How does each growth scenario predict noun development?
-
-To test the network growth scenarios, we fit different growth models to the data.
-We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function:
 \begin{equation}
@@
 
-\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
-A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for an illustration of how growth values $d_i$ are defined in each growth scenario).
-The normalization includes all words that could be learned at that month.
+\noindent where \(\beta\) is a fitted parameter that captures the
+magnitude of the relationship between network parameters and growth
+(analogous to a regression coefficient). A positive value of \(\beta\)
+means that words with higher growth values \(d_i\) are acquired first,
+and a negative value means that words with lower growth values are
+acquired first (see Figure \ref{fig:growth} for an illustration of how
+growth values \(d_i\) are defined in each growth scenario). The
+normalization includes all words that could be learned at that month.
 
-We estimated the parameter $\beta$ using a Bayesian approach.
-The inference was performed using the probabilistic programming language  WebPPL [@dippl].
-We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1).
-Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
+We estimated the parameter \(\beta\) using a Bayesian approach. The
+inference was performed using the probabilistic programming language
+WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
+over \(\beta\), and at each month, we computed the likelihood function
+over words that could possibly enter the lexicon at that month, fit to
+the words that have been learned at that month (using formula 1). Markov
+Chain Monte Carlo sampling resulted in a posterior distribution over
+\(\beta\), which we summarized in Figure \ref{fig:pred_ind}.
 
-<!--Besides fitting a growth model to the data, we conducted a separate evaluation.
-This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
-For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.-->
+For the semantic networks, the results replicate Hills et al.'s finding
+in English, which is that the semantic network grows by PAC, not by PAT.
+Moreover, this finding holds in seven of the eight languages we
+examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
+However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.}
+The PAC model also fits better than PAT for phonological networks. We
+note however that PAT, though weaker, fares better for the phonological
+networks (where it predicts part of the growth process in some languages
+such as Croatian, English, Norwegian and Russian) than it does for the
+semantic networks (where it is rather universally unpredictive).
 
-<!--The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{We do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}-->For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT.
-Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.} The PAC model also fits better than PAT for phonological networks.
-We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).
+\subsubsection{What is the relative contribution of each growth
+model?}\label{what-is-the-relative-contribution-of-each-growth-model}
 
-### What is the relative contribution of each growth model?
+Above we evaluated the network growth scenarios individually. As a next
+step, we analyzed their relative contribution to the learning process.
+This was done through adding more fitted parameters to the model, that
+is, by substituting \(\beta d_i\) in formula (1) with:
+\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
+where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
+PhonoPAC. Using the same fitting technique, we obtained the values shown
+in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
+phonological and semantic networks contribute to lexical growth, but the
+phonological network appears to be stronger and more consistent across
+languages. In summary, the findings show that both semantic and
+phonological networks contribute to the learning process, and that they
+both grow primarily by PAC, relying on the external connectivity in the
+learning environment, rather than the internal connectivity in the
+acquired lexicon.
 
-Above we evaluated the network growth scenarios individually.
-As a next step, we analyzed their relative contribution to the learning process.
-This was done through adding more fitted parameters to the model, that is, by substituting $\beta d_i$ in formula (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
-Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_ind}.
-PAC dominates the learning.
-Both phonological and semantic networks contribute to lexical growth, but the phonological network appears to be stronger and more consistent across languages.
-In summary, the findings show that both semantic and phonological networks contribute to the learning process, and that they both grow primarily by PAC, relying on the external connectivity in the learning environment, rather than the internal connectivity in the acquired lexicon.
+\begin{CodeChunk}
+\begin{figure*}[h]
 
-```{r }
+{\centering \includegraphics{figs/regressions_img-1}
 
-#Import data from saved
-regressions <- feather::read_feather("../saved_data/regressions_bis.feather")
+}
 
-pred_regressions <- ggplot(regressions, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor), size=0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  facet_wrap(~language, ncol=4)  +
-  coord_flip() +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7)
-
-ggsave("figs/pred_regressions.png", plot = pred_regressions, width = 8, height = 4)
-```
-
-```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\\% confidence intervals.
+\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\% confidence intervals.
 Positive values indicate a positive relationship (e.g.
 longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA)."}
+words with higher frequency tend to have a lower AoA).}\label{fig:regressions_img}
+\end{figure*}
+\end{CodeChunk}
 
-pred_regressions
+\subsection{Comparison to other predictors of age of
+acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}
 
-#img <- png::readPNG("figs/pred_regressions.png")
-#grid::grid.raster(img)
-```
+We saw that the way semantic and phonological information is structured
+in the learning environment (i.e., PAC) contributes to noun learning
+across languages. However, we know that other factors influence learning
+as well (e.g., Braginsky et al., 2016). Next we investigated how
+semantic and phonological connectivity interact with two other factors.
+The first one is word frequency, a well studied factor shown to predict
+the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
+2008). The second factor is word length, which correlates with
+phonological connectivity.
 
-## Comparison to other predictors of age of acquisition
+Since PAT was uninformative, we dropped it from this analysis, keeping
+only PAC. This simplified the model because we no longer needed to fit
+growth
+month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.}
+A more direct way to assess and compare the contribution of PAC in
+relation to other word-level factors is through conducting linear
+regressions, where connectivity in the learning environment, frequency
+and length predict the age of acquisition.
 
-We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contributes to noun learning across languages.
-However, we know that other factors influence learning as well [e.g., @braginsky2016].
-Next we investigated how semantic and phonological connectivity interact with two other factors.
-The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g.
-@goodman2008].
-The second factor is word length, which correlates with phonological connectivity.
-<!-- [@pisoni1985].-->
+We used the frequency estimates from Braginsky et al. (2016) where
+unigram counts were derived based on CHILDES corpora in each
+language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.}
+For each word, counts included words that shared the same stem (e.g.,
+``cats'' counts as ``cat''), or words that were synonymous (e.g.
+``father'' counts as ``daddy''). For word length, we counted the number
+of phonemes in our generated IPA transcription.
 
-Since PAT was uninformative, we dropped it from this analysis, keeping only PAC.
-This simplified the model because we no longer needed to fit growth month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.} A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
-
-We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.} For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g.
-"father" counts as "daddy").
-For word length, we counted the number of phonemes in our generated IPA transcription.
-
-We conducted two analyses.
-We fit a linear regression for each language, and we fit a linear mixed-effect model to all the data pooled across languages, with language as a random effect.
-Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and Figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
-The findings were as follows.
-Overall, frequency is the largest and most consistent predictor of age of acquisition, replicating results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015].
-Word length predicts learning in some languages such as Croatian and Norwegian, but not in others (including English).
-It remains, however, a significant predictor in the global model.
-As for the factors of interest, i.e., semantic and phonological connectivity, we also found cross-linguistic differences.
-Phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but not in English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
+We conducted two analyses. We fit a linear regression for each language,
+and we fit a linear mixed-effect model to all the data pooled across
+languages, with language as a random effect. Figure
+\ref{fig:regressions_img} shows the coefficient estimate for each
+predictor in each language, and Figure \ref{fig:regressions_all_img}
+shows the coefficient estimates for all languages combined (all
+predictors were centered and scaled). The findings were as follows.
+Overall, frequency is the largest and most consistent predictor of age
+of acquisition, replicating results for nouns across a variety of
+analyses (Braginsky et al., 2016; J. C. Goodman et al., 2008; B. C. Roy,
+Frank, DeCamp, Miller, \& Roy, 2015). Word length predicts learning in
+some languages such as Croatian and Norwegian, but not in others
+(including English). It remains, however, a significant predictor in the
+global model. As for the factors of interest, i.e., semantic and
+phonological connectivity, we also found cross-linguistic differences.
+Phonological connectivity contributes to learning in languages such as
+Croatian, English and Russian, whereas semantic connectivity contributes
+to learning in Turkish, Spanish and to some extent in Croatian, but not
+in
+English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
 This contrasts with the original finding in Hills et al.
@@
 However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: Our study uses a larger set of nouns.} Despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
+Another important difference is the number of words tested: Our study uses a larger set of nouns.}
+Despite these cross-linguistic differences, both phonological and
+semantic connectivity are significant predictors in the combined model.
 
-# Discussion
+\section{Discussion}\label{discussion}
 
-The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
-We compared two network growth scenarios and assessed their relative contributions across eight languages.
-One scenario, PAT, described a rich-get-richer network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.
-Our findings largely replicate the results obtained by @hills2009: Semantic networks grow by preferential acquisition, not by preferential attachment.
-A novel finding is that phonological networks also grow primarily by preferential acquisition.
-Moreover, both semantic and phonological connectivity in the learning environment predict growth.
-These findings generalize well across languages.
-When pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
-Nevertheless, this cross-linguistic variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
-In fact, both phonological and semantic connectivity are significant predictors when data are pooled across languages.
+The present study provided a comprehensive analysis of how lexical
+connectivity influences the age of acquisition of nouns in toddlers. We
+compared two network growth scenarios and assessed their relative
+contributions across eight languages. One scenario, PAT, described a
+rich-get-richer network growth model in which the structure of the
+learner's internal network determines future growth; the other, PAC,
+described a model in which the external, global environmental network
+structure determines learners' growth patterns. Our findings largely
+replicate the results obtained by Hills et al. (2009): Semantic networks
+grow by preferential acquisition, not by preferential attachment. A
+novel finding is that phonological networks also grow primarily by
+preferential acquisition. Moreover, both semantic and phonological
+connectivity in the learning environment predict growth. These findings
+generalize well across languages. When pitted against other known
+predictors of age of acquisition (word frequency and length), the effect
+of word connectivity shows a cross-linguistic variation, predicting
+learning in some languages, but not in others. Nevertheless, this
+cross-linguistic variability is to be taken with a grain of salt as it
+might be exaggerated in our study by the limited and
+partially-overlapping sample of nouns for each language. In fact, both
+phonological and semantic connectivity are significant predictors when
+data are pooled across languages.
 
-```{r }
+\begin{CodeChunk}
+\begin{figure}[H]
 
-#Import data from saved
-regression_all <- feather::read_feather("../saved_data/regression_all_bis.feather")
-regression_all_noCov <- feather::read_feather("../saved_data/regression_all_bis_noCov.feather")
+{\centering \includegraphics{figs/regressions_all_img-1}
 
-pred_regression_all <- ggplot(regression_all, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor), size=0.3)+
-  geom_pointrange(data=regression_all_noCov,
-                  aes(ymin = lower, ymax = upper, col = predictor),
-                  position = position_dodge(width = .3),
-                  linetype=1,
-                  size = 0.7,
-                  fatten = 1.5,
-                  alpha = 0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7)
+}
 
-ggsave("figs/pred_regression_all.png", plot = pred_regression_all, width = 4, height = 2)
-```
+\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
+Ranges indicate 95\% confidence intervals.
+Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
+\end{figure}
+\end{CodeChunk}
 
-```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
-Ranges indicate 95\\% confidence intervals.
-Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}
-
-pred_regression_all
-
-#img <- png::readPNG("figs/pred_regression_all.png")
-#grid::grid.raster(img)
-```
-
-Children start by learning words that have high semantic and phonological similarity to a variety of other words in the learning environment, not in the child's available lexicon.
-This result suggests that children are sensitive to connectivity even without having first acquired the connected words.
-How can children indirectly detect highly connected words, and why would such words be more readily learned?
+Children start by learning words that have high semantic and
+phonological similarity to a variety of other words in the learning
+environment, not in the child's available lexicon. This result suggests
+that children are sensitive to connectivity even without having first
+acquired the connected words. How can children indirectly detect highly
+connected words, and why would such words be more readily learned?
 
 In the semantic case, the networks are based on free association norms.
-These associations can be (partly) derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts.
-In a network structure, highly connected words would be the words that co-occur with many other words in various contexts.
-Why would such words be easier to learn?
-One possibility, suggested by @hills2010, is that the referents of these words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].
+These associations can be (partly) derived from the patterns of
+word-word co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007),
+i.e., two words are associated if they co-occur in many different
+contexts. In a network structure, highly connected words would be the
+words that co-occur with many other words in various contexts. Why would
+such words be easier to learn? One possibility, suggested by Hills et
+al. (2010), is that the referents of these words are more easily
+disambiguated from other potential referents because their presence in
+multiple contexts provides more cross-situational, disambiguating
+statistics about their true referents (Smith \& Yu, 2008).
 
-In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999].
-That is, highly connected words tend to be made of frequent sound sequences.
-Even infants show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
-Moreover, phonotactic probability facilitates learning and recognition [e.g., @storkel2001].
-In other words, children's sensitivity to local phonotactic regularities might lead them to learn higher-probability words more easily.
-This learning effect, in turn, would lead to an observed pattern of growth that would appear to follow the PAC growth model even though learners themselves would only be tracking local statistics.
+In the phonological case, connectivity is inherently correlated with
+phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
+is, highly connected words tend to be made of frequent sound sequences.
+Even infants show a sensitivity for high frequency sound sequences in
+the ambient language (Jusczyk, Luce, \& Charles-Luce, 1994). Moreover,
+phonotactic probability facilitates learning and recognition (e.g.,
+Storkel, 2001). In other words, children's sensitivity to local
+phonotactic regularities might lead them to learn higher-probability
+words more easily. This learning effect, in turn, would lead to an
+observed pattern of growth that would appear to follow the PAC growth
+model even though learners themselves would only be tracking local
+statistics.
 
-Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms in both the semantic and phonological domains.
-One question for future experimental work is whether such patterns of growth can be produced in controlled behavioral experiments.
-<!--Finally, this study shares a number of limitations with previous studies using similar research strategy and dataset.For instance, we used normative age of acquisition.
-However, individual children may follow different learning trajectories.
-The use of longitudinal data would allow us to assess how the aggregate behavior relates to these individual trajectories [e.g., typical vs.
-late talkers, @beckage2011].
-Moreover,In particular, the results provide correlational but not causal evidence.
-Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments.
--->
+Finally, while validating previous results using network growth models,
+our study suggests that these correlational patterns may emerge from the
+operation of simpler mechanisms in both the semantic and phonological
+domains. One question for future experimental work is whether such
+patterns of growth can be produced in controlled behavioral experiments.
 
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
+\vspace{1em}
 
-# Acknowledgements
+\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
+\vspace{1em}
 
-This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
+\section{Acknowledgements}\label{acknowledgements}
 
-# References
+This work was supported by a post-doctoral grant from the Fyssen
+Foundation, NSF \#1528526, and NSF \#1659585.
 
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
+\section{References}\label{references}
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
+
+\hypertarget{refs}{}
+\hypertarget{ref-barabasi99}{}
+Barabasi, A.-L., \& Albert, R. (1999). Emergence of scaling in random
+networks. \emph{Science}, \emph{286}(5439), 509--512.
+
+\hypertarget{ref-braginsky2016}{}
+Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2016).
+From uh-oh to tomorrow: Predicting age of acquisition for early words
+across languages. In \emph{Proceedings of the 38th Annual Conference of
+the Cognitive Science Society}.
+
+\hypertarget{ref-clauset09}{}
+Clauset, A., Shalizi, C. R., \& Newman, M. E. J. (2009). Power-law
+distributions in empirical data. \emph{SIAM Review}, \emph{51}(4),
+661--703.
+
+\hypertarget{ref-fenson94}{}
+Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
+Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early
+communicative development. \emph{Monographs of the Society for Research
+in Child Development}, \emph{59}(5), i--185.
+
+\hypertarget{ref-frank2017}{}
+Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017).
+Wordbank: An open repository for developmental vocabulary data.
+\emph{Journal of Child Language}, \emph{44}(3), 677--694.
+
+\hypertarget{ref-gillespie15}{}
+Gillespie, C. S. (2015). Fitting heavy tailed distributions: The
+poweRlaw package. \emph{Journal of Statistical Software}, \emph{64}(2),
+1--16. Retrieved from \url{http://www.jstatsoft.org/v64/i02/}
+
+\hypertarget{ref-goodman2008}{}
+Goodman, J. C., Dale, P. S., \& Li, P. (2008). Does frequency count?
+Parental input and the acquisition of vocabulary. \emph{Journal of Child
+Language}, \emph{35}(3), 515--531.
+
+\hypertarget{ref-dippl}{}
+Goodman, N., \& Stuhlmuller, A. (2014). The Design and Implementation of
+Probabilistic Programming Languages. \url{http://dippl.org}.
+
+\hypertarget{ref-griffiths07}{}
+Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
+semantic representation. \emph{Psychological Review}, \emph{114}(2),
+2007.
+
+\hypertarget{ref-hills2010}{}
+Hills, T. T., Maouene, J., Riordan, B., \& Smith, L. B. (2010). The
+associative structure of language: Contextual diversity in early word
+learning. \emph{Journal of Memory and Language}, \emph{63}(3), 259--273.
+
+\hypertarget{ref-hills2009}{}
+Hills, T. T., Maouene, M., Maouene, J., Sheya, A., \& Smith, L. (2009).
+Longitudinal analysis of early semantic networks: Preferential
+attachment or preferential acquisition? \emph{Psychological Science},
+\emph{20}(6), 729--739.
+
+\hypertarget{ref-jusczyk1994}{}
+Jusczyk, P. W., Luce, P. A., \& Charles-Luce, J. (1994). Infant's
+sensitivity to phonotactic patterns in the native language.
+\emph{Journal of Memory and Language}, \emph{33}(5), 630--645.
+
+\hypertarget{ref-nelson1998}{}
+Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). The University
+of South Florida word association, rhyme, and word fragment norms.
+Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
+
+\hypertarget{ref-roy2015}{}
+Roy, B. C., Frank, M. C., DeCamp, P., Miller, M., \& Roy, D. (2015).
+Predicting the birth of a spoken word. \emph{Proceedings of the National
+Academy of Sciences}, \emph{112}(41), 12663--12668.
+
+\hypertarget{ref-smith2008}{}
+Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent
+mappings via cross-situational statistics. \emph{Cognition},
+\emph{106}(3), 1558--1568.
+
+\hypertarget{ref-steyvers2005}{}
+Steyvers, M., \& Tenenbaum, J. B. (2005). The large-scale structure of
+semantic networks: Statistical analyses and a model of semantic growth.
+\emph{Cognitive Science}, \emph{29}(1), 41--78.
+
+\hypertarget{ref-storkel2001}{}
+Storkel, H. L. (2001). Learning new words: Phonotactic probability in
+language development. \emph{Journal of Speech, Language, and Hearing
+Research}, \emph{44}(6), 1321--1337.
+
+\hypertarget{ref-storkel2009}{}
+Storkel, H. L. (2009). Developmental differences in the effects of
+phonological, lexical and semantic variables on word learning by
+infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
+
+\hypertarget{ref-vitevitch1999}{}
+Vitevitch, M. S., Luce, P. A., Pisoni, D. B., \& Auer, E. T. (1999).
+Phonotactics, neighborhood activation, and lexical access for spoken
+words. \emph{Brain and Language}, \emph{68}(1), 306--311.
+
+\end{document}

### 2018-12-15 exp_sim/experiment1.js

@@ -1,0 +1,358 @@
+
+// ## Helper functions
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+
+function randomInt(min,max)
+{
+    return Math.floor(Math.random()*(max-min+1)+min);
+}
+
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get a random integer less than n.
+//function randomInteger(n) {
+//	return Math.floor(Math.random()*n);
+//}
+
+//shuffle an array
+function shuffleArray(a) {
+
+    for (var i = a.length - 1; i > 0; i--) {
+        var j = Math.floor(Math.random() * (i + 1));
+        var temp = a[i];
+        a[i] = a[j];
+        a[j] = temp;
+    }
+    return a;
+}
+
+
+// Get a random element from an array (e.g., <code>random_element([4,8,7])</code> could return 4, 8, or 7). This is useful for condition randomization.
+function randomElement(array) {
+  return array[randomInteger(array.length)];
+}
+
+
+var MyInstruct = {
+  
+    "pre1" :"This is a similarity judgement task. You will be shown pictures of pairs of objects and you should rate the similarity of the two objects on a scale from 1 (very similar) to 9 (very different).<br><br> You will now start a practice session. The purpose of this session is to get you familiarized with the objects and the range of similarities you will encounter later.   We encourage you to develop a consistent way of using the ratings. Moreover, try to use the entire 1-9 scale and spread your judgements out evenly as much as possible.",
+    
+    "pre2" :"Now you will start the real session!"
+    
+}
+var col = "#ffffff";
+
+
+var bird = new Ecosystem.Genus('bird', {col2:col, col3:col, col3:col, tar1:1, tar2:0 });
+    
+var flower = new Ecosystem.Genus('flower', {col2:col, col3:col, col4: col,  tar1:1, tar2:0 });
+
+var fish = new Ecosystem.Genus('fish', {col2:col, col3:col, col4:col, tar1:1, tar2:0 });
+    
+var bug = new Ecosystem.Genus('bug', {col2:col, col3:col, col4:col, tar1:1, tar2:0 });
+
[…]

### 2018-12-17 exp_sim/experiment1.js
new experiment

@@ -38,12 +38,25 @@ function randomElement(array) {
   return array[randomInteger(array.length)];
 }
 
+var $task = new $('<img>').attr('src','images/task.png').height(300).width(400);
+
+
 
 var MyInstruct = {
   
-    "pre1" :"This is a similarity judgement task. You will be shown pictures of pairs of objects and you should rate the similarity of the two objects on a scale from 1 (very similar) to 9 (very different).<br><br> You will now start a practice session. The purpose of this session is to get you familiarized with the objects and the range of similarities you will encounter later.   We encourage you to develop a consistent way of using the ratings. Moreover, try to use the entire 1-9 scale and spread your judgements out evenly as much as possible.",
+    "obj_inst" :"In this part of the survey, you will rate the similarity between some objects.  As shown in the illustration below, in each trial you will see a test object in the center, and 2 reference objects on each side of the scale. Your task is to determine the degree to which the test object resembles the reference objects by a selecting a value from 1 to 7.",
     
-    "pre2" :"Now you will start the real session!"
+    "obj_inst_prac" : "You will now start a practice session. The purpose of this session is to get you familiarized with the objects and the range of similarities you will encounter later.   We encourage you to develop a consistent way of using the ratings. Moreover, try to use the entire 1-7 scale and spread your judgements out evenly as much as possible.",
+    
+    "sound_inst" :"In this second and last part of the survey, you will rate the similarity between pairs of random sounds.  In each trial you, will hear two sounds (e.g., 'lif' vs. 'neem') and your task is to determine the degree to which the these sounds are similar or different by a selecting a value from 1 to 7. </br></br> Note that some sounds are not in English, and that we are interested in your <i>subjective</i> similarity rating.",
+    
+    "sound_inst_prac" : "You will now start a practice session. The purpose of this session is to get you familiarized with the sounds and the range of similarities you will encounter later. We encourage you to develop a consistent way of using the ratings. Moreover, try to use the entire 1-7 scale and spread your judgements out evenly as much as possible.",
+    
[…]

### 2018-12-17 exp_sim/experiment1.js
sim exp modif

@@ -106,7 +106,7 @@ myTrials.push(myTrial={
         });
 
 //Pre-trials
-for (i=0; i < prac_ind.length-6; i++){
+for (i=0; i < prac_ind.length; i++){
     myTrial = {
         trial_number: i+1,
         trial_type: "obj_prac",
@@ -123,9 +123,9 @@ myTrials.push(myTrial={
         });
 
 
-for(k=0; k < 1; k++){
+for(k=0; k < 3; k++){
     var rand_ind = shuffleArray(myIndices)
-    for (i=0; i < rand_ind.length-6; i++){
+    for (i=0; i < rand_ind.length; i++){
         myTrial = {
             trial_number: i+1,
             trial_type: "obj_real",
@@ -198,7 +198,7 @@ myTrials.push(myTrial={
 
 var indices_s = [0,1,2,3,4,5,6]
     
-for (k=0; k < 1; k++) {
+for (k=0; k < 3; k++) {
     
 var rand_ind_s = shuffleArray(indices_s)
 

### 2018-12-17 exp_sim/experiment1.js
sim exp minor stuff

@@ -196,7 +196,7 @@ myTrials.push(myTrial={
         });
 
 
-var indices_s = [0,1,2,3,4,5,6]
+var indices_s = [0,1,2,3,4,5,6,7]
     
 for (k=0; k < 3; k++) {
     

### 2018-12-17 exp_sim/experiment1.js
sim exp minor stuff

@@ -52,7 +52,7 @@ var MyInstruct = {
     
     "sound_inst_prac" : "You will now start a practice session. The purpose of this session is to get you familiarized with the sounds and the range of similarities you will encounter later. We encourage you to develop a consistent way of using the ratings. Moreover, try to use the entire 1-7 scale and spread your judgements out evenly as much as possible.",
     
-    "real_inst" :"Now you will start the real session!"
+    "real_inst" :"</br></br></br></br></br>Now you will start the real session!"
     
     
     

### 2018-12-25 Analysis/process.Rmd
new changes

@@
 library(langcog)
-theme_set(theme_bw())
+library(ggthemes)
+library(lme4)
+library(purrr)
+theme_set(theme_few())
 ```
 
-Data.
+Processing for IRB
+
+```{r}
+d1 <- read_delim("data_real1.txt", delim = " ")  %>%
+  filter(code != 'test',
+         !is.na(code)) %>%
+  distinct(ID, gender, age, code)
+
+d2 <- read_delim("data_real2.txt", delim = " ") %>%
+  filter(code != 'test',
+         !is.na(code)) %>%
+  distinct(ID, gender, age, code)
+
+d3 <- read_delim("data_winter.txt", delim = " ") %>%
+  filter(code != 'test',
+         !is.na(code)) %>%
+  distinct(ID, gender, age, code)
+
+d_all <- d1 %>%
+  bind_rows(d2) %>%
+  bind_rows(d3) %>%
+  rowwise() %>%
+  mutate(date = strsplit(code, split = "-")[[1]][2]) %>%
+  select(-code, -ID)
+
+d_final <- cbind(subjects = rownames(d_all), d_all)  %>%
+  mutate(ID= paste('child_', subjects, sep="")) %>%
+  select(ID, gender, age, date)
+
+write.csv(d_final, file = "data_IRB_fourtassi.csv")
+
+```
+
+Adult data.
 
@@
 
-d_word_summer <- read_delim("data_summer_2.txt", delim = " ") %>%
+d_adult <- read_delim("adult_pilot_3.txt", delim = " ")  %>%
+  filter(type == "Test") %>%
+  mutate(iscorrect=ifelse(answer==correct, 1, 0))
+
+d_adult_score <- d_adult %>%
+  group_by(ID, sound_dist, concept_dist) %>%
+  dplyr::summarise(mean = mean(iscorrect))
+
+d_adult_excl <- d_adult_score %>%
+  filter(sound_dist == 'catch') %>%
+  ungroup() %>%
+  select(ID, mean) %>%
+  dplyr::rename(score = mean)
+  #select(ID, score)
+
+d_adult_good <- d_adult %>%
+  left_join(d_adult_excl) %>%
+  filter(score >0.7) %>%
+  filter(sound_dist != 'catch')
+
+feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
+```
+
+Children data
+
+```{r}
+d_child <- read_delim("data_summer_all.txt", delim = " ") %>%
   filter(type == "Test") %>%
@@
          !is.na(code)) %>%
-  filter(grepl('soph', code))
-
-d_all <- d_word_summer %>%
+  filter(grepl('soph', code))%>%
   mutate(iscorrect=ifelse(answer==correct, 1, 0))
 
-```
-
-Process data:
-
-```{r}
-
-data <- d_all %>%
+d_child_score <- d_child %>%
   group_by(ID, sound_dist, concept_dist) %>%
   dplyr::summarise(mean = mean(iscorrect))
-  #multi_boot_standard(col = "iscorrect")
 
 #Catch
-data_excl <- data %>%
+d_child_excl <- d_child_score %>%
   filter(sound_dist == 'catch') %>%
@@
 
-data_catch <- d_all %>%
-  left_join(data_excl) %>%
+d_child_good <- d_child %>%
+  left_join(d_child_excl) %>%
   filter(score > 0.5) %>%
@@
 
-#Exclude items 
-#item_excl <- (data %>%
-#  filter(sound_dist != 'catch') %>%
-#  filter(mean < 0.25) %>%
-#  ungroup() %>%
-#  distinct(ID))$ID
+feather::write_feather(d_child_good, "../saved_data/data_child.feather")
 
-#data_reverse <- d_word %>%
-# filter(!(ID %in% item_excl))
+```
 
-#data_catch_reverse <- d_word %>%
-#  left_join(data_excl) %>%
-#  filter(score >= 0.5) %>%
-#  filter(!(ID %in% item_excl))
+Similarity data
 
-#data_final <- data_good %>%
-#  mutate(age2 = ifelse(grepl('4',age), 4, 5))
+```{r}
+
+d_sim <- read_delim("sim_results.txt", delim = " ")  %>%
+  filter(condition != "obj_prac" & condition != "sound_prac") %>%
+  filter(problem == 'No')
+
+d_sim_summary <- d_sim %>%
+  group_by(condition, distance) %>%
+  summarise(mean = mean(answer),
+                   sd = sd(answer),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se)
+
+d_sim_transform <-  d_sim_summary %>%
+  mutate(scale1 = (mean-1)/6) %>%
+  mutate(myscale =ifelse(condition=='sound_real', scale1/0.926, scale1))
+
+#d_sim_summary$distance <- factor(sum_child$concept_dist, levels = c("similar", "different"))
+#sum_child$sound_dist <- factor(sum_child$sound_dist, levels = c("similar", "different"))
+
+ggplot(d_sim_summary, 
+      aes(x = distance, y = mean)) +
+  #geom_point()+
+  geom_pointrange(aes(ymin = lower, ymax = upper), 
+                 position = position_dodge(width = .1)) + 
+  xlab("Distance") +ylab("rating")+
+  theme_few()+
+theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11)
+      ) + facet_grid(.~condition)
 
@@
 Summary
-```{r }
-#{r fig.width=2, fig.height=5}
 
-sum_catch <- data_catch %>%
+```{r}
+
+sum_adult <- d_adult_good %>%
   group_by(sound_dist, concept_dist) %>%
-  #group_by(sound_dist) %>%
+  dplyr::summarise(mean = mean(iscorrect),
+                   sd = sd(iscorrect),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se)
+
+sum_child <- d_child_good %>%
+  group_by(sound_dist, concept_dist) %>%
   dplyr::summarise(mean = mean(iscorrect),
@@
 
-ggplot(sum_catch, 
-      aes(x = sound_dist, y = mean, col = factor(concept_dist))) +
+```
+
+Plots
+```{r fig.width=3, fig.height=1.7}
+
+sum_child$concept_dist <- factor(sum_child$concept_dist, levels = c("similar", "different"))
+sum_child$sound_dist <- factor(sum_child$sound_dist, levels = c("similar", "different"))
+
+plot_child <- ggplot(sum_child, 
+      aes(x = sound_dist, y = mean, group = factor(concept_dist), col = factor(concept_dist))) +
   #geom_point()+
@@
                  position = position_dodge(width = .1)) + 
-  #geom_line(lty = 2) + 
-  geom_hline(yintercept = 0.50) +
-  xlab("Aud distance") +ylab("% Accurate")+
-  scale_colour_discrete(name="Vis Dist")+
-theme(legend.title = element_text(size=8))
+  geom_line() + 
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("Auditory similary") +ylab("Accuracy")+
+  scale_colour_discrete(name="Visual similarity")+
+  theme_few()+
+theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11)
+      ) #+ facet_grid(.~block)
 
-#Model
-data_model <- data_catch %>%
-  mutate(s_dist=ifelse(sound_dist=="similar", 0, 1),
-         c_dist=ifelse(concept_dist=="similar", 0, 1))
+plot_child
 
-model <- glmer(iscorrect ~ s_dist + c_dist + 
-                 (1 | ID) + 
+sum_adult$concept_dist <- factor(sum_adult$concept_dist, levels = c("similar", "different"))
+sum_adult$sound_dist <- factor(sum_adult$sound_dist, levels = c("similar", "different"))
+
+plot_adult <- ggplot(sum_adult, 
+       aes(x = sound_dist, y = mean, group = factor(concept_dist), col = factor(concept_dist))) +
+
+  geom_pointrange(aes(ymin = lower.ci, ymax = upper.ci), 
+                  position = position_dodge(width = .1)) +
+
+  geom_hline(yintercept = .50, linetype="dashed") + 
+  geom_line() +
+  xlab("Auditory similary") +ylab("Accuracy")+
+  #scale_colour_manual(values = c("red", "blue"), name="Vis Dist")+
+  scale_colour_discrete(name="Visual similarity")+
+
+  #scale_y_continuous(limits = c(0.45, 0.9))+
+  theme_few()+
+theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11)
+      ) #+ facet_grid(. ~ block)+
+
+#theme(plot.title = element_text(size = 12, face = "bold"),
+#    legend.title=element_text(size=10), 
+#    legend.text=element_text(size=9))
+plot_adult
+
+```
+
+Models
+```{r}
+
+#Code and center levels
+data_ch <- d_child_good %>%
+  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
+         c_dist=ifelse(concept_dist=="similar", -1, 1))
+
+data_ad <- d_adult_good %>%
+  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
+         c_dist=ifelse(concept_dist=="similar", -1, 1))
+
+#Maximal (does not converge)
+model_ch <- glmer(iscorrect ~ s_dist * c_dist + 
+                 (s_dist * c_dist  | ID) + 
+                 (c_dist | item_object) + 
+                 (s_dist | item_sound), 
+               data = data_ch, family = binomial(),
+               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+model_ad <- glmer(iscorrect ~ s_dist * c_dist + 
+                 (s_dist * c_dist  | ID) + 
+                 (c_dist | sound) + 
+                 (s_dist | concept), 
+               data = data_ad, family = binomial(),
+               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+#1) Simplify random structure till the model converges
+
+#Drop interaction from random slope per subject (Stil does not converge)
+model1 <- glmer(iscorrect ~ s_dist * c_dist + 
+                 (s_dist + c_dist  | ID) + 
+                 (1 + c_dist| item_object) + 
+                 (1 + s_dist| item_sound), 
+               data = data_model, family = binomial())
+
+#Drop random slope per stimuli  (hooray! This one converges now)
+model2 <- glmer(iscorrect ~ s_dist * c_dist + 
+                 (s_dist + c_dist  | ID) + 
+                 (1 | item_object) + 
+                 (1 | item_sound), 
+               data = data_model, family = binomial(),
+              glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+model00 <- mixed(iscorrect ~ s_dist * c_dist + 
+                 (s_dist + c_dist  | ID) + 
+                 (1 | item_object) + 
+                 (1 | item_sound), 
+                 method = "LRT",
+               data = data_model, family = binomial(),
+              glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+#2) Use likelihood ration to prune fixed effects
+
+#drop interaction term from fixed effect (This works! less degrees of freedom and similar explanatory power)
+
+model3 <- glmer(iscorrect ~ s_dist + c_dist + 
+                 (s_dist + c_dist  | ID) + 
                  (1 | item_object) + 
@@
 
-summary(model)
+anova(model2, model5)
 
 ```
+
+```{r fig.width=2.5, fig.height=1.2}
+hi <- get_speaker_statistics()
+
+hello <- hi %>%
+  #filter(speaker_role=="Target_Child") %>%
+  mutate(age = round(target_child_age/12)) %>%
+  filter(age <11) %>%
+  mutate(role = ifelse(speaker_role=='Target_Child', 'child', 'adult')) %>%
+  group_by(age, role, target_child_sex) %>%
+  summarise(utt = sum(num_utterances)) %>%
+  filter(target_child_sex == 'male' | target_child_sex == 'female') %>%
+  rename(gender = target_child_sex) %>%
+  mutate(gender2 = ifelse(gender=='male', 'male children', 'female children'))
+
+ggplot(hello, 
+      aes(x = age, y = utt, col = factor(role))) +
+  geom_point()+
+  geom_line(aes(lty=factor(role))) + 
+  scale_x_continuous(breaks=c(1,2,3,4, 5, 6, 7,8,9, 10)) +
+  #scale_y_continuous(name="number of utterances", labels = scales::comma) +
+  scale_y_continuous(labels = scales::comma) +
+  xlab("Age (years)") +ylab("Number of utterances")+
+  guides(col=guide_legend(title="Speaker"), lty=guide_legend(title="Speaker"))+
+  facet_grid(.~gender2)
+
+  #geom_hline(yintercept = 0.50) +
+  #xlab("Aud distance") +ylab("% Accurate")+
+  #scale_colour_discrete(name="Vis Dist")+
+#theme(legend.title = element_text(size=8))
+
+hello <- hi %>%
+  #filter(speaker_role=="Target_Child") %>%
+  mutate(age = round(target_child_age/12)) %>%
+  filter(age <11) %>%
+  mutate(role = ifelse(speaker_role=='Target_Child', 'child', 'adult')) %>%
+  group_by(age, role, ) %>%
+  summarise(utt = sum(num_utterances)) #%>%
+  #filter(target_child_sex == 'male' | target_child_sex == 'female')
+
+```
+
+Simualte the probability space
+
+```{r}
+#Process the data to prepare for the fit
+data_fit_adult <- sum_adult %>%
+  rename(lower  = lower.ci,
+         upper = upper.ci) %>%
+  mutate(group = 'adults',
+         s_dist = ifelse(sound_dist =='different',  0.66, 0.23),
+         c_dist = ifelse(concept_dist =='different', 0.40, 0.19))
+
+data_fit_child <- sum_child %>% 
+   mutate(group = 'children',
+         s_dist = ifelse(sound_dist =='different',  1, 0.66),
+         c_dist = ifelse(concept_dist =='different', 1, 0.40))
+
+data_fit <- data_fit_adult %>%
+  bind_rows(data_fit_child)
+```
+
+Now I need to predict accuracy as function of sound and meaning similarity 
+```{r}
+
+#This the analytical solution of the posterior + luce rule
+combine_cues <- function(s, o, Vr) {
+  s1 = 0
+  o1 = 0
+  no_acc <- exp(-(s1-s)^2/(2*Vr)) + exp(-(o1-o)^2/(2*Vr))
+  acc <- 1 + exp(-((s1-s)^2+(o1-o)^2)/(2*Vr)) 
+  acc_norm <- acc/(acc+no_acc)
+
+  return(acc_norm)
+}
+
+combine_cues_2 <- function(s, o, Vr_s, Vr_o) {
+  s1 = 0
+  o1 = 0
+  no_acc <- exp(-(s1-s)^2/(2*Vr_s)) + exp(-(o1-o)^2/(2*Vr_o))
+  acc <- 1 + exp(-((s1-s)^2/(2*Vr_s)+(o1-o)^2/(2*Vr_o))) 
+  acc_norm <- acc/(acc+no_acc)
+
+  return(acc_norm)
+}
+
+fit_adults <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='adults'), start=list(Vr=0.01), lower=c(0), algorithm="port")
+
+fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.04, Vr_o=0.04), lower=c(0,0), algorithm="port")
+
+Vr_ad <- coef(fit_adults)
+Vr_s_ad <- coef(fit_adults_2)[1]
+Vr_o_ad <- coef(fit_adults_2)[2]
+
+fit_children <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='children'), start=list(Vr=0.3), lower=c(0), algorithm="port")
+
+fit_children_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='children'), start=list(Vr_s=0.3, Vr_o=0.3), lower=c(0,0), algorithm="port")
+
+Vr_ch <- coef(fit_children)
+Vr_s_ch <- coef(fit_children_2)[1]
+Vr_o_ch <- coef(fit_children_2)[2]
+
+model_data <- data_fit %>%
+  mutate(prediction = ifelse(group=='adults', 
+                             combine_cues(s_dist, c_dist, Vr_ad),
+                             combine_cues(s_dist, c_dist, Vr_ch)
+                             )) %>%
+  mutate(prediction_2 = ifelse(group=='adults', 
+                             combine_cues_2(s_dist, c_dist, Vr_s_ad, Vr_o_ad),
+                             combine_cues_2(s_dist, c_dist, Vr_s_ch, Vr_o_ch)
+                             )) %>%
+  rename(human = mean)
+
+model_data_plot <-  model_data %>%
+  gather(key, value, human, prediction, prediction_2) %>%
+  mutate(ci.upper = ifelse(key=='human', upper, value),
+         ci.lower = ifelse(key=='human', lower, value))
+
+feather::write_feather(model_data_plot, "../saved_data/data_human_model.feather")
+
+```
+
+Simulations
+```{r}
+
+simulation1 <- function(s,o,Vr) {
+  s1 = 0
+  o1 = 0
+  no_acc <- exp(-(s1-s)^2/(2*Vr)) + exp(-(o1-o)^2/(2*Vr))
+  acc <- 1 + exp(-((s1-s)^2+(o1-o)^2)/(2*Vr)) 
+  acc_norm <- acc/(acc+no_acc)
+
+  return(acc_norm)
+}
+
+s <- seq(0,1,0.01)
+
+simulation_data <- data.frame(x=s, y=simulation1(s, o=0.25, Vr=(0.15)^2), sigma = '0.15', object_distance = '0.25') %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=0.5, Vr=(0.15)^2), sigma = '0.15', object_distance = '0.5')) %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=1, Vr=(0.15)^2), sigma = '0.15', object_distance = '1')) %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=0.25, Vr=(0.3)^2), sigma = '0.3', object_distance = '0.25')) %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=0.5, Vr=(0.3)^2), sigma = '0.3', object_distance = '0.5')) %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=1, Vr=(0.3)^2), sigma = '0.3', object_distance = '1')) %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=0.25, Vr=(0.6)^2), sigma = '0.6', object_distance = '0.25')) %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=0.5, Vr=(0.6)^2), sigma = '0.6', object_distance = '0.5')) %>%
+  bind_rows(data.frame(x=s, y=simulation1(s, o=1, Vr=(0.6)^2), sigma = '0.6', object_distance = '1'))
+
+feather::write_feather(simulation_data, "../saved_data/simulations.feather")
+
+ggplot(simulation_data, aes(x=x, y=y, col=sigma)) + 
+  geom_line() + 
+  theme_few()+
+  theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11),
+      aspect.ratio = 0.7
+      )+
+  ylim(c(0.4,1))+
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("sound distance") + ylab("Prob. accurate") +
+  facet_grid(.~object_distance)
+
+```
+
+```{r}
+
+model_data_plot$group <- factor(model_data_plot$group, levels = c("children", "adults"))
+
+ggplot(model_data_plot, 
+#ggplot(subset(model_data_plot, group=='children'),
+      aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
+  #geom_point()+
+  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
+                 position = position_dodge(width = .1),
+                 size=0.2) + 
+  geom_line() + 
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("Auditory similary") +ylab("Accuracy")+
+  scale_colour_discrete(name="Visual similarity")+
+  theme_few()+
+theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11)
+      ) + facet_grid(group~key, scales="free_y") +
+  theme(aspect.ratio = 0.7)
+
+```
+
+plots 
+```{r}
+
+Gdist <- function(s0, Vr, x){
+
+  return((1/sqrt(2*pi*Vr))*exp(-(s0-x)^2/(2*Vr)))
+}
+
+s = seq(-1,1.5,0.01)
+y = Gdist(0,1,x)
+
+illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), x.pos = "0", type='within') %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), x.pos = "0.5", type='within')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='within')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='within')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), x.pos = "0.5", type='between')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between'))
+
+ggplot(illustration, aes(x=x, y=y, col=x.pos)) + 
+  geom_line() + 
+  theme_few()+
+  theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11),
+      aspect.ratio = 0.7
+      )+
+  #xlim(c(-1,1))+
+  #ylim(c(0,1))+
+  #geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("position") + ylab("Prob") #+
+  #facet_grid(.~object_distance)
+
+```

### 2018-12-25 cogsci/cogsci.Rmd
new changes

@@
    - \usepackage[subtle]{savetrees}
+   - \usepackage{tipa}
 
@@
 library(BBmisc)
+library(stargazer)
+library(lme4)
 ```
@@
 
-How do children acquire words?
+Over the first year of life, children become sensitive to the phonetic variations that are used to distinguish meanings in their native language (Werker and Tees, 1984).
+One could imagine that these perceptual skills would be automatically applied to the task of word learning.
+However, developmental data show that 14 m.o children find it challenging to associate minimally different (but perceptually discriminated) sounds such as "bin" and "din" to different objects (Stager & Werker, 1997).
+
+Several factors can explain this pattern of results.
+For example it is possible that the task of meaning learning increases cognitive demands on children (compared to a simple perceptual descrimination).
+In particular, it requires paying attention to both the sounds and the corresponding objects, which may hinder precise encoding in memory of some phonetic details (Stager a& Werker, 1997).
+Additional difficulty might arise from ambiguous phonological boundaries at this stage of development (e.g., Rost & McMurray, 2009), or from uncertainty about the referential status of the novel word (Fennell & Waxman, 2009).
+
+Regardless of the exact explanation, it is generally accepted that by around 17 m.o, chidlren succeed under the same circumstances (Werker et al.
+2002).
+What could be the mechanism of development?
+Swingley contrasted a binary-discontinuous scenario to a probabilstic-continuous one.
+On the discontinuous account, younger children learn a single, underspecified representation of similar words (e.g., "bin"/"din").
+Development occurs when children specify this intial coarse reprepsentation and learn two distinct catgories.
+On the continuous account, distinct represetations are successfully learned from the start, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks.
+
+Experimental evidence suggest a probabilsitic-continuous, rather than a stage-like develomental scenario.
+On the one hand, 14-month-olds who typically fail in the original task succeed when learning is probed using a testing method with lower memory demands (Yoshida et al.
+1009), and when uncertainty in the emerging representations is mitigated using disambiguating contextual cues (Thiessen, 2007; Dautriche et al., 2016).
+On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases (Pajak et al., 2016; White et al., 2013).
+
+Following this experimental studies, the purpose of the current work is to propose a precise probabilsitc model of the Stager and Werker's task, and to explore the extent to which such a model could provide a unified accounts for several documented (as well as new) patterns of learning and development.
+We first present the model and explain how it can be used to make precise predictions of the target behavioral responses.
+Second, using new data collected from both preschool children and adults, we show how the probabilistic strucure of the model can explain behavioral patterns both within the same age and across development.
+
+```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios.
+Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
+Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
+"}
+
+img <- png::readPNG("figs/task.png")
+grid::grid.raster(img)
+
+```
+
+# Model
+
+## Task
+
+We model a variant of the task used in Yoshida et al.
+2009.
+In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects.
+After this exposure phase, participants perform a series of two-alternative forced choices.
+In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
+
+<!--In previous studies, only the similarity of the sounds was varied across conditions (e.g., "bin"/"din" vs.
+"lif"/"neem").
+In our task, we also vary the visual similarity of the objects, which allows us to explore the effect of additional probabilistic cues on novel word learning and recognition.
+An overview of the task is presented in Figure XX.
+-->
+
+## Probabilistic strcuture
+
+Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation.
+These variables are related in a way that refelects the simple generative scenario represented graphically in Figure XX.
+When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind.
+The concept prompted the cooresponding label $L$.
+Finally, the label was physically instantiated by the sound $s$.
+
+```{r model, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
+Circles indicate random variables (shading indicates observed variables).
+The squares indicates fixed model parameters."}
+
+img <- png::readPNG("figs/model.png")
+grid::grid.raster(img)
+
+```
+
+Because of the noisy nature of the representations, the observer can only determine the hidden variables (i.e., the concept $C$ and the label $L$) in a probabilistic fashion.
+For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectivel, are normally distributed:
+
+$$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
+$$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
+We assume there to be one-to-one mappings between concepts and labels, and that observers have successfully learned these mappings during the exposure phase:
+$$
+P(L_i|C_j) = 
+\begin{cases}
+  1 & \text{if  }  i=j \\  
+  0  & \text{if  }  i\neq j 
+\end{cases}
+$$
+## Predictions
+
+During the testing phase (see Figure 1), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and two possible objects $o_1$ and $o_2$.
+In order to make a choice, we determine which object is more probable under the lable $s_T$, in other words, we compare the the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$.
+The values of these probabilities can be computed by summing over all possible labels:
+$$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
+The joint probability $P(o, C, L, s)$ is obtained by factoring the bayesian network in Figure 2:
+$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
+which could be tansformed using Bayes rule into:
+
+$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
+Finally, assuming that the concept prior is a uniform ditribution, we obtain the following expression, where all conditional dependencies have been defined in the previous secton.
+
+\begin{equation}
+P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
+\end{equation}
+
+From the general expression (1) we were able to derive the exact analytical expression of the probability of correct responses in the testing phase of our simplified experimenal setting (Figure 1).
+
+\begin{equation}
+P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
+\end{equation}
+
+We simulate the values of this probability as a function of the perceptual distance between the sounds $\Delta s$, using the two remining parameters of the model: the visual distance between the semantic referents $\Delta o$ and the values of the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
+The simulations are shown in Figure 3.
+```{r }
+
+#Import data from saved
+simulations <- feather::read_feather("../saved_data/simulations.feather")
+
+plot_simulation <- ggplot(simulations, aes(x=x, y=y, col=sigma)) + 
+  geom_line() + 
+  theme_few()+
+  theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11),
+      aspect.ratio = 0.7
+      )+
+  #plot.margin=grid::unit(c(0,0,0,0), "mm")
+  ylim(c(0.4,1))+
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("sound distance") + ylab("Prob. accurate") +
+  facet_grid(.~object_distance)
+
+#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
+
+```
+
+```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits."}
+plot_simulation
+#img <- png::readPNG("figs/data_all.png")
+#grid::grid.raster(img)
+
+```
+
+The simulations explain previousely documented facts, and make new predictions:
+
+1) For fixed values of $\Delta o$ and  $\sigma$, the probability of accurate responses increases as a function of $\Delta s$.
+This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren (Stager and Werker, 1997) and adults (Pajak et al.
+2016).
+
+2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the noise characterized with $\sigma$ decreases.
+This fact may explain development, i.e., youger children have noisier representations (Swingley, 2007; Yoshida et al.
+2009), which lead to lower word recognition accuracy, especially for similar sounding words.
+
+3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases when the visual distance between the semantic referents $\Delta o$ increases.
+This is a new predcition that our model makes.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (see introduction), But no previous study tested the effect of the visual distance between the semantic referents.
+
+To sum, we introduced a model that accounts for some qualitative patterns observed in previous studies, and makes new predictions.
+In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool chidlren and adults.
+
+```{r}
+
+Gdist <- function(s0, Vr, s){
+  return((1/sqrt(2*pi*Vr))*exp(-(s0-s)^2/(2*Vr)))
+}
+
+s = seq(-1,2.5,0.01)
+y = Gdist(0,1,s)
+
+illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Disambig.') %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Disambig.')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambig.')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambig.')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Develop.')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Develop.')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Develop.')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Develop.'))
+
+illustration$case <- factor(illustration$case, levels = c("low accuracy", "high accuracy"))
+illustration$type <- factor(illustration$type, levels = c("Disambig.", "Develop."))
+
+probs <- subset(subset(illustration, x==0)) %>%
+  group_by(type, case) %>%
+  mutate(prob = round(y/sum(y),2)) %>%
+  filter(rep=='1')
+
+illus_plot <- ggplot(illustration, aes(x=x, y=y, linetype=rep)) + 
+  geom_line() + 
+  theme_few()+
+  theme(legend.title = element_text(size=9),
+      legend.text=element_text(size=9),
+      axis.text = element_text(size = 9),
+      strip.text = element_text(size = 9),
+      axis.title = element_text(size = 9),
+      aspect.ratio = 0.5
+      )+
+
+  geom_col(aes(x = x, y = y, fill = rep),
+               position=position_dodge(), 
+               width=0.2,
+               data = subset(illustration, x==0))+
+  geom_text(aes(label=paste("Acc=", prob, sep="")),
+            x=1.7, y=1, size=2.5, 
+            data=probs)+
+  xlab("Perceptual space") + ylab("Prob") +
+  facet_grid(type~case) +
+  theme(legend.position="none")
+
+```
+
+```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus}Graphical representation of our model.
+Circles indicate random variables (shading indicates observed variables).
+The squares indicates fixed model parameters."}
+
+illus_plot
+```
+<!--
+To illustrate, imagine that $S_T = S_1$, expression XX leads to:
+$$P(O_1 | S_1) \propto P(S_1|L_1)P(O_1| C_1) + P(S_1|L_2)P(O_1| C_2)$$ 
+$$P(O_2 | S_1) \propto P(S_1|L_1)P(O_2| C_1) + P(S_1|L_2)P(O_2| C_2)$$
+
+This formula explain why learners may still struggle with learning the meaning of similar words even if they learn the correct mappings. Indeed, one can learn that the sound $S_1$ is a better match to
+
+Yet infants could have learned that bih is a better match to the ‘bih’ object than dih without triggering greater looking to the switch; the similar word could be judged to be a plausible instance of the newly learned label
+-->
+
+<!--How do children acquire words?
 An important step consists in mapping a phonological form (e.g.
@@
 A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008).
-However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998).
+However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998), and, though this similarity structure influnces word recognition (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
+
 Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.
@@
 2016).
-Here we explore
+Here we explore  -->
 
-Talk a bit about what we do
+# Experiment
 
-# Experiment 1
-Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
+In this experiment, we tested participants in the word learning task introduced above (Figure 1).
+We explored all three parameters of the model.
+Both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simulataneousely in a within-subject design.
+Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characteized with the degree of uncertainty, $\sigma$, in the probabilsitic representations.
+<!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
 After training, children performed a series of two-alternative forced choices.
@@
 Finally, the pair of words that are similar on both levels should be the most difficult to learn.
+-->
 
@@
 So far, we collected data from N=47 children (mean age= months, F=).
-An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as specified in the pre-registration).
+An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as was specified in the pre-registration\footnote{https://osf.io/jrh38/}).
+We also collected a planed sample of N=30 adults on Amazon Mechanical Turk.
+N=2 adult participants were excluded because of low scores on the catch trials (see pre-registration).
 
-### Stimuli
-The sound stimuli were generated using the MBROLA Speech Synthesizer (Cite) using an American English voice.
-We generated two similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof").
-We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure).
-As for the objects used as semantic referents, we used the Dynamic Categories Stimuli (Cite) which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish" (plus the additional category "flower" for the catch trial).
+### Stimuli and similarity rating
+The sound stimuli were generated using the MBROLA Speech Synthesizer (Dutoit et al., 1996).
+We generated three kinds of sound pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
+
+As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish".
 These categories are supposed to be naturally occuring kinds that might be seen on an alien planet.
-In each category, we generated instances that varied in their similarity by manipuating a continuous property controling features of the category's shape.
+In each category, we generated "different", "intermediate" and "similar" levels of similarity by manipuating a continuous property controling features of the category's shape (e.g, body strech and head fatness).
+
+In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and objcet pair on a 7-point scale.
+We used the average ratings across participants as qunatitaive measures of sound pairs' distance ($\Delta s$) and object pairs' distance ($\Delta o$).
+
+<!--We quantified experimetnally the similarity of sound and object pairs that we generated. 
+We generated three levels of similarity pairs and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively.
+Examples of the resuting pairs are shown in Figure XX.
 This property was the head fatness for the category "bug", the body strech for "bird", the tail size relative to the body fatness for "fish", the width of the trunk for "tree", and finally center size for "flower".
 All these continous properties varied on a scale from 0 to 1.
-We generated "similar" and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively.
-Examples of the resuting pairs are shown in Figure XX.
+similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof").
+We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure).
+-->
 
 ###Design 
-The experiment consisted of 4 conditions which consisted, each, of a pair of sounds-objects associations.
-These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design.
-Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar to the previous ones.
-It involved different sounds and different objects, and it was used only to select participant who were able to follow the instructions and show minimal learning (not at chance level).
+Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs.
+"intermediate" for preschoolers, and "intermediate" vs.
+"similar" for adults.
+The experiment consisted of four conditions which involved, each, one pair of sounds-objects associations.
+These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design in each age group.
+Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its stucture to the other ones, but was used only to select participant who were able to follow the instructions and show minimal learning.
+
+```{r }
+
+#Import data from saved
+data_human_model <- feather::read_feather("../saved_data/data_human_model.feather")
+
+data_human_model$group <- factor(data_human_model$group, levels = c("children", "adults"))
+
+plot_data <- ggplot(data_human_model, 
+#ggplot(subset(model_data_plot, group=='children'),
+      aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
+  #geom_point()+
+  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
+                 position = position_dodge(width = .1),
+                 size=0.2) + 
+  geom_line() + 
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("Auditory similary") +ylab("Accuracy")+
+  scale_colour_discrete(name="Visual similarity")+
+  theme_few()+
+theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11)
+      ) + facet_grid(group~key, scales="free_y") +
+  theme(aspect.ratio = 0.7)
+
+#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
+
+```
+
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits."}
+plot_data
+#img <- png::readPNG("figs/data_all.png")
+#grid::grid.raster(img)
+
+```
 
 ### Procedure
-Children were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time.
+
+Preschoolers were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time.
 The experimenter explained that the game consisted in learning some words spoken in an alien planet.
@@
 right) of the two pictures on each testing trial.
-The experiment can be views online using this link XX.
 
-### Results
+The procedure for preschoolers and adults were identical except that preschoolers were accompagnied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.
 
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios.
-Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
-Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
-For PAC, the utility of a candidate node is its degree in the entire network.
-According to PAC, the node E2 is more likely to enter the lexicon first."}
+### Model fitting
 
-img <- png::readPNG("figs/growth2.png")
-grid::grid.raster(img)
+We fit the analystical expression (equation 2) to the participants' responses in each age group.
+The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (described in the stimuli sub-section).
+We used two models: \textbf{model 1} fit only one parameter ($\sigma = \sigma_C =\sigma_L$), and \textbf{model 2} fit two parameters ($\sigma_C  \neq \sigma_L$).
+The values of the parameters were derived using weighted least-squares estimates.
 
+## Results
+
+First we analyzed the experimental results shown in Figure (XX, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture (Barr et al.
+2013).
+Results are shown in Table XX.
+We found a main effect of sound distance on the accuray of learning in both children and adults, thus replicating previous findings.
+We also found a main effect of object distance, thus confirming the new hypothesis derived from our model.
+
+```{r, results='asis'}
+
+data_child <- feather::read_feather("../saved_data/data_child.feather") %>%
+  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
+         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
+  rename(Accuracy = iscorrect)
+data_adult <- feather::read_feather("../saved_data/data_adult.feather") %>%
+  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
+         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
+  rename(Accuracy = iscorrect)
+
+model_ch <- glmer(Accuracy ~ s_dist * c_dist + 
+                 (s_dist * c_dist  | ID) + 
+                 (c_dist | item_object) + 
+                 (s_dist | item_sound), 
+               data = data_child, family = binomial(),
+               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+model_ad <- glmer(Accuracy ~ s_dist * c_dist + 
+                 (s_dist * c_dist  | ID) + 
+                 (c_dist | sound) + 
+                 (s_dist | concept), 
+               data = data_adult, family = binomial(),
+               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+stargazer(model_ch, model_ad, 
+          column.labels = c("Children","Adults"),
+          model.numbers=FALSE,
+          intercept.bottom = FALSE,
+          covariate.labels=c("(Intercept)","Sound ","Object","Sound x Object"),
+          no.space=TRUE,
+          single.row=TRUE,
+          star.cutoffs =c(0.05, 0.01, 0.001),
+          omit.stat = "all",
+          table.layout ="-c-!t-n",
+          header=FALSE,
+          #notes=c("[0.*]","[0.**]"),
+          title="Estimates of predictor coefficients (and their standard errors) by age group in the regression model")
 ```
-
-Studies that investigate lexical network growth have focused on semantic networks using English data [@steyvers2005; @hills2009; @hills2010].
-The novelty of the current study is threefold:  First, it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT.
-Second, it provides a systematic comparison of both network growth scenarios in the phonological and the semantic domains and assesses their relative contribution to the learning process.
-Third, it tests the generality of the findings across eight languages.
-
-```{r }
-
-#Import data from saved
-data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")
-
-#tidy data
-data_long <- data_all_scaled %>%
-  gather(predictor, value, length:freq_mika)
-
-data_long <- data_long %>%
-  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
-  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))
-
-data_long$predictor <- mapValues(data_long$predictor, 
-                                 from = c("PAC_assoc", "PAC_phono_t2"), 
-                                 to = c("Sem.", "Phono."))
-
-#Compute the correlations 
-correlations <-  data_long %>%
-  group_by(language, predictor) %>%
-  dplyr::summarise(cor = round(cor(AoA, value), 2))
-
-plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
-  facet_grid(predictor ~ language)+#, scales = "free") +
-  geom_jitter(#aes(colour = lexical_class),
-    colour = solarized_palette(1),
-    size = 0.5, alpha = 0.5) +
-  geom_abline(slope = -1)+
-  coord_cartesian(xlim=c(-1,5))+
-  #scale_x_continuous(limits=c(-2,5))+
-  scale_y_continuous(breaks =c(15,25,35))+
-  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
-  scale_colour_solarized(name = "") +
-  theme_few()+
-  #theme_bw()+
-  theme(aspect.ratio = 0.7, 
-        plot.margin=grid::unit(c(0,0,0,0), "mm")
-        )+
-  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
-  xlab("degree z-score") +ylab("AoA")
-
-ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
-
-```
-
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits."}
-plot_data_all
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
-
-```
-
-```{r }
-
-#Import data from saved
-degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
-  dplyr::rename(Dimension = dimension)
-
-plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
-  facet_grid(. ~ language)+
-  geom_point(size = 0.5, alpha = 0.5) +
-  scale_y_log10() + scale_x_log10() +
-  theme_few()+
-  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
-  xlab("degree") +ylab("probability")
-
-ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)
-
-```
-
-```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
-A perfect power-law distribution should appear as a straight line in this graph."}
-plot_dist
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
-
-```
-
-# Networks
-## Data
-We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist.
-Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94].
-We used the *Words and Sentences* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies [@storkel2009; @hills2009], we restricted our analysis to nouns.
-We defined the age of acquisition of a given word by the month at which this word was produced by at least 50% of children [@goodman2008], and we excluded nouns that have not been learned (according to this criterion) by the last month for which we have CDI data.
-
-We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish.
-We used the subset of nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages.
-Table \ref{tab:stats} gives an overview of the data used.
-Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available.
-Note, however, that all languages have at least 60% of nouns translated.
-
-```{r stats, results="asis", echo=FALSE}
-
-statistics <- feather::read_feather("../saved_data/statistics.feather") 
-rownames(statistics) <- NULL
-
-tab <- xtable::xtable(statistics,
-                      caption = "\\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
-We included in our study the subset of these nouns that had available English translations (middle).
-The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).")
-
-print(tab, type="latex", comment = F, table.placement = "H")
-
-#print(statistics, type="latex", comment = F, table.placement = "H")
-```
-
-## Semantic networks
-
-We constructed semantic networks following the procedure outlined in @hills2009.
-We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998].
-This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target).
-For example, when given the word "ball", they might answer with the word "game".
-A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms.
-The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.
-To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.
-
-## Phonological networks
-
-We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes.
-The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.
-
-In previous studies, two nodes were linked if they had an edit distance of 1 [e.g., @storkel2009].
-However, in these previous studies the network was built using an adult vocabulary.
-In the current study, however, network growth models are based on the children's early vocabulary which contains very few word pairs with an edit distance of 1.
-When using this threshold, the resulting networks were too sparse and uninformative.
-Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.
-The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.
-
-<!--## Network growth
-
-We tested two network growth scenarios discussed in @hills2009.
-The first one was *Preferential Attachment* (PAT).
-According to this mechanism, the network structure of known words predicts what words will be learned next.
-A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network.
-The second mechanism was *Preferential Acquisition* (PAC).
-In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.
-Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.
-For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to.
-Thus, according to PAT, the node N1 is more likely to enter the lexicon first.
-For PAC, each candidate node was characterized with its degree in the entire network.
-According th PAC, the node N3 is more likely to enter the lexicon first.
-
--->
-
-# Analysis
-
-## Static properties of the global network
-
-We start by analyzing word connectivity in the global (static) network.
-We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds to the network by 30 months).
-This global network is the end-state towards which both PAT and PAC should converge by the last month of learning.
-Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment.
-Below we analyze properties of this global networks that are relevant to PAC and/or PAT.
-
-###Connectivity predicts the age of acquisition
-
-Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}).
-Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
-Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network).
-For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages.
-The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.
-
-###Power-law degree distribution?
-We also analyzed the global network's degree distribution.
-The shape of this distribution is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99].
-If the network displays this property, this fact would suggest a PAT-like generative process.
-Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT.
-The log-log plots are shown in Figure \ref{fig:degree_distribution}.
-We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15].
-In brief, the analysis consisted in two steps.
-First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$.
-Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model.
-Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we obtained  $p < 0.05$, suggesting that the power law can be ruled out in this particular case.
-
-In sum, the static properties of the global network are *a priori* compatible with both PAT and PAC.
-In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
-<!--
-```{r }
-
-#Import data from saved
-post_combined <- feather::read_feather("../saved_data/combined_net.feather")
-
-pred_comb <- ggplot(post_combined, aes(x = model, y = mean)) +
-  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = model), size=0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_bw()+
-  theme(aspect.ratio = 0.7)
-
-ggsave("figs/pred_comb.png", plot = pred_comb, width = 8, height = 4)
-```
-
-```{r pred_comb_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language.
-Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\\% credible intervals (computed using the highest density intervals).
-"}
-pred_comb
-#img <- png::readPNG("figs/pred_comb.png")
-#grid::grid.raster(img)
-```
--->
-
-```{r }
-
-#Import data from saved
-individual <- feather::read_feather("../saved_data/individual_both.feather") %>%
-  filter(Evaluation =='Fit') %>%
-  select(-Evaluation) %>%
-  mutate(Test = 'Individual')
-
-combined <- feather::read_feather("../saved_data/combined_net.feather") %>%
-  dplyr::rename(lower = hdi_lower,
-                upper = hdi_upper) %>%
-  mutate(Test = 'Combined')
-
-growth_all <- bind_rows(individual, combined)
-
-pred_ind <- ggplot(growth_all, aes(x = model , y = mean)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Test),
-                  position = position_dodge(width = .5),
-                  size = 0.5,
-                  fatten = 0.5)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  facet_wrap(~language, ncol=4)  +
-  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7, axis.text.x = element_text(size=8))
-
-ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)
-
-```
-
-```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
-Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals).
-Positive values mean that learning proceeds according to the predictions of the growth scenario.
-Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}
-
-pred_ind
-
-#img <- png::readPNG("figs/pred_ind.png")
-#grid::grid.raster(img)
-```
-
-## Network growth models
-
-### How does each growth scenario predict noun development?
-
-To test the network growth scenarios, we fit different growth models to the data.
-We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function:
-\begin{equation}
- p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
-\end{equation}
-
-\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient).
-A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for an illustration of how growth values $d_i$ are defined in each growth scenario).
-The normalization includes all words that could be learned at that month.
-
-We estimated the parameter $\beta$ using a Bayesian approach.
-The inference was performed using the probabilistic programming language  WebPPL [@dippl].
-We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1).
-Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.
-
-<!--Besides fitting a growth model to the data, we conducted a separate evaluation.
-This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.
-For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.-->
-
-<!--The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{We do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}-->For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT.
-Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.} The PAC model also fits better than PAT for phonological networks.
-We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).
-
-### What is the relative contribution of each growth model?
-
-Above we evaluated the network growth scenarios individually.
-As a next step, we analyzed their relative contribution to the learning process.
-This was done through adding more fitted parameters to the model, that is, by substituting $\beta d_i$ in formula (1) with: $$\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}$$ where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and PhonoPAC.
-Using the same fitting technique, we obtained the values shown in Figure \ref{fig:pred_ind}.
-PAC dominates the learning.
-Both phonological and semantic networks contribute to lexical growth, but the phonological network appears to be stronger and more consistent across languages.
-In summary, the findings show that both semantic and phonological networks contribute to the learning process, and that they both grow primarily by PAC, relying on the external connectivity in the learning environment, rather than the internal connectivity in the acquired lexicon.
-
-```{r }
-
-#Import data from saved
-regressions <- feather::read_feather("../saved_data/regressions_bis.feather")
-
-pred_regressions <- ggplot(regressions, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor), size=0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  facet_wrap(~language, ncol=4)  +
-  coord_flip() +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7)
-
-ggsave("figs/pred_regressions.png", plot = pred_regressions, width = 8, height = 4)
-```
-
-```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\\% confidence intervals.
-Positive values indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA)."}
-
-pred_regressions
-
-#img <- png::readPNG("figs/pred_regressions.png")
-#grid::grid.raster(img)
-```
-
-## Comparison to other predictors of age of acquisition
-
-We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contributes to noun learning across languages.
-However, we know that other factors influence learning as well [e.g., @braginsky2016].
-Next we investigated how semantic and phonological connectivity interact with two other factors.
-The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g.
-@goodman2008].
-The second factor is word length, which correlates with phonological connectivity.
-<!-- [@pisoni1985].-->
-
-Since PAT was uninformative, we dropped it from this analysis, keeping only PAC.
-This simplified the model because we no longer needed to fit growth month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.} A more direct way to assess and compare the contribution of PAC in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.
-
-We used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.} For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g.
-"father" counts as "daddy").
-For word length, we counted the number of phonemes in our generated IPA transcription.
-
-We conducted two analyses.
-We fit a linear regression for each language, and we fit a linear mixed-effect model to all the data pooled across languages, with language as a random effect.
-Figure \ref{fig:regressions_img} shows the coefficient estimate for each predictor in each language, and Figure \ref{fig:regressions_all_img} shows the coefficient estimates for all languages combined (all predictors were centered and scaled).
-The findings were as follows.
-Overall, frequency is the largest and most consistent predictor of age of acquisition, replicating results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015].
-Word length predicts learning in some languages such as Croatian and Norwegian, but not in others (including English).
-It remains, however, a significant predictor in the global model.
-As for the factors of interest, i.e., semantic and phonological connectivity, we also found cross-linguistic differences.
-Phonological connectivity contributes to learning in languages such as Croatian, English and Russian, whereas semantic connectivity contributes to learning in Turkish, Spanish and to some extent in Croatian, but not in English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
-This contrasts with the original finding in Hills et al.
-2009.
-However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: Our study uses a larger set of nouns.} Despite these cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model.
-
-# Discussion
-
-The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers.
-We compared two network growth scenarios and assessed their relative contributions across eight languages.
-One scenario, PAT, described a rich-get-richer network growth model in which the structure of the learner's internal network determines future growth; the other, PAC, described a model in which the external, global environmental network structure determines learners' growth patterns.
-Our findings largely replicate the results obtained by @hills2009: Semantic networks grow by preferential acquisition, not by preferential attachment.
-A novel finding is that phonological networks also grow primarily by preferential acquisition.
-Moreover, both semantic and phonological connectivity in the learning environment predict growth.
-These findings generalize well across languages.
-When pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others.
-Nevertheless, this cross-linguistic variability is to be taken with a grain of salt as it might be exaggerated in our study by the limited and partially-overlapping sample of nouns for each language.
-In fact, both phonological and semantic connectivity are significant predictors when data are pooled across languages.
-
-```{r }
-
-#Import data from saved
-regression_all <- feather::read_feather("../saved_data/regression_all_bis.feather")
-regression_all_noCov <- feather::read_feather("../saved_data/regression_all_bis_noCov.feather")
-
-pred_regression_all <- ggplot(regression_all, aes(x = predictor, y = estimate)) +
-  geom_pointrange(aes(ymin = lower, ymax = upper, col = predictor), size=0.3)+
-  geom_pointrange(data=regression_all_noCov,
-                  aes(ymin = lower, ymax = upper, col = predictor),
-                  position = position_dodge(width = .3),
-                  linetype=1,
-                  size = 0.7,
-                  fatten = 1.5,
-                  alpha = 0.3)+
-  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
-  coord_flip() +
-  guides(colour=FALSE)+
-  scale_colour_solarized() +
-  theme_few()+
-  theme(aspect.ratio = 0.7)
-
-ggsave("figs/pred_regression_all.png", plot = pred_regression_all, width = 4, height = 2)
-```
-
-```{r regressions_all_img, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=3, fig.cap = "\\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
-Ranges indicate 95\\% confidence intervals.
-Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}
-
-pred_regression_all
-
-#img <- png::readPNG("figs/pred_regression_all.png")
-#grid::grid.raster(img)
-```
-
-Children start by learning words that have high semantic and phonological similarity to a variety of other words in the learning environment, not in the child's available lexicon.
-This result suggests that children are sensitive to connectivity even without having first acquired the connected words.
-How can children indirectly detect highly connected words, and why would such words be more readily learned?
-
-In the semantic case, the networks are based on free association norms.
-These associations can be (partly) derived from the patterns of word-word co-occurrence [e.g., @griffiths07], i.e., two words are associated if they co-occur in many different contexts.
-In a network structure, highly connected words would be the words that co-occur with many other words in various contexts.
-Why would such words be easier to learn?
-One possibility, suggested by @hills2010, is that the referents of these words are more easily disambiguated from other potential referents because their presence in multiple contexts provides more cross-situational, disambiguating statistics about their true referents [@smith2008].
-
-In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999].
-That is, highly connected words tend to be made of frequent sound sequences.
-Even infants show a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994].
-Moreover, phonotactic probability facilitates learning and recognition [e.g., @storkel2001].
-In other words, children's sensitivity to local phonotactic regularities might lead them to learn higher-probability words more easily.
-This learning effect, in turn, would lead to an observed pattern of growth that would appear to follow the PAC growth model even though learners themselves would only be tracking local statistics.
-
-Finally, while validating previous results using network growth models, our study suggests that these correlational patterns may emerge from the operation of simpler mechanisms in both the semantic and phonological domains.
-One question for future experimental work is whether such patterns of growth can be produced in controlled behavioral experiments.
-<!--Finally, this study shares a number of limitations with previous studies using similar research strategy and dataset.For instance, we used normative age of acquisition.
-However, individual children may follow different learning trajectories.
-The use of longitudinal data would allow us to assess how the aggregate behavior relates to these individual trajectories [e.g., typical vs.
-late talkers, @beckage2011].
-Moreover,In particular, the results provide correlational but not causal evidence.
-Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments.
--->
 

### 2018-12-25 cogsci/cogsci.tex
new changes

@@
 \usepackage[subtle]{savetrees}
+\usepackage{tipa}
 
@@
 
-How do children acquire words? An important step consists in mapping a
-phonological form (e.g.~the sound ``cat'') to a semantic referent (the
-concept CAT). A large body of work has been devoted to explore the
-mechanism of this mapping (Quine, 1960; Markman, 1990; Smith and Yu,
-2008). However, words do not exist in a vacuum; they are organized into
-a strcuture based on both semantic and phonological similarity
-principles (e.g., Collins \& Loftus, 1975; Luce \& Pisoni, 1998). A more
-accurate understanding of word learning should account not only for how
-sounds are mapped to meanings, but also for how sound similarity and
-meaning similarity may influence the process of aqusition.
+Over the first year of life, children become sensitive to the phonetic
+variations that are used to distinguish meanings in their native
+language (Werker and Tees, 1984). One could imagine that these
+perceptual skills would be automatically applied to the task of word
+learning. However, developmental data show that 14 m.o children find it
+challenging to associate minimally different (but perceptually
+discriminated) sounds such as ``bin'' and ``din'' to different objects
+(Stager \& Werker, 1997).
 
-We know that similarity affect word recognition in both adults and
-children. For example, exposure to a word such as ``cat'' influences
-subsequent recognition of phonologically and smantically similar words
-like ``cab'' and ``dog'' (Goldinger, Luce \& Pisoni, 1989; McNamara,
-2006; Arias-Trejo \& Plunkett, 2010; Mani \& Plunkett, 2011).
+Several factors can explain this pattern of results. For example it is
+possible that the task of meaning learning increases cognitive demands
+on children (compared to a simple perceptual descrimination). In
+particular, it requires paying attention to both the sounds and the
+corresponding objects, which may hinder precise encoding in memory of
+some phonetic details (Stager a\& Werker, 1997). Additional difficulty
+might arise from ambiguous phonological boundaries at this stage of
+development (e.g., Rost \& McMurray, 2009), or from uncertainty about
+the referential status of the novel word (Fennell \& Waxman, 2009).
 
-Crucially, similarity influences not only the recognition of know words,
-but also the learning of novel words. For example, Swingley \& Aslin
-(2007) showed that infants found it more challenging to learn the
-meaning of a novel word such as ``tog'' (which is similar a the familiar
-word ``dog'') than to learn the meaning of a word such as ``shang''
-(which is not similar to any words children knew). When learning two
-novel words, Stager and Werker (1997) found that infatns were more
-likely to succeed when these words were phonologically distant (e.g.,
-``lif''/``neem''), than when they were phonologcially simialr
-(``bin/''din``). Besides, children learn the semantic relationship among
-newly learned words spontaneousely (Wojcik \& Saffran, 2013), and they
-prioritize the acquisition of words that are distinct in the semantic
-space (Engelthaler \& Hills, 2017).
+Regardless of the exact explanation, it is generally accepted that by
+around 17 m.o, chidlren succeed under the same circumstances (Werker et
+al. 2002). What could be the mechanism of development? Swingley
+contrasted a binary-discontinuous scenario to a probabilstic-continuous
+one. On the discontinuous account, younger children learn a single,
+underspecified representation of similar words (e.g., ``bin''/``din'').
+Development occurs when children specify this intial coarse
+reprepsentation and learn two distinct catgories. On the continuous
+account, distinct represetations are successfully learned from the
+start, but these representations are encoded with higher uncertainty in
+youger children, leading to apparent failure in relatively demanding
+tasks.
 
-That said, previous experimental work has studied the effect of
-phonological and semantic similarity separately. Some studied the
-mechanism of word learning using a toy lexicon where only the
-phonological similarity varied (e.g., Stager and Werker, 1997), and
-others studied the learning of a toy lexicon where only the semantic
-similarity varied (e.g., Wojcik \& Saffran, 2013). However, children
-acquire a lexicon which is more richly structured than these special
-cases. In particular, as reviewed abvove, the end-state lexicon involves
-variability along both the phonological and semantic domains. Thus, to
-have a deeper understanding of word acquisition in the real world, it is
-crucial to study how learners acquire a lexicon that simulates this
-bi-dimensional variation.
+Experimental evidence suggest a probabilsitic-continuous, rather than a
+stage-like develomental scenario. On the one hand, 14-month-olds who
+typically fail in the original task succeed when learning is probed
+using a testing method with lower memory demands (Yoshida et al. 1009),
+and when uncertainty in the emerging representations is mitigated using
+disambiguating contextual cues (Thiessen, 2007; Dautriche et al., 2016).
+On the other hand, adults show patterns of learning similar to those
+shown by 14-month-olds when the task is more challenging and when
+similarity between words increases (Pajak et al., 2016; White et al.,
+2013).
 
-One could imagine two learning scenarios. On the first one, children's
-learning, at least in some challenging situations, is primarily
-determined by one dimension (Sloutsky \& Napolitano, 2003; Colavita et
-al. 1975). For example, it is possible that similar sounding words are
-confusable and hard to learn regardless of their semantic similarity.
-Vice-versa, similar meanings might be challenging to learn regardless of
-the phonological similarity of their forms. On the second scenario,
-learners combine cues from both dimensions to optimize their learning
-(Fourtassi and Frank, 2018; Ernst \& Banks, 2002). Thus, confusability
-that may arise from high similarity along one dimension can be mitigated
-via higher distance from the other dimension. In this study, we explore
-these hypothesis, bla bla
+Following this experimental studies, the purpose of the current work is
+to propose a precise probabilsitc model of the Stager and Werker's task,
+and to explore the extent to which such a model could provide a unified
+accounts for several documented (as well as new) patterns of learning
+and development. We first present the model and explain how it can be
+used to make precise predictions of the target behavioral responses.
+Second, using new data collected from both preschool children and
+adults, we show how the probabilistic strucure of the model can explain
+behavioral patterns both within the same age and across development.
 
-A second goal of this work is to investigate how the learning mechanism
-develops over the life span. According to one hypothesis, adults use
-qualitatively distinct learning mechanisms than children, due, for
-example, to maturational factors. To illustrate, in the experimental
-setting used in Stager and Werker (1997), children's difficulty with
-learning similar sounding words--despite their ability to perceptually
-differentiate them--might be attributed to their inferior working
-memory, hindering their ability to attend simultaneously to the sound
-contrast and the meanings. A second hypothesis proposes that learners
-use fundamentally similar mechanisms across the life span, and that the
-difference might be one of degree, not kind. For example, though they
-have vastly greater working memory capacity, adults show patterns of
-word processing and learning which parallel results obtained with
-children in Stager and Werker's study (White et al. 2013; Pajak et al.
-2016). Here we explore
+\begin{CodeChunk}
+\begin{figure}[H]
 
-Talk a bit about what we do
+{\centering \includegraphics{figs/growth-1}
 
-\section{Experiment 1}\label{experiment-1}
+}
 
-Children were trained to learn the association between pairs of
-nonesense words (e.g., ``lif''/``neem'') and pairs of objects (e.g., two
-flowers). After training, children performed a series of two-alternative
+\caption{\label{fig:growth}Illustration of the growth scenarios.
+Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
+Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
+}\label{fig:growth}
+\end{figure}
+\end{CodeChunk}
+
+\section{Model}\label{model}
+
+\subsection{Task}\label{task}
+
+We model a variant of the task used in Yoshida et al. 2009. In this
+task, particiants are first exposed to the association between pairs of
+nonesense words (e.g., ``lif''/``neem'') and pairs of objects. After
+this exposure phase, participants perform a series of two-alternative
 forced choices. In each testing trial, one of the two sounds is uttered
 (e.g., ``lif'') and participants choose the corresponding object from
-the two alternatives (e.g., flower 1 or flower 2). Each child learned an
-artificial lexicon where both the pairs of sounds and the pairs of
-objects can be similar or different. Our predictions were as follows. If
-the sound and meaning interact in word learning, then the pair of words
-that differ on both the meaning and sound levels should be the easiest
-to learn, followed by the pairs of words that are different on one
-level, but similar on another level. Finally, the pair of words that are
-similar on both levels should be the most difficult to learn.
+the two alternatives.
+
+\subsection{Probabilistic strcuture}\label{probabilistic-strcuture}
+
+Our model consists of a set of variables describing the general process
+of spoken word recognition in a referential situation. These variables
+are related in a way that refelects the simple generative scenario
+represented graphically in Figure XX. When a speaker utters a sound in
+the presence of an object, the observer assumes that the object \(o\)
+activated the concept \(C\) in the speaker's mind. The concept prompted
+the cooresponding label \(L\). Finally, the label was physically
+instantiated by the sound \(s\).
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/model-1}
+
+}
+
+\caption{\label{fig:model}Graphical representation of our model.
+Circles indicate random variables (shading indicates observed variables).
+The squares indicates fixed model parameters.}\label{fig:model}
+\end{figure}
+\end{CodeChunk}
+
+Because of the noisy nature of the representations, the observer can
+only determine the hidden variables (i.e., the concept \(C\) and the
+label \(L\)) in a probabilistic fashion. For simplicity, we assume that
+the probability of membership of objects and sounds to concepts and
+labels, respectivel, are normally distributed:
+
+\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
+\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
+one-to-one mappings between concepts and labels, and that observers have
+successfully learned these mappings during the exposure phase: \[
+P(L_i|C_j) = 
+\begin{cases}
+  1 & \text{if  }  i=j \\  
+  0  & \text{if  }  i\neq j 
+\end{cases}
+\] \#\# Predictions
+
+During the testing phase (see Figure 1), participants are presented with
+one target sound \(s_T \in\{s_1, s_2\}\) and two possible objects
+\(o_1\) and \(o_2\). In order to make a choice, we determine which
+object is more probable under the lable \(s_T\), in other words, we
+compare the the probabilities \(P(o_1|s_T)\) and \(P(o_2|s_T)\). The
+values of these probabilities can be computed by summing over all
+possible labels:
+\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
+The joint probability \(P(o, C, L, s)\) is obtained by factoring the
+bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
+which could be tansformed using Bayes rule into:
+
+\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
+concept prior is a uniform ditribution, we obtain the following
+expression, where all conditional dependencies have been defined in the
+previous secton.
+
+\begin{equation}
+P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
+\end{equation}
+
+From the general expression (1) we were able to derive the exact
+analytical expression of the probability of correct responses in the
+testing phase of our simplified experimenal setting (Figure 1).
+
+\begin{equation}
+P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
+\end{equation}
+
+We simulate the values of this probability as a function of the
+perceptual distance between the sounds \(\Delta s\), using the two
+remining parameters of the model: the visual distance between the
+semantic referents \(\Delta o\) and the values of the standard deviation
+of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
+simulation, have similar values, i.e.,
+\(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
+Figure 3.
+
+\begin{CodeChunk}
+\begin{figure*}[h]
+
+{\centering \includegraphics{figs/simulation-1}
+
+}
+
+\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits.}\label{fig:simulation}
+\end{figure*}
+\end{CodeChunk}
+
+The simulations explain previousely documented facts, and make new
+predictions:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\item
+  For fixed values of \(\Delta o\) and \(\sigma\), the probability of
+  accurate responses increases as a function of \(\Delta s\). This
+  pattern accounts for the fact that similar sounds are generally more
+  challenging to learn than different sounds for both chidlren (Stager
+  and Werker, 1997) and adults (Pajak et al. 2016).
+\item
+  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
+  when the noise characterized with \(\sigma\) decreases. This fact may
+  explain development, i.e., youger children have noisier
+  representations (Swingley, 2007; Yoshida et al. 2009), which lead to
+  lower word recognition accuracy, especially for similar sounding
+  words.
+\item
+  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
+  when the visual distance between the semantic referents \(\Delta o\)
+  increases. This is a new predcition that our model makes. Previous
+  work studied the effect of several bottom-up and top-down properties
+  in disambiguating similar sounding words (see introduction), But no
+  previous study tested the effect of the visual distance between the
+  semantic referents.
+\end{enumerate}
+
+To sum, we introduced a model that accounts for some qualitative
+patterns observed in previous studies, and makes new predictions. In the
+experiment below, we test whether the model makes accurate
+\emph{quantitative} predictions by fitting it to new experimental data
+collected from preschool chidlren and adults.
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/illus-1}
+
+}
+
+\caption{\label{fig:illus}Graphical representation of our model.
+Circles indicate random variables (shading indicates observed variables).
+The squares indicates fixed model parameters.}\label{fig:illus}
+\end{figure}
+\end{CodeChunk}
+
+\section{Experiment}\label{experiment}
+
+In this experiment, we tested participants in the word learning task
+introduced above (Figure 1). We explored all three parameters of the
+model. Both the sound similarity (\(\Delta s\)) and object similarity
+(\(\Delta o\)) were varied simulataneousely in a within-subject design.
+Besides, two age groups (preschool children and adults) were tested on
+the same task to explore whether development can be characteized with
+the degree of uncertainty, \(\sigma\), in the probabilsitic
+representations.
 
@@
 28 children participated but were removed from analyses because they
-were not above chance on the catch trials (as specified in the
-pre-registration).
+were not above chance on the catch trials (as was specified in the
+pre-registration\footnote{https://osf.io/jrh38/}). We also collected a
+planed sample of N=30 adults on Amazon Mechanical Turk. N=2 adult
+participants were excluded because of low scores on the catch trials
+(see pre-registration).
 
-\subsubsection{Stimuli}\label{stimuli}
+\subsubsection{Stimuli and similarity
+rating}\label{stimuli-and-similarity-rating}
 
 The sound stimuli were generated using the MBROLA Speech Synthesizer
-(Cite) using an American English voice. We generated two similar sound
-pairs (``aka''/``ama'' and ``ada''/``aba'') and two different sound
-pairs (``lif''/``neem'' and ``zem''/``doof''). We generated a addtional
-pair (``nak''/``veep'') which we used in the catch trial (see
-Procedure). As for the objects used as semantic referents, we used the
-Dynamic Categories Stimuli (Cite) which allowed us to generate objects
-in four different categories: ``tree'', ``bird'', ``bug'', and ``fish''
-(plus the additional category ``flower'' for the catch trial). These
-categories are supposed to be naturally occuring kinds that might be
-seen on an alien planet. In each category, we generated instances that
-varied in their similarity by manipuating a continuous property
-controling features of the category's shape. This property was the head
-fatness for the category ``bug'', the body strech for ``bird'', the tail
-size relative to the body fatness for ``fish'', the width of the trunk
-for ``tree'', and finally center size for ``flower''. All these
-continous properties varied on a scale from 0 to 1. We generated
-``similar'' and ``different'' objects' pairs (whithin each category) by
-setting the values of this properties to 0 and 0.5, and to 0 and 1,
-respectively. Examples of the resuting pairs are shown in Figure XX.
+(Dutoit et al., 1996). We generated three kinds of sound pairs which
+varied in their degree of similarity to English speakers: 1)
+``different'': ``lif''/``neem'' and ``zem''/``doof'', 2)
+``intermediate'': ``aka''/``ama'' and ``ada''/``aba'', and 3)
+``similar'' non-English minimal pairs: ``ada''/``a\textipa{d\super h}a''
+(in hindi) and ``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).
+
+As for the objects, we used the Dynamic Stimuli javascript
+library\footnote{https://github.com/erindb/stimuli} which allowed us to
+generate objects in four different categories: ``tree'', ``bird'',
+``bug'', and ``fish''. These categories are supposed to be naturally
+occuring kinds that might be seen on an alien planet. In each category,
+we generated ``different'', ``intermediate'' and ``similar'' levels of
+similarity by manipuating a continuous property controling features of
+the category's shape (e.g, body strech and head fatness).
+
+In a separate survey, \(N=20\) participants recruited on Amazon
+Mechanical Turk evaluated the similarity of each sound and objcet pair
+on a 7-point scale. We used the average ratings across participants as
+qunatitaive measures of sound pairs' distance (\(\Delta s\)) and object
+pairs' distance (\(\Delta o\)).
 
@@
 
-The experiment consisted of 4 conditions which consisted, each, of a
-pair of sounds-objects associations. These conditions were constructed
-by crossing the sound's degree of similarity with the object's degree of
-similarity leading to a 2x2 factorial design. Besides the 4 conditions,
-we also tested participants on a fifth catch condition which was similar
-to the previous ones. It involved different sounds and different
-objects, and it was used only to select participant who were able to
-follow the instructions and show minimal learning (not at chance level).
+Each age group saw only two of the three levels of similarity described
+in the previous sub-section: ``different'' vs. ``intermediate'' for
+preschoolers, and ``intermediate'' vs. ``similar'' for adults. The
+experiment consisted of four conditions which involved, each, one pair
+of sounds-objects associations. These conditions were constructed by
+crossing the sound's degree of similarity with the object's degree of
+similarity leading to a 2x2 factorial design in each age group. Besides
+the 4 conditions, we also tested participants on a fifth catch condition
+which was similar in its stucture to the other ones, but was used only
+to select participant who were able to follow the instructions and show
+minimal learning.
+
+\begin{CodeChunk}
+\begin{figure*}[h]
+
+{\centering \includegraphics{figs/all_data-1}
+
+}
+
+\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
+Results are shown in each language for phonological and semantic networks.
+Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
+\end{figure*}
+\end{CodeChunk}
 
@@
 
-Children were asked if they would be willing to play a game on a tablet
-with the experimenter and were informed that they could stop playing at
-any time. The experimenter explained that the game consisted in learning
-some words spoken in an alien planet. The experiment began with two
-simple examples (not included in the analysis), and in these examples
-children were given feedback from the experimenter so as to make sure
-they correctly understood the structure of the task. After the
+Preschoolers were asked if they would be willing to play a game on a
+tablet with the experimenter and were informed that they could stop
+playing at any time. The experimenter explained that the game consisted
+in learning some words spoken in an alien planet. The experiment began
+with two simple examples (not included in the analysis), and in these
+examples children were given feedback from the experimenter so as to
+make sure they correctly understood the structure of the task. After the
 introduction and examples, children were tested in a sequence of five
@@
 the on-screen position (left vs.~right) of the two pictures on each
-testing trial. The experiment can be views online using this link XX.
+testing trial.
 
-\subsubsection{Results}\label{results}
+The procedure for preschoolers and adults were identical except that
+preschoolers were accompagnied by an experimenter and used a tablet,
+whereas adults used their local computers to complete the experiment
+online.
 
-\begin{CodeChunk}
-\begin{figure}[H]
+\subsubsection{Model fitting}\label{model-fitting}
 
-{\centering \includegraphics{figs/growth-1}
+We fit the analystical expression (equation 2) to the participants'
+responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
+were set based on data from the similarity judgment task (described in
+the stimuli sub-section). We used two models: \textbf{model 1} fit only
+one parameter (\(\sigma = \sigma_C =\sigma_L\)), and \textbf{model 2}
+fit two parameters (\(\sigma_C \neq \sigma_L\)). The values of the
+parameters were derived using weighted least-squares estimates.
 
-}
+\subsection{Results}\label{results}
 
-\caption{\label{fig:growth}Illustration of the growth scenarios.
-Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
-Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to.
-Thus, according to PAT, the node E1 is more likely to enter the lexicon first.
-For PAC, the utility of a candidate node is its degree in the entire network.
-According to PAC, the node E2 is more likely to enter the lexicon first.}\label{fig:growth}
-\end{figure}
-\end{CodeChunk}
+First we analyzed the experimental results shown in Figure (XX, left),
+using a mixed-effects logistic regression with sound and object
+distances as fixed effects, and with a maximal random effects strcuture
+(Barr et al. 2013). Results are shown in Table XX. We found a main
+effect of sound distance on the accuray of learning in both children and
+adults, thus replicating previous findings. We also found a main effect
+of object distance, thus confirming the new hypothesis derived from our
+model.
 
-Studies that investigate lexical network growth have focused on semantic
-networks using English data (Hills, Maouene, Riordan, \& Smith, 2010;
-Hills, Maouene, Maouene, Sheya, \& Smith, 2009; Steyvers \& Tenenbaum,
-2005). The novelty of the current study is threefold: First, it
-investigates whether phonological networks, like semantic networks, grow
-by PAC, or if they rather grow by PAT. Second, it provides a systematic
-comparison of both network growth scenarios in the phonological and the
-semantic domains and assesses their relative contribution to the
-learning process. Third, it tests the generality of the findings across
-eight languages.
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/all_data-1}
-
-}
-
-\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
-\end{figure*}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/degree_distribution-1}
-
-}
-
-\caption{\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages.
-A perfect power-law distribution should appear as a straight line in this graph.}\label{fig:degree_distribution}
-\end{figure*}
-\end{CodeChunk}
-
-\section{Networks}\label{networks}
-
-\subsection{Data}\label{data}
-
-We used data from Wordbank (Frank, Braginsky, Yurovsky, \& Marchman,
-2017), an open repository aggregating cross-linguistic language
-developmental data of the MacArthur-Bates Communicative Development
-Inventory (CDI), a parent report vocabulary checklist. Parent report is
-a reliable and valid measure of children's vocabulary that allows for
-the cost-effective collection of datasets large enough to test
-network-based models of acquisition (Fenson et al., 1994). We used the
-\emph{Words and Sentences} version of the CDI which contains the
-productive vocabulary of toddlers (age varied between 16 to 36 months).
-Following previous studies (Hills et al., 2009; Storkel, 2009), we
-restricted our analysis to nouns. We defined the age of acquisition of a
-given word by the month at which this word was produced by at least 50\%
-of children (J. C. Goodman, Dale, \& Li, 2008), and we excluded nouns
-that have not been learned (according to this criterion) by the last
-month for which we have CDI data.
-
-We obtained these nouns in eight languages: Croatian, Danish, English,
-Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of
-nouns that had entries in the Florida Association Norms (see below).
-Since these norms are available only in English, we used the
-hand-checked translation equivalents provided by Braginsky, Yurovsky,
-Marchman, \& Frank (2016), allowing us to use the English association
-norms across languages. Table \ref{tab:stats} gives an overview of the
-data used. Translation equivalents were originally constructed for a
-subset of words appearing on the toddler CDI form, and so not all words
-are currently available. Note, however, that all languages have at least
-60\% of nouns translated.
-
-\begin{table}[H]
-\centering
-\begin{tabular}{rlrrr}
-  \hline
- & language & total & translated & normed \\ 
-  \hline
-1 & Croatian & 253 & 177 & 170 \\ 
-  2 & Danish & 295 & 198 & 187 \\ 
-  3 & English & 296 & 296 & 274 \\ 
-  4 & Italian & 311 & 203 & 194 \\ 
-  5 & Norwegian & 305 & 193 & 186 \\ 
-  6 & Russian & 311 & 311 & 285 \\ 
-  7 & Spanish & 240 & 173 & 163 \\ 
-  8 & Turkish & 293 & 175 & 164 \\ 
-   \hline
+\begin{table}[!htbp] \centering 
+  \caption{Estimates of predictor coefficients (and their standard errors) by age group in the regression model} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lcc} 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & Children & Adults \\ 
+\hline \\[-1.8ex] 
+ (Intercept) & 0.426$^{*}$ (0.199) & 3.114$^{**}$ (1.015) \\ 
+  Sound  & 0.272$^{**}$ (0.100) & 2.320$^{*}$ (0.981) \\ 
+  Object & 0.315$^{*}$ (0.137) & 2.133$^{*}$ (0.952) \\ 
+  Sound x Object & 0.151 (0.097) & 1.821 (0.976) \\ 
+ \hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.05; $^{**}$p$<$0.01; $^{***}$p$<$0.001} \\ 
 \end{tabular} 
-\caption{\label{tab:stats}Total number of nouns produced by toddlers in the CDI (left).
-We included in our study the subset of these nouns that had available English translations (middle).
-The final set consisted of nouns that had both available translations as well entries in the Free Association Norms (right).}
 \end{table}
-
-\subsection{Semantic networks}\label{semantic-networks}
-
-We constructed semantic networks following the procedure outlined in
-Hills et al. (2009). We used as an index of semantic relatedness the
-Florida Free Association Norms (Nelson, McEvoy, \& Schreiber, 1998).
-This dataset was collected by giving adult participants a word (the
-cue), and asking them to write the first word that comes to mind (the
-target). For example, when given the word ``ball'', they might answer
-with the word ``game''. A pair of nodes were connected by a directed
-link from the cue to the target if there was a cue-target relationship
-between these nodes in the association norms. The connectivity of a
-given node was characterized by its \emph{indegree}: the number of links
-for which the word was the target. To model growth from month to month,
-we constructed a different network at each month, based on the words
-that have been acquired by that month.
-
-\subsection{Phonological networks}\label{phonological-networks}
-
-We generated approximate International Phonetic Alphabet (IPA)
-transcriptions from the orthographic transcription, across languages,
-using the open source text-to-speech software
-\textbf{\href{http://http://espeak.sourceforge.net/}{Espeak}.} We used
-the Levenshtein distance (also known as edit distance) as a measure of
-phonological relatedness between two nodes. The measure counts the
-minimum number of operations (insertions, deletions, substitutions)
-required to change one string into another.
-
-In previous studies, two nodes were linked if they had an edit distance
-of 1 (e.g., Storkel, 2009). However, in these previous studies the
-network was built using an adult vocabulary. In the current study,
-however, network growth models are based on the children's early
-vocabulary which contains very few word pairs with an edit distance of
-1. When using this threshold, the resulting networks were too sparse and
-uninformative. Thus, we increased the threshold from 1 to 2, that is,
-two nodes were related if their edit distance was equal to 1 or 2. The
-connectivity of a given node was characterized with its \emph{degree}:
-the number of links it shares with other words.
-
-\section{Analysis}\label{analysis}
-
-\subsection{Static properties of the global
-network}\label{static-properties-of-the-global-network}
-
-We start by analyzing word connectivity in the global (static) network.
-We constructed this network using nouns learned by the oldest age for
-which we have CDI data (e.g., in English this corresponds to the network
-by 30 months). This global network is the end-state towards which both
-PAT and PAC should converge by the last month of learning. Moreover,
-following Hills et al. (2009), we used this end-state network as a proxy
-for the external connectivity in the learning environment. Below we
-analyze properties of this global networks that are relevant to PAC
-and/or PAT.
-
-\subsubsection{Connectivity predicts the age of
-acquisition}\label{connectivity-predicts-the-age-of-acquisition}
-
-Connectivity in the global network is directly related to PAC as it
-represents the explicit criterion PAC uses to determine what words
-should be learned first (Figure \ref{fig:growth}). Therefore, a direct
-consequence of a PAC-like growth scenario is a correlation between
-connectivity in the global network and the age of
-acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed.
-Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around.
-Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.}
-Figure \ref{fig:data_all} shows how the age of acquisition for each word
-varies as a function of its degree (or indegree for the semantic
-network). For ease of visual comparison, the predictor (i.e., the
-degree) was centered and scaled across languages. The plots show,
-overall, a negative correlation between the month of acquisition and the
-degree, indicating that nouns with higher degrees are generally learned
-earlier.
-
-\subsubsection{Power-law degree
-distribution?}\label{power-law-degree-distribution}
-
-We also analyzed the global network's degree distribution. The shape of
-this distribution is particularly relevant to PAT as this growth
-scenario is known to generate networks with a power-law degree
-distribution (i.e., a distribution of the form
-\(p(k) \propto \frac{1}{k^{\alpha}}\), Barabasi \& Albert, 1999). If the
-network displays this property, this fact would suggest a PAT-like
-generative process. Conversely, if the degree distribution does not
-follow a power law, this fact would weaken the case for PAT. The log-log
-plots are shown in Figure \ref{fig:degree_distribution}. We fit a power
-law to each empirical degree distribution following the procedure
-outlined in Clauset, Shalizi, \& Newman (2009) and using the related R
-package (poweRlaw, Gillespie, 2015). In brief, the analysis consisted in
-two steps. First, we derived the optimal cut-off, \(k_{min}\), above
-which the distribution is more likely to follow a power
-law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.}
-and we estimate the corresponding scaling parameter \(\alpha\). Second
-we calculated the goodness-to-fit, which resulted in a \(p\)-value
-quantifying the plausibility of the model. Overall, we could not reject
-the null hypothesis of a power-law distribution: the \(p\)-value was
-generally above 0.1, except for the Italian phonological network where
-we obtained \(p < 0.05\), suggesting that the power law can be ruled out
-in this particular case.
-
-In sum, the static properties of the global network are \emph{a priori}
-compatible with both PAT and PAC. In order to decide between these two
-developmental scenarios, we need to fit explicit growth models to the
-data.
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/pred_ind_img-1}
-
-}
-
-\caption{\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid).
-Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\% credible intervals (computed using the highest density intervals).
-Positive values mean that learning proceeds according to the predictions of the growth scenario.
-Negative values mean that learning proceeds in opposition to the predictions of the growth scenario.}\label{fig:pred_ind_img}
-\end{figure*}
-\end{CodeChunk}
-
-\subsection{Network growth models}\label{network-growth-models}
-
-\subsubsection{How does each growth scenario predict noun
-development?}\label{how-does-each-growth-scenario-predict-noun-development}
-
-To test the network growth scenarios, we fit different growth models to
-the data. We calculated the probability that a word \(w_i\), with a
-growth value \(d_i\) would enter the lexicon at a given month, using a
-softmax function:
-
-\begin{equation}
- p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
-\end{equation}
-
-\noindent where \(\beta\) is a fitted parameter that captures the
-magnitude of the relationship between network parameters and growth
-(analogous to a regression coefficient). A positive value of \(\beta\)
-means that words with higher growth values \(d_i\) are acquired first,
-and a negative value means that words with lower growth values are
-acquired first (see Figure \ref{fig:growth} for an illustration of how
-growth values \(d_i\) are defined in each growth scenario). The
-normalization includes all words that could be learned at that month.
-
-We estimated the parameter \(\beta\) using a Bayesian approach. The
-inference was performed using the probabilistic programming language
-WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
-over \(\beta\), and at each month, we computed the likelihood function
-over words that could possibly enter the lexicon at that month, fit to
-the words that have been learned at that month (using formula 1). Markov
-Chain Monte Carlo sampling resulted in a posterior distribution over
-\(\beta\), which we summarized in Figure \ref{fig:pred_ind}.
-
-For the semantic networks, the results replicate Hills et al.'s finding
-in English, which is that the semantic network grows by PAC, not by PAT.
-Moreover, this finding holds in seven of the eight languages we
-examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences.
-However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.}
-The PAC model also fits better than PAT for phonological networks. We
-note however that PAT, though weaker, fares better for the phonological
-networks (where it predicts part of the growth process in some languages
-such as Croatian, English, Norwegian and Russian) than it does for the
-semantic networks (where it is rather universally unpredictive).
-
-\subsubsection{What is the relative contribution of each growth
-model?}\label{what-is-the-relative-contribution-of-each-growth-model}
-
-Above we evaluated the network growth scenarios individually. As a next
-step, we analyzed their relative contribution to the learning process.
-This was done through adding more fitted parameters to the model, that
-is, by substituting \(\beta d_i\) in formula (1) with:
-\[\beta_{1} d_{i, 1} + \beta_{2} d_{i, 2} + \beta_{3} d_{i, 3} + \beta_{4} d_{i, 4}\]
-where the indices represent the 4 networks: semPAT, semPAC, phonoPAT and
-PhonoPAC. Using the same fitting technique, we obtained the values shown
-in Figure \ref{fig:pred_ind}. PAC dominates the learning. Both
-phonological and semantic networks contribute to lexical growth, but the
-phonological network appears to be stronger and more consistent across
-languages. In summary, the findings show that both semantic and
-phonological networks contribute to the learning process, and that they
-both grow primarily by PAC, relying on the external connectivity in the
-learning environment, rather than the internal connectivity in the
-acquired lexicon.
-
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/regressions_img-1}
-
-}
-
-\caption{\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\% confidence intervals.
-Positive values indicate a positive relationship (e.g.
-longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g.
-words with higher frequency tend to have a lower AoA).}\label{fig:regressions_img}
-\end{figure*}
-\end{CodeChunk}
-
-\subsection{Comparison to other predictors of age of
-acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}
-
-We saw that the way semantic and phonological information is structured
-in the learning environment (i.e., PAC) contributes to noun learning
-across languages. However, we know that other factors influence learning
-as well (e.g., Braginsky et al., 2016). Next we investigated how
-semantic and phonological connectivity interact with two other factors.
-The first one is word frequency, a well studied factor shown to predict
-the age of acquisition in a reliable fashion (e.g. J. C. Goodman et al.,
-2008). The second factor is word length, which correlates with
-phonological connectivity.
-
-Since PAT was uninformative, we dropped it from this analysis, keeping
-only PAC. This simplified the model because we no longer needed to fit
-growth
-month-by-month.\footnote{This was a requirement only for PAT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network.}
-A more direct way to assess and compare the contribution of PAC in
-relation to other word-level factors is through conducting linear
-regressions, where connectivity in the learning environment, frequency
-and length predict the age of acquisition.
-
-We used the frequency estimates from Braginsky et al. (2016) where
-unigram counts were derived based on CHILDES corpora in each
-language.\footnote{Note that these frequency counts are based on transcripts from independent sets of children and represent a general estimate of environmental frequency across children.}
-For each word, counts included words that shared the same stem (e.g.,
-``cats'' counts as ``cat''), or words that were synonymous (e.g.
-``father'' counts as ``daddy''). For word length, we counted the number
-of phonemes in our generated IPA transcription.
-
-We conducted two analyses. We fit a linear regression for each language,
-and we fit a linear mixed-effect model to all the data pooled across
-languages, with language as a random effect. Figure
-\ref{fig:regressions_img} shows the coefficient estimate for each
-predictor in each language, and Figure \ref{fig:regressions_all_img}
-shows the coefficient estimates for all languages combined (all
-predictors were centered and scaled). The findings were as follows.
-Overall, frequency is the largest and most consistent predictor of age
-of acquisition, replicating results for nouns across a variety of
-analyses (Braginsky et al., 2016; J. C. Goodman et al., 2008; B. C. Roy,
-Frank, DeCamp, Miller, \& Roy, 2015). Word length predicts learning in
-some languages such as Croatian and Norwegian, but not in others
-(including English). It remains, however, a significant predictor in the
-global model. As for the factors of interest, i.e., semantic and
-phonological connectivity, we also found cross-linguistic differences.
-Phonological connectivity contributes to learning in languages such as
-Croatian, English and Russian, whereas semantic connectivity contributes
-to learning in Turkish, Spanish and to some extent in Croatian, but not
-in
-English.\footnote{Semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length.
-This contrasts with the original finding in Hills et al.
-2009.
-However, in this previous study, semantic connectivity was not tested in a model that included frequency, length and phonological connectivity as covariates.
-Another important difference is the number of words tested: Our study uses a larger set of nouns.}
-Despite these cross-linguistic differences, both phonological and
-semantic connectivity are significant predictors in the combined model.
-
-\section{Discussion}\label{discussion}
-
-The present study provided a comprehensive analysis of how lexical
-connectivity influences the age of acquisition of nouns in toddlers. We
-compared two network growth scenarios and assessed their relative
-contributions across eight languages. One scenario, PAT, described a
-rich-get-richer network growth model in which the structure of the
-learner's internal network determines future growth; the other, PAC,
-described a model in which the external, global environmental network
-structure determines learners' growth patterns. Our findings largely
-replicate the results obtained by Hills et al. (2009): Semantic networks
-grow by preferential acquisition, not by preferential attachment. A
-novel finding is that phonological networks also grow primarily by
-preferential acquisition. Moreover, both semantic and phonological
-connectivity in the learning environment predict growth. These findings
-generalize well across languages. When pitted against other known
-predictors of age of acquisition (word frequency and length), the effect
-of word connectivity shows a cross-linguistic variation, predicting
-learning in some languages, but not in others. Nevertheless, this
-cross-linguistic variability is to be taken with a grain of salt as it
-might be exaggerated in our study by the limited and
-partially-overlapping sample of nouns for each language. In fact, both
-phonological and semantic connectivity are significant predictors when
-data are pooled across languages.
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/regressions_all_img-1}
-
-}
-
-\caption{\label{fig:regressions_all_img}Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect.
-Ranges indicate 95\% confidence intervals.
-Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates.}\label{fig:regressions_all_img}
-\end{figure}
-\end{CodeChunk}
-
-Children start by learning words that have high semantic and
-phonological similarity to a variety of other words in the learning
-environment, not in the child's available lexicon. This result suggests
-that children are sensitive to connectivity even without having first
-acquired the connected words. How can children indirectly detect highly
-connected words, and why would such words be more readily learned?
-
-In the semantic case, the networks are based on free association norms.
-These associations can be (partly) derived from the patterns of
-word-word co-occurrence (e.g., Griffiths, Steyvers, \& Tenenbaum, 2007),
-i.e., two words are associated if they co-occur in many different
-contexts. In a network structure, highly connected words would be the
-words that co-occur with many other words in various contexts. Why would
-such words be easier to learn? One possibility, suggested by Hills et
-al. (2010), is that the referents of these words are more easily
-disambiguated from other potential referents because their presence in
-multiple contexts provides more cross-situational, disambiguating
-statistics about their true referents (Smith \& Yu, 2008).
-
-In the phonological case, connectivity is inherently correlated with
-phonotactic probability (Vitevitch, Luce, Pisoni, \& Auer, 1999). That
-is, highly connected words tend to be made of frequent sound sequences.
-Even infants show a sensitivity for high frequency sound sequences in
-the ambient language (Jusczyk, Luce, \& Charles-Luce, 1994). Moreover,
-phonotactic probability facilitates learning and recognition (e.g.,
-Storkel, 2001). In other words, children's sensitivity to local
-phonotactic regularities might lead them to learn higher-probability
-words more easily. This learning effect, in turn, would lead to an
-observed pattern of growth that would appear to follow the PAC growth
-model even though learners themselves would only be tracking local
-statistics.
-
-Finally, while validating previous results using network growth models,
-our study suggests that these correlational patterns may emerge from the
-operation of simpler mechanisms in both the semantic and phonological
-domains. One question for future experimental work is whether such
-patterns of growth can be produced in controlled behavioral experiments.
 
@@
 
-\hypertarget{refs}{}
-\hypertarget{ref-barabasi99}{}
-Barabasi, A.-L., \& Albert, R. (1999). Emergence of scaling in random
-networks. \emph{Science}, \emph{286}(5439), 509--512.
-
-\hypertarget{ref-braginsky2016}{}
-Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2016).
-From uh-oh to tomorrow: Predicting age of acquisition for early words
-across languages. In \emph{Proceedings of the 38th Annual Conference of
-the Cognitive Science Society}.
-
-\hypertarget{ref-clauset09}{}
-Clauset, A., Shalizi, C. R., \& Newman, M. E. J. (2009). Power-law
-distributions in empirical data. \emph{SIAM Review}, \emph{51}(4),
-661--703.
-
-\hypertarget{ref-fenson94}{}
-Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J.,
-Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early
-communicative development. \emph{Monographs of the Society for Research
-in Child Development}, \emph{59}(5), i--185.
-
-\hypertarget{ref-frank2017}{}
-Frank, M. C., Braginsky, M., Yurovsky, D., \& Marchman, V. A. (2017).
-Wordbank: An open repository for developmental vocabulary data.
-\emph{Journal of Child Language}, \emph{44}(3), 677--694.
-
-\hypertarget{ref-gillespie15}{}
-Gillespie, C. S. (2015). Fitting heavy tailed distributions: The
-poweRlaw package. \emph{Journal of Statistical Software}, \emph{64}(2),
-1--16. Retrieved from \url{http://www.jstatsoft.org/v64/i02/}
-
-\hypertarget{ref-goodman2008}{}
-Goodman, J. C., Dale, P. S., \& Li, P. (2008). Does frequency count?
-Parental input and the acquisition of vocabulary. \emph{Journal of Child
-Language}, \emph{35}(3), 515--531.
-
-\hypertarget{ref-dippl}{}
-Goodman, N., \& Stuhlmuller, A. (2014). The Design and Implementation of
-Probabilistic Programming Languages. \url{http://dippl.org}.
-
-\hypertarget{ref-griffiths07}{}
-Griffiths, T. L., Steyvers, M., \& Tenenbaum, J. B. (2007). Topics in
-semantic representation. \emph{Psychological Review}, \emph{114}(2),
-2007.
-
-\hypertarget{ref-hills2010}{}
-Hills, T. T., Maouene, J., Riordan, B., \& Smith, L. B. (2010). The
-associative structure of language: Contextual diversity in early word
-learning. \emph{Journal of Memory and Language}, \emph{63}(3), 259--273.
-
-\hypertarget{ref-hills2009}{}
-Hills, T. T., Maouene, M., Maouene, J., Sheya, A., \& Smith, L. (2009).
-Longitudinal analysis of early semantic networks: Preferential
-attachment or preferential acquisition? \emph{Psychological Science},
-\emph{20}(6), 729--739.
-
-\hypertarget{ref-jusczyk1994}{}
-Jusczyk, P. W., Luce, P. A., \& Charles-Luce, J. (1994). Infant's
-sensitivity to phonotactic patterns in the native language.
-\emph{Journal of Memory and Language}, \emph{33}(5), 630--645.
-
-\hypertarget{ref-nelson1998}{}
-Nelson, D. L., McEvoy, C. L., \& Schreiber, T. A. (1998). The University
-of South Florida word association, rhyme, and word fragment norms.
-Retrieved from \url{http://w3.usf.edu/FreeAssociation/}
-
-\hypertarget{ref-roy2015}{}
-Roy, B. C., Frank, M. C., DeCamp, P., Miller, M., \& Roy, D. (2015).
-Predicting the birth of a spoken word. \emph{Proceedings of the National
-Academy of Sciences}, \emph{112}(41), 12663--12668.
-
-\hypertarget{ref-smith2008}{}
-Smith, L., \& Yu, C. (2008). Infants rapidly learn word-referent
-mappings via cross-situational statistics. \emph{Cognition},
-\emph{106}(3), 1558--1568.
-
-\hypertarget{ref-steyvers2005}{}
-Steyvers, M., \& Tenenbaum, J. B. (2005). The large-scale structure of
-semantic networks: Statistical analyses and a model of semantic growth.
-\emph{Cognitive Science}, \emph{29}(1), 41--78.
-
-\hypertarget{ref-storkel2001}{}
-Storkel, H. L. (2001). Learning new words: Phonotactic probability in
-language development. \emph{Journal of Speech, Language, and Hearing
-Research}, \emph{44}(6), 1321--1337.
-
-\hypertarget{ref-storkel2009}{}
-Storkel, H. L. (2009). Developmental differences in the effects of
-phonological, lexical and semantic variables on word learning by
-infants. \emph{Journal of Child Language}, \emph{36}(2), 29--321.
-
-\hypertarget{ref-vitevitch1999}{}
-Vitevitch, M. S., Luce, P. A., Pisoni, D. B., \& Auer, E. T. (1999).
-Phonotactics, neighborhood activation, and lexical access for spoken
-words. \emph{Brain and Language}, \emph{68}(1), 306--311.
-
 \end{document}

### 2018-12-28 Analysis/process.Rmd
new modif on manuscript

@@
 theme_set(theme_few())
-```
-
-Processing for IRB
-
-```{r}
-d1 <- read_delim("data_real1.txt", delim = " ")  %>%
-  filter(code != 'test',
-         !is.na(code)) %>%
-  distinct(ID, gender, age, code)
-
-d2 <- read_delim("data_real2.txt", delim = " ") %>%
-  filter(code != 'test',
-         !is.na(code)) %>%
-  distinct(ID, gender, age, code)
-
-d3 <- read_delim("data_winter.txt", delim = " ") %>%
-  filter(code != 'test',
-         !is.na(code)) %>%
-  distinct(ID, gender, age, code)
-
-d_all <- d1 %>%
-  bind_rows(d2) %>%
-  bind_rows(d3) %>%
-  rowwise() %>%
-  mutate(date = strsplit(code, split = "-")[[1]][2]) %>%
-  select(-code, -ID)
-
-d_final <- cbind(subjects = rownames(d_all), d_all)  %>%
-  mutate(ID= paste('child_', subjects, sep="")) %>%
-  select(ID, gender, age, date)
-
-write.csv(d_final, file = "data_IRB_fourtassi.csv")
-
 ```
@@
   filter(condition != "obj_prac" & condition != "sound_prac") %>%
-  filter(problem == 'No')
+  filter(problem == 'No') %>%
+  mutate(scaled = (answer-1)/6)
 
@@
   group_by(condition, distance) %>%
-  summarise(mean = mean(answer),
-                   sd = sd(answer),
+  summarise(mean = mean(scaled),
+                   sd = sd(scaled),
                    n = n()) %>%
@@
 d_sim_transform <-  d_sim_summary %>%
-  mutate(scale1 = (mean-1)/6) %>%
-  mutate(myscale =ifelse(condition=='sound_real', scale1/0.926, scale1))
+  mutate(normalized =ifelse(condition=='sound_real', mean/0.926, mean)) %>% #Here I only normalize sounds, objects are already normalized
+  filter(distance != "iden") %>%
+  mutate(mydist = ifelse(distance=="0.6", 1, myscale))%>% # Here I create a ligne for different which were not explicitly asked from participants because it was used as a prototype, thus dist=1
+  mutate(labels = ifelse(distance=='0.1','similar', 
+                         ifelse(distance=='0.3','intermediate', 
+                                ifelse(distance=='sim','similar',
+                                       ifelse(distance=='med','intermediate', 'different')))))
 
@@
 
-ggplot(d_sim_summary, 
-      aes(x = distance, y = mean)) +
-  #geom_point()+
-  geom_pointrange(aes(ymin = lower, ymax = upper), 
-                 position = position_dodge(width = .1)) + 
+ggplot(d_sim_transform, 
+      aes(x = labels, y = mydist, col=condition)) +
+  geom_point()+
+  #geom_pointrange(aes(ymin = lower, ymax = upper), 
+     #            position = position_dodge(width = .1)) + 
   xlab("Distance") +ylab("rating")+
@@
       axis.text = element_text(size = 11)
-      ) + facet_grid(.~condition)
+      ) +
+  ylim(c(0,1.1))
 
@@
 
-#Maximal (does not converge)
+#Maximal random structure
 model_ch <- glmer(iscorrect ~ s_dist * c_dist + 
@@
 
-#1) Simplify random structure till the model converges
-
-#Drop interaction from random slope per subject (Stil does not converge)
-model1 <- glmer(iscorrect ~ s_dist * c_dist + 
-                 (s_dist + c_dist  | ID) + 
-                 (1 + c_dist| item_object) + 
-                 (1 + s_dist| item_sound), 
-               data = data_model, family = binomial())
-
-#Drop random slope per stimuli  (hooray! This one converges now)
-model2 <- glmer(iscorrect ~ s_dist * c_dist + 
-                 (s_dist + c_dist  | ID) + 
-                 (1 | item_object) + 
-                 (1 | item_sound), 
-               data = data_model, family = binomial(),
-              glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-model00 <- mixed(iscorrect ~ s_dist * c_dist + 
-                 (s_dist + c_dist  | ID) + 
-                 (1 | item_object) + 
-                 (1 | item_sound), 
-                 method = "LRT",
-               data = data_model, family = binomial(),
-              glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-#2) Use likelihood ration to prune fixed effects
-
-#drop interaction term from fixed effect (This works! less degrees of freedom and similar explanatory power)
-
-model3 <- glmer(iscorrect ~ s_dist + c_dist + 
-                 (s_dist + c_dist  | ID) + 
-                 (1 | item_object) + 
-                 (1 | item_sound), 
-               data = data_model, family = binomial())
-
-anova(model2, model5)
-
 ```
 
-```{r fig.width=2.5, fig.height=1.2}
-hi <- get_speaker_statistics()
-
-hello <- hi %>%
-  #filter(speaker_role=="Target_Child") %>%
-  mutate(age = round(target_child_age/12)) %>%
-  filter(age <11) %>%
-  mutate(role = ifelse(speaker_role=='Target_Child', 'child', 'adult')) %>%
-  group_by(age, role, target_child_sex) %>%
-  summarise(utt = sum(num_utterances)) %>%
-  filter(target_child_sex == 'male' | target_child_sex == 'female') %>%
-  rename(gender = target_child_sex) %>%
-  mutate(gender2 = ifelse(gender=='male', 'male children', 'female children'))
-
-ggplot(hello, 
-      aes(x = age, y = utt, col = factor(role))) +
-  geom_point()+
-  geom_line(aes(lty=factor(role))) + 
-  scale_x_continuous(breaks=c(1,2,3,4, 5, 6, 7,8,9, 10)) +
-  #scale_y_continuous(name="number of utterances", labels = scales::comma) +
-  scale_y_continuous(labels = scales::comma) +
-  xlab("Age (years)") +ylab("Number of utterances")+
-  guides(col=guide_legend(title="Speaker"), lty=guide_legend(title="Speaker"))+
-  facet_grid(.~gender2)
-
-  #geom_hline(yintercept = 0.50) +
-  #xlab("Aud distance") +ylab("% Accurate")+
-  #scale_colour_discrete(name="Vis Dist")+
-#theme(legend.title = element_text(size=8))
-
-hello <- hi %>%
-  #filter(speaker_role=="Target_Child") %>%
-  mutate(age = round(target_child_age/12)) %>%
-  filter(age <11) %>%
-  mutate(role = ifelse(speaker_role=='Target_Child', 'child', 'adult')) %>%
-  group_by(age, role, ) %>%
-  summarise(utt = sum(num_utterances)) #%>%
-  #filter(target_child_sex == 'male' | target_child_sex == 'female')
-
-```
-
-Simualte the probability space
+Use values of perceptual distance from the similarity judgement task
 
@@
 
-Now I need to predict accuracy as function of sound and meaning similarity 
+Now I need to predict accuracy as a function of sound and meaning similarity 
 ```{r}
@@
   o1 = 0
-  no_acc <- exp(-(s1-s)^2/(2*Vr)) + exp(-(o1-o)^2/(2*Vr))
-  acc <- 1 + exp(-((s1-s)^2+(o1-o)^2)/(2*Vr)) 
+  no_acc <- exp(-(s1-s)^2/(2*(Vr)^2)) + exp(-(o1-o)^2/(2*(Vr)^2))
+  acc <- 1 + exp(-((s1-s)^2+(o1-o)^2)/(2*(Vr)^2)) 
   acc_norm <- acc/(acc+no_acc)
@@
   o1 = 0
-  no_acc <- exp(-(s1-s)^2/(2*Vr_s)) + exp(-(o1-o)^2/(2*Vr_o))
-  acc <- 1 + exp(-((s1-s)^2/(2*Vr_s)+(o1-o)^2/(2*Vr_o))) 
+  no_acc <- exp(-(s1-s)^2/(2*(Vr_s)^2)) + exp(-(o1-o)^2/(2*(Vr_o)^2))
+  acc <- 1 + exp(-((s1-s)^2/(2*(Vr_s)^2)+(o1-o)^2/(2*(Vr_o)^2))) 
   acc_norm <- acc/(acc+no_acc)
@@
 
-fit_adults <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='adults'), start=list(Vr=0.01), lower=c(0), algorithm="port")
+fit_adults <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='adults'), start=list(Vr=0.1), lower=c(0), algorithm="port")
 
-fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.04, Vr_o=0.04), lower=c(0,0), algorithm="port")
+fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.1, Vr_o=0.04), lower=c(0,0), algorithm="port")
 
@@
 
-fit_children <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='children'), start=list(Vr=0.3), lower=c(0), algorithm="port")
+fit_children <- nls(mean ~ combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='children'), start=list(Vr=0.5), lower=c(0), algorithm="port")
 
-fit_children_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='children'), start=list(Vr_s=0.3, Vr_o=0.3), lower=c(0,0), algorithm="port")
+fit_children_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='children'), start=list(Vr_s=0.5, Vr_o=0.3), lower=c(0,0), algorithm="port")
 
@@
 Vr_o_ch <- coef(fit_children_2)[2]
+
+model1_val <- as.data.frame(confint2(fit_children)) %>%
+  mutate(val= Vr_ch, 
+         model=1, 
+         group = "children") %>%
+  bind_rows(as.data.frame(confint2(fit_adults)) %>%
+              mutate(val= Vr_ad, 
+                     model=1, 
+                     group = "adults"))
+
+model2_val <- add_rownames(as.data.frame(confint2(fit_children_2)), "param") %>%
+  mutate(val= ifelse(param=='Vr_s',Vr_s_ch, Vr_o_ch),
+         model=2, 
+         group = "children") %>%
+  bind_rows(add_rownames(as.data.frame(confint2(fit_adults_2)), "param") %>%
+              mutate(val= ifelse(param=='Vr_s',Vr_s_ad, Vr_o_ad),
+                     model=2, 
+                     group = "adults"))
+
+feather::write_feather(model1_val, "../saved_data/values_mod1.feather")       
+feather::write_feather(model2_val, "../saved_data/values_mod2.feather")
+
+model2_val <- c(confint(fit_children_2), Vr_s_ch, Vr_o_ch, model="2", group = "children") %>%
+  bind_rows(c(confint(fit_adults_2), Vr_s_ad, Vr_o_ad, model="2", group = "adults"))
 
@@
   rename(human = mean)
+
+feather::write_feather(model_data, "../saved_data/data_correlations.feather")
 
@@
 
-s = seq(-1,1.5,0.01)
+s = seq(-1,2.5,0.01)
 y = Gdist(0,1,x)
 
-illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), x.pos = "0", type='within') %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), x.pos = "0.5", type='within')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='within')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='within')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), x.pos = "0.5", type='between')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.3, s), x.pos = "1", variance='between'))
+illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Disambiguation') %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Disambiguation')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambiguation')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambiguation')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Development')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Development')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Development')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Development'))
 
-ggplot(illustration, aes(x=x, y=y, col=x.pos)) + 
+illustration$case <- factor(illustration$case, levels = c("low accuracy", "high accuracy"))
+illustration$type <- factor(illustration$type, levels = c("Disambiguation", "Development"))
+
+probs <- subset(subset(illustration, x==0)) %>%
+  group_by(type, case) %>%
+  mutate(prob = round(y/sum(y),2)) %>%
+  filter(rep=='1')
+
+ggplot(illustration, aes(x=x, y=y, linetype=rep)) + 
   geom_line() + 
@@
       axis.text = element_text(size = 11),
-      aspect.ratio = 0.7
+      strip.text = element_text(size = 11),
+      aspect.ratio = 0.5
       )+
@@
   #ylim(c(0,1))+
-  #geom_hline(yintercept = 0.50, linetype="dashed") +
-  xlab("position") + ylab("Prob") #+
-  #facet_grid(.~object_distance)
+  #geom_vline(xintercept = 0.0, color="red") +
+  #geom_segment(aes(x = 0, y = 0, xend = 0, yend = y, colour = rep),
+  #             position=position_dodge(width = .2), 
+   #            data = subset(illustration, x==0))+
+
+  geom_col(aes(x = x, y = y, fill = rep),
+               position=position_dodge(), 
+               width=0.2,
+               data = subset(illustration, x==0))+
+  geom_text(aes(label=paste("Acc=", prob, sep="")),
+            x=2, y=1, size=4, 
+            fontface = "bold",
+            data=probs)+
+  xlab("Perceptual space") + ylab("Prob") +
+  facet_grid(type~case) +
+  theme(legend.position="none")
 

### 2018-12-28 cogsci/cogsci.Rmd
new modif on manuscript

@@
 header-includes:
-   - \usepackage[subtle]{savetrees}
    - \usepackage{tipa}
@@
 
-Over the first year of life, children become sensitive to the phonetic variations that are used to distinguish meanings in their native language (Werker and Tees, 1984).
+Over the first year of life, children become sensitive to the phonetic variations that are used to distinguish meanings in their native language [@werker1984].
 One could imagine that these perceptual skills would be automatically applied to the task of word learning.
-However, developmental data show that 14 m.o children find it challenging to associate minimally different (but perceptually discriminated) sounds such as "bin" and "din" to different objects (Stager & Werker, 1997).
+However, developmental data show that 14 m.o children find it challenging to associate minimally different (but perceptually discriminated) sounds such as "bin" and "din" to different objects [@stager1997].
 
-Several factors can explain this pattern of results.
+Several factors can explain this finding.
 For example it is possible that the task of meaning learning increases cognitive demands on children (compared to a simple perceptual descrimination).
-In particular, it requires paying attention to both the sounds and the corresponding objects, which may hinder precise encoding in memory of some phonetic details (Stager a& Werker, 1997).
-Additional difficulty might arise from ambiguous phonological boundaries at this stage of development (e.g., Rost & McMurray, 2009), or from uncertainty about the referential status of the novel word (Fennell & Waxman, 2009).
+In particular, it requires paying attention to both the sounds and the corresponding objects, which may hinder precise encoding in memory of some phonetic details [@stager1997; @hofer2017].
+Additional difficulty might arise from ambiguous phonological boundaries at this stage of development [e.g., @rost2009], or from uncertainty about the referential status of the novel word [@fennell2010].
 
-Regardless of the exact explanation, it is generally accepted that by around 17 m.o, chidlren succeed under the same circumstances (Werker et al.
-2002).
+Regardless of the exact explanation, it is generally accepted that by around 17 m.o, chidlren succeed under the same circumstances [@werker2002].
 What could be the mechanism of development?
-Swingley contrasted a binary-discontinuous scenario to a probabilstic-continuous one.
-On the discontinuous account, younger children learn a single, underspecified representation of similar words (e.g., "bin"/"din").
+On one possible account, learning is stage-like: younger children learn a single, underspecified representation of similar words (e.g., "bin"/"din").
 Development occurs when children specify this intial coarse reprepsentation and learn two distinct catgories.
-On the continuous account, distinct represetations are successfully learned from the start, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks.
+On an other account, learning is continuous: distinct represetations are learned even by younger children, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks.
+Development is a continuous process whereby the intinial noisy representations become more precise [see also, @swingley2007].
 
-Experimental evidence suggest a probabilsitic-continuous, rather than a stage-like develomental scenario.
-On the one hand, 14-month-olds who typically fail in the original task succeed when learning is probed using a testing method with lower memory demands (Yoshida et al.
-1009), and when uncertainty in the emerging representations is mitigated using disambiguating contextual cues (Thiessen, 2007; Dautriche et al., 2016).
-On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases (Pajak et al., 2016; White et al., 2013).
+Experimental evidence suggest a probabilsitic/continuous, rather than a binary/discontinuous develomental scenario.
+On the one hand, 14-month-olds who typically fail in the original task succeed both when an easier testing method is used [@yoshida2009], and when uncertainty is mitigated via disambiguating cues [@thiessen2007; @dautriche2015].
+On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases [@white2013; @pajak2016].
 
-Following this experimental studies, the purpose of the current work is to propose a precise probabilsitc model of the Stager and Werker's task, and to explore the extent to which such a model could provide a unified accounts for several documented (as well as new) patterns of learning and development.
-We first present the model and explain how it can be used to make precise predictions of the target behavioral responses.
-Second, using new data collected from both preschool children and adults, we show how the probabilistic strucure of the model can explain behavioral patterns both within the same age and across development.
+In the light of these evidence, the purpose of the current work is to propose a precise probabilsitc model of the Stager and Werker's task where developmment is understood to proceed in a continuous fashion across the lifespan.
+We use this model to both provide a unifying account for documented experimental findings, and to make new predicitions that have not been tested before.
+Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.
 
-```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios.
-Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
-Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-"}
+<!-- The paper is organized as follows.
+First we present the model and explain how it can be used to make precise predictions about learning and development in the context of Stager and Werker's task.
+-->
+
+# Model
+
+## Task
+
+We model the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009.
+In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects.
+After this exposure phase, participants perform a series of two-alternative forced choices.
+In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
+An overview of the task is shown in Figure\ \@ref(fig:task).
+
+```{r task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:task}An overview of the task used in this study."}
 
@@
 ```
-
-# Model
-
-## Task
-
-We model a variant of the task used in Yoshida et al.
-2009.
-In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects.
-After this exposure phase, participants perform a series of two-alternative forced choices.
-In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
 
@@
 Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation.
-These variables are related in a way that refelects the simple generative scenario represented graphically in Figure XX.
+These variables are related in a way that refelects the simple generative scenario represented graphically in Figure\ \@ref(fig:model).
 When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind.
@@
 
-```{r model, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
-Circles indicate random variables (shading indicates observed variables).
-The squares indicates fixed model parameters."}
-
-img <- png::readPNG("figs/model.png")
-grid::grid.raster(img)
-
-```
-
 Because of the noisy nature of the representations, the observer can only determine the hidden variables (i.e., the concept $C$ and the label $L$) in a probabilistic fashion.
-For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectivel, are normally distributed:
+For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectively, are normally distributed:
 
@@
 $$
-## Predictions
 
-During the testing phase (see Figure 1), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and two possible objects $o_1$ and $o_2$.
-In order to make a choice, we determine which object is more probable under the lable $s_T$, in other words, we compare the the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$.
-The values of these probabilities can be computed by summing over all possible labels:
+## Simulations
+
+During the testing phase, participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and the two objects $o_1$ and $o_2$ presented during the learning phase.
+In order to make a choice, we determine which object is more probable under the target sound $s_T$, in other words, we compare the the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$.
+The values of these probabilities can be computed by summing over all possible concepts and labels:
 $$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
@@
 $$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
-Finally, assuming that the concept prior is a uniform ditribution, we obtain the following expression, where all conditional dependencies have been defined in the previous secton.
+Finally, assuming that the concept prior probability is uniformly ditributed, we obtain the following expression, where all conditional dependencies have been defined in the previous sub-section.
 
@@
 
-From the general expression (1) we were able to derive the exact analytical expression of the probability of correct responses in the testing phase of our simplified experimenal setting (Figure 1).
+From the general expression (1) we derive the exact analytical formula which expresses the probability of accurate responses in the testing phase (Figure 1).
 
@@
 
-We simulate the values of this probability as a function of the perceptual distance between the sounds $\Delta s$, using the two remining parameters of the model: the visual distance between the semantic referents $\Delta o$ and the values of the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
+```{r model, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
+Circles indicate random variables (shading indicates observed variables).
+The squares indicates fixed model parameters."}
+
+img <- png::readPNG("figs/model.png")
+grid::grid.raster(img)
+
+```
+
+We provide an intuitive illustration of how this probabilistic account explain patterns of learning and development in Figure XX.
+Low accuracy in word learning occurs when the perceptual distance between the labels is small relative to the uncertainty with wich these labels are encoded.
+For example, in Stager and Werker's orginal experiment, children are supposed to associate lable 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
+Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the lable "bih", thanks to the relatively large variance/tolerance of the encoding.
+
+Accuracy is high when the perceptual distance between the labels is large relative to the uncertainty of their encoding.
+Thus, improvement can occur in the same developmental stage if the perceptual distance of the labels is enhanced either through using different-sounding labels (e.g., "lif" vs.
+"neem" instead of "bih" and "dih") or through using additional disambiguating cues [e.g., @thiessen2007].
+Accuracy improves over development because the encoding's uncertainty itself is reduced.
+
+In order to have a more quantitative understanding of the mdoel, we simulate the values of the predicted accuracy (Expression 2) as a function of the perceptual distance between the sounds $\Delta s$.
+We used as parameters the two remaning variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
 The simulations are shown in Figure 3.
@@
 
-```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits."}
+```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the task of learning two similar-sounding words, as a function the perceptual distance between the sounds.
+Colors indicate different values of the standard deviation which we assume is common to both the label and concept probabilistic representations.
+Panels represent graphs using different values of the visual distance between the objects."}
 plot_simulation
@@
 1) For fixed values of $\Delta o$ and  $\sigma$, the probability of accurate responses increases as a function of $\Delta s$.
-This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren (Stager and Werker, 1997) and adults (Pajak et al.
-2016).
+This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren [@stager1997] and adults [@paja2016].
 
-2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the noise characterized with $\sigma$ decreases.
-This fact may explain development, i.e., youger children have noisier representations (Swingley, 2007; Yoshida et al.
-2009), which lead to lower word recognition accuracy, especially for similar sounding words.
+2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational noise (characterized with $\sigma$) decreases.
+This fact may explain development, i.e., youger children have noisier representations [@swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar sounding words.
 
-3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases when the visual distance between the semantic referents $\Delta o$ increases.
+3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases with the visual distance between the semantic referents $\Delta o$.
 This is a new predcition that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (see introduction), But no previous study tested the effect of the visual distance between the semantic referents.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (see review in the introduction), But no previous study tested the effect of the visual distance between the semantic referents.
 
-To sum, we introduced a model that accounts for some qualitative patterns observed in previous studies, and makes new predictions.
+To sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
 In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool chidlren and adults.
@@
 
-```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus}Graphical representation of our model.
-Circles indicate random variables (shading indicates observed variables).
-The squares indicates fixed model parameters."}
+```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of how a probabilsitic account (where distinct categories are encoded with different degrees of uncertainty) can explain patterns of learning and development.
+Accuracy experesses the extent to which a given sound instance indicates a unique category.
+The values vary between 0.5 (total overlap) and 1 (no overalp).
+Accuracy is low when the perceptual distance between labels is small relative to the category variance.
+Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development)."}
 
@@
 ### Stimuli and similarity rating
-The sound stimuli were generated using the MBROLA Speech Synthesizer (Dutoit et al., 1996).
+The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996].
 We generated three kinds of sound pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
@@
 In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and objcet pair on a 7-point scale.
-We used the average ratings across participants as qunatitaive measures of sound pairs' distance ($\Delta s$) and object pairs' distance ($\Delta o$).
+We computed averge ratings across partcipants, and we normalized the data so that the values vary between 0 to 1.
+Results are shown in Figure XX, for each stimuli group.
+This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).
+
+```{r}
+sim_transform <- feather::read_feather("../saved_data/d_sim_transform.feather")
+
+sim_plot <- ggplot(sim_transform, 
+      aes(x = labels, y = normalized_all, group = factor(stimuli), col=factor(stimuli))) +
+  geom_point(size=2)+
+  geom_line()+
+  #geom_pointrange(aes(ymin = lower, ymax = upper), 
+     #            position = position_dodge(width = .1)) + 
+  scale_colour_discrete(name="Stimuli")+
+  theme_few()+
+theme(legend.title = element_text(size=7.5),
+      legend.text=element_text(size=7.5),
+      axis.text = element_text(size = 7.5),
+      strip.text = element_text(size = 7.5),
+      axis.title = element_text(size = 7.5),
+      aspect.ratio = 0.7
+      ) +
+  ylim(c(0,1.1)) +
+  xlab("Stimuli group")+ ylab("Perceptual distance (experimental)")
+
+```
+
+```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:stim}Normalized distances for both sound and object pairs used in this study."}
+
+sim_plot
+```
 
@@
 #Import data from saved
-data_human_model <- feather::read_feather("../saved_data/data_human_model.feather")
+data_human_model <- feather::read_feather("../saved_data/data_human_model.feather") %>%
+  mutate(source = ifelse(key == "human", "Experimental",
+                         ifelse(key == "prediction", "Model 1", "Model 2")))
 
@@
       axis.text = element_text(size = 11)
-      ) + facet_grid(group~key, scales="free_y") +
+      ) + facet_grid(group~source, scales="free_y") +
   theme(aspect.ratio = 0.7)
@@
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits."}
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+Adults).
+Experimental results are shown on the left.
+Predictions from Model 1 (one free parameter) and Model 2 (two free parameters) are shown in the middle and on the right, respectively."}
 plot_data
@@
 
-First we analyzed the experimental results shown in Figure (XX, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture (Barr et al.
-2013).
+First we analyzed the experimental results shown in Figure (XX, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture [@barr2013].
 Results are shown in Table XX.
 We found a main effect of sound distance on the accuray of learning in both children and adults, thus replicating previous findings.
-We also found a main effect of object distance, thus confirming the new hypothesis derived from our model.
+We also found a main effect of object distance, thus confirming the new prediction of our model.
 
@@
 
+```{r}
+
+data_correlations <- feather::read_feather("../saved_data/data_correlations.feather")
+
+R2_model1 <-  round(cor(data_correlations$human, data_correlations$prediction)^2, 2)
+R2_model2 <-  round(cor(data_correlations$human, data_correlations$prediction_2)^2, 2)
+
+mod1_val <- feather::read_feather("../saved_data/values_mod1.feather") %>%
+  rename(lower =`2.5 %`,
+         upper = `97.5 %`)
+
+mod2_val <- feather::read_feather("../saved_data/values_mod2.feather") %>%
+  rename(lower =`2.5 %`,
+         upper = `97.5 %`)
+
+```
+
+Figures XX (middle and right graphs) show the predictions of the models.
+Both model 1 and model 2 fit reseanaby well the the experimental data in both children and adults.
+They both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
+
+For Model 1, we obtained a noise parameter of $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`] for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
+It explained the majority of the variance ($R^2=$ `r R2_model1`).
+For model 2, children had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
+Adults had a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`], and a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`].
+The model explain almost all the variance ($R^2=$ `r R2_model2`).
+
+# General Discussion
+
 \vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}

### 2018-12-28 cogsci/cogsci.tex
new modif on manuscript

@@
 
-\usepackage[subtle]{savetrees}
 \usepackage{tipa}
@@
 variations that are used to distinguish meanings in their native
-language (Werker and Tees, 1984). One could imagine that these
-perceptual skills would be automatically applied to the task of word
-learning. However, developmental data show that 14 m.o children find it
+language (Werker \& Tees, 1984). One could imagine that these perceptual
+skills would be automatically applied to the task of word learning.
+However, developmental data show that 14 m.o children find it
 challenging to associate minimally different (but perceptually
@@
 
-Several factors can explain this pattern of results. For example it is
-possible that the task of meaning learning increases cognitive demands
-on children (compared to a simple perceptual descrimination). In
+Several factors can explain this finding. For example it is possible
+that the task of meaning learning increases cognitive demands on
+children (compared to a simple perceptual descrimination). In
 particular, it requires paying attention to both the sounds and the
 corresponding objects, which may hinder precise encoding in memory of
-some phonetic details (Stager a\& Werker, 1997). Additional difficulty
-might arise from ambiguous phonological boundaries at this stage of
-development (e.g., Rost \& McMurray, 2009), or from uncertainty about
-the referential status of the novel word (Fennell \& Waxman, 2009).
+some phonetic details (Hofer \& Levy, 2017; Stager \& Werker, 1997).
+Additional difficulty might arise from ambiguous phonological boundaries
+at this stage of development (e.g., Rost \& McMurray, 2009), or from
+uncertainty about the referential status of the novel word (Fennell \&
+Waxman, 2010).
 
 Regardless of the exact explanation, it is generally accepted that by
-around 17 m.o, chidlren succeed under the same circumstances (Werker et
-al. 2002). What could be the mechanism of development? Swingley
-contrasted a binary-discontinuous scenario to a probabilstic-continuous
-one. On the discontinuous account, younger children learn a single,
-underspecified representation of similar words (e.g., ``bin''/``din'').
-Development occurs when children specify this intial coarse
-reprepsentation and learn two distinct catgories. On the continuous
-account, distinct represetations are successfully learned from the
-start, but these representations are encoded with higher uncertainty in
-youger children, leading to apparent failure in relatively demanding
-tasks.
+around 17 m.o, chidlren succeed under the same circumstances (Werker,
+Fennell, Corcoran, \& Stager, 2002). What could be the mechanism of
+development? On one possible account, learning is stage-like: younger
+children learn a single, underspecified representation of similar words
+(e.g., ``bin''/``din''). Development occurs when children specify this
+intial coarse reprepsentation and learn two distinct catgories. On an
+other account, learning is continuous: distinct represetations are
+learned even by younger children, but these representations are encoded
+with higher uncertainty in youger children, leading to apparent failure
+in relatively demanding tasks. Development is a continuous process
+whereby the intinial noisy representations become more precise (see
+also, Swingley, 2007).
 
-Experimental evidence suggest a probabilsitic-continuous, rather than a
-stage-like develomental scenario. On the one hand, 14-month-olds who
-typically fail in the original task succeed when learning is probed
-using a testing method with lower memory demands (Yoshida et al. 1009),
-and when uncertainty in the emerging representations is mitigated using
-disambiguating contextual cues (Thiessen, 2007; Dautriche et al., 2016).
-On the other hand, adults show patterns of learning similar to those
-shown by 14-month-olds when the task is more challenging and when
-similarity between words increases (Pajak et al., 2016; White et al.,
-2013).
+Experimental evidence suggest a probabilsitic/continuous, rather than a
+binary/discontinuous develomental scenario. On the one hand,
+14-month-olds who typically fail in the original task succeed both when
+an easier testing method is used (Yoshida, Fennell, Swingley, \& Werker,
+2009), and when uncertainty is mitigated via disambiguating cues
+(Dautriche, Swingley, \& Christophe, 2015; Thiessen, 2007). On the other
+hand, adults show patterns of learning similar to those shown by
+14-month-olds when the task is more challenging and when similarity
+between words increases (Pajak, Creel, \& Levy, 2016; White, Yee,
+Blumstein, \& Morgan, 2013).
 
-Following this experimental studies, the purpose of the current work is
-to propose a precise probabilsitc model of the Stager and Werker's task,
-and to explore the extent to which such a model could provide a unified
-accounts for several documented (as well as new) patterns of learning
-and development. We first present the model and explain how it can be
-used to make precise predictions of the target behavioral responses.
-Second, using new data collected from both preschool children and
-adults, we show how the probabilistic strucure of the model can explain
-behavioral patterns both within the same age and across development.
-
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/growth-1}
-
-}
-
-\caption{\label{fig:growth}Illustration of the growth scenarios.
-Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external).
-Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant.
-}\label{fig:growth}
-\end{figure}
-\end{CodeChunk}
+In the light of these evidence, the purpose of the current work is to
+propose a precise probabilsitc model of the Stager and Werker's task
+where developmment is understood to proceed in a continuous fashion
+across the lifespan. We use this model to both provide a unifying
+account for documented experimental findings, and to make new
+predicitions that have not been tested before. Using new data collected
+from both preschool children and adults, we show that the model can
+explain various patterns of learning both within the same age and across
+development.
 
@@
 
-We model a variant of the task used in Yoshida et al. 2009. In this
-task, particiants are first exposed to the association between pairs of
-nonesense words (e.g., ``lif''/``neem'') and pairs of objects. After
-this exposure phase, participants perform a series of two-alternative
-forced choices. In each testing trial, one of the two sounds is uttered
-(e.g., ``lif'') and participants choose the corresponding object from
-the two alternatives.
+We model the word learning task introduced by Stager \& Werker (1997),
+and a testing method similar to the one used by Yoshida et al. (2009).
+In this task, particiants are first exposed to the association between
+pairs of nonesense words (e.g., ``lif''/``neem'') and pairs of objects.
+After this exposure phase, participants perform a series of
+two-alternative forced choices. In each testing trial, one of the two
+sounds is uttered (e.g., ``lif'') and participants choose the
+corresponding object from the two alternatives. An overview of the task
+is shown in Figure~@ref(fig:task).
+
+\begin{CodeChunk}
+\begin{figure}[t]
+
+{\centering \includegraphics{figs/task-1}
+
+}
+
+\caption{\label{fig:task}An overview of the task used in this study.}\label{fig:task}
+\end{figure}
+\end{CodeChunk}
 
@@
 are related in a way that refelects the simple generative scenario
-represented graphically in Figure XX. When a speaker utters a sound in
-the presence of an object, the observer assumes that the object \(o\)
-activated the concept \(C\) in the speaker's mind. The concept prompted
-the cooresponding label \(L\). Finally, the label was physically
-instantiated by the sound \(s\).
+represented graphically in Figure~@ref(fig:model). When a speaker utters
+a sound in the presence of an object, the observer assumes that the
+object \(o\) activated the concept \(C\) in the speaker's mind. The
+concept prompted the cooresponding label \(L\). Finally, the label was
+physically instantiated by the sound \(s\).
+
+Because of the noisy nature of the representations, the observer can
+only determine the hidden variables (i.e., the concept \(C\) and the
+label \(L\)) in a probabilistic fashion. For simplicity, we assume that
+the probability of membership of objects and sounds to concepts and
+labels, respectively, are normally distributed:
+
+\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
+\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
+one-to-one mappings between concepts and labels, and that observers have
+successfully learned these mappings during the exposure phase: \[
+P(L_i|C_j) = 
+\begin{cases}
+  1 & \text{if  }  i=j \\  
+  0  & \text{if  }  i\neq j 
+\end{cases}
+\]
+
+\subsection{Simulations}\label{simulations}
+
+During the testing phase, participants are presented with one target
+sound \(s_T \in\{s_1, s_2\}\) and the two objects \(o_1\) and \(o_2\)
+presented during the learning phase. In order to make a choice, we
+determine which object is more probable under the target sound \(s_T\),
+in other words, we compare the the probabilities \(P(o_1|s_T)\) and
+\(P(o_2|s_T)\). The values of these probabilities can be computed by
+summing over all possible concepts and labels:
+\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
+The joint probability \(P(o, C, L, s)\) is obtained by factoring the
+bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
+which could be tansformed using Bayes rule into:
+
+\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
+concept prior probability is uniformly ditributed, we obtain the
+following expression, where all conditional dependencies have been
+defined in the previous sub-section.
+
+\begin{equation}
+P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
+\end{equation}
+
+From the general expression (1) we derive the exact analytical formula
+which expresses the probability of accurate responses in the testing
+phase (Figure 1).
+
+\begin{equation}
+P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
+\end{equation}
 
 \begin{CodeChunk}
-\begin{figure}[H]
+\begin{figure}[h]
 
@@
 
-Because of the noisy nature of the representations, the observer can
-only determine the hidden variables (i.e., the concept \(C\) and the
-label \(L\)) in a probabilistic fashion. For simplicity, we assume that
-the probability of membership of objects and sounds to concepts and
-labels, respectivel, are normally distributed:
+We provide an intuitive illustration of how this probabilistic account
+explain patterns of learning and development in Figure XX. Low accuracy
+in word learning occurs when the perceptual distance between the labels
+is small relative to the uncertainty with wich these labels are encoded.
+For example, in Stager and Werker's orginal experiment, children are
+supposed to associate lable 1 (``bih'') and label 2 (``dih'') with
+object 1 and object 2, respectively. Though children could learn that
+the label ``bih'' is a better match to object 1 than ``dih'', they could
+still judge the sound ``dih'' as a plausible instance of the lable
+``bih'', thanks to the relatively large variance/tolerance of the
+encoding.
 
-\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
-\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
-one-to-one mappings between concepts and labels, and that observers have
-successfully learned these mappings during the exposure phase: \[
-P(L_i|C_j) = 
-\begin{cases}
-  1 & \text{if  }  i=j \\  
-  0  & \text{if  }  i\neq j 
-\end{cases}
-\] \#\# Predictions
+Accuracy is high when the perceptual distance between the labels is
+large relative to the uncertainty of their encoding. Thus, improvement
+can occur in the same developmental stage if the perceptual distance of
+the labels is enhanced either through using different-sounding labels
+(e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or through
+using additional disambiguating cues (e.g., Thiessen, 2007). Accuracy
+improves over development because the encoding's uncertainty itself is
+reduced.
 
-During the testing phase (see Figure 1), participants are presented with
-one target sound \(s_T \in\{s_1, s_2\}\) and two possible objects
-\(o_1\) and \(o_2\). In order to make a choice, we determine which
-object is more probable under the lable \(s_T\), in other words, we
-compare the the probabilities \(P(o_1|s_T)\) and \(P(o_2|s_T)\). The
-values of these probabilities can be computed by summing over all
-possible labels:
-\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
-The joint probability \(P(o, C, L, s)\) is obtained by factoring the
-bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
-which could be tansformed using Bayes rule into:
-
-\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
-concept prior is a uniform ditribution, we obtain the following
-expression, where all conditional dependencies have been defined in the
-previous secton.
-
-\begin{equation}
-P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-\end{equation}
-
-From the general expression (1) we were able to derive the exact
-analytical expression of the probability of correct responses in the
-testing phase of our simplified experimenal setting (Figure 1).
-
-\begin{equation}
-P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
-\end{equation}
-
-We simulate the values of this probability as a function of the
-perceptual distance between the sounds \(\Delta s\), using the two
-remining parameters of the model: the visual distance between the
-semantic referents \(\Delta o\) and the values of the standard deviation
+In order to have a more quantitative understanding of the mdoel, we
+simulate the values of the predicted accuracy (Expression 2) as a
+function of the perceptual distance between the sounds \(\Delta s\). We
+used as parameters the two remaning variables, i.e., the visual distance
+between the semantic referents \(\Delta o\) and the standard deviation
 of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
@@
 
-\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits.}\label{fig:simulation}
+\caption{\label{fig:simulation}The predicted probability of accurate responses in the task of learning two similar-sounding words, as a function the perceptual distance between the sounds.
+Colors indicate different values of the standard deviation which we assume is common to both the label and concept probabilistic representations.
+Panels represent graphs using different values of the visual distance between the objects.}\label{fig:simulation}
 \end{figure*}
@@
   challenging to learn than different sounds for both chidlren (Stager
-  and Werker, 1997) and adults (Pajak et al. 2016).
+  \& Werker, 1997) and adults ({\textbf{???}}).
 \item
   For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
-  when the noise characterized with \(\sigma\) decreases. This fact may
-  explain development, i.e., youger children have noisier
-  representations (Swingley, 2007; Yoshida et al. 2009), which lead to
-  lower word recognition accuracy, especially for similar sounding
-  words.
+  when the representational noise (characterized with \(\sigma\))
+  decreases. This fact may explain development, i.e., youger children
+  have noisier representations (Swingley, 2007; Yoshida et al., 2009),
+  which leads to lower word recognition accuracy, especially for similar
+  sounding words.
 \item
   For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
-  when the visual distance between the semantic referents \(\Delta o\)
-  increases. This is a new predcition that our model makes. Previous
-  work studied the effect of several bottom-up and top-down properties
-  in disambiguating similar sounding words (see introduction), But no
-  previous study tested the effect of the visual distance between the
-  semantic referents.
+  with the visual distance between the semantic referents \(\Delta o\).
+  This is a new predcition that our model makes. Previous work studied
+  the effect of several bottom-up and top-down properties in
+  disambiguating similar sounding words (see review in the
+  introduction), But no previous study tested the effect of the visual
+  distance between the semantic referents.
 \end{enumerate}
@@
 To sum, we introduced a model that accounts for some qualitative
-patterns observed in previous studies, and makes new predictions. In the
-experiment below, we test whether the model makes accurate
-\emph{quantitative} predictions by fitting it to new experimental data
-collected from preschool chidlren and adults.
+learning patterns observed in previous studies, and makes a new
+prediction. In the experiment below, we test whether the model makes
+accurate \emph{quantitative} predictions by fitting it to new
+experimental data collected from preschool chidlren and adults.
 
@@
 
-\caption{\label{fig:illus}Graphical representation of our model.
-Circles indicate random variables (shading indicates observed variables).
-The squares indicates fixed model parameters.}\label{fig:illus}
+\caption{\label{fig:illus} An illustration of how a probabilsitic account (where distinct categories are encoded with different degrees of uncertainty) can explain patterns of learning and development.
+Accuracy experesses the extent to which a given sound instance indicates a unique category.
+The values vary between 0.5 (total overlap) and 1 (no overalp).
+Accuracy is low when the perceptual distance between labels is small relative to the category variance.
+Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
 \end{figure}
@@
 The sound stimuli were generated using the MBROLA Speech Synthesizer
-(Dutoit et al., 1996). We generated three kinds of sound pairs which
-varied in their degree of similarity to English speakers: 1)
-``different'': ``lif''/``neem'' and ``zem''/``doof'', 2)
-``intermediate'': ``aka''/``ama'' and ``ada''/``aba'', and 3)
-``similar'' non-English minimal pairs: ``ada''/``a\textipa{d\super h}a''
-(in hindi) and ``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).
+(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
+generated three kinds of sound pairs which varied in their degree of
+similarity to English speakers: 1) ``different'': ``lif''/``neem'' and
+``zem''/``doof'', 2) ``intermediate'': ``aka''/``ama'' and
+``ada''/``aba'', and 3) ``similar'' non-English minimal pairs:
+``ada''/``a\textipa{d\super h}a'' (in hindi) and
+``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).
 
@@
 Mechanical Turk evaluated the similarity of each sound and objcet pair
-on a 7-point scale. We used the average ratings across participants as
-qunatitaive measures of sound pairs' distance (\(\Delta s\)) and object
-pairs' distance (\(\Delta o\)).
+on a 7-point scale. We computed averge ratings across partcipants, and
+we normalized the data so that the values vary between 0 to 1. Results
+are shown in Figure XX, for each stimuli group. This data will be used
+in the models as the perceptual distance of sound pairs (\(\Delta s\))
+and object pairs (\(\Delta o\)).
+
+\begin{CodeChunk}
+\begin{figure}[h]
+
+{\centering \includegraphics{figs/stim-1}
+
+}
+
+\caption{\label{fig:stim}Normalized distances for both sound and object pairs used in this study.}\label{fig:stim}
+\end{figure}
+\end{CodeChunk}
 
@@
 
-\caption{\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network.
-Results are shown in each language for phonological and semantic networks.
-Each point is a word, with lines indicating linear model fits.}\label{fig:all_data}
+\caption{\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+Adults).
+Experimental results are shown on the left.
+Predictions from Model 1 (one free parameter) and Model 2 (two free parameters) are shown in the middle and on the right, respectively.}\label{fig:all_data}
 \end{figure*}
@@
 distances as fixed effects, and with a maximal random effects strcuture
-(Barr et al. 2013). Results are shown in Table XX. We found a main
-effect of sound distance on the accuray of learning in both children and
-adults, thus replicating previous findings. We also found a main effect
-of object distance, thus confirming the new hypothesis derived from our
-model.
+(Barr, Levy, Scheepers, \& Tily, 2013). Results are shown in Table XX.
+We found a main effect of sound distance on the accuray of learning in
+both children and adults, thus replicating previous findings. We also
+found a main effect of object distance, thus confirming the new
+prediction of our model.
 
@@
 
+Figures XX (middle and right graphs) show the predictions of the models.
+Both model 1 and model 2 fit reseanaby well the the experimental data in
+both children and adults. They both correcly predict the relative
+recognition accuacy accross conditions: the pair of words that differ on
+both the object and sound levels were the easiest to learn, followed by
+the pairs of words that differ on only one level, then the pair of words
+that are similar on both levels.
+
+For Model 1, we obtained a noise parameter of \(\sigma =\) 0.63 {[}0.53,
+0.73{]} for preschoolers, and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for
+adults. It explained the majority of the variance (\(R^2=\) 0.94). For
+model 2, children had a sound specific noise of \(\sigma_S =\) 0.9
+{[}0.68, 1.11{]}, and a concept specific noise of \(\sigma_C =\) 0.29
+{[}0.1, 0.49{]}. Adults had a concept specific noise of \(\sigma_C =\)
+0.14 {[}0.05, 0.23{]}, and a sound specific noise of \(\sigma_S =\) 0.16
+{[}0.05, 0.28{]}. The model explain almost all the variance (\(R^2=\)
+0.96).
+
+\section{General Discussion}\label{general-discussion}
+
 \vspace{1em}
@@
 
+\hypertarget{refs}{}
+\hypertarget{ref-barr2013}{}
+Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects
+structure for confirmatory hypothesis testing: Keep it maximal.
+\emph{Journal of Memory and Language}, \emph{68}(3).
+
+\hypertarget{ref-dautriche2015}{}
+Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
+phonological neighbors: Syntactic category matters. \emph{Cognition},
+\emph{143}.
+
+\hypertarget{ref-dutoit1996}{}
+Dutoit, T., Pagel, V., Pierret, N., Bataille, F., \& Van der Vrecken, O.
+(1996). The mbrola project: Towards a set of high quality speech
+synthesizers free of use for non commercial purposes. In
+\emph{Proceedings of ICSLP} (Vol. 3). IEEE.
+
+\hypertarget{ref-fennell2010}{}
+Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow
+for infant use of phonetic detail in word learning. \emph{Child
+Development}, \emph{81}.
+
+\hypertarget{ref-hofer2017}{}
+Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken
+Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the
+Cognitive Science Society}.
+
+\hypertarget{ref-pajak2016}{}
+Pajak, B., Creel, S., \& Levy, R. (2016). Difficulty in learning
+similar-sounding words: A developmental stage or a general property of
+learning? \emph{Journal of Experimental Psychology: Learning, Memory,
+and Cognition}, \emph{42}(9).
+
+\hypertarget{ref-rost2009}{}
+Rost, G. C., \& McMurray, B. (2009). Speaker variability augments
+phonological processing in early word learning. \emph{Developmental
+Science}, \emph{12}.
+
+\hypertarget{ref-stager1997}{}
+Stager, C., \& Werker, J. (1997). Infants listen for more phonetic
+detail in speech perception than in word-learning tasks. \emph{Nature},
+\emph{388}(6640).
+
+\hypertarget{ref-swingley2007}{}
+Swingley, D. (2007). Lexical exposure and word-form encoding in
+1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2).
+
+\hypertarget{ref-thiessen2007}{}
+Thiessen, E. (2007). The effect of distributional information on
+children's use of phonemic contrasts. \emph{Journal of Memory and
+Language}, \emph{56}.
+
+\hypertarget{ref-werker1984}{}
+Werker, J., \& Tees, R. (1984). Cross-language speech perception:
+Evidence for perceptual reorganization during the first year of life.
+\emph{Infant Behavior and Development}, \emph{7}.
+
+\hypertarget{ref-werker2002}{}
+Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants'
+ability to learn phonetically similar words: Effects of age and
+vocabulary size. \emph{Infancy}, \emph{3}.
+
+\hypertarget{ref-white2013}{}
+White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show
+less sensitivity to phonetic detail in unfamiliar words, too.
+\emph{Journal of Memory and Language}, \emph{68}(4).
+
+\hypertarget{ref-yoshida2009}{}
+Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009).
+14-month-olds learn similar-sounding words. \emph{Developmental
+Science}, \emph{12}.
+
 \end{document}

### 2019-01-02 Analysis/process.Rmd
new modif on manuscript

@@
   filter(distance != "iden") %>%
-  mutate(mydist = ifelse(distance=="0.6", 1, myscale))%>% # Here I create a ligne for different which were not explicitly asked from participants because it was used as a prototype, thus dist=1
+  mutate(stimuli = ifelse(condition =='obj_real','objects','sounds')) %>%
+  mutate(normalized_all = ifelse(distance=="0.6", 1, normalized))%>% # Here I create a ligne for "different", which were not explicitly asked from participants because it was used as a prototype, thus dist=1
   mutate(labels = ifelse(distance=='0.1','similar', 
@@
 
-#d_sim_summary$distance <- factor(sum_child$concept_dist, levels = c("similar", "different"))
+d_sim_transform$labels <- factor(d_sim_transform$labels, levels = c("similar","intermediate","different"))
 #sum_child$sound_dist <- factor(sum_child$sound_dist, levels = c("similar", "different"))
 
+feather::write_feather(d_sim_transform, "../saved_data/d_sim_transform.feather")
+
 ggplot(d_sim_transform, 
-      aes(x = labels, y = mydist, col=condition)) +
-  geom_point()+
+      aes(x = labels, y = normalized_all, group = factor(stimuli), col=factor(stimuli))) +
+  geom_point(size=2)+
+  geom_line()+
   #geom_pointrange(aes(ymin = lower, ymax = upper), 
      #            position = position_dodge(width = .1)) + 
-  xlab("Distance") +ylab("rating")+
+  scale_colour_discrete(name="Stimuli")+
   theme_few()+
@@
       legend.text=element_text(size=11),
-      axis.text = element_text(size = 11)
+      axis.text = element_text(size = 11),
+      aspect.ratio = 0.7
       ) +
-  ylim(c(0,1.1))
+  ylim(c(0,1.1)) +
+  xlab("Stimuli group")+ ylab("Perceptual distance (experimental)")
 

### 2019-01-02 cogsci/cogsci.Rmd
new modif on manuscript

@@
 
-    "Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions.
-Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.
-One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words.
-Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon.
-The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages.
-We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically.
-The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."
+    "Stager and Werker (1997) first showed that chidlren's early ability to distinguish similar sounds do not automatically translate into word learning skills.
+Early explanations proposed that children may not be able to encode subtile phonetic contrasts when learning novel word meanings, thus suggesting a binary/discontinuous pattern of development.
+However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a rather probabilitic/continuous pattern of development.
+The present study proposes a precise probabisitic model describing how development may processd in a continuous fashion.
+The purpose of the model is to account for previousely documented facts while providing new predictions.
+We collected data from both preschool children and adults, and we show that the model can explain various patterns of learning both within the same age and across development.
+More generally, our work highlight the role of computational modeling in advancing our understanding of development through both organizing exsinting knowledge and generating new principled hypotheses."
 
 keywords:
-    "semantic network, phonological network, network growth, mechanism of word learning"
+    "word learning, cogniive development, computational modeling"
 
@@
 
+Here talk about the continuous hypothesis a bit later here. after introducing the experimental evidecne.
+
+Also talk more about the major assumption of model, what is contiuous about him? and what is the source of this hypothsis (swingley, Yoshida, ...)
+
 In the light of these evidence, the purpose of the current work is to propose a precise probabilsitc model of the Stager and Werker's task where developmment is understood to proceed in a continuous fashion across the lifespan.
@@
 
-Because of the noisy nature of the representations, the observer can only determine the hidden variables (i.e., the concept $C$ and the label $L$) in a probabilistic fashion.
+A similar probabilsitic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning.
+However, the first study assumed that the sounds are heard unambiguousely, and the second assumed the concepts are observed unambiguously.
+In our model, we made the more reaistic assumption of ambiguity at the level of both the sounds and the objects.
 For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectively, are normally distributed:
@@
 1) For fixed values of $\Delta o$ and  $\sigma$, the probability of accurate responses increases as a function of $\Delta s$.
-This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren [@stager1997] and adults [@paja2016].
+This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren [@stager1997] and adults [@pajak2016].
 
@@
 This is a new predcition that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (see review in the introduction), But no previous study tested the effect of the visual distance between the semantic referents.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [@rost2009; @thiessen2007; @dautriche2015; @fennell2010], but no previous study tested the effect of the visual distance between the semantic referents.
 
@@
 Figures XX (middle and right graphs) show the predictions of the models.
-Both model 1 and model 2 fit reseanaby well the the experimental data in both children and adults.
-They both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
+Both model 1 and model 2 fit reseanaby well the experimental data in both children and adults.
+In particular, they both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
 
-For Model 1, we obtained a noise parameter of $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`] for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
+For Model 1, the fitted noise parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`] for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
 It explained the majority of the variance ($R^2=$ `r R2_model1`).
 For model 2, children had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
-Adults had a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`], and a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`].
-The model explain almost all the variance ($R^2=$ `r R2_model2`).
+Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`].
+The model explain almost all the variance ($R^2=$ `r R2_model2`), and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
+Note that, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 which used two degrees of freedom.
 
 # General Discussion
+
+Here maybe be more precise about what the model does (providing a summary in prose of the main results )
+
+Subsequent studies have shown that   To account for this phenomenon, we proposed a model where words and their semantic referents are both encoded in a probabilistic fashion.
+A pair of words may be encoded simultaneousely, but successful recognition depends both on the perceptual distance between the words and on the degree of uncertainty of their encoding.
+These predictions explained learning patterns both within and across developmental stages, respectively.
+
+Besides accounting for previous findings, our model made a new prediction: learning similar words is not only modulated by to similarity of their phonological forms, but also by the visual similarity of their semantic referents.
+More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggest that children may prioritize the acqusition of words that are quite distant in the semantic space.
+This suggestion is supported by recent findings based on the investigation of early vocabulary growth [@engelthaler2017; @sizemore2018].
+That said, further work is needed to explore the effect on word learning of other semantic dimensions that could be encoded by children (e.g., conceptual/functional features).
+
+<!--Not only does our model predict that both phonological and semantic relatedness matter in learning novel words, it also provides
+a precise account of *how* these two dimensions interact to predict learning. In fact,-->
+Our model can be seen as an ideal observer [@anderson1990] in the sense that it provides a precise charaterization of the task, and shows how information can used optimally to perform this task.
+In our case, the input is categorized with uncertainty, thus the model performs an optimal probabilistic (Bayesian) inference, combining cues from both the sound and the semantic referents.
+Crucially, we assume the degree of this uncertainty to vary across development.
+Thus, although children and adults appear to behave differently, they are both near-optimal with resprect to their own encoding's uncertainty.
+Note that our model is agnostic as to the precise source of this uncertainty: part of it maybe due to ambiguous phonological boundaries [@rost], and another part could be due to various task demands [@hofer].
+
+To conclude, this study proposed a model of novel word is compatible with the hypothesis according to which development is not so much about a qualitative cognitive change as much as it is about the quantitative refinement of similar skills acrss the lifespan [@yoshida2009; @swingley2007; @pajak2016].
+
+<!--Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [@rost2009; @thiessen2007; @dautriche2015; @fennell2010], But our study is, to our knowledge, the first to test the effect of the visual distance between the semantic referents.
+-->
+
+<!--In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).
+
+That said, previous experimental work has studied the effect of phonological and semantic similarity separately.
+Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).
+However, children  acquire a lexicon which is more richly structured than these special cases.
+In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains.
+Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.
+
+One could imagine two learning scenarios.
+On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al.
+1975).
+For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity.
+Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms.
+On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002).
+Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension.
+In this study, we explore these hypothesis, bla bla -->
+
+Discuss Hofer & Levy, 2017, and Fourtassi & Frank, 2017
 

### 2019-01-02 cogsci/cogsci.tex
new modif on manuscript

@@
 \begin{abstract}
-Children tend to produce words earlier when they are connected to a
-variety of other words along both the phonological and semantic
-dimensions. Though this connectivity effect has been extensively
-documented, little is known about the underlying developmental
-mechanism. One view suggests that learning is primarily driven by a
-network growth model where highly connected words in the child's early
-lexicon attract similar words. Another view suggests that learning is
-driven by highly connected words in the external learning environment
-instead of highly connected words in the early internal lexicon. The
-present study tests both scenarios systematically in both the
-phonological and semantic domains, and across 8 languages. We show that
-external connectivity in the learning environment drives growth in both
-the semantic and the phonological networks, and that this pattern is
-consistent cross-linguistically. The findings suggest a word learning
-mechanism where children harness their statistical learning abilities to
-(indirectly) detect and learn highly connected words in the learning
-environment.
+Stager and Werker (1997) first showed that chidlren's early ability to
+distinguish similar sounds do not automatically translate into word
+learning skills. Early explanations proposed that children may not be
+able to encode subtile phonetic contrasts when learning novel word
+meanings, thus suggesting a binary/discontinuous pattern of development.
+However, later work has revealed (e.g., through using simpler testing
+methods) that children do encode such contrasts, thus favoring a rather
+probabilitic/continuous pattern of development. The present study
+proposes a precise probabisitic model describing how development may
+processd in a continuous fashion. The purpose of the model is to account
+for previousely documented facts while providing new predictions. We
+collected data from both preschool children and adults, and we show that
+the model can explain various patterns of learning both within the same
+age and across development. More generally, our work highlight the role
+of computational modeling in advancing our understanding of development
+through both organizing exsinting knowledge and generating new
+principled hypotheses.
 
 \textbf{Keywords:}
-semantic network, phonological network, network growth, mechanism of
-word learning
+word learning, cogniive development, computational modeling
 \end{abstract}
@@
 
+Here talk about the continuous hypothesis a bit later here. after
+introducing the experimental evidecne.
+
+Also talk more about the major assumption of model, what is contiuous
+about him? and what is the source of this hypothsis (swingley, Yoshida,
+\ldots{})
+
 In the light of these evidence, the purpose of the current work is to
@@
 
-Because of the noisy nature of the representations, the observer can
-only determine the hidden variables (i.e., the concept \(C\) and the
-label \(L\)) in a probabilistic fashion. For simplicity, we assume that
-the probability of membership of objects and sounds to concepts and
-labels, respectively, are normally distributed:
+A similar probabilsitic structure was used by Lewis \& Frank (2013) to
+model concept learning, and by Hofer \& Levy (2017) to model spoken word
+learning. However, the first study assumed that the sounds are heard
+unambiguousely, and the second assumed the concepts are observed
+unambiguously. In our model, we made the more reaistic assumption of
+ambiguity at the level of both the sounds and the objects. For
+simplicity, we assume that the probability of membership of objects and
+sounds to concepts and labels, respectively, are normally distributed:
 
@@
   challenging to learn than different sounds for both chidlren (Stager
-  \& Werker, 1997) and adults ({\textbf{???}}).
+  \& Werker, 1997) and adults (Pajak et al., 2016).
 \item
@@
   the effect of several bottom-up and top-down properties in
-  disambiguating similar sounding words (see review in the
-  introduction), But no previous study tested the effect of the visual
-  distance between the semantic referents.
+  disambiguating similar sounding words (Dautriche et al., 2015; Fennell
+  \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007), but no
+  previous study tested the effect of the visual distance between the
+  semantic referents.
 \end{enumerate}
@@
 Figures XX (middle and right graphs) show the predictions of the models.
-Both model 1 and model 2 fit reseanaby well the the experimental data in
-both children and adults. They both correcly predict the relative
-recognition accuacy accross conditions: the pair of words that differ on
-both the object and sound levels were the easiest to learn, followed by
-the pairs of words that differ on only one level, then the pair of words
-that are similar on both levels.
+Both model 1 and model 2 fit reseanaby well the experimental data in
+both children and adults. In particular, they both correcly predict the
+relative recognition accuacy accross conditions: the pair of words that
+differ on both the object and sound levels were the easiest to learn,
+followed by the pairs of words that differ on only one level, then the
+pair of words that are similar on both levels.
 
-For Model 1, we obtained a noise parameter of \(\sigma =\) 0.63 {[}0.53,
+For Model 1, the fitted noise parameter was \(\sigma =\) 0.63 {[}0.53,
 0.73{]} for preschoolers, and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for
@@
 {[}0.68, 1.11{]}, and a concept specific noise of \(\sigma_C =\) 0.29
-{[}0.1, 0.49{]}. Adults had a concept specific noise of \(\sigma_C =\)
-0.14 {[}0.05, 0.23{]}, and a sound specific noise of \(\sigma_S =\) 0.16
-{[}0.05, 0.28{]}. The model explain almost all the variance (\(R^2=\)
-0.96).
+{[}0.1, 0.49{]}. Adults had a sound specific noise of \(\sigma_S =\)
+0.16 {[}0.05, 0.28{]}. The model explain almost all the variance
+(\(R^2=\) 0.96), and a concept specific noise of \(\sigma_C =\) 0.14
+{[}0.05, 0.23{]}. Note that, despite the fact that Model 1 used only one
+degree of freedom, it captures the data variance almost as well as Model
+2 which used two degrees of freedom.
 
 \section{General Discussion}\label{general-discussion}
+
+Here maybe be more precise about what the model does (providing a
+summary in prose of the main results )
+
+Subsequent studies have shown that To account for this phenomenon, we
+proposed a model where words and their semantic referents are both
+encoded in a probabilistic fashion. A pair of words may be encoded
+simultaneousely, but successful recognition depends both on the
+perceptual distance between the words and on the degree of uncertainty
+of their encoding. These predictions explained learning patterns both
+within and across developmental stages, respectively.
+
+Besides accounting for previous findings, our model made a new
+prediction: learning similar words is not only modulated by to
+similarity of their phonological forms, but also by the visual
+similarity of their semantic referents. More generally, since visual
+similarity is an early organizing feature in the semantic domain (e.g.,
+Wojcik \& Saffran, 2013), our finding suggest that children may
+prioritize the acqusition of words that are quite distant in the
+semantic space. This suggestion is supported by recent findings based on
+the investigation of early vocabulary growth (Engelthaler \& Hills,
+2017; Sizemore, Karuza, Giusti, \& Bassett, 2018). That said, further
+work is needed to explore the effect on word learning of other semantic
+dimensions that could be encoded by children (e.g.,
+conceptual/functional features).
+
+Our model can be seen as an ideal observer (Anderson, 1990) in the sense
+that it provides a precise charaterization of the task, and shows how
+information can used optimally to perform this task. In our case, the
+input is categorized with uncertainty, thus the model performs an
+optimal probabilistic (Bayesian) inference, combining cues from both the
+sound and the semantic referents. Crucially, we assume the degree of
+this uncertainty to vary across development. Thus, although children and
+adults appear to behave differently, they are both near-optimal with
+resprect to their own encoding's uncertainty. Note that our model is
+agnostic as to the precise source of this uncertainty: part of it maybe
+due to ambiguous phonological boundaries ({\textbf{???}}), and another
+part could be due to various task demands ({\textbf{???}}).
+
+To conclude, this study proposed a model of novel word is compatible
+with the hypothesis according to which development is not so much about
+a qualitative cognitive change as much as it is about the quantitative
+refinement of similar skills acrss the lifespan (Pajak et al., 2016;
+Swingley, 2007; Yoshida et al., 2009).
+
+Discuss Hofer \& Levy, 2017, and Fourtassi \& Frank, 2017
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-anderson1990}{}
+Anderson, J. R. (1990). \emph{The adaptive character of thought}.
+Hillsdale, NJ: Erlbaum.
+
 \hypertarget{ref-barr2013}{}
@@
 
+\hypertarget{ref-engelthaler2017}{}
+Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word
+learning: Network distinctiveness predicts age of acquisition.
+\emph{Cognitive Science}, \emph{41}.
+
 \hypertarget{ref-fennell2010}{}
@@
 Cognitive Science Society}.
+
+\hypertarget{ref-lewis2013}{}
+Lewis, M., \& Frank, M. (2013). An integrated model of concept learning
+and word-concept mapping. In \emph{Proceedings of the annual meeting of
+the cognitive science society} (Vol. 35).
 
@@
 Science}, \emph{12}.
+
+\hypertarget{ref-sizemore2018}{}
+Sizemore, A. E., Karuza, E. A., Giusti, C., \& Bassett, D. S. (2018).
+Knowledge gaps in the early growth of semantic feature networks.
+\emph{Nature Human Behaviour}, \emph{2}(9).
 
@@
 
+\hypertarget{ref-wojcik2013}{}
+Wojcik, E., \& Saffran, J. (2013). The ontogeny of lexical networks:
+Toddlers encode the relationships among referents when learning novel
+words. \emph{Psychological Science}, \emph{24}(10).
+
 \hypertarget{ref-yoshida2009}{}

### 2019-01-09 cogsci/cogsci.Rmd
new modif on manuscript

@@
     "Stager and Werker (1997) first showed that chidlren's early ability to distinguish similar sounds do not automatically translate into word learning skills.
-Early explanations proposed that children may not be able to encode subtile phonetic contrasts when learning novel word meanings, thus suggesting a binary/discontinuous pattern of development.
-However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a rather probabilitic/continuous pattern of development.
+Early explanations proposed that children may not be able to encode subtile phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development.
+However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a rather a continuous pattern of development.
 The present study proposes a precise probabisitic model describing how development may processd in a continuous fashion.
@@
 We collected data from both preschool children and adults, and we show that the model can explain various patterns of learning both within the same age and across development.
-More generally, our work highlight the role of computational modeling in advancing our understanding of development through both organizing exsinting knowledge and generating new principled hypotheses."
+Our work highlight the role of computational modeling in advancing our understanding of development through both organizing exsinting knowledge and generating new principled hypotheses."
 
@@
 
-Regardless of the exact explanation, it is generally accepted that by around 17 m.o, chidlren succeed under the same circumstances [@werker2002].
+Regardless of the exact explanation, it is generally accepted that by around 17 m.o, children succeed in the same task [@werker2002].
 What could be the mechanism of development?
-On one possible account, learning is stage-like: younger children learn a single, underspecified representation of similar words (e.g., "bin"/"din").
-Development occurs when children specify this intial coarse reprepsentation and learn two distinct catgories.
-On an other account, learning is continuous: distinct represetations are learned even by younger children, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks.
-Development is a continuous process whereby the intinial noisy representations become more precise [see also, @swingley2007].
+Early acccounts assumed–whether implcitly or explicitly– that children encode words in a binary way: they either fail or succeed in encoding the relevant phonetic details (simulataneousely with the meanings).
+This account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.
 
-Experimental evidence suggest a probabilsitic/continuous, rather than a binary/discontinuous develomental scenario.
-On the one hand, 14-month-olds who typically fail in the original task succeed both when an easier testing method is used [@yoshida2009], and when uncertainty is mitigated via disambiguating cues [@thiessen2007; @dautriche2015].
+Nevertheless, subsequent findings suggest otherwise.
+On the one hand, 14-month-olds–who typically fail in the original task–succeed when an easier *testing* method is used, even under the same *learning* conditions [@yoshida2009].
+They also succeed when uncertainty is mitigated via disambiguating cues [e.g., @thiessen2007].
 On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases [@white2013; @pajak2016].
 
-Here talk about the continuous hypothesis a bit later here. after introducing the experimental evidecne.
+These evidence point towards another scenario, where the representations are encoded in a probablistic (rather than binary) way, and where development is continuous, rather than stage-like [@swingley2007; @yoshida2009; @pajak2016; @hofer2017].
+On this account, correct represetations are learned early in development, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks.
+Development is a continuous process whereby the intinial noisy representations become more precise.
+Crucially, more precise representation are still imperfect, as low accuracy learning can be obtained even with adults when the sounds are subtle enough, e.g., non-native sounds [@pajak2016].
 
-Also talk more about the major assumption of model, what is contiuous about him? and what is the source of this hypothsis (swingley, Yoshida, ...)
+We provide an intuitive illustration of how such an account explains patterns of learning and development in Figure \ref{fig:illus}.
+We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty/tolerance with wich these labels are encoded.
+For example, in Stager and Werker's orginal experiment, children are supposed to associate lable 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
+Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the lable "bih", thanks to the relatively large tolerance of the encoding.
 
-In the light of these evidence, the purpose of the current work is to propose a precise probabilsitc model of the Stager and Werker's task where developmment is understood to proceed in a continuous fashion across the lifespan.
-We use this model to both provide a unifying account for documented experimental findings, and to make new predicitions that have not been tested before.
+Accuracy in word learning increases when the perceived distance between the labels is large relative to the tolerance of their encoding.
+This improvement can occur in the same developmental stage if the perceptual distance between labels is enhanced through using different-sounding labels (e.g., "lif" vs.
+"neem" instead of "bih" and "dih") or through using contextual cues [@thiessen2007; @rost2009].
+Besides, accuracy can improve across development through the refinement of the encoding, i.e., if the uncertainy of the encoding decreases.
+
+Building on this intuition, the current work proposes a precise probabilsitc model, which we use to both account for previous experimental findings, and to make new predicitions that have not been tested before.
 Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.
-
-<!-- The paper is organized as follows.
-First we present the model and explain how it can be used to make precise predictions about learning and development in the context of Stager and Werker's task.
--->
-
-# Model
-
-## Task
-
-We model the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009.
-In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects.
-After this exposure phase, participants perform a series of two-alternative forced choices.
-In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
-An overview of the task is shown in Figure\ \@ref(fig:task).
-
-```{r task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:task}An overview of the task used in this study."}
-
-img <- png::readPNG("figs/task.png")
-grid::grid.raster(img)
-
-```
-
-<!--In previous studies, only the similarity of the sounds was varied across conditions (e.g., "bin"/"din" vs.
-"lif"/"neem").
-In our task, we also vary the visual similarity of the objects, which allows us to explore the effect of additional probabilistic cues on novel word learning and recognition.
-An overview of the task is presented in Figure XX.
--->
-
-## Probabilistic strcuture
-
-Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation.
-These variables are related in a way that refelects the simple generative scenario represented graphically in Figure\ \@ref(fig:model).
-When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind.
-The concept prompted the cooresponding label $L$.
-Finally, the label was physically instantiated by the sound $s$.
-
-A similar probabilsitic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning.
-However, the first study assumed that the sounds are heard unambiguousely, and the second assumed the concepts are observed unambiguously.
-In our model, we made the more reaistic assumption of ambiguity at the level of both the sounds and the objects.
-For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectively, are normally distributed:
-
-$$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
-$$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
-We assume there to be one-to-one mappings between concepts and labels, and that observers have successfully learned these mappings during the exposure phase:
-$$
-P(L_i|C_j) = 
-\begin{cases}
-  1 & \text{if  }  i=j \\  
-  0  & \text{if  }  i\neq j 
-\end{cases}
-$$
-
-## Simulations
-
-During the testing phase, participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and the two objects $o_1$ and $o_2$ presented during the learning phase.
-In order to make a choice, we determine which object is more probable under the target sound $s_T$, in other words, we compare the the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$.
-The values of these probabilities can be computed by summing over all possible concepts and labels:
-$$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
-The joint probability $P(o, C, L, s)$ is obtained by factoring the bayesian network in Figure 2:
-$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
-which could be tansformed using Bayes rule into:
-
-$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
-Finally, assuming that the concept prior probability is uniformly ditributed, we obtain the following expression, where all conditional dependencies have been defined in the previous sub-section.
-
-\begin{equation}
-P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-\end{equation}
-
-From the general expression (1) we derive the exact analytical formula which expresses the probability of accurate responses in the testing phase (Figure 1).
-
-\begin{equation}
-P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
-\end{equation}
-
-```{r model, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
-Circles indicate random variables (shading indicates observed variables).
-The squares indicates fixed model parameters."}
-
-img <- png::readPNG("figs/model.png")
-grid::grid.raster(img)
-
-```
-
-We provide an intuitive illustration of how this probabilistic account explain patterns of learning and development in Figure XX.
-Low accuracy in word learning occurs when the perceptual distance between the labels is small relative to the uncertainty with wich these labels are encoded.
-For example, in Stager and Werker's orginal experiment, children are supposed to associate lable 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
-Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the lable "bih", thanks to the relatively large variance/tolerance of the encoding.
-
-Accuracy is high when the perceptual distance between the labels is large relative to the uncertainty of their encoding.
-Thus, improvement can occur in the same developmental stage if the perceptual distance of the labels is enhanced either through using different-sounding labels (e.g., "lif" vs.
-"neem" instead of "bih" and "dih") or through using additional disambiguating cues [e.g., @thiessen2007].
-Accuracy improves over development because the encoding's uncertainty itself is reduced.
-
-In order to have a more quantitative understanding of the mdoel, we simulate the values of the predicted accuracy (Expression 2) as a function of the perceptual distance between the sounds $\Delta s$.
-We used as parameters the two remaning variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
-The simulations are shown in Figure 3.
-```{r }
-
-#Import data from saved
-simulations <- feather::read_feather("../saved_data/simulations.feather")
-
-plot_simulation <- ggplot(simulations, aes(x=x, y=y, col=sigma)) + 
-  geom_line() + 
-  theme_few()+
-  theme(legend.title = element_text(size=11),
-      legend.text=element_text(size=11),
-      axis.text = element_text(size = 11),
-      aspect.ratio = 0.7
-      )+
-  #plot.margin=grid::unit(c(0,0,0,0), "mm")
-  ylim(c(0.4,1))+
-  geom_hline(yintercept = 0.50, linetype="dashed") +
-  xlab("sound distance") + ylab("Prob. accurate") +
-  facet_grid(.~object_distance)
-
-#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
-
-```
-
-```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the task of learning two similar-sounding words, as a function the perceptual distance between the sounds.
-Colors indicate different values of the standard deviation which we assume is common to both the label and concept probabilistic representations.
-Panels represent graphs using different values of the visual distance between the objects."}
-plot_simulation
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
-
-```
-
-The simulations explain previousely documented facts, and make new predictions:
-
-1) For fixed values of $\Delta o$ and  $\sigma$, the probability of accurate responses increases as a function of $\Delta s$.
-This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren [@stager1997] and adults [@pajak2016].
-
-2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational noise (characterized with $\sigma$) decreases.
-This fact may explain development, i.e., youger children have noisier representations [@swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar sounding words.
-
-3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases with the visual distance between the semantic referents $\Delta o$.
-This is a new predcition that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [@rost2009; @thiessen2007; @dautriche2015; @fennell2010], but no previous study tested the effect of the visual distance between the semantic referents.
-
-To sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
-In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool chidlren and adults.
 
@@
 
-```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of how a probabilsitic account (where distinct categories are encoded with different degrees of uncertainty) can explain patterns of learning and development.
-Accuracy experesses the extent to which a given sound instance indicates a unique category.
-The values vary between 0.5 (total overlap) and 1 (no overalp).
+```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilsitic account of similar word learning using simulated data.
+Words are category distributions over the perceptual space, encoded with different degrees of uncertainty.
+Accuracy experesses the extent to which a given sound instance indicates a unique underlying category.
+The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp).
 Accuracy is low when the perceptual distance between labels is small relative to the category variance.
@@
 ```
-<!--
-To illustrate, imagine that $S_T = S_1$, expression XX leads to:
-$$P(O_1 | S_1) \propto P(S_1|L_1)P(O_1| C_1) + P(S_1|L_2)P(O_1| C_2)$$ 
-$$P(O_2 | S_1) \propto P(S_1|L_1)P(O_2| C_1) + P(S_1|L_2)P(O_2| C_2)$$
 
-This formula explain why learners may still struggle with learning the meaning of similar words even if they learn the correct mappings. Indeed, one can learn that the sound $S_1$ is a better match to
+# Model
 
-Yet infants could have learned that bih is a better match to the ‘bih’ object than dih without triggering greater looking to the switch; the similar word could be judged to be a plausible instance of the newly learned label
+## Task
+
+We model the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009.
+In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects.
+After this exposure phase, participants perform a series of two-alternative forced choices.
+In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
+An overview of the task is shown in Figure \ref{fig:task}.
+
+<!--In previous studies, only the similarity of the sounds was varied across conditions (e.g., "bin"/"din" vs.
+"lif"/"neem").
+In our task, we also vary the visual similarity of the objects, which allows us to explore the effect of additional probabilistic cues on novel word learning and recognition.
+An overview of the task is presented in Figure XX.
 -->
 
-<!--How do children acquire words?
-An important step consists in mapping a phonological form (e.g.
-the sound "cat") to a semantic referent (the concept CAT).
-A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008).
-However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998), and, though this similarity structure influnces word recognition (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
+```{r task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:task}An overview of the task used in this study."}
 
-Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.
+img <- png::readPNG("figs/task.png")
+grid::grid.raster(img)
 
-We know that similarity affect word recognition in both adults and children.
-For example, exposure to a word such as "cat" influences subsequent recognition of phonologically and smantically similar words like "cab" and "dog" (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
+```
 
-Crucially, similarity influences not only the recognition of know words, but also the learning of novel words.
-In the phonological domain, Swingley & Aslin (2007) showed that infants found it more challenging to learn a novel word such as "tog" (which is similar a the familiar word "dog") than to learn a word such as "shang" (which is not similar to any words children knew).
-When learning two novel words, Stager and Werker (1997) found that infatns were more likely to succeed when the words were phonologically distant (e.g., "lif"/"neem"), than when they were phonologcially simialr ("bin/"din").
-In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).
+## Probabilistic strcuture
 
-That said, previous experimental work has studied the effect of phonological and semantic similarity separately.
-Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).
-However, children  acquire a lexicon which is more richly structured than these special cases.
-In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains.
-Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.
+Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation.
+These variables are related in a way that refelects the simple generative scenario represented graphically in Figure \ref{fig:model}.
+When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind.
+The concept prompted the corresponding label $L$.
+Finally, the label was physically instantiated by the sound $s$.
 
-One could imagine two learning scenarios.
-On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al.
-1975).
-For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity.
-Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms.
-On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002).
-Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension.
-In this study, we explore these hypothesis, bla bla
+A similar probabilsitic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning.
+However, the first study assumed that the sounds are heard unambiguousely, and the second assumed the concepts are observed unambiguously.
+In our model, we assume there to be ambiguity at the level of both the labels and the concepts.
+For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectively, are normally distributed:
 
-A second goal of this work is to investigate how the learning mechanism develops over the life span.
-According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors.
-To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.
-A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind.
-For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al.
-2013; Pajak et al.
-2016).
-Here we explore  -->
+$$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
+$$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
+Finally, we assume there to be one-to-one mappings between concepts and labels, and that observers have successfully learned these mappings during the exposure phase:
+$$
+P(L_i|C_j) = 
+\begin{cases}
+  1 & \text{if  }  i=j \\  
+  0  & \text{if  }  i\neq j 
+\end{cases}
+$$
+
+## Simulations
+
+<!--If we denote the correct/target object as $o_T$ and the incorrect object as $o_{\lnot T}$, then the probability of chosing the correct object is: $P(o_T|s_T) = $ -->
+
+During the testing phase (Figure \ref{fig:task}), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and with both objects $o_1$ and $o_2$.
+In order to make a choice, we need to determine which object is more probable under the target sound $s_T$.
+In other words, we need to compare the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$.
+The values of these probabilities can be computed by summing over all possible concepts and labels:
+$$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
+The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in (Figure \ref{fig:model}):
+$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
+which could be tansformed using Bayes rule into:
+
+$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
+Finally, assuming that the concepts' prior probability is uniformly ditributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation.
+See the stimuli sub-section in the Experiment below.}, we obtain the following expression, where all conditional dependencies are now well defined:
+
+$$
+P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
+$$
+
+From this general expression we derive the exact analytical formula, which expresses the probability of accurate responses in the testing phase of the task:
+
+\begin{equation}
+P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
+\end{equation}
+
+```{r model, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
+Circles indicate random variables (shading indicates observed variables).
+The squares indicates fixed model parameters."}
+
+img <- png::readPNG("figs/model.png")
+grid::grid.raster(img)
+
+```
+
+In order to have a more quantitative understanding of the model, we simulate the values of the predicted accuracy (Expression 1) as a function of the perceptual distance between the sounds $\Delta s$.
+We used as parameters the two remaning variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, are assumed to have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
+The simulations are shown in Figure \ref{fig:simulation}.
+```{r }
+
+#Import data from saved
+simulations <- feather::read_feather("../saved_data/simulations.feather")
+
+plot_simulation <- ggplot(simulations, aes(x=x, y=y, col=sigma)) + 
+  geom_line() + 
+  theme_few()+
+  theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11),
+      aspect.ratio = 0.7
+      )+
+  #plot.margin=grid::unit(c(0,0,0,0), "mm")
+  ylim(c(0.4,1))+
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("sound distance") + ylab("Prob. accurate") +
+  facet_grid(.~object_distance)
+
+#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
+
+```
+
+```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase, as a function the perceptual distance between the sounds.
+Colors indicate different values of the standard deviation which we assume is common to both the labels' and concepts' probabilistic representations.
+Panels represent graphs using different values of the visual distance between the objects."}
+plot_simulation
+#img <- png::readPNG("figs/data_all.png")
+#grid::grid.raster(img)
+
+```
+
+The simulations explain previousely documented facts, and make new predictions:
+
+1) For fixed values of $\Delta o$ and  $\sigma$, the probability of accurate responses increases as a function of $\Delta s$.
+This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren [@stager1997] and adults [@pajak2016].
+
+2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational uncertainty (characterized with $\sigma$) decreases.
+This fact may explain development, i.e., youger children have noisier representations [see @swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar-sounding words.
+
+3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases with the visual distance between the semantic referents $\Delta o$.
+This is a new predcition that our model makes.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [@rost2009; @thiessen2007; @dautriche2015; @fennell2010], but no previous study tested the effect of the visual distance between the semantic referents.
+
+To sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
+In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool chidlren and adults.
 
@@
 
-In this experiment, we tested participants in the word learning task introduced above (Figure 1).
+In this experiment, we tested participants in the word learning task introduced above (Figure \ref{fig:task}).
 We explored all three parameters of the model.
-Both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simulataneousely in a within-subject design.
-Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characteized with the degree of uncertainty, $\sigma$, in the probabilsitic representations.
+In particular, both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simulataneousely in a within-subject design.
+Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characteized with the uncertainty parameter, $\sigma$, in the probabilsitic representations.
 <!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
@@
 An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as was specified in the pre-registration\footnote{https://osf.io/jrh38/}).
-We also collected a planed sample of N=30 adults on Amazon Mechanical Turk.
+We also collected a sample of N=20 adults on Amazon Mechanical Turk (this is a pilot, I will plan for 60 participants).
 N=2 adult participants were excluded because of low scores on the catch trials (see pre-registration).
+(I still need to write the code that derives these numbers directly from the data).
 
@@
 The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996].
-We generated three kinds of sound pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
+We generated three kinds of non-sense word pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
 
@@
 These categories are supposed to be naturally occuring kinds that might be seen on an alien planet.
-In each category, we generated "different", "intermediate" and "similar" levels of similarity by manipuating a continuous property controling features of the category's shape (e.g, body strech and head fatness).
+In each category, we generated "different", "intermediate" and "similar" pairs by manipuating a continuous property controling features of the category's shape (e.g, body strech or head fatness).
 
 In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and objcet pair on a 7-point scale.
-We computed averge ratings across partcipants, and we normalized the data so that the values vary between 0 to 1.
-Results are shown in Figure XX, for each stimuli group.
+We processed the resulting data so that it can be used in the model.
+We normalized the values with respect to the most distant level, and we scaled them within the range [0,1].
+Processed data are shown in Figure \ref{fig:stim}, for each stimuli group.
 This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).
@@
 "similar" for adults.
+We made this choice because, on the one hand, adults were at ceiling with "different" sounds, and on the other hand, children were at chance with the "similar" sounds.
+That said, this difference in the level of similairty is accounted for in the model through using the appropriate perceptual distance for each age group (Figure \ref{fig:stim})
+
 The experiment consisted of four conditions which involved, each, one pair of sounds-objects associations.
 These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design in each age group.
-Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its stucture to the other ones, but was used only to select participant who were able to follow the instructions and show minimal learning.
+Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its stucture to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
 
@@
 After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition.
-In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) follwoed by an additional four testing trials.
+In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.
 
@@
 
-The procedure for preschoolers and adults were identical except that preschoolers were accompagnied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.
+The procedure adults were identical except to that of preschool children, except that preschoolers were accompagnied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.
 
@@
 
-We fit the analystical expression (equation 2) to the participants' responses in each age group.
+We fit the probability function (equation 2) to the participants' responses in each age group.
 The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (described in the stimuli sub-section).
@@
 
-First we analyzed the experimental results shown in Figure (XX, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture [@barr2013].
-Results are shown in Table XX.
+We first analyzed the experimental results shown in Figure (\ref{fig:data_all}, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture [@barr2013].
+Results are shown in Table 1.
 We found a main effect of sound distance on the accuray of learning in both children and adults, thus replicating previous findings.
@@
 
-Figures XX (middle and right graphs) show the predictions of the models.
+Figures (\ref{fig:data_all}, middle and right graphs) show the predictions of the models.
 Both model 1 and model 2 fit reseanaby well the experimental data in both children and adults.
@@
 
-For Model 1, the fitted noise parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`] for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
+For Model 1, the fitted noise parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
 It explained the majority of the variance ($R^2=$ `r R2_model1`).
@@
 The model explain almost all the variance ($R^2=$ `r R2_model2`), and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
-Note that, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 which used two degrees of freedom.
+Interestingly, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 (which used two degrees of freedom).
 
@@
 
-Discuss Hofer & Levy, 2017, and Fourtassi & Frank, 2017
+<!--
+
+How do children acquire words?
+An important step consists in mapping a phonological form (e.g.
+the sound "cat") to a semantic referent (the concept CAT).
+A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008).
+However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998), and, though this similarity structure influnces word recognition (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
+
+Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.
+
+We know that similarity affect word recognition in both adults and children.
+For example, exposure to a word such as "cat" influences subsequent recognition of phonologically and smantically similar words like "cab" and "dog" (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
+
+Crucially, similarity influences not only the recognition of know words, but also the learning of novel words.
+In the phonological domain, Swingley & Aslin (2007) showed that infants found it more challenging to learn a novel word such as "tog" (which is similar a the familiar word "dog") than to learn a word such as "shang" (which is not similar to any words children knew).
+When learning two novel words, Stager and Werker (1997) found that infatns were more likely to succeed when the words were phonologically distant (e.g., "lif"/"neem"), than when they were phonologcially simialr ("bin/"din").
+In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).
+
+That said, previous experimental work has studied the effect of phonological and semantic similarity separately.
+Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).
+However, children  acquire a lexicon which is more richly structured than these special cases.
+In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains.
+Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.
+
+One could imagine two learning scenarios.
+On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al.
+1975).
+For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity.
+Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms.
+On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002).
+Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension.
+In this study, we explore these hypothesis, bla bla
+
+A second goal of this work is to investigate how the learning mechanism develops over the life span.
+According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors.
+To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.
+A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind.
+For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al.
+2013; Pajak et al.
+2016).
+Here we explore  -->
 

### 2019-01-09 cogsci/cogsci.tex
new modif on manuscript

@@
 able to encode subtile phonetic contrasts when learning novel word
-meanings, thus suggesting a binary/discontinuous pattern of development.
-However, later work has revealed (e.g., through using simpler testing
-methods) that children do encode such contrasts, thus favoring a rather
-probabilitic/continuous pattern of development. The present study
+meanings, thus suggesting a discontinuous/stage-like pattern of
+development. However, later work has revealed (e.g., through using
+simpler testing methods) that children do encode such contrasts, thus
+favoring a rather a continuous pattern of development. The present study
 proposes a precise probabisitic model describing how development may
@@
 the model can explain various patterns of learning both within the same
-age and across development. More generally, our work highlight the role
-of computational modeling in advancing our understanding of development
-through both organizing exsinting knowledge and generating new
-principled hypotheses.
+age and across development. Our work highlight the role of computational
+modeling in advancing our understanding of development through both
+organizing exsinting knowledge and generating new principled hypotheses.
 
@@
 Regardless of the exact explanation, it is generally accepted that by
-around 17 m.o, chidlren succeed under the same circumstances (Werker,
-Fennell, Corcoran, \& Stager, 2002). What could be the mechanism of
-development? On one possible account, learning is stage-like: younger
-children learn a single, underspecified representation of similar words
-(e.g., ``bin''/``din''). Development occurs when children specify this
-intial coarse reprepsentation and learn two distinct catgories. On an
-other account, learning is continuous: distinct represetations are
-learned even by younger children, but these representations are encoded
-with higher uncertainty in youger children, leading to apparent failure
-in relatively demanding tasks. Development is a continuous process
-whereby the intinial noisy representations become more precise (see
-also, Swingley, 2007).
+around 17 m.o, children succeed in the same task (Werker, Fennell,
+Corcoran, \& Stager, 2002). What could be the mechanism of development?
+Early acccounts assumed--whether implcitly or explicitly-- that children
+encode words in a binary way: they either fail or succeed in encoding
+the relevant phonetic details (simulataneousely with the meanings). This
+account suggested a discontinuous/stage-like pattern of development
+whereby younger children fail to encode the contrastive phonetic detail,
+whereas older children succeed.
 
-Experimental evidence suggest a probabilsitic/continuous, rather than a
-binary/discontinuous develomental scenario. On the one hand,
-14-month-olds who typically fail in the original task succeed both when
-an easier testing method is used (Yoshida, Fennell, Swingley, \& Werker,
-2009), and when uncertainty is mitigated via disambiguating cues
-(Dautriche, Swingley, \& Christophe, 2015; Thiessen, 2007). On the other
-hand, adults show patterns of learning similar to those shown by
-14-month-olds when the task is more challenging and when similarity
-between words increases (Pajak, Creel, \& Levy, 2016; White, Yee,
-Blumstein, \& Morgan, 2013).
+Nevertheless, subsequent findings suggest otherwise. On the one hand,
+14-month-olds--who typically fail in the original task--succeed when an
+easier \emph{testing} method is used, even under the same
+\emph{learning} conditions (Yoshida, Fennell, Swingley, \& Werker,
+2009). They also succeed when uncertainty is mitigated via
+disambiguating cues (e.g., Thiessen, 2007). On the other hand, adults
+show patterns of learning similar to those shown by 14-month-olds when
+the task is more challenging and when similarity between words increases
+(Pajak, Creel, \& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
 
-Here talk about the continuous hypothesis a bit later here. after
-introducing the experimental evidecne.
+These evidence point towards another scenario, where the representations
+are encoded in a probablistic (rather than binary) way, and where
+development is continuous, rather than stage-like (Hofer \& Levy, 2017;
+Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009). On this
+account, correct represetations are learned early in development, but
+these representations are encoded with higher uncertainty in youger
+children, leading to apparent failure in relatively demanding tasks.
+Development is a continuous process whereby the intinial noisy
+representations become more precise. Crucially, more precise
+representation are still imperfect, as low accuracy learning can be
+obtained even with adults when the sounds are subtle enough, e.g.,
+non-native sounds (Pajak et al., 2016).
 
-Also talk more about the major assumption of model, what is contiuous
-about him? and what is the source of this hypothsis (swingley, Yoshida,
-\ldots{})
+We provide an intuitive illustration of how such an account explains
+patterns of learning and development in Figure \ref{fig:illus}. We
+observe low accuracy in word learning when the perceptual distance
+between the labels is small relative to the uncertainty/tolerance with
+wich these labels are encoded. For example, in Stager and Werker's
+orginal experiment, children are supposed to associate lable 1 (``bih'')
+and label 2 (``dih'') with object 1 and object 2, respectively. Though
+children could learn that the label ``bih'' is a better match to object
+1 than ``dih'', they could still judge the sound ``dih'' as a plausible
+instance of the lable ``bih'', thanks to the relatively large tolerance
+of the encoding.
 
-In the light of these evidence, the purpose of the current work is to
-propose a precise probabilsitc model of the Stager and Werker's task
-where developmment is understood to proceed in a continuous fashion
-across the lifespan. We use this model to both provide a unifying
-account for documented experimental findings, and to make new
-predicitions that have not been tested before. Using new data collected
-from both preschool children and adults, we show that the model can
-explain various patterns of learning both within the same age and across
-development.
+Accuracy in word learning increases when the perceived distance between
+the labels is large relative to the tolerance of their encoding. This
+improvement can occur in the same developmental stage if the perceptual
+distance between labels is enhanced through using different-sounding
+labels (e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or
+through using contextual cues (Rost \& McMurray, 2009; Thiessen, 2007).
+Besides, accuracy can improve across development through the refinement
+of the encoding, i.e., if the uncertainy of the encoding decreases.
+
+Building on this intuition, the current work proposes a precise
+probabilsitc model, which we use to both account for previous
+experimental findings, and to make new predicitions that have not been
+tested before. Using new data collected from both preschool children and
+adults, we show that the model can explain various patterns of learning
+both within the same age and across development.
+
+\begin{CodeChunk}
+\begin{figure}[H]
+
+{\centering \includegraphics{figs/illus-1}
+
+}
+
+\caption{\label{fig:illus} An illustration of the probabilsitic account using simulated data.
+Words are category distributions over the perceptual space, encoded with different degrees of uncertainty.
+Accuracy experesses the extent to which a given sound instance indicates a unique underlying category.
+The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp).
+Accuracy is low when the perceptual distance between labels is small relative to the category variance.
+Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
+\end{figure}
+\end{CodeChunk}
 
@@
 corresponding object from the two alternatives. An overview of the task
-is shown in Figure~@ref(fig:task).
+is shown in Figure \ref{fig:task}.
 
@@
 are related in a way that refelects the simple generative scenario
-represented graphically in Figure~@ref(fig:model). When a speaker utters
+represented graphically in Figure \ref{fig:model}. When a speaker utters
 a sound in the presence of an object, the observer assumes that the
 object \(o\) activated the concept \(C\) in the speaker's mind. The
-concept prompted the cooresponding label \(L\). Finally, the label was
+concept prompted the corresponding label \(L\). Finally, the label was
 physically instantiated by the sound \(s\).
@@
 unambiguousely, and the second assumed the concepts are observed
-unambiguously. In our model, we made the more reaistic assumption of
-ambiguity at the level of both the sounds and the objects. For
-simplicity, we assume that the probability of membership of objects and
-sounds to concepts and labels, respectively, are normally distributed:
+unambiguously. In our model, we assume there to be ambiguity at the
+level of both the labels and the concepts. For simplicity, we assume
+that the probability of membership of objects and sounds to concepts and
+labels, respectively, are normally distributed:
 
 \[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
-\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] We assume there to be
-one-to-one mappings between concepts and labels, and that observers have
-successfully learned these mappings during the exposure phase: \[
+\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] Finally, we assume
+there to be one-to-one mappings between concepts and labels, and that
+observers have successfully learned these mappings during the exposure
+phase: \[
 P(L_i|C_j) = 
@@
 
-During the testing phase, participants are presented with one target
-sound \(s_T \in\{s_1, s_2\}\) and the two objects \(o_1\) and \(o_2\)
-presented during the learning phase. In order to make a choice, we
-determine which object is more probable under the target sound \(s_T\),
-in other words, we compare the the probabilities \(P(o_1|s_T)\) and
+During the testing phase (Figure \ref{fig:task}), participants are
+presented with one target sound \(s_T \in\{s_1, s_2\}\) and with both
+objects \(o_1\) and \(o_2\). In order to make a choice, we need to
+determine which object is more probable under the target sound \(s_T\).
+In other words, we need to compare the probabilities \(P(o_1|s_T)\) and
 \(P(o_2|s_T)\). The values of these probabilities can be computed by
@@
 The joint probability \(P(o, C, L, s)\) is obtained by factoring the
-bayesian network in Figure 2: \[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
-which could be tansformed using Bayes rule into:
+Bayesian network in (Figure \ref{fig:model}):
+\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which could be tansformed using
+Bayes rule into:
 
 \[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
-concept prior probability is uniformly ditributed, we obtain the
-following expression, where all conditional dependencies have been
-defined in the previous sub-section.
+concepts' prior probability is uniformly
+ditributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in the Experiment below.},
+we obtain the following expression, where all conditional dependencies
+are now well defined:
 
-\begin{equation}
+\[
 P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-\end{equation}
+\]
 
-From the general expression (1) we derive the exact analytical formula
+From this general expression we derive the exact analytical formula,
 which expresses the probability of accurate responses in the testing
-phase (Figure 1).
+phase of the task:
 
@@
 \begin{CodeChunk}
-\begin{figure}[h]
+\begin{figure}[t]
 
@@
 
-We provide an intuitive illustration of how this probabilistic account
-explain patterns of learning and development in Figure XX. Low accuracy
-in word learning occurs when the perceptual distance between the labels
-is small relative to the uncertainty with wich these labels are encoded.
-For example, in Stager and Werker's orginal experiment, children are
-supposed to associate lable 1 (``bih'') and label 2 (``dih'') with
-object 1 and object 2, respectively. Though children could learn that
-the label ``bih'' is a better match to object 1 than ``dih'', they could
-still judge the sound ``dih'' as a plausible instance of the lable
-``bih'', thanks to the relatively large variance/tolerance of the
-encoding.
-
-Accuracy is high when the perceptual distance between the labels is
-large relative to the uncertainty of their encoding. Thus, improvement
-can occur in the same developmental stage if the perceptual distance of
-the labels is enhanced either through using different-sounding labels
-(e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or through
-using additional disambiguating cues (e.g., Thiessen, 2007). Accuracy
-improves over development because the encoding's uncertainty itself is
-reduced.
-
-In order to have a more quantitative understanding of the mdoel, we
-simulate the values of the predicted accuracy (Expression 2) as a
+In order to have a more quantitative understanding of the model, we
+simulate the values of the predicted accuracy (Expression 1) as a
 function of the perceptual distance between the sounds \(\Delta s\). We
@@
 of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
-simulation, have similar values, i.e.,
+simulation, are assumed to have similar values, i.e.,
 \(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
-Figure 3.
+Figure \ref{fig:simulation}.
 
@@
 
-\caption{\label{fig:simulation}The predicted probability of accurate responses in the task of learning two similar-sounding words, as a function the perceptual distance between the sounds.
-Colors indicate different values of the standard deviation which we assume is common to both the label and concept probabilistic representations.
+\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase, as a function the perceptual distance between the sounds.
+Colors indicate different values of the standard deviation which we assume is common to both the labels' and concepts' probabilistic representations.
 Panels represent graphs using different values of the visual distance between the objects.}\label{fig:simulation}
@@
   For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
-  when the representational noise (characterized with \(\sigma\))
+  when the representational uncertainty (characterized with \(\sigma\))
   decreases. This fact may explain development, i.e., youger children
-  have noisier representations (Swingley, 2007; Yoshida et al., 2009),
-  which leads to lower word recognition accuracy, especially for similar
-  sounding words.
+  have noisier representations (see Swingley, 2007; Yoshida et al.,
+  2009), which leads to lower word recognition accuracy, especially for
+  similar-sounding words.
 \item
@@
   the effect of several bottom-up and top-down properties in
-  disambiguating similar sounding words (Dautriche et al., 2015; Fennell
-  \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007), but no
-  previous study tested the effect of the visual distance between the
-  semantic referents.
+  disambiguating similar sounding words (Dautriche, Swingley, \&
+  Christophe, 2015; Fennell \& Waxman, 2010; Rost \& McMurray, 2009;
+  Thiessen, 2007), but no previous study tested the effect of the visual
+  distance between the semantic referents.
 \end{enumerate}
@@
 
-\begin{CodeChunk}
-\begin{figure}[H]
-
-{\centering \includegraphics{figs/illus-1}
-
-}
-
-\caption{\label{fig:illus} An illustration of how a probabilsitic account (where distinct categories are encoded with different degrees of uncertainty) can explain patterns of learning and development.
-Accuracy experesses the extent to which a given sound instance indicates a unique category.
-The values vary between 0.5 (total overlap) and 1 (no overalp).
-Accuracy is low when the perceptual distance between labels is small relative to the category variance.
-Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
-\end{figure}
-\end{CodeChunk}
-
 \section{Experiment}\label{experiment}
@@
 In this experiment, we tested participants in the word learning task
-introduced above (Figure 1). We explored all three parameters of the
-model. Both the sound similarity (\(\Delta s\)) and object similarity
-(\(\Delta o\)) were varied simulataneousely in a within-subject design.
-Besides, two age groups (preschool children and adults) were tested on
-the same task to explore whether development can be characteized with
-the degree of uncertainty, \(\sigma\), in the probabilsitic
-representations.
+introduced above (Figure \ref{fig:task}). We explored all three
+parameters of the model. In particular, both the sound similarity
+(\(\Delta s\)) and object similarity (\(\Delta o\)) were varied
+simulataneousely in a within-subject design. Besides, two age groups
+(preschool children and adults) were tested on the same task to explore
+whether development can be characteized with the uncertainty parameter,
+\(\sigma\), in the probabilsitic representations.
 
@@
 pre-registration\footnote{https://osf.io/jrh38/}). We also collected a
-planed sample of N=30 adults on Amazon Mechanical Turk. N=2 adult
-participants were excluded because of low scores on the catch trials
-(see pre-registration).
+sample of N=20 adults on Amazon Mechanical Turk (this is a pilot, I will
+plan for 60 participants). N=2 adult participants were excluded because
+of low scores on the catch trials (see pre-registration). (I still need
+to write the code that derives these numbers directly from the data).
 
@@
 (Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
-generated three kinds of sound pairs which varied in their degree of
-similarity to English speakers: 1) ``different'': ``lif''/``neem'' and
-``zem''/``doof'', 2) ``intermediate'': ``aka''/``ama'' and
-``ada''/``aba'', and 3) ``similar'' non-English minimal pairs:
-``ada''/``a\textipa{d\super h}a'' (in hindi) and
+generated three kinds of non-sense word pairs which varied in their
+degree of similarity to English speakers: 1) ``different'':
+``lif''/``neem'' and ``zem''/``doof'', 2) ``intermediate'':
+``aka''/``ama'' and ``ada''/``aba'', and 3) ``similar'' non-English
+minimal pairs: ``ada''/``a\textipa{d\super h}a'' (in hindi) and
 ``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).
@@
 occuring kinds that might be seen on an alien planet. In each category,
-we generated ``different'', ``intermediate'' and ``similar'' levels of
-similarity by manipuating a continuous property controling features of
-the category's shape (e.g, body strech and head fatness).
+we generated ``different'', ``intermediate'' and ``similar'' pairs by
+manipuating a continuous property controling features of the category's
+shape (e.g, body strech or head fatness).
 
@@
 Mechanical Turk evaluated the similarity of each sound and objcet pair
-on a 7-point scale. We computed averge ratings across partcipants, and
-we normalized the data so that the values vary between 0 to 1. Results
-are shown in Figure XX, for each stimuli group. This data will be used
-in the models as the perceptual distance of sound pairs (\(\Delta s\))
-and object pairs (\(\Delta o\)).
+on a 7-point scale. We processed the resulting data so that it can be
+used in the model. We normalized the values with respect to the most
+distant level, and we scaled them within the range {[}0,1{]}. Processed
+data are shown in Figure \ref{fig:stim}, for each stimuli group. This
+data will be used in the models as the perceptual distance of sound
+pairs (\(\Delta s\)) and object pairs (\(\Delta o\)).
 
@@
 in the previous sub-section: ``different'' vs. ``intermediate'' for
-preschoolers, and ``intermediate'' vs. ``similar'' for adults. The
-experiment consisted of four conditions which involved, each, one pair
-of sounds-objects associations. These conditions were constructed by
-crossing the sound's degree of similarity with the object's degree of
+preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
+this choice because, on the one hand, adults were at ceiling with
+``different'' sounds, and on the other hand, children were at chance
+with the ``similar'' sounds. That said, this difference in the level of
+similairty is accounted for in the model through using the appropriate
+perceptual distance for each age group (Figure \ref{fig:stim})
+
+The experiment consisted of four conditions which involved, each, one
+pair of sounds-objects associations. These conditions were constructed
+by crossing the sound's degree of similarity with the object's degree of
 similarity leading to a 2x2 factorial design in each age group. Besides
@@
 which was similar in its stucture to the other ones, but was used only
-to select participant who were able to follow the instructions and show
+to select participants who were able to follow the instructions and show
 minimal learning.
@@
 the on-screen position (left vs.~right) of the two pictures on each
-testing trial.
-
-The procedure for preschoolers and adults were identical except that
-preschoolers were accompagnied by an experimenter and used a tablet,
-whereas adults used their local computers to complete the experiment
-online.
+testing trial. The procedure for preschoolers and adults were identical
+except that preschoolers were accompagnied by an experimenter and used a
+tablet, whereas adults used their local computers to complete the
+experiment online.
 
@@
 Swingley, 2007; Yoshida et al., 2009).
-
-Discuss Hofer \& Levy, 2017, and Fourtassi \& Frank, 2017
 

### 2019-01-09 cogsci/cogsci.Rmd
new modif on manuscript

@@
 In particular, they both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
+Note, however, that both model predict a
 
-For Model 1, the fitted noise parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
-It explained the majority of the variance ($R^2=$ `r R2_model1`).
-For model 2, children had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
-Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`].
-The model explain almost all the variance ($R^2=$ `r R2_model2`), and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
+For Model 1, the fitted uncertainty parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
+The model explained the majority of the variance ($R^2=$ `r R2_model1`).
+For model 2, children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
+Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
+The model explained almost all the variance ($R^2=$ `r R2_model2`).
 Interestingly, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 (which used two degrees of freedom).
@@
 
-Here maybe be more precise about what the model does (providing a summary in prose of the main results )
-
-Subsequent studies have shown that   To account for this phenomenon, we proposed a model where words and their semantic referents are both encoded in a probabilistic fashion.
+...To account for this phenomenon, we proposed a model where words and their semantic referents are both encoded in a probabilistic fashion.
 A pair of words may be encoded simultaneousely, but successful recognition depends both on the perceptual distance between the words and on the degree of uncertainty of their encoding.

### 2019-01-09 cogsci/cogsci.tex
new modif on manuscript

@@
 
-\caption{\label{fig:illus} An illustration of the probabilsitic account using simulated data.
+\caption{\label{fig:illus} An illustration of the probabilsitic account of similar word learning using simulated data.
 Words are category distributions over the perceptual space, encoded with different degrees of uncertainty.
@@
 trials followed by four testing trials, and a second block of two
-exposure trials (for memory refreshment) follwoed by an additional four
+exposure trials (for memory refreshment) followed by an additional four
 testing trials.
@@
 the on-screen position (left vs.~right) of the two pictures on each
-testing trial. The procedure for preschoolers and adults were identical
-except that preschoolers were accompagnied by an experimenter and used a
-tablet, whereas adults used their local computers to complete the
-experiment online.
+testing trial.
+
+The procedure adults were identical except to that of preschool
+children, except that preschoolers were accompagnied by an experimenter
+and used a tablet, whereas adults used their local computers to complete
+the experiment online.
 
@@
 
-We fit the analystical expression (equation 2) to the participants'
+We fit the probability function (equation 2) to the participants'
 responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
@@
 
-First we analyzed the experimental results shown in Figure (XX, left),
-using a mixed-effects logistic regression with sound and object
-distances as fixed effects, and with a maximal random effects strcuture
-(Barr, Levy, Scheepers, \& Tily, 2013). Results are shown in Table XX.
-We found a main effect of sound distance on the accuray of learning in
-both children and adults, thus replicating previous findings. We also
-found a main effect of object distance, thus confirming the new
-prediction of our model.
+We first analyzed the experimental results shown in Figure
+(\ref{fig:data_all}, left), using a mixed-effects logistic regression
+with sound and object distances as fixed effects, and with a maximal
+random effects strcuture (Barr, Levy, Scheepers, \& Tily, 2013). Results
+are shown in Table 1. We found a main effect of sound distance on the
+accuray of learning in both children and adults, thus replicating
+previous findings. We also found a main effect of object distance, thus
+confirming the new prediction of our model.
 
@@
 
-Figures XX (middle and right graphs) show the predictions of the models.
-Both model 1 and model 2 fit reseanaby well the experimental data in
-both children and adults. In particular, they both correcly predict the
-relative recognition accuacy accross conditions: the pair of words that
-differ on both the object and sound levels were the easiest to learn,
-followed by the pairs of words that differ on only one level, then the
-pair of words that are similar on both levels.
+Figures (\ref{fig:data_all}, middle and right graphs) show the
+predictions of the models. Both model 1 and model 2 fit reseanaby well
+the experimental data in both children and adults. In particular, they
+both correcly predict the relative recognition accuacy accross
+conditions: the pair of words that differ on both the object and sound
+levels were the easiest to learn, followed by the pairs of words that
+differ on only one level, then the pair of words that are similar on
+both levels. Note, however, that both model predict a
 
-For Model 1, the fitted noise parameter was \(\sigma =\) 0.63 {[}0.53,
-0.73{]} for preschoolers, and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for
-adults. It explained the majority of the variance (\(R^2=\) 0.94). For
-model 2, children had a sound specific noise of \(\sigma_S =\) 0.9
-{[}0.68, 1.11{]}, and a concept specific noise of \(\sigma_C =\) 0.29
-{[}0.1, 0.49{]}. Adults had a sound specific noise of \(\sigma_S =\)
-0.16 {[}0.05, 0.28{]}. The model explain almost all the variance
-(\(R^2=\) 0.96), and a concept specific noise of \(\sigma_C =\) 0.14
-{[}0.05, 0.23{]}. Note that, despite the fact that Model 1 used only one
-degree of freedom, it captures the data variance almost as well as Model
-2 which used two degrees of freedom.
+For Model 1, the fitted uncertainty parameter was \(\sigma =\) 0.63
+{[}0.53, 0.73{]}\footnote{95 \% Confidence intervals.} for preschoolers,
+and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for adults. The model explained
+the majority of the variance (\(R^2=\) 0.94). For model 2, children had
+a label-specific uncertainty of \(\sigma_S =\) 0.9 {[}0.68, 1.11{]}, and
+a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1, 0.49{]}.
+Adults had a sound specific noise of \(\sigma_S =\) 0.16 {[}0.05,
+0.28{]}, and a concept-specific noise of \(\sigma_C =\) 0.14 {[}0.05,
+0.23{]}. The model explained almost all the variance (\(R^2=\) 0.96).
+Interestingly, despite the fact that Model 1 used only one degree of
+freedom, it captures the data variance almost as well as Model 2 (which
+used two degrees of freedom).
 
@@
 
-Here maybe be more precise about what the model does (providing a
-summary in prose of the main results )
-
-Subsequent studies have shown that To account for this phenomenon, we
-proposed a model where words and their semantic referents are both
-encoded in a probabilistic fashion. A pair of words may be encoded
-simultaneousely, but successful recognition depends both on the
-perceptual distance between the words and on the degree of uncertainty
-of their encoding. These predictions explained learning patterns both
-within and across developmental stages, respectively.
+\ldots{}To account for this phenomenon, we proposed a model where words
+and their semantic referents are both encoded in a probabilistic
+fashion. A pair of words may be encoded simultaneousely, but successful
+recognition depends both on the perceptual distance between the words
+and on the degree of uncertainty of their encoding. These predictions
+explained learning patterns both within and across developmental stages,
+respectively.
 

### 2019-01-09 cogsci/cogsci.tex
new modif on manuscript

@@
 
-\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois \And {\large \bf Michael C.
+\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
 Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

### 2019-01-09 cogsci/cogsci.Rmd
new modif on manuscript

@@
 ---
-title: "Word Learning as Network Growth: A Cross-linguistic Analysis"
+title: "Continuous Development in Learning Similar-sounding Words"
 
@@
     \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
-    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
+    \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University
     \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

### 2019-01-09 cogsci/cogsci.tex
new modif on manuscript

@@
 
-\title{Word Learning as Network Growth: A Cross-linguistic Analysis}
+\title{Continuous Development in Learning Similar-sounding Words}
 
@@
 
-\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
+\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
 Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

### 2019-01-09 cogsci/cogsci.Rmd
new modif on manuscript

@@
 
-    "Stager and Werker (1997) first showed that chidlren's early ability to distinguish similar sounds do not automatically translate into word learning skills.
-Early explanations proposed that children may not be able to encode subtile phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development.
+    "Stager and Werker (1997) first showed that children's early ability to distinguish similar sounds do not automatically translate into word learning skills.
+Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development.
 However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a rather a continuous pattern of development.
-The present study proposes a precise probabisitic model describing how development may processd in a continuous fashion.
-The purpose of the model is to account for previousely documented facts while providing new predictions.
-We collected data from both preschool children and adults, and we show that the model can explain various patterns of learning both within the same age and across development.
-Our work highlight the role of computational modeling in advancing our understanding of development through both organizing exsinting knowledge and generating new principled hypotheses."
+The present study proposes a precise probabilistic model describing how development may proceed in a continuous fashion across the lifespan.
+The purpose of the model is to account for previously documented facts while providing new predictions.
+We collected data from both preschool children and adults, and we showed that the model can explain various patterns of learning both within the same age and across development.
+Our work highlights the role of computational modeling in advancing our understanding of development both through organizing exsinting knowledge and through generating new principled hypotheses."
 
 keywords:
-    "word learning, cogniive development, computational modeling"
+    "word learning, cognitive development, computational modeling"
 
@@
 Several factors can explain this finding.
-For example it is possible that the task of meaning learning increases cognitive demands on children (compared to a simple perceptual descrimination).
+For example it is possible that the task of meaning learning increases cognitive demands on children (compared to a simple perceptual discrimination).
 In particular, it requires paying attention to both the sounds and the corresponding objects, which may hinder precise encoding in memory of some phonetic details [@stager1997; @hofer2017].
@@
 What could be the mechanism of development?
-Early acccounts assumed–whether implcitly or explicitly– that children encode words in a binary way: they either fail or succeed in encoding the relevant phonetic details (simulataneousely with the meanings).
+Early accounts assumed–whether implicitly or explicitly– that children encode words in a binary way: they either fail or succeed in encoding the relevant phonetic details (simultaneously with the meanings).
 This account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.
@@
 
-These evidence point towards another scenario, where the representations are encoded in a probablistic (rather than binary) way, and where development is continuous, rather than stage-like [@swingley2007; @yoshida2009; @pajak2016; @hofer2017].
-On this account, correct represetations are learned early in development, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks.
-Development is a continuous process whereby the intinial noisy representations become more precise.
-Crucially, more precise representation are still imperfect, as low accuracy learning can be obtained even with adults when the sounds are subtle enough, e.g., non-native sounds [@pajak2016].
+These evidence point towards another scenario, where the representations are encoded in a probabilistic (rather than binary) way, and where development is continuous, rather than stage-like [@swingley2007; @yoshida2009; @pajak2016].
+On this account, correct representations are learned early in development, but these representations are encoded with higher uncertainty in younger children, leading to apparent failure in relatively demanding tasks.
+Development is a continuous process whereby the initial noisy representations become more precise.
+Crucially, more precise representation are still imperfect: Even with adults show low accuracy learning when the sounds are subtle enough, e.g., non-native sounds [@pajak2016].
 
 We provide an intuitive illustration of how such an account explains patterns of learning and development in Figure \ref{fig:illus}.
-We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty/tolerance with wich these labels are encoded.
-For example, in Stager and Werker's orginal experiment, children are supposed to associate lable 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
-Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the lable "bih", thanks to the relatively large tolerance of the encoding.
+We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty/tolerance with which these labels are encoded.
+For example, in Stager and Werker's original experiment, children are supposed to associate label 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
+Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large tolerance of the encoding.
 
@@
 This improvement can occur in the same developmental stage if the perceptual distance between labels is enhanced through using different-sounding labels (e.g., "lif" vs.
-"neem" instead of "bih" and "dih") or through using contextual cues [@thiessen2007; @rost2009].
-Besides, accuracy can improve across development through the refinement of the encoding, i.e., if the uncertainy of the encoding decreases.
+"neem" instead of "bih" and "dih") or through using additional cues [@thiessen2007; @rost2009].
+Besides, accuracy can improve across development through the refinement of the encoding.
 
-Building on this intuition, the current work proposes a precise probabilsitc model, which we use to both account for previous experimental findings, and to make new predicitions that have not been tested before.
+Building on this intuition, the current work proposes a precise probabilistic model, which we use to both account for previous experimental findings, and to make new predictions that have not been tested before.
 Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.
@@
 
-```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilsitic account of similar word learning using simulated data.
-Words are category distributions over the perceptual space, encoded with different degrees of uncertainty.
-Accuracy experesses the extent to which a given sound instance indicates a unique underlying category.
-The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp).
-Accuracy is low when the perceptual distance between labels is small relative to the category variance.
+```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
+Two words are represented as distributions over the perceptual space.
+Here accuracy expresses the extent to which a given sound instance indicates the word on the left (red bar), as opposed to the word on the right (green bar).
+The values vary between 0.5 (total overlap between the distributions) and 1 (no overlap).
+Accuracy is low when the perceptual distance between labels is small relative to the variance.
 Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development)."}
@@
 We model the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009.
-In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects.
+In this task, participants are first exposed to the association between pairs of nonsense words (e.g., "lif"/"neem") and pairs of objects.
 After this exposure phase, participants perform a series of two-alternative forced choices.
@@
 
-## Probabilistic strcuture
+## Probabilistic structure
 
 Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation.
-These variables are related in a way that refelects the simple generative scenario represented graphically in Figure \ref{fig:model}.
+These variables are related in a way that reflects the simple generative scenario represented graphically in Figure \ref{fig:model}.
 When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind.
@@
 
-A similar probabilsitic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning.
-However, the first study assumed that the sounds are heard unambiguousely, and the second assumed the concepts are observed unambiguously.
+A similar probabilistic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning.
+However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously.
 In our model, we assume there to be ambiguity at the level of both the labels and the concepts.
@@
 
-During the testing phase (Figure \ref{fig:task}), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and with both objects $o_1$ and $o_2$.
+During the testing phase (see Figure \ref{fig:task}), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and with both objects $o_1$ and $o_2$.
 In order to make a choice, we need to determine which object is more probable under the target sound $s_T$.
@@
 $$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
-The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in (Figure \ref{fig:model}):
+The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in Figure \ref{fig:model}:
 $$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
-which could be tansformed using Bayes rule into:
+which could be transformed using Bayes rule into:
 
 $$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
-Finally, assuming that the concepts' prior probability is uniformly ditributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation.
+Finally, assuming that the concepts' prior probability is uniformly distributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation.
 See the stimuli sub-section in the Experiment below.}, we obtain the following expression, where all conditional dependencies are now well defined:
@@
 In order to have a more quantitative understanding of the model, we simulate the values of the predicted accuracy (Expression 1) as a function of the perceptual distance between the sounds $\Delta s$.
-We used as parameters the two remaning variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, are assumed to have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
+We used as parameters the two remaining variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the distributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, are assumed to have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
 The simulations are shown in Figure \ref{fig:simulation}.
@@
 
-The simulations explain previousely documented facts, and make new predictions:
+The simulations explain some previousely documented facts, and make new predictions:
 
 1) For fixed values of $\Delta o$ and  $\sigma$, the probability of accurate responses increases as a function of $\Delta s$.
-This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both chidlren [@stager1997] and adults [@pajak2016].
+This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both children [@stager1997] and adults [@pajak2016].
 
 2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational uncertainty (characterized with $\sigma$) decreases.
-This fact may explain development, i.e., youger children have noisier representations [see @swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar-sounding words.
+This fact may explain development, i.e., younger children have noisier representations [see @swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar-sounding words.
 
 3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases with the visual distance between the semantic referents $\Delta o$.
-This is a new predcition that our model makes.
+This is a new prediction that our model makes.
 Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [@rost2009; @thiessen2007; @dautriche2015; @fennell2010], but no previous study tested the effect of the visual distance between the semantic referents.
@@
 To sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
-In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool chidlren and adults.
+In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool children and adults.
 
@@
 We explored all three parameters of the model.
-In particular, both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simulataneousely in a within-subject design.
-Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characteized with the uncertainty parameter, $\sigma$, in the probabilsitic representations.
+In particular, both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design.
+Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameter, $\sigma$, in the probabilsitic representations.
 <!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
@@
 N=2 adult participants were excluded because of low scores on the catch trials (see pre-registration).
-(I still need to write the code that derives these numbers directly from the data).
+(I still need to write the code that derives these numbers automatically from the data).
 
@@
 The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996].
-We generated three kinds of non-sense word pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
+We generated three kinds of nonsense word pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
 
 As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish".
-These categories are supposed to be naturally occuring kinds that might be seen on an alien planet.
-In each category, we generated "different", "intermediate" and "similar" pairs by manipuating a continuous property controling features of the category's shape (e.g, body strech or head fatness).
+These categories are supposed to be naturally occurring kinds that might be seen on an alien planet.
+In each category, we generated "different", "intermediate" and "similar" pairs by manipulating a continuous property controlling features of the category's shape (e.g, body stretch or head fatness).
 
-In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and objcet pair on a 7-point scale.
+In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and object pair on a 7-point scale.
 We processed the resulting data so that it can be used in the model.
@@
 "similar" for adults.
-We made this choice because, on the one hand, adults were at ceiling with "different" sounds, and on the other hand, children were at chance with the "similar" sounds.
-That said, this difference in the level of similairty is accounted for in the model through using the appropriate perceptual distance for each age group (Figure \ref{fig:stim})
+We made this choice because, on the one hand, adults were at ceiling with "different" sounds/objects, and on the other hand, children were at chance with the "similar" sounds/objects.
+That said, this difference in the level of similarity is accounted for in the model through using the appropriate perceptual distance used in each age group (Figure \ref{fig:stim}).
 
@@
 These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design in each age group.
-Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its stucture to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
+Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
 
@@
 For both objects, visual stimuli were present for the duration of the sound clip (∼800ms).
-In the testing trials, children saw both objects simultaneousely and heard only one sound.
+In the testing trials, children saw both objects simultaneously and heard only one sound.
 They completed the trial by selecting which of the two objects corresponded to the sound.
@@
 
-The procedure adults were identical except to that of preschool children, except that preschoolers were accompagnied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.
+The procedure in the adult experiment was identical to that of preschool children, except that preschoolers were accompanied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.
 
@@
 We fit the probability function (equation 2) to the participants' responses in each age group.
-The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (described in the stimuli sub-section).
+The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \ref{fig:stim}).
 We used two models: \textbf{model 1} fit only one parameter ($\sigma = \sigma_C =\sigma_L$), and \textbf{model 2} fit two parameters ($\sigma_C  \neq \sigma_L$).
@@
 
-We first analyzed the experimental results shown in Figure (\ref{fig:data_all}, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture [@barr2013].
+We first analyzed the experimental results shown in Figure (\ref{fig:data_all}, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects structure [@barr2013].
 Results are shown in Table 1.
-We found a main effect of sound distance on the accuray of learning in both children and adults, thus replicating previous findings.
+We found a main effect of sound distance on the accuracy of learning in both children and adults, thus replicating previous findings.
 We also found a main effect of object distance, thus confirming the new prediction of our model.
@@
 Figures (\ref{fig:data_all}, middle and right graphs) show the predictions of the models.
-Both model 1 and model 2 fit reseanaby well the experimental data in both children and adults.
-In particular, they both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
-Note, however, that both model predict a
+Both model 1 and model 2 fit reasonably well the experimental data in both children and adults.
+In particular, they both correctly predict the relative recognition accuracy across conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
+Note, however, that both models predict a slight interaction between sounds and objects, but such an interaction was not significant in the the experimental data (Table 1).
 
 For Model 1, the fitted uncertainty parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
+As predicted, the uncertainty parameter was larger for children than it was for adults.
 The model explained the majority of the variance ($R^2=$ `r R2_model1`).
 For model 2, children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
-Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
+Adults had a label-specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
 The model explained almost all the variance ($R^2=$ `r R2_model2`).
@@
 
-...To account for this phenomenon, we proposed a model where words and their semantic referents are both encoded in a probabilistic fashion.
-A pair of words may be encoded simultaneousely, but successful recognition depends both on the perceptual distance between the words and on the degree of uncertainty of their encoding.
-These predictions explained learning patterns both within and across developmental stages, respectively.
+Since the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills, researchers have debated about the source of such a discrepancy.
+In this work, we were more interested in the development of this phenomenon, regardless of its exact origin.
+Building on some previous findings and discussions [@yoshida2009; @swingley2007], we proposed a model which assumes that subtle perceptual features are correctly encoded during word meaning learning, but that the precision of this encoding vary across development.
+We compared the predictions to new data which we collected from preschool children and adults.
+We found that the probabilistic model captured not only the patterns of development, but also various learning patterns within the same age group.
 
-Besides accounting for previous findings, our model made a new prediction: learning similar words is not only modulated by to similarity of their phonological forms, but also by the visual similarity of their semantic referents.
-More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggest that children may prioritize the acqusition of words that are quite distant in the semantic space.
+The model made a new prediction which we tested experimentally for the first time: learning similar words is not only modulated by to similarity of their phonological forms, but also by the visual similarity of their semantic referents.
+More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.
 This suggestion is supported by recent findings based on the investigation of early vocabulary growth [@engelthaler2017; @sizemore2018].
@@
 
+To conclude, this paper proposes a computational model for the probabilistic/continuous account, and the findings do endorse this account as a valid framework for the study of similar word learning and the mechanism of its development.
+More generally, together with previous modeling efforts [e.g., @apfelbaum2011; @hofer2017], our work highlight the crucial role computation models can play in theory building through both a compact organization of existing knowledge and through generating new principled hypothesis.
+
 <!--Not only does our model predict that both phonological and semantic relatedness matter in learning novel words, it also provides
 a precise account of *how* these two dimensions interact to predict learning. In fact,-->
-Our model can be seen as an ideal observer [@anderson1990] in the sense that it provides a precise charaterization of the task, and shows how information can used optimally to perform this task.
+<!--Our model can be seen as an ideal observer [@anderson1990] in the sense that it provides a precise charaterization of the task, and shows how information can used optimally to perform this task.
 In our case, the input is categorized with uncertainty, thus the model performs an optimal probabilistic (Bayesian) inference, combining cues from both the sound and the semantic referents.
@@
 Note that our model is agnostic as to the precise source of this uncertainty: part of it maybe due to ambiguous phonological boundaries [@rost], and another part could be due to various task demands [@hofer].
+-->
 
-To conclude, this study proposed a model of novel word is compatible with the hypothesis according to which development is not so much about a qualitative cognitive change as much as it is about the quantitative refinement of similar skills acrss the lifespan [@yoshida2009; @swingley2007; @pajak2016].
+<!--To conclude, this study proposed a model of novel word is compatible with the hypothesis according to which development is not so much about a qualitative cognitive change as much as it is about the quantitative refinement of similar skills acrss the lifespan [@yoshida2009; @swingley2007; @pajak2016].
+-->
 

### 2019-01-09 cogsci/cogsci.tex
new modif on manuscript

@@
 \begin{abstract}
-Stager and Werker (1997) first showed that chidlren's early ability to
+Stager and Werker (1997) first showed that children's early ability to
 distinguish similar sounds do not automatically translate into word
 learning skills. Early explanations proposed that children may not be
-able to encode subtile phonetic contrasts when learning novel word
+able to encode subtle phonetic contrasts when learning novel word
 meanings, thus suggesting a discontinuous/stage-like pattern of
@@
 favoring a rather a continuous pattern of development. The present study
-proposes a precise probabisitic model describing how development may
-processd in a continuous fashion. The purpose of the model is to account
-for previousely documented facts while providing new predictions. We
-collected data from both preschool children and adults, and we show that
-the model can explain various patterns of learning both within the same
-age and across development. Our work highlight the role of computational
-modeling in advancing our understanding of development through both
-organizing exsinting knowledge and generating new principled hypotheses.
+proposes a precise probabilistic model describing how development may
+proceed in a continuous fashion across the lifespan. The purpose of the
+model is to account for previously documented facts while providing new
+predictions. We collected data from both preschool children and adults,
+and we showed that the model can explain various patterns of learning
+both within the same age and across development. Our work highlights the
+role of computational modeling in advancing our understanding of
+development both through organizing exsinting knowledge and through
+generating new principled hypotheses.
 
 \textbf{Keywords:}
-word learning, cogniive development, computational modeling
+word learning, cognitive development, computational modeling
 \end{abstract}
@@
 that the task of meaning learning increases cognitive demands on
-children (compared to a simple perceptual descrimination). In
+children (compared to a simple perceptual discrimination). In
 particular, it requires paying attention to both the sounds and the
@@
 Corcoran, \& Stager, 2002). What could be the mechanism of development?
-Early acccounts assumed--whether implcitly or explicitly-- that children
+Early accounts assumed--whether implicitly or explicitly-- that children
 encode words in a binary way: they either fail or succeed in encoding
-the relevant phonetic details (simulataneousely with the meanings). This
+the relevant phonetic details (simultaneously with the meanings). This
 account suggested a discontinuous/stage-like pattern of development
@@
 These evidence point towards another scenario, where the representations
-are encoded in a probablistic (rather than binary) way, and where
-development is continuous, rather than stage-like (Hofer \& Levy, 2017;
-Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009). On this
-account, correct represetations are learned early in development, but
-these representations are encoded with higher uncertainty in youger
-children, leading to apparent failure in relatively demanding tasks.
-Development is a continuous process whereby the intinial noisy
-representations become more precise. Crucially, more precise
-representation are still imperfect, as low accuracy learning can be
-obtained even with adults when the sounds are subtle enough, e.g.,
-non-native sounds (Pajak et al., 2016).
+are encoded in a probabilistic (rather than binary) way, and where
+development is continuous, rather than stage-like (Pajak et al., 2016;
+Swingley, 2007; Yoshida et al., 2009). On this account, correct
+representations are learned early in development, but these
+representations are encoded with higher uncertainty in younger children,
+leading to apparent failure in relatively demanding tasks. Development
+is a continuous process whereby the initial noisy representations become
+more precise. Crucially, more precise representation are still
+imperfect: Even with adults show low accuracy learning when the sounds
+are subtle enough, e.g., non-native sounds (Pajak et al., 2016).
 
@@
 between the labels is small relative to the uncertainty/tolerance with
-wich these labels are encoded. For example, in Stager and Werker's
-orginal experiment, children are supposed to associate lable 1 (``bih'')
-and label 2 (``dih'') with object 1 and object 2, respectively. Though
-children could learn that the label ``bih'' is a better match to object
-1 than ``dih'', they could still judge the sound ``dih'' as a plausible
-instance of the lable ``bih'', thanks to the relatively large tolerance
-of the encoding.
+which these labels are encoded. For example, in Stager and Werker's
+original experiment, children are supposed to associate label 1
+(``bih'') and label 2 (``dih'') with object 1 and object 2,
+respectively. Though children could learn that the label ``bih'' is a
+better match to object 1 than ``dih'', they could still judge the sound
+``dih'' as a plausible instance of the label ``bih'', thanks to the
+relatively large tolerance of the encoding.
 
@@
 labels (e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or
-through using contextual cues (Rost \& McMurray, 2009; Thiessen, 2007).
+through using additional cues (Rost \& McMurray, 2009; Thiessen, 2007).
 Besides, accuracy can improve across development through the refinement
-of the encoding, i.e., if the uncertainy of the encoding decreases.
+of the encoding.
 
 Building on this intuition, the current work proposes a precise
-probabilsitc model, which we use to both account for previous
-experimental findings, and to make new predicitions that have not been
+probabilistic model, which we use to both account for previous
+experimental findings, and to make new predictions that have not been
 tested before. Using new data collected from both preschool children and
@@
 
-\caption{\label{fig:illus} An illustration of the probabilsitic account of similar word learning using simulated data.
-Words are category distributions over the perceptual space, encoded with different degrees of uncertainty.
-Accuracy experesses the extent to which a given sound instance indicates a unique underlying category.
-The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp).
-Accuracy is low when the perceptual distance between labels is small relative to the category variance.
+\caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
+Two words are represented as distributions over the perceptual space.
+Here accuracy expresses the extent to which a given sound instance indicates the word on the left (red bar), as opposed to the word on the right (green bar).
+The values vary between 0.5 (total overlap between the distributions) and 1 (no overlap).
+Accuracy is low when the perceptual distance between labels is small relative to the variance.
 Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
@@
 and a testing method similar to the one used by Yoshida et al. (2009).
-In this task, particiants are first exposed to the association between
-pairs of nonesense words (e.g., ``lif''/``neem'') and pairs of objects.
+In this task, participants are first exposed to the association between
+pairs of nonsense words (e.g., ``lif''/``neem'') and pairs of objects.
 After this exposure phase, participants perform a series of
@@
 
-\subsection{Probabilistic strcuture}\label{probabilistic-strcuture}
+\subsection{Probabilistic structure}\label{probabilistic-structure}
 
@@
 of spoken word recognition in a referential situation. These variables
-are related in a way that refelects the simple generative scenario
+are related in a way that reflects the simple generative scenario
 represented graphically in Figure \ref{fig:model}. When a speaker utters
@@
 
-A similar probabilsitic structure was used by Lewis \& Frank (2013) to
+A similar probabilistic structure was used by Lewis \& Frank (2013) to
 model concept learning, and by Hofer \& Levy (2017) to model spoken word
 learning. However, the first study assumed that the sounds are heard
-unambiguousely, and the second assumed the concepts are observed
+unambiguously, and the second assumed the concepts are observed
 unambiguously. In our model, we assume there to be ambiguity at the
@@
 
-During the testing phase (Figure \ref{fig:task}), participants are
+During the testing phase (see Figure \ref{fig:task}), participants are
 presented with one target sound \(s_T \in\{s_1, s_2\}\) and with both
@@
 The joint probability \(P(o, C, L, s)\) is obtained by factoring the
-Bayesian network in (Figure \ref{fig:model}):
-\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which could be tansformed using
-Bayes rule into:
+Bayesian network in Figure \ref{fig:model}:
+\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which could be transformed
+using Bayes rule into:
 
@@
 concepts' prior probability is uniformly
-ditributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in the Experiment below.},
+distributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in the Experiment below.},
 we obtain the following expression, where all conditional dependencies
@@
 function of the perceptual distance between the sounds \(\Delta s\). We
-used as parameters the two remaning variables, i.e., the visual distance
-between the semantic referents \(\Delta o\) and the standard deviation
-of the dsitributions \(p(s| L)\) and \(p(o | C)\) (which, in this
-simulation, are assumed to have similar values, i.e.,
+used as parameters the two remaining variables, i.e., the visual
+distance between the semantic referents \(\Delta o\) and the standard
+deviation of the distributions \(p(s| L)\) and \(p(o | C)\) (which, in
+this simulation, are assumed to have similar values, i.e.,
 \(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
@@
 
-The simulations explain previousely documented facts, and make new
+The simulations explain some previousely documented facts, and make new
 predictions:
@@
   pattern accounts for the fact that similar sounds are generally more
-  challenging to learn than different sounds for both chidlren (Stager
+  challenging to learn than different sounds for both children (Stager
   \& Werker, 1997) and adults (Pajak et al., 2016).
@@
   when the representational uncertainty (characterized with \(\sigma\))
-  decreases. This fact may explain development, i.e., youger children
+  decreases. This fact may explain development, i.e., younger children
   have noisier representations (see Swingley, 2007; Yoshida et al.,
@@
   with the visual distance between the semantic referents \(\Delta o\).
-  This is a new predcition that our model makes. Previous work studied
+  This is a new prediction that our model makes. Previous work studied
   the effect of several bottom-up and top-down properties in
@@
 accurate \emph{quantitative} predictions by fitting it to new
-experimental data collected from preschool chidlren and adults.
+experimental data collected from preschool children and adults.
 
@@
 (\(\Delta s\)) and object similarity (\(\Delta o\)) were varied
-simulataneousely in a within-subject design. Besides, two age groups
+simultaneously in a within-subject design. Besides, two age groups
 (preschool children and adults) were tested on the same task to explore
-whether development can be characteized with the uncertainty parameter,
+whether development can be characterized with the uncertainty parameter,
 \(\sigma\), in the probabilsitic representations.
@@
 of low scores on the catch trials (see pre-registration). (I still need
-to write the code that derives these numbers directly from the data).
+to write the code that derives these numbers automatically from the
+data).
 
@@
 (Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
-generated three kinds of non-sense word pairs which varied in their
+generated three kinds of nonsense word pairs which varied in their
 degree of similarity to English speakers: 1) ``different'':
@@
 ``bug'', and ``fish''. These categories are supposed to be naturally
-occuring kinds that might be seen on an alien planet. In each category,
+occurring kinds that might be seen on an alien planet. In each category,
 we generated ``different'', ``intermediate'' and ``similar'' pairs by
-manipuating a continuous property controling features of the category's
-shape (e.g, body strech or head fatness).
+manipulating a continuous property controlling features of the
+category's shape (e.g, body stretch or head fatness).
 
 In a separate survey, \(N=20\) participants recruited on Amazon
-Mechanical Turk evaluated the similarity of each sound and objcet pair
+Mechanical Turk evaluated the similarity of each sound and object pair
 on a 7-point scale. We processed the resulting data so that it can be
@@
 this choice because, on the one hand, adults were at ceiling with
-``different'' sounds, and on the other hand, children were at chance
-with the ``similar'' sounds. That said, this difference in the level of
-similairty is accounted for in the model through using the appropriate
-perceptual distance for each age group (Figure \ref{fig:stim})
+``different'' sounds/objects, and on the other hand, children were at
+chance with the ``similar'' sounds/objects. That said, this difference
+in the level of similarity is accounted for in the model through using
+the appropriate perceptual distance used in each age group (Figure
+\ref{fig:stim}).
 
@@
 the 4 conditions, we also tested participants on a fifth catch condition
-which was similar in its stucture to the other ones, but was used only
+which was similar in its structure to the other ones, but was used only
 to select participants who were able to follow the instructions and show
@@
 duration of the sound clip (∼800ms). In the testing trials, children saw
-both objects simultaneousely and heard only one sound. They completed
-the trial by selecting which of the two objects corresponded to the
-sound. They responded by touching one of the pictures on the tablet.
+both objects simultaneously and heard only one sound. They completed the
+trial by selecting which of the two objects corresponded to the sound.
+They responded by touching one of the pictures on the tablet.
 
@@
 
-The procedure adults were identical except to that of preschool
-children, except that preschoolers were accompagnied by an experimenter
+The procedure in the adult experiment was identical to that of preschool
+children, except that preschoolers were accompanied by an experimenter
 and used a tablet, whereas adults used their local computers to complete
@@
 responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
-were set based on data from the similarity judgment task (described in
-the stimuli sub-section). We used two models: \textbf{model 1} fit only
-one parameter (\(\sigma = \sigma_C =\sigma_L\)), and \textbf{model 2}
-fit two parameters (\(\sigma_C \neq \sigma_L\)). The values of the
+were set based on data from the similarity judgment task (Figure
+\ref{fig:stim}). We used two models: \textbf{model 1} fit only one
+parameter (\(\sigma = \sigma_C =\sigma_L\)), and \textbf{model 2} fit
+two parameters (\(\sigma_C \neq \sigma_L\)). The values of the
 parameters were derived using weighted least-squares estimates.
@@
 with sound and object distances as fixed effects, and with a maximal
-random effects strcuture (Barr, Levy, Scheepers, \& Tily, 2013). Results
+random effects structure (Barr, Levy, Scheepers, \& Tily, 2013). Results
 are shown in Table 1. We found a main effect of sound distance on the
-accuray of learning in both children and adults, thus replicating
+accuracy of learning in both children and adults, thus replicating
 previous findings. We also found a main effect of object distance, thus
@@
 Figures (\ref{fig:data_all}, middle and right graphs) show the
-predictions of the models. Both model 1 and model 2 fit reseanaby well
+predictions of the models. Both model 1 and model 2 fit reasonably well
 the experimental data in both children and adults. In particular, they
-both correcly predict the relative recognition accuacy accross
+both correctly predict the relative recognition accuracy across
 conditions: the pair of words that differ on both the object and sound
@@
 differ on only one level, then the pair of words that are similar on
-both levels. Note, however, that both model predict a
+both levels. Note, however, that both models predict a slight
+interaction between sounds and objects, but such an interaction was not
+significant in the the experimental data (Table 1).
 
@@
 {[}0.53, 0.73{]}\footnote{95 \% Confidence intervals.} for preschoolers,
-and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for adults. The model explained
-the majority of the variance (\(R^2=\) 0.94). For model 2, children had
-a label-specific uncertainty of \(\sigma_S =\) 0.9 {[}0.68, 1.11{]}, and
-a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1, 0.49{]}.
-Adults had a sound specific noise of \(\sigma_S =\) 0.16 {[}0.05,
-0.28{]}, and a concept-specific noise of \(\sigma_C =\) 0.14 {[}0.05,
-0.23{]}. The model explained almost all the variance (\(R^2=\) 0.96).
-Interestingly, despite the fact that Model 1 used only one degree of
-freedom, it captures the data variance almost as well as Model 2 (which
-used two degrees of freedom).
+and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for adults. As predicted, the
+uncertainty parameter was larger for children than it was for adults.
+The model explained the majority of the variance (\(R^2=\) 0.94). For
+model 2, children had a label-specific uncertainty of \(\sigma_S =\) 0.9
+{[}0.68, 1.11{]}, and a concept-specific uncertainty of \(\sigma_C =\)
+0.29 {[}0.1, 0.49{]}. Adults had a label-specific noise of
+\(\sigma_S =\) 0.16 {[}0.05, 0.28{]}, and a concept-specific noise of
+\(\sigma_C =\) 0.14 {[}0.05, 0.23{]}. The model explained almost all the
+variance (\(R^2=\) 0.96). Interestingly, despite the fact that Model 1
+used only one degree of freedom, it captures the data variance almost as
+well as Model 2 (which used two degrees of freedom).
 
@@
 
-\ldots{}To account for this phenomenon, we proposed a model where words
-and their semantic referents are both encoded in a probabilistic
-fashion. A pair of words may be encoded simultaneousely, but successful
-recognition depends both on the perceptual distance between the words
-and on the degree of uncertainty of their encoding. These predictions
-explained learning patterns both within and across developmental stages,
-respectively.
+Since the seminal work of Stager \& Werker (1997) showing a discrepancy
+between children's speech perception abilities and their word learning
+skills, researchers have debated about the source of such a discrepancy.
+In this work, we were more interested in the development of this
+phenomenon, regardless of its exact origin. Building on some previous
+findings and discussions (Swingley, 2007; Yoshida et al., 2009), we
+proposed a model which assumes that subtle perceptual features are
+correctly encoded during word meaning learning, but that the precision
+of this encoding vary across development. We compared the predictions to
+new data which we collected from preschool children and adults. We found
+that the probabilistic model captured not only the patterns of
+development, but also various learning patterns within the same age
+group.
 
-Besides accounting for previous findings, our model made a new
-prediction: learning similar words is not only modulated by to
+The model made a new prediction which we tested experimentally for the
+first time: learning similar words is not only modulated by to
 similarity of their phonological forms, but also by the visual
@@
 similarity is an early organizing feature in the semantic domain (e.g.,
-Wojcik \& Saffran, 2013), our finding suggest that children may
-prioritize the acqusition of words that are quite distant in the
+Wojcik \& Saffran, 2013), our finding suggests that children may
+prioritize the acquisition of words that are quite distant in the
 semantic space. This suggestion is supported by recent findings based on
@@
 
-Our model can be seen as an ideal observer (Anderson, 1990) in the sense
-that it provides a precise charaterization of the task, and shows how
-information can used optimally to perform this task. In our case, the
-input is categorized with uncertainty, thus the model performs an
-optimal probabilistic (Bayesian) inference, combining cues from both the
-sound and the semantic referents. Crucially, we assume the degree of
-this uncertainty to vary across development. Thus, although children and
-adults appear to behave differently, they are both near-optimal with
-resprect to their own encoding's uncertainty. Note that our model is
-agnostic as to the precise source of this uncertainty: part of it maybe
-due to ambiguous phonological boundaries ({\textbf{???}}), and another
-part could be due to various task demands ({\textbf{???}}).
-
-To conclude, this study proposed a model of novel word is compatible
-with the hypothesis according to which development is not so much about
-a qualitative cognitive change as much as it is about the quantitative
-refinement of similar skills acrss the lifespan (Pajak et al., 2016;
-Swingley, 2007; Yoshida et al., 2009).
+To conclude, this paper proposes a computational model for the
+probabilistic/continuous account, and the findings do endorse this
+account as a valid framework for the study of similar word learning and
+the mechanism of its development. More generally, together with previous
+modeling efforts (e.g., Apfelbaum \& McMurray, 2011; Hofer \& Levy,
+2017), our work highlight the crucial role computation models can play
+in theory building through both a compact organization of existing
+knowledge and through generating new principled hypothesis.
 
@@
 \hypertarget{refs}{}
-\hypertarget{ref-anderson1990}{}
-Anderson, J. R. (1990). \emph{The adaptive character of thought}.
-Hillsdale, NJ: Erlbaum.
+\hypertarget{ref-apfelbaum2011}{}
+Apfelbaum, K., \& McMurray, B. (2011). Using variability to guide
+dimensional weighting: Associative mechanisms in early word learning.
+\emph{Cognitive Science}, \emph{35}(6).
 
@@
 \hypertarget{ref-rost2009}{}
-Rost, G. C., \& McMurray, B. (2009). Speaker variability augments
+Rost, G., \& McMurray, B. (2009). Speaker variability augments
 phonological processing in early word learning. \emph{Developmental

### 2019-01-29 Analysis/process.Rmd
second draft cogsci

--- 2018-12-28 Analysis/process.Rmd
@@
 library(lme4)
+library(nlstools)
+library(MuMIn)
 library(purrr)
@@
 
-d_sim_transform <-  d_sim_summary %>%
-  mutate(normalized =ifelse(condition=='sound_real', mean/0.926, mean)) %>% #Here I only normalize sounds, objects are already normalized
-  filter(distance != "iden") %>%
-  mutate(mydist = ifelse(distance=="0.6", 1, myscale))%>% # Here I create a ligne for different which were not explicitly asked from participants because it was used as a prototype, thus dist=1
+d_sim_process <- d_sim_summary %>%
+  bind_rows(data.frame(condition="obj_real", distance="1", mean= 1, lower=1,upper=1)) %>%
+  mutate(stimuli = ifelse(condition =='obj_real','objects','sounds')) %>%
+  filter(distance != "iden",
+         distance != "0.6") %>%
   mutate(labels = ifelse(distance=='0.1','similar', 
@@
                                 ifelse(distance=='sim','similar',
-                                       ifelse(distance=='med','intermediate', 'different')))))
+                                       ifelse(distance=='med','intermediate', 'different'))))) %>%
+  select(-condition, -distance)
 
-#d_sim_summary$distance <- factor(sum_child$concept_dist, levels = c("similar", "different"))
-#sum_child$sound_dist <- factor(sum_child$sound_dist, levels = c("similar", "different"))
+d_sim_process$labels <- factor(d_sim_process$labels, levels = c("similar","intermediate","different"))
 
-ggplot(d_sim_transform, 
-      aes(x = labels, y = mydist, col=condition)) +
-  geom_point()+
-  #geom_pointrange(aes(ymin = lower, ymax = upper), 
-     #            position = position_dodge(width = .1)) + 
-  xlab("Distance") +ylab("rating")+
+feather::write_feather(d_sim_process, "../saved_data/d_sim_process.feather")
+
+#d_sim_transform <-  d_sim_summary %>%
+#  mutate(normalized =ifelse(stimuli=='sounds', mean/0.926, mean))  #Here I only normalize sounds, objects are already normalized
+
+ggplot(d_sim_process, 
+      aes(x = labels, y = mean, group = factor(stimuli), col=factor(stimuli))) +
+  #geom_point(size=2)+
+  geom_line()+
+  geom_pointrange(aes(ymin = lower, ymax = upper), 
+                 position = position_dodge(width = .1),
+                 size=0.2) + 
+  scale_colour_discrete(name="Stimuli")+
   theme_few()+
@@
 
+#Combine both  
+data_both_ch <- data_ch %>%
+  select(ID, c_dist, s_dist, item_object, item_sound, iscorrect) %>%
+  mutate(age = -1)
+
+data_both_ad <- data_ad %>%
+  select(ID, c_dist, s_dist, concept, sound,iscorrect) %>%
+  rename(item_object = concept,
+         item_sound = sound) %>%
+  mutate(age = 1)
+
+data_both <- data_both_ch %>%
+  bind_rows(data_both_ad)
+
 #Maximal random structure
@@
                glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+model_both <- glmer(iscorrect ~ s_dist * c_dist * age+ 
+                 (s_dist * c_dist  | ID) + 
+                 (c_dist | item_object) + 
+                 (s_dist | item_sound) +
+                 (s_dist * c_dist | age), 
+               data = data_both, family = binomial(),
+               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+stargazer(model_ch, model_ad, 
+          column.labels = c("Children","Adults"),
+          model.numbers=FALSE,
+          intercept.bottom = FALSE,
+          covariate.labels=c("(Intercept)","Sound ","Object","Sound x Object"),
+          no.space=TRUE,
+          single.row=TRUE,
+          star.cutoffs =c(0.05, 0.01, 0.001),
+          digits=2,
+          omit.stat = "all",
+          table.layout ="-c-!t-n",
+          header=FALSE,
+          #notes=c("[0.*]","[0.**]"),
+          title="Estimates of predictor coefficients (and their standard errors) by age group in the regression model")
 
@@
 
-model2_val <- add_rownames(as.data.frame(confint2(fit_children_2)), "param") %>%
+model2_val <- tibble::rownames_to_column(as.data.frame(confint2(fit_children_2)), "param") %>%
   mutate(val= ifelse(param=='Vr_s',Vr_s_ch, Vr_o_ch),
@@
          group = "children") %>%
-  bind_rows(add_rownames(as.data.frame(confint2(fit_adults_2)), "param") %>%
+  bind_rows(tibble::rownames_to_column(as.data.frame(confint2(fit_adults_2)), "param") %>%
               mutate(val= ifelse(param=='Vr_s',Vr_s_ad, Vr_o_ad),
@@
 
+#Model comparison
+
+model_comparison <- tibble::rownames_to_column(AIC(fit_adults, fit_adults_2), 'model') %>%
+  bind_rows(tibble::rownames_to_column(AIC(fit_children, fit_children_2), 'model'))
+
 feather::write_feather(model1_val, "../saved_data/values_mod1.feather")       
 feather::write_feather(model2_val, "../saved_data/values_mod2.feather")
+
+feather::write_feather(model_comparison, "../saved_data/model_comparison.feather")
 

### 2019-01-29 cogsci/cogsci.Rmd
second draft cogsci

@@
 ---
-title: "Continuous Development in Learning Similar-sounding Words"
+title: "The role of continuous developmental change in explaining discontinuities in word learning"
 
@@
    - \usepackage{tipa}
+   - \usepackage[rightcaption]{sidecap}
 
@@
 
-    "Stager and Werker (1997) first showed that children's early ability to distinguish similar sounds do not automatically translate into word learning skills.
+    "Cognitive development is often characterized in term of discontinuities.
+Nevertheless, in some cases, this characterization can be problematic and unnecessary.
+In this paper, we show that a phenomenon that appears stage-like, can be well described by a continuous account.
+We used as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
 Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development.
-However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a rather a continuous pattern of development.
-The present study proposes a precise probabilistic model describing how development may proceed in a continuous fashion across the lifespan.
-The purpose of the model is to account for previously documented facts while providing new predictions.
-We collected data from both preschool children and adults, and we showed that the model can explain various patterns of learning both within the same age and across development.
-Our work highlights the role of computational modeling in advancing our understanding of development both through organizing exsinting knowledge and through generating new principled hypotheses."
+However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development.
+Here we propose a precise probabilistic model describing how development may proceed in a continuous fashion across the lifespan.
+The model accounts for previously documented facts and provides new predictions.
+We collected data from preschool children and adults, and we showed that the model can explain various patterns of learning both within the same age and across development.
+The findings suggest that other aspects of cognitive development which are typically thought of as discontinuities, may emerge from simpler, continuous mechanisms."
 
@@
 
-Over the first year of life, children become sensitive to the phonetic variations that are used to distinguish meanings in their native language [@werker1984].
+Cognitive development is sometimes characterized in terms of a succession of discontinuous stages [@piaget1954].
+Such characterization may be problematic as it often renders the study of the learning mechanism quite challenging.
+Indeed, it is unclear how a precise algorithm––whose steps are gradual and logically related––can account for transitions between stages involving qualitatively different representations [e.g., @carey2009].
+
+Nevertheless, at least in some cases, development may only appear to be stage-like.
+This appearance can be due, for example, to the use of a cognitively-demanding task which may mask learning, or to the use of hard statistical thresholding (in particular, p-value < 0.05) which creates a spurious dichotomy between success and failure in observing a given behavior.
+In such cases, positing discontinuous stages is unnecessary.
+Instead, as we shall see in this paper, a continuous model––involving similar representations across the lifespan––may provide a simpler and more transparent account of development.
+
+We use a case study from word learning literature.
+@stager1997 first showed that children's early ability to distinguish similar sounds ("dih" vs.
+"bih") does not automatically translate into word learning skills (i.e., associating these sounds with different meanings).
+Subsequent research has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017;  @rost2009].
+
+In this work we focus, rather, on the development of this phenomenon.
+In fact, regardless of the exact explanation, it is generally accepted that by around 17 m.o, children succeed in the same task [@werker2002].
+How does development proceed?
+Early accounts assumed that children encode words in a binary way: they either fail or succeed in encoding the relevant phonetic details (simultaneously with the meanings).
+This account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.
+
+<!--Over the first year of life, children become sensitive to the phonetic variations that are used to distinguish meanings in their native language [@werker1984].
 One could imagine that these perceptual skills would be automatically applied to the task of word learning.
-However, developmental data show that 14 m.o children find it challenging to associate minimally different (but perceptually discriminated) sounds such as "bin" and "din" to different objects [@stager1997].
+However, developmental data show that 14 m.o children find it challenging to associate minimally different (but perceptually discriminated) sounds such as "bih" and "dih" to different objects [@stager1997].
+-->
 
-Several factors can explain this finding.
+<!--can explain this finding.
 For example it is possible that the task of meaning learning increases cognitive demands on children (compared to a simple perceptual discrimination).
@@
 Additional difficulty might arise from ambiguous phonological boundaries at this stage of development [e.g., @rost2009], or from uncertainty about the referential status of the novel word [@fennell2010].
+-->
 
-Regardless of the exact explanation, it is generally accepted that by around 17 m.o, children succeed in the same task [@werker2002].
-What could be the mechanism of development?
-Early accounts assumed–whether implicitly or explicitly– that children encode words in a binary way: they either fail or succeed in encoding the relevant phonetic details (simultaneously with the meanings).
-This account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.
-
-Nevertheless, subsequent findings suggest otherwise.
-On the one hand, 14-month-olds–who typically fail in the original task–succeed when an easier *testing* method is used, even under the same *learning* conditions [@yoshida2009].
+Nevertheless, subsequent findings have suggested otherwise.
+On the one hand, 14-month-olds–who typically fail in the original task–succeed when an easier testing method is used, even under the same learning conditions [@yoshida2009].
 They also succeed when uncertainty is mitigated via disambiguating cues [e.g., @thiessen2007].
@@
 Development is a continuous process whereby the initial noisy representations become more precise.
-Crucially, more precise representation are still imperfect: Even with adults show low accuracy learning when the sounds are subtle enough, e.g., non-native sounds [@pajak2016].
+Crucially, more precise representation are still imperfect: Even adults show low accuracy learning when the sounds are subtle enough, e.g., non-native sounds [@pajak2016].
 
 We provide an intuitive illustration of how such an account explains patterns of learning and development in Figure \ref{fig:illus}.
-We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty/tolerance with which these labels are encoded.
+We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty with which these labels are encoded.
 For example, in Stager and Werker's original experiment, children are supposed to associate label 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
-Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large tolerance of the encoding.
+Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large uncertainty of the encoding.
 
-Accuracy in word learning increases when the perceived distance between the labels is large relative to the tolerance of their encoding.
-This improvement can occur in the same developmental stage if the perceptual distance between labels is enhanced through using different-sounding labels (e.g., "lif" vs.
-"neem" instead of "bih" and "dih") or through using additional cues [@thiessen2007; @rost2009].
-Besides, accuracy can improve across development through the refinement of the encoding.
-
+According to this account, accuracy in word learning improves if we increase either the perceptual distinctiveness of the stimuli (e.g., through using different-sounding labels), or the precision of the encoding itself (e.g., across development).
 Building on this intuition, the current work proposes a precise probabilistic model, which we use to both account for previous experimental findings, and to make new predictions that have not been tested before.
 Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.
+
+<!-- "lif" vs. "neem" instead of "bih" and "dih" -->
 
@@
 
-illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Disambig.') %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Disambig.')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambig.')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambig.')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Develop.')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Develop.')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Develop.')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Develop.'))
+illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Distinctiveness') %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Distinctiveness')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Distinctiveness')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Distinctiveness')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Precision')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Precision')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Precision')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Precision'))
 
 illustration$case <- factor(illustration$case, levels = c("low accuracy", "high accuracy"))
-illustration$type <- factor(illustration$type, levels = c("Disambig.", "Develop."))
+illustration$type <- factor(illustration$type, levels = c("Distinctiveness", "Precision"))
 
@@
 
-illus_plot <- ggplot(illustration, aes(x=x, y=y, linetype=rep)) + 
+```
+
+```{r fig.width=2, fig.height=2.5}
+illus_plot <- ggplot(illustration, aes(x=x, y=y, col=rep)) + 
   geom_line() + 
@@
       axis.title = element_text(size = 9),
-      aspect.ratio = 0.5
+      aspect.ratio = 0.7
       )+
@@
   geom_text(aes(label=paste("Acc=", prob, sep="")),
-            x=1.7, y=1, size=2.5, 
-            data=probs)+
+            x=1.7, y=1, size=3, 
+            data=probs, 
+            col='black')+
   xlab("Perceptual space") + ylab("Prob") +
@@
 ```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
-Two words are represented as distributions over the perceptual space.
-Here accuracy expresses the extent to which a given sound instance indicates the word on the left (red bar), as opposed to the word on the right (green bar).
-The values vary between 0.5 (total overlap between the distributions) and 1 (no overlap).
-Accuracy is low when the perceptual distance between labels is small relative to the variance.
-Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development)."}
+A word is represented with a distribution over the perceptual space (indicated in red or green).
+When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
+The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel)."}
 
-illus_plot
+img <- png::readPNG("figs/illustration.png")
+grid::grid.raster(img)
 ```
@@
 # Model
-
-## Task
-
-We model the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009.
-In this task, participants are first exposed to the association between pairs of nonsense words (e.g., "lif"/"neem") and pairs of objects.
-After this exposure phase, participants perform a series of two-alternative forced choices.
-In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
-An overview of the task is shown in Figure \ref{fig:task}.
 
@@
 -->
-
-```{r task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:task}An overview of the task used in this study."}
-
-img <- png::readPNG("figs/task.png")
-grid::grid.raster(img)
-
-```
 
@@
 Finally, the label was physically instantiated by the sound $s$.
+
+\begin{SCfigure}
+\centering
+\includegraphics[width=1.5in]{figs/model.png}
+\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters.}
+\label{fig:model}
+\end{SCfigure}
 
@@
 
-## Simulations
-
-<!--If we denote the correct/target object as $o_T$ and the incorrect object as $o_{\lnot T}$, then the probability of chosing the correct object is: $P(o_T|s_T) = $ -->
-
-During the testing phase (see Figure \ref{fig:task}), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and with both objects $o_1$ and $o_2$.
-In order to make a choice, we need to determine which object is more probable under the target sound $s_T$.
-In other words, we need to compare the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$.
-The values of these probabilities can be computed by summing over all possible concepts and labels:
+## Inference
+<!--If we denote the correct/target object as $o_T$ and the incorrect object as $o_{\lnot T}$, then the probability of chosing the correct object is: $P(o_T|s_T) = $ 
+(see Figure \ref{fig:task})
+-->
+The learner hears a sound $s$ and has to decided which object $o$ provides an optimal match to this sound.
+To this end, the learner has to compute the probability $P(o|s)$ for all possible objects.
+This probability can be computed by summing over all possible concepts and labels:
 $$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
-The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in Figure \ref{fig:model}:
+The joint probability $P(o, C, L, s_T)$ is obtained by factoring the Bayesian network in Figure \ref{fig:model}:
 $$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
@@
 
-$$
+\begin{equation}
 P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-$$
-
-From this general expression we derive the exact analytical formula, which expresses the probability of accurate responses in the testing phase of the task:
-
-\begin{equation}
-P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
 \end{equation}
 
-```{r model, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
+<!--
+```{r model, fig.env = "figure", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
 Circles indicate random variables (shading indicates observed variables).
@@
 ```
+-->
 
-In order to have a more quantitative understanding of the model, we simulate the values of the predicted accuracy (Expression 1) as a function of the perceptual distance between the sounds $\Delta s$.
-We used as parameters the two remaining variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the distributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, are assumed to have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
-The simulations are shown in Figure \ref{fig:simulation}.
+## Task and model predictions
+
+```{r task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:task}An overview of the task used in this study."}
+
+img <- png::readPNG("figs/task.png")
+grid::grid.raster(img)
+
+```
+
+We use the model to predict performance in the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009.
+In this task, participants are first exposed to the association between pairs of nonsense words (e.g., "lif"/"neem") and pairs of objects.
+After this exposure phase, participants perform a series of test trials.
+In each of these trials, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
+An overview of the task is shown in Figure \ref{fig:task}.
+
+We use the general Equation 1 to derive the exact analytical expression for the probability of accurate responses $p(o_T | s)$ (target object $o_T$ given a sound $s$) in the simple case of two-alternative forced choice in the testing phase of our experimental task:
+
+\begin{equation}
+P(o_T|s)= \frac{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}}{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}+ e^{-\Delta s^2 /2\sigma_L^2} + e^{-\Delta o^2 /2\sigma_C^2 }}
+\end{equation}
+
+Figure \ref{fig:simulation} show simulations of the predicted accuracy (Expression 2) as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the precision parameter, i.e., the variance of the distributions $p(s| L)$ and $p(o | C)$ (which, for ease of the simulations' interpretation, are assumed to have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
+
+```{r, echo=FALSE}
+pdf.options(encoding='CP1250')
+```
+
 ```{r }
@@
 #Import data from saved
-simulations <- feather::read_feather("../saved_data/simulations.feather")
+simulations <- feather::read_feather("../saved_data/simulations.feather") %>%
+  mutate(obj = ifelse(object_distance == "0.25", "\u0394o = 0.25",
+                      ifelse(object_distance == "0.5","\u0394o = 0.5",
+                             "\u0394o = 1")))
 
@@
       legend.text=element_text(size=11),
-      axis.text = element_text(size = 11),
+      axis.text = element_text(size = 8),
       aspect.ratio = 0.7
@@
   geom_hline(yintercept = 0.50, linetype="dashed") +
-  xlab("sound distance") + ylab("Prob. accurate") +
-  facet_grid(.~object_distance)
+  xlab(expression(Delta*"s")) + ylab(expression("P("*o['T']*"| s)")) +
+  facet_grid(.~obj) +
+  #facet_grid(.~object_distance) +
+  scale_color_discrete(name = expression(sigma))
 
-#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
+ggsave('simulations.png', plot = plot_simulation, width = 7, height = 2)
+#ggsave('simulations.png', plot = plot_simulation)
+```
+
+```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, sanitize=FALSE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ (x-axis) and $\\Delta o$ (different panels) and representation precision $\\sigma$ (color).
+Dashed line represents chance."}
+#plot_simulation
+#ggsave(plot_simulation, filename = 'simulations.png')
+img <- png::readPNG("simulations.png")
+grid::grid.raster(img)
 
@@
 
-```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase, as a function the perceptual distance between the sounds.
-Colors indicate different values of the standard deviation which we assume is common to both the labels' and concepts' probabilistic representations.
-Panels represent graphs using different values of the visual distance between the objects."}
-plot_simulation
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
-
-```
-
-The simulations explain some previousely documented facts, and make new predictions:
+The simulations explain some previously documented facts, and make new predictions:
 
@@
 This is a new prediction that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [@rost2009; @thiessen2007; @dautriche2015; @fennell2010], but no previous study tested the effect of the visual distance between the semantic referents.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [e.g., @fennell2010; @rost2009; @thiessen2007], but no previous study tested the effect of the visual distance between the semantic referents.
 
-To sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
-In the experiment below, we test whether the model makes accurate *quantitative* predictions by fitting it to new experimental data collected from preschool children and adults.
+In sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
+In the experiment below, we test whether the model makes accurate quantitative predictions by fitting it to new experimental data collected from preschool children and adults.
 
@@
 In particular, both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design.
-Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameter, $\sigma$, in the probabilsitic representations.
+Two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameter, $\sigma$, in the probabilistic representations.
+The Experiment and the predictions were pre-registered.
 <!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
@@
 ```{r}
-sim_transform <- feather::read_feather("../saved_data/d_sim_transform.feather")
+sim_transform <- feather::read_feather("../saved_data/d_sim_process.feather")
 
 sim_plot <- ggplot(sim_transform, 
-      aes(x = labels, y = normalized_all, group = factor(stimuli), col=factor(stimuli))) +
-  geom_point(size=2)+
+      aes(x = labels, y = mean, group = factor(stimuli), col=factor(stimuli))) +
+  #geom_point(size=2)+
   geom_line()+
-  #geom_pointrange(aes(ymin = lower, ymax = upper), 
-     #            position = position_dodge(width = .1)) + 
+  geom_pointrange(aes(ymin = lower, ymax = upper), 
+                 position = position_dodge(width = .1),
+                 size=0.2) + 
   scale_colour_discrete(name="Stimuli")+
@@
 
-```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:stim}Normalized distances for both sound and object pairs used in this study."}
+```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:stim}Distances for both sound and object pairs from an adult norming study.
+Error bars represent 95\\% confidence intervals."}
 
@@
   mutate(source = ifelse(key == "human", "Experimental",
-                         ifelse(key == "prediction", "Model 1", "Model 2")))
+                         ifelse(key == "prediction", "Model 1", "Model"))) %>%
+  filter(source != "Model 1")
 
@@
       axis.text = element_text(size = 11)
-      ) + facet_grid(group~source, scales="free_y") +
+      #) + facet_grid(group~source, scales="free_y") +
+      ) + facet_grid(source~group) +
   theme(aspect.ratio = 0.7)
 
-#ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)
+#ggsave("figs/data_all.png", plot = plot_data, width = 3, height = 6)
+#ggsave("figs/data_all.png", plot = plot_data, width = 8, height = 16)
 
@@
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=6, fig.height=12, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
 Adults).
-Experimental results are shown on the left.
-Predictions from Model 1 (one free parameter) and Model 2 (two free parameters) are shown in the middle and on the right, respectively."}
+We show both experimental results (top) and model predictions (bottom).
+Error bars represent 95\\% confidence intervals."}
 plot_data
@@
 
-Preschoolers were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time.
-The experimenter explained that the game consisted in learning some words spoken in an alien planet.
+<!--and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet.
+
 The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task.
-After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition.
+After the introduction and examples,
+-->
+
+Preschoolers were tested at the nursery school using a tablet, whereas adults used their local computers to complete the same experiment online.
+Participants were tested in a sequence of five conditions: the four experimental conditions plus the catch condition.
 In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.
 
-In the exposure trials, children saw two objects associated with their corresponding sounds.
+In the exposure trials, participants saw two objects associated with their corresponding sounds.
 We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound.
@@
 For both objects, visual stimuli were present for the duration of the sound clip (∼800ms).
-In the testing trials, children saw both objects simultaneously and heard only one sound.
+In the testing trials, participants saw both objects simultaneously and heard only one sound.
 They completed the trial by selecting which of the two objects corresponded to the sound.
-They responded by touching one of the pictures on the tablet.
-
 The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence).
@@
 
-The procedure in the adult experiment was identical to that of preschool children, except that preschoolers were accompanied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.
-
-### Model fitting
-
-We fit the probability function (equation 2) to the participants' responses in each age group.
-The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \ref{fig:stim}).
-We used two models: \textbf{model 1} fit only one parameter ($\sigma = \sigma_C =\sigma_L$), and \textbf{model 2} fit two parameters ($\sigma_C  \neq \sigma_L$).
-The values of the parameters were derived using weighted least-squares estimates.
-
 ## Results
-
-We first analyzed the experimental results shown in Figure (\ref{fig:data_all}, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects structure [@barr2013].
-Results are shown in Table 1.
-We found a main effect of sound distance on the accuracy of learning in both children and adults, thus replicating previous findings.
-We also found a main effect of object distance, thus confirming the new prediction of our model.
 
@@
 
-data_child <- feather::read_feather("../saved_data/data_child.feather") %>%
+data_ch <- feather::read_feather("../saved_data/data_child.feather") %>%
   mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
          c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
-  rename(Accuracy = iscorrect)
-data_adult <- feather::read_feather("../saved_data/data_adult.feather") %>%
+  rename(accuracy = iscorrect)
+data_ad <- feather::read_feather("../saved_data/data_adult.feather") %>%
   mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
          c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
-  rename(Accuracy = iscorrect)
+  rename(accuracy = iscorrect)
 
-model_ch <- glmer(Accuracy ~ s_dist * c_dist + 
+#Combine both  
+data_both_ch <- data_ch %>%
+  select(ID, c_dist, s_dist, item_object, item_sound, accuracy) %>%
+  mutate(age = -1)
+
+data_both_ad <- data_ad %>%
+  select(ID, c_dist, s_dist, concept, sound, accuracy) %>%
+  rename(item_object = concept,
+         item_sound = sound) %>%
+  mutate(age = 1) %>%
+  mutate(ID2 = sub("+$", "_ad", ID)) %>%
+  select(-ID) %>%
+  rename(ID=ID2)
+
+data_both <- data_both_ch %>%
+  bind_rows(data_both_ad)
+
+model_both <- glmer(accuracy ~ s_dist * c_dist * age+ 
                  (s_dist * c_dist  | ID) + 
                  (c_dist | item_object) + 
-                 (s_dist | item_sound), 
-               data = data_child, family = binomial(),
+                 (s_dist | item_sound) +
+                 (s_dist * c_dist | age), 
+               data = data_both, family = binomial(),
                glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
 
-model_ad <- glmer(Accuracy ~ s_dist * c_dist + 
-                 (s_dist * c_dist  | ID) + 
-                 (c_dist | sound) + 
-                 (s_dist | concept), 
-               data = data_adult, family = binomial(),
-               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+model_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(model_both))), "effect")
 
-stargazer(model_ch, model_ad, 
-          column.labels = c("Children","Adults"),
-          model.numbers=FALSE,
-          intercept.bottom = FALSE,
-          covariate.labels=c("(Intercept)","Sound ","Object","Sound x Object"),
-          no.space=TRUE,
-          single.row=TRUE,
-          star.cutoffs =c(0.05, 0.01, 0.001),
-          omit.stat = "all",
-          table.layout ="-c-!t-n",
-          header=FALSE,
-          #notes=c("[0.*]","[0.**]"),
-          title="Estimates of predictor coefficients (and their standard errors) by age group in the regression model")
+p_val <- function(val) {
+  if(val < 0.001) 
+    {'< 0.001'} 
+  else if(val < 0.01)
+    {'<0.01'} 
+  else if(val < 0.05)
+    {'<0.05'} 
+  else {paste('=', round(val,2))}
+}
+
+s_coef <- round(model_coef$Estimate[which(model_coef$effect=="s_dist")],2)
+s_p = model_coef$'Pr(>|z|)'[which(model_coef$effect=="s_dist")]
+
+c_coef <- round(model_coef$Estimate[which(model_coef$effect=="c_dist")],2)
+c_p = model_coef$'Pr(>|z|)'[which(model_coef$effect=="c_dist")]
+
+age_coef <- round(model_coef$Estimate[which(model_coef$effect=="age")],2)
+age_p = model_coef$'Pr(>|z|)'[which(model_coef$effect=="age")]
+
+c_s_coef <- round(model_coef$Estimate[which(model_coef$effect=="s_dist:c_dist")],2)
+c_s_p = model_coef$'Pr(>|z|)'[which(model_coef$effect=="s_dist:c_dist")]
+
+s_age_coef <- round(model_coef$Estimate[which(model_coef$effect=="s_dist:age")],2)
+s_age_p = model_coef$'Pr(>|z|)'[which(model_coef$effect=="s_dist:age")]
 ```
+
+We first analyzed the experimental results shown in Figure (\ref{fig:data_all}, top), using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) [@barr2013].
+We found main effects for all the fixed effects, i.e., the sound distance ($\beta =$ `r s_coef`, $p$ `r p_val(s_p)`)---replicating previous findings, the object distance ($\beta =$ `r c_coef`, $p$ `r p_val(c_p)`)---confirming the new prediction of our model, and age group ($\beta =$ `r age_coef`, $p$ `r p_val(age_p)`)---showing that performance improves with age.
+Besides, we found two-way interactions between sound and object distances ($\beta =$ `r c_s_coef`, $p$ `r p_val(c_s_p)`) and between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`).
 
@@
 
+#Model comparison
+model_comparison <- feather::read_feather("../saved_data/model_comparison.feather")
+
+diff_adults <- model_comparison$AIC[which(model_comparison$model=='fit_adults_2')] - model_comparison$AIC[which(model_comparison$model=='fit_adults')]
+
+diff_children <- model_comparison$AIC[which(model_comparison$model=='fit_children_2')] - model_comparison$AIC[which(model_comparison$model=='fit_children')]
+
 ```
 
-Figures (\ref{fig:data_all}, middle and right graphs) show the predictions of the models.
-Both model 1 and model 2 fit reasonably well the experimental data in both children and adults.
-In particular, they both correctly predict the relative recognition accuracy across conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
-Note, however, that both models predict a slight interaction between sounds and objects, but such an interaction was not significant in the the experimental data (Table 1).
+Second, we fit the probability function (Equation 2) to the participants' responses in each age group.
+The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \ref{fig:stim}).
+Thus, the model has two degrees of freedom in each group, i.e., $\sigma_C$ and $\sigma_L$.
+Figure \ref{fig:data_all} (bottom) show the predictions of the model.
+The model correctly predicts the relative recognition accuracy across conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
+At the quantitative level, the models explained almost all the variance in the participants' mean responses ($R^2=$ `r R2_model2`).
 
+We also fit a simplified model with only one degree of freedom ($\sigma = \sigma_C =\sigma_L$).
+This second model is not intended to test any theoretical hypothesis.
+We use it, rather, as a baseline to understand how much of the explanatory power of the model is due to the extra degree of freedom.
+This baseline model still captured the qualitative pattern (graph not shown), and  explained the majority of the variance ($R^2=$ `r R2_model1`).
+Besides, model comparison using Akaike information criterion yielded $AIC(model) - AIC(baseline) =$ `r round(diff_children,2)` for children data and $AIC(model) - AIC(baseline) =$ `r round(diff_adults,2)` for adult data.
+These numbers suggest that the model remains highly predictive even with one degree of freedom.
+<!--
+
+These results suggest 1) the model captures very well the experimental data, and 2) the model remains highly predictive even with one degree of freedom.
+
+Note, however, that both models predict a slight interaction between sounds and objects, but no such interaction was found in the the experimental data (Table 1)\footnote{It is possibe, however, that the absence of interaction is due to uncetainty in the experimental measurements.}
+
+We also fit a simplified model with only one degree of freedom ($\sigma = \sigma_C =\sigma_L$).
+This second model is not intended to test any theoretical hypothethesis.
+We use it, rather, as a baseline to understand how much of the explantory power of the orginal model is due to the extra degree of freedom.
+We call this baseline model the single-variance model (by contrast to the double-variance model).
+Both models were fit using weighted least-squares estimates.
+-->
+
+<!--At the quantitative level, both models explained almost all the variance.
+We obtained $R^2=$ `r R2_model1` for the single-variance model, and $R^2=$ `r R2_model2` for the double-variance model.
+Besides, model comparison using Akaike information criterion yielded $AIC(double) - AIC(single) =$ `r diff_children` for children data and $AIC(double) - AIC(single) =$ `r diff_adults`.
+These numbers suggest 1) the model captures very well the experimental data, and 2) the model remains highly predictive even with one degree of freedom.
+-->
+
+As for the values of the parameters, children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`]\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.}, and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
+Adults had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
+As predicted, the uncertainty parameters were larger for children than they were for adults.
+<!--
 For Model 1, the fitted uncertainty parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
@@
 The model explained the majority of the variance ($R^2=$ `r R2_model1`).
-For model 2, children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
-Adults had a label-specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
-The model explained almost all the variance ($R^2=$ `r R2_model2`).
-Interestingly, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 (which used two degrees of freedom).
+-->
 
@@
 
-Since the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills, researchers have debated about the source of such a discrepancy.
+This paper studies the hypothesis that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion.
+We used as a case study the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills.
+While most previous work debated the source of this discrepancy, here we were more interested in its mechanism of development.
+
+<!--Since the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills, researchers have debated about the source of such a discrepancy.
 In this work, we were more interested in the development of this phenomenon, regardless of its exact origin.
-Building on some previous findings and discussions [@yoshida2009; @swingley2007], we proposed a model which assumes that subtle perceptual features are correctly encoded during word meaning learning, but that the precision of this encoding vary across development.
-We compared the predictions to new data which we collected from preschool children and adults.
-We found that the probabilistic model captured not only the patterns of development, but also various learning patterns within the same age group.
+-->
 
-The model made a new prediction which we tested experimentally for the first time: learning similar words is not only modulated by to similarity of their phonological forms, but also by the visual similarity of their semantic referents.
+Building on some previous findings and discussions [e.g., @swingley2007; @yoshida2009], we proposed a model which assumes that subtle perceptual features are correctly encoded during word meaning learning, but that the precision of this encoding improves across development.
+We tested the model's predictions against data collected from preschool children and adults and we showed that development can be characterized as a continuous refinement in qualitatively similar representations across the life span.
+
+The model made a new prediction which we tested experimentally for the first time: learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
 More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.
@@
 
-To conclude, this paper proposes a computational model for the probabilistic/continuous account, and the findings do endorse this account as a valid framework for the study of similar word learning and the mechanism of its development.
-More generally, together with previous modeling efforts [e.g., @apfelbaum2011; @hofer2017], our work highlight the crucial role computation models can play in theory building through both a compact organization of existing knowledge and through generating new principled hypothesis.
+One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (around 14 month-old).
+While an important conclusion of this paper is that the same process may apply to different developmental stages, it would be interesting to experimentally verify the generality of this conclusion in the context of early language acquisition.
+A challenge to this next step would be to construct a computational framework which would compare performance across heterogeneous testing methods (e.g., looking time vs.
+forced-choice).
 
-<!--Not only does our model predict that both phonological and semantic relatedness matter in learning novel words, it also provides
+To sum, this paper proposes a model that accounts for the development of an important aspect of word learning.
+The findings show that data can be explained based on a continuous process operating over similar representations across development.
+We used a case from word learning as an example, but the same idea might apply to other aspects of cognitive development which are tyipcally thought of as stage-like (e.g., acquisition of a theory of mind).
+A crucial task would be to investigate the extent to which such discontinuities emerge due to genuine qualitative changes, and the extent to which they reflect the granularity of the researchers' own measurement tools.
+<!--
+More generally, our work highlights the crucial role computation models can play in theory building through both a compact organization of existing knowledge and through generating new principled hypothesis.
+
+positing discontinuous stages, as it was shown that development a continuous account as a valid framework for the study of similar word learning and the mechanism of its development.
+More generally, together with previous modeling efforts [e.g., @hofer2017], our work highlight the crucial role computation models can play in theory building through both a compact organization of existing knowledge and through generating new principled hypothesis.
+
+Not only does our model predict that both phonological and semantic relatedness matter in learning novel words, it also provides
 a precise account of *how* these two dimensions interact to predict learning. In fact,-->
@@
 
+<!--
 \vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
@@
 
+-->
 # References

### 2019-01-29 cogsci/cogsci.tex
second draft cogsci

@@
 
-\title{Continuous Development in Learning Similar-sounding Words}
+\title{The role of continuous developmental change in explaining
+discontinuities in word learning}
 
 \usepackage{tipa}
+\usepackage[rightcaption]{sidecap}
 
@@
 \begin{abstract}
-Stager and Werker (1997) first showed that children's early ability to
-distinguish similar sounds do not automatically translate into word
-learning skills. Early explanations proposed that children may not be
-able to encode subtle phonetic contrasts when learning novel word
+Cognitive development is often characterized in term of discontinuities.
+Nevertheless, in some cases, this characterization can be problematic
+and unnecessary. In this paper, we show that a phenomenon that appears
+stage-like, can be well described by a continuous account. We used as a
+case study the finding by Stager and Werker (1997) that children's early
+ability to distinguish similar sounds does not automatically translate
+into word learning skills. Early explanations proposed that children may
+not be able to encode subtle phonetic contrasts when learning novel word
 meanings, thus suggesting a discontinuous/stage-like pattern of
@@
 simpler testing methods) that children do encode such contrasts, thus
-favoring a rather a continuous pattern of development. The present study
-proposes a precise probabilistic model describing how development may
-proceed in a continuous fashion across the lifespan. The purpose of the
-model is to account for previously documented facts while providing new
-predictions. We collected data from both preschool children and adults,
-and we showed that the model can explain various patterns of learning
-both within the same age and across development. Our work highlights the
-role of computational modeling in advancing our understanding of
-development both through organizing exsinting knowledge and through
-generating new principled hypotheses.
+favoring a continuous pattern of development. Here we propose a precise
+probabilistic model describing how development may proceed in a
+continuous fashion across the lifespan. The model accounts for
+previously documented facts and provides new predictions. We collected
+data from preschool children and adults, and we showed that the model
+can explain various patterns of learning both within the same age and
+across development. The findings suggest that other aspects of cognitive
+development which are typically thought of as discontinuities, may
+emerge from simpler, continuous mechanisms.
 
@@
 
-Over the first year of life, children become sensitive to the phonetic
-variations that are used to distinguish meanings in their native
-language (Werker \& Tees, 1984). One could imagine that these perceptual
-skills would be automatically applied to the task of word learning.
-However, developmental data show that 14 m.o children find it
-challenging to associate minimally different (but perceptually
-discriminated) sounds such as ``bin'' and ``din'' to different objects
-(Stager \& Werker, 1997).
+Cognitive development is sometimes characterized in terms of a
+succession of discontinuous stages (Piaget, 1954). Such characterization
+may be problematic as it often renders the study of the learning
+mechanism quite challenging. Indeed, it is unclear how a precise
+algorithm----whose steps are gradual and logically related----can
+account for transitions between stages involving qualitatively different
+representations (e.g., Carey, 2009).
 
-Several factors can explain this finding. For example it is possible
-that the task of meaning learning increases cognitive demands on
-children (compared to a simple perceptual discrimination). In
-particular, it requires paying attention to both the sounds and the
-corresponding objects, which may hinder precise encoding in memory of
-some phonetic details (Hofer \& Levy, 2017; Stager \& Werker, 1997).
-Additional difficulty might arise from ambiguous phonological boundaries
-at this stage of development (e.g., Rost \& McMurray, 2009), or from
-uncertainty about the referential status of the novel word (Fennell \&
-Waxman, 2010).
+Nevertheless, at least in some cases, development may only appear to be
+stage-like. This appearance can be due, for example, to the use of a
+cognitively-demanding task which may mask learning, or to the use of
+hard statistical thresholding (in particular, p-value \textless{} 0.05)
+which creates a spurious dichotomy between success and failure in
+observing a given behavior. In such cases, positing discontinuous stages
+is unnecessary. Instead, as we shall see in this paper, a continuous
+model----involving similar representations across the lifespan----may
+provide a simpler and more transparent account of development.
 
-Regardless of the exact explanation, it is generally accepted that by
-around 17 m.o, children succeed in the same task (Werker, Fennell,
-Corcoran, \& Stager, 2002). What could be the mechanism of development?
-Early accounts assumed--whether implicitly or explicitly-- that children
-encode words in a binary way: they either fail or succeed in encoding
-the relevant phonetic details (simultaneously with the meanings). This
-account suggested a discontinuous/stage-like pattern of development
-whereby younger children fail to encode the contrastive phonetic detail,
-whereas older children succeed.
+We use a case study from word learning literature. Stager \& Werker
+(1997) first showed that children's early ability to distinguish similar
+sounds (``dih'' vs. ``bih'') does not automatically translate into word
+learning skills (i.e., associating these sounds with different
+meanings). Subsequent research has focused on proposing possible
+explanations for this observed gap between speech perception and word
+learning (e.g., Fennell \& Waxman, 2010; Hofer \& Levy, 2017; Rost \&
+McMurray, 2009; Stager \& Werker, 1997).
 
-Nevertheless, subsequent findings suggest otherwise. On the one hand,
-14-month-olds--who typically fail in the original task--succeed when an
-easier \emph{testing} method is used, even under the same
-\emph{learning} conditions (Yoshida, Fennell, Swingley, \& Werker,
-2009). They also succeed when uncertainty is mitigated via
-disambiguating cues (e.g., Thiessen, 2007). On the other hand, adults
-show patterns of learning similar to those shown by 14-month-olds when
-the task is more challenging and when similarity between words increases
-(Pajak, Creel, \& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
+In this work we focus, rather, on the development of this phenomenon. In
+fact, regardless of the exact explanation, it is generally accepted that
+by around 17 m.o, children succeed in the same task (Werker, Fennell,
+Corcoran, \& Stager, 2002). How does development proceed? Early accounts
+assumed that children encode words in a binary way: they either fail or
+succeed in encoding the relevant phonetic details (simultaneously with
+the meanings). This account suggested a discontinuous/stage-like pattern
+of development whereby younger children fail to encode the contrastive
+phonetic detail, whereas older children succeed.
+
+Nevertheless, subsequent findings have suggested otherwise. On the one
+hand, 14-month-olds--who typically fail in the original task--succeed
+when an easier testing method is used, even under the same learning
+conditions (Yoshida, Fennell, Swingley, \& Werker, 2009). They also
+succeed when uncertainty is mitigated via disambiguating cues (e.g.,
+Thiessen, 2007). On the other hand, adults show patterns of learning
+similar to those shown by 14-month-olds when the task is more
+challenging and when similarity between words increases (Pajak, Creel,
+\& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
 
@@
 more precise. Crucially, more precise representation are still
-imperfect: Even with adults show low accuracy learning when the sounds
-are subtle enough, e.g., non-native sounds (Pajak et al., 2016).
+imperfect: Even adults show low accuracy learning when the sounds are
+subtle enough, e.g., non-native sounds (Pajak et al., 2016).
 
@@
 observe low accuracy in word learning when the perceptual distance
-between the labels is small relative to the uncertainty/tolerance with
-which these labels are encoded. For example, in Stager and Werker's
-original experiment, children are supposed to associate label 1
-(``bih'') and label 2 (``dih'') with object 1 and object 2,
-respectively. Though children could learn that the label ``bih'' is a
-better match to object 1 than ``dih'', they could still judge the sound
-``dih'' as a plausible instance of the label ``bih'', thanks to the
-relatively large tolerance of the encoding.
+between the labels is small relative to the uncertainty with which these
+labels are encoded. For example, in Stager and Werker's original
+experiment, children are supposed to associate label 1 (``bih'') and
+label 2 (``dih'') with object 1 and object 2, respectively. Though
+children could learn that the label ``bih'' is a better match to object
+1 than ``dih'', they could still judge the sound ``dih'' as a plausible
+instance of the label ``bih'', thanks to the relatively large
+uncertainty of the encoding.
 
-Accuracy in word learning increases when the perceived distance between
-the labels is large relative to the tolerance of their encoding. This
-improvement can occur in the same developmental stage if the perceptual
-distance between labels is enhanced through using different-sounding
-labels (e.g., ``lif'' vs. ``neem'' instead of ``bih'' and ``dih'') or
-through using additional cues (Rost \& McMurray, 2009; Thiessen, 2007).
-Besides, accuracy can improve across development through the refinement
-of the encoding.
-
-Building on this intuition, the current work proposes a precise
-probabilistic model, which we use to both account for previous
-experimental findings, and to make new predictions that have not been
-tested before. Using new data collected from both preschool children and
-adults, we show that the model can explain various patterns of learning
-both within the same age and across development.
+According to this account, accuracy in word learning improves if we
+increase either the perceptual distinctiveness of the stimuli (e.g.,
+through using different-sounding labels), or the precision of the
+encoding itself (e.g., across development). Building on this intuition,
+the current work proposes a precise probabilistic model, which we use to
+both account for previous experimental findings, and to make new
+predictions that have not been tested before. Using new data collected
+from both preschool children and adults, we show that the model can
+explain various patterns of learning both within the same age and across
+development.
 
@@
 \caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
-Two words are represented as distributions over the perceptual space.
-Here accuracy expresses the extent to which a given sound instance indicates the word on the left (red bar), as opposed to the word on the right (green bar).
-The values vary between 0.5 (total overlap between the distributions) and 1 (no overlap).
-Accuracy is low when the perceptual distance between labels is small relative to the variance.
-Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development).}\label{fig:illus}
+A word is represented with a distribution over the perceptual space (indicated in red or green).
+When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
+The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
 \end{figure}
@@
 \section{Model}\label{model}
-
-\subsection{Task}\label{task}
-
-We model the word learning task introduced by Stager \& Werker (1997),
-and a testing method similar to the one used by Yoshida et al. (2009).
-In this task, participants are first exposed to the association between
-pairs of nonsense words (e.g., ``lif''/``neem'') and pairs of objects.
-After this exposure phase, participants perform a series of
-two-alternative forced choices. In each testing trial, one of the two
-sounds is uttered (e.g., ``lif'') and participants choose the
-corresponding object from the two alternatives. An overview of the task
-is shown in Figure \ref{fig:task}.
-
-\begin{CodeChunk}
-\begin{figure}[t]
-
-{\centering \includegraphics{figs/task-1}
-
-}
-
-\caption{\label{fig:task}An overview of the task used in this study.}\label{fig:task}
-\end{figure}
-\end{CodeChunk}
 
@@
 physically instantiated by the sound \(s\).
+
+\begin{SCfigure}
+\centering
+\includegraphics[width=1.5in]{figs/model.png}
+\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters.}
+\label{fig:model}
+\end{SCfigure}
 
@@
 
-\subsection{Simulations}\label{simulations}
+\subsection{Inference}\label{inference}
 
-During the testing phase (see Figure \ref{fig:task}), participants are
-presented with one target sound \(s_T \in\{s_1, s_2\}\) and with both
-objects \(o_1\) and \(o_2\). In order to make a choice, we need to
-determine which object is more probable under the target sound \(s_T\).
-In other words, we need to compare the probabilities \(P(o_1|s_T)\) and
-\(P(o_2|s_T)\). The values of these probabilities can be computed by
-summing over all possible concepts and labels:
+The learner hears a sound \(s\) and has to decided which object \(o\)
+provides an optimal match to this sound. To this end, the learner has to
+compute the probability \(P(o|s)\) for all possible objects. This
+probability can be computed by summing over all possible concepts and
+labels:
 \[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
-The joint probability \(P(o, C, L, s)\) is obtained by factoring the
+The joint probability \(P(o, C, L, s_T)\) is obtained by factoring the
 Bayesian network in Figure \ref{fig:model}:
@@
 
-\[
+\begin{equation}
 P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-\]
+\end{equation}
 
-From this general expression we derive the exact analytical formula,
-which expresses the probability of accurate responses in the testing
-phase of the task:
-
-\begin{equation}
-P(o_T|s_T)= \frac{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2}}{1 + e^{-(\Delta s^2 + \Delta o^2) /2\sigma^2} + e^{-\Delta s^2 /2\sigma^2} + e^{-\Delta o^2 /2\sigma^2 }}
-\end{equation}
+\subsection{Task and model
+predictions}\label{task-and-model-predictions}
 
@@
 
-{\centering \includegraphics{figs/model-1}
+{\centering \includegraphics{figs/task-1}
 
@@
 
-\caption{\label{fig:model}Graphical representation of our model.
-Circles indicate random variables (shading indicates observed variables).
-The squares indicates fixed model parameters.}\label{fig:model}
+\caption{\label{fig:task}An overview of the task used in this study.}\label{fig:task}
 \end{figure}
@@
 
-In order to have a more quantitative understanding of the model, we
-simulate the values of the predicted accuracy (Expression 1) as a
-function of the perceptual distance between the sounds \(\Delta s\). We
-used as parameters the two remaining variables, i.e., the visual
-distance between the semantic referents \(\Delta o\) and the standard
-deviation of the distributions \(p(s| L)\) and \(p(o | C)\) (which, in
-this simulation, are assumed to have similar values, i.e.,
-\(\sigma =\sigma_C \approx \sigma_L\)). The simulations are shown in
-Figure \ref{fig:simulation}.
+We use the model to predict performance in the word learning task
+introduced by Stager \& Werker (1997), and a testing method similar to
+the one used by Yoshida et al. (2009). In this task, participants are
+first exposed to the association between pairs of nonsense words (e.g.,
+``lif''/``neem'') and pairs of objects. After this exposure phase,
+participants perform a series of test trials. In each of these trials,
+one of the two sounds is uttered (e.g., ``lif'') and participants choose
+the corresponding object from the two alternatives. An overview of the
+task is shown in Figure \ref{fig:task}.
+
+We use the general Equation 1 to derive the exact analytical expression
+for the probability of accurate responses \(p(o_T | s)\) (target object
+\(o_T\) given a sound \(s\)) in the simple case of two-alternative
+forced choice in the testing phase of our experimental task:
+
+\begin{equation}
+P(o_T|s)= \frac{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}}{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}+ e^{-\Delta s^2 /2\sigma_L^2} + e^{-\Delta o^2 /2\sigma_C^2 }}
+\end{equation}
+
+Figure \ref{fig:simulation} show simulations of the predicted accuracy
+(Expression 2) as a function of the distinctiveness parameters
+(\(\Delta s\) and \(\Delta o\)) and the precision parameter, i.e., the
+variance of the distributions \(p(s| L)\) and \(p(o | C)\) (which, for
+ease of the simulations' interpretation, are assumed to have similar
+values, i.e., \(\sigma =\sigma_C \approx \sigma_L\)).
 
@@
 
-\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase, as a function the perceptual distance between the sounds.
-Colors indicate different values of the standard deviation which we assume is common to both the labels' and concepts' probabilistic representations.
-Panels represent graphs using different values of the visual distance between the objects.}\label{fig:simulation}
+\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\Delta s$ (x-axis) and $\Delta o$ (different panels) and representation precision $\sigma$ (color).
+Dashed line represents chance.}\label{fig:simulation}
 \end{figure*}
@@
 
-The simulations explain some previousely documented facts, and make new
+The simulations explain some previously documented facts, and make new
 predictions:
@@
   the effect of several bottom-up and top-down properties in
-  disambiguating similar sounding words (Dautriche, Swingley, \&
-  Christophe, 2015; Fennell \& Waxman, 2010; Rost \& McMurray, 2009;
-  Thiessen, 2007), but no previous study tested the effect of the visual
-  distance between the semantic referents.
+  disambiguating similar sounding words (e.g., Fennell \& Waxman, 2010;
+  Rost \& McMurray, 2009; Thiessen, 2007), but no previous study tested
+  the effect of the visual distance between the semantic referents.
 \end{enumerate}
 
-To sum, we introduced a model that accounts for some qualitative
+In sum, we introduced a model that accounts for some qualitative
 learning patterns observed in previous studies, and makes a new
 prediction. In the experiment below, we test whether the model makes
-accurate \emph{quantitative} predictions by fitting it to new
-experimental data collected from preschool children and adults.
+accurate quantitative predictions by fitting it to new experimental data
+collected from preschool children and adults.
 
@@
 (\(\Delta s\)) and object similarity (\(\Delta o\)) were varied
-simultaneously in a within-subject design. Besides, two age groups
-(preschool children and adults) were tested on the same task to explore
-whether development can be characterized with the uncertainty parameter,
-\(\sigma\), in the probabilsitic representations.
+simultaneously in a within-subject design. Two age groups (preschool
+children and adults) were tested on the same task to explore whether
+development can be characterized with the uncertainty parameter,
+\(\sigma\), in the probabilistic representations. The Experiment and the
+predictions were pre-registered.
 
@@
 
-\caption{\label{fig:stim}Normalized distances for both sound and object pairs used in this study.}\label{fig:stim}
+\caption{\label{fig:stim}Distances for both sound and object pairs from an adult norming study. Error bars represent 95\% confidence intervals.}\label{fig:stim}
 \end{figure}
@@
 Adults).
-Experimental results are shown on the left.
-Predictions from Model 1 (one free parameter) and Model 2 (two free parameters) are shown in the middle and on the right, respectively.}\label{fig:all_data}
+We show both experimental results (top) and model predictions (bottom).
+Error bars represent 95\% confidence intervals.}\label{fig:all_data}
 \end{figure*}
@@
 
-Preschoolers were asked if they would be willing to play a game on a
-tablet with the experimenter and were informed that they could stop
-playing at any time. The experimenter explained that the game consisted
-in learning some words spoken in an alien planet. The experiment began
-with two simple examples (not included in the analysis), and in these
-examples children were given feedback from the experimenter so as to
-make sure they correctly understood the structure of the task. After the
-introduction and examples, children were tested in a sequence of five
-conditions: the four experimental conditions plus the catch condition.
-In each condition, participants saw a first block of four exposure
-trials followed by four testing trials, and a second block of two
-exposure trials (for memory refreshment) followed by an additional four
-testing trials.
+Preschoolers were tested at the nursery school using a tablet, whereas
+adults used their local computers to complete the same experiment
+online. Participants were tested in a sequence of five conditions: the
+four experimental conditions plus the catch condition. In each
+condition, participants saw a first block of four exposure trials
+followed by four testing trials, and a second block of two exposure
+trials (for memory refreshment) followed by an additional four testing
+trials.
 
-In the exposure trials, children saw two objects associated with their
-corresponding sounds. We presented the first object on the left side of
-the tablet's screen simultaneously with the corresponding sound. The
-second sound-object association followed on the other side of the screen
-after 500ms. For both objects, visual stimuli were present for the
-duration of the sound clip (∼800ms). In the testing trials, children saw
-both objects simultaneously and heard only one sound. They completed the
-trial by selecting which of the two objects corresponded to the sound.
-They responded by touching one of the pictures on the tablet.
-
-The object-sound pairings were randomized across participants, as was
-the order of the conditions (except for the catch condition which was
-always placed in the middle of the testing sequence). We also randomized
-the on-screen position (left vs.~right) of the two pictures on each
-testing trial.
-
-The procedure in the adult experiment was identical to that of preschool
-children, except that preschoolers were accompanied by an experimenter
-and used a tablet, whereas adults used their local computers to complete
-the experiment online.
-
-\subsubsection{Model fitting}\label{model-fitting}
-
-We fit the probability function (equation 2) to the participants'
-responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
-were set based on data from the similarity judgment task (Figure
-\ref{fig:stim}). We used two models: \textbf{model 1} fit only one
-parameter (\(\sigma = \sigma_C =\sigma_L\)), and \textbf{model 2} fit
-two parameters (\(\sigma_C \neq \sigma_L\)). The values of the
-parameters were derived using weighted least-squares estimates.
+In the exposure trials, participants saw two objects associated with
+their corresponding sounds. We presented the first object on the left
+side of the tablet's screen simultaneously with the corresponding sound.
+The second sound-object association followed on the other side of the
+screen after 500ms. For both objects, visual stimuli were present for
+the duration of the sound clip (∼800ms). In the testing trials,
+participants saw both objects simultaneously and heard only one sound.
+They completed the trial by selecting which of the two objects
+corresponded to the sound. The object-sound pairings were randomized
+across participants, as was the order of the conditions (except for the
+catch condition which was always placed in the middle of the testing
+sequence). We also randomized the on-screen position (left vs.~right) of
+the two pictures on each testing trial.
 
@@
 We first analyzed the experimental results shown in Figure
-(\ref{fig:data_all}, left), using a mixed-effects logistic regression
-with sound and object distances as fixed effects, and with a maximal
-random effects structure (Barr, Levy, Scheepers, \& Tily, 2013). Results
-are shown in Table 1. We found a main effect of sound distance on the
-accuracy of learning in both children and adults, thus replicating
-previous findings. We also found a main effect of object distance, thus
-confirming the new prediction of our model.
+(\ref{fig:data_all}, top), using a mixed-effects logistic regression
+with sound distance, object distance and age group as fixed effects, and
+with a maximal random effects structure (allowing us to take into
+account the full nested structure of our data) (Barr, Levy, Scheepers,
+\& Tily, 2013). We found main effects for all the fixed effects, i.e.,
+the sound distance (\(\beta =\) 0.68, \(p\) \textless{}
+0.001)---replicating previous findings, the object distance (\(\beta =\)
+0.6, \(p\) \textless{} 0.001)---confirming the new prediction of our
+model, and age group (\(\beta =\) 0.59, \(p\) \textless{}
+0.001)---showing that performance improves with age. Besides, we found
+two-way interactions between sound and object distances (\(\beta =\)
+0.36, \(p\) \textless{}0.05) and between sound distance and age
+(\(\beta =\) 0.37, \(p\) \textless{}0.01).
 
-\begin{table}[!htbp] \centering 
-  \caption{Estimates of predictor coefficients (and their standard errors) by age group in the regression model} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lcc} 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & Children & Adults \\ 
-\hline \\[-1.8ex] 
- (Intercept) & 0.426$^{*}$ (0.199) & 3.114$^{**}$ (1.015) \\ 
-  Sound  & 0.272$^{**}$ (0.100) & 2.320$^{*}$ (0.981) \\ 
-  Object & 0.315$^{*}$ (0.137) & 2.133$^{*}$ (0.952) \\ 
-  Sound x Object & 0.151 (0.097) & 1.821 (0.976) \\ 
- \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.05; $^{**}$p$<$0.01; $^{***}$p$<$0.001} \\ 
-\end{tabular} 
-\end{table}
+Second, we fit the probability function (Equation 2) to the
+participants' responses in each age group. The values of \(\Delta s\)
+and \(\Delta o\) were set based on data from the similarity judgment
+task (Figure \ref{fig:stim}). Thus, the model has two degrees of freedom
+in each group, i.e., \(\sigma_C\) and \(\sigma_L\). Figure
+\ref{fig:data_all} (bottom) show the predictions of the model. The model
+correctly predicts the relative recognition accuracy across conditions:
+the pair of words that differ on both the object and sound levels were
+the easiest to learn, followed by the pairs of words that differ on only
+one level, then the pair of words that are similar on both levels. At
+the quantitative level, the models explained almost all the variance in
+the participants' mean responses (\(R^2=\) 0.96).
 
-Figures (\ref{fig:data_all}, middle and right graphs) show the
-predictions of the models. Both model 1 and model 2 fit reasonably well
-the experimental data in both children and adults. In particular, they
-both correctly predict the relative recognition accuracy across
-conditions: the pair of words that differ on both the object and sound
-levels were the easiest to learn, followed by the pairs of words that
-differ on only one level, then the pair of words that are similar on
-both levels. Note, however, that both models predict a slight
-interaction between sounds and objects, but such an interaction was not
-significant in the the experimental data (Table 1).
+We also fit a simplified model with only one degree of freedom
+(\(\sigma = \sigma_C =\sigma_L\)). This second model is not intended to
+test any theoretical hypothesis. We use it, rather, as a baseline to
+understand how much of the explanatory power of the model is due to the
+extra degree of freedom. This baseline model still captured the
+qualitative pattern (graph not shown), and explained the majority of the
+variance (\(R^2=\) 0.94). Besides, model comparison using Akaike
+information criterion yielded \(AIC(model) - AIC(baseline) =\) -3.79 for
+children data and \(AIC(model) - AIC(baseline) =\) 1.62 for adult data.
+These numbers suggest that the model remains highly predictive even with
+one degree of freedom.
 
-For Model 1, the fitted uncertainty parameter was \(\sigma =\) 0.63
-{[}0.53, 0.73{]}\footnote{95 \% Confidence intervals.} for preschoolers,
-and \(\sigma =\) 0.16 {[}0.12, 0.19{]} for adults. As predicted, the
-uncertainty parameter was larger for children than it was for adults.
-The model explained the majority of the variance (\(R^2=\) 0.94). For
-model 2, children had a label-specific uncertainty of \(\sigma_S =\) 0.9
-{[}0.68, 1.11{]}, and a concept-specific uncertainty of \(\sigma_C =\)
-0.29 {[}0.1, 0.49{]}. Adults had a label-specific noise of
-\(\sigma_S =\) 0.16 {[}0.05, 0.28{]}, and a concept-specific noise of
-\(\sigma_C =\) 0.14 {[}0.05, 0.23{]}. The model explained almost all the
-variance (\(R^2=\) 0.96). Interestingly, despite the fact that Model 1
-used only one degree of freedom, it captures the data variance almost as
-well as Model 2 (which used two degrees of freedom).
+As for the values of the parameters, children had a label-specific
+uncertainty of \(\sigma_S =\) 0.9 {[}0.68,
+1.11{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
+and a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1,
+0.49{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.16
+{[}0.05, 0.28{]}, and a concept-specific uncertainty of \(\sigma_C =\)
+0.14 {[}0.05, 0.23{]}. As predicted, the uncertainty parameters were
+larger for children than they were for adults.
 
@@
 
-Since the seminal work of Stager \& Werker (1997) showing a discrepancy
-between children's speech perception abilities and their word learning
-skills, researchers have debated about the source of such a discrepancy.
-In this work, we were more interested in the development of this
-phenomenon, regardless of its exact origin. Building on some previous
-findings and discussions (Swingley, 2007; Yoshida et al., 2009), we
-proposed a model which assumes that subtle perceptual features are
-correctly encoded during word meaning learning, but that the precision
-of this encoding vary across development. We compared the predictions to
-new data which we collected from preschool children and adults. We found
-that the probabilistic model captured not only the patterns of
-development, but also various learning patterns within the same age
-group.
+This paper studies the hypothesis that some seemingly stage-like
+patterns in cognitive development can be characterized in a continuous
+fashion. We used as a case study the seminal work of Stager \& Werker
+(1997) showing a discrepancy between children's speech perception
+abilities and their word learning skills. While most previous work
+debated the source of this discrepancy, here we were more interested in
+its mechanism of development.
+
+Building on some previous findings and discussions (e.g., Swingley,
+2007; Yoshida et al., 2009), we proposed a model which assumes that
+subtle perceptual features are correctly encoded during word meaning
+learning, but that the precision of this encoding improves across
+development. We tested the model's predictions against data collected
+from preschool children and adults and we showed that development can be
+characterized as a continuous refinement in qualitatively similar
+representations across the life span.
 
 The model made a new prediction which we tested experimentally for the
-first time: learning similar words is not only modulated by to
+first time: learning similar words is not only modulated by the
 similarity of their phonological forms, but also by the visual
@@
 
-To conclude, this paper proposes a computational model for the
-probabilistic/continuous account, and the findings do endorse this
-account as a valid framework for the study of similar word learning and
-the mechanism of its development. More generally, together with previous
-modeling efforts (e.g., Apfelbaum \& McMurray, 2011; Hofer \& Levy,
-2017), our work highlight the crucial role computation models can play
-in theory building through both a compact organization of existing
-knowledge and through generating new principled hypothesis.
+One limitation of this work is that the model was fit to data from
+children at a relatively older age (4-5 years old) than what is
+typically studied in the literature (around 14 month-old). While an
+important conclusion of this paper is that the same process may apply to
+different developmental stages, it would be interesting to
+experimentally verify the generality of this conclusion in the context
+of early language acquisition. A challenge to this next step would be to
+construct a computational framework which would compare performance
+across heterogeneous testing methods (e.g., looking time
+vs.~forced-choice).
 
-\vspace{1em}
-
-\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
-\vspace{1em}
-
-\section{Acknowledgements}\label{acknowledgements}
-
-This work was supported by a post-doctoral grant from the Fyssen
-Foundation, NSF \#1528526, and NSF \#1659585.
+To sum, this paper proposes a model that accounts for the development of
+an important aspect of word learning. The findings show that data can be
+explained based on a continuous process operating over similar
+representations across development. We used a case from word learning as
+an example, but the same idea might apply to other aspects of cognitive
+development which are tyipcally thought of as stage-like (e.g.,
+acquisition of a theory of mind). A crucial task would be to investigate
+the extent to which such discontinuities emerge due to genuine
+qualitative changes, and the extent to which they reflect the
+granularity of the researchers' own measurement tools.
 
@@
 \hypertarget{refs}{}
-\hypertarget{ref-apfelbaum2011}{}
-Apfelbaum, K., \& McMurray, B. (2011). Using variability to guide
-dimensional weighting: Associative mechanisms in early word learning.
-\emph{Cognitive Science}, \emph{35}(6).
-
 \hypertarget{ref-barr2013}{}
@@
 
-\hypertarget{ref-dautriche2015}{}
-Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
-phonological neighbors: Syntactic category matters. \emph{Cognition},
-\emph{143}.
+\hypertarget{ref-carey2009}{}
+Carey, S. (2009). \emph{The origin of concepts}. Oxford University
+Press.
 
@@
 
+\hypertarget{ref-piaget1954}{}
+Piaget, J. (1954). \emph{The construction of reality in the child}. New
+York, NY, US: Basic Books.
+
 \hypertarget{ref-rost2009}{}
@@
 
-\hypertarget{ref-werker1984}{}
-Werker, J., \& Tees, R. (1984). Cross-language speech perception:
-Evidence for perceptual reorganization during the first year of life.
-\emph{Infant Behavior and Development}, \emph{7}.
-
 \hypertarget{ref-werker2002}{}

### 2019-01-29 cogsci/cogsci.Rmd
second draft cogsci

@@
 In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and object pair on a 7-point scale.
-We processed the resulting data so that it can be used in the model.
-We normalized the values with respect to the most distant level, and we scaled them within the range [0,1].
-Processed data are shown in Figure \ref{fig:stim}, for each stimuli group.
+We scaled responses within the range [0,1].
+Data are shown in Figure \ref{fig:stim}, for each stimuli group.
 This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).

### 2019-01-29 cogsci/cogsci.tex
second draft cogsci

@@
 Mechanical Turk evaluated the similarity of each sound and object pair
-on a 7-point scale. We processed the resulting data so that it can be
-used in the model. We normalized the values with respect to the most
-distant level, and we scaled them within the range {[}0,1{]}. Processed
-data are shown in Figure \ref{fig:stim}, for each stimuli group. This
-data will be used in the models as the perceptual distance of sound
-pairs (\(\Delta s\)) and object pairs (\(\Delta o\)).
+on a 7-point scale. We scaled responses within the range {[}0,1{]}. Data
+are shown in Figure \ref{fig:stim}, for each stimuli group. This data
+will be used in the models as the perceptual distance of sound pairs
+(\(\Delta s\)) and object pairs (\(\Delta o\)).
 

### 2019-01-29 switch_adults.js
new adult experiment

@@ -206,22 +206,21 @@ var sound_similar =[
 var sound_different=[
     
     //["aba_ada", "ada_aba", "aba", "ada"],
-    ["asa_asha", "asha_asa", "asa", "asha"],
+    ["aba_ada", "ada_aba", "aba", "ada"],
     ["aka_ama", "ama_aka", "aka", "ama"]
 ]
 
 var sound_similar_rand = shuffleArray(sound_similar)
 var sound_different_rand = shuffleArray(sound_different) 
 
-var sound_training = ["aba_ada", "ada_aba", "aba", "ada"]
+var sound_training = ["asa_asha", "asha_asa", "asa", "asha"]
 
-var sound_catch =  ["aba_ada", "ada_aba", "aba", "ada"]
+var sound_catch =  ["asa_asha", "asha_asa", "asa", "asha"]
 
 var sound_cluster1 = [
     [sound_similar[0], 'similar'],
     [sound_different[0], 'different']
 ]
-
 
 
 var sound_cluster2 = [

### 2019-01-30 switch_adults.js
modif exp adults

@@ -877,6 +877,7 @@ var experiment = {
     age:[],
     gender:[],
     native:[],
+    second:[],
     problem:[],
     ifproblem:[],
     comment:[]
@@ -967,7 +968,7 @@ var experiment = {
             experiment.brief.gender.push(document.getElementById("gender").value);
             experiment.brief.native.push(document.getElementById("native").value);
                 
-            experiment.brief.native.push(document.getElementById("second").value);
+            experiment.brief.second.push(document.getElementById("second").value);
             experiment.brief.problem.push(document.getElementById("problem").value);
             experiment.brief.ifproblem.push(document.getElementById("ifproblem").value);
                 

### 2019-01-31 Analysis/process.Rmd
specify sample size for adult data
modif exp adults
second version cogsci

@@
 
+Sample size:
+The following are the analysese done with adult pilot data.
+We plan to collect data from 60 participants on Amazaon MTurk.
+
 Adult data.
@@
 
-d_adult <- read_delim("adult_pilot_3.txt", delim = " ")  %>%
-  filter(type == "Test") %>%
+#The following is a test with adult pilot data
+d_adult <- read_delim("adults_final.txt", delim = " ")  %>%
+#d_adult <- read_delim("adult_pilot_3.txt", delim = " ")  %>%
+  filter(type == "Test", #Here I will  filter out particiapants whose first language is arabic or hindi
+         other != "yes") %>%
   mutate(iscorrect=ifelse(answer==correct, 1, 0))
@@
       axis.text = element_text(size = 11)
-      ) #+ facet_grid(. ~ block)+
+      ) #+ facet_grid(. ~ block)
 
@@
 
-fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.1, Vr_o=0.04), lower=c(0,0), algorithm="port")
+fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.1, Vr_o=0.1), lower=c(0,0), algorithm="port")
 
@@
 
-ggplot(model_data_plot, 
-#ggplot(subset(model_data_plot, group=='children'),
-      aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
+ggplot(subset(model_data_plot, key == "human"), 
+      aes(x = sound_dist, y = value, 
+          group = factor(concept_dist), 
+          col = factor(concept_dist)
+          )) +
   #geom_point()+
@@
   geom_line() + 
+  geom_line(data=subset(model_data_plot, key == "prediction_2"), linetype=2, size=0.5, col='black')+
+  geom_point(data=subset(model_data_plot, key == "prediction_2"), size=1, col='black')+
   geom_hline(yintercept = 0.50, linetype="dashed") +
@@
       axis.text = element_text(size = 11)
-      ) + facet_grid(group~key, scales="free_y") +
+      ) + facet_grid(.~group) +
   theme(aspect.ratio = 0.7)

### 2019-01-31 cogsci/cogsci.Rmd
second version cogsci

@@
 ---
-title: "The role of continuous developmental change in explaining discontinuities in word learning"
+title: "Continuous developmental change can explain discontinuities in word learning"
 
@@
 
-    "Cognitive development is often characterized in term of discontinuities.
-Nevertheless, in some cases, this characterization can be problematic and unnecessary.
-In this paper, we show that a phenomenon that appears stage-like, can be well described by a continuous account.
-We used as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
+    "Cognitive development is often characterized in term of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
+To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
 Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development.
 However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development.
-Here we propose a precise probabilistic model describing how development may proceed in a continuous fashion across the lifespan.
+Here we propose a probabilistic model describing how development may proceed in a continuous fashion across the lifespan.
 The model accounts for previously documented facts and provides new predictions.
 We collected data from preschool children and adults, and we showed that the model can explain various patterns of learning both within the same age and across development.
-The findings suggest that other aspects of cognitive development which are typically thought of as discontinuities, may emerge from simpler, continuous mechanisms."
+The findings suggest that major aspects of cognitive development that are typically thought of as discontinuities, may emerge from simpler, continuous mechanisms."
 
@@
 Cognitive development is sometimes characterized in terms of a succession of discontinuous stages [@piaget1954].
-Such characterization may be problematic as it often renders the study of the learning mechanism quite challenging.
-Indeed, it is unclear how a precise algorithm––whose steps are gradual and logically related––can account for transitions between stages involving qualitatively different representations [e.g., @carey2009].
+Although intuitively appealing, stage theories can be challenging to integrate with theories of learning, which typically posit that knowledge and skills improve incrementally with experience.
+Indeed, one of the central challenges of cognitive development has been to explain transitions between stages which appear to be qualitatively different [@carey2009].
 
 Nevertheless, at least in some cases, development may only appear to be stage-like.
-This appearance can be due, for example, to the use of a cognitively-demanding task which may mask learning, or to the use of hard statistical thresholding (in particular, p-value < 0.05) which creates a spurious dichotomy between success and failure in observing a given behavior.
+This appearance can be due, for example, to the use of a cognitively-demanding task which may mask learning, or to the use of statistical thresholding (in particular, p-value < 0.05) which can create a spurious dichotomy between success and failure in observing a given behavior.
 In such cases, positing discontinuous stages is unnecessary.
-Instead, as we shall see in this paper, a continuous model––involving similar representations across the lifespan––may provide a simpler and more transparent account of development.
+Instead, a continuous model–involving similar representations across the lifespan–may provide a simpler and more transparent account of development.
 
 We use a case study from word learning literature.
-@stager1997 first showed that children's early ability to distinguish similar sounds ("dih" vs.
-"bih") does not automatically translate into word learning skills (i.e., associating these sounds with different meanings).
+@stager1997 first showed that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
+Indeed, though infants around 14-month old can distinguish similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects.
 Subsequent research has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017;  @rost2009].
+In this work we focus, rather, on the mechanism of development.
 
-In this work we focus, rather, on the development of this phenomenon.
-In fact, regardless of the exact explanation, it is generally accepted that by around 17 m.o, children succeed in the same task [@werker2002].
+By around 17 m.o, children succeed in the same task [@werker2002].
 How does development proceed?
@@
 
-Nevertheless, subsequent findings have suggested otherwise.
+Subsequent findings have suggested otherwise.
 On the one hand, 14-month-olds–who typically fail in the original task–succeed when an easier testing method is used, even under the same learning conditions [@yoshida2009].
@@
 
-These evidence point towards another scenario, where the representations are encoded in a probabilistic (rather than binary) way, and where development is continuous, rather than stage-like [@swingley2007; @yoshida2009; @pajak2016].
+This pattern of evidence points towards another scenario, where the representations are encoded in a probabilistic (rather than binary) way, and where development is continuous, rather than stage-like [see also @swingley2007].
 On this account, correct representations are learned early in development, but these representations are encoded with higher uncertainty in younger children, leading to apparent failure in relatively demanding tasks.
 Development is a continuous process whereby the initial noisy representations become more precise.
-Crucially, more precise representation are still imperfect: Even adults show low accuracy learning when the sounds are subtle enough, e.g., non-native sounds [@pajak2016].
+In addition, more precise representation are still imperfect: Even adults show low accuracy learning when the sounds are subtle, e.g., non-native sounds [@pajak2016].
 
@@
 For example, in Stager and Werker's original experiment, children are supposed to associate label 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
-Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large uncertainty of the encoding.
+Though infants could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large uncertainty of the encoding, and this confusion leads to "failure" in the recognition task.
+According to this account, accuracy in word learning improves if we increase either the perceptual distinctiveness of the stimuli (e.g., through using different-sounding labels), or the precision of the encoding itself (e.g., across development).
 
-According to this account, accuracy in word learning improves if we increase either the perceptual distinctiveness of the stimuli (e.g., through using different-sounding labels), or the precision of the encoding itself (e.g., across development).
-Building on this intuition, the current work proposes a precise probabilistic model, which we use to both account for previous experimental findings, and to make new predictions that have not been tested before.
+Building on this intuition, the current work proposes a probabilistic model, which we use to both account for previous experimental findings, and to make new predictions that have not been tested before.
 Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.
@@
 However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously.
-In our model, we assume there to be ambiguity at the level of both the labels and the concepts.
-For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectively, are normally distributed:
+In our model, we assume that both labels and concepts are observed with a certain amount of perceptual noise, which we assume, for simplicity, that it is captured by a normal distribution:
 
@@
   1 & \text{if  }  i=j \\  
-  0  & \text{if  }  i\neq j 
+  0  & \text{otherwise  }
 \end{cases}
@@
 -->
-The learner hears a sound $s$ and has to decided which object $o$ provides an optimal match to this sound.
+The learner hears a sound $s$ and has to decide which object $o$ provides an optimal match to this sound.
 To this end, the learner has to compute the probability $P(o|s)$ for all possible objects.
@@
 $$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
-The joint probability $P(o, C, L, s_T)$ is obtained by factoring the Bayesian network in Figure \ref{fig:model}:
+The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in Figure \ref{fig:model}:
 $$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
@@
 Finally, assuming that the concepts' prior probability is uniformly distributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation.
-See the stimuli sub-section in the Experiment below.}, we obtain the following expression, where all conditional dependencies are now well defined:
+See the stimuli sub-section in Experiment.}, we obtain the following expression, where all conditional dependencies are now well defined:
 
@@
 -->
-
 ## Task and model predictions
@@
 In this task, participants are first exposed to the association between pairs of nonsense words (e.g., "lif"/"neem") and pairs of objects.
+The word-object associations are introduced sequentially.
 After this exposure phase, participants perform a series of test trials.
@@
 
-Figure \ref{fig:simulation} show simulations of the predicted accuracy (Expression 2) as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the precision parameter, i.e., the variance of the distributions $p(s| L)$ and $p(o | C)$ (which, for ease of the simulations' interpretation, are assumed to have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$).
+Figure \ref{fig:simulation} show simulations of the predicted accuracy (Expression 2) as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the precision parameters, i.e., the variances of the distributions $p(s| L)$ and $p(o | C)$.
+To understand the qualitative behavior of the model, we assumed for simplicity that the precision parameter has similar values in both distributions, i.e., $\sigma =\sigma_C \approx \sigma_L$ (but we will allow those parameters to vary independently in the rest of the paper).
 
@@
 
-```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, sanitize=FALSE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ (x-axis) and $\\Delta o$ (different panels) and representation precision $\\sigma$ (color).
+```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, sanitize=FALSE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ and $\\Delta o$ and representation precision $\\sigma$ (For clarity, we assume here that $\\sigma$=$\\sigma_C$=$\\sigma_L$).
 Dashed line represents chance."}
@@
 This is a new prediction that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [e.g., @fennell2010; @rost2009; @thiessen2007], but no previous study tested the effect of the visual distance between the semantic referents.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [e.g., @fennell2010; @rost2009; @thiessen2007], but to our knowledge no previous study in the literature tested the effect of the visual distance between the semantic referents.
 
-In sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
+<!--In sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
 In the experiment below, we test whether the model makes accurate quantitative predictions by fitting it to new experimental data collected from preschool children and adults.
+-->
 
@@
 In this experiment, we tested participants in the word learning task introduced above (Figure \ref{fig:task}).
-We explored all three parameters of the model.
-In particular, both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design.
-Two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameter, $\sigma$, in the probabilistic representations.
-The Experiment and the predictions were pre-registered.
+More precisely, we explored the predictions related to both distinctiveness and precision.
+Sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design.
+Two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
+The Experiment, sample size, exclusion criteria and the model's main predictions were pre-registered.
 <!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
@@
 
+```{r}
+#Sample size
+
+#Children:
+
+d_child <- read_delim("../Analysis/data_summer_all.txt", delim = " ") %>%
+  filter(type == "Test") %>%
+  filter(age != 6) %>%
+  filter(code != 'test',
+         !is.na(code)) %>%
+  filter(grepl('soph', code)) %>%
+  mutate(iscorrect=ifelse(answer==correct, 1, 0))
+
+d_child_score <- d_child %>%
+  group_by(ID, sound_dist, concept_dist) %>%
+  dplyr::summarise(mean = mean(iscorrect))
+
+#Catch
+d_child_excl <- d_child_score %>%
+  filter(sound_dist == 'catch') %>%
+  ungroup() %>%
+  select(ID, mean) %>%
+  dplyr::rename(score = mean)
+
+d_child_good <- d_child %>%
+  left_join(d_child_excl) %>%
+  filter(score > 0.5) %>%
+  filter(sound_dist != 'catch')
+
+N_all_ch <- d_child %>% distinct(ID) %>% nrow()
+N_good_ch <- d_child_good %>% distinct(ID) %>% nrow()
+
+#Adults
+
+d_adult <- read_delim("../Analysis/adults_final.txt", delim = " ")  %>%
+  filter(type == "Test") %>%
+  mutate(iscorrect=ifelse(answer==correct, 1, 0))
+
+d_adult_lang <- d_adult %>% #Here I will  filter out particiapants whose first language is arabic or hindi
+  filter(other == "yes") %>% distinct(ID) %>% nrow()
+
+d_adult_score <- d_adult %>%
+  group_by(ID, sound_dist, concept_dist) %>%
+  dplyr::summarise(mean = mean(iscorrect))
+
+d_adult_excl <- d_adult_score %>%
+  filter(sound_dist == 'catch') %>%
+  ungroup() %>%
+  select(ID, mean) %>%
+  dplyr::rename(score = mean)
+  #select(ID, score)
+
+d_adult_good <- d_adult %>%
+  left_join(d_adult_excl) %>%
+  filter(other != "yes") %>%
+  filter(score >0.7) %>%
+  filter(sound_dist != 'catch')
+
+N_all_ad <- d_adult %>% distinct(ID) %>% nrow()
+N_good_ad <- d_adult_good %>% distinct(ID) %>% nrow()
+
+```
+
 ## Methods
@@
 ### Participants
-We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
-So far, we collected data from N=47 children (mean age= months, F=).
-An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as was specified in the pre-registration\footnote{https://osf.io/jrh38/}).
-We also collected a sample of N=20 adults on Amazon Mechanical Turk (this is a pilot, I will plan for 60 participants).
-N=2 adult participants were excluded because of low scores on the catch trials (see pre-registration).
-(I still need to write the code that derives these numbers automatically from the data).
+We planned to recruit a sample of N=60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
+So far, we have collected data from n=`r N_good_ch` children.
+An additional n=`r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials.
+We also planned to recruit a sample of N=60 adults on Amazon Mechanical Turk.
+This study used sata from n=`r N_good_ad` adult participants.
+An additional n=`r N_all_ad-N_good_ad` participants were tested but excluded because of low scores on the catch trials (n=`r N_all_ad-N_good_ad-d_adult_lang` ) or because they were familiar with the non-English sound stimuli we used in the adult experiment (n=`r d_adult_lang`).
 
@@
 
-```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:stim}Distances for both sound and object pairs from an adult norming study.
-Error bars represent 95\\% confidence intervals."}
-
-sim_plot
-```
-
 <!--We quantified experimetnally the similarity of sound and object pairs that we generated. 
@@
 "similar" for adults.
-We made this choice because, on the one hand, adults were at ceiling with "different" sounds/objects, and on the other hand, children were at chance with the "similar" sounds/objects.
+We made this choice in the light of pilot studies showing that adults were at ceiling with "different" sounds/objects, and children were at chance with the "similar" sounds/objects.
 That said, this difference in the level of similarity is accounted for in the model through using the appropriate perceptual distance used in each age group (Figure \ref{fig:stim}).
 
-The experiment consisted of four conditions which involved, each, one pair of sounds-objects associations.
-These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design in each age group.
+```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:stim}Distances for both sound and object pairs from an adult norming study.
+Error bars represent 95\\% confidence intervals."}
+
+sim_plot
+```
+The experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
 Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
@@
 
+#plot_data <- ggplot(subset(data_human_model, source =='Experimental'), 
 plot_data <- ggplot(data_human_model, 
-#ggplot(subset(model_data_plot, group=='children'),
       aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
@@
   geom_line() + 
+  #geom_line(data=subset(data_human_model, source == "Model"), linetype=2, size=0.5, col='black')+
+  #geom_point(data=subset(data_human_model, source == "Model"), size=1, col='black')+
   geom_hline(yintercept = 0.50, linetype="dashed") +
   xlab("Auditory similary") +ylab("Accuracy")+
-  scale_colour_discrete(name="Visual similarity")+
+  #scale_colour_discrete(name="Visual similarity")+
   theme_few()+
+  ggthemes::scale_color_ptol(name="Visual similarity")+
 theme(legend.title = element_text(size=11),
@@
 ```
+### Procedure
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=6, fig.height=12, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+<!--and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet.
+
+The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task.
+After the introduction and examples,
+-->
+
+Preschoolers were tested at the nursery school using a tablet, whereas adults used their own computers to complete the same experiment online.
+Participants were tested in a sequence of five conditions: the four experimental conditions plus the catch condition.
+In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.
+
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=6, fig.height=4, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
 Adults).
@@
 ``` 
-
-### Procedure
-
-<!--and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet.
-
-The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task.
-After the introduction and examples,
--->
-
-Preschoolers were tested at the nursery school using a tablet, whereas adults used their local computers to complete the same experiment online.
-Participants were tested in a sequence of five conditions: the four experimental conditions plus the catch condition.
-In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.
-
 In the exposure trials, participants saw two objects associated with their corresponding sounds.
@@
 s_age_p = model_coef$'Pr(>|z|)'[which(model_coef$effect=="s_dist:age")]
+
+c_age_coef <- round(model_coef$Estimate[which(model_coef$effect=="c_dist:age")],2)
+c_age_p = model_coef$'Pr(>|z|)'[which(model_coef$effect=="c_dist:age")]
+
 ```
 
-We first analyzed the experimental results shown in Figure (\ref{fig:data_all}, top), using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) [@barr2013].
-We found main effects for all the fixed effects, i.e., the sound distance ($\beta =$ `r s_coef`, $p$ `r p_val(s_p)`)---replicating previous findings, the object distance ($\beta =$ `r c_coef`, $p$ `r p_val(c_p)`)---confirming the new prediction of our model, and age group ($\beta =$ `r age_coef`, $p$ `r p_val(age_p)`)---showing that performance improves with age.
-Besides, we found two-way interactions between sound and object distances ($\beta =$ `r c_s_coef`, $p$ `r p_val(c_s_p)`) and between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`).
+Experimental results are shown in Figure 6 (top).
+We first analyzed the results using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) [@barr2013].
+We found main effects for all the fixed effects in the regression, i.e., the sound distance ($\beta =$ `r s_coef`, $p$ `r p_val(s_p)`)–replicating previous findings, the object distance ($\beta =$ `r c_coef`, $p$ `r p_val(c_p)`)–confirming the new prediction of our model, and age group ($\beta =$ `r age_coef`, $p$ `r p_val(age_p)`)–showing that performance improves with age.
+Besides, we found two-way interactions between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`) and between object distance and age ($\beta =$ `r c_age_coef`, $p$ `r p_val(c_age_p)`).
 
@@
 
-Second, we fit the probability function (Equation 2) to the participants' responses in each age group.
+Second, we fit our model (using Equation 2) to the participants' responses in each age group.
 The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \ref{fig:stim}).
-Thus, the model has two degrees of freedom in each group, i.e., $\sigma_C$ and $\sigma_L$.
-Figure \ref{fig:data_all} (bottom) show the predictions of the model.
-The model correctly predicts the relative recognition accuracy across conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
+Thus, the model has two degrees of freedom for each group, i.e., $\sigma_C$ and $\sigma_L$.
+Figure \ref{fig:data_all} (bottom) shows the predictions.
+The model captures the qualitative patterns in both age groups: starting from a low accuracy recognition when both the sound and object distances are small, the model correctly predicts an increase in accuracy when either the sound distance or the object distance increases.
+Besides, accuracy is correctly predicted to be maximal when both the sound and object distances are high.
+
+The values of the parameters were as follows.
+Children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`]\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.}, and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
+Adults had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
+As predicted, the uncertainty parameters were larger for children than they were for adults, showing that the probabilsitic representations becomes more refined (that is, $\sigma$ becomes smaller) across development.
+
+The models explained the majority of the variance in the participants' mean responses ($R^2=$ `r R2_model2`, for the combined adult and children's data).
+To investigate whether the model's predictive power is due to overfitting, we fit a simplified version with only one degree of freedom (i.e., a single variance common to both sounds and objects).
+This single-variance model explained as much variance in the mean responses ($R^2=$ `r R2_model1`).
+It also captured the main qualitative patterns (graph not shown), suggesting that the explanatory power of the model is largely due to its structure, rather than its degrees of freedom.
+
+An unexpected outcome was that adult participants deviated slightly from the model's predicted numbers.
+While the model predicted recognition accuracy to be more sensitive to object distance when sound distance is different (and vice-versa), adult participants showed the opposite pattern.
+This deviation is interesting as it suggests that participants adapt their auditory-visual cue integration strategy to the ambiguity of the situation: They are highly sensitive to the presence or absence of disambiguating visual information when sound ambiguity is higher (and vice-versa).
+\footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}
+
+<!--relative recognition accuracy across conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
 At the quantitative level, the models explained almost all the variance in the participants' mean responses ($R^2=$ `r R2_model2`).
+-->
 
-We also fit a simplified model with only one degree of freedom ($\sigma = \sigma_C =\sigma_L$).
+<!--We also fit a simplified model with only one degree of freedom ($\sigma = \sigma_C =\sigma_L$).
 This second model is not intended to test any theoretical hypothesis.
@@
 
-As for the values of the parameters, children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`]\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.}, and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
-Adults had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
-As predicted, the uncertainty parameters were larger for children than they were for adults.
 <!--
@@
 
-This paper studies the hypothesis that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion.
+This paper explored the idea that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion.
 We used as a case study the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills.
-While most previous work debated the source of this discrepancy, here we were more interested in its mechanism of development.
+While most previous work debated the source of this discrepancy, here we were more interested in how it reflects developmental change.
 
@@
 
-Building on some previous findings and discussions [e.g., @swingley2007; @yoshida2009], we proposed a model which assumes that subtle perceptual features are correctly encoded during word meaning learning, but that the precision of this encoding improves across development.
-We tested the model's predictions against data collected from preschool children and adults and we showed that development can be characterized as a continuous refinement in qualitatively similar representations across the life span.
+Building on some previous discussions [e.g., @swingley2007; @yoshida2009], we proposed a model which assumes that subtle perceptual features are correctly encoded during word meaning learning, but that the precision of this encoding varies.
+We tested the model's predictions against data collected from preschool children and adults and we showed that developmental changes in word-object mappings can indeed be characterized as a continuous refinement (reducing the encoding uncertainty) in qualitatively similar representations across the life span.
 
-The model made a new prediction which we tested experimentally for the first time: learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
+The model made a new prediction to which we provided the first experimental test: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
 More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.
@@
 One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (around 14 month-old).
-While an important conclusion of this paper is that the same process may apply to different developmental stages, it would be interesting to experimentally verify the generality of this conclusion in the context of early language acquisition.
+Nonetheless, this choice was related to two measurement difficulties.
+First, model fitting requires several, reliably-measured data points.
+In our case, data collection involved presenting participants with several trials across four conditions in a between-subject design.
+It would have been challenging to obtain these measures with infants.
+Second, the study of infants requires using specific testing methods.
+This fact would have made the quantitative study of development challenging.
+Indeed, it is not clear how data from these methods would directly compare to data collected using more typical methods in older children and adults.
+<!--While an important conclusion of this paper is that the same process may apply to different developmental stages, it would be interesting to experimentally verify the generality of this conclusion in the context of early language acquisition.
 A challenge to this next step would be to construct a computational framework which would compare performance across heterogeneous testing methods (e.g., looking time vs.
 forced-choice).
+-->
+In sum, this paper proposes a model that accounts for the development of an important aspect of word learning.
+The findings show that data can be explained based on a continuous process operating over similar representations across development.
+We used a case from word learning as an example, but the same idea might apply to other aspects of cognitive development that are typically thought of as stage-like (e.g., acquisition of a theory of mind).
+Computational models such as the one proposed here can help us investigate the extent to which such discontinuities emerge due to genuine qualitative changes, and the extent to which they reflect the granularity of the researchers' own measurement tools.
 
-To sum, this paper proposes a model that accounts for the development of an important aspect of word learning.
-The findings show that data can be explained based on a continuous process operating over similar representations across development.
-We used a case from word learning as an example, but the same idea might apply to other aspects of cognitive development which are tyipcally thought of as stage-like (e.g., acquisition of a theory of mind).
-A crucial task would be to investigate the extent to which such discontinuities emerge due to genuine qualitative changes, and the extent to which they reflect the granularity of the researchers' own measurement tools.
 <!--

### 2019-01-31 cogsci/cogsci.tex
second version cogsci

@@
 
-\title{The role of continuous developmental change in explaining
-discontinuities in word learning}
+\title{Continuous developmental change can explain discontinuities in word
+learning}
 
@@
 \begin{abstract}
-Cognitive development is often characterized in term of discontinuities.
-Nevertheless, in some cases, this characterization can be problematic
-and unnecessary. In this paper, we show that a phenomenon that appears
-stage-like, can be well described by a continuous account. We used as a
-case study the finding by Stager and Werker (1997) that children's early
-ability to distinguish similar sounds does not automatically translate
-into word learning skills. Early explanations proposed that children may
-not be able to encode subtle phonetic contrasts when learning novel word
-meanings, thus suggesting a discontinuous/stage-like pattern of
-development. However, later work has revealed (e.g., through using
-simpler testing methods) that children do encode such contrasts, thus
-favoring a continuous pattern of development. Here we propose a precise
-probabilistic model describing how development may proceed in a
-continuous fashion across the lifespan. The model accounts for
-previously documented facts and provides new predictions. We collected
-data from preschool children and adults, and we showed that the model
-can explain various patterns of learning both within the same age and
-across development. The findings suggest that other aspects of cognitive
-development which are typically thought of as discontinuities, may
-emerge from simpler, continuous mechanisms.
+Cognitive development is often characterized in term of discontinuities,
+but these discontinuities can sometimes be apparent rather than actual
+and can arise from continuous developmental change. To explore this
+idea, we use as a case study the finding by Stager and Werker (1997)
+that children's early ability to distinguish similar sounds does not
+automatically translate into word learning skills. Early explanations
+proposed that children may not be able to encode subtle phonetic
+contrasts when learning novel word meanings, thus suggesting a
+discontinuous/stage-like pattern of development. However, later work has
+revealed (e.g., through using simpler testing methods) that children do
+encode such contrasts, thus favoring a continuous pattern of
+development. Here we propose a probabilistic model describing how
+development may proceed in a continuous fashion across the lifespan. The
+model accounts for previously documented facts and provides new
+predictions. We collected data from preschool children and adults, and
+we showed that the model can explain various patterns of learning both
+within the same age and across development. The findings suggest that
+major aspects of cognitive development that are typically thought of as
+discontinuities, may emerge from simpler, continuous mechanisms.
 
@@
 Cognitive development is sometimes characterized in terms of a
-succession of discontinuous stages (Piaget, 1954). Such characterization
-may be problematic as it often renders the study of the learning
-mechanism quite challenging. Indeed, it is unclear how a precise
-algorithm----whose steps are gradual and logically related----can
-account for transitions between stages involving qualitatively different
-representations (e.g., Carey, 2009).
+succession of discontinuous stages (Piaget, 1954). Although intuitively
+appealing, stage theories can be challenging to integrate with theories
+of learning, which typically posit that knowledge and skills improve
+incrementally with experience. Indeed, one of the central challenges of
+cognitive development has been to explain transitions between stages
+which appear to be qualitatively different (Carey, 2009).
 
@@
 cognitively-demanding task which may mask learning, or to the use of
-hard statistical thresholding (in particular, p-value \textless{} 0.05)
-which creates a spurious dichotomy between success and failure in
-observing a given behavior. In such cases, positing discontinuous stages
-is unnecessary. Instead, as we shall see in this paper, a continuous
-model----involving similar representations across the lifespan----may
-provide a simpler and more transparent account of development.
+statistical thresholding (in particular, p-value \textless{} 0.05) which
+can create a spurious dichotomy between success and failure in observing
+a given behavior. In such cases, positing discontinuous stages is
+unnecessary. Instead, a continuous model--involving similar
+representations across the lifespan--may provide a simpler and more
+transparent account of development.
 
@@
 (1997) first showed that children's early ability to distinguish similar
-sounds (``dih'' vs. ``bih'') does not automatically translate into word
-learning skills (i.e., associating these sounds with different
-meanings). Subsequent research has focused on proposing possible
-explanations for this observed gap between speech perception and word
-learning (e.g., Fennell \& Waxman, 2010; Hofer \& Levy, 2017; Rost \&
-McMurray, 2009; Stager \& Werker, 1997).
+sounds does not automatically translate into word learning skills.
+Indeed, though infants around 14-month old can distinguish similar sound
+pairs such as ``dih'' and ``bih'', they appear to fail in mapping this
+pair to two different objects. Subsequent research has focused on
+proposing possible explanations for this observed gap between speech
+perception and word learning (e.g., Fennell \& Waxman, 2010; Hofer \&
+Levy, 2017; Rost \& McMurray, 2009; Stager \& Werker, 1997). In this
+work we focus, rather, on the mechanism of development.
 
-In this work we focus, rather, on the development of this phenomenon. In
-fact, regardless of the exact explanation, it is generally accepted that
-by around 17 m.o, children succeed in the same task (Werker, Fennell,
+By around 17 m.o, children succeed in the same task (Werker, Fennell,
 Corcoran, \& Stager, 2002). How does development proceed? Early accounts
@@
 
-Nevertheless, subsequent findings have suggested otherwise. On the one
-hand, 14-month-olds--who typically fail in the original task--succeed
-when an easier testing method is used, even under the same learning
-conditions (Yoshida, Fennell, Swingley, \& Werker, 2009). They also
-succeed when uncertainty is mitigated via disambiguating cues (e.g.,
-Thiessen, 2007). On the other hand, adults show patterns of learning
-similar to those shown by 14-month-olds when the task is more
-challenging and when similarity between words increases (Pajak, Creel,
-\& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
+Subsequent findings have suggested otherwise. On the one hand,
+14-month-olds--who typically fail in the original task--succeed when an
+easier testing method is used, even under the same learning conditions
+(Yoshida, Fennell, Swingley, \& Werker, 2009). They also succeed when
+uncertainty is mitigated via disambiguating cues (e.g., Thiessen, 2007).
+On the other hand, adults show patterns of learning similar to those
+shown by 14-month-olds when the task is more challenging and when
+similarity between words increases (Pajak, Creel, \& Levy, 2016; White,
+Yee, Blumstein, \& Morgan, 2013).
 
-These evidence point towards another scenario, where the representations
-are encoded in a probabilistic (rather than binary) way, and where
-development is continuous, rather than stage-like (Pajak et al., 2016;
-Swingley, 2007; Yoshida et al., 2009). On this account, correct
-representations are learned early in development, but these
-representations are encoded with higher uncertainty in younger children,
-leading to apparent failure in relatively demanding tasks. Development
-is a continuous process whereby the initial noisy representations become
-more precise. Crucially, more precise representation are still
-imperfect: Even adults show low accuracy learning when the sounds are
-subtle enough, e.g., non-native sounds (Pajak et al., 2016).
+This pattern of evidence points towards another scenario, where the
+representations are encoded in a probabilistic (rather than binary) way,
+and where development is continuous, rather than stage-like (see also
+Swingley, 2007). On this account, correct representations are learned
+early in development, but these representations are encoded with higher
+uncertainty in younger children, leading to apparent failure in
+relatively demanding tasks. Development is a continuous process whereby
+the initial noisy representations become more precise. In addition, more
+precise representation are still imperfect: Even adults show low
+accuracy learning when the sounds are subtle, e.g., non-native sounds
+(Pajak et al., 2016).
 
@@
 label 2 (``dih'') with object 1 and object 2, respectively. Though
-children could learn that the label ``bih'' is a better match to object
-1 than ``dih'', they could still judge the sound ``dih'' as a plausible
+infants could learn that the label ``bih'' is a better match to object 1
+than ``dih'', they could still judge the sound ``dih'' as a plausible
 instance of the label ``bih'', thanks to the relatively large
-uncertainty of the encoding.
+uncertainty of the encoding, and this confusion leads to ``failure'' in
+the recognition task. According to this account, accuracy in word
+learning improves if we increase either the perceptual distinctiveness
+of the stimuli (e.g., through using different-sounding labels), or the
+precision of the encoding itself (e.g., across development).
 
-According to this account, accuracy in word learning improves if we
-increase either the perceptual distinctiveness of the stimuli (e.g.,
-through using different-sounding labels), or the precision of the
-encoding itself (e.g., across development). Building on this intuition,
-the current work proposes a precise probabilistic model, which we use to
-both account for previous experimental findings, and to make new
-predictions that have not been tested before. Using new data collected
-from both preschool children and adults, we show that the model can
-explain various patterns of learning both within the same age and across
-development.
+Building on this intuition, the current work proposes a probabilistic
+model, which we use to both account for previous experimental findings,
+and to make new predictions that have not been tested before. Using new
+data collected from both preschool children and adults, we show that the
+model can explain various patterns of learning both within the same age
+and across development.
 
@@
 unambiguously, and the second assumed the concepts are observed
-unambiguously. In our model, we assume there to be ambiguity at the
-level of both the labels and the concepts. For simplicity, we assume
-that the probability of membership of objects and sounds to concepts and
-labels, respectively, are normally distributed:
+unambiguously. In our model, we assume that both labels and concepts are
+observed with a certain amount of perceptual noise, which we assume, for
+simplicity, that it is captured by a normal distribution:
 
@@
 
-The learner hears a sound \(s\) and has to decided which object \(o\)
+The learner hears a sound \(s\) and has to decide which object \(o\)
 provides an optimal match to this sound. To this end, the learner has to
@@
 \[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
-The joint probability \(P(o, C, L, s_T)\) is obtained by factoring the
+The joint probability \(P(o, C, L, s)\) is obtained by factoring the
 Bayesian network in Figure \ref{fig:model}:
@@
 concepts' prior probability is uniformly
-distributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in the Experiment below.},
+distributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in Experiment.},
 we obtain the following expression, where all conditional dependencies
@@
 first exposed to the association between pairs of nonsense words (e.g.,
-``lif''/``neem'') and pairs of objects. After this exposure phase,
-participants perform a series of test trials. In each of these trials,
-one of the two sounds is uttered (e.g., ``lif'') and participants choose
-the corresponding object from the two alternatives. An overview of the
-task is shown in Figure \ref{fig:task}.
+``lif''/``neem'') and pairs of objects. The word-object associations are
+introduced sequentially. After this exposure phase, participants perform
+a series of test trials. In each of these trials, one of the two sounds
+is uttered (e.g., ``lif'') and participants choose the corresponding
+object from the two alternatives. An overview of the task is shown in
+Figure \ref{fig:task}.
 
@@
 (Expression 2) as a function of the distinctiveness parameters
-(\(\Delta s\) and \(\Delta o\)) and the precision parameter, i.e., the
-variance of the distributions \(p(s| L)\) and \(p(o | C)\) (which, for
-ease of the simulations' interpretation, are assumed to have similar
-values, i.e., \(\sigma =\sigma_C \approx \sigma_L\)).
+(\(\Delta s\) and \(\Delta o\)) and the precision parameters, i.e., the
+variances of the distributions \(p(s| L)\) and \(p(o | C)\). To
+understand the qualitative behavior of the model, we assumed for
+simplicity that the precision parameter has similar values in both
+distributions, i.e., \(\sigma =\sigma_C \approx \sigma_L\) (but we will
+allow those parameters to vary independently in the rest of the paper).
 
@@
 
-\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\Delta s$ (x-axis) and $\Delta o$ (different panels) and representation precision $\sigma$ (color).
+\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\Delta s$ and $\Delta o$ and representation precision $\sigma$ (For clarity, we assume here that $\sigma$=$\sigma_C$=$\sigma_L$).
 Dashed line represents chance.}\label{fig:simulation}
@@
   disambiguating similar sounding words (e.g., Fennell \& Waxman, 2010;
-  Rost \& McMurray, 2009; Thiessen, 2007), but no previous study tested
-  the effect of the visual distance between the semantic referents.
+  Rost \& McMurray, 2009; Thiessen, 2007), but to our knowledge no
+  previous study in the literature tested the effect of the visual
+  distance between the semantic referents.
 \end{enumerate}
-
-In sum, we introduced a model that accounts for some qualitative
-learning patterns observed in previous studies, and makes a new
-prediction. In the experiment below, we test whether the model makes
-accurate quantitative predictions by fitting it to new experimental data
-collected from preschool children and adults.
 
@@
 In this experiment, we tested participants in the word learning task
-introduced above (Figure \ref{fig:task}). We explored all three
-parameters of the model. In particular, both the sound similarity
-(\(\Delta s\)) and object similarity (\(\Delta o\)) were varied
-simultaneously in a within-subject design. Two age groups (preschool
-children and adults) were tested on the same task to explore whether
-development can be characterized with the uncertainty parameter,
-\(\sigma\), in the probabilistic representations. The Experiment and the
-predictions were pre-registered.
+introduced above (Figure \ref{fig:task}). More precisely, we explored
+the predictions related to both distinctiveness and precision. Sound
+similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were
+varied simultaneously in a within-subject design. Two age groups
+(preschool children and adults) were tested on the same task to explore
+whether development can be characterized with the uncertainty
+parameters, \(\sigma_C\) and \(\sigma_L\). The Experiment, sample size,
+exclusion criteria and the model's main predictions were pre-registered.
 
@@
 
-We planned to recruit a sample of 60 children ages 4-5 years from the
-Bing Nursery School on Stanford University's campus. So far, we
-collected data from N=47 children (mean age= months, F=). An additional
-28 children participated but were removed from analyses because they
-were not above chance on the catch trials (as was specified in the
-pre-registration\footnote{https://osf.io/jrh38/}). We also collected a
-sample of N=20 adults on Amazon Mechanical Turk (this is a pilot, I will
-plan for 60 participants). N=2 adult participants were excluded because
-of low scores on the catch trials (see pre-registration). (I still need
-to write the code that derives these numbers automatically from the
-data).
+We planned to recruit a sample of N=60 children ages 4-5 years from the
+Bing Nursery School on Stanford University's campus. So far, we have
+collected data from n=47 children. An additional n=28 children
+participated but were removed from analyses because they were not above
+chance on the catch trials. We also planned to recruit a sample of N=60
+adults on Amazon Mechanical Turk. This study used sata from n=50 adult
+participants. An additional n=10 participants were tested but excluded
+because of low scores on the catch trials (n=9 ) or because they were
+familiar with the non-English sound stimuli we used in the adult
+experiment (n=1).
 
@@
 
+\subsubsection{Design}\label{design}
+
+Each age group saw only two of the three levels of similarity described
+in the previous sub-section: ``different'' vs. ``intermediate'' for
+preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
+this choice in the light of pilot studies showing that adults were at
+ceiling with ``different'' sounds/objects, and children were at chance
+with the ``similar'' sounds/objects. That said, this difference in the
+level of similarity is accounted for in the model through using the
+appropriate perceptual distance used in each age group (Figure
+\ref{fig:stim}).
+
 \begin{CodeChunk}
@@
 
-\subsubsection{Design}\label{design}
+The experiment was a 2x2 within-subjects factorial design with four
+conditions: high/low sound similarity crossed with high/low visual
+object similarity. Besides the 4 conditions, we also tested participants
+on a fifth catch condition which was similar in its structure to the
+other ones, but was used only to select participants who were able to
+follow the instructions and show minimal learning.
 
-Each age group saw only two of the three levels of similarity described
-in the previous sub-section: ``different'' vs. ``intermediate'' for
-preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
-this choice because, on the one hand, adults were at ceiling with
-``different'' sounds/objects, and on the other hand, children were at
-chance with the ``similar'' sounds/objects. That said, this difference
-in the level of similarity is accounted for in the model through using
-the appropriate perceptual distance used in each age group (Figure
-\ref{fig:stim}).
+\subsubsection{Procedure}\label{procedure}
 
-The experiment consisted of four conditions which involved, each, one
-pair of sounds-objects associations. These conditions were constructed
-by crossing the sound's degree of similarity with the object's degree of
-similarity leading to a 2x2 factorial design in each age group. Besides
-the 4 conditions, we also tested participants on a fifth catch condition
-which was similar in its structure to the other ones, but was used only
-to select participants who were able to follow the instructions and show
-minimal learning.
+Preschoolers were tested at the nursery school using a tablet, whereas
+adults used their own computers to complete the same experiment online.
+Participants were tested in a sequence of five conditions: the four
+experimental conditions plus the catch condition. In each condition,
+participants saw a first block of four exposure trials followed by four
+testing trials, and a second block of two exposure trials (for memory
+refreshment) followed by an additional four testing trials.
 
@@
 \end{CodeChunk}
-
-\subsubsection{Procedure}\label{procedure}
-
-Preschoolers were tested at the nursery school using a tablet, whereas
-adults used their local computers to complete the same experiment
-online. Participants were tested in a sequence of five conditions: the
-four experimental conditions plus the catch condition. In each
-condition, participants saw a first block of four exposure trials
-followed by four testing trials, and a second block of two exposure
-trials (for memory refreshment) followed by an additional four testing
-trials.
 
@@
 
-We first analyzed the experimental results shown in Figure
-(\ref{fig:data_all}, top), using a mixed-effects logistic regression
-with sound distance, object distance and age group as fixed effects, and
-with a maximal random effects structure (allowing us to take into
-account the full nested structure of our data) (Barr, Levy, Scheepers,
-\& Tily, 2013). We found main effects for all the fixed effects, i.e.,
-the sound distance (\(\beta =\) 0.68, \(p\) \textless{}
-0.001)---replicating previous findings, the object distance (\(\beta =\)
-0.6, \(p\) \textless{} 0.001)---confirming the new prediction of our
-model, and age group (\(\beta =\) 0.59, \(p\) \textless{}
-0.001)---showing that performance improves with age. Besides, we found
-two-way interactions between sound and object distances (\(\beta =\)
-0.36, \(p\) \textless{}0.05) and between sound distance and age
-(\(\beta =\) 0.37, \(p\) \textless{}0.01).
+Experimental results are shown in Figure 6 (top). We first analyzed the
+results using a mixed-effects logistic regression with sound distance,
+object distance and age group as fixed effects, and with a maximal
+random effects structure (allowing us to take into account the full
+nested structure of our data) (Barr, Levy, Scheepers, \& Tily, 2013). We
+found main effects for all the fixed effects in the regression, i.e.,
+the sound distance (\(\beta =\) 0.44, \(p\) \textless{}
+0.001)--replicating previous findings, the object distance (\(\beta =\)
+0.5, \(p\) \textless{} 0.001)--confirming the new prediction of our
+model, and age group (\(\beta =\) 0.43, \(p\) \textless{}
+0.001)--showing that performance improves with age. Besides, we found
+two-way interactions between sound distance and age (\(\beta =\) 0.17,
+\(p\) \textless{}0.05) and between object distance and age (\(\beta =\)
+0.18, \(p\) \textless{}0.05).
 
-Second, we fit the probability function (Equation 2) to the
-participants' responses in each age group. The values of \(\Delta s\)
-and \(\Delta o\) were set based on data from the similarity judgment
-task (Figure \ref{fig:stim}). Thus, the model has two degrees of freedom
-in each group, i.e., \(\sigma_C\) and \(\sigma_L\). Figure
-\ref{fig:data_all} (bottom) show the predictions of the model. The model
-correctly predicts the relative recognition accuracy across conditions:
-the pair of words that differ on both the object and sound levels were
-the easiest to learn, followed by the pairs of words that differ on only
-one level, then the pair of words that are similar on both levels. At
-the quantitative level, the models explained almost all the variance in
-the participants' mean responses (\(R^2=\) 0.96).
+Second, we fit our model (using Equation 2) to the participants'
+responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
+were set based on data from the similarity judgment task (Figure
+\ref{fig:stim}). Thus, the model has two degrees of freedom for each
+group, i.e., \(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all}
+(bottom) shows the predictions. The model captures the qualitative
+patterns in both age groups: starting from a low accuracy recognition
+when both the sound and object distances are small, the model correctly
+predicts an increase in accuracy when either the sound distance or the
+object distance increases. Besides, accuracy is correctly predicted to
+be maximal when both the sound and object distances are high.
 
-We also fit a simplified model with only one degree of freedom
-(\(\sigma = \sigma_C =\sigma_L\)). This second model is not intended to
-test any theoretical hypothesis. We use it, rather, as a baseline to
-understand how much of the explanatory power of the model is due to the
-extra degree of freedom. This baseline model still captured the
-qualitative pattern (graph not shown), and explained the majority of the
-variance (\(R^2=\) 0.94). Besides, model comparison using Akaike
-information criterion yielded \(AIC(model) - AIC(baseline) =\) -3.79 for
-children data and \(AIC(model) - AIC(baseline) =\) 1.62 for adult data.
-These numbers suggest that the model remains highly predictive even with
-one degree of freedom.
-
-As for the values of the parameters, children had a label-specific
-uncertainty of \(\sigma_S =\) 0.9 {[}0.68,
+The values of the parameters were as follows. Children had a
+label-specific uncertainty of \(\sigma_S =\) 0.9 {[}0.68,
 1.11{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
 and a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1,
-0.49{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.16
-{[}0.05, 0.28{]}, and a concept-specific uncertainty of \(\sigma_C =\)
-0.14 {[}0.05, 0.23{]}. As predicted, the uncertainty parameters were
-larger for children than they were for adults.
+0.49{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.14
+{[}-0.02, 0.3{]}, and a concept-specific uncertainty of \(\sigma_C =\)
+0.19 {[}0.04, 0.34{]}. As predicted, the uncertainty parameters were
+larger for children than they were for adults, showing that the
+probabilsitic representations becomes more refined (that is, \(\sigma\)
+becomes smaller) across development.
+
+The models explained the majority of the variance in the participants'
+mean responses (\(R^2=\) 0.86, for the combined adult and children's
+data). To investigate whether the model's predictive power is due to
+overfitting, we fit a simplified version with only one degree of freedom
+(i.e., a single variance common to both sounds and objects). This
+single-variance model explained as much variance in the mean responses
+(\(R^2=\) 0.87). It also captured the main qualitative patterns (graph
+not shown), suggesting that the explanatory power of the model is
+largely due to its structure, rather than its degrees of freedom.
+
+An unexpected outcome was that adult participants deviated slightly from
+the model's predicted numbers. While the model predicted recognition
+accuracy to be more sensitive to object distance when sound distance is
+different (and vice-versa), adult participants showed the opposite
+pattern. This deviation is interesting as it suggests that participants
+adapt their auditory-visual cue integration strategy to the ambiguity of
+the situation: They are highly sensitive to the presence or absence of
+disambiguating visual information when sound ambiguity is higher (and
+vice-versa).
+\footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}
 
@@
 
-This paper studies the hypothesis that some seemingly stage-like
-patterns in cognitive development can be characterized in a continuous
-fashion. We used as a case study the seminal work of Stager \& Werker
-(1997) showing a discrepancy between children's speech perception
-abilities and their word learning skills. While most previous work
-debated the source of this discrepancy, here we were more interested in
-its mechanism of development.
+This paper explored the idea that some seemingly stage-like patterns in
+cognitive development can be characterized in a continuous fashion. We
+used as a case study the seminal work of Stager \& Werker (1997) showing
+a discrepancy between children's speech perception abilities and their
+word learning skills. While most previous work debated the source of
+this discrepancy, here we were more interested in how it reflects
+developmental change.
 
-Building on some previous findings and discussions (e.g., Swingley,
-2007; Yoshida et al., 2009), we proposed a model which assumes that
-subtle perceptual features are correctly encoded during word meaning
-learning, but that the precision of this encoding improves across
-development. We tested the model's predictions against data collected
-from preschool children and adults and we showed that development can be
-characterized as a continuous refinement in qualitatively similar
-representations across the life span.
+Building on some previous discussions (e.g., Swingley, 2007; Yoshida et
+al., 2009), we proposed a model which assumes that subtle perceptual
+features are correctly encoded during word meaning learning, but that
+the precision of this encoding varies. We tested the model's predictions
+against data collected from preschool children and adults and we showed
+that developmental changes in word-object mappings can indeed be
+characterized as a continuous refinement (reducing the encoding
+uncertainty) in qualitatively similar representations across the life
+span.
 
-The model made a new prediction which we tested experimentally for the
-first time: learning similar words is not only modulated by the
+The model made a new prediction to which we provided the first
+experimental test: Learning similar words is not only modulated by the
 similarity of their phonological forms, but also by the visual
@@
 children at a relatively older age (4-5 years old) than what is
-typically studied in the literature (around 14 month-old). While an
-important conclusion of this paper is that the same process may apply to
-different developmental stages, it would be interesting to
-experimentally verify the generality of this conclusion in the context
-of early language acquisition. A challenge to this next step would be to
-construct a computational framework which would compare performance
-across heterogeneous testing methods (e.g., looking time
-vs.~forced-choice).
-
-To sum, this paper proposes a model that accounts for the development of
-an important aspect of word learning. The findings show that data can be
+typically studied in the literature (around 14 month-old). Nonetheless,
+this choice was related to two measurement difficulties. First, model
+fitting requires several, reliably-measured data points. In our case,
+data collection involved presenting participants with several trials
+across four conditions in a between-subject design. It would have been
+challenging to obtain these measures with infants. Second, the study of
+infants requires using specific testing methods. This fact would have
+made the quantitative study of development challenging. Indeed, it is
+not clear how data from these methods would directly compare to data
+collected using more typical methods in older children and adults. In
+sum, this paper proposes a model that accounts for the development of an
+important aspect of word learning. The findings show that data can be
 explained based on a continuous process operating over similar
@@
 an example, but the same idea might apply to other aspects of cognitive
-development which are tyipcally thought of as stage-like (e.g.,
-acquisition of a theory of mind). A crucial task would be to investigate
-the extent to which such discontinuities emerge due to genuine
-qualitative changes, and the extent to which they reflect the
-granularity of the researchers' own measurement tools.
+development that are typically thought of as stage-like (e.g.,
+acquisition of a theory of mind). Computational models such as the one
+proposed here can help us investigate the extent to which such
+discontinuities emerge due to genuine qualitative changes, and the
+extent to which they reflect the granularity of the researchers' own
+measurement tools.
 

### 2019-01-31 cogsci/cogsci.Rmd
second version cogsci

@@
 An unexpected outcome was that adult participants deviated slightly from the model's predicted numbers.
-While the model predicted recognition accuracy to be more sensitive to object distance when sound distance is different (and vice-versa), adult participants showed the opposite pattern.
-This deviation is interesting as it suggests that participants adapt their auditory-visual cue integration strategy to the ambiguity of the situation: They are highly sensitive to the presence or absence of disambiguating visual information when sound ambiguity is higher (and vice-versa).
+While the model predicted recognition accuracy to be more sensitive to object distance when sound distance is high (and vice-versa), adult participants showed the opposite pattern.
+This deviation is interesting as it suggests that participants adapt their auditory-visual cue integration strategy to the ambiguity of the situation: They are more sensitive to the presence or absence of disambiguating visual information when sound ambiguity is higher (and vice-versa).
 \footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}

### 2019-01-31 cogsci/cogsci.tex
second version cogsci

@@
 accuracy to be more sensitive to object distance when sound distance is
-different (and vice-versa), adult participants showed the opposite
-pattern. This deviation is interesting as it suggests that participants
-adapt their auditory-visual cue integration strategy to the ambiguity of
-the situation: They are highly sensitive to the presence or absence of
+high (and vice-versa), adult participants showed the opposite pattern.
+This deviation is interesting as it suggests that participants adapt
+their auditory-visual cue integration strategy to the ambiguity of the
+situation: They are more sensitive to the presence or absence of
 disambiguating visual information when sound ambiguity is higher (and

### 2019-01-31 cogsci/cogsci.Rmd
second version cogsci

@@
 
-An unexpected outcome was that adult participants deviated slightly from the model's predicted numbers.
-While the model predicted recognition accuracy to be more sensitive to object distance when sound distance is high (and vice-versa), adult participants showed the opposite pattern.
-This deviation is interesting as it suggests that participants adapt their auditory-visual cue integration strategy to the ambiguity of the situation: They are more sensitive to the presence or absence of disambiguating visual information when sound ambiguity is higher (and vice-versa).
+An unexpected outcome was that adult participants deviated slightly from the model's numbers.
+While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern.
+This deviation is interesting as it suggests that participants are more likely to pay attention and integrate additional sources of information when ambiguity is higher.
 \footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}
@@
 -->
+
 In sum, this paper proposes a model that accounts for the development of an important aspect of word learning.

### 2019-01-31 cogsci/cogsci.tex
second version cogsci

@@
 An unexpected outcome was that adult participants deviated slightly from
-the model's predicted numbers. While the model predicted recognition
-accuracy to be more sensitive to object distance when sound distance is
-high (and vice-versa), adult participants showed the opposite pattern.
-This deviation is interesting as it suggests that participants adapt
-their auditory-visual cue integration strategy to the ambiguity of the
-situation: They are more sensitive to the presence or absence of
-disambiguating visual information when sound ambiguity is higher (and
-vice-versa).
+the model's numbers. While the model predicted accuracy to be more
+sensitive to object distance when sound distance is higher (and
+vice-versa), adult participants showed the opposite pattern. This
+deviation is interesting as it suggests that participants are more
+likely to pay attention and integrate additional sources of information
+when ambiguity is higher.
 \footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}
@@
 not clear how data from these methods would directly compare to data
-collected using more typical methods in older children and adults. In
-sum, this paper proposes a model that accounts for the development of an
-important aspect of word learning. The findings show that data can be
+collected using more typical methods in older children and adults.
+
+In sum, this paper proposes a model that accounts for the development of
+an important aspect of word learning. The findings show that data can be
 explained based on a continuous process operating over similar

### 2019-01-31 cogsci/cogsci.Rmd
second version cogsci

@@
 
-An unexpected outcome was that adult participants deviated slightly from the model's numbers.
-While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern.
+An unexpected outcome was that adult participants deviated slightly from the model's numbers: While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern.
 This deviation is interesting as it suggests that participants are more likely to pay attention and integrate additional sources of information when ambiguity is higher.
@@
 
-Building on some previous discussions [e.g., @swingley2007; @yoshida2009], we proposed a model which assumes that subtle perceptual features are correctly encoded during word meaning learning, but that the precision of this encoding varies.
-We tested the model's predictions against data collected from preschool children and adults and we showed that developmental changes in word-object mappings can indeed be characterized as a continuous refinement (reducing the encoding uncertainty) in qualitatively similar representations across the life span.
+Building on some previous discussions [e.g., @swingley2007; @yoshida2009], we proposed a model where perceptual stimuli are encoded probabilistically.
+We tested the model's predictions against data collected from preschool children and adults and we showed that developmental changes in word-object mappings can indeed be characterized as a continuous refinement (i.e., uncertainty reduction) in qualitatively similar representations across the life span.
 
@@
 This suggestion is supported by recent findings based on the investigation of early vocabulary growth [@engelthaler2017; @sizemore2018].
-That said, further work is needed to explore the effect on word learning of other semantic dimensions that could be encoded by children (e.g., conceptual/functional features).
+
+<!--That said, further work is needed to explore the effect on word learning of other semantic dimensions that could be encoded by children (e.g., conceptual/functional features). -->
 

### 2019-01-31 cogsci/cogsci.tex
second version cogsci

@@
 An unexpected outcome was that adult participants deviated slightly from
-the model's numbers. While the model predicted accuracy to be more
+the model's numbers: While the model predicted accuracy to be more
 sensitive to object distance when sound distance is higher (and
@@
 Building on some previous discussions (e.g., Swingley, 2007; Yoshida et
-al., 2009), we proposed a model which assumes that subtle perceptual
-features are correctly encoded during word meaning learning, but that
-the precision of this encoding varies. We tested the model's predictions
-against data collected from preschool children and adults and we showed
-that developmental changes in word-object mappings can indeed be
-characterized as a continuous refinement (reducing the encoding
-uncertainty) in qualitatively similar representations across the life
-span.
+al., 2009), we proposed a model where perceptual stimuli are encoded
+probabilistically. We tested the model's predictions against data
+collected from preschool children and adults and we showed that
+developmental changes in word-object mappings can indeed be
+characterized as a continuous refinement (i.e., uncertainty reduction)
+in qualitatively similar representations across the life span.
 
@@
 the investigation of early vocabulary growth (Engelthaler \& Hills,
-2017; Sizemore, Karuza, Giusti, \& Bassett, 2018). That said, further
-work is needed to explore the effect on word learning of other semantic
-dimensions that could be encoded by children (e.g.,
-conceptual/functional features).
+2017; Sizemore, Karuza, Giusti, \& Bassett, 2018).
 

### 2019-02-01 cogsci/cogsci.Rmd
final version cogsci

@@
 In such cases, positing discontinuous stages is unnecessary.
-Instead, a continuous model–involving similar representations across the lifespan–may provide a simpler and more transparent account of development.
+Instead, a continuous model---involving similar representations across the lifespan---may provide a simpler and more transparent account of development.
 
@@
 Indeed, though infants around 14-month old can distinguish similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects.
-Subsequent research has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017;  @rost2009].
-In this work we focus, rather, on the mechanism of development.
+Follow-up studies has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017;  @rost2009].
+
+<!--In this work we focus, rather, on the mechanism of development. -->
 
@@
 Subsequent findings have suggested otherwise.
-On the one hand, 14-month-olds–who typically fail in the original task–succeed when an easier testing method is used, even under the same learning conditions [@yoshida2009].
+On the one hand, 14-month-olds---who typically fail in the original tas---succeed when an easier testing method is used, even under the same learning conditions [@yoshida2009].
 They also succeed when uncertainty is mitigated via disambiguating cues [e.g., @thiessen2007].
@@
 \includegraphics[width=1.5in]{figs/model.png}
-\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters.}
+\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicate fixed model parameters.}
 \label{fig:model}
@@
 However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously.
-In our model, we assume that both labels and concepts are observed with a certain amount of perceptual noise, which we assume, for simplicity, that it is captured by a normal distribution:
+In our model, we assume that both labels and concepts are observed with a certain amount of perceptual noise, which we assume, for simplicity, is captured by a normal distribution:
 
@@
 The learner hears a sound $s$ and has to decide which object $o$ provides an optimal match to this sound.
-To this end, the learner has to compute the probability $P(o|s)$ for all possible objects.
+To this end, they must compute the probability $P(o|s)$ for all possible objects.
 This probability can be computed by summing over all possible concepts and labels:
@@
 $$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
-which could be transformed using Bayes rule into:
+which can be transformed using Bayes rule into:
 
 $$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
-Finally, assuming that the concepts' prior probability is uniformly distributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation.
-See the stimuli sub-section in Experiment.}, we obtain the following expression, where all conditional dependencies are now well defined:
+Finally, assuming that the concepts' prior probability is uniformly distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.}, we obtain the following expression, where all conditional dependencies are now well defined:
 
@@
 
-We use the model to predict performance in the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009.
+  We use the model to predict performance in the word learning task introduced by @stager1997, with a two-alternative forced choice as in @yoshida2009.
 In this task, participants are first exposed to the association between pairs of nonsense words (e.g., "lif"/"neem") and pairs of objects.
@@
 
-We use the general Equation 1 to derive the exact analytical expression for the probability of accurate responses $p(o_T | s)$ (target object $o_T$ given a sound $s$) in the simple case of two-alternative forced choice in the testing phase of our experimental task:
+We used Equation 1 to obtain the exact analytical expression for the probability of accurate responses $p(o_T | s)$ (target object $o_T$ given a sound $s$) in the simple case of two-alternative forced choice in the testing phase of our experimental task:
 
@@
 Two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
-The Experiment, sample size, exclusion criteria and the model's main predictions were pre-registered.
+The experiment, sample size, exclusion criteria and the model's main predictions were pre-registered.
 <!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
@@
 We planned to recruit a sample of N=60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
-So far, we have collected data from n=`r N_good_ch` children.
-An additional n=`r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials.
+Here we report data from n=`r N_good_ch` children.
+An additional n=`r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
 We also planned to recruit a sample of N=60 adults on Amazon Mechanical Turk.
-This study used sata from n=`r N_good_ad` adult participants.
-An additional n=`r N_all_ad-N_good_ad` participants were tested but excluded because of low scores on the catch trials (n=`r N_all_ad-N_good_ad-d_adult_lang` ) or because they were familiar with the non-English sound stimuli we used in the adult experiment (n=`r d_adult_lang`).
+Data from n=`r N_all_ad-N_good_ad` participants were excluded due to low scores on the catch trials (n=`r N_all_ad-N_good_ad-d_adult_lang` ) or because they were familiar with the non-English sound stimuli we used in the adult experiment (n=`r d_adult_lang`), yielding a final sample of n=`r N_good_ad`.
 
@@
 We scaled responses within the range [0,1].
-Data are shown in Figure \ref{fig:stim}, for each stimuli group.
-This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).
+Data are shown in Figure \ref{fig:stim}, for each stimulus group.
+These data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).
 
@@
 ###Design
+
 Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs.
@@
 "similar" for adults.
-We made this choice in the light of pilot studies showing that adults were at ceiling with "different" sounds/objects, and children were at chance with the "similar" sounds/objects.
+We made this choice in light of pilot studies showing that adults were at ceiling with "different" sounds/objects, and children were at chance with the "similar" sounds/objects.
 That said, this difference in the level of similarity is accounted for in the model through using the appropriate perceptual distance used in each age group (Figure \ref{fig:stim}).
@@
 ```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:stim}Distances for both sound and object pairs from an adult norming study.
+Data represent Likert values normalized to [0,1] interval.
 Error bars represent 95\\% confidence intervals."}
@@
 ```
-The experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
+
+To maximize our ability to measure subtle stimulus effects, the experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
 Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
@@
 
-#plot_data <- ggplot(subset(data_human_model, source =='Experimental'), 
-plot_data <- ggplot(data_human_model, 
+plot_data <- ggplot(subset(data_human_model, source =='Experimental'), 
+#plot_data <- ggplot(data_human_model, 
       aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
@@
   geom_line() + 
-  #geom_line(data=subset(data_human_model, source == "Model"), linetype=2, size=0.5, col='black')+
-  #geom_point(data=subset(data_human_model, source == "Model"), size=1, col='black')+
+  geom_line(data=subset(data_human_model, source == "Model"), linetype=2, size=0.5)+
+  geom_point(data=subset(data_human_model, source == "Model"), size=1.5, alpha=0.5)+
   geom_hline(yintercept = 0.50, linetype="dashed") +
@@
       #) + facet_grid(group~source, scales="free_y") +
-      ) + facet_grid(source~group) +
+      ) + facet_grid(.~group) +
   theme(aspect.ratio = 0.7)
@@
 In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.
+The length of this procedure was demanding, especially for children, but we adopted a fully within-subjects design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=6, fig.height=4, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
 Adults).
-We show both experimental results (top) and model predictions (bottom).
+We show both experimental results (solid lines) and model predictions (dashed lines).
 Error bars represent 95\\% confidence intervals."}
@@
 We first analyzed the results using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) [@barr2013].
-We found main effects for all the fixed effects in the regression, i.e., the sound distance ($\beta =$ `r s_coef`, $p$ `r p_val(s_p)`)–replicating previous findings, the object distance ($\beta =$ `r c_coef`, $p$ `r p_val(c_p)`)–confirming the new prediction of our model, and age group ($\beta =$ `r age_coef`, $p$ `r p_val(age_p)`)–showing that performance improves with age.
-Besides, we found two-way interactions between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`) and between object distance and age ($\beta =$ `r c_age_coef`, $p$ `r p_val(c_age_p)`).
+We found main effects for all the fixed effects in the regression.
+For the sound distance, we obtained $\beta =$ `r s_coef` ($p$ `r p_val(s_p)`), replicating previous findings.
+For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model.
+Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that performance improves with age.
+In addition, we found two-way interactions between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`) and between object distance and age ($\beta =$ `r c_age_coef`, $p$ `r p_val(c_age_p)`).
 
@@
 
-Second, we fit our model (using Equation 2) to the participants' responses in each age group.
+We next fit our model (using Equation 2) to the participants' responses in each age group.
 The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \ref{fig:stim}).
@@
 The model captures the qualitative patterns in both age groups: starting from a low accuracy recognition when both the sound and object distances are small, the model correctly predicts an increase in accuracy when either the sound distance or the object distance increases.
-Besides, accuracy is correctly predicted to be maximal when both the sound and object distances are high.
+Further, accuracy is correctly predicted to be maximal when both the sound and object distances are high.
 
@@
 Adults had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`], and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`].
-As predicted, the uncertainty parameters were larger for children than they were for adults, showing that the probabilsitic representations becomes more refined (that is, $\sigma$ becomes smaller) across development.
+As predicted, the uncertainty parameters were larger for children than they were for adults, showing that the probabilistic representations becomes more refined (that is, $\sigma$ becomes smaller) across development.
+The developmental effect was more important for the label-specific uncertainty.
 
 The models explained the majority of the variance in the participants' mean responses ($R^2=$ `r R2_model2`, for the combined adult and children's data).
-To investigate whether the model's predictive power is due to overfitting, we fit a simplified version with only one degree of freedom (i.e., a single variance common to both sounds and objects).
+To investigate whether the model's predictive power was due to overfitting, we fit a simplified version with only one degree of freedom (i.e., a single variance common to both sounds and objects).
 This single-variance model explained as much variance in the mean responses ($R^2=$ `r R2_model1`).
@@
 An unexpected outcome was that adult participants deviated slightly from the model's numbers: While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern.
-This deviation is interesting as it suggests that participants are more likely to pay attention and integrate additional sources of information when ambiguity is higher.
-\footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}
+This deviation is an interesting starting point for future work as it may suggest that participants are more likely to pay attention to and integrate additional sources of information when ambiguity is higher.
 
@@
 We used as a case study the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills.
-While most previous work debated the source of this discrepancy, here we were more interested in how it reflects developmental change.
-
+While much of the previous investigation of this finding has been interested in the source of this discrepancy, here we have explored how it could arise from continuous developmental change in perceptual uncertainty.
 <!--Since the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills, researchers have debated about the source of such a discrepancy.
@@
 
-The model made a new prediction to which we provided the first experimental test: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
+The model made a new prediction to which which we tested experimentally: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
 More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.
@@
 
-One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (around 14 month-old).
-Nonetheless, this choice was related to two measurement difficulties.
+One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-18 month-old).
+We selected this age group based on two measurement issues.
 First, model fitting requires several, reliably-measured data points.
@@
 It would have been challenging to obtain these measures with infants.
-Second, the study of infants requires using specific testing methods.
-This fact would have made the quantitative study of development challenging.
+Second, experiments with infants on this topic have often used habituation methods [but cf.
+@yoshida2009], which require additional linking assumptions.
 Indeed, it is not clear how data from these methods would directly compare to data collected using more typical methods in older children and adults.
@@
 In sum, this paper proposes a model that accounts for the development of an important aspect of word learning.
-The findings show that data can be explained based on a continuous process operating over similar representations across development.
+Our account suggests that the developmental data can be explained based on a continuous process operating over similar representations across development, suggesting developmental continuity.
 We used a case from word learning as an example, but the same idea might apply to other aspects of cognitive development that are typically thought of as stage-like (e.g., acquisition of a theory of mind).

### 2019-02-01 cogsci/cogsci.tex
final version cogsci

@@
 a given behavior. In such cases, positing discontinuous stages is
-unnecessary. Instead, a continuous model--involving similar
-representations across the lifespan--may provide a simpler and more
+unnecessary. Instead, a continuous model---involving similar
+representations across the lifespan---may provide a simpler and more
 transparent account of development.
@@
 pairs such as ``dih'' and ``bih'', they appear to fail in mapping this
-pair to two different objects. Subsequent research has focused on
+pair to two different objects. Follow-up studies has focused on
 proposing possible explanations for this observed gap between speech
 perception and word learning (e.g., Fennell \& Waxman, 2010; Hofer \&
-Levy, 2017; Rost \& McMurray, 2009; Stager \& Werker, 1997). In this
-work we focus, rather, on the mechanism of development.
+Levy, 2017; Rost \& McMurray, 2009; Stager \& Werker, 1997).
 
@@
 Subsequent findings have suggested otherwise. On the one hand,
-14-month-olds--who typically fail in the original task--succeed when an
+14-month-olds---who typically fail in the original tas---succeed when an
 easier testing method is used, even under the same learning conditions
@@
 observed with a certain amount of perceptual noise, which we assume, for
-simplicity, that it is captured by a normal distribution:
+simplicity, is captured by a normal distribution:
 
@@
 The learner hears a sound \(s\) and has to decide which object \(o\)
-provides an optimal match to this sound. To this end, the learner has to
-compute the probability \(P(o|s)\) for all possible objects. This
-probability can be computed by summing over all possible concepts and
-labels:
+provides an optimal match to this sound. To this end, they must compute
+the probability \(P(o|s)\) for all possible objects. This probability
+can be computed by summing over all possible concepts and labels:
 \[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
@@
 Bayesian network in Figure \ref{fig:model}:
-\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which could be transformed
-using Bayes rule into:
+\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which can be transformed using
+Bayes rule into:
 
@@
 concepts' prior probability is uniformly
-distributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in Experiment.},
+distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.},
 we obtain the following expression, where all conditional dependencies
@@
 We use the model to predict performance in the word learning task
-introduced by Stager \& Werker (1997), and a testing method similar to
-the one used by Yoshida et al. (2009). In this task, participants are
-first exposed to the association between pairs of nonsense words (e.g.,
+introduced by Stager \& Werker (1997), with a two-alternative forced
+choice as in Yoshida et al. (2009). In this task, participants are first
+exposed to the association between pairs of nonsense words (e.g.,
 ``lif''/``neem'') and pairs of objects. The word-object associations are
@@
 
-We use the general Equation 1 to derive the exact analytical expression
-for the probability of accurate responses \(p(o_T | s)\) (target object
-\(o_T\) given a sound \(s\)) in the simple case of two-alternative
-forced choice in the testing phase of our experimental task:
+We used Equation 1 to obtain the exact analytical expression for the
+probability of accurate responses \(p(o_T | s)\) (target object \(o_T\)
+given a sound \(s\)) in the simple case of two-alternative forced choice
+in the testing phase of our experimental task:
 
@@
 whether development can be characterized with the uncertainty
-parameters, \(\sigma_C\) and \(\sigma_L\). The Experiment, sample size,
+parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
 exclusion criteria and the model's main predictions were pre-registered.
@@
 We planned to recruit a sample of N=60 children ages 4-5 years from the
-Bing Nursery School on Stanford University's campus. So far, we have
-collected data from n=47 children. An additional n=28 children
-participated but were removed from analyses because they were not above
-chance on the catch trials. We also planned to recruit a sample of N=60
-adults on Amazon Mechanical Turk. This study used sata from n=50 adult
-participants. An additional n=10 participants were tested but excluded
-because of low scores on the catch trials (n=9 ) or because they were
-familiar with the non-English sound stimuli we used in the adult
-experiment (n=1).
+Bing Nursery School on Stanford University's campus. Here we report data
+from n=47 children. An additional n=28 children participated but were
+removed from analyses because they were not above chance on the catch
+trials due to the challenging nature of our procedure (see below). We
+also planned to recruit a sample of N=60 adults on Amazon Mechanical
+Turk. Data from n=10 participants were excluded due to low scores on the
+catch trials (n=9 ) or because they were familiar with the non-English
+sound stimuli we used in the adult experiment (n=1), yielding a final
+sample of n=50.
 
@@
 on a 7-point scale. We scaled responses within the range {[}0,1{]}. Data
-are shown in Figure \ref{fig:stim}, for each stimuli group. This data
+are shown in Figure \ref{fig:stim}, for each stimulus group. These data
 will be used in the models as the perceptual distance of sound pairs
@@
 preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
-this choice in the light of pilot studies showing that adults were at
+this choice in light of pilot studies showing that adults were at
 ceiling with ``different'' sounds/objects, and children were at chance
@@
 
-\caption{\label{fig:stim}Distances for both sound and object pairs from an adult norming study. Error bars represent 95\% confidence intervals.}\label{fig:stim}
+\caption{\label{fig:stim}Distances for both sound and object pairs from an adult norming study.
+Data represent Likert values normalized to [0,1] interval.
+Error bars represent 95\% confidence intervals.}\label{fig:stim}
 \end{figure}
@@
 
-The experiment was a 2x2 within-subjects factorial design with four
+To maximize our ability to measure subtle stimulus effects, the
+experiment was a 2x2 within-subjects factorial design with four
 conditions: high/low sound similarity crossed with high/low visual
@@
 testing trials, and a second block of two exposure trials (for memory
-refreshment) followed by an additional four testing trials.
+refreshment) followed by an additional four testing trials. The length
+of this procedure was demanding, especially for children, but we adopted
+a fully within-subjects design based on pilot testing that indicated
+that precision of measurement was critical for testing our experimental
+predictions.
 
@@
 Adults).
-We show both experimental results (top) and model predictions (bottom).
+We show both experimental results (solid lines) and model predictions (dashed lines).
 Error bars represent 95\% confidence intervals.}\label{fig:all_data}
@@
 nested structure of our data) (Barr, Levy, Scheepers, \& Tily, 2013). We
-found main effects for all the fixed effects in the regression, i.e.,
-the sound distance (\(\beta =\) 0.44, \(p\) \textless{}
-0.001)--replicating previous findings, the object distance (\(\beta =\)
-0.5, \(p\) \textless{} 0.001)--confirming the new prediction of our
-model, and age group (\(\beta =\) 0.43, \(p\) \textless{}
-0.001)--showing that performance improves with age. Besides, we found
-two-way interactions between sound distance and age (\(\beta =\) 0.17,
-\(p\) \textless{}0.05) and between object distance and age (\(\beta =\)
-0.18, \(p\) \textless{}0.05).
+found main effects for all the fixed effects in the regression. For the
+sound distance, we obtained \(\beta =\) 0.44 (\(p\) \textless{} 0.001),
+replicating previous findings. For object distance, we found \(\beta =\)
+0.5 (\(p\) \textless{} 0.001), and this finding confirms the new
+prediction of our model. Finally, for the age group, we obtained
+\(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that performance
+improves with age. In addition, we found two-way interactions between
+sound distance and age (\(\beta =\) 0.17, \(p\) \textless{}0.05) and
+between object distance and age (\(\beta =\) 0.18, \(p\)
+\textless{}0.05).
 
-Second, we fit our model (using Equation 2) to the participants'
-responses in each age group. The values of \(\Delta s\) and \(\Delta o\)
-were set based on data from the similarity judgment task (Figure
-\ref{fig:stim}). Thus, the model has two degrees of freedom for each
-group, i.e., \(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all}
-(bottom) shows the predictions. The model captures the qualitative
-patterns in both age groups: starting from a low accuracy recognition
-when both the sound and object distances are small, the model correctly
-predicts an increase in accuracy when either the sound distance or the
-object distance increases. Besides, accuracy is correctly predicted to
-be maximal when both the sound and object distances are high.
+We next fit our model (using Equation 2) to the participants' responses
+in each age group. The values of \(\Delta s\) and \(\Delta o\) were set
+based on data from the similarity judgment task (Figure \ref{fig:stim}).
+Thus, the model has two degrees of freedom for each group, i.e.,
+\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (bottom) shows
+the predictions. The model captures the qualitative patterns in both age
+groups: starting from a low accuracy recognition when both the sound and
+object distances are small, the model correctly predicts an increase in
+accuracy when either the sound distance or the object distance
+increases. Further, accuracy is correctly predicted to be maximal when
+both the sound and object distances are high.
 
@@
 larger for children than they were for adults, showing that the
-probabilsitic representations becomes more refined (that is, \(\sigma\)
-becomes smaller) across development.
+probabilistic representations becomes more refined (that is, \(\sigma\)
+becomes smaller) across development. The developmental effect was more
+important for the label-specific uncertainty.
 
@@
 mean responses (\(R^2=\) 0.86, for the combined adult and children's
-data). To investigate whether the model's predictive power is due to
+data). To investigate whether the model's predictive power was due to
 overfitting, we fit a simplified version with only one degree of freedom
@@
 vice-versa), adult participants showed the opposite pattern. This
-deviation is interesting as it suggests that participants are more
-likely to pay attention and integrate additional sources of information
-when ambiguity is higher.
-\footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}
+deviation is an interesting starting point for future work as it may
+suggest that participants are more likely to pay attention to and
+integrate additional sources of information when ambiguity is higher.
 
@@
 a discrepancy between children's speech perception abilities and their
-word learning skills. While most previous work debated the source of
-this discrepancy, here we were more interested in how it reflects
-developmental change.
+word learning skills. While much of the previous investigation of this
+finding has been interested in the source of this discrepancy, here we
+have explored how it could arise from continuous developmental change in
+perceptual uncertainty.
 
@@
 
-The model made a new prediction to which we provided the first
-experimental test: Learning similar words is not only modulated by the
-similarity of their phonological forms, but also by the visual
-similarity of their semantic referents. More generally, since visual
-similarity is an early organizing feature in the semantic domain (e.g.,
-Wojcik \& Saffran, 2013), our finding suggests that children may
-prioritize the acquisition of words that are quite distant in the
-semantic space. This suggestion is supported by recent findings based on
-the investigation of early vocabulary growth (Engelthaler \& Hills,
-2017; Sizemore, Karuza, Giusti, \& Bassett, 2018).
+The model made a new prediction to which which we tested experimentally:
+Learning similar words is not only modulated by the similarity of their
+phonological forms, but also by the visual similarity of their semantic
+referents. More generally, since visual similarity is an early
+organizing feature in the semantic domain (e.g., Wojcik \& Saffran,
+2013), our finding suggests that children may prioritize the acquisition
+of words that are quite distant in the semantic space. This suggestion
+is supported by recent findings based on the investigation of early
+vocabulary growth (Engelthaler \& Hills, 2017; Sizemore, Karuza, Giusti,
+\& Bassett, 2018).
 
@@
 children at a relatively older age (4-5 years old) than what is
-typically studied in the literature (around 14 month-old). Nonetheless,
-this choice was related to two measurement difficulties. First, model
-fitting requires several, reliably-measured data points. In our case,
-data collection involved presenting participants with several trials
-across four conditions in a between-subject design. It would have been
-challenging to obtain these measures with infants. Second, the study of
-infants requires using specific testing methods. This fact would have
-made the quantitative study of development challenging. Indeed, it is
+typically studied in the literature (14-18 month-old). We selected this
+age group based on two measurement issues. First, model fitting requires
+several, reliably-measured data points. In our case, data collection
+involved presenting participants with several trials across four
+conditions in a between-subject design. It would have been challenging
+to obtain these measures with infants. Second, experiments with infants
+on this topic have often used habituation methods (but cf. Yoshida et
+al., 2009), which require additional linking assumptions. Indeed, it is
 not clear how data from these methods would directly compare to data
@@
 In sum, this paper proposes a model that accounts for the development of
-an important aspect of word learning. The findings show that data can be
-explained based on a continuous process operating over similar
-representations across development. We used a case from word learning as
-an example, but the same idea might apply to other aspects of cognitive
+an important aspect of word learning. Our account suggests that the
+developmental data can be explained based on a continuous process
+operating over similar representations across development, suggesting
+developmental continuity. We used a case from word learning as an
+example, but the same idea might apply to other aspects of cognitive
 development that are typically thought of as stage-like (e.g.,

### 2019-02-01 cogsci/cogsci.tex
final version cogsci

@@
 
-Experimental results are shown in Figure 6 (top). We first analyzed the
-results using a mixed-effects logistic regression with sound distance,
-object distance and age group as fixed effects, and with a maximal
-random effects structure (allowing us to take into account the full
-nested structure of our data) (Barr, Levy, Scheepers, \& Tily, 2013). We
-found main effects for all the fixed effects in the regression. For the
-sound distance, we obtained \(\beta =\) 0.44 (\(p\) \textless{} 0.001),
-replicating previous findings. For object distance, we found \(\beta =\)
-0.5 (\(p\) \textless{} 0.001), and this finding confirms the new
-prediction of our model. Finally, for the age group, we obtained
-\(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that performance
-improves with age. In addition, we found two-way interactions between
-sound distance and age (\(\beta =\) 0.17, \(p\) \textless{}0.05) and
-between object distance and age (\(\beta =\) 0.18, \(p\)
-\textless{}0.05).
+Experimental results are shown in Figure 6 (solid lines). We first
+analyzed the results using a mixed-effects logistic regression with
+sound distance, object distance and age group as fixed effects, and with
+a maximal random effects structure (allowing us to take into account the
+full nested structure of our data) (Barr, Levy, Scheepers, \& Tily,
+2013). We found main effects for all the fixed effects in the
+regression. For the sound distance, we obtained \(\beta =\) 0.44 (\(p\)
+\textless{} 0.001), replicating previous findings. For object distance,
+we found \(\beta =\) 0.5 (\(p\) \textless{} 0.001), and this finding
+confirms the new prediction of our model. Finally, for the age group, we
+obtained \(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that
+performance improves with age. In addition, we found two-way
+interactions between sound distance and age (\(\beta =\) 0.17, \(p\)
+\textless{}0.05) and between object distance and age (\(\beta =\) 0.18,
+\(p\) \textless{}0.05).
 
@@
 Thus, the model has two degrees of freedom for each group, i.e.,
-\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (bottom) shows
-the predictions. The model captures the qualitative patterns in both age
-groups: starting from a low accuracy recognition when both the sound and
-object distances are small, the model correctly predicts an increase in
-accuracy when either the sound distance or the object distance
-increases. Further, accuracy is correctly predicted to be maximal when
-both the sound and object distances are high.
+\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (dashed lines)
+shows the predictions. The model captures the qualitative patterns in
+both age groups: starting from a low accuracy recognition when both the
+sound and object distances are small, the model correctly predicts an
+increase in accuracy when either the sound distance or the object
+distance increases. Further, accuracy is correctly predicted to be
+maximal when both the sound and object distances are high.
 

### 2019-02-01 cogsci/cogsci.Rmd
final version cogsci

@@
 Subsequent findings have suggested otherwise.
-On the one hand, 14-month-olds---who typically fail in the original tas---succeed when an easier testing method is used, even under the same learning conditions [@yoshida2009].
+On the one hand, 14-month-olds---who typically fail in the original task---succeed when an easier testing method is used, even under the same learning conditions [@yoshida2009].
 They also succeed when uncertainty is mitigated via disambiguating cues [e.g., @thiessen2007].
@@
 $$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
-Finally, we assume there to be one-to-one mappings between concepts and labels, and that observers have successfully learned these mappings during the exposure phase:
+Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
 $$
@@
 
-We used Equation 1 to obtain the exact analytical expression for the probability of accurate responses $p(o_T | s)$ (target object $o_T$ given a sound $s$) in the simple case of two-alternative forced choice in the testing phase of our experimental task:
+We used Equation 1 and the probability distributions defined above to obtain the exact analytical expression for the probability of accurate responses $p(o_T | s)$ (target object $o_T$ given a sound $s$) in the simple case of two-alternative forced choice in the testing phase of our experimental task:
 
@@
 ```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
-Adults).
+adults).
 We show both experimental results (solid lines) and model predictions (dashed lines).
@@
 
-Experimental results are shown in Figure 6 (top).
+Experimental results are shown in Figure 6 (solid lines).
 We first analyzed the results using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) [@barr2013].
@@
 Thus, the model has two degrees of freedom for each group, i.e., $\sigma_C$ and $\sigma_L$.
-Figure \ref{fig:data_all} (bottom) shows the predictions.
+Figure \ref{fig:data_all} (dashed lines) shows the predictions.
 The model captures the qualitative patterns in both age groups: starting from a low accuracy recognition when both the sound and object distances are small, the model correctly predicts an increase in accuracy when either the sound distance or the object distance increases.
@@
 
-The model made a new prediction to which which we tested experimentally: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
+The model made a new prediction to which we tested experimentally: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
 More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.
@@
 We used a case from word learning as an example, but the same idea might apply to other aspects of cognitive development that are typically thought of as stage-like (e.g., acquisition of a theory of mind).
-Computational models such as the one proposed here can help us investigate the extent to which such discontinuities emerge due to genuine qualitative changes, and the extent to which they reflect the granularity of the researchers' own measurement tools.
+Computational models, such as the one proposed here, can help us investigate the extent to which such discontinuities emerge due to genuine qualitative changes and the extent to which they reflect the granularity of the researchers' own measurement tools.
 

### 2019-02-01 cogsci/cogsci.tex
final version cogsci

@@
 Subsequent findings have suggested otherwise. On the one hand,
-14-month-olds---who typically fail in the original tas---succeed when an
-easier testing method is used, even under the same learning conditions
-(Yoshida, Fennell, Swingley, \& Werker, 2009). They also succeed when
-uncertainty is mitigated via disambiguating cues (e.g., Thiessen, 2007).
-On the other hand, adults show patterns of learning similar to those
-shown by 14-month-olds when the task is more challenging and when
-similarity between words increases (Pajak, Creel, \& Levy, 2016; White,
-Yee, Blumstein, \& Morgan, 2013).
+14-month-olds---who typically fail in the original task---succeed when
+an easier testing method is used, even under the same learning
+conditions (Yoshida, Fennell, Swingley, \& Werker, 2009). They also
+succeed when uncertainty is mitigated via disambiguating cues (e.g.,
+Thiessen, 2007). On the other hand, adults show patterns of learning
+similar to those shown by 14-month-olds when the task is more
+challenging and when similarity between words increases (Pajak, Creel,
+\& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
 
@@
 \[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] Finally, we assume
-there to be one-to-one mappings between concepts and labels, and that
+there to be one-to-one mappings between concepts and labels and that
 observers have successfully learned these mappings during the exposure
@@
 
-We used Equation 1 to obtain the exact analytical expression for the
-probability of accurate responses \(p(o_T | s)\) (target object \(o_T\)
-given a sound \(s\)) in the simple case of two-alternative forced choice
-in the testing phase of our experimental task:
+We used Equation 1 and the probability distributions defined above to
+obtain the exact analytical expression for the probability of accurate
+responses \(p(o_T | s)\) (target object \(o_T\) given a sound \(s\)) in
+the simple case of two-alternative forced choice in the testing phase of
+our experimental task:
 
@@
 \caption{\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
-Adults).
+adults).
 We show both experimental results (solid lines) and model predictions (dashed lines).
@@
 
-The model made a new prediction to which which we tested experimentally:
+The model made a new prediction to which we tested experimentally:
 Learning similar words is not only modulated by the similarity of their
@@
 development that are typically thought of as stage-like (e.g.,
-acquisition of a theory of mind). Computational models such as the one
-proposed here can help us investigate the extent to which such
-discontinuities emerge due to genuine qualitative changes, and the
-extent to which they reflect the granularity of the researchers' own
+acquisition of a theory of mind). Computational models, such as the one
+proposed here, can help us investigate the extent to which such
+discontinuities emerge due to genuine qualitative changes and the extent
+to which they reflect the granularity of the researchers' own
 measurement tools.

### 2019-02-02 cogsci/cogsci.Rmd
final version cogsci

@@
 author-information: >
-    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
-    \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University
-    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
+
+    \author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }
 
@@
 ```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
-A word is represented with a distribution over the perceptual space (indicated in red or green).
+A word is represented with a distribution over the perceptual space (indicated in red or blue).
 When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
@@
 One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-18 month-old).
-We selected this age group based on two measurement issues.
-First, model fitting requires several, reliably-measured data points.
-In our case, data collection involved presenting participants with several trials across four conditions in a between-subject design.
-It would have been challenging to obtain these measures with infants.
-Second, experiments with infants on this topic have often used habituation methods [but cf.
+We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting).
+Data collection involved presenting participants with several trials across four conditions in a between-subject design.
+It would have been challenging to obtain such measures with infants.
+<!--Second, experiments with infants on this topic have often used habituation methods [but cf.
 @yoshida2009], which require additional linking assumptions.
 Indeed, it is not clear how data from these methods would directly compare to data collected using more typical methods in older children and adults.
+-->
 <!--While an important conclusion of this paper is that the same process may apply to different developmental stages, it would be interesting to experimentally verify the generality of this conclusion in the context of early language acquisition.
@@
 
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}
+
 <!--
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
-
 # Acknowledgements
@@
 This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
+-->
 
--->
 # References

### 2019-02-02 cogsci/cogsci.tex
final version cogsci

@@
 
-\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
-Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
+\author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }
 
@@
 \caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
-A word is represented with a distribution over the perceptual space (indicated in red or green).
+A word is represented with a distribution over the perceptual space (indicated in red or blue).
 When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
@@
 typically studied in the literature (14-18 month-old). We selected this
-age group based on two measurement issues. First, model fitting requires
-several, reliably-measured data points. In our case, data collection
-involved presenting participants with several trials across four
-conditions in a between-subject design. It would have been challenging
-to obtain these measures with infants. Second, experiments with infants
-on this topic have often used habituation methods (but cf. Yoshida et
-al., 2009), which require additional linking assumptions. Indeed, it is
-not clear how data from these methods would directly compare to data
-collected using more typical methods in older children and adults.
+older age group to optimize the number and precision of the experimental
+measures (both are crucial to model fitting). Data collection involved
+presenting participants with several trials across four conditions in a
+between-subject design. It would have been challenging to obtain such
+measures with infants.
 
@@
 measurement tools.
+
+\vspace{1em}
+
+\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}}
+\vspace{1em}
 

### 2019-04-05 Analysis/process.Rmd
adults N 100

@@
 The following are the analysese done with adult pilot data.
-We plan to collect data from 60 participants on Amazaon MTurk.
+We plan to collect data from 100 participants on Amazaon MTurk.
 
@@
   left_join(d_adult_excl) %>%
-  filter(score >0.7) %>%
+  filter(score ==1) %>%
   filter(sound_dist != 'catch')
 
-feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
+#feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
 ```
@@
 ```{r}
-d_child <- read_delim("data_summer_all.txt", delim = " ") %>%
+d_child <- read_delim("kids_all.txt", delim = " ") %>%
   filter(type == "Test") %>%
@@
 
-feather::write_feather(d_child_good, "../saved_data/data_child.feather")
+#feather::write_feather(d_child_good, "../saved_data/data_child.feather")
 
@@
 
-Summary
-
+Summary children
 ```{r}
-
-sum_adult <- d_adult_good %>%
-  group_by(sound_dist, concept_dist) %>%
-  dplyr::summarise(mean = mean(iscorrect),
-                   sd = sd(iscorrect),
-                   n = n()) %>%
-  mutate(se = sd / sqrt(n),
-         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
-         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
-  select(-sd, -n, -se)
-
 sum_child <- d_child_good %>%
@@
 
-Plots
-```{r fig.width=3, fig.height=1.7}
+Plot children
+```{r fig.width=5, fig.height=4}
 
@@
 
+```
+Summary adults
+
+```{r}
+
+sum_adult <- d_adult_good %>%
+  group_by(sound_dist, concept_dist) %>%
+  dplyr::summarise(mean = mean(iscorrect),
+                   sd = sd(iscorrect),
+                   n = n()) %>%
+  mutate(se = sd / sqrt(n),
+         lower.ci = mean - qt(1 - (0.05 / 2), n - 1) * se,
+         upper.ci = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
+  select(-sd, -n, -se)
+
+```
+
+```{r}
+
 sum_adult$concept_dist <- factor(sum_adult$concept_dist, levels = c("similar", "different"))
@@
       axis.text = element_text(size = 11)
-      ) #+ facet_grid(. ~ block)
+      ) #+ facet_grid(. ~ concept)
 

### 2019-05-14 Analysis/process.Rmd
cogsci camera ready

@@
 #The following is a test with adult pilot data
-d_adult <- read_delim("adults_final.txt", delim = " ")  %>%
-#d_adult <- read_delim("adult_pilot_3.txt", delim = " ")  %>%
+#d_adult <- read_delim("adults_final.txt", delim = " ")  %>%
+d_adult <- read_delim("adults_100.txt", delim = " ")  %>%
   filter(type == "Test", #Here I will  filter out particiapants whose first language is arabic or hindi
@@
   left_join(d_adult_excl) %>%
-  filter(score ==1) %>%
+  filter(score == 1) %>%
   filter(sound_dist != 'catch')
 
-#feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
+feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
 ```
@@
 
-#feather::write_feather(d_child_good, "../saved_data/data_child.feather")
+feather::write_feather(d_child_good, "../saved_data/data_child.feather")
 
@@
 Plot children
-```{r fig.width=5, fig.height=4}
+```{r}
 
@@
       axis.text = element_text(size = 11)
-      ) #+ facet_grid(.~block)
+      )# + facet_grid(.~block)
 
@@
       axis.text = element_text(size = 11)
-      ) #+ facet_grid(. ~ concept)
+      ) #+ facet_grid(. ~ block)
 
@@
 
-Models
+Regression Model
 ```{r}
@@
 
-#Combine both  
+#Add a centerd variable for age group and combine both data 
 data_both_ch <- data_ch %>%
@@
 #Process the data to prepare for the fit
+
+#Extract distance values
+dist_sim_c <- round(d_sim_process$mean[which(d_sim_process$condition=='obj_real' & d_sim_process$labels=='similar')],2)
+dist_inter_c <- round(d_sim_process$mean[which(d_sim_process$condition=='obj_real' & d_sim_process$labels=='intermediate')],2)
+dist_diff_c <- round(d_sim_process$mean[which(d_sim_process$condition=='obj_real' & d_sim_process$labels=='different')],2)
+
+dist_sim_s <- d_sim_process$mean[which(d_sim_process$condition=='sound_real' & d_sim_process$labels=='similar')]
+dist_inter_s <- d_sim_process$mean[which(d_sim_process$condition=='sound_real' & d_sim_process$labels=='intermediate')]
+dist_diff_s <- d_sim_process$mean[which(d_sim_process$condition=='sound_real' & d_sim_process$labels=='different')]
+
+#Here normalize the sound with respect to the most distant pair
+
+dist_sim_s <- round(dist_sim_s/dist_diff_s,2)
+dist_inter_s <- round(dist_inter_s/dist_diff_s,2)
+dist_diff_s <- round(dist_diff_s/dist_diff_s,2)
+
+#For adults: use the similar vs. intermediate pairs
 data_fit_adult <- sum_adult %>%
@@
   mutate(group = 'adults',
-         s_dist = ifelse(sound_dist =='different',  0.66, 0.23),
-         c_dist = ifelse(concept_dist =='different', 0.40, 0.19))
+         s_dist = ifelse(sound_dist =='different',  dist_inter_s, dist_sim_s),
+         c_dist = ifelse(concept_dist =='different', dist_inter_c, dist_sim_c))
 
+#For children: use the intermediate vs. different pairs 
 data_fit_child <- sum_child %>% 
    mutate(group = 'children',
-         s_dist = ifelse(sound_dist =='different',  1, 0.66),
-         c_dist = ifelse(concept_dist =='different', 1, 0.40))
+         s_dist = ifelse(sound_dist =='different',  dist_diff_s, dist_inter_s),
+         c_dist = ifelse(concept_dist =='different', dist_diff_c, dist_inter_c))
 
@@
 
-Now I need to predict accuracy as a function of sound and meaning similarity 
+Now I need to predict the mean accuracy as a function of sound and meaning similarity 
 ```{r}
@@
   acc <- 1 + exp(-((s1-s)^2+(o1-o)^2)/(2*(Vr)^2)) 
+  acc_norm <- acc/(acc+no_acc)
+
+  return(acc_norm)
+}
+
+no_combine_cues <- function(s, o, Vr) {
+  s1 = 0
+  o1 = 0
+
+   no_acc <- exp(-(s1-s)^2/(2*(Vr)^2)) 
+  acc <- 1 
   acc_norm <- acc/(acc+no_acc)
@@
 
+fit_adults_no <- nls(mean ~ no_combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='adults'), start=list(Vr=0.5), lower=c(0), algorithm="port")
+
 fit_adults_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='adults'), start=list(Vr_s=0.1, Vr_o=0.1), lower=c(0,0), algorithm="port")
@@
 Vr_ad <- coef(fit_adults)
+Vr_ad_no <- coef(fit_adults_no)
 Vr_s_ad <- coef(fit_adults_2)[1]
@@
 
+fit_children_no <- nls(mean ~ no_combine_cues(s_dist, c_dist, Vr), data=subset(data_fit, group=='children'), start=list(Vr=0.5), lower=c(0), algorithm="port")
+
 fit_children_2 <- nls(mean ~ combine_cues_2(s_dist, c_dist, Vr_s, Vr_o), data=subset(data_fit, group=='children'), start=list(Vr_s=0.5, Vr_o=0.3), lower=c(0,0), algorithm="port")
@@
 Vr_ch <- coef(fit_children)
+Vr_ch_no <- coef(fit_children_no)
 Vr_s_ch <- coef(fit_children_2)[1]
@@
               mutate(val= Vr_ad, 
+                     model=1, 
+                     group = "adults"))
+
+model_no_val <- as.data.frame(confint2(fit_children_no)) %>%
+  mutate(val= Vr_ch_no, 
+         model=1, 
+         group = "children") %>%
+  bind_rows(as.data.frame(confint2(fit_adults)) %>%
+              mutate(val= Vr_ad_no, 
                      model=1, 
@@
 
-model_comparison <- tibble::rownames_to_column(AIC(fit_adults, fit_adults_2), 'model') %>%
-  bind_rows(tibble::rownames_to_column(AIC(fit_children, fit_children_2), 'model'))
+#model_comparison <- tibble::rownames_to_column(AIC(fit_adults, fit_adults_2), 'model') %>%
+#  bind_rows(tibble::rownames_to_column(AIC(fit_children, fit_children_2), 'model'))
 
 feather::write_feather(model1_val, "../saved_data/values_mod1.feather")  
+feather::write_feather(model_no_val, "../saved_data/values_mod_no.feather")
+
 feather::write_feather(model2_val, "../saved_data/values_mod2.feather")
 
-feather::write_feather(model_comparison, "../saved_data/model_comparison.feather")
+#feather::write_feather(model_comparison, "../saved_data/model_comparison.feather")
 
@@
                              )) %>%
+  mutate(prediction_no = ifelse(group=='adults', 
+                             no_combine_cues(s_dist, c_dist, Vr_ad_no),
+                             no_combine_cues(s_dist, c_dist, Vr_ch_no)
+                             )) %>%
   mutate(prediction_2 = ifelse(group=='adults', 
@@
 feather::write_feather(model_data, "../saved_data/data_correlations.feather")
+R2_model1 <-  round(cor(model_data$human, model_data$prediction)^2, 2)
+R2_model_no <-  round(cor(model_data$human, model_data$prediction_no)^2, 2)
+R2_model2 <-  round(cor(model_data$human, model_data$prediction_2)^2, 2)
 
 model_data_plot <-  model_data %>%
-  gather(key, value, human, prediction, prediction_2) %>%
-  mutate(ci.upper = ifelse(key=='human', upper, value),
-         ci.lower = ifelse(key=='human', lower, value))
+  gather(key, value, prediction, prediction_no, prediction_2) #%>%
+  #mutate(ci.upper = ifelse(key=='human', upper, value),
+  #       ci.lower = ifelse(key=='human', lower, value))
 
 feather::write_feather(model_data_plot, "../saved_data/data_human_model.feather")
+
+```
+
+```{r}
+
+model_data_plot$group <- factor(model_data_plot$group, levels = c("children", "adults"))
+
+ggplot(subset(model_data_plot, key == "human"), 
+      aes(x = sound_dist, y = value, 
+          group = factor(concept_dist), 
+          col = factor(concept_dist)
+          )) +
+  #geom_point()+
+  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
+                 position = position_dodge(width = .1),
+                 size=0.2) + 
+  geom_line() + 
+  geom_line(data=subset(model_data_plot, key == "prediction"), linetype=2, size=0.5, col='black')+
+  geom_point(data=subset(model_data_plot, key == "prediction"), size=1, col='black')+
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("Auditory similary") +ylab("Accuracy")+
+  scale_colour_discrete(name="Visual similarity")+
+  theme_few()+
+theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11)
+      ) + facet_grid(.~group) +
+  theme(aspect.ratio = 0.7)
+
+ggplot(subset(model_data_plot, key == "human"), 
+      aes(x = sound_dist, y = value, 
+          group = factor(concept_dist), 
+          col = factor(concept_dist)
+          )) +
+  #geom_point()+
+  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
+                 position = position_dodge(width = .1),
+                 size=0.2) + 
+  geom_line() + 
+  geom_line(data=subset(model_data_plot, key == "prediction_2"), linetype=2, size=0.5, col='black')+
+  geom_point(data=subset(model_data_plot, key == "prediction_2"), size=1, col='black')+
+  geom_hline(yintercept = 0.50, linetype="dashed") +
+  xlab("Auditory similary") +ylab("Accuracy")+
+  scale_colour_discrete(name="Visual similarity")+
+  theme_few()+
+theme(legend.title = element_text(size=11),
+      legend.text=element_text(size=11),
+      axis.text = element_text(size = 11)
+      ) + facet_grid(.~group) +
+  theme(aspect.ratio = 0.7)
 
@@
 
+plots 
 ```{r}
 
-model_data_plot$group <- factor(model_data_plot$group, levels = c("children", "adults"))
-
-ggplot(subset(model_data_plot, key == "human"), 
-      aes(x = sound_dist, y = value, 
-          group = factor(concept_dist), 
-          col = factor(concept_dist)
-          )) +
-  #geom_point()+
-  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
-                 position = position_dodge(width = .1),
-                 size=0.2) + 
-  geom_line() + 
-  geom_line(data=subset(model_data_plot, key == "prediction_2"), linetype=2, size=0.5, col='black')+
-  geom_point(data=subset(model_data_plot, key == "prediction_2"), size=1, col='black')+
-  geom_hline(yintercept = 0.50, linetype="dashed") +
-  xlab("Auditory similary") +ylab("Accuracy")+
-  scale_colour_discrete(name="Visual similarity")+
-  theme_few()+
-theme(legend.title = element_text(size=11),
-      legend.text=element_text(size=11),
-      axis.text = element_text(size = 11)
-      ) + facet_grid(.~group) +
-  theme(aspect.ratio = 0.7)
-
-```
-
-plots 
-```{r}
+x <- 0
 
@@
 
-s = seq(-1,2.5,0.01)
+s = seq(-1.5,4,0.01)
 y = Gdist(0,1,x)
 
-illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Disambiguation') %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Disambiguation')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambiguation')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambiguation')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Development')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Development')) %>%
+illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=1, s), rep = "1", case = "low accuracy", type='Disambiguation') %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=2, Vr=1, s), rep = "2", case = "low accuracy", type='Disambiguation')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.5, s), rep = "1", case = "high accuracy", type='Disambiguation')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=2, Vr=0.5, s), rep = "2", case = "high accuracy", type='Disambiguation')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.5, s), rep = "1", case = "low accuracy", type='Development')) %>%
+  bind_rows(data.frame(x=s, y=Gdist(s0=1, Vr=0.5, s), rep = "2", case = "low accuracy", type='Development')) %>%
   bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Development')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Development'))
+  bind_rows(data.frame(x=s, y=Gdist(s0=2, Vr=0.1, s), rep = "2", case = "high accuracy", type='Development'))
 
@@
 
-ggplot(illustration, aes(x=x, y=y, linetype=rep)) + 
+ggplot(illustration, aes(x=x, y=y, col=rep)) + 
   geom_line() + 
@@
       )+
-  #xlim(c(-1,1))+
-  #ylim(c(0,1))+
-  #geom_vline(xintercept = 0.0, color="red") +
-  #geom_segment(aes(x = 0, y = 0, xend = 0, yend = y, colour = rep),
-  #             position=position_dodge(width = .2), 
+  #geom_col(aes(x = x, y = y, fill = rep),
+  #             position=position_dodge(), 
+  #             width=0.2,
   #             data = subset(illustration, x==0))+
-
-  geom_col(aes(x = x, y = y, fill = rep),
-               position=position_dodge(), 
-               width=0.2,
-               data = subset(illustration, x==0))+
-  geom_text(aes(label=paste("Acc=", prob, sep="")),
-            x=2, y=1, size=4, 
-            fontface = "bold",
-            data=probs)+
+  #geom_text(aes(label=paste("Acc=", prob, sep="")),
+  #          x=2, y=1, size=4, 
+  #          fontface = "bold",
+  #          data=probs)+
   xlab("Perceptual space") + ylab("Prob") +
@@
   theme(legend.position="none")
+  #xlim(c(-1,3))
 
 ```
+
+Regression
+
+```{r}
+data_ch <- d_child_good %>%
+  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
+         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
+  rename(accuracy = iscorrect)
+
+data_ad <- d_adult_good %>%
+  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
+         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
+  rename(accuracy = iscorrect)
+
+#Combine both  
+data_both_ch <- data_ch %>%
+  select(ID, c_dist, s_dist, item_object, item_sound, accuracy) %>%
+  mutate(age = -1)
+
+data_both_ad <- data_ad %>%
+  select(ID, c_dist, s_dist, concept, sound, accuracy) %>%
+  rename(item_object = concept,
+         item_sound = sound) %>%
+  mutate(age = 1) %>%
+  mutate(ID2 = sub("+$", "_ad", ID)) %>%
+  select(-ID) %>%
+  rename(ID=ID2)
+
+data_both <- data_both_ch %>%
+  bind_rows(data_both_ad)
+
+model_both <- glmer(accuracy ~ s_dist * c_dist * age+ 
+                 (s_dist * c_dist  | ID) + 
+                 (c_dist | item_object) + 
+                 (s_dist | item_sound) +
+                 (s_dist * c_dist | age), 
+               data = data_both, family = binomial(),
+               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
+
+model_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(model_both))), "effect")
+
+feather::write_feather(model_coef, "../saved_data/model_regression.feather")
+
+```

### 2019-05-14 cogsci/cogsci.Rmd
cogsci camera ready

@@
 
-    \author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }
+    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
+    \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ University of Illinois
+    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
 
@@
 Indeed, though infants around 14-month old can distinguish similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects.
-Follow-up studies has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017;  @rost2009].
+Follow-up studies have focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017;  @rost2009].
 
@@
 They also succeed when uncertainty is mitigated via disambiguating cues [e.g., @thiessen2007].
-On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases [@white2013; @pajak2016].
+On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when the similarity between words increases [@white2013; @pajak2016].
 
@@
 Development is a continuous process whereby the initial noisy representations become more precise.
-In addition, more precise representation are still imperfect: Even adults show low accuracy learning when the sounds are subtle, e.g., non-native sounds [@pajak2016].
+In addition, more precise representations are still imperfect: Even adults show low accuracy learning when the sound contrasts are subtle, e.g., non-native sounds [@pajak2016].
 
@@
 Though infants could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large uncertainty of the encoding, and this confusion leads to "failure" in the recognition task.
-According to this account, accuracy in word learning improves if we increase either the perceptual distinctiveness of the stimuli (e.g., through using different-sounding labels), or the precision of the encoding itself (e.g., across development).
+According to this account, accuracy in word learning improves if we increase either the perceptual distinctiveness of the stimuli (e.g., through using different-sounding labels) or the precision of the encoding itself (e.g., across development).
 
@@
 
-```{r}
-
-Gdist <- function(s0, Vr, s){
-  return((1/sqrt(2*pi*Vr))*exp(-(s0-s)^2/(2*Vr)))
-}
-
-s = seq(-1,2.5,0.01)
-y = Gdist(0,1,s)
-
-illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Distinctiveness') %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Distinctiveness')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Distinctiveness')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Distinctiveness')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Precision')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Precision')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Precision')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Precision'))
-
-illustration$case <- factor(illustration$case, levels = c("low accuracy", "high accuracy"))
-illustration$type <- factor(illustration$type, levels = c("Distinctiveness", "Precision"))
-
-probs <- subset(subset(illustration, x==0)) %>%
-  group_by(type, case) %>%
-  mutate(prob = round(y/sum(y),2)) %>%
-  filter(rep=='1')
-
-```
-
-```{r fig.width=2, fig.height=2.5}
-illus_plot <- ggplot(illustration, aes(x=x, y=y, col=rep)) + 
-  geom_line() + 
-  theme_few()+
-  theme(legend.title = element_text(size=9),
-      legend.text=element_text(size=9),
-      axis.text = element_text(size = 9),
-      strip.text = element_text(size = 9),
-      axis.title = element_text(size = 9),
-      aspect.ratio = 0.7
-      )+
-
-  geom_col(aes(x = x, y = y, fill = rep),
-               position=position_dodge(), 
-               width=0.2,
-               data = subset(illustration, x==0))+
-  geom_text(aes(label=paste("Acc=", prob, sep="")),
-            x=1.7, y=1, size=3, 
-            data=probs, 
-            col='black')+
-  xlab("Perceptual space") + ylab("Prob") +
-  facet_grid(type~case) +
-  theme(legend.position="none")
-
-```
-
-```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
+```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "An illustration of the probabilistic/continuous account using simulated data.
 A word is represented with a distribution over the perceptual space (indicated in red or blue).
 When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
-The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel)."}
+The accuracy increases when the stimuli are less similar (left panel), or when the representations are more precise (right panel)."}
 
@@
 
-```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, sanitize=FALSE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ and $\\Delta o$ and representation precision $\\sigma$ (For clarity, we assume here that $\\sigma$=$\\sigma_C$=$\\sigma_L$).
+```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, sanitize=FALSE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ and $\\Delta o$ and representation precision $\\sigma$ (for simplicity, we assume here that $\\sigma$=$\\sigma_C$=$\\sigma_L$).
 Dashed line represents chance."}
@@
 This is a new prediction that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [e.g., @fennell2010; @rost2009; @thiessen2007], but to our knowledge no previous study in the literature tested the effect of the visual distance between the semantic referents.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [e.g., @fennell2010; @rost2009; @thiessen2007], but to our knowledge, no previous study in the literature tested the effect of the visual distance between the semantic referents.
 
@@
 
-d_child <- read_delim("../Analysis/data_summer_all.txt", delim = " ") %>%
+d_child <- read_delim("../Analysis/kids_all.txt", delim = " ") %>%
   filter(type == "Test") %>%
@@
 
-d_adult <- read_delim("../Analysis/adults_final.txt", delim = " ")  %>%
+d_adult <- read_delim("../Analysis/adults_100.txt", delim = " ")  %>%
   filter(type == "Test") %>%
@@
 ### Participants
-We planned to recruit a sample of N=60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
-Here we report data from n=`r N_good_ch` children.
-An additional n=`r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
-We also planned to recruit a sample of N=60 adults on Amazon Mechanical Turk.
-Data from n=`r N_all_ad-N_good_ad` participants were excluded due to low scores on the catch trials (n=`r N_all_ad-N_good_ad-d_adult_lang` ) or because they were familiar with the non-English sound stimuli we used in the adult experiment (n=`r d_adult_lang`), yielding a final sample of n=`r N_good_ad`.
+We planned to recruit a sample of $N=60$ children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
+Here we report data from $N=$ `r N_good_ch` children.
+An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
+We also collected a planned sample of $N=100$ adult participants through Amazon Mechanical Turk.
+We planned to exclude data from participants who did not do well on the catch trials ($N=$ `r N_all_ad-N_good_ad`) and from participants who were familiar with the non-English sound stimuli we used in the adult experiment ($N=$ `r d_adult_lang`), yielding a final sample of $N=$ `r N_good_ad`.
 
@@
 Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs.
-"intermediate" for preschoolers, and "intermediate" vs.
+"intermediate" for preschoolers and "intermediate" vs.
 "similar" for adults.
 We made this choice in light of pilot studies showing that adults were at ceiling with "different" sounds/objects, and children were at chance with the "similar" sounds/objects.
-That said, this difference in the level of similarity is accounted for in the model through using the appropriate perceptual distance used in each age group (Figure \ref{fig:stim}).
+That said, this difference in the level of similarity is accounted for in the model by using the appropriate perceptual distance used in each age group (Figure \ref{fig:stim}).
 
@@
 To maximize our ability to measure subtle stimulus effects, the experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
-Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
+Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones but was used only to select participants who were able to follow the instructions and show minimal learning.
 
-```{r }
-
+```{r}
 #Import data from saved
 data_human_model <- feather::read_feather("../saved_data/data_human_model.feather") %>%
-  mutate(source = ifelse(key == "human", "Experimental",
-                         ifelse(key == "prediction", "Model 1", "Model"))) %>%
-  filter(source != "Model 1")
+  filter(key != "prediction_no") %>%
+  mutate(key = ifelse(key == "prediction", "Single Variance","Double Variance"))
 
 data_human_model$group <- factor(data_human_model$group, levels = c("children", "adults"))
+data_human_model$key <- factor(data_human_model$key, levels = c("Single Variance", "Double Variance"))
 
-plot_data <- ggplot(subset(data_human_model, source =='Experimental'), 
-#plot_data <- ggplot(data_human_model, 
-      aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
-  #geom_point()+
-  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
+plot_data <- ggplot(data_human_model, 
+      aes(x = sound_dist, y = human, group = factor(concept_dist), col = factor(concept_dist))) +
+  geom_point()+
+  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1),
@@
   geom_line() + 
-  geom_line(data=subset(data_human_model, source == "Model"), linetype=2, size=0.5)+
-  geom_point(data=subset(data_human_model, source == "Model"), size=1.5, alpha=0.5)+
+  geom_line(aes(x=sound_dist, y=value), 
+            position = position_dodge(width = .2),
+            linetype=2,
+            size=0.5)+
+  geom_point(aes(x=sound_dist, y=value),
+             position = position_dodge(width = .2),
+             size=1.5, alpha=0.5)+
   geom_hline(yintercept = 0.50, linetype="dashed") +
@@
       #) + facet_grid(group~source, scales="free_y") +
-      ) + facet_grid(.~group) +
-  theme(aspect.ratio = 0.7)
-
-#ggsave("figs/data_all.png", plot = plot_data, width = 3, height = 6)
-#ggsave("figs/data_all.png", plot = plot_data, width = 8, height = 16)
+      ) + facet_grid(key~group) +
+  theme(aspect.ratio = 0.7)+
+  ylim(c(0.45,1))
 
 ```
+
 ### Procedure
@@
 -->
-
 Preschoolers were tested at the nursery school using a tablet, whereas adults used their own computers to complete the same experiment online.
@@
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
 adults).
-We show both experimental results (solid lines) and model predictions (dashed lines).
+We show both the models' predictions (dashed lines) and the experimental results (solid lines).
 Error bars represent 95\\% confidence intervals."}
@@
 
-```{r, results='asis'}
+```{r}
 
-data_ch <- feather::read_feather("../saved_data/data_child.feather") %>%
-  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
-         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
-  rename(accuracy = iscorrect)
-data_ad <- feather::read_feather("../saved_data/data_adult.feather") %>%
-  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
-         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
-  rename(accuracy = iscorrect)
-
-#Combine both  
-data_both_ch <- data_ch %>%
-  select(ID, c_dist, s_dist, item_object, item_sound, accuracy) %>%
-  mutate(age = -1)
-
-data_both_ad <- data_ad %>%
-  select(ID, c_dist, s_dist, concept, sound, accuracy) %>%
-  rename(item_object = concept,
-         item_sound = sound) %>%
-  mutate(age = 1) %>%
-  mutate(ID2 = sub("+$", "_ad", ID)) %>%
-  select(-ID) %>%
-  rename(ID=ID2)
-
-data_both <- data_both_ch %>%
-  bind_rows(data_both_ad)
-
-model_both <- glmer(accuracy ~ s_dist * c_dist * age+ 
-                 (s_dist * c_dist  | ID) + 
-                 (c_dist | item_object) + 
-                 (s_dist | item_sound) +
-                 (s_dist * c_dist | age), 
-               data = data_both, family = binomial(),
-               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-model_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(model_both))), "effect")
+model_coef <- feather::read_feather("../saved_data/model_regression.feather")
 
@@
 
-Experimental results are shown in Figure 6 (solid lines).
 We first analyzed the results using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) [@barr2013].
@@
 Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that performance improves with age.
-In addition, we found two-way interactions between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`) and between object distance and age ($\beta =$ `r c_age_coef`, $p$ `r p_val(c_age_p)`).
+<!--In addition, we found two-way interactions between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`) and between object distance and age ($\beta =$ `r c_age_coef`, $p$ `r p_val(c_age_p)`).
+-->
 
@@
 
-We next fit our model (using Equation 2) to the participants' responses in each age group.
+We next fit our model (using Equation 2) to the participants' responses in each age group using non-linear least-squares.
 The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \ref{fig:stim}).
-Thus, the model has two degrees of freedom for each group, i.e., $\sigma_C$ and $\sigma_L$.
+The model has two degrees of freedom for each group, i.e., $\sigma_C$ and $\sigma_L$.
+We call it the double-variance model.
 Figure \ref{fig:data_all} (dashed lines) shows the predictions.
-The model captures the qualitative patterns in both age groups: starting from a low accuracy recognition when both the sound and object distances are small, the model correctly predicts an increase in accuracy when either the sound distance or the object distance increases.
+The double-variance model captures the behavioral patterns in both age groups: starting from a low accuracy recognition when both the sound and object distances are small, the model correctly predicts an increase in accuracy when either the sound distance or the object distance increases.
 Further, accuracy is correctly predicted to be maximal when both the sound and object distances are high.
@@
 
-The models explained the majority of the variance in the participants' mean responses ($R^2=$ `r R2_model2`, for the combined adult and children's data).
-To investigate whether the model's predictive power was due to overfitting, we fit a simplified version with only one degree of freedom (i.e., a single variance common to both sounds and objects).
-This single-variance model explained as much variance in the mean responses ($R^2=$ `r R2_model1`).
-It also captured the main qualitative patterns (graph not shown), suggesting that the explanatory power of the model is largely due to its structure, rather than its degrees of freedom.
+The double-variance model explained almost all the variance in the participants' mean responses.
+To investigate whether the model's strong predictive power was due to overfitting, we fit a simplified version with only one degree of freedom (i.e., a single variance common to both sounds and objects).
+This single-variance model also captured the main qualitative patterns and remained highly predictive ($R^2=$ `r R2_model1`).
+This result suggests that the explanatory power of the model is largely due to its structure, rather than its degrees of freedom.
 
-An unexpected outcome was that adult participants deviated slightly from the model's numbers: While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern.
-This deviation is an interesting starting point for future work as it may suggest that participants are more likely to pay attention to and integrate additional sources of information when ambiguity is higher.
+<!--An unexpected outcome was that adult participants deviated slightly from the model's numbers: While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern.
+This deviation is an interesting starting point for future work as it may suggest that participants are more likely to pay attention to and integrate additional sources of information when ambiguity is higher.-->
 
@@
 
-The model made a new prediction to which we tested experimentally: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
+The model made a new prediction which we tested experimentally: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
 More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}
+\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code are available online at\ \url{https://github.com/afourtassi/kidswitch} }} \vspace{1em}
 

### 2019-05-14 journal/ms.Rmd
cogsci camera ready

--- 2019-02-02 cogsci/cogsci.Rmd
@@
 ---
-title: "Continuous developmental change can explain discontinuities in word learning"
+title             : "Continuous developmental change can explain discontinuities in word learning"
+shorttitle        : "Continuous Development of Word Learning"
+#numbersections: true
 
-bibliography: library.bib
-csl: apa6.csl
-document-params: "10pt, letterpaper"
+author: 
+  - name          : "Abdellah Fourtassi"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Postal address"
+    email         : "afourtas@stanford.edu"
 
-header-includes:
-   - \usepackage{tipa}
-   - \usepackage[rightcaption]{sidecap}
+  - name          : "Sophie Regan"
+    affiliation   : "1"
+    email         : "sregan20@stanford.edu"
 
-author-information: >
+  - name          : "Michael C. Frank"
+    affiliation   : "1"
+    email         : "mcfrank@stanford.edu"
 
-    \author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }
+affiliation:
+  - id            : "1"
+    institution   : "Department of Psychology, Stanford University"
 
-abstract:
+author_note: |
+
+  Abdellah Fourtassi
+
+  Department of Psychology
+
+  Stanford University
+
+  50 Serra Mall
+
+  Jordan Hall, Building 420
+
+  Stanford, CA 94301
+
+abstract: |
 
@@
 
-keywords:
-    "word learning, cognitive development, computational modeling"
+keywords          : "word learning, cognitive development, computational modeling"
 
-output: cogsci2016::cogsci_paper
+header-includes:
+   - \usepackage{tipa}
+   - \usepackage[sortcites=false,sorting=none]{biblatex}
+
+bibliography      : ["references.bib"]
+
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : yes
+
+lang              : "english"
+class             : "man"
+output            : papaja::apa6_pdf
+
+citation_package: biblatex
+
 ---
 
-```{r global_options, include=FALSE}
-rm(list=ls())
-
-#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
-#                      echo=F, warning=F, cache=F, message=F, sanitize = T)
-
-knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, message=F, sanitize = T)
-
+```{r}
+knitr::opts_chunk$set(echo=F, warning=F, cache=F, message=F, sanitize = T)
 ```
 
-```{r, libraries}
+```{r load_packages, include = FALSE}
+library(papaja)
 library(png)
@@
 
-# Introduction
+#Introduction
 
@@
 Indeed, though infants around 14-month old can distinguish similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects.
-Follow-up studies has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017;  @rost2009].
 
-<!--In this work we focus, rather, on the mechanism of development. -->
+<!--Follow-up studies has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017; @rost2009]. -->
 
@@
 How does development proceed?
-Early accounts assumed that children encode words in a binary way: they either fail or succeed in encoding the relevant phonetic details (simultaneously with the meanings).
-This account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.
+The answer to this question depends on the nature of the chidlren's word encoding in the task.
+Early accounts assumed that children encode words in a rather binary way: they either fail or succeed in attending to the relevant phonetic details (simultaneously with the meanings).
+In the orginal paper, @stager1997 noted that "Infants of 14 months fail to detect the same phonetic detail that they can easily detect in a simple syllable discrimination task".
+They argued that the high cogntive demands of the task make children experience a limitation in the amount of phonetic details they can access.
+In a similar vein, Pater et al.
+(2004) argued that "when a contrast is first acquired, it is not stable and can be lost under processing demands".
+This binary account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.
 
-<!--Over the first year of life, children become sensitive to the phonetic variations that are used to distinguish meanings in their native language [@werker1984].
-One could imagine that these perceptual skills would be automatically applied to the task of word learning.
-However, developmental data show that 14 m.o children find it challenging to associate minimally different (but perceptually discriminated) sounds such as "bih" and "dih" to different objects [@stager1997].
--->
+Subsequent findings have investigated the implications of this hypothesis in both infants and adults.
+First, if the demands of the task totally empede the encoding of subtle phonetic contrasts, then infants should fail in learning the mappings between the sounds and the objects, regardless of how this learning is probed.
+However, 14-month-olds succeed in this task under the same *learning* conditions as in @stager1997, but when an easier *testing* method is used [@yoshida2009].
+Second, if the minsmatch between sound distrimination and word learning is only related to limited cognitive resources in infancy, then adults --- who have greater attentianal and working memory capacity --- should always succeed in mapping pairs of sounds they can discriminate to different objects.
+Nonetheless, even adults show patterns learning that mirror those shown by 14-month-olds [@white2013; @pajak2016].
 
-<!--can explain this finding.
-For example it is possible that the task of meaning learning increases cognitive demands on children (compared to a simple perceptual discrimination).
-In particular, it requires paying attention to both the sounds and the corresponding objects, which may hinder precise encoding in memory of some phonetic details [@stager1997; @hofer2017].
-Additional difficulty might arise from ambiguous phonological boundaries at this stage of development [e.g., @rost2009], or from uncertainty about the referential status of the novel word [@fennell2010].
--->
+This new set of evidence points towards another scenario, where the representations are encoded in a probabilistic (rather than binary) way, and where development is continuous, rather than stage-like [see also @swingley2007].
+On this account, correct representations are learned early in development, but these representations are encoded with higher uncertainty in younger children, leading to *apparent* failure in relatively demanding tasks.
+Development is a continuous process whereby the initial noisy representations become more precise.
+Crucially, in a probabilsitic account, more precise representation do not mean they perfect, thus accounting for the fact that even adults show low accuracy learning when the sounds are subtle, e.g., non-native [@pajak2016].
 
-Subsequent findings have suggested otherwise.
-On the one hand, 14-month-olds---who typically fail in the original task---succeed when an easier testing method is used, even under the same learning conditions [@yoshida2009].
-They also succeed when uncertainty is mitigated via disambiguating cues [e.g., @thiessen2007].
-On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases [@white2013; @pajak2016].
-
-This pattern of evidence points towards another scenario, where the representations are encoded in a probabilistic (rather than binary) way, and where development is continuous, rather than stage-like [see also @swingley2007].
-On this account, correct representations are learned early in development, but these representations are encoded with higher uncertainty in younger children, leading to apparent failure in relatively demanding tasks.
-Development is a continuous process whereby the initial noisy representations become more precise.
-In addition, more precise representation are still imperfect: Even adults show low accuracy learning when the sounds are subtle, e.g., non-native sounds [@pajak2016].
-
-We provide an intuitive illustration of how such an account explains patterns of learning and development in Figure \ref{fig:illus}.
+We provide an intuitive illustration of how such an account explains patterns of learning and development in Figure \@ref(fig:illus).
 We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty with which these labels are encoded.
@@
 
-<!-- "lif" vs. "neem" instead of "bih" and "dih" -->
-
-```{r}
-
-Gdist <- function(s0, Vr, s){
-  return((1/sqrt(2*pi*Vr))*exp(-(s0-s)^2/(2*Vr)))
-}
-
-s = seq(-1,2.5,0.01)
-y = Gdist(0,1,s)
-
-illustration <- data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Distinctiveness') %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Distinctiveness')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "high accuracy", type='Distinctiveness')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=1.1, Vr=0.5, s), rep = "2", case = "high accuracy", type='Distinctiveness')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.5, s), rep = "1", case = "low accuracy", type='Precision')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.5, s), rep = "2", case = "low accuracy", type='Precision')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0, Vr=0.1, s), rep = "1", case = "high accuracy", type='Precision')) %>%
-  bind_rows(data.frame(x=s, y=Gdist(s0=0.5, Vr=0.1, s), rep = "2", case = "high accuracy", type='Precision'))
-
-illustration$case <- factor(illustration$case, levels = c("low accuracy", "high accuracy"))
-illustration$type <- factor(illustration$type, levels = c("Distinctiveness", "Precision"))
-
-probs <- subset(subset(illustration, x==0)) %>%
-  group_by(type, case) %>%
-  mutate(prob = round(y/sum(y),2)) %>%
-  filter(rep=='1')
-
-```
-
-```{r fig.width=2, fig.height=2.5}
-illus_plot <- ggplot(illustration, aes(x=x, y=y, col=rep)) + 
-  geom_line() + 
-  theme_few()+
-  theme(legend.title = element_text(size=9),
-      legend.text=element_text(size=9),
-      axis.text = element_text(size = 9),
-      strip.text = element_text(size = 9),
-      axis.title = element_text(size = 9),
-      aspect.ratio = 0.7
-      )+
-
-  geom_col(aes(x = x, y = y, fill = rep),
-               position=position_dodge(), 
-               width=0.2,
-               data = subset(illustration, x==0))+
-  geom_text(aes(label=paste("Acc=", prob, sep="")),
-            x=1.7, y=1, size=3, 
-            data=probs, 
-            col='black')+
-  xlab("Perceptual space") + ylab("Prob") +
-  facet_grid(type~case) +
-  theme(legend.position="none")
-
-```
-
-```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
+```{r illus, fig.cap = "An illustration of the probabilistic/continuous account using simulated data.
 A word is represented with a distribution over the perceptual space (indicated in red or blue).
 When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
-The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel)."}
-
-img <- png::readPNG("figs/illustration.png")
-grid::grid.raster(img)
+The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).", fig.align = "center", out.width = "300px"}
+knitr::include_graphics("figs/illustration.png")
 ```
@@
 Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation.
-These variables are related in a way that reflects the simple generative scenario represented graphically in Figure \ref{fig:model}.
+These variables are related in a way that reflects the simple generative scenario represented graphically in Figure \@ref(fig:model).
 When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind.
@@
 
-\begin{SCfigure}
-\centering
-\includegraphics[width=1.5in]{figs/model.png}
-\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicate fixed model parameters.}
-\label{fig:model}
-\end{SCfigure}
+```{r model, fig.cap = "Graphical representation of our model.
+Circles indicate random variables (shading indicates observed variables).
+The squares indicate fixed model parameters.", fig.align = "center", out.width = "300px"}
+knitr::include_graphics("figs/model.png")
+```
 
@@
 $$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
+
 $$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
+
 Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
@@
 ## Inference
-<!--If we denote the correct/target object as $o_T$ and the incorrect object as $o_{\lnot T}$, then the probability of chosing the correct object is: $P(o_T|s_T) = $ 
-(see Figure \ref{fig:task})
--->
+
 The learner hears a sound $s$ and has to decide which object $o$ provides an optimal match to this sound.
@@
 $$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
-The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in Figure \ref{fig:model}:
+
+The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in Figure \@ref(fig:model):
 $$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
+
 which can be transformed using Bayes rule into:
@@
 $$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
+
 Finally, assuming that the concepts' prior probability is uniformly distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.}, we obtain the following expression, where all conditional dependencies are now well defined:
@@
 
-<!--
-```{r model, fig.env = "figure", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model.
-Circles indicate random variables (shading indicates observed variables).
-The squares indicates fixed model parameters."}
-
-img <- png::readPNG("figs/model.png")
-grid::grid.raster(img)
-
-```
--->
 ## Task and model predictions
 
-```{r task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=3, fig.cap = "\\label{fig:task}An overview of the task used in this study."}
+```{r task, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=4, fig.height=3, fig.cap = "An overview of the task used in this study."}
 
-img <- png::readPNG("figs/task.png")
-grid::grid.raster(img)
+knitr::include_graphics("figs/task.png")
 
@@
 In each of these trials, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives.
-An overview of the task is shown in Figure \ref{fig:task}.
+An overview of the task is shown in Figure \@ref(fig:task).
 
@@
 
-ggsave('simulations.png', plot = plot_simulation, width = 7, height = 2)
-#ggsave('simulations.png', plot = plot_simulation)
 ```
 
-```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, sanitize=FALSE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ and $\\Delta o$ and representation precision $\\sigma$ (For clarity, we assume here that $\\sigma$=$\\sigma_C$=$\\sigma_L$).
+```{r simulation, fig.cap = "The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ and $\\Delta o$ and representation precision $\\sigma$ (For clarity, we assume here that $\\sigma$=$\\sigma_C$=$\\sigma_L$).
 Dashed line represents chance."}
-#plot_simulation
-#ggsave(plot_simulation, filename = 'simulations.png')
-img <- png::readPNG("simulations.png")
-grid::grid.raster(img)
+plot_simulation
 
@@
 
-<!--In sum, we introduced a model that accounts for some qualitative learning patterns observed in previous studies, and makes a new prediction.
-In the experiment below, we test whether the model makes accurate quantitative predictions by fitting it to new experimental data collected from preschool children and adults.
--->
-
 # Experiment
 
-In this experiment, we tested participants in the word learning task introduced above (Figure \ref{fig:task}).
+In this experiment, we tested participants in the word learning task introduced above (Figure \@ref(fig:task)).
 More precisely, we explored the predictions related to both distinctiveness and precision.
@@
 The experiment, sample size, exclusion criteria and the model's main predictions were pre-registered.
-<!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers).
-After training, children performed a series of two-alternative forced choices.
-In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2).
-Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different.
-Our predictions were as follows.
-If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level.
-Finally, the pair of words that are similar on both levels should be the most difficult to learn.
--->
 
@@
 We scaled responses within the range [0,1].
-Data are shown in Figure \ref{fig:stim}, for each stimulus group.
+Data are shown in Figure \@ref(fig:stim), for each stimulus group.
 These data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).
@@
 
-<!--We quantified experimetnally the similarity of sound and object pairs that we generated. 
-We generated three levels of similarity pairs and "different" objects' pairs (whithin each category) by setting the values of this properties to 0 and 0.5, and to 0 and 1, respectively.
-Examples of the resuting pairs are shown in Figure XX.
-This property was the head fatness for the category "bug", the body strech for "bird", the tail size relative to the body fatness for "fish", the width of the trunk for "tree", and finally center size for "flower".
-All these continous properties varied on a scale from 0 to 1.
-similar sound pairs ("aka"/"ama" and "ada"/"aba") and two different sound pairs ("lif"/"neem" and "zem"/"doof").
-We generated a addtional pair ("nak"/"veep") which we used in the catch trial (see Procedure).
--->
-
-###Design
-
-Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs.
-"intermediate" for preschoolers, and "intermediate" vs.
-"similar" for adults.
-We made this choice in light of pilot studies showing that adults were at ceiling with "different" sounds/objects, and children were at chance with the "similar" sounds/objects.
-That said, this difference in the level of similarity is accounted for in the model through using the appropriate perceptual distance used in each age group (Figure \ref{fig:stim}).
-
-```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:stim}Distances for both sound and object pairs from an adult norming study.
-Data represent Likert values normalized to [0,1] interval.
-Error bars represent 95\\% confidence intervals."}
-
-sim_plot
-```
-
-To maximize our ability to measure subtle stimulus effects, the experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
-Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
-
 ```{r }
@@
 #Import data from saved
-data_human_model <- feather::read_feather("../saved_data/data_human_model.feather") %>%
-  mutate(source = ifelse(key == "human", "Experimental",
-                         ifelse(key == "prediction", "Model 1", "Model"))) %>%
-  filter(source != "Model 1")
+data_human_model <- feather::read_feather("../saved_data/data_human_model.feather") #%>%
+  #mutate(Model = ifelse(key == "prediction", "Single Variance", "Double Variance"))
 
 data_human_model$group <- factor(data_human_model$group, levels = c("children", "adults"))
+#data_human_model$Model <- factor(data_human_model$Model, levels = c("Single Variance", "Double Variance"))
 
-plot_data <- ggplot(subset(data_human_model, source =='Experimental'), 
-#plot_data <- ggplot(data_human_model, 
-      aes(x = sound_dist, y = value, group = factor(concept_dist), col = factor(concept_dist))) +
-  #geom_point()+
-  geom_pointrange(aes(ymin = ci.lower, ymax = ci.upper), 
+plot_data <- ggplot(data_human_model, 
+      aes(x = sound_dist, y = human, group = factor(concept_dist), col = factor(concept_dist))) +
+  geom_point()+
+  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1),
@@
       #) + facet_grid(group~source, scales="free_y") +
-      ) + facet_grid(.~group) +
-  theme(aspect.ratio = 0.7)
+      ) + facet_grid(key~group) +
+  theme(aspect.ratio = 0.7)+
+  ylim(c(0.45,1))
 
-#ggsave("figs/data_all.png", plot = plot_data, width = 3, height = 6)
-#ggsave("figs/data_all.png", plot = plot_data, width = 8, height = 16)
+plot_data
+```
+###Design
+
+Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs.
+"intermediate" for preschoolers, and "intermediate" vs.
+"similar" for adults.
+We made this choice in light of pilot studies showing that adults were at ceiling with "different" sounds/objects, and children were at chance with the "similar" sounds/objects.
+That said, this difference in the level of similarity is accounted for in the model through using the appropriate perceptual distance used in each age group (Figure \@ref(fig:stim)).
+
+```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "Distances for both sound and object pairs from an adult norming study.
+Data represent Likert values normalized to [0,1] interval.
+Error bars represent 95\\% confidence intervals."}
+
+sim_plot
 
 ```
+
+To maximize our ability to measure subtle stimulus effects, the experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
+Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
+
 ### Procedure
-
-<!--and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet.
-
-The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task.
-After the introduction and examples,
--->
 
@@
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=3, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
-adults).
-We show both experimental results (solid lines) and model predictions (dashed lines).
-Error bars represent 95\\% confidence intervals."}
-plot_data
-#img <- png::readPNG("figs/data_all.png")
-#grid::grid.raster(img)
-
-``` 
 In the exposure trials, participants saw two objects associated with their corresponding sounds.
@@
 The second sound-object association followed on the other side of the screen after 500ms.
-For both objects, visual stimuli were present for the duration of the sound clip (∼800ms).
+For both objects, visual stimuli were present for the duration of the sound clip (about 800ms).
 In the testing trials, participants saw both objects simultaneously and heard only one sound.
@@
 
-data_ch <- feather::read_feather("../saved_data/data_child.feather") %>%
-  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
-         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
-  rename(accuracy = iscorrect)
-data_ad <- feather::read_feather("../saved_data/data_adult.feather") %>%
-  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
-         c_dist=ifelse(concept_dist=="similar", -1, 1)) %>%
-  rename(accuracy = iscorrect)
-
-#Combine both  
-data_both_ch <- data_ch %>%
-  select(ID, c_dist, s_dist, item_object, item_sound, accuracy) %>%
-  mutate(age = -1)
-
-data_both_ad <- data_ad %>%
-  select(ID, c_dist, s_dist, concept, sound, accuracy) %>%
-  rename(item_object = concept,
-         item_sound = sound) %>%
-  mutate(age = 1) %>%
-  mutate(ID2 = sub("+$", "_ad", ID)) %>%
-  select(-ID) %>%
-  rename(ID=ID2)
-
-data_both <- data_both_ch %>%
-  bind_rows(data_both_ad)
-
-model_both <- glmer(accuracy ~ s_dist * c_dist * age+ 
-                 (s_dist * c_dist  | ID) + 
-                 (c_dist | item_object) + 
-                 (s_dist | item_sound) +
-                 (s_dist * c_dist | age), 
-               data = data_both, family = binomial(),
-               glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
-
-model_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(model_both))), "effect")
+model_coef <- feather::read_feather("../saved_data/model_regression.feather")
 
@@
 
-Experimental results are shown in Figure 6 (solid lines).
+```{r allData, fig.env = "figure", fig.pos = "h", fig.align='center', fig.cap = "Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+adults).
+We show both experimental results (solid lines) and model predictions (dashed lines).
+Error bars represent 95\\% confidence intervals."}
+
+plot_data
+```
+
+Experimental results are shown in Figure \@ref(fig:allData) (solid lines).
 We first analyzed the results using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) [@barr2013].
@@
 
-#Model comparison
-model_comparison <- feather::read_feather("../saved_data/model_comparison.feather")
-
-diff_adults <- model_comparison$AIC[which(model_comparison$model=='fit_adults_2')] - model_comparison$AIC[which(model_comparison$model=='fit_adults')]
-
-diff_children <- model_comparison$AIC[which(model_comparison$model=='fit_children_2')] - model_comparison$AIC[which(model_comparison$model=='fit_children')]
-
 ```
@@
 We next fit our model (using Equation 2) to the participants' responses in each age group.
-The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \ref{fig:stim}).
+The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \@ref(fig:stim)).
 Thus, the model has two degrees of freedom for each group, i.e., $\sigma_C$ and $\sigma_L$.
-Figure \ref{fig:data_all} (dashed lines) shows the predictions.
+Figure \@ref(fig:allData) (dashed lines) shows the predictions.
 The model captures the qualitative patterns in both age groups: starting from a low accuracy recognition when both the sound and object distances are small, the model correctly predicts an increase in accuracy when either the sound distance or the object distance increases.
@@
 
-<!--relative recognition accuracy across conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.
-At the quantitative level, the models explained almost all the variance in the participants' mean responses ($R^2=$ `r R2_model2`).
--->
-
-<!--We also fit a simplified model with only one degree of freedom ($\sigma = \sigma_C =\sigma_L$).
-This second model is not intended to test any theoretical hypothesis.
-We use it, rather, as a baseline to understand how much of the explanatory power of the model is due to the extra degree of freedom.
-This baseline model still captured the qualitative pattern (graph not shown), and  explained the majority of the variance ($R^2=$ `r R2_model1`).
-Besides, model comparison using Akaike information criterion yielded $AIC(model) - AIC(baseline) =$ `r round(diff_children,2)` for children data and $AIC(model) - AIC(baseline) =$ `r round(diff_adults,2)` for adult data.
-These numbers suggest that the model remains highly predictive even with one degree of freedom.
-<!--
-
-These results suggest 1) the model captures very well the experimental data, and 2) the model remains highly predictive even with one degree of freedom.
-
-Note, however, that both models predict a slight interaction between sounds and objects, but no such interaction was found in the the experimental data (Table 1)\footnote{It is possibe, however, that the absence of interaction is due to uncetainty in the experimental measurements.}
-
-We also fit a simplified model with only one degree of freedom ($\sigma = \sigma_C =\sigma_L$).
-This second model is not intended to test any theoretical hypothethesis.
-We use it, rather, as a baseline to understand how much of the explantory power of the orginal model is due to the extra degree of freedom.
-We call this baseline model the single-variance model (by contrast to the double-variance model).
-Both models were fit using weighted least-squares estimates.
--->
-
-<!--At the quantitative level, both models explained almost all the variance.
-We obtained $R^2=$ `r R2_model1` for the single-variance model, and $R^2=$ `r R2_model2` for the double-variance model.
-Besides, model comparison using Akaike information criterion yielded $AIC(double) - AIC(single) =$ `r diff_children` for children data and $AIC(double) - AIC(single) =$ `r diff_adults`.
-These numbers suggest 1) the model captures very well the experimental data, and 2) the model remains highly predictive even with one degree of freedom.
--->
-
-<!--
-For Model 1, the fitted uncertainty parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults.
-As predicted, the uncertainty parameter was larger for children than it was for adults.
-The model explained the majority of the variance ($R^2=$ `r R2_model1`).
--->
-
 # General Discussion
@@
 While much of the previous investigation of this finding has been interested in the source of this discrepancy, here we have explored how it could arise from continuous developmental change in perceptual uncertainty.
-<!--Since the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills, researchers have debated about the source of such a discrepancy.
-In this work, we were more interested in the development of this phenomenon, regardless of its exact origin.
--->
 
@@
 
-<!--That said, further work is needed to explore the effect on word learning of other semantic dimensions that could be encoded by children (e.g., conceptual/functional features). -->
-
 One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-18 month-old).
@@
 It would have been challenging to obtain such measures with infants.
-<!--Second, experiments with infants on this topic have often used habituation methods [but cf.
-@yoshida2009], which require additional linking assumptions.
-Indeed, it is not clear how data from these methods would directly compare to data collected using more typical methods in older children and adults.
--->
-<!--While an important conclusion of this paper is that the same process may apply to different developmental stages, it would be interesting to experimentally verify the generality of this conclusion in the context of early language acquisition.
-A challenge to this next step would be to construct a computational framework which would compare performance across heterogeneous testing methods (e.g., looking time vs.
-forced-choice).
--->
 
@@
 
-<!--
-More generally, our work highlights the crucial role computation models can play in theory building through both a compact organization of existing knowledge and through generating new principled hypothesis.
+\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
 
-positing discontinuous stages, as it was shown that development a continuous account as a valid framework for the study of similar word learning and the mechanism of its development.
-More generally, together with previous modeling efforts [e.g., @hofer2017], our work highlight the crucial role computation models can play in theory building through both a compact organization of existing knowledge and through generating new principled hypothesis.
+# Acknowledgements
+This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
 
-Not only does our model predict that both phonological and semantic relatedness matter in learning novel words, it also provides
-a precise account of *how* these two dimensions interact to predict learning. In fact,-->
-<!--Our model can be seen as an ideal observer [@anderson1990] in the sense that it provides a precise charaterization of the task, and shows how information can used optimally to perform this task.
-In our case, the input is categorized with uncertainty, thus the model performs an optimal probabilistic (Bayesian) inference, combining cues from both the sound and the semantic referents.
-Crucially, we assume the degree of this uncertainty to vary across development.
-Thus, although children and adults appear to behave differently, they are both near-optimal with resprect to their own encoding's uncertainty.
-Note that our model is agnostic as to the precise source of this uncertainty: part of it maybe due to ambiguous phonological boundaries [@rost], and another part could be due to various task demands [@hofer].
--->
-
-<!--To conclude, this study proposed a model of novel word is compatible with the hypothesis according to which development is not so much about a qualitative cognitive change as much as it is about the quantitative refinement of similar skills acrss the lifespan [@yoshida2009; @swingley2007; @pajak2016].
--->
-
-<!--Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [@rost2009; @thiessen2007; @dautriche2015; @fennell2010], But our study is, to our knowledge, the first to test the effect of the visual distance between the semantic referents.
--->
-
-<!--In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).
-
-That said, previous experimental work has studied the effect of phonological and semantic similarity separately.
-Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).
-However, children  acquire a lexicon which is more richly structured than these special cases.
-In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains.
-Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.
-
-One could imagine two learning scenarios.
-On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al.
-1975).
-For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity.
-Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms.
-On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002).
-Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension.
-In this study, we explore these hypothesis, bla bla -->
-
-<!--
-
-How do children acquire words?
-An important step consists in mapping a phonological form (e.g.
-the sound "cat") to a semantic referent (the concept CAT).
-A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008).
-However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998), and, though this similarity structure influnces word recognition (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
-
-Thus, a more accurate understanding of word learning should account not only for how sounds are mapped to meanings, but also for how sound and meaning similarity may influence the process of aquisition.
-
-We know that similarity affect word recognition in both adults and children.
-For example, exposure to a word such as "cat" influences subsequent recognition of phonologically and smantically similar words like "cab" and "dog" (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
-
-Crucially, similarity influences not only the recognition of know words, but also the learning of novel words.
-In the phonological domain, Swingley & Aslin (2007) showed that infants found it more challenging to learn a novel word such as "tog" (which is similar a the familiar word "dog") than to learn a word such as "shang" (which is not similar to any words children knew).
-When learning two novel words, Stager and Werker (1997) found that infatns were more likely to succeed when the words were phonologically distant (e.g., "lif"/"neem"), than when they were phonologcially simialr ("bin/"din").
-In the semantic domain, children learn the semantic relationship among newly learned words spontaneousely (Wojcik & Saffran, 2013), and they prioritize the acquisition of words that are distinct in the semantic space (Engelthaler & Hills, 2017).
-
-That said, previous experimental work has studied the effect of phonological and semantic similarity separately.
-Some studied the mechanism of word learning using a toy lexicon where only the phonological similarity varied (e.g., Stager and Werker, 1997), and others studied the learning of a toy lexicon where only the semantic similarity varied (e.g., Wojcik & Saffran, 2013).
-However, children  acquire a lexicon which is more richly structured than these special cases.
-In particular, as reviewed abvove, the end-state lexicon involves variability along both the phonological and semantic domains.
-Thus, to have a deeper understanding of word acquisition in the real world, it is crucial to study how learners acquire a lexicon that simulates this bi-dimensional variation.
-
-One could imagine two learning scenarios.
-On the first one, children’s learning, at least in some challenging situations, is primarily determined by one dimension (Sloutsky & Napolitano, 2003; Colavita et al.
-1975).
-For example, it is possible that similar sounding words are confusable and hard to learn regardless of their semantic similarity.
-Vice-versa, similar meanings might be challenging to learn regardless of the phonological similarity of their forms.
-On the second scenario, learners combine cues from both dimensions to optimize their learning (Fourtassi and Frank, 2018; Ernst & Banks, 2002).
-Thus, confusability that may arise from high similarity along one dimension can be mitigated via higher distance from the other dimension.
-In this study, we explore these hypothesis, bla bla
-
-A second goal of this work is to investigate how the learning mechanism develops over the life span.
-According to one hypothesis, adults use qualitatively distinct learning mechanisms than children, due, for example, to maturational factors.
-To illustrate, in the experimental setting used in Stager and Werker (1997), children’s difficulty with learning similar sounding words–despite their ability to perceptually differentiate them–might be attributed to their inferior working memory, hindering their ability to attend simultaneously to the sound contrast and the meanings.
-A second hypothesis proposes that learners use fundamentally similar mechanisms across the life span, and that the difference might be one of degree, not kind.
-For example, though they have vastly greater working memory capacity, adults show patterns of word processing and learning which parallel results obtained with children in Stager and Werker’s study (White et al.
-2013; Pajak et al.
-2016).
-Here we explore  -->
-
-\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}} \vspace{1em}
-
-<!--
-# Acknowledgements
-
-This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
--->
+# Disclosure statement
+None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
 
 # References
-
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
+```{r create_r-references}
+r_refs(file = "references.bib")
 ```
 
-\setlength{\parindent}{-0.1in} 
-\setlength{\leftskip}{0.125in}
-\noindent
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}

### 2019-05-14 journal/ms.tex
cogsci camera ready

--- 2019-02-02 cogsci/cogsci.tex
@@
-% Template for Cogsci submission with R Markdown
+\documentclass[english,,man,floatsintext]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{hyperref}
+\hypersetup{unicode=true,
+            pdftitle={Continuous developmental change can explain discontinuities in word learning},
+            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
+            pdfkeywords={word learning, cognitive development, computational modeling},
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\fi
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-% Stuff changed from original Markdown PLOS Template
-\documentclass[10pt, letterpaper]{article}
-
-\usepackage{cogsci}
-\usepackage{pslatex}
-\usepackage{float}
-\usepackage{caption}
-
-% amsmath package, useful for mathematical formulas
-\usepackage{amsmath}
-
-% amssymb package, useful for mathematical symbols
-\usepackage{amssymb}
-
-% hyperref package, useful for hyperlinks
-\usepackage{hyperref}
-
-% graphicx package, useful for including eps and pdf graphics
-% include graphics with the command \includegraphics
-\usepackage{graphicx}
-
-% Sweave(-like)
-\usepackage{fancyvrb}
-\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
-\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
-\newenvironment{Schunk}{}{}
-\DefineVerbatimEnvironment{Code}{Verbatim}{}
-\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
-\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
-\newenvironment{CodeChunk}{}{}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-\usepackage{color}
-
-% Use doublespacing - comment out for single spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% % Text layout
-% \topmargin 0.0cm
-% \oddsidemargin 0.5cm
-% \evensidemargin 0.5cm
-% \textwidth 16cm
-% \textheight 21cm
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
 
@@
 learning}
+    \author{Abdellah Fourtassi\textsuperscript{1}, Sophie Regan\textsuperscript{1},
+\& Michael C. Frank\textsuperscript{1}}
+    \date{}
 
+\shorttitle{Continuous Development of Word Learning}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Psychology, Stanford University}
+\keywords{word learning, cognitive development, computational modeling}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{tipa}
-\usepackage[rightcaption]{sidecap}
+\usepackage[sortcites=false,sorting=none]{biblatex}
 
-\author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }
+\authornote{ Abdellah Fourtassi
 
-\begin{document}
+Department of Psychology
 
-\maketitle
+Stanford University
 
-\begin{abstract}
-Cognitive development is often characterized in term of discontinuities,
-but these discontinuities can sometimes be apparent rather than actual
-and can arise from continuous developmental change. To explore this
-idea, we use as a case study the finding by Stager and Werker (1997)
-that children's early ability to distinguish similar sounds does not
-automatically translate into word learning skills. Early explanations
-proposed that children may not be able to encode subtle phonetic
-contrasts when learning novel word meanings, thus suggesting a
+50 Serra Mall
+
+Jordan Hall, Building 420
+
+Stanford, CA 94301
+
+Correspondence concerning this article should be addressed to Abdellah
+Fourtassi, Postal address. E-mail:
+\href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}}
+
+\abstract{
+``Cognitive development is often characterized in term of
+discontinuities, but these discontinuities can sometimes be apparent
+rather than actual and can arise from continuous developmental change.
+To explore this idea, we use as a case study the finding by Stager and
+Werker (1997) that children's early ability to distinguish similar
+sounds does not automatically translate into word learning skills. Early
+explanations proposed that children may not be able to encode subtle
+phonetic contrasts when learning novel word meanings, thus suggesting a
 discontinuous/stage-like pattern of development. However, later work has
@@
 major aspects of cognitive development that are typically thought of as
-discontinuities, may emerge from simpler, continuous mechanisms.
+discontinuities, may emerge from simpler, continuous mechanisms.''
 
-\textbf{Keywords:}
-word learning, cognitive development, computational modeling
-\end{abstract}
+}
+
+\usepackage{amsthm}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{proposition}{Proposition}[section]
+\theoremstyle{definition}
+\newtheorem{example}{Example}[section]
+\theoremstyle{definition}
+\newtheorem{exercise}{Exercise}[section]
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\newtheorem*{solution}{Solution}
+\begin{document}
+\maketitle
 
@@
 
-We use a case study from word learning literature. Stager \& Werker
+We use a case study from word learning literature. Stager and Werker
 (1997) first showed that children's early ability to distinguish similar
@@
 Indeed, though infants around 14-month old can distinguish similar sound
-pairs such as ``dih'' and ``bih'', they appear to fail in mapping this
-pair to two different objects. Follow-up studies has focused on
-proposing possible explanations for this observed gap between speech
-perception and word learning (e.g., Fennell \& Waxman, 2010; Hofer \&
-Levy, 2017; Rost \& McMurray, 2009; Stager \& Werker, 1997).
+pairs such as \enquote{dih} and \enquote{bih}, they appear to fail in
+mapping this pair to two different objects.
 
 By around 17 m.o, children succeed in the same task (Werker, Fennell,
-Corcoran, \& Stager, 2002). How does development proceed? Early accounts
-assumed that children encode words in a binary way: they either fail or
-succeed in encoding the relevant phonetic details (simultaneously with
-the meanings). This account suggested a discontinuous/stage-like pattern
-of development whereby younger children fail to encode the contrastive
-phonetic detail, whereas older children succeed.
+Corcoran, \& Stager, 2002). How does development proceed? The answer to
+this question depends on the nature of the chidlren's word encoding in
+the task. Early accounts assumed that children encode words in a rather
+binary way: they either fail or succeed in attending to the relevant
+phonetic details (simultaneously with the meanings). In the orginal
+paper, Stager and Werker (1997) noted that \enquote{Infants of 14 months
+fail to detect the same phonetic detail that they can easily detect in a
+simple syllable discrimination task}. They argued that the high cogntive
+demands of the task make children experience a limitation in the amount
+of phonetic details they can access. In a similar vein, Pater et al.
+(2004) argued that \enquote{when a contrast is first acquired, it is not
+stable and can be lost under processing demands}. This binary account
+suggested a discontinuous/stage-like pattern of development whereby
+younger children fail to encode the contrastive phonetic detail, whereas
+older children succeed.
 
-Subsequent findings have suggested otherwise. On the one hand,
-14-month-olds---who typically fail in the original task---succeed when
-an easier testing method is used, even under the same learning
-conditions (Yoshida, Fennell, Swingley, \& Werker, 2009). They also
-succeed when uncertainty is mitigated via disambiguating cues (e.g.,
-Thiessen, 2007). On the other hand, adults show patterns of learning
-similar to those shown by 14-month-olds when the task is more
-challenging and when similarity between words increases (Pajak, Creel,
-\& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
+Subsequent findings have investigated the implications of this
+hypothesis in both infants and adults. First, if the demands of the task
+totally empede the encoding of subtle phonetic contrasts, then infants
+should fail in learning the mappings between the sounds and the objects,
+regardless of how this learning is probed. However, 14-month-olds
+succeed in this task under the same \emph{learning} conditions as in
+Stager and Werker (1997), but when an easier \emph{testing} method is
+used (Yoshida, Fennell, Swingley, \& Werker, 2009). Second, if the
+minsmatch between sound distrimination and word learning is only related
+to limited cognitive resources in infancy, then adults --- who have
+greater attentianal and working memory capacity --- should always
+succeed in mapping pairs of sounds they can discriminate to different
+objects. Nonetheless, even adults show patterns learning that mirror
+those shown by 14-month-olds (Pajak, Creel, \& Levy, 2016; White, Yee,
+Blumstein, \& Morgan, 2013).
 
-This pattern of evidence points towards another scenario, where the
+This new set of evidence points towards another scenario, where the
 representations are encoded in a probabilistic (rather than binary) way,
@@
 early in development, but these representations are encoded with higher
-uncertainty in younger children, leading to apparent failure in
+uncertainty in younger children, leading to \emph{apparent} failure in
 relatively demanding tasks. Development is a continuous process whereby
-the initial noisy representations become more precise. In addition, more
-precise representation are still imperfect: Even adults show low
-accuracy learning when the sounds are subtle, e.g., non-native sounds
-(Pajak et al., 2016).
+the initial noisy representations become more precise. Crucially, in a
+probabilsitic account, more precise representation do not mean they
+perfect, thus accounting for the fact that even adults show low accuracy
+learning when the sounds are subtle, e.g., non-native (Pajak et al.,
+2016).
 
@@
 labels are encoded. For example, in Stager and Werker's original
-experiment, children are supposed to associate label 1 (``bih'') and
-label 2 (``dih'') with object 1 and object 2, respectively. Though
-infants could learn that the label ``bih'' is a better match to object 1
-than ``dih'', they could still judge the sound ``dih'' as a plausible
-instance of the label ``bih'', thanks to the relatively large
-uncertainty of the encoding, and this confusion leads to ``failure'' in
-the recognition task. According to this account, accuracy in word
-learning improves if we increase either the perceptual distinctiveness
-of the stimuli (e.g., through using different-sounding labels), or the
-precision of the encoding itself (e.g., across development).
+experiment, children are supposed to associate label 1 (\enquote{bih})
+and label 2 (\enquote{dih}) with object 1 and object 2, respectively.
+Though infants could learn that the label \enquote{bih} is a better
+match to object 1 than \enquote{dih}, they could still judge the sound
+\enquote{dih} as a plausible instance of the label \enquote{bih}, thanks
+to the relatively large uncertainty of the encoding, and this confusion
+leads to \enquote{failure} in the recognition task. According to this
+account, accuracy in word learning improves if we increase either the
+perceptual distinctiveness of the stimuli (e.g., through using
+different-sounding labels), or the precision of the encoding itself
+(e.g., across development).
 
@@
 
-\begin{CodeChunk}
-\begin{figure}[H]
+\begin{figure}
 
-{\centering \includegraphics{figs/illus-1}
+{\centering \includegraphics[width=300px]{figs/illustration}
 
@@
 
-\caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
+\caption{An illustration of the probabilistic/continuous account using simulated data.
 A word is represented with a distribution over the perceptual space (indicated in red or blue).
@@
 \end{figure}
-\end{CodeChunk}
 
@@
 
-\begin{SCfigure}
-\centering
-\includegraphics[width=1.5in]{figs/model.png}
-\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicate fixed model parameters.}
-\label{fig:model}
-\end{SCfigure}
+\begin{figure}
 
-A similar probabilistic structure was used by Lewis \& Frank (2013) to
-model concept learning, and by Hofer \& Levy (2017) to model spoken word
-learning. However, the first study assumed that the sounds are heard
-unambiguously, and the second assumed the concepts are observed
+{\centering \includegraphics[width=300px]{figs/model}
+
+}
+
+\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicate fixed model parameters.}\label{fig:model}
+\end{figure}
+
+A similar probabilistic structure was used by Lewis and Frank (2013) to
+model concept learning, and by Hofer and Levy (2017) to model spoken
+word learning. However, the first study assumed that the sounds are
+heard unambiguously, and the second assumed the concepts are observed
 unambiguously. In our model, we assume that both labels and concepts are
@@
 \[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
-\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] Finally, we assume
-there to be one-to-one mappings between concepts and labels and that
-observers have successfully learned these mappings during the exposure
-phase: \[
+
+\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \]
+
+Finally, we assume there to be one-to-one mappings between concepts and
+labels and that observers have successfully learned these mappings
+during the exposure phase: \[
 P(L_i|C_j) = 
@@
 \[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
+
 The joint probability \(P(o, C, L, s)\) is obtained by factoring the
 Bayesian network in Figure \ref{fig:model}:
-\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which can be transformed using
-Bayes rule into:
+\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
 
-\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
-concepts' prior probability is uniformly
+which can be transformed using Bayes rule into:
+
+\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \]
+
+Finally, assuming that the concepts' prior probability is uniformly
 distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.},
@@
 
-\begin{CodeChunk}
 \begin{figure}[t]
 
-{\centering \includegraphics{figs/task-1}
+{\centering \includegraphics[width=3.75in]{figs/task}
 
@@
 
-\caption{\label{fig:task}An overview of the task used in this study.}\label{fig:task}
+\caption{An overview of the task used in this study.}\label{fig:task}
 \end{figure}
-\end{CodeChunk}
 
 We use the model to predict performance in the word learning task
-introduced by Stager \& Werker (1997), with a two-alternative forced
+introduced by Stager and Werker (1997), with a two-alternative forced
 choice as in Yoshida et al. (2009). In this task, participants are first
 exposed to the association between pairs of nonsense words (e.g.,
-``lif''/``neem'') and pairs of objects. The word-object associations are
-introduced sequentially. After this exposure phase, participants perform
-a series of test trials. In each of these trials, one of the two sounds
-is uttered (e.g., ``lif'') and participants choose the corresponding
-object from the two alternatives. An overview of the task is shown in
-Figure \ref{fig:task}.
+\enquote{lif}/\enquote{neem}) and pairs of objects. The word-object
+associations are introduced sequentially. After this exposure phase,
+participants perform a series of test trials. In each of these trials,
+one of the two sounds is uttered (e.g., \enquote{lif}) and participants
+choose the corresponding object from the two alternatives. An overview
+of the task is shown in Figure \ref{fig:task}.
 
@@
 
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/simulation-1}
-
-}
-
-\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\Delta s$ and $\Delta o$ and representation precision $\sigma$ (For clarity, we assume here that $\sigma$=$\sigma_C$=$\sigma_L$).
-Dashed line represents chance.}\label{fig:simulation}
-\end{figure*}
-\end{CodeChunk}
+\begin{figure}[htbp]
+\centering
+\includegraphics{ms_files/figure-latex/simulation-1.pdf}
+\caption{\label{fig:simulation}The predicted probability of accurate
+responses in the testing phase as a function of stimuli distinctiveness
+\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
+(For clarity, we assume here that \(\sigma\)=\(\sigma_C\)=\(\sigma_L\)).
+Dashed line represents chance.}
+\end{figure}
 
@@
 Bing Nursery School on Stanford University's campus. Here we report data
-from n=47 children. An additional n=28 children participated but were
+from n=55 children. An additional n=35 children participated but were
 removed from analyses because they were not above chance on the catch
@@
 also planned to recruit a sample of N=60 adults on Amazon Mechanical
-Turk. Data from n=10 participants were excluded due to low scores on the
-catch trials (n=9 ) or because they were familiar with the non-English
-sound stimuli we used in the adult experiment (n=1), yielding a final
-sample of n=50.
+Turk. Data from n=26 participants were excluded due to low scores on the
+catch trials (n=26 ) or because they were familiar with the non-English
+sound stimuli we used in the adult experiment (n=0), yielding a final
+sample of n=74.
 
@@
 generated three kinds of nonsense word pairs which varied in their
-degree of similarity to English speakers: 1) ``different'':
-``lif''/``neem'' and ``zem''/``doof'', 2) ``intermediate'':
-``aka''/``ama'' and ``ada''/``aba'', and 3) ``similar'' non-English
-minimal pairs: ``ada''/``a\textipa{d\super h}a'' (in hindi) and
-``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).
+degree of similarity to English speakers: 1) \enquote{different}:
+\enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2)
+\enquote{intermediate}: \enquote{aka}/\enquote{ama} and
+\enquote{ada}/\enquote{aba}, and 3) \enquote{similar} non-English
+minimal pairs: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi)
+and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
 
@@
 library\footnote{https://github.com/erindb/stimuli} which allowed us to
-generate objects in four different categories: ``tree'', ``bird'',
-``bug'', and ``fish''. These categories are supposed to be naturally
-occurring kinds that might be seen on an alien planet. In each category,
-we generated ``different'', ``intermediate'' and ``similar'' pairs by
-manipulating a continuous property controlling features of the
-category's shape (e.g, body stretch or head fatness).
+generate objects in four different categories: \enquote{tree},
+\enquote{bird}, \enquote{bug}, and \enquote{fish}. These categories are
+supposed to be naturally occurring kinds that might be seen on an alien
+planet. In each category, we generated \enquote{different},
+\enquote{intermediate} and \enquote{similar} pairs by manipulating a
+continuous property controlling features of the category's shape (e.g,
+body stretch or head fatness).
 
@@
 
-\subsubsection{Design}\label{design}
+\includegraphics{ms_files/figure-latex/unnamed-chunk-6-1.pdf}
+\#\#\#Design
 
 Each age group saw only two of the three levels of similarity described
-in the previous sub-section: ``different'' vs. ``intermediate'' for
-preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
-this choice in light of pilot studies showing that adults were at
-ceiling with ``different'' sounds/objects, and children were at chance
-with the ``similar'' sounds/objects. That said, this difference in the
-level of similarity is accounted for in the model through using the
-appropriate perceptual distance used in each age group (Figure
-\ref{fig:stim}).
+in the previous sub-section: \enquote{different} vs.
+\enquote{intermediate} for preschoolers, and \enquote{intermediate} vs.
+\enquote{similar} for adults. We made this choice in light of pilot
+studies showing that adults were at ceiling with \enquote{different}
+sounds/objects, and children were at chance with the \enquote{similar}
+sounds/objects. That said, this difference in the level of similarity is
+accounted for in the model through using the appropriate perceptual
+distance used in each age group (Figure \ref{fig:stim}).
 
-\begin{CodeChunk}
 \begin{figure}[h]
 
-{\centering \includegraphics{figs/stim-1}
+{\centering \includegraphics{ms_files/figure-latex/stim-1}
 
@@
 
-\caption{\label{fig:stim}Distances for both sound and object pairs from an adult norming study.
+\caption{Distances for both sound and object pairs from an adult norming study.
 Data represent Likert values normalized to [0,1] interval.
@@
 
-\begin{CodeChunk}
-\begin{figure*}[h]
-
-{\centering \includegraphics{figs/all_data-1}
-
-}
-
-\caption{\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
-adults).
-We show both experimental results (solid lines) and model predictions (dashed lines).
-Error bars represent 95\% confidence intervals.}\label{fig:all_data}
-\end{figure*}
-\end{CodeChunk}
-
 In the exposure trials, participants saw two objects associated with
@@
 screen after 500ms. For both objects, visual stimuli were present for
-the duration of the sound clip (∼800ms). In the testing trials,
+the duration of the sound clip (about 800ms). In the testing trials,
 participants saw both objects simultaneously and heard only one sound.
@@
 
-Experimental results are shown in Figure 6 (solid lines). We first
-analyzed the results using a mixed-effects logistic regression with
-sound distance, object distance and age group as fixed effects, and with
-a maximal random effects structure (allowing us to take into account the
-full nested structure of our data) (Barr, Levy, Scheepers, \& Tily,
-2013). We found main effects for all the fixed effects in the
-regression. For the sound distance, we obtained \(\beta =\) 0.44 (\(p\)
-\textless{} 0.001), replicating previous findings. For object distance,
-we found \(\beta =\) 0.5 (\(p\) \textless{} 0.001), and this finding
-confirms the new prediction of our model. Finally, for the age group, we
-obtained \(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that
-performance improves with age. In addition, we found two-way
-interactions between sound distance and age (\(\beta =\) 0.17, \(p\)
-\textless{}0.05) and between object distance and age (\(\beta =\) 0.18,
-\(p\) \textless{}0.05).
+\begin{figure}[h]
+
+{\centering \includegraphics{ms_files/figure-latex/allData-1}
+
+}
+
+\caption{Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+adults).
+We show both experimental results (solid lines) and model predictions (dashed lines).
+Error bars represent 95\% confidence intervals.}\label{fig:allData}
+\end{figure}
+
+Experimental results are shown in Figure \ref{fig:allData} (solid
+lines). We first analyzed the results using a mixed-effects logistic
+regression with sound distance, object distance and age group as fixed
+effects, and with a maximal random effects structure (allowing us to
+take into account the full nested structure of our data) (Barr, Levy,
+Scheepers, \& Tily, 2013). We found main effects for all the fixed
+effects in the regression. For the sound distance, we obtained
+\(\beta =\) 0.52 (\(p\) \textless{} 0.001), replicating previous
+findings. For object distance, we found \(\beta =\) 0.83 (\(p\)
+\textless{} 0.001), and this finding confirms the new prediction of our
+model. Finally, for the age group, we obtained \(\beta =\) 0.76 (\(p\)
+\textless{} 0.001), showing that performance improves with age. In
+addition, we found two-way interactions between sound distance and age
+(\(\beta =\) 0.15, \(p\) = 0.17) and between object distance and age
+(\(\beta =\) 0.45, \(p\) \textless{} 0.001).
 
@@
 Thus, the model has two degrees of freedom for each group, i.e.,
-\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (dashed lines)
+\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:allData} (dashed lines)
 shows the predictions. The model captures the qualitative patterns in
@@
 The values of the parameters were as follows. Children had a
-label-specific uncertainty of \(\sigma_S =\) 0.9 {[}0.68,
-1.11{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
-and a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1,
-0.49{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.14
-{[}-0.02, 0.3{]}, and a concept-specific uncertainty of \(\sigma_C =\)
-0.19 {[}0.04, 0.34{]}. As predicted, the uncertainty parameters were
+label-specific uncertainty of \(\sigma_S =\) 0.83 {[}0.64,
+1.02{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
+and a concept-specific uncertainty of \(\sigma_C =\) 0.31 {[}0.11,
+0.51{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.12
+{[}0.12, 0.13{]}, and a concept-specific uncertainty of \(\sigma_C =\)
+0.17 {[}0.16, 0.18{]}. As predicted, the uncertainty parameters were
 larger for children than they were for adults, showing that the
@@
 The models explained the majority of the variance in the participants'
-mean responses (\(R^2=\) 0.86, for the combined adult and children's
-data). To investigate whether the model's predictive power was due to
+mean responses (\(R^2=\) 1, for the combined adult and children's data).
+To investigate whether the model's predictive power was due to
 overfitting, we fit a simplified version with only one degree of freedom
@@
 single-variance model explained as much variance in the mean responses
-(\(R^2=\) 0.87). It also captured the main qualitative patterns (graph
+(\(R^2=\) 0.95). It also captured the main qualitative patterns (graph
 not shown), suggesting that the explanatory power of the model is
@@
 cognitive development can be characterized in a continuous fashion. We
-used as a case study the seminal work of Stager \& Werker (1997) showing
-a discrepancy between children's speech perception abilities and their
-word learning skills. While much of the previous investigation of this
-finding has been interested in the source of this discrepancy, here we
-have explored how it could arise from continuous developmental change in
-perceptual uncertainty.
+used as a case study the seminal work of Stager and Werker (1997)
+showing a discrepancy between children's speech perception abilities and
+their word learning skills. While much of the previous investigation of
+this finding has been interested in the source of this discrepancy, here
+we have explored how it could arise from continuous developmental change
+in perceptual uncertainty.
 
@@
 
-\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}}
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
 \vspace{1em}
+
+\section{Acknowledgements}\label{acknowledgements}
+
+This work was supported by a post-doctoral grant from the Fyssen
+Foundation, NSF \#1528526, and NSF \#1659585.
+
+\section{Disclosure statement}\label{disclosure-statement}
+
+None of the authors have any financial interest or a conflict of
+interest regarding this work and this submission.
 
@@
 
-\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
+\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
 

### 2019-07-22 journal/ms.Rmd
journal v1

@@
 We collected data from preschool children and adults, and we showed that the model can explain various patterns of learning both within the same age and across development.
-The findings suggest that major aspects of cognitive development that are typically thought of as discontinuities, may emerge from simpler, continuous mechanisms."
+The findings suggest that major aspects of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms."
 
@@
 library(lme4)
+library(kableExtra)
 ```
@@
 @stager1997 first showed that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
-Indeed, though infants around 14-month old can distinguish similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects.
+The authors measured word learning using an audio-visual habituation Switch task.
+First, infants are familiarized with two word-object pairings (e.g., Word A with Object A and Word B with Object B).
+Second, they are tested using two types of trials.
+The control 'same' trial consists of a correct pairing  (e.g., Word A with Object A) and the 'switch' trial consists of a wrong pairing (e.g., Word A with Object B).
+If babies have correctly learned the association during the familiarization, they are supposed to be surprised by the 'switch' trial and not by the 'same' trial.
+The former should thus result in a greater looking time compared to the latter [@werker1998].
 
-<!--Follow-up studies has focused on proposing possible explanations for this observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017; @rost2009]. -->
+Though infants around 14-month old can distinguish perceptually similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects in the switch task.
+This failure has initially been taken as evidence that 14-month olds do not encode subtle sounds during meaning learning [@stager1997; @pater2004].
+This interpretation suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children, around 17 months [@werker2002], typically do.
 
-By around 17 m.o, children succeed in the same task [@werker2002].
-How does development proceed?
-The answer to this question depends on the nature of the chidlren's word encoding in the task.
-Early accounts assumed that children encode words in a rather binary way: they either fail or succeed in attending to the relevant phonetic details (simultaneously with the meanings).
-In the orginal paper, @stager1997 noted that "Infants of 14 months fail to detect the same phonetic detail that they can easily detect in a simple syllable discrimination task".
+<!-- In fact, @stager1997 noted that "Infants of 14 months fail to detect the same phonetic detail that they can easily detect in a simple syllable discrimination task".
 They argued that the high cogntive demands of the task make children experience a limitation in the amount of phonetic details they can access.
 In a similar vein, Pater et al.
-(2004) argued that "when a contrast is first acquired, it is not stable and can be lost under processing demands".
-This binary account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.
+(2004) argued that "when a contrast is first acquired, it is not stable and can be lost under processing demands"-->
 
-Subsequent findings have investigated the implications of this hypothesis in both infants and adults.
-First, if the demands of the task totally empede the encoding of subtle phonetic contrasts, then infants should fail in learning the mappings between the sounds and the objects, regardless of how this learning is probed.
-However, 14-month-olds succeed in this task under the same *learning* conditions as in @stager1997, but when an easier *testing* method is used [@yoshida2009].
-Second, if the minsmatch between sound distrimination and word learning is only related to limited cognitive resources in infancy, then adults --- who have greater attentianal and working memory capacity --- should always succeed in mapping pairs of sounds they can discriminate to different objects.
-Nonetheless, even adults show patterns learning that mirror those shown by 14-month-olds [@white2013; @pajak2016].
+<!--Follow-up studies has focused mainly on proposing possible explanations for the observed gap between speech perception and word learning [e.g., @fennell2010; @stager1997; @hofer2017; @rost2009].
+-->
 
-This new set of evidence points towards another scenario, where the representations are encoded in a probabilistic (rather than binary) way, and where development is continuous, rather than stage-like [see also @swingley2007].
-On this account, correct representations are learned early in development, but these representations are encoded with higher uncertainty in younger children, leading to *apparent* failure in relatively demanding tasks.
-Development is a continuous process whereby the initial noisy representations become more precise.
-Crucially, in a probabilsitic account, more precise representation do not mean they perfect, thus accounting for the fact that even adults show low accuracy learning when the sounds are subtle, e.g., non-native [@pajak2016].
+The initial discontinuous interpretation has been challenged by subsequent work.
+For instance, @yoshida2009 investigated whether failure in the switch task reflects a lack of sound encoding during *familiarization*, or whether it is only due to the demands of the *testing* method which does not allow learning below a certain threshold to be detected.
+They used the same familiarization procedure as @stager1997, but instead of comparing the looking times in 'same' and 'switch' trials, they tested infants using a two-alternative choice task comparing fixations to target and distractor objects [@golinkoff1987; @fernald2006].
+Using this simpler and finer-grained task, the researcher found evidence for learning even in 14-month olds.
 
-We provide an intuitive illustration of how such an account explains patterns of learning and development in Figure \@ref(fig:illus).
-We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty with which these labels are encoded.
-For example, in Stager and Werker's original experiment, children are supposed to associate label 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.
-Though infants could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large uncertainty of the encoding, and this confusion leads to "failure" in the recognition task.
-According to this account, accuracy in word learning improves if we increase either the perceptual distinctiveness of the stimuli (e.g., through using different-sounding labels), or the precision of the encoding itself (e.g., across development).
+Another challenge to the discontinuous account of development came from adult studies.
+If the mismatch between sound discrimination and word learning is only a stage in early infancy, then this mismatch should disappear by adulthood.
+Nonetheless, even adults show patterns of learning that mirror those shown by 14-month-olds when the sound contrasts more challenging [@white2013; @pajak2016].
 
-Building on this intuition, the current work proposes a probabilistic model, which we use to both account for previous experimental findings, and to make new predictions that have not been tested before.
-Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.
+Some researchers [e.g., @swingley2007; @yoshida2009; @pajak2016] proposed that the phonological form may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
+Rather, they may be encoding the phonological form of words in a probabilistic fashion.
+According to this view, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy representations.
+
+In a probabilistic account, a word can be represented as a probability distribution over sound instances organized in a similarity space.
+The probability is highest at the most typical sound instance.
+It decreases as the instance becomes less typical.
+The precision of the representation can be characterized by how much it tolerates slightly atypical pronunciations.
+This tolerance is captured formally by the variance of the probability distribution: larger variance indicates higher tolerance and lower precision, whereas smaller variance indicates lower tolerance and higher precision.
+
+This framework can explain several findings.
+In Stager and Werker's original experiment, children are supposed to associate one label "bih" with object 1 and a second label "dih" with object 2.
+Though infants could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large variance of the early encoding, and this confusion leads to "failure" in the recognition task (Figure \@ref(fig:illus), top).
+Though learning is small and is easily disrupted by the Switch task, it can still be detected when less demanding methods are used [@yoshida2009].
+
+The learning accuracy increases (and is detected even by demanding tests such as the Switch) for more distinct word-forms (e.g., "lif" vs.
+"neem") where the perceptual distance is large relative to the variance (Figure \@ref(fig:illus), left).
+Distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference [@rost2009; @rost2010; @thiessen2007; @yeung09; @dautriche2015].
+
+Finally, development can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic representations (Figure \@ref(fig:illus), right).
+Such an increase in precision renders minimally different sounds less confusing.
+Importantly, a more precise representation still has a non-zero variance --- Learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrate in adults studies [@white2013; @pajak2016].
+
+## This study
+
+The probabilistic account has been put forward to explain patterns of learning and development at the qualitative level.
+However, it is crucial to have a precise computational instantiation of this account which would allow us to *quantify* its explanatory power.
+We could find one previous work that attempted to provide such a computational instantiation  (Hofer and Levy, 2017).
+However, this previous work was designed with the goal of reproducing the results of a specific study [@pajak2016] which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
+
+The present work proposes a model of word-pair learning based on the probabilistic account.
+We tested the ability of this model to both *explain* various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to *predict* new learning patterns that have not been tested before (i.e., the effect of the referents' similarity on word learning).
+Crucially, we explored the extent to which development can be understood as a continuous refinement in similar representations across the lifespan.
+
+The paper is organized as follows.
+First, we introduce the model and we explain how it allows us to characterize behavior in a word learning task which resembles the one used in @stager1997 and @yoshida2009.
+Then we explore the predictions of the model through simulating its behavior across different parameter settings.
+Next we quantify the extent to which the model's predictions account for human data we collected from both preschool children and adults.
+Finally, we discuss the results in the lights of existing accounts of word development.
 
@@
 
-The learner hears a sound $s$ and has to decide which object $o$ provides an optimal match to this sound.
+The learner hears a sound $s$ and has to decide which object $o$ provides an optimal match to this sound (see Figure \@ref(fig:task)).
 To this end, they must compute the probability $P(o|s)$ for all possible objects.
@@
 
-\begin{equation}
+$$
 P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-\end{equation}
+$$
 
@@
 
-We use the model to predict performance in the word learning task introduced by @stager1997, with a two-alternative forced choice as in @yoshida2009.
+We use the model to predict word learning in a task similar to the one introduced by @stager1997.
+We used a modified version of the task where the testing method consists in a two-alternative forced choice [@yoshida2009].
 In this task, participants are first exposed to the association between pairs of nonsense words (e.g., "lif"/"neem") and pairs of objects.
@@
 
-We used Equation 1 and the probability distributions defined above to obtain the exact analytical expression for the probability of accurate responses $p(o_T | s)$ (target object $o_T$ given a sound $s$) in the simple case of two-alternative forced choice in the testing phase of our experimental task:
+From the general expression (1), we derive three exact analytical solutions instantiating different learning assumptions.
+The first solution is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty $\sigma_L$, but that concepts are unambiguously recovered from the observed objects, i.e., $\sigma_C \rightarrow 0$.
+This assumption has been made --- whether implicitly or explicitly --- by most previous work in this line of research.
+One important implication of this assumption is that only the similarity of word sounds modulates success in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually).
+This assumption yields the following probability function:
 
 \begin{equation}
-P(o_T|s)= \frac{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}}{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}+ e^{-\Delta s^2 /2\sigma_L^2} + e^{-\Delta o^2 /2\sigma_C^2 }}
+P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
 \end{equation}
 
-Figure \ref{fig:simulation} show simulations of the predicted accuracy (Expression 2) as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the precision parameters, i.e., the variances of the distributions $p(s| L)$ and $p(o | C)$.
-To understand the qualitative behavior of the model, we assumed for simplicity that the precision parameter has similar values in both distributions, i.e., $\sigma =\sigma_C \approx \sigma_L$ (but we will allow those parameters to vary independently in the rest of the paper).
+The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with ambiguity from the sounds and objects.
+We first introduce the simplifying assumption that the label-related uncertainty $\sigma_L$ and the concept-related uncertainty $\sigma_C$ are of a similar magnitude, i.e., $\sigma_C \approx \sigma_L = \sigma$.
+This assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way.
+Furthermore, it allows us to study the behavior of the model with minimal free parameters.
+
+\begin{equation}
+P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
+\end{equation}
+
+We finally derive the third (and most general) solution which allows label- and concept-related uncertainties to vary independently.
+
+\begin{equation}
+P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
+\end{equation}
+
+In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show some simulations of the accuracy $P(o_T|s)$ as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the uncertainty parameters $\sigma_L$ and $\sigma_C$.
 
@@
 
-The simulations explain some previously documented facts, and make new predictions:
+The simulations explain two experimental results from previous studies and make one new prediction:
 
@@
 
-2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational uncertainty (characterized with $\sigma$) decreases.
+2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational uncertainty $\sigma$ decreases.
 This fact may explain development, i.e., younger children have noisier representations [see @swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar-sounding words.
@@
 Two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
-The experiment, sample size, exclusion criteria and the model's main predictions were pre-registered.
+The experiment, sample size, exclusion criteria and the model's main predictions were pre-registered.\footnote{https://osf.io/942gv/}
 
@@
 
-d_child <- read_delim("../Analysis/kids_all.txt", delim = " ") %>%
+d_child <- read_delim("../Analysis/kids_all_final.txt", delim = " ") %>%
   filter(type == "Test") %>%
@@
 ### Participants
-We planned to recruit a sample of N=60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
-Here we report data from n=`r N_good_ch` children.
-An additional n=`r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
-We also planned to recruit a sample of N=60 adults on Amazon Mechanical Turk.
-Data from n=`r N_all_ad-N_good_ad` participants were excluded due to low scores on the catch trials (n=`r N_all_ad-N_good_ad-d_adult_lang` ) or because they were familiar with the non-English sound stimuli we used in the adult experiment (n=`r d_adult_lang`), yielding a final sample of n=`r N_good_ad`.
+We report data from $N=$ `r N_good_ch` children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
+An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
+We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk.
+An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.
 
@@
 The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996].
-We generated three kinds of nonsense word pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
+We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) *different* pairs: "lif"/"neem" and "zem"/"doof", 2) *intermediate* pairs: "aka"/"ama" and "ada"/"aba", and 3) *similar* non-English pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
 
-As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish".
-These categories are supposed to be naturally occurring kinds that might be seen on an alien planet.
-In each category, we generated "different", "intermediate" and "similar" pairs by manipulating a continuous property controlling features of the category's shape (e.g, body stretch or head fatness).
+As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree," "bird," "bug," and "fish." These categories are supposed to be naturally occurring kinds that might be seen on an alien planet.
+In each category, we generated *different*, *intermediate* and *similar* pairs by manipulating a continuous property controlling features of the category's shape (e.g, body stretch or head fatness).
 
-In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and object pair on a 7-point scale.
-We scaled responses within the range [0,1].
-Data are shown in Figure \@ref(fig:stim), for each stimulus group.
-These data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).
+In order to validate and quantify our similarity scales, we ran a separate survey on Amazon Mechanical Turk where we asked $N=20$ adults participants to evaluate the similarity of each sound and object pair on a 7-point scale.
+Data are shown in Figure \@ref(fig:stim) where we scaled responses within the range [0,1] for each stimulus group.
+These data will be used in all models as a proxy for the perceptual distance between the sound pairs ($\Delta s$) and the object pairs ($\Delta o$).
+
+<!--Though these distances were collected from adults particiapants only, we make the assumption that they measure an perecptual distances represent the "objective" for both adults and children and that only the way these sounds are paired to object vary across age groups.-->
 
@@
 #Import data from saved
-data_human_model <- feather::read_feather("../saved_data/data_human_model.feather") #%>%
-  #mutate(Model = ifelse(key == "prediction", "Single Variance", "Double Variance"))
+data_human_model <- feather::read_feather("../saved_data/data_human_model.feather") %>%
+  mutate(key = ifelse(key == "prediction_no", "Model 1",
+                      ifelse(key == "prediction", "Model 2", "Model 3")))
 
@@
 
-plot_data
 ```
+
 ###Design
 
-Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs.
-"intermediate" for preschoolers, and "intermediate" vs.
-"similar" for adults.
-We made this choice in light of pilot studies showing that adults were at ceiling with "different" sounds/objects, and children were at chance with the "similar" sounds/objects.
-That said, this difference in the level of similarity is accounted for in the model through using the appropriate perceptual distance used in each age group (Figure \@ref(fig:stim)).
+Each age group saw only two of the three levels of similarity described in the previous sub-section: *different* vs.
+*intermediate* for the preschoolers, and *intermediate* vs.
+*similar* for adults.
+We made this choice in light of pilot studies showing that adults were at ceiling with *different* sounds/objects, and children were at chance with the *similar* sounds/objects.
+That said, this difference in the level of similarity is accounted for in the model through using the appropriate distance (Figure \@ref(fig:stim)).
 
@@
 To maximize our ability to measure subtle stimulus effects, the experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
-Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.
+Besides the four conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones but was used only to select participants who were able to follow the instructions and show minimal learning.
 
@@
 
-```{r allData, fig.env = "figure", fig.pos = "h", fig.align='center', fig.cap = "Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+```{r allData, fig.env = "figure", fig.pos = "h", fig.align='center', fig.cap = "Accuracy of word recognition as a function of the sound distance, the object distance, and the age group (preschool children vs.
 adults).
-We show both experimental results (solid lines) and model predictions (dashed lines).
+We show both the models' predictions (dashed lines) and the experimental results (solid lines).
+The single-variance model uses one joint fitting parameter for both sound and meaning variances.
+The double-variance model uses two separate fittings parameters for the sound and the meaning variances.
 Error bars represent 95\\% confidence intervals."}
@@
 We found main effects for all the fixed effects in the regression.
-For the sound distance, we obtained $\beta =$ `r s_coef` ($p$ `r p_val(s_p)`), replicating previous findings.
-For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model.
-Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that performance improves with age.
-In addition, we found two-way interactions between sound distance and age ($\beta =$ `r s_age_coef`, $p$ `r p_val(s_age_p)`) and between object distance and age ($\beta =$ `r c_age_coef`, $p$ `r p_val(c_age_p)`).
+For the sound distance, we obtained $\beta =$ `r s_coef` ($p$ `r p_val(s_p)`), replicating previous findings that sound distance modulates success in word learning [e.g., @stager1997].
+For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model according to which object distance also modulates success in word learning.
+Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that overall performance improves with age.
 
@@
 
-R2_model1 <-  round(cor(data_correlations$human, data_correlations$prediction)^2, 2)
-R2_model2 <-  round(cor(data_correlations$human, data_correlations$prediction_2)^2, 2)
+R2_model1 <-  round(cor(data_correlations$human, data_correlations$prediction_no)^2, 2)
+R2_model2 <-  round(cor(data_correlations$human, data_correlations$prediction)^2, 2)
+R2_model3 <-  round(cor(data_correlations$human, data_correlations$prediction_2)^2, 2)
+
+mod0_val <- feather::read_feather("../saved_data/values_mod_no.feather") %>%
+  rename(lower =`2.5 %`,
+         upper = `97.5 %`)
 
@@
 
-We next fit our model (using Equation 2) to the participants' responses in each age group.
-The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (Figure \@ref(fig:stim)).
-Thus, the model has two degrees of freedom for each group, i.e., $\sigma_C$ and $\sigma_L$.
-Figure \@ref(fig:allData) (dashed lines) shows the predictions.
-The model captures the qualitative patterns in both age groups: starting from a low accuracy recognition when both the sound and object distances are small, the model correctly predicts an increase in accuracy when either the sound distance or the object distance increases.
-Further, accuracy is correctly predicted to be maximal when both the sound and object distances are high.
+```{r models, results="asis", echo=FALSE}
 
-The values of the parameters were as follows.
+mods <- data.frame(models = c('model 1', 'model 2', 'model 3'),
+                   struc = c("Sig\\textsubscript{L} only",
+                             "Sig\\textsubscript{L} = Sig\\textsubscript{C}",
+                             "Sig\\textsubscript{L} != Sig\\textsubscript{C}"),
+                   param = c(1,1,2),
+                   R = c(R2_model1, R2_model2, R2_model3),
+                   sigS_C = c(round(mod0_val$val[which(mod0_val$group=="children")],2),
+                              round(mod1_val$val[which(mod1_val$group=="children")],2),
+                              round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)
+                              ),
+                   sigO_C = c('--',
+                              round(mod1_val$val[which(mod1_val$group=="children")],2),
+                              round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)
+                              ),
+                   sigS_A = c(round(mod0_val$val[which(mod0_val$group=="adults")],2),
+                              round(mod1_val$val[which(mod1_val$group=="adults")],2),
+                              round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)
+                              ),
+                   sigO_A = c('--',
+                              round(mod1_val$val[which(mod1_val$group=="adults")],2),
+                              round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)
+                   ))
+
+kable(mods, format = "latex", escape = FALSE, booktabs = TRUE,
+      linesep = "", format.args = list(big.mark = ","),
+      caption = "Characteristics and performance of the models used in this study.",
+      col.names = c("Model",  "Structure", "Param.", "R\\textsuperscript{2}", "Sig\\textsubscript{L}", "Sig\\textsubscript{C}", "Sig\\textsubscript{L}", "Sig\\textsubscript{C}")) %>%
+  add_header_above(c("", "","","","Children" = 2, "Adults" = 2)) %>%
+  column_spec(1, bold = TRUE) %>%
+  kable_styling(position = "center")
+
+```
+
+We next fit the three models obtained through expressions (1), (2), and (3) to the participants' responses in each age group.
+The predictions of the models are shown \@ref(fig:allData) (dashed lines) and the parameter estimates (for $\sigma_L$ and $\sigma_C$) as well as models' goodness to fit (i.e., measured through $R^2$) are presented in Table \@ref(tab:models).
+
+Model 1, which does not take into account ambiguity in recovering concepts from observed objects, explains only a small part of the variance.
+In contrast, Model 3, which does take into account this ambiguity, accounts for all the variance.
+Interestingly, Model 2 which has a single, shared uncertainty parameter for both auditory and visual modalities still explains almost all the variance in human data, suggesting that the explanatory power of the general Model 3 is largely due to its structure, rather than its degrees of freedom.
+
+As predicted, the uncertainty parameters were larger for children than they were for adults (Table \@ref(tab:models)), showing that the probabilistic representations become more refined (that is, $\sigma$ becomes smaller) across development.
+Further, the parameter estimates of Model 3 show that this developmental effect is more important for the label-specific uncertainty that it is for the concept-specific uncertainty.
+
+<!-- The values of the parameters were as follows.
 Children had a label-specific uncertainty of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`]\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.}, and a concept-specific uncertainty of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`].
@@
 The developmental effect was more important for the label-specific uncertainty.
-
-The models explained the majority of the variance in the participants' mean responses ($R^2=$ `r R2_model2`, for the combined adult and children's data).
-To investigate whether the model's predictive power was due to overfitting, we fit a simplified version with only one degree of freedom (i.e., a single variance common to both sounds and objects).
-This single-variance model explained as much variance in the mean responses ($R^2=$ `r R2_model1`).
-It also captured the main qualitative patterns (graph not shown), suggesting that the explanatory power of the model is largely due to its structure, rather than its degrees of freedom.
-
-An unexpected outcome was that adult participants deviated slightly from the model's numbers: While the model predicted  accuracy to be more sensitive to object distance when sound distance is higher (and vice-versa), adult participants showed the opposite pattern.
-This deviation is an interesting starting point for future work as it may suggest that participants are more likely to pay attention to and integrate additional sources of information when ambiguity is higher.
+-->
 
@@
 We used as a case study the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills.
-While much of the previous investigation of this finding has been interested in the source of this discrepancy, here we have explored how it could arise from continuous developmental change in perceptual uncertainty.
+While this fact might seem like a specific stage in early development, our model demonstrated, instead, that it can be more simply understood in terms of continuous developmental change.
 
-Building on some previous discussions [e.g., @swingley2007; @yoshida2009], we proposed a model where perceptual stimuli are encoded probabilistically.
-We tested the model's predictions against data collected from preschool children and adults and we showed that developmental changes in word-object mappings can indeed be characterized as a continuous refinement (i.e., uncertainty reduction) in qualitatively similar representations across the life span.
+The main assumption of the model was that both word form and referent are encoded in a probabilistic fashion.
+The model provided a quantitative instantiation of the continuous development hypothesis [e.g., @swingley2007; @yoshida2009; @pajak2016]).
+More precisely, we showed that developmental changes in word-object mappings can be characterized as a continuous refinement in the precision of the probabilistic representations.
 
-The model made a new prediction to which we tested experimentally: Learning similar words is not only modulated by the similarity of their phonological forms, but also by the visual similarity of their semantic referents.
-More generally, since visual similarity is an early organizing feature in the semantic domain [e.g.,@wojcik2013], our finding suggests that children may prioritize the acquisition of words that are quite distant in the semantic space.
-This suggestion is supported by recent findings based on the investigation of early vocabulary growth [@engelthaler2017; @sizemore2018].
+We find in the literature two broad accounts of development in the Switch task: One that suggests *direct* development of the sound representation and one that hypothesizes *indirect* development of this representation through improvement in general cognitive resources.
+On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories, i.e., contrasting word meaning [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011].
+On the second account, the precision of sound encoding in the switch task improves as a result of the maturation of more general resources like the attentional and working memory capacity [@stager1997; @werker2004; @hofer2017].
+Such improvement allows older children and adults to better encode the sound details while simultaneously matching these sounds to visual objects.
+These two accounts are complementary and both seem to play a role [see @tsui2019 for a review].
 
-One limitation of this work is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-18 month-old).
+ <!---In addition, both accounts are compatible with the continuous development hypothesis: In the first account, refining the phonetic/phonological categories can proceed gradually over probabilstic representations that encode degrees of beleif (Swingley, 2007; feldman et al.).
+In the second account, general cognitive capacity is likely to develop in a continuous fashion --- rather than in stages (cite XX).
+The continuous nature of both kinds of development is supported by the fact that even adults --- who have both more refined phonetic categories and larger cognitive capacity --- show learing patterns remiscient of the early discrepancy between sound perception and meaning learning (Pajak et al.
+2016).
+--->
+
+Our model is compatible with both of these accounts.
+In our work, the probability distributions do not distinguish between the direct and indirect sources of uncertainty --- both are included.
+Indeed, part of the measured uncertainty reflects the learner's degrees of confidence in the phonetic/phonological boundaries (i.e., the direct account) and another part reflects a possible drop in perceptual acuity due to high cognitive load (i.e., the indirect account).
+Note, however, that the model (at least in its current format) is incapable of answering questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.
+
+@werker2005 proposed to explain development in the Switch task using their theory called Processing Rich Information from Multidimensional Interactive Representations (or PRIMIR) which purports to explain various phenomena in early speech perception and word learning within a unified framework.
+PRIMIR posits that children initially try to attend to various features of the speech signal, regardless of whether or not these features are relevant to the task at hand.
+For example, when learning the meaning of similar sounds, infants are unsure what detail is most important to identify words (i.e., the phonemes), and will instead activate several aspects of the information simultaneously (including, for example, the gender of the speaker).
+The lack of attentional selection leads to confusion and then to failure in the task.
+
+According to PRIMIR, learning similar-sounding words becomes more robust over time as children develop abstract phonemic categories.
+The latter act as filters, allowing children to attend selectively to the important information.
+This account is also compatible with our model (as it resembles the direct account we discussed above).
+Developing a better attentional strategy (thanks to phoneme) can translate into a reduction in the uncertainty about whether a sound contrast signals a change in meaning.
+
+<!--The initial lack of a robust phonemic representation cause younger children to confuse neighboring phoneme.
+This effect is formally described in terms of a large overalp between the probabilsitic representations (Figure 1).
+Thus, development can be understood as uncertainty reduction in these representations.
+As we mentioned above, this source od uncertainty is part of the effective, global uncertainty that we estimate in the model.
+-->
+
+While most research focused on the sound representation in analyzing the Switch task, this work showed that the visual representation of the referent is equally important.
+Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded.
+As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents.
+
+Model 2, which predicts that sound similarity and visual similarity influence word learning accuracy in the same way, explained slightly less variance than Model 3 which predicts that these modalities influence word learning differently.
+More precisely, a comparison of the variance estimates across age groups shows that uncertainty reduction in the visual modality was lower compared to that of the auditory modality (Table 1).
+Perhaps this difference is due to the fact that, in our task, the auditory speech had more sources of noise --- that children have to deal with --- than the visual input does.
+The processing of speech involved dealing with both perceptual noise and categorical ambiguity (due to the fact that the phonemic boundaries are still developing).
+In contrast, the processing of the visual input in our task involved only perceptual noise and no category-related uncertainty.
+<!--In real life, however, many semantic referents are conceptual categories and not just individual objects.
+In that case, the asymmetry between the auditory and visual modalities may disappear.
+-->
+
+Our finding that word learning is mediated by the visual similaérity of the semantic objects has implications for theories of lexical development.
+It suggests that, all things being equal, children may prioritize the acquisition of words whose semantic referents are visually different, as this allows them to minimize semantic ambiguity.
+It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space.
+This suggestion is, indeed, supported by recent work investigating vocabulary development [@engelthaler2017; @sizemore2018; @fourtassi2018]
+
+There are a few limitations to this work.
+One is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-17 month-old).
 We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting).
@@
 It would have been challenging to obtain such measures with infants.
+That said, though we used data from older children, we still found clear differences compared to adults, suggesting that development does not stop at 17 months, but continues throughout childhood.
 
-In sum, this paper proposes a model that accounts for the development of an important aspect of word learning.
-Our account suggests that the developmental data can be explained based on a continuous process operating over similar representations across development, suggesting developmental continuity.
+One limitation of the model is that it only accounts for bottom-up, similarity-based effects.
+It does not account for how high-level factors such as social and communicative cues can influence learning.
+For example, @fennell2010 highlighted the fact that the Switch task introduces novel words in isolation (e.g., "neem!") rather than within a naming phrase (e.g., "look at the neem!").
+This fact may prompt children to interpret these novel words in a non-referential way (e.g., an exclamation such as "Wow!").
+
+<!--Our work contibutes to our undestanding of this mechanism by emphasing its continuous nature. -->
+
+To conclude, this paper proposes a model that accounts for the development of an important aspect of word learning.
+Our account suggests that the developmental data can be explained based on a continuous process operating over similar representations across the lifespan, suggesting developmental continuity.
 We used a case from word learning as an example, but the same idea might apply to other aspects of cognitive development that are typically thought of as stage-like (e.g., acquisition of a theory of mind).

### 2019-07-22 journal/ms.tex
journal v1

@@
 major aspects of cognitive development that are typically thought of as
-discontinuities, may emerge from simpler, continuous mechanisms.''
+discontinuities may emerge from simpler, continuous mechanisms.''
 
@@
 (1997) first showed that children's early ability to distinguish similar
-sounds does not automatically translate into word learning skills.
-Indeed, though infants around 14-month old can distinguish similar sound
-pairs such as \enquote{dih} and \enquote{bih}, they appear to fail in
-mapping this pair to two different objects.
+sounds does not automatically translate into word learning skills. The
+authors measured word learning using an audio-visual habituation Switch
+task. First, infants are familiarized with two word-object pairings
+(e.g., Word A with Object A and Word B with Object B). Second, they are
+tested using two types of trials. The control \enquote{same} trial
+consists of a correct pairing (e.g., Word A with Object A) and the
+\enquote{switch} trial consists of a wrong pairing (e.g., Word A with
+Object B). If babies have correctly learned the association during the
+familiarization, they are supposed to be surprised by the
+\enquote{switch} trial and not by the \enquote{same} trial. The former
+should thus result in a greater looking time compared to the latter
+(Werker, Cohen, Lloyd, Casasola, \& Stager, 1998).
 
-By around 17 m.o, children succeed in the same task (Werker, Fennell,
-Corcoran, \& Stager, 2002). How does development proceed? The answer to
-this question depends on the nature of the chidlren's word encoding in
-the task. Early accounts assumed that children encode words in a rather
-binary way: they either fail or succeed in attending to the relevant
-phonetic details (simultaneously with the meanings). In the orginal
-paper, Stager and Werker (1997) noted that \enquote{Infants of 14 months
-fail to detect the same phonetic detail that they can easily detect in a
-simple syllable discrimination task}. They argued that the high cogntive
-demands of the task make children experience a limitation in the amount
-of phonetic details they can access. In a similar vein, Pater et al.
-(2004) argued that \enquote{when a contrast is first acquired, it is not
-stable and can be lost under processing demands}. This binary account
-suggested a discontinuous/stage-like pattern of development whereby
-younger children fail to encode the contrastive phonetic detail, whereas
-older children succeed.
+Though infants around 14-month old can distinguish perceptually similar
+sound pairs such as \enquote{dih} and \enquote{bih}, they appear to fail
+in mapping this pair to two different objects in the switch task. This
+failure has initially been taken as evidence that 14-month olds do not
+encode subtle sounds during meaning learning (Pater, Stager, \& Werker,
+2004; Stager \& Werker, 1997). This interpretation suggested a
+discontinuous/stage-like pattern of development whereby younger children
+fail to encode the contrastive phonetic detail, whereas older children,
+around 17 months (Werker, Fennell, Corcoran, \& Stager, 2002), typically
+do.
 
-Subsequent findings have investigated the implications of this
-hypothesis in both infants and adults. First, if the demands of the task
-totally empede the encoding of subtle phonetic contrasts, then infants
-should fail in learning the mappings between the sounds and the objects,
-regardless of how this learning is probed. However, 14-month-olds
-succeed in this task under the same \emph{learning} conditions as in
-Stager and Werker (1997), but when an easier \emph{testing} method is
-used (Yoshida, Fennell, Swingley, \& Werker, 2009). Second, if the
-minsmatch between sound distrimination and word learning is only related
-to limited cognitive resources in infancy, then adults --- who have
-greater attentianal and working memory capacity --- should always
-succeed in mapping pairs of sounds they can discriminate to different
-objects. Nonetheless, even adults show patterns learning that mirror
-those shown by 14-month-olds (Pajak, Creel, \& Levy, 2016; White, Yee,
+The initial discontinuous interpretation has been challenged by
+subsequent work. For instance, Yoshida, Fennell, Swingley, and Werker
+(2009) investigated whether failure in the switch task reflects a lack
+of sound encoding during \emph{familiarization}, or whether it is only
+due to the demands of the \emph{testing} method which does not allow
+learning below a certain threshold to be detected. They used the same
+familiarization procedure as Stager and Werker (1997), but instead of
+comparing the looking times in \enquote{same} and \enquote{switch}
+trials, they tested infants using a two-alternative choice task
+comparing fixations to target and distractor objects (Fernald, Perfors,
+\& Marchman, 2006; Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987).
+Using this simpler and finer-grained task, the researcher found evidence
+for learning even in 14-month olds.
+
+Another challenge to the discontinuous account of development came from
+adult studies. If the mismatch between sound discrimination and word
+learning is only a stage in early infancy, then this mismatch should
+disappear by adulthood. Nonetheless, even adults show patterns of
+learning that mirror those shown by 14-month-olds when the sound
+contrasts more challenging (Pajak, Creel, \& Levy, 2016; White, Yee,
 Blumstein, \& Morgan, 2013).
 
-This new set of evidence points towards another scenario, where the
-representations are encoded in a probabilistic (rather than binary) way,
-and where development is continuous, rather than stage-like (see also
-Swingley, 2007). On this account, correct representations are learned
-early in development, but these representations are encoded with higher
-uncertainty in younger children, leading to \emph{apparent} failure in
-relatively demanding tasks. Development is a continuous process whereby
-the initial noisy representations become more precise. Crucially, in a
-probabilsitic account, more precise representation do not mean they
-perfect, thus accounting for the fact that even adults show low accuracy
-learning when the sounds are subtle, e.g., non-native (Pajak et al.,
-2016).
+Some researchers (Pajak et al., 2016; e.g., Swingley, 2007; Yoshida et
+al., 2009) proposed that the phonological form may not be encoded in a
+binary fashion, i.e., it is not the case that children either succeed or
+fail in encoding minimal contrast when learning the meanings. Rather,
+they may be encoding the phonological form of words in a probabilistic
+fashion. According to this view, development does not so much involve a
+qualitative shift (i.e., a sudden emergence of an ability that did not
+exist before) as much as it consists in the continuous refinement of
+initially noisy representations.
 
-We provide an intuitive illustration of how such an account explains
-patterns of learning and development in Figure \ref{fig:illus}. We
-observe low accuracy in word learning when the perceptual distance
-between the labels is small relative to the uncertainty with which these
-labels are encoded. For example, in Stager and Werker's original
-experiment, children are supposed to associate label 1 (\enquote{bih})
-and label 2 (\enquote{dih}) with object 1 and object 2, respectively.
-Though infants could learn that the label \enquote{bih} is a better
+In a probabilistic account, a word can be represented as a probability
+distribution over sound instances organized in a similarity space. The
+probability is highest at the most typical sound instance. It decreases
+as the instance becomes less typical. The precision of the
+representation can be characterized by how much it tolerates slightly
+atypical pronunciations. This tolerance is captured formally by the
+variance of the probability distribution: larger variance indicates
+higher tolerance and lower precision, whereas smaller variance indicates
+lower tolerance and higher precision.
+
+This framework can explain several findings. In Stager and Werker's
+original experiment, children are supposed to associate one label
+\enquote{bih} with object 1 and a second label \enquote{dih} with object
+2. Though infants could learn that the label \enquote{bih} is a better
 match to object 1 than \enquote{dih}, they could still judge the sound
 \enquote{dih} as a plausible instance of the label \enquote{bih}, thanks
-to the relatively large uncertainty of the encoding, and this confusion
-leads to \enquote{failure} in the recognition task. According to this
-account, accuracy in word learning improves if we increase either the
-perceptual distinctiveness of the stimuli (e.g., through using
-different-sounding labels), or the precision of the encoding itself
-(e.g., across development).
+to the relatively large variance of the early encoding, and this
+confusion leads to \enquote{failure} in the recognition task (Figure
+\ref{fig:illus}, top). Though learning is small and is easily disrupted
+by the Switch task, it can still be detected when less demanding methods
+are used (Yoshida et al., 2009).
 
-Building on this intuition, the current work proposes a probabilistic
-model, which we use to both account for previous experimental findings,
-and to make new predictions that have not been tested before. Using new
-data collected from both preschool children and adults, we show that the
-model can explain various patterns of learning both within the same age
-and across development.
+The learning accuracy increases (and is detected even by demanding tests
+such as the Switch) for more distinct word-forms (e.g., \enquote{lif}
+vs. \enquote{neem}) where the perceptual distance is large relative to
+the variance (Figure \ref{fig:illus}, left). Distinctiveness can be
+enhanced even for minimally different sounds when other cues highlight
+their difference (Dautriche, Swingley, \& Christophe, 2015; Rost \&
+McMurray, 2009, 2010; Thiessen, 2007; Yeung \& Werker, 2009).
+
+Finally, development can be understood as an increase in the precision
+(i.e., a decrease in the variance) of the probabilistic representations
+(Figure \ref{fig:illus}, right). Such an increase in precision renders
+minimally different sounds less confusing. Importantly, a more precise
+representation still has a non-zero variance --- Learning difficulties
+can still be induced with challenging stimuli or in cognitively
+demanding situations as was demonstrate in adults studies (Pajak et al.,
+2016; White et al., 2013).
+
+\subsection{This study}\label{this-study}
+
+The probabilistic account has been put forward to explain patterns of
+learning and development at the qualitative level. However, it is
+crucial to have a precise computational instantiation of this account
+which would allow us to \emph{quantify} its explanatory power. We could
+find one previous work that attempted to provide such a computational
+instantiation (Hofer and Levy, 2017). However, this previous work was
+designed with the goal of reproducing the results of a specific study
+(Pajak et al., 2016) which focused on explaining the mismatch between
+speech perception and word learning in adults rather than on exploring
+the mechanism of development.
+
+The present work proposes a model of word-pair learning based on the
+probabilistic account. We tested the ability of this model to both
+\emph{explain} various findings in previous experiments in both children
+and adults (e.g., the fact that similar words are harder to learn than
+different words) and to \emph{predict} new learning patterns that have
+not been tested before (i.e., the effect of the referents' similarity on
+word learning). Crucially, we explored the extent to which development
+can be understood as a continuous refinement in similar representations
+across the lifespan.
+
+The paper is organized as follows. First, we introduce the model and we
+explain how it allows us to characterize behavior in a word learning
+task which resembles the one used in Stager and Werker (1997) and
+Yoshida et al. (2009). Then we explore the predictions of the model
+through simulating its behavior across different parameter settings.
+Next we quantify the extent to which the model's predictions account for
+human data we collected from both preschool children and adults.
+Finally, we discuss the results in the lights of existing accounts of
+word development.
 
@@
 The learner hears a sound \(s\) and has to decide which object \(o\)
-provides an optimal match to this sound. To this end, they must compute
-the probability \(P(o|s)\) for all possible objects. This probability
-can be computed by summing over all possible concepts and labels:
+provides an optimal match to this sound (see Figure \ref{fig:task}). To
+this end, they must compute the probability \(P(o|s)\) for all possible
+objects. This probability can be computed by summing over all possible
+concepts and labels:
 \[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
@@
 
-\begin{equation}
+\[
 P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-\end{equation}
+\]
 
@@
 
-We use the model to predict performance in the word learning task
-introduced by Stager and Werker (1997), with a two-alternative forced
-choice as in Yoshida et al. (2009). In this task, participants are first
+We use the model to predict word learning in a task similar to the one
+introduced by Stager and Werker (1997). We used a modified version of
+the task where the testing method consists in a two-alternative forced
+choice (Yoshida et al., 2009). In this task, participants are first
 exposed to the association between pairs of nonsense words (e.g.,
@@
 
-We used Equation 1 and the probability distributions defined above to
-obtain the exact analytical expression for the probability of accurate
-responses \(p(o_T | s)\) (target object \(o_T\) given a sound \(s\)) in
-the simple case of two-alternative forced choice in the testing phase of
-our experimental task:
+From the general expression (1), we derive three exact analytical
+solutions instantiating different learning assumptions. The first
+solution is derived by assuming that the labels are recovered from
+sounds with a certain level of uncertainty \(\sigma_L\), but that
+concepts are unambiguously recovered from the observed objects, i.e.,
+\(\sigma_C \rightarrow 0\). This assumption has been made --- whether
+implicitly or explicitly --- by most previous work in this line of
+research. One important implication of this assumption is that only the
+similarity of word sounds modulates success in word learning, not the
+similarity of the referents (as long as these referents are
+differentiated perceptually). This assumption yields the following
+probability function:
 
 \begin{equation}
-P(o_T|s)= \frac{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}}{1 + e^{-(\Delta s^2/2\sigma_L^2+ \Delta o^2/2\sigma_C^2)}+ e^{-\Delta s^2 /2\sigma_L^2} + e^{-\Delta o^2 /2\sigma_C^2 }}
+P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
 \end{equation}
 
-Figure \ref{fig:simulation} show simulations of the predicted accuracy
-(Expression 2) as a function of the distinctiveness parameters
-(\(\Delta s\) and \(\Delta o\)) and the precision parameters, i.e., the
-variances of the distributions \(p(s| L)\) and \(p(o | C)\). To
-understand the qualitative behavior of the model, we assumed for
-simplicity that the precision parameter has similar values in both
-distributions, i.e., \(\sigma =\sigma_C \approx \sigma_L\) (but we will
-allow those parameters to vary independently in the rest of the paper).
+The second solution is derived by making the more general assumption
+that both the labels and the concepts are recovered with ambiguity from
+the sounds and objects. We first introduce the simplifying assumption
+that the label-related uncertainty \(\sigma_L\) and the concept-related
+uncertainty \(\sigma_C\) are of a similar magnitude, i.e.,
+\(\sigma_C \approx \sigma_L = \sigma\). This assumption makes the
+prediction that the sound similarity and the object similarity impact
+word learning accuracy in exactly the same way. Furthermore, it allows
+us to study the behavior of the model with minimal free parameters.
+
+\begin{equation}
+P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
+\end{equation}
+
+We finally derive the third (and most general) solution which allows
+label- and concept-related uncertainties to vary independently.
+
+\begin{equation}
+P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
+\end{equation}
+
+In order to understand the predictions of the models (especially the
+more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation}
+show some simulations of the accuracy \(P(o_T|s)\) as a function of the
+distinctiveness parameters (\(\Delta s\) and \(\Delta o\)) and the
+uncertainty parameters \(\sigma_L\) and \(\sigma_C\).
 
@@
 
-The simulations explain some previously documented facts, and make new
-predictions:
+The simulations explain two experimental results from previous studies
+and make one new prediction:
 
@@
   For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
-  when the representational uncertainty (characterized with \(\sigma\))
-  decreases. This fact may explain development, i.e., younger children
-  have noisier representations (see Swingley, 2007; Yoshida et al.,
-  2009), which leads to lower word recognition accuracy, especially for
+  when the representational uncertainty \(\sigma\) decreases. This fact
+  may explain development, i.e., younger children have noisier
+  representations (see Swingley, 2007; Yoshida et al., 2009), which
+  leads to lower word recognition accuracy, especially for
   similar-sounding words.
@@
   disambiguating similar sounding words (e.g., Fennell \& Waxman, 2010;
-  Rost \& McMurray, 2009; Thiessen, 2007), but to our knowledge no
+  Rost \& McMurray, 2009; Thiessen, 2007), but to our knowledge, no
   previous study in the literature tested the effect of the visual
@@
 parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
-exclusion criteria and the model's main predictions were pre-registered.
+exclusion criteria and the model's main predictions were
+pre-registered.\footnote{https://osf.io/942gv/}
 
@@
 
-We planned to recruit a sample of N=60 children ages 4-5 years from the
-Bing Nursery School on Stanford University's campus. Here we report data
-from n=55 children. An additional n=35 children participated but were
-removed from analyses because they were not above chance on the catch
-trials due to the challenging nature of our procedure (see below). We
-also planned to recruit a sample of N=60 adults on Amazon Mechanical
-Turk. Data from n=26 participants were excluded due to low scores on the
-catch trials (n=26 ) or because they were familiar with the non-English
-sound stimuli we used in the adult experiment (n=0), yielding a final
-sample of n=74.
+We report data from \(N=\) 63 children ages 4-5 years from the Bing
+Nursery School on Stanford University's campus. An additional \(N=\) 39
+children participated but were removed from analyses because they were
+not above chance on the catch trials due to the challenging nature of
+our procedure (see below). We also report data from \(N=\) 74 adult
+participants tested on Amazon Mechanical Turk. An additional \(N=\) 26
+were tested but removed from analyses because they had low scores on the
+catch trials or because they were familiar with the non-English sound
+stimuli we used in the adult experiment.
 
@@
 generated three kinds of nonsense word pairs which varied in their
-degree of similarity to English speakers: 1) \enquote{different}:
-\enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2)
-\enquote{intermediate}: \enquote{aka}/\enquote{ama} and
-\enquote{ada}/\enquote{aba}, and 3) \enquote{similar} non-English
-minimal pairs: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi)
-and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
+degree of perceptual similarity to English speakers: 1) \emph{different}
+pairs: \enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2)
+\emph{intermediate} pairs: \enquote{aka}/\enquote{ama} and
+\enquote{ada}/\enquote{aba}, and 3) \emph{similar} non-English pairs:
+\enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and
+\enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
 
@@
 library\footnote{https://github.com/erindb/stimuli} which allowed us to
-generate objects in four different categories: \enquote{tree},
-\enquote{bird}, \enquote{bug}, and \enquote{fish}. These categories are
+generate objects in four different categories: \enquote{tree,}
+\enquote{bird,} \enquote{bug,} and \enquote{fish.} These categories are
 supposed to be naturally occurring kinds that might be seen on an alien
-planet. In each category, we generated \enquote{different},
-\enquote{intermediate} and \enquote{similar} pairs by manipulating a
+planet. In each category, we generated \emph{different},
+\emph{intermediate} and \emph{similar} pairs by manipulating a
 continuous property controlling features of the category's shape (e.g,
@@
 
-In a separate survey, \(N=20\) participants recruited on Amazon
-Mechanical Turk evaluated the similarity of each sound and object pair
-on a 7-point scale. We scaled responses within the range {[}0,1{]}. Data
-are shown in Figure \ref{fig:stim}, for each stimulus group. These data
-will be used in the models as the perceptual distance of sound pairs
-(\(\Delta s\)) and object pairs (\(\Delta o\)).
+In order to validate and quantify our similarity scales, we ran a
+separate survey on Amazon Mechanical Turk where we asked \(N=20\) adults
+participants to evaluate the similarity of each sound and object pair on
+a 7-point scale. Data are shown in Figure \ref{fig:stim} where we scaled
+responses within the range {[}0,1{]} for each stimulus group. These data
+will be used in all models as a proxy for the perceptual distance
+between the sound pairs (\(\Delta s\)) and the object pairs
+(\(\Delta o\)).
 
-\includegraphics{ms_files/figure-latex/unnamed-chunk-6-1.pdf}
-\#\#\#Design
+\subsubsection{Design}\label{design}
 
 Each age group saw only two of the three levels of similarity described
-in the previous sub-section: \enquote{different} vs.
-\enquote{intermediate} for preschoolers, and \enquote{intermediate} vs.
-\enquote{similar} for adults. We made this choice in light of pilot
-studies showing that adults were at ceiling with \enquote{different}
-sounds/objects, and children were at chance with the \enquote{similar}
-sounds/objects. That said, this difference in the level of similarity is
-accounted for in the model through using the appropriate perceptual
-distance used in each age group (Figure \ref{fig:stim}).
+in the previous sub-section: \emph{different} vs. \emph{intermediate}
+for the preschoolers, and \emph{intermediate} vs. \emph{similar} for
+adults. We made this choice in light of pilot studies showing that
+adults were at ceiling with \emph{different} sounds/objects, and
+children were at chance with the \emph{similar} sounds/objects. That
+said, this difference in the level of similarity is accounted for in the
+model through using the appropriate distance (Figure \ref{fig:stim}).
 
@@
 conditions: high/low sound similarity crossed with high/low visual
-object similarity. Besides the 4 conditions, we also tested participants
-on a fifth catch condition which was similar in its structure to the
-other ones, but was used only to select participants who were able to
-follow the instructions and show minimal learning.
+object similarity. Besides the four conditions, we also tested
+participants on a fifth catch condition which was similar in its
+structure to the other ones but was used only to select participants who
+were able to follow the instructions and show minimal learning.
 
@@
 
-\caption{Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+\caption{Accuracy of word recognition as a function of the sound distance, the object distance, and the age group (preschool children vs.
 adults).
-We show both experimental results (solid lines) and model predictions (dashed lines).
+We show both the models' predictions (dashed lines) and the experimental results (solid lines).
+The single-variance model uses one joint fitting parameter for both sound and meaning variances.
+The double-variance model uses two separate fittings parameters for the sound and the meaning variances.
 Error bars represent 95\% confidence intervals.}\label{fig:allData}
@@
 \(\beta =\) 0.52 (\(p\) \textless{} 0.001), replicating previous
-findings. For object distance, we found \(\beta =\) 0.83 (\(p\)
-\textless{} 0.001), and this finding confirms the new prediction of our
-model. Finally, for the age group, we obtained \(\beta =\) 0.76 (\(p\)
-\textless{} 0.001), showing that performance improves with age. In
-addition, we found two-way interactions between sound distance and age
-(\(\beta =\) 0.15, \(p\) = 0.17) and between object distance and age
-(\(\beta =\) 0.45, \(p\) \textless{} 0.001).
+findings that sound distance modulates success in word learning (e.g.,
+Stager \& Werker, 1997). For object distance, we found \(\beta =\) 0.83
+(\(p\) \textless{} 0.001), and this finding confirms the new prediction
+of our model according to which object distance also modulates success
+in word learning. Finally, for the age group, we obtained \(\beta =\)
+0.76 (\(p\) \textless{} 0.001), showing that overall performance
+improves with age.
 
-We next fit our model (using Equation 2) to the participants' responses
-in each age group. The values of \(\Delta s\) and \(\Delta o\) were set
-based on data from the similarity judgment task (Figure \ref{fig:stim}).
-Thus, the model has two degrees of freedom for each group, i.e.,
-\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:allData} (dashed lines)
-shows the predictions. The model captures the qualitative patterns in
-both age groups: starting from a low accuracy recognition when both the
-sound and object distances are small, the model correctly predicts an
-increase in accuracy when either the sound distance or the object
-distance increases. Further, accuracy is correctly predicted to be
-maximal when both the sound and object distances are high.
+\begin{table}
 
-The values of the parameters were as follows. Children had a
-label-specific uncertainty of \(\sigma_S =\) 0.83 {[}0.64,
-1.02{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
-and a concept-specific uncertainty of \(\sigma_C =\) 0.31 {[}0.11,
-0.51{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.12
-{[}0.12, 0.13{]}, and a concept-specific uncertainty of \(\sigma_C =\)
-0.17 {[}0.16, 0.18{]}. As predicted, the uncertainty parameters were
-larger for children than they were for adults, showing that the
-probabilistic representations becomes more refined (that is, \(\sigma\)
-becomes smaller) across development. The developmental effect was more
-important for the label-specific uncertainty.
+\caption{\label{tab:models}Characteristics and performance of the models used in this study.}
+\centering
+\begin{tabular}[t]{>{\bfseries}llrrrlrl}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Children} & \multicolumn{2}{c}{Adults} \\
+\cmidrule(l{2pt}r{2pt}){5-6} \cmidrule(l{2pt}r{2pt}){7-8}
+Model & Structure & Param. & R\textsuperscript{2} & Sig\textsubscript{L} & Sig\textsubscript{C} & Sig\textsubscript{L} & Sig\textsubscript{C}\\
+\midrule
+model 1 & Sig\textsubscript{L} only & 1 & 0.27 & 1.00 & -- & 0.37 & --\\
+model 2 & Sig\textsubscript{L} = Sig\textsubscript{C} & 1 & 0.95 & 0.60 & 0.6 & 0.15 & 0.15\\
+model 3 & Sig\textsubscript{L} != Sig\textsubscript{C} & 2 & 1.00 & 0.83 & 0.31 & 0.12 & 0.17\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-The models explained the majority of the variance in the participants'
-mean responses (\(R^2=\) 1, for the combined adult and children's data).
-To investigate whether the model's predictive power was due to
-overfitting, we fit a simplified version with only one degree of freedom
-(i.e., a single variance common to both sounds and objects). This
-single-variance model explained as much variance in the mean responses
-(\(R^2=\) 0.95). It also captured the main qualitative patterns (graph
-not shown), suggesting that the explanatory power of the model is
-largely due to its structure, rather than its degrees of freedom.
+We next fit the three models obtained through expressions (1), (2), and
+(3) to the participants' responses in each age group. The predictions of
+the models are shown \ref{fig:allData} (dashed lines) and the parameter
+estimates (for \(\sigma_L\) and \(\sigma_C\)) as well as models'
+goodness to fit (i.e., measured through \(R^2\)) are presented in Table
+\ref{tab:models}.
 
-An unexpected outcome was that adult participants deviated slightly from
-the model's numbers: While the model predicted accuracy to be more
-sensitive to object distance when sound distance is higher (and
-vice-versa), adult participants showed the opposite pattern. This
-deviation is an interesting starting point for future work as it may
-suggest that participants are more likely to pay attention to and
-integrate additional sources of information when ambiguity is higher.
+Model 1, which does not take into account ambiguity in recovering
+concepts from observed objects, explains only a small part of the
+variance. In contrast, Model 3, which does take into account this
+ambiguity, accounts for all the variance. Interestingly, Model 2 which
+has a single, shared uncertainty parameter for both auditory and visual
+modalities still explains almost all the variance in human data,
+suggesting that the explanatory power of the general Model 3 is largely
+due to its structure, rather than its degrees of freedom.
+
+As predicted, the uncertainty parameters were larger for children than
+they were for adults (Table \ref{tab:models}), showing that the
+probabilistic representations become more refined (that is, \(\sigma\)
+becomes smaller) across development. Further, the parameter estimates of
+Model 3 show that this developmental effect is more important for the
+label-specific uncertainty that it is for the concept-specific
+uncertainty.
 
@@
 showing a discrepancy between children's speech perception abilities and
-their word learning skills. While much of the previous investigation of
-this finding has been interested in the source of this discrepancy, here
-we have explored how it could arise from continuous developmental change
-in perceptual uncertainty.
+their word learning skills. While this fact might seem like a specific
+stage in early development, our model demonstrated, instead, that it can
+be more simply understood in terms of continuous developmental change.
 
-Building on some previous discussions (e.g., Swingley, 2007; Yoshida et
-al., 2009), we proposed a model where perceptual stimuli are encoded
-probabilistically. We tested the model's predictions against data
-collected from preschool children and adults and we showed that
-developmental changes in word-object mappings can indeed be
-characterized as a continuous refinement (i.e., uncertainty reduction)
-in qualitatively similar representations across the life span.
+The main assumption of the model was that both word form and referent
+are encoded in a probabilistic fashion. The model provided a
+quantitative instantiation of the continuous development hypothesis
+(Pajak et al., 2016; e.g., Swingley, 2007; Yoshida et al., 2009)). More
+precisely, we showed that developmental changes in word-object mappings
+can be characterized as a continuous refinement in the precision of the
+probabilistic representations.
 
-The model made a new prediction to which we tested experimentally:
-Learning similar words is not only modulated by the similarity of their
-phonological forms, but also by the visual similarity of their semantic
-referents. More generally, since visual similarity is an early
-organizing feature in the semantic domain (e.g., Wojcik \& Saffran,
-2013), our finding suggests that children may prioritize the acquisition
-of words that are quite distant in the semantic space. This suggestion
-is supported by recent findings based on the investigation of early
-vocabulary growth (Engelthaler \& Hills, 2017; Sizemore, Karuza, Giusti,
-\& Bassett, 2018).
+We find in the literature two broad accounts of development in the
+Switch task: One that suggests \emph{direct} development of the sound
+representation and one that hypothesizes \emph{indirect} development of
+this representation through improvement in general cognitive resources.
+On the first account, the sound representation becomes more precise as
+learners refine the boundaries of their initially ambiguous phonetic
+categories and as they gain more experience with the functional role of
+these categories, i.e., contrasting word meaning (Apfelbaum \& McMurray,
+2011; Dietrich, Swingley, \& Werker, 2007; Rost \& McMurray, 2009, 2010;
+Yoshida et al., 2009). On the second account, the precision of sound
+encoding in the switch task improves as a result of the maturation of
+more general resources like the attentional and working memory capacity
+(Hofer \& Levy, 2017; Stager \& Werker, 1997; Werker \& Fennell, 2004).
+Such improvement allows older children and adults to better encode the
+sound details while simultaneously matching these sounds to visual
+objects. These two accounts are complementary and both seem to play a
+role (see Tsui, Byers-Heinlein, \& Fennell, 2019 for a review).
 
-One limitation of this work is that the model was fit to data from
-children at a relatively older age (4-5 years old) than what is
-typically studied in the literature (14-18 month-old). We selected this
-older age group to optimize the number and precision of the experimental
-measures (both are crucial to model fitting). Data collection involved
-presenting participants with several trials across four conditions in a
-between-subject design. It would have been challenging to obtain such
-measures with infants.
+Our model is compatible with both of these accounts. In our work, the
+probability distributions do not distinguish between the direct and
+indirect sources of uncertainty --- both are included. Indeed, part of
+the measured uncertainty reflects the learner's degrees of confidence in
+the phonetic/phonological boundaries (i.e., the direct account) and
+another part reflects a possible drop in perceptual acuity due to high
+cognitive load (i.e., the indirect account). Note, however, that the
+model (at least in its current format) is incapable of answering
+questions about the development of each of these sources of uncertainty
+separately or about their relative contribution to the global
+uncertainty.
 
-In sum, this paper proposes a model that accounts for the development of
-an important aspect of word learning. Our account suggests that the
-developmental data can be explained based on a continuous process
-operating over similar representations across development, suggesting
-developmental continuity. We used a case from word learning as an
-example, but the same idea might apply to other aspects of cognitive
-development that are typically thought of as stage-like (e.g.,
-acquisition of a theory of mind). Computational models, such as the one
-proposed here, can help us investigate the extent to which such
+Werker and Curtin (2005) proposed to explain development in the Switch
+task using their theory called Processing Rich Information from
+Multidimensional Interactive Representations (or PRIMIR) which purports
+to explain various phenomena in early speech perception and word
+learning within a unified framework. PRIMIR posits that children
+initially try to attend to various features of the speech signal,
+regardless of whether or not these features are relevant to the task at
+hand. For example, when learning the meaning of similar sounds, infants
+are unsure what detail is most important to identify words (i.e., the
+phonemes), and will instead activate several aspects of the information
+simultaneously (including, for example, the gender of the speaker). The
+lack of attentional selection leads to confusion and then to failure in
+the task.
+
+According to PRIMIR, learning similar-sounding words becomes more robust
+over time as children develop abstract phonemic categories. The latter
+act as filters, allowing children to attend selectively to the important
+information. This account is also compatible with our model (as it
+resembles the direct account we discussed above). Developing a better
+attentional strategy (thanks to phoneme) can translate into a reduction
+in the uncertainty about whether a sound contrast signals a change in
+meaning.
+
+While most research focused on the sound representation in analyzing the
+Switch task, this work showed that the visual representation of the
+referent is equally important. Indeed, Model 1 --- which assumes that
+any visually discriminable contrast can be encoded unambiguously as
+separate referents --- failed to explain the data, whereas Model 2 and 3
+--- which take into account visual ambiguity --- succeeded. As a
+consequence of this assumption, we found that just like word learning is
+modulated by the phonological similarity of the form, it is also
+modulated by the visual similarity of the semantic referents.
+
+Model 2, which predicts that sound similarity and visual similarity
+influence word learning accuracy in the same way, explained slightly
+less variance than Model 3 which predicts that these modalities
+influence word learning differently. More precisely, a comparison of the
+variance estimates across age groups shows that uncertainty reduction in
+the visual modality was lower compared to that of the auditory modality
+(Table 1). Perhaps this difference is due to the fact that, in our task,
+the auditory speech had more sources of noise --- that children have to
+deal with --- than the visual input does. The processing of speech
+involved dealing with both perceptual noise and categorical ambiguity
+(due to the fact that the phonemic boundaries are still developing). In
+contrast, the processing of the visual input in our task involved only
+perceptual noise and no category-related uncertainty.
+
+Our finding that word learning is mediated by the visual similaérity of
+the semantic objects has implications for theories of lexical
+development. It suggests that, all things being equal, children may
+prioritize the acquisition of words whose semantic referents are
+visually different, as this allows them to minimize semantic ambiguity.
+It will be interesting for future work to explore whether the results
+that we obtained using visual similarity generalize to richer, more
+conceptual features in the semantic space. This suggestion is, indeed,
+supported by recent work investigating vocabulary development
+(Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore,
+Karuza, Giusti, \& Bassett, 2018)
+
+There are a few limitations to this work. One is that the model was fit
+to data from children at a relatively older age (4-5 years old) than
+what is typically studied in the literature (14-17 month-old). We
+selected this older age group to optimize the number and precision of
+the experimental measures (both are crucial to model fitting). Data
+collection involved presenting participants with several trials across
+four conditions in a between-subject design. It would have been
+challenging to obtain such measures with infants. That said, though we
+used data from older children, we still found clear differences compared
+to adults, suggesting that development does not stop at 17 months, but
+continues throughout childhood.
+
+One limitation of the model is that it only accounts for bottom-up,
+similarity-based effects. It does not account for how high-level factors
+such as social and communicative cues can influence learning. For
+example, Fennell and Waxman (2010) highlighted the fact that the Switch
+task introduces novel words in isolation (e.g., \enquote{neem!}) rather
+than within a naming phrase (e.g., \enquote{look at the neem!}). This
+fact may prompt children to interpret these novel words in a
+non-referential way (e.g., an exclamation such as \enquote{Wow!}).
+
+To conclude, this paper proposes a model that accounts for the
+development of an important aspect of word learning. Our account
+suggests that the developmental data can be explained based on a
+continuous process operating over similar representations across the
+lifespan, suggesting developmental continuity. We used a case from word
+learning as an example, but the same idea might apply to other aspects
+of cognitive development that are typically thought of as stage-like
+(e.g., acquisition of a theory of mind). Computational models, such as
+the one proposed here, can help us investigate the extent to which such
 discontinuities emerge due to genuine qualitative changes and the extent
@@
 \hypertarget{refs}{}
+\hypertarget{ref-apfelbaum2011}{}
+Apfelbaum, K. S., \& McMurray, B. (2011). Using variability to guide
+dimensional weighting: Associative mechanisms in early word learning.
+\emph{Cognitive Science}, \emph{35}.
+
 \hypertarget{ref-barr2013}{}
@@
 Press.
+
+\hypertarget{ref-dautriche2015}{}
+Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
+phonological neighbors: Syntactic category matters. \emph{Cognition},
+\emph{143}.
+
+\hypertarget{ref-dietrich2007}{}
+Dietrich, C., Swingley, D., \& Werker, J. (2007). Native language
+governs interpretation of salient speech sound differences at 18 months.
+\emph{Proceedings of the National Academy of Sciences}, \emph{104}.
 
@@
 
+\hypertarget{ref-fernald2006}{}
+Fernald, A., Perfors, A., \& Marchman, V. A. (2006). Picking up speed in
+understanding: Speech processing efficiency and vocabulary growth across
+the 2nd year. \emph{Developmental Psychology}, \emph{42}.
+
+\hypertarget{ref-fourtassi2018}{}
+Fourtassi, A., Bian, Y., \& Frank, M. C. (2018). Word learning as
+network growth: A cross-linguistic analysis. In \emph{CogSci}.
+
+\hypertarget{ref-golinkoff1987}{}
+Golinkoff, R. M., Hirsh-Pasek, K., Cauley, K. M., \& Gordon, L. (1987).
+The eyes have it: Lexical and syntactic comprehension in a new paradigm.
+\emph{Journal of Child Language}, \emph{14}.
+
 \hypertarget{ref-hofer2017}{}
@@
 
+\hypertarget{ref-pater2004}{}
+Pater, J., Stager, C., \& Werker, J. (2004). The perceptual acquisition
+of phonological contrasts. \emph{Language}, \emph{80}.
+
 \hypertarget{ref-piaget1954}{}
@@
 Science}, \emph{12}.
+
+\hypertarget{ref-rost2010}{}
+Rost, G., \& McMurray, B. (2010). Finding the signal by adding noise:
+The role of noncontrastive phonetic variability in early word learning.
+\emph{Infancy}, \emph{15}.
 
@@
 
+\hypertarget{ref-tsui2019}{}
+Tsui, A. S. M., Byers-Heinlein, K., \& Fennell, C. (2019). Associative
+word learning in infancy: A meta-analysis of the switch task.
+\emph{Developmental Psychology}, \emph{55}.
+
+\hypertarget{ref-werker2005}{}
+Werker, J., \& Curtin, S. (2005). PRIMIR: A developmental framework of
+infant speech processing. \emph{Language Learning and Development},
+\emph{1}.
+
+\hypertarget{ref-werker2004}{}
+Werker, J., \& Fennell, C. (2004). Listening to sounds versus listening
+to words: Early steps in word learning. In D. G. Hall \& S. Waxman
+(Eds.), \emph{Weaving a lexicon}. Cambridge: MIT Press.
+
+\hypertarget{ref-werker1998}{}
+Werker, J., Cohen, L. B., Lloyd, V. L., Casasola, M., \& Stager, C.
+(1998). Acquisition of word--object associations by 14-month-old
+infants. \emph{Developmental Psychology}, \emph{34}.
+
 \hypertarget{ref-werker2002}{}
@@
 
-\hypertarget{ref-wojcik2013}{}
-Wojcik, E., \& Saffran, J. (2013). The ontogeny of lexical networks:
-Toddlers encode the relationships among referents when learning novel
-words. \emph{Psychological Science}, \emph{24}(10).
+\hypertarget{ref-yeung09}{}
+Yeung, H., \& Werker, J. (2009). Learning words' sounds before learning
+how words sound: 9-month-olds use distinct objects as cues to categorize
+speech information. \emph{Cognition}, \emph{113}.
 

### 2019-07-22 journal/ms.Rmd
journal version

@@
 
-Some researchers [e.g., @swingley2007; @yoshida2009; @pajak2016] proposed that the phonological form may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
+Some researchers [@swingley2007; @yoshida2009; @pajak2016] proposed that the phonological form may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
 Rather, they may be encoding the phonological form of words in a probabilistic fashion.
@@
 The main assumption of the model was that both word form and referent are encoded in a probabilistic fashion.
-The model provided a quantitative instantiation of the continuous development hypothesis [e.g., @swingley2007; @yoshida2009; @pajak2016]).
+The model provided a quantitative instantiation of the continuous development hypothesis [@swingley2007; @yoshida2009; @pajak2016].
 More precisely, we showed that developmental changes in word-object mappings can be characterized as a continuous refinement in the precision of the probabilistic representations.

### 2019-07-22 journal/ms.tex
journal version

@@
 
-Some researchers (Pajak et al., 2016; e.g., Swingley, 2007; Yoshida et
-al., 2009) proposed that the phonological form may not be encoded in a
-binary fashion, i.e., it is not the case that children either succeed or
-fail in encoding minimal contrast when learning the meanings. Rather,
-they may be encoding the phonological form of words in a probabilistic
+Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al.,
+2009) proposed that the phonological form may not be encoded in a binary
+fashion, i.e., it is not the case that children either succeed or fail
+in encoding minimal contrast when learning the meanings. Rather, they
+may be encoding the phonological form of words in a probabilistic
 fashion. According to this view, development does not so much involve a
@@
 quantitative instantiation of the continuous development hypothesis
-(Pajak et al., 2016; e.g., Swingley, 2007; Yoshida et al., 2009)). More
+(Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009). More
 precisely, we showed that developmental changes in word-object mappings

### 2019-07-22 journal/ms.Rmd
journal vers

@@
 The authors measured word learning using an audio-visual habituation Switch task.
-First, infants are familiarized with two word-object pairings (e.g., Word A with Object A and Word B with Object B).
+First, infants are familiarized with two word-object pairings (e.g., lable A with object A and label B with object B).
 Second, they are tested using two types of trials.
-The control 'same' trial consists of a correct pairing  (e.g., Word A with Object A) and the 'switch' trial consists of a wrong pairing (e.g., Word A with Object B).
+The control 'same' trial consists of a correct pairing  (e.g., label A with object A) and the 'switch' trial consists of a wrong pairing (e.g., label A with object B).
 If babies have correctly learned the association during the familiarization, they are supposed to be surprised by the 'switch' trial and not by the 'same' trial.
@@
 This failure has initially been taken as evidence that 14-month olds do not encode subtle sounds during meaning learning [@stager1997; @pater2004].
-This interpretation suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children, around 17 months [@werker2002], typically do.
+This interpretation suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children, around 17 months, typically do [@werker2002].
 
@@
 
-Our finding that word learning is mediated by the visual similaérity of the semantic objects has implications for theories of lexical development.
+Our finding that word learning is mediated by the visual similarity of the semantic objects has implications for theories of lexical development.
 It suggests that, all things being equal, children may prioritize the acquisition of words whose semantic referents are visually different, as this allows them to minimize semantic ambiguity.

### 2019-07-22 journal/ms.tex
journal vers

@@
 task. First, infants are familiarized with two word-object pairings
-(e.g., Word A with Object A and Word B with Object B). Second, they are
-tested using two types of trials. The control \enquote{same} trial
-consists of a correct pairing (e.g., Word A with Object A) and the
-\enquote{switch} trial consists of a wrong pairing (e.g., Word A with
-Object B). If babies have correctly learned the association during the
+(e.g., lable A with object A and label B with object B). Second, they
+are tested using two types of trials. The control \enquote{same} trial
+consists of a correct pairing (e.g., label A with object A) and the
+\enquote{switch} trial consists of a wrong pairing (e.g., label A with
+object B). If babies have correctly learned the association during the
 familiarization, they are supposed to be surprised by the
@@
 fail to encode the contrastive phonetic detail, whereas older children,
-around 17 months (Werker, Fennell, Corcoran, \& Stager, 2002), typically
-do.
+around 17 months, typically do (Werker, Fennell, Corcoran, \& Stager,
+2002).
 
@@
 
-Our finding that word learning is mediated by the visual similaérity of
+Our finding that word learning is mediated by the visual similarity of
 the semantic objects has implications for theories of lexical

### 2019-08-13 Analysis/process.Rmd
new stuff jounral

@@
 ```{r}
-d_child <- read_delim("kids_all.txt", delim = " ") %>%
+d_child <- read_delim("kids_all_final.txt", delim = " ") %>%
   filter(type == "Test") %>%

### 2019-08-13 cogsci/cogsci.Rmd
new stuff jounral

@@
     \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
-    \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ University of Illinois
+    \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University
     \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
@@
 
-```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+```{r all_data, fig.env = "figure*", fig.pos = "h", fig.align = "center", fig.width=8, fig.height=4, fig.cap = "\\label{fig:data_all}Accuracy of novel word recognition as a function of the sound distance, the object distance, and the age group (preschool children vs.
 adults).
 We show both the models' predictions (dashed lines) and the experimental results (solid lines).
+The single-variance model uses one joint fitting parameter for both sound and meaning variances.
+The double-variance model uses two separate fittings parameters for the sound and the meaning variances.
 Error bars represent 95\\% confidence intervals."}

### 2019-08-13 cogsci/cogsci.tex
new stuff jounral

@@
 
-\author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }
+\author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Sophie Regan} \\ \texttt{sregan20@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
+Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
 
@@
 pairs such as ``dih'' and ``bih'', they appear to fail in mapping this
-pair to two different objects. Follow-up studies has focused on
+pair to two different objects. Follow-up studies have focused on
 proposing possible explanations for this observed gap between speech
@@
 similar to those shown by 14-month-olds when the task is more
-challenging and when similarity between words increases (Pajak, Creel,
-\& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
+challenging and when the similarity between words increases (Pajak,
+Creel, \& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
 
@@
 the initial noisy representations become more precise. In addition, more
-precise representation are still imperfect: Even adults show low
-accuracy learning when the sounds are subtle, e.g., non-native sounds
-(Pajak et al., 2016).
+precise representations are still imperfect: Even adults show low
+accuracy learning when the sound contrasts are subtle, e.g., non-native
+sounds (Pajak et al., 2016).
 
@@
 learning improves if we increase either the perceptual distinctiveness
-of the stimuli (e.g., through using different-sounding labels), or the
+of the stimuli (e.g., through using different-sounding labels) or the
 precision of the encoding itself (e.g., across development).
@@
 
-\caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data.
+\caption[An illustration of the probabilistic/continuous account using simulated data]{An illustration of the probabilistic/continuous account using simulated data.
 A word is represented with a distribution over the perceptual space (indicated in red or blue).
 When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
-The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
+The accuracy increases when the stimuli are less similar (left panel), or when the representations are more precise (right panel).}\label{fig:illus}
 \end{figure}
@@
 
-\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\Delta s$ and $\Delta o$ and representation precision $\sigma$ (For clarity, we assume here that $\sigma$=$\sigma_C$=$\sigma_L$).
+\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\Delta s$ and $\Delta o$ and representation precision $\sigma$ (for simplicity, we assume here that $\sigma$=$\sigma_C$=$\sigma_L$).
 Dashed line represents chance.}\label{fig:simulation}
@@
 
-We planned to recruit a sample of N=60 children ages 4-5 years from the
-Bing Nursery School on Stanford University's campus. Here we report data
-from n=47 children. An additional n=28 children participated but were
-removed from analyses because they were not above chance on the catch
-trials due to the challenging nature of our procedure (see below). We
-also planned to recruit a sample of N=60 adults on Amazon Mechanical
-Turk. Data from n=10 participants were excluded due to low scores on the
-catch trials (n=9 ) or because they were familiar with the non-English
-sound stimuli we used in the adult experiment (n=1), yielding a final
-sample of n=50.
+We planned to recruit a sample of \(N=60\) children ages 4-5 years from
+the Bing Nursery School on Stanford University's campus. Here we report
+data from \(N=\) 55 children. An additional \(N=\) 35 children
+participated but were removed from analyses because they were not above
+chance on the catch trials due to the challenging nature of our
+procedure (see below). We also collected a planned sample of \(N=100\)
+adult participants through Amazon Mechanical Turk. We planned to exclude
+data from participants who did not do well on the catch trials (\(N=\)
+26) and from participants who were familiar with the non-English sound
+stimuli we used in the adult experiment (\(N=\) 0), yielding a final
+sample of \(N=\) 74.
 
@@
 in the previous sub-section: ``different'' vs. ``intermediate'' for
-preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
+preschoolers and ``intermediate'' vs. ``similar'' for adults. We made
 this choice in light of pilot studies showing that adults were at
@@
 with the ``similar'' sounds/objects. That said, this difference in the
-level of similarity is accounted for in the model through using the
+level of similarity is accounted for in the model by using the
 appropriate perceptual distance used in each age group (Figure
@@
 on a fifth catch condition which was similar in its structure to the
-other ones, but was used only to select participants who were able to
+other ones but was used only to select participants who were able to
 follow the instructions and show minimal learning.
@@
 
-\caption{\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs.
+\caption{\label{fig:data_all}Accuracy of novel word recognition as a function of the sound distance, the object distance, and the age group (preschool children vs.
 adults).
-We show both experimental results (solid lines) and model predictions (dashed lines).
+We show both the models' predictions (dashed lines) and the experimental results (solid lines).
+The single-variance model uses one joint fitting parameter for both sound and meaning variances.
+The double-variance model uses two separate fittings parameters for the sound and the meaning variances.
 Error bars represent 95\% confidence intervals.}\label{fig:all_data}
@@
 
-Experimental results are shown in Figure 6 (solid lines). We first
-analyzed the results using a mixed-effects logistic regression with
-sound distance, object distance and age group as fixed effects, and with
-a maximal random effects structure (allowing us to take into account the
-full nested structure of our data) (Barr, Levy, Scheepers, \& Tily,
-2013). We found main effects for all the fixed effects in the
-regression. For the sound distance, we obtained \(\beta =\) 0.44 (\(p\)
+We first analyzed the results using a mixed-effects logistic regression
+with sound distance, object distance and age group as fixed effects, and
+with a maximal random effects structure (allowing us to take into
+account the full nested structure of our data) (Barr, Levy, Scheepers,
+\& Tily, 2013). We found main effects for all the fixed effects in the
+regression. For the sound distance, we obtained \(\beta =\) 0.52 (\(p\)
 \textless{} 0.001), replicating previous findings. For object distance,
-we found \(\beta =\) 0.5 (\(p\) \textless{} 0.001), and this finding
+we found \(\beta =\) 0.83 (\(p\) \textless{} 0.001), and this finding
 confirms the new prediction of our model. Finally, for the age group, we
-obtained \(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that
-performance improves with age. In addition, we found two-way
-interactions between sound distance and age (\(\beta =\) 0.17, \(p\)
-\textless{}0.05) and between object distance and age (\(\beta =\) 0.18,
-\(p\) \textless{}0.05).
+obtained \(\beta =\) 0.76 (\(p\) \textless{} 0.001), showing that
+performance improves with age.
 
 We next fit our model (using Equation 2) to the participants' responses
-in each age group. The values of \(\Delta s\) and \(\Delta o\) were set
-based on data from the similarity judgment task (Figure \ref{fig:stim}).
-Thus, the model has two degrees of freedom for each group, i.e.,
-\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (dashed lines)
-shows the predictions. The model captures the qualitative patterns in
-both age groups: starting from a low accuracy recognition when both the
-sound and object distances are small, the model correctly predicts an
-increase in accuracy when either the sound distance or the object
-distance increases. Further, accuracy is correctly predicted to be
-maximal when both the sound and object distances are high.
+in each age group using non-linear least-squares. The values of
+\(\Delta s\) and \(\Delta o\) were set based on data from the similarity
+judgment task (Figure \ref{fig:stim}). The model has two degrees of
+freedom for each group, i.e., \(\sigma_C\) and \(\sigma_L\). We call it
+the double-variance model. Figure \ref{fig:data_all} (dashed lines)
+shows the predictions. The double-variance model captures the behavioral
+patterns in both age groups: starting from a low accuracy recognition
+when both the sound and object distances are small, the model correctly
+predicts an increase in accuracy when either the sound distance or the
+object distance increases. Further, accuracy is correctly predicted to
+be maximal when both the sound and object distances are high.
 
 The values of the parameters were as follows. Children had a
-label-specific uncertainty of \(\sigma_S =\) 0.9 {[}0.68,
-1.11{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
-and a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1,
-0.49{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.14
-{[}-0.02, 0.3{]}, and a concept-specific uncertainty of \(\sigma_C =\)
-0.19 {[}0.04, 0.34{]}. As predicted, the uncertainty parameters were
+label-specific uncertainty of \(\sigma_S =\) 0.83 {[}0.64,
+1.02{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
+and a concept-specific uncertainty of \(\sigma_C =\) 0.31 {[}0.11,
+0.51{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.12
+{[}0.12, 0.13{]}, and a concept-specific uncertainty of \(\sigma_C =\)
+0.17 {[}0.16, 0.18{]}. As predicted, the uncertainty parameters were
 larger for children than they were for adults, showing that the
@@
 
-The models explained the majority of the variance in the participants'
-mean responses (\(R^2=\) 0.86, for the combined adult and children's
-data). To investigate whether the model's predictive power was due to
-overfitting, we fit a simplified version with only one degree of freedom
-(i.e., a single variance common to both sounds and objects). This
-single-variance model explained as much variance in the mean responses
-(\(R^2=\) 0.87). It also captured the main qualitative patterns (graph
-not shown), suggesting that the explanatory power of the model is
-largely due to its structure, rather than its degrees of freedom.
-
-An unexpected outcome was that adult participants deviated slightly from
-the model's numbers: While the model predicted accuracy to be more
-sensitive to object distance when sound distance is higher (and
-vice-versa), adult participants showed the opposite pattern. This
-deviation is an interesting starting point for future work as it may
-suggest that participants are more likely to pay attention to and
-integrate additional sources of information when ambiguity is higher.
+The double-variance model explained almost all the variance in the
+participants' mean responses. To investigate whether the model's strong
+predictive power was due to overfitting, we fit a simplified version
+with only one degree of freedom (i.e., a single variance common to both
+sounds and objects). This single-variance model also captured the main
+qualitative patterns and remained highly predictive (\(R^2=\) 0.95).
+This result suggests that the explanatory power of the model is largely
+due to its structure, rather than its degrees of freedom.
 
@@
 
-The model made a new prediction to which we tested experimentally:
-Learning similar words is not only modulated by the similarity of their
+The model made a new prediction which we tested experimentally: Learning
+similar words is not only modulated by the similarity of their
 phonological forms, but also by the visual similarity of their semantic
@@
 
-\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code will be available online}}
+\fbox{\parbox[b][][c]{7.3cm}{\centering All data and code are available online at\ \url{https://github.com/afourtassi/kidswitch} }}
 \vspace{1em}

### 2019-08-13 journal/ms.Rmd
new stuff jounral

@@
 ---
-title             : "Continuous developmental change can explain discontinuities in word learning"
+title             : "Continuous developmental change explains discontinuities in word learning"
 shorttitle        : "Continuous Development of Word Learning"
@@
 Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development.
-However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development.
+However, later work has revealed (e.g., through using more precise testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development.
 Here we propose a probabilistic model describing how development may proceed in a continuous fashion across the lifespan.
-The model accounts for previously documented facts and provides new predictions.
-We collected data from preschool children and adults, and we showed that the model can explain various patterns of learning both within the same age and across development.
-The findings suggest that major aspects of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms."
+It characterizes developmental change as improvement in the precision of perceptual encoding.
+Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word leanring accuracy.
+The models' predictions were corroborated by human data we collected from both preschool children and adults.
+The braoder impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cogntive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms."
 
@@
 Cognitive development is sometimes characterized in terms of a succession of discontinuous stages [@piaget1954].
-Although intuitively appealing, stage theories can be challenging to integrate with theories of learning, which typically posit that knowledge and skills improve incrementally with experience.
+Although intuitively appealing, this sort of stage theories can be challenging to integrate with theories of learning, which typically posit that knowledge and skills improve incrementally with experience.
 Indeed, one of the central challenges of cognitive development has been to explain transitions between stages which appear to be qualitatively different [@carey2009].
@@
 Nevertheless, at least in some cases, development may only appear to be stage-like.
-This appearance can be due, for example, to the use of a cognitively-demanding task which may mask learning, or to the use of statistical thresholding (in particular, p-value < 0.05) which can create a spurious dichotomy between success and failure in observing a given behavior.
+Some discontinuities may be related to how we measure a specific skill --- some tasks may not allow us to detect successful learning.
+Other discontinuities may emerge due to statistical thresholding (e.g., p-value < 0.05) which can create a spurious dichotomy between success and failure in observing a given behavior.
 In such cases, positing discontinuous stages is unnecessary.
-Instead, a continuous model---involving similar representations across the lifespan---may provide a simpler and more transparent account of development.
+Instead, a continuous model --- involving similar representations across the lifespan --- may provide a simpler and more transparent account of development.
 
@@
 Though infants around 14-month old can distinguish perceptually similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects in the switch task.
-This failure has initially been taken as evidence that 14-month olds do not encode subtle sounds during meaning learning [@stager1997; @pater2004].
+This failure was initially taken as evidence that 14-month olds do not encode subtle sounds during meaning learning [@stager1997; @pater2004].
 This interpretation suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children, around 17 months, typically do [@werker2002].
@@
 They used the same familiarization procedure as @stager1997, but instead of comparing the looking times in 'same' and 'switch' trials, they tested infants using a two-alternative choice task comparing fixations to target and distractor objects [@golinkoff1987; @fernald2006].
-Using this simpler and finer-grained task, the researcher found evidence for learning even in 14-month olds.
+Using this easier and more precise task, the researcher found evidence for learning even in 14-month olds.
 
@@
 If the mismatch between sound discrimination and word learning is only a stage in early infancy, then this mismatch should disappear by adulthood.
-Nonetheless, even adults show patterns of learning that mirror those shown by 14-month-olds when the sound contrasts more challenging [@white2013; @pajak2016].
+Nonetheless, even adults show patterns of learning that mirror those shown by 14-month-olds when the sound contrasts are more challenging [@white2013; @pajak2016].
 
-Some researchers [@swingley2007; @yoshida2009; @pajak2016] proposed that the phonological form may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
-Rather, they may be encoding the phonological form of words in a probabilistic fashion.
-According to this view, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy representations.
+Some researchers [@swingley2007; @yoshida2009; @pajak2016] proposed that word knowledge may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
+Rather, they may be encoding this knowledge in a graded fashion (ses also munakata, 2001).
+According to this view, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy knowledge.
 
-In a probabilistic account, a word can be represented as a probability distribution over sound instances organized in a similarity space.
+Many different computational formalisms can represent graded knowledge.
+Here we use probabilistic models, a formalism that allows both easy examination of internal representations and quantification of the robustness of these representations.
+Word knowledge can be characterized with a probability distribution over sound instances organized in a similarity space.
 The probability is highest at the most typical sound instance.
 It decreases as the instance becomes less typical.
-The precision of the representation can be characterized by how much it tolerates slightly atypical pronunciations.
-This tolerance is captured formally by the variance of the probability distribution: larger variance indicates higher tolerance and lower precision, whereas smaller variance indicates lower tolerance and higher precision.
+The precision of word knowledge can be characterized by whether it tolerates slightly atypical pronunciations.
+This tolerance is captured formally by the variance of the probability distribution: larger variance indicates higher tolerance and lower precision, whereas smaller variance indicates lower tolerance and higher precision (for an illustration, see Figure \@ref(fig:illus) top and right panels).
 
-This framework can explain several findings.
-In Stager and Werker's original experiment, children are supposed to associate one label "bih" with object 1 and a second label "dih" with object 2.
-Though infants could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the label "bih", thanks to the relatively large variance of the early encoding, and this confusion leads to "failure" in the recognition task (Figure \@ref(fig:illus), top).
-Though learning is small and is easily disrupted by the Switch task, it can still be detected when less demanding methods are used [@yoshida2009].
+This general framework --- in which the precision of word knowledge is characterize with the variance of a probability distribution --- can already provide an intuitive way of thinking about several findings.
+In particular, unlike the binary view, the probabilistic view allows for the possibility that knowldege can be successful while still being noisy.
+This new understanding can provide an account for the fact that children show evidence of learning in some testing condition [@yoshida2009], but not in others [@stager1997].
 
-The learning accuracy increases (and is detected even by demanding tests such as the Switch) for more distinct word-forms (e.g., "lif" vs.
-"neem") where the perceptual distance is large relative to the variance (Figure \@ref(fig:illus), left).
-Distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference [@rost2009; @rost2010; @thiessen2007; @yeung09; @dautriche2015].
+In a word-pair learning paradigm, children are supposed to associate one label, e.g, "bih", with object 1 and a second label, e.g., "dih", with object 2.
+Infants may succeed in learning both associations.
+Nevertheless, the precision with which the words are encoded can still be large, causing their probability distributions to overalp (Figure \@ref(fig:illus), top).
+The way this knowledge is tested can lead to divering results.
 
-Finally, development can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic representations (Figure \@ref(fig:illus), right).
-Such an increase in precision renders minimally different sounds less confusing.
+Failure in the Switch task [@stager1997] can be exlained as follows.
+Children are understood to succeed if they reject the wrong pairing (e.g., "bih" with object 2).
+However, the overlap means that children could think of "bih" as plausible misprononciation of "dih".
+They may require a stronger sound mismatch to confidently reject the possibility that the wrong label is just an acceptable deviation from the tyical pronouciation.
+In contrast, success in the two-alternative choice task [@yoshida2009] occurs precisely becasue children do not have to reject a wrong pairing.
+Instead, the setting allows them to just choose which objects is a better match to a given label, thus revealing whether they have a prefernce, albeit samll, for the correct pairing.
+
+In addition to explaining behavior in different tasks, the probabilsitic understanding also accounts for different behaviors in the same task.
+In particular, when the labels are quite distinct in the pereptual space ("lif" vs.
+"neem"), the distributions do not overlap as much as in the case of similar-sounding words (Figure \@ref(fig:illus), left).
+This fact means that the learners will have a stronger preference fot the correct label-object pairings and less tolerance for the wrong ones.
+That said, perceptual distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference [@rost2009; @rost2010; @thiessen2007; @yeung09; @dautriche2015].
+
+Finally, development can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic representations, leading to a lower overlap between the similar-sounding words (Figure \@ref(fig:illus), right).
 Importantly, a more precise representation still has a non-zero variance --- Learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrate in adults studies [@white2013; @pajak2016].
@@
 The probabilistic account has been put forward to explain patterns of learning and development at the qualitative level.
-However, it is crucial to have a precise computational instantiation of this account which would allow us to *quantify* its explanatory power.
-We could find one previous work that attempted to provide such a computational instantiation  (Hofer and Levy, 2017).
+However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.
+One previous study attempted to provide such a computational instantiation [@hofer2017].
 However, this previous work was designed with the goal of reproducing the results of a specific study [@pajak2016] which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
@@
 We tested the ability of this model to both *explain* various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to *predict* new learning patterns that have not been tested before (i.e., the effect of the referents' similarity on word learning).
-Crucially, we explored the extent to which development can be understood as a continuous refinement in similar representations across the lifespan.
+The broader impact of this work is to explore the extent to which development can be understood as a continuous refinement in similar representations across the lifespan.
 

### 2019-08-13 journal/ms.tex
new stuff jounral

@@
 \hypersetup{unicode=true,
-            pdftitle={Continuous developmental change can explain discontinuities in word learning},
+            pdftitle={Continuous developmental change explains discontinuities in word learning},
             pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
@@
 
-  \title{Continuous developmental change can explain discontinuities in word
+  \title{Continuous developmental change explains discontinuities in word
 learning}
@@
 discontinuous/stage-like pattern of development. However, later work has
-revealed (e.g., through using simpler testing methods) that children do
-encode such contrasts, thus favoring a continuous pattern of
+revealed (e.g., through using more precise testing methods) that
+children do encode such contrasts, thus favoring a continuous pattern of
 development. Here we propose a probabilistic model describing how
-development may proceed in a continuous fashion across the lifespan. The
-model accounts for previously documented facts and provides new
-predictions. We collected data from preschool children and adults, and
-we showed that the model can explain various patterns of learning both
-within the same age and across development. The findings suggest that
-major aspects of cognitive development that are typically thought of as
+development may proceed in a continuous fashion across the lifespan. It
+characterizes developmental change as improvement in the precision of
+perceptual encoding. Our model explained previous findings in the
+literature and provided a new prediction --- the referents' visual
+similarity modulates word leanring accuracy. The models' predictions
+were corroborated by human data we collected from both preschool
+children and adults. The braoder impact of this work is to show that
+computational models, such as ours, can help us explore the extent to
+which episodes of cogntive development that are typically thought of as
 discontinuities may emerge from simpler, continuous mechanisms.''
@@
 succession of discontinuous stages (Piaget, 1954). Although intuitively
-appealing, stage theories can be challenging to integrate with theories
-of learning, which typically posit that knowledge and skills improve
-incrementally with experience. Indeed, one of the central challenges of
-cognitive development has been to explain transitions between stages
-which appear to be qualitatively different (Carey, 2009).
+appealing, this sort of stage theories can be challenging to integrate
+with theories of learning, which typically posit that knowledge and
+skills improve incrementally with experience. Indeed, one of the central
+challenges of cognitive development has been to explain transitions
+between stages which appear to be qualitatively different (Carey, 2009).
 
 Nevertheless, at least in some cases, development may only appear to be
-stage-like. This appearance can be due, for example, to the use of a
-cognitively-demanding task which may mask learning, or to the use of
-statistical thresholding (in particular, p-value \textless{} 0.05) which
-can create a spurious dichotomy between success and failure in observing
-a given behavior. In such cases, positing discontinuous stages is
-unnecessary. Instead, a continuous model---involving similar
-representations across the lifespan---may provide a simpler and more
-transparent account of development.
+stage-like. Some discontinuities may be related to how we measure a
+specific skill --- some tasks may not allow us to detect successful
+learning. Other discontinuities may emerge due to statistical
+thresholding (e.g., p-value \textless{} 0.05) which can create a
+spurious dichotomy between success and failure in observing a given
+behavior. In such cases, positing discontinuous stages is unnecessary.
+Instead, a continuous model --- involving similar representations across
+the lifespan --- may provide a simpler and more transparent account of
+development.
 
@@
 in mapping this pair to two different objects in the switch task. This
-failure has initially been taken as evidence that 14-month olds do not
-encode subtle sounds during meaning learning (Pater, Stager, \& Werker,
-2004; Stager \& Werker, 1997). This interpretation suggested a
+failure was initially taken as evidence that 14-month olds do not encode
+subtle sounds during meaning learning (Pater, Stager, \& Werker, 2004;
+Stager \& Werker, 1997). This interpretation suggested a
 discontinuous/stage-like pattern of development whereby younger children
@@
 \& Marchman, 2006; Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987).
-Using this simpler and finer-grained task, the researcher found evidence
+Using this easier and more precise task, the researcher found evidence
 for learning even in 14-month olds.
@@
 learning that mirror those shown by 14-month-olds when the sound
-contrasts more challenging (Pajak, Creel, \& Levy, 2016; White, Yee,
+contrasts are more challenging (Pajak, Creel, \& Levy, 2016; White, Yee,
 Blumstein, \& Morgan, 2013).
@@
 Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al.,
-2009) proposed that the phonological form may not be encoded in a binary
+2009) proposed that word knowledge may not be encoded in a binary
 fashion, i.e., it is not the case that children either succeed or fail
 in encoding minimal contrast when learning the meanings. Rather, they
-may be encoding the phonological form of words in a probabilistic
-fashion. According to this view, development does not so much involve a
+may be encoding this knowledge in a graded fashion (ses also munakata,
+2001). According to this view, development does not so much involve a
 qualitative shift (i.e., a sudden emergence of an ability that did not
 exist before) as much as it consists in the continuous refinement of
-initially noisy representations.
-
-In a probabilistic account, a word can be represented as a probability
-distribution over sound instances organized in a similarity space. The
-probability is highest at the most typical sound instance. It decreases
-as the instance becomes less typical. The precision of the
-representation can be characterized by how much it tolerates slightly
-atypical pronunciations. This tolerance is captured formally by the
-variance of the probability distribution: larger variance indicates
+initially noisy knowledge.
+
+Many different computational formalisms can represent graded knowledge.
+Here we use probabilistic models, a formalism that allows both easy
+examination of internal representations and quantification of the
+robustness of these representations. Word knowledge can be characterized
+with a probability distribution over sound instances organized in a
+similarity space. The probability is highest at the most typical sound
+instance. It decreases as the instance becomes less typical. The
+precision of word knowledge can be characterized by whether it tolerates
+slightly atypical pronunciations. This tolerance is captured formally by
+the variance of the probability distribution: larger variance indicates
 higher tolerance and lower precision, whereas smaller variance indicates
-lower tolerance and higher precision.
-
-This framework can explain several findings. In Stager and Werker's
-original experiment, children are supposed to associate one label
-\enquote{bih} with object 1 and a second label \enquote{dih} with object
-2. Though infants could learn that the label \enquote{bih} is a better
-match to object 1 than \enquote{dih}, they could still judge the sound
-\enquote{dih} as a plausible instance of the label \enquote{bih}, thanks
-to the relatively large variance of the early encoding, and this
-confusion leads to \enquote{failure} in the recognition task (Figure
-\ref{fig:illus}, top). Though learning is small and is easily disrupted
-by the Switch task, it can still be detected when less demanding methods
-are used (Yoshida et al., 2009).
-
-The learning accuracy increases (and is detected even by demanding tests
-such as the Switch) for more distinct word-forms (e.g., \enquote{lif}
-vs. \enquote{neem}) where the perceptual distance is large relative to
-the variance (Figure \ref{fig:illus}, left). Distinctiveness can be
-enhanced even for minimally different sounds when other cues highlight
-their difference (Dautriche, Swingley, \& Christophe, 2015; Rost \&
-McMurray, 2009, 2010; Thiessen, 2007; Yeung \& Werker, 2009).
+lower tolerance and higher precision (for an illustration, see Figure
+\ref{fig:illus} top and right panels).
+
+This general framework --- in which the precision of word knowledge is
+characterize with the variance of a probability distribution --- can
+already provide an intuitive way of thinking about several findings. In
+particular, unlike the binary view, the probabilistic view allows for
+the possibility that knowldege can be successful while still being
+noisy. This new understanding can provide an account for the fact that
+children show evidence of learning in some testing condition (Yoshida et
+al., 2009), but not in others (Stager \& Werker, 1997).
+
+In a word-pair learning paradigm, children are supposed to associate one
+label, e.g, \enquote{bih}, with object 1 and a second label, e.g.,
+\enquote{dih}, with object 2. Infants may succeed in learning both
+associations. Nevertheless, the precision with which the words are
+encoded can still be large, causing their probability distributions to
+overalp (Figure \ref{fig:illus}, top). The way this knowledge is tested
+can lead to divering results.
+
+Failure in the Switch task (Stager \& Werker, 1997) can be exlained as
+follows. Children are understood to succeed if they reject the wrong
+pairing (e.g., \enquote{bih} with object 2). However, the overlap means
+that children could think of \enquote{bih} as plausible misprononciation
+of \enquote{dih}. They may require a stronger sound mismatch to
+confidently reject the possibility that the wrong label is just an
+acceptable deviation from the tyical pronouciation. In contrast, success
+in the two-alternative choice task (Yoshida et al., 2009) occurs
+precisely becasue children do not have to reject a wrong pairing.
+Instead, the setting allows them to just choose which objects is a
+better match to a given label, thus revealing whether they have a
+prefernce, albeit samll, for the correct pairing.
+
+In addition to explaining behavior in different tasks, the probabilsitic
+understanding also accounts for different behaviors in the same task. In
+particular, when the labels are quite distinct in the pereptual space
+(\enquote{lif} vs. \enquote{neem}), the distributions do not overlap as
+much as in the case of similar-sounding words (Figure \ref{fig:illus},
+left). This fact means that the learners will have a stronger preference
+fot the correct label-object pairings and less tolerance for the wrong
+ones. That said, perceptual distinctiveness can be enhanced even for
+minimally different sounds when other cues highlight their difference
+(Dautriche, Swingley, \& Christophe, 2015; Rost \& McMurray, 2009, 2010;
+Thiessen, 2007; Yeung \& Werker, 2009).
 
 Finally, development can be understood as an increase in the precision
-(i.e., a decrease in the variance) of the probabilistic representations
-(Figure \ref{fig:illus}, right). Such an increase in precision renders
-minimally different sounds less confusing. Importantly, a more precise
-representation still has a non-zero variance --- Learning difficulties
-can still be induced with challenging stimuli or in cognitively
-demanding situations as was demonstrate in adults studies (Pajak et al.,
-2016; White et al., 2013).
+(i.e., a decrease in the variance) of the probabilistic representations,
+leading to a lower overlap between the similar-sounding words (Figure
+\ref{fig:illus}, right). Importantly, a more precise representation
+still has a non-zero variance --- Learning difficulties can still be
+induced with challenging stimuli or in cognitively demanding situations
+as was demonstrate in adults studies (Pajak et al., 2016; White et al.,
+2013).
 
@@
 crucial to have a precise computational instantiation of this account
-which would allow us to \emph{quantify} its explanatory power. We could
-find one previous work that attempted to provide such a computational
-instantiation (Hofer and Levy, 2017). However, this previous work was
-designed with the goal of reproducing the results of a specific study
-(Pajak et al., 2016) which focused on explaining the mismatch between
-speech perception and word learning in adults rather than on exploring
-the mechanism of development.
+which would help us 1) test this theoretical hypothesis more directly
+and 2) identify the particular parameters that are the locus of
+developmental change. One previous study attempted to provide such a
+computational instantiation (Hofer \& Levy, 2017). However, this
+previous work was designed with the goal of reproducing the results of a
+specific study (Pajak et al., 2016) which focused on explaining the
+mismatch between speech perception and word learning in adults rather
+than on exploring the mechanism of development.
 
@@
 not been tested before (i.e., the effect of the referents' similarity on
-word learning). Crucially, we explored the extent to which development
-can be understood as a continuous refinement in similar representations
-across the lifespan.
+word learning). The broader impact of this work is to explore the extent
+to which development can be understood as a continuous refinement in
+similar representations across the lifespan.
 

### 2019-08-27 Analysis/process.Rmd
first version journal

@@
          group = "children") %>%
-  bind_rows(as.data.frame(confint2(fit_adults)) %>%
+  bind_rows(as.data.frame(confint2(fit_adults_no)) %>%
               mutate(val= Vr_ad_no, 

### 2019-08-27 journal/ms.Rmd
first version journal

@@
 
- "Cognitive development is often characterized in term of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
+ "Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
 To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
@@
 However, later work has revealed (e.g., through using more precise testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development.
-Here we propose a probabilistic model describing how development may proceed in a continuous fashion across the lifespan.
-It characterizes developmental change as improvement in the precision of perceptual encoding.
-Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word leanring accuracy.
+Here we propose a probabilistic model that represents word knowledge in a graded fashion and characterizes developmental change as improvement in the precision of this graded knowledge.
+Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word learning accuracy.
 The models' predictions were corroborated by human data we collected from both preschool children and adults.
-The braoder impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cogntive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms."
+The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms."
 
@@
 Nevertheless, at least in some cases, development may only appear to be stage-like.
-Some discontinuities may be related to how we measure a specific skill --- some tasks may not allow us to detect successful learning.
+Some discontinuities may be related to how we measure a specific skill.
 Other discontinuities may emerge due to statistical thresholding (e.g., p-value < 0.05) which can create a spurious dichotomy between success and failure in observing a given behavior.
 In such cases, positing discontinuous stages is unnecessary.
-Instead, a continuous model --- involving similar representations across the lifespan --- may provide a simpler and more transparent account of development.
+Instead, a continuous model --- involving similar representations across the lifespan --- may provide a simpler and more transparent account of development (see also @McMurray2007 and @shultz1995).
 
@@
 The authors measured word learning using an audio-visual habituation Switch task.
-First, infants are familiarized with two word-object pairings (e.g., lable A with object A and label B with object B).
+First, infants are familiarized with two word-object pairings (e.g., label 1 with object 1 and label 2 with object 2).
 Second, they are tested using two types of trials.
-The control 'same' trial consists of a correct pairing  (e.g., label A with object A) and the 'switch' trial consists of a wrong pairing (e.g., label A with object B).
+The control 'same' trial consists of a correct pairing  (e.g., label 1 with object 1) and the 'switch' trial consists of a wrong pairing (e.g., label 1 with object 2).
 If babies have correctly learned the association during the familiarization, they are supposed to be surprised by the 'switch' trial and not by the 'same' trial.
@@
 The initial discontinuous interpretation has been challenged by subsequent work.
-For instance, @yoshida2009 investigated whether failure in the switch task reflects a lack of sound encoding during *familiarization*, or whether it is only due to the demands of the *testing* method which does not allow learning below a certain threshold to be detected.
+For instance, @yoshida2009 investigated whether failure in the Switch task reflects a lack of sound encoding during *familiarization*, or whether it is only due to the nature of the *testing* method which does not allow learning below a certain threshold to be detected.
 They used the same familiarization procedure as @stager1997, but instead of comparing the looking times in 'same' and 'switch' trials, they tested infants using a two-alternative choice task comparing fixations to target and distractor objects [@golinkoff1987; @fernald2006].
-Using this easier and more precise task, the researcher found evidence for learning even in 14-month olds.
+Using this testing method, the researcher found evidence for learning even in 14-month olds.
 
@@
 Some researchers [@swingley2007; @yoshida2009; @pajak2016] proposed that word knowledge may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
-Rather, they may be encoding this knowledge in a graded fashion (ses also munakata, 2001).
+Rather, they may be encoding this knowledge in a graded fashion (see also @Munakata2001).
 According to this view, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy knowledge.
@@
 
-This general framework --- in which the precision of word knowledge is characterize with the variance of a probability distribution --- can already provide an intuitive way of thinking about several findings.
-In particular, unlike the binary view, the probabilistic view allows for the possibility that knowldege can be successful while still being noisy.
-This new understanding can provide an account for the fact that children show evidence of learning in some testing condition [@yoshida2009], but not in others [@stager1997].
+This general framework --- in which the precision of word knowledge is characterized with the variance of a probability distribution --- can already provide an intuitive way of thinking about several findings.
+In particular, unlike the binary view, the probabilistic view allows for the possibility of word knowledge being both successful and noisy.
+This new understanding can provide an account for the fact that children show evidence of learning in some testing condition [e.g., @yoshida2009] but not in others [e.g., @stager1997] --- depending on the precision of the measurement.
 
-In a word-pair learning paradigm, children are supposed to associate one label, e.g, "bih", with object 1 and a second label, e.g., "dih", with object 2.
+In a word-pair learning paradigm, children are supposed to associate one label, e.g., "bih", with object 1 and a second label, e.g., "dih", with object 2.
 Infants may succeed in learning both associations.
-Nevertheless, the precision with which the words are encoded can still be large, causing their probability distributions to overalp (Figure \@ref(fig:illus), top).
-The way this knowledge is tested can lead to divering results.
+Nevertheless, the variance with which the pair of words are encoded can still be large, causing their probability distributions to overlap (Figure \@ref(fig:illus), top).
+The way this (noisy) knowledge is probed can lead to different results.
 
-Failure in the Switch task [@stager1997] can be exlained as follows.
-Children are understood to succeed if they reject the wrong pairing (e.g., "bih" with object 2).
-However, the overlap means that children could think of "bih" as plausible misprononciation of "dih".
-They may require a stronger sound mismatch to confidently reject the possibility that the wrong label is just an acceptable deviation from the tyical pronouciation.
-In contrast, success in the two-alternative choice task [@yoshida2009] occurs precisely becasue children do not have to reject a wrong pairing.
-Instead, the setting allows them to just choose which objects is a better match to a given label, thus revealing whether they have a prefernce, albeit samll, for the correct pairing.
+In the Switch task [@stager1997], children are understood to succeed if they reject a wrong association (e.g., "bih" with object 2).
+However, a large overlap between "bin" and "din" means that "bih" is itself a plausible mispronunciation of "dih".
+The wrong association may not be rejected by children because the speaker could have said "bih" but meant "dih".
+In the two-alternative choice task [@yoshida2009], children do not have to reject the wrong association; they only need to show a preference for the correct one.
+Given a label, e.g., "bih", they pick which object is a better match to this label.
+Though it is possible that the speaker said "bih" and meant "dih", it is *more* likely that the speaker both said and meant "bih" --- this higher probability leads to a preference for the correct object.
 
-In addition to explaining behavior in different tasks, the probabilsitic understanding also accounts for different behaviors in the same task.
-In particular, when the labels are quite distinct in the pereptual space ("lif" vs.
-"neem"), the distributions do not overlap as much as in the case of similar-sounding words (Figure \@ref(fig:illus), left).
-This fact means that the learners will have a stronger preference fot the correct label-object pairings and less tolerance for the wrong ones.
-That said, perceptual distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference [@rost2009; @rost2010; @thiessen2007; @yeung09; @dautriche2015].
+In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains difference in behavior within the same task.
+In particular, when the labels are quite distinct in the perceptual space ("lif" vs.
+"neem"), the probabilistic distributions do not overlap as much as in the case of similar-sounding words (Figure \@ref(fig:illus), left).
+This fact means that the learners will have less tolerance for the wrong association, leading to a successful rejection in the Switch task (as was reported by @stager1997 and subsequent studies using the same paradigm).
+Further, distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference [@rost2009; @rost2010; @thiessen2007; @yeung09; @dautriche2015].
 
-Finally, development can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic representations, leading to a lower overlap between the similar-sounding words (Figure \@ref(fig:illus), right).
-Importantly, a more precise representation still has a non-zero variance --- Learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrate in adults studies [@white2013; @pajak2016].
+Finally, development can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic knowledge, leading to a lower overlap between the distributions of similar-sounding words (Figure \@ref(fig:illus), right).
+Importantly, a more precise representation still has a non-zero variance --- Learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adults studies [@white2013; @pajak2016].
 
@@
 We tested the ability of this model to both *explain* various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to *predict* new learning patterns that have not been tested before (i.e., the effect of the referents' similarity on word learning).
-The broader impact of this work is to explore the extent to which development can be understood as a continuous refinement in similar representations across the lifespan.
+We explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.
 
 The paper is organized as follows.
-First, we introduce the model and we explain how it allows us to characterize behavior in a word learning task which resembles the one used in @stager1997 and @yoshida2009.
+First, we introduce the model and we explain how it allows us to characterize behavior in a word-pair-learning paradigm.
 Then we explore the predictions of the model through simulating its behavior across different parameter settings.
-Next we quantify the extent to which the model's predictions account for human data we collected from both preschool children and adults.
+Next, we quantify the extent to which the model's predictions account for human data we collected from both preschool children and adults.
 Finally, we discuss the results in the lights of existing accounts of word development.
@@
 When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
-The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).", fig.align = "center", out.width = "300px"}
+The accuracy is higher when the stimuli are less similar (left panel), or when the representation are more precise (right panel).", fig.align = "center", out.width = "300px"}
 knitr::include_graphics("figs/illustration.png")
@@
 Circles indicate random variables (shading indicates observed variables).
-The squares indicate fixed model parameters.", fig.align = "center", out.width = "300px"}
+The squares indicate fixed model parameters.", fig.align = "center", out.width = "150px"}
 knitr::include_graphics("figs/model.png")
@@
 
-$$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
+\begin{equation} \label{eq:object}
+ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) 
+\end{equation}
 
-$$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
+\begin{center}
+and 
+\end{center}
+
+\begin{equation} \label{eq:sound}
+p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L)
+\end{equation}
 
 Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
-$$
+\begin{equation}
 P(L_i|C_j) = 
@@
 \end{cases}
-$$
+\end{equation}
 
@@
 
-The learner hears a sound $s$ and has to decide which object $o$ provides an optimal match to this sound (see Figure \@ref(fig:task)).
+In our canonical inference case, the learner hears a sound $s$ and has to decide which object $o$ provides an optimal match to this sound (see Figure \@ref(fig:task)).
 To this end, they must compute the probability $P(o|s)$ for all possible objects.
 This probability can be computed by summing over all possible concepts and labels:
-$$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
 
-The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in Figure \@ref(fig:model):
-$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
+\begin{equation}
+P(o|s)=\sum_{C,L} P(o, C, L| s)  
+\end{equation}
 
-which can be transformed using Bayes rule into:
+Using the fact that $P(o,C,L|s) = \frac{P(o,C,L,s)}{P(s)}$ and that $P(s)$ does not depend on $o$, we arrive at the equation:
 
-$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
+\begin{equation}
+P(o|s) \propto \sum_{C,L} P(o, C, L, s) 
+\end{equation}
 
-Finally, assuming that the concepts' prior probability is uniformly distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.}, we obtain the following expression, where all conditional dependencies are now well defined:
+The joint probability $P(o,C,L,s)$ is obtained by factoring the graphical model in Figure \@ref(fig:model):
 
-$$
-P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-$$
+$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o)$$
+
+Using Bayes' rule, we can rewrite $P(C|o)$ in terms of $P(o|C)$:
+
+$$P(C|o) = \frac{P(o|C)P(C)}{P(o)}$$
+
+By subtituting this term in the expression of the joint distribution $P(o,C,L,S)$ we obtain:
+
+$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C)$$
+
+Finally, assuming that the concepts' prior probability $P(C)$ is uniformly distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in our experiment.} we obtain the following expression, where all conditional dependencies are now well defined:
+
+\begin{equation} \label{eq:general}
+P(o|s) \propto \sum_{C,L}  P(s|L)P(L|C)P(o|C)
+\end{equation}
 
@@
 We use the model to predict word learning in a task similar to the one introduced by @stager1997.
-We used a modified version of the task where the testing method consists in a two-alternative forced choice [@yoshida2009].
-In this task, participants are first exposed to the association between pairs of nonsense words (e.g., "lif"/"neem") and pairs of objects.
+We used a modified version of the task where the testing method consists in a two-alternative forced-choice [@yoshida2009].
+In this task, participants are first exposed to two different word-object pairings (e.g., "lif" - object 1, "neem" - object 2).
 The word-object associations are introduced sequentially.
@@
 
-From the general expression (1), we derive three exact analytical solutions instantiating different learning assumptions.
-The first solution is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty $\sigma_L$, but that concepts are unambiguously recovered from the observed objects, i.e., $\sigma_C \rightarrow 0$.
+### Model 1
+From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions.
+Recall from expressions \ref{eq:object} and \ref{eq:sound} that $P(o|C)$ and $P(s|L)$ have parameters $\sigma_C$ and $\sigma_L$, respectively, that control perceptual uncertainty.
+The first solution is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty $\sigma_L > 0$, but that concepts are unambiguously recovered from the observed objects, i.e., $\sigma_C \rightarrow 0$.
 This assumption has been made --- whether implicitly or explicitly --- by most previous work in this line of research.
+For example, in @stager1997, the objects were quite dissimilar.
+Thus, the assumption that they were easily discriminated by infants seems relatively well justified.
 One important implication of this assumption is that only the similarity of word sounds modulates success in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually).
@@
 
-\begin{equation}
+\begin{equation} \label{eq:model1}
 P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
@@
 
-The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with ambiguity from the sounds and objects.
+### Model 2
+The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with noise from the sounds and objects.
 We first introduce the simplifying assumption that the label-related uncertainty $\sigma_L$ and the concept-related uncertainty $\sigma_C$ are of a similar magnitude, i.e., $\sigma_C \approx \sigma_L = \sigma$.
 This assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way.
-Furthermore, it allows us to study the behavior of the model with minimal free parameters.
+Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given infant experiment.
 
-\begin{equation}
+\begin{equation} \label{eq:model2}
 P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
@@
 
+### Model 3
 We finally derive the third (and most general) solution which allows label- and concept-related uncertainties to vary independently.
 
-\begin{equation}
+\begin{equation} \label{eq:model3}
 P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
@@
 
-In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show some simulations of the accuracy $P(o_T|s)$ as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the uncertainty parameters $\sigma_L$ and $\sigma_C$.
+In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show simulations of the accuracy $P(o_T|s)$ as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the uncertainty parameters $\sigma_L$ and $\sigma_C$.
 
@@
 
-```{r simulation, fig.cap = "The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ and $\\Delta o$ and representation precision $\\sigma$ (For clarity, we assume here that $\\sigma$=$\\sigma_C$=$\\sigma_L$).
+```{r simulation, fig.cap = "The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\\Delta s$ and $\\Delta o$ and representation precision $\\sigma$ (For simplicity, we use model 2, which assumes that $\\sigma$=$\\sigma_C$=$\\sigma_L$).
 Dashed line represents chance."}
@@
 2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational uncertainty $\sigma$ decreases.
-This fact may explain development, i.e., younger children have noisier representations [see @swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar-sounding words.
+This observation provides a simple model for developmental change.
+Younger children have noisier representations [see @swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar-sounding words.
 
@@
 We report data from $N=$ `r N_good_ch` children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
-An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
+An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
 We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk.
-An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.
+An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses (again, using preregistered exclusion criteria) because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.
 
@@
 
-As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree," "bird," "bug," and "fish." These categories are supposed to be naturally occurring kinds that might be seen on an alien planet.
-In each category, we generated *different*, *intermediate* and *similar* pairs by manipulating a continuous property controlling features of the category's shape (e.g, body stretch or head fatness).
+As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree," "bird," "bug," and "fish." These categories were described to participants as naturally occurring kinds on an alien planet.
+In each category, we generated *different*, *intermediate*, and *similar* pairs by manipulating a continuous property controlling features of the category's shape (e.g., body stretch or head fatness).
 
@@
 Data are shown in Figure \@ref(fig:stim) where we scaled responses within the range [0,1] for each stimulus group.
-These data will be used in all models as a proxy for the perceptual distance between the sound pairs ($\Delta s$) and the object pairs ($\Delta o$).
+We used these data in all models as an empirical measurement of the  perceptual distance between the sound pairs and the object pairs.
+The use of empirical measurement allows us to eliminate $\Delta s$ and $\Delta s$ as free parameters (see @frank2012 and @xu2007 for a similar strategy).
 
@@
       ) +
-  ylim(c(0,1.1)) +
-  xlab("Stimuli group")+ ylab("Perceptual distance (experimental)")
+  ylim(c(-0.1,1.2))+
+  scale_y_continuous(breaks = c(0,0.25,0.5, 0.75,1))+
+  #ylim(c(0,1.2)) +
+  xlab("Stimulus group")+ ylab("Perceptual distance (empirical)")
 
@@
 We made this choice in light of pilot studies showing that adults were at ceiling with *different* sounds/objects, and children were at chance with the *similar* sounds/objects.
-That said, this difference in the level of similarity is accounted for in the model through using the appropriate distance (Figure \@ref(fig:stim)).
+That said, this difference in the level of similarity is accounted for in the model: We used empirical distance measurement to fill in the appropriate values of $\Delta s$ and $\Delta o$ for each age group.
 
-```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "Distances for both sound and object pairs from an adult norming study.
+```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=4, fig.height=3, fig.cap = "Distances for both sound and object pairs from an adult norming study.
 Data represent Likert values normalized to [0,1] interval.
@@
 To maximize our ability to measure subtle stimulus effects, the experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
-Besides the four conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones but was used only to select participants who were able to follow the instructions and show minimal learning.
+Besides the four conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones but was trivially easy and used only to select participants who were able to follow the instructions and show minimal learning.
 
@@
 Preschoolers were tested at the nursery school using a tablet, whereas adults used their own computers to complete the same experiment online.
-Participants were tested in a sequence of five conditions: the four experimental conditions plus the catch condition.
+Participants were tested in a random sequence of five conditions: the four experimental conditions plus the catch condition.
 In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.
@@
 We also randomized the on-screen position (left vs.
-right) of the two pictures on each testing trial.
+right) of the two pictures on each testing trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}
+
+```{r allData, fig.env = "figure", fig.pos = "h", fig.align='center', fig.cap = "Accuracy of word recognition as a function of the sound distance, the object distance, and the age group (preschool children vs.
+adults).
+We show both the models' predictions (dashed lines) and the experimental results (solid lines, same across the three panels).
+Error bars represent 95\\% confidence intervals."}
+
+plot_data
+```
 
@@
 
-```{r allData, fig.env = "figure", fig.pos = "h", fig.align='center', fig.cap = "Accuracy of word recognition as a function of the sound distance, the object distance, and the age group (preschool children vs.
-adults).
-We show both the models' predictions (dashed lines) and the experimental results (solid lines).
-The single-variance model uses one joint fitting parameter for both sound and meaning variances.
-The double-variance model uses two separate fittings parameters for the sound and the meaning variances.
-Error bars represent 95\\% confidence intervals."}
-
-plot_data
-```
-
 Experimental results are shown in Figure \@ref(fig:allData) (solid lines).
@@
 For the sound distance, we obtained $\beta =$ `r s_coef` ($p$ `r p_val(s_p)`), replicating previous findings that sound distance modulates success in word learning [e.g., @stager1997].
-For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model according to which object distance also modulates success in word learning.
+
+For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model, according to which, object distance also modulates success in word learning.
+Note, in particular, that increasing the visual similarity of the objects makes children succeed in learning the similar-sounding words.
 Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that overall performance improves with age.
+The full output of the regression model is shown in the Appendix.
 
@@
 
+##Children
+mod1_ch_val = toString(round(mod0_val$val[which(mod0_val$group=="children")],2))
+mod1_ch_conf1 = toString(round(mod0_val$lower[which(mod0_val$group=="children")],2))
+mod1_ch_conf2 = toString(round(mod0_val$upper[which(mod0_val$group=="children")],2))
+
+mod1_ch = paste(mod1_ch_val, paste('[',mod1_ch_conf1,',', mod1_ch_conf2, ']', sep =''))
+
+mod2_ch_val = toString(round(mod1_val$val[which(mod1_val$group=="children")],2))
+mod2_ch_conf1 = toString(round(mod1_val$lower[which(mod1_val$group=="children")],2))
+mod2_ch_conf2 = toString(round(mod1_val$upper[which(mod1_val$group=="children")],2))
+
+mod2_ch = paste(mod2_ch_val, paste('[',mod2_ch_conf1,',', mod2_ch_conf2, ']', sep =''))
+
+mod3_ch_s_val = toString(round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2))
+mod3_ch_s_conf1 = toString(round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2))
+mod3_ch_s_conf2 = toString(round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2))
+
+mod3_ch_s = paste(mod3_ch_s_val, paste('[',mod3_ch_s_conf1,',', mod3_ch_s_conf2, ']', sep =''))
+
+mod3_ch_o_val = toString(round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2))
+mod3_ch_o_conf1 = toString(round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2))
+mod3_ch_o_conf2 = toString(round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2))
+
+mod3_ch_o = paste(mod3_ch_o_val, paste('[', mod3_ch_o_conf1,',', mod3_ch_o_conf2, ']', sep =''))
+
+##Adults
+
+mod1_ad_val = toString(round(mod0_val$val[which(mod0_val$group=="adults")],2))
+mod1_ad_conf1 = toString(round(mod0_val$lower[which(mod0_val$group=="adults")],2))
+mod1_ad_conf2 = toString(round(mod0_val$upper[which(mod0_val$group=="adults")],2))
+
+mod1_ad = paste(mod1_ad_val, paste('[',mod1_ad_conf1,',', mod1_ad_conf2, ']', sep =''))
+
+mod2_ad_val = toString(round(mod1_val$val[which(mod1_val$group=="adults")],2))
+mod2_ad_conf1 = toString(round(mod1_val$lower[which(mod1_val$group=="adults")],2))
+mod2_ad_conf2 = toString(round(mod1_val$upper[which(mod1_val$group=="adults")],2))
+
+mod2_ad = paste(mod2_ad_val, paste('[',mod2_ad_conf1,',', mod2_ad_conf2, ']', sep =''))
+
+mod3_ad_s_val = toString(round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2))
+mod3_ad_s_conf1 = toString(round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2))
+mod3_ad_s_conf2 = toString(round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2))
+
+mod3_ad_s = paste(mod3_ad_s_val, paste('[',mod3_ad_s_conf1,',', mod3_ad_s_conf2, ']', sep =''))
+
+mod3_ad_o_val = toString(round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2))
+mod3_ad_o_conf1 = toString(round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2))
+mod3_ad_o_conf2 = toString(round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2))
+
+mod3_ad_o = paste(mod3_ad_o_val, paste('[', mod3_ad_o_conf1,',', mod3_ad_o_conf2, ']', sep =''))
+
 mods <- data.frame(models = c('model 1', 'model 2', 'model 3'),
-                   struc = c("Sig\\textsubscript{L} only",
-                             "Sig\\textsubscript{L} = Sig\\textsubscript{C}",
-                             "Sig\\textsubscript{L} != Sig\\textsubscript{C}"),
+                   struc = c("$\\sigma$\\textsubscript{L} only",
+                             "$\\sigma$\\textsubscript{L} = $\\sigma$\\textsubscript{C}",
+                             "$\\sigma$\\textsubscript{L} $\\neq$ $\\sigma$\\textsubscript{C}"),
                    param = c(1,1,2),
                    R = c(R2_model1, R2_model2, R2_model3),
-                   sigS_C = c(round(mod0_val$val[which(mod0_val$group=="children")],2),
-                              round(mod1_val$val[which(mod1_val$group=="children")],2),
-                              round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)
+                   sigS_C = c(mod1_ch_val,
+                              mod2_ch_val,
+                              mod3_ch_s_val
                               ),
                    sigO_C = c('--',
-                              round(mod1_val$val[which(mod1_val$group=="children")],2),
-                              round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)
+                              mod2_ch_val,
+                              mod3_ch_o_val
                               ),
-                   sigS_A = c(round(mod0_val$val[which(mod0_val$group=="adults")],2),
-                              round(mod1_val$val[which(mod1_val$group=="adults")],2),
-                              round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)
+                   sigS_A = c(mod1_ad_val,
+                              mod2_ad_val,
+                              mod3_ad_s_val
                               ),
                    sigO_A = c('--',
-                              round(mod1_val$val[which(mod1_val$group=="adults")],2),
-                              round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)
+                              mod2_ad_val,
+                              mod3_ad_o_val
+
                    ))
@@
       caption = "Characteristics and performance of the models used in this study.",
-      col.names = c("Model",  "Structure", "Param.", "R\\textsuperscript{2}", "Sig\\textsubscript{L}", "Sig\\textsubscript{C}", "Sig\\textsubscript{L}", "Sig\\textsubscript{C}")) %>%
+      col.names = c("Model",  "Structure", "Param.", "R\\textsuperscript{2}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}")) %>%
   add_header_above(c("", "","","","Children" = 2, "Adults" = 2)) %>%
@@
 
-We next fit the three models obtained through expressions (1), (2), and (3) to the participants' responses in each age group.
-The predictions of the models are shown \@ref(fig:allData) (dashed lines) and the parameter estimates (for $\sigma_L$ and $\sigma_C$) as well as models' goodness to fit (i.e., measured through $R^2$) are presented in Table \@ref(tab:models).
+We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the participants' responses in each age group.
+The predictions of the models are shown \@ref(fig:allData).
+The parameter estimates (for $\sigma_L$ and $\sigma_C$) as well as models' goodness to fit (i.e., measured through $R^2$) are presented in Table \@ref(tab:models).
 
@@
 In contrast, Model 3, which does take into account this ambiguity, accounts for all the variance.
-Interestingly, Model 2 which has a single, shared uncertainty parameter for both auditory and visual modalities still explains almost all the variance in human data, suggesting that the explanatory power of the general Model 3 is largely due to its structure, rather than its degrees of freedom.
+Interestingly, Model 2 which has a single, shared uncertainty parameter for both auditory and visual modalities still explains almost all the variance in human data.
 
-As predicted, the uncertainty parameters were larger for children than they were for adults (Table \@ref(tab:models)), showing that the probabilistic representations become more refined (that is, $\sigma$ becomes smaller) across development.
-Further, the parameter estimates of Model 3 show that this developmental effect is more important for the label-specific uncertainty that it is for the concept-specific uncertainty.
+As predicted, the uncertainty parameters were larger for children than they were for adults (Table \@ref(tab:models)), showing that word knowledge gets more precise with development.
+Further, the parameter estimates of Model 3 show that this developmental effect is larger for labels ($\sigma_L$ varies between `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` in children and `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` in adults) than it is for concepts ($\sigma_C$ varies between `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` in children and `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` in adults).
 
@@
 We used as a case study the seminal work of @stager1997 showing a discrepancy between children's speech perception abilities and their word learning skills.
-While this fact might seem like a specific stage in early development, our model demonstrated, instead, that it can be more simply understood in terms of continuous developmental change.
-
-The main assumption of the model was that both word form and referent are encoded in a probabilistic fashion.
-The model provided a quantitative instantiation of the continuous development hypothesis [@swingley2007; @yoshida2009; @pajak2016].
-More precisely, we showed that developmental changes in word-object mappings can be characterized as a continuous refinement in the precision of the probabilistic representations.
+The development of this discrepancy could be understood in terms of a discrete change in word representation.
+But our model demonstrates that it can also be parsimoniously described as a result of continuous developmental change in the precision of children's graded word knowledge.
+Our model instantiates the continuous development hypothesis [@swingley2007; @yoshida2009; @pajak2016].
 
 We find in the literature two broad accounts of development in the Switch task: One that suggests *direct* development of the sound representation and one that hypothesizes *indirect* development of this representation through improvement in general cognitive resources.
-On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories, i.e., contrasting word meaning [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011].
+On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011].
 On the second account, the precision of sound encoding in the switch task improves as a result of the maturation of more general resources like the attentional and working memory capacity [@stager1997; @werker2004; @hofer2017].
 Such improvement allows older children and adults to better encode the sound details while simultaneously matching these sounds to visual objects.
-These two accounts are complementary and both seem to play a role [see @tsui2019 for a review].
+Indeed, one recent meta-analysis of the switch task concluded that both changing representation precision and better memory/attention play a role in developmental changes [@tsui2019].
 
@@
 
-@werker2005 proposed to explain development in the Switch task using their theory called Processing Rich Information from Multidimensional Interactive Representations (or PRIMIR) which purports to explain various phenomena in early speech perception and word learning within a unified framework.
+@werker2005 proposed to explain development in the Switch task using their theory called Processing Rich Information from Multidimensional Interactive Representations (or PRIMIR) which attempts to explain various phenomena in early speech perception and word learning within a unified framework.
 PRIMIR posits that children initially try to attend to various features of the speech signal, regardless of whether or not these features are relevant to the task at hand.
 For example, when learning the meaning of similar sounds, infants are unsure what detail is most important to identify words (i.e., the phonemes), and will instead activate several aspects of the information simultaneously (including, for example, the gender of the speaker).
-The lack of attentional selection leads to confusion and then to failure in the task.
+The lack of selective attention leads to confusion and then to failure in the task.
 
@@
 The latter act as filters, allowing children to attend selectively to the important information.
-This account is also compatible with our model (as it resembles the direct account we discussed above).
-Developing a better attentional strategy (thanks to phoneme) can translate into a reduction in the uncertainty about whether a sound contrast signals a change in meaning.
+This account is also compatible with our model: Developing phonemic categories allows learners to better determine when a sound contrast signals a change in meaning (i.e., when this contrast straddles two categories as in "bin" vs.
+"din") and when a sound contrast does not change word meaning (i.e.,  when it instantiates a variation within the same category).
+In fact, learning to distinguish contrastive vs.
+non-contrastive pairs amounts to reducing the overlap between the probability distribution of two neighboring words.
 
@@
 
-While most research focused on the sound representation in analyzing the Switch task, this work showed that the visual representation of the referent is equally important.
+While most research focused on the sound representation in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important.
 Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded.
@@
 Model 2, which predicts that sound similarity and visual similarity influence word learning accuracy in the same way, explained slightly less variance than Model 3 which predicts that these modalities influence word learning differently.
-More precisely, a comparison of the variance estimates across age groups shows that uncertainty reduction in the visual modality was lower compared to that of the auditory modality (Table 1).
-Perhaps this difference is due to the fact that, in our task, the auditory speech had more sources of noise --- that children have to deal with --- than the visual input does.
+Further, as we stated in the results' section, a comparison of the variance estimates across age groups showed that uncertainty reduction in the visual modality was lower compared to that of the auditory modality (Table 1).
+Perhaps this difference is due to the fact that, in our task, the auditory speech had more sources of noise --- that children have to deal with --- than the visual input did.
 The processing of speech involved dealing with both perceptual noise and categorical ambiguity (due to the fact that the phonemic boundaries are still developing).
 In contrast, the processing of the visual input in our task involved only perceptual noise and no category-related uncertainty.
-<!--In real life, however, many semantic referents are conceptual categories and not just individual objects.
-In that case, the asymmetry between the auditory and visual modalities may disappear.
--->
+A future direction of research is independent measurement and comparison of these parameters in children.
+
+<!--In real life, however, many semantic referents are conceptual categories and not just individual objects. In that case, the asymmetry between the auditory and visual modalities may disappear. -->
 
 Our finding that word learning is mediated by the visual similarity of the semantic objects has implications for theories of lexical development.
-It suggests that, all things being equal, children may prioritize the acquisition of words whose semantic referents are visually different, as this allows them to minimize semantic ambiguity.
+It suggests that, all things being equal, children may learn, first, words whose semantic referents are visually different as this allows them to minimize semantic ambiguity.
 It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space.
-This suggestion is, indeed, supported by recent work investigating vocabulary development [@engelthaler2017; @sizemore2018; @fourtassi2018]
+In addition, it is important to study how laboratory experiment of this sort may explain patterns of word learning in the wild [@engelthaler2017; @sizemore2018; @fourtassi2018].
 
@@
 It would have been challenging to obtain such measures with infants.
-That said, though we used data from older children, we still found clear differences compared to adults, suggesting that development does not stop at 17 months, but continues throughout childhood.
+That said, though we used data from older children, we still found clear developmental differences with adults, confirming and extending findings that the ability to distinguish similar-sounding words continues developing well beyond 17 months [@Fennell2014; @Mattock2010; @hazan2000].
 
-One limitation of the model is that it only accounts for bottom-up, similarity-based effects.
-It does not account for how high-level factors such as social and communicative cues can influence learning.
-For example, @fennell2010 highlighted the fact that the Switch task introduces novel words in isolation (e.g., "neem!") rather than within a naming phrase (e.g., "look at the neem!").
+One limitation of our models is that they only account for bottom-up, similarity-based effects.
+They do not account for how high-level factors such as social and communicative cues can influence learning.
+For example, @fennell2010 highlighted the fact that some laboratory tasks such as the one used in @stager1997 introduce novel words in isolation (e.g., "neem!") rather than within a naming phrase (e.g., "look at the neem!").
 This fact may prompt children to interpret these novel words in a non-referential way (e.g., an exclamation such as "Wow!").
-
-<!--Our work contibutes to our undestanding of this mechanism by emphasing its continuous nature. -->
 
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}} \vspace{1em}
+\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}} \vspace{1em}
+
+# Appendix
+
+We show in Table 2 the output of the regression model we used to analyze behavioral data in the experiment.
+```{r xtable, results="asis"}
+
+predictors <- as.data.frame(model_coef) %>%
+  rename(Predictor = effect,
+         Std.Error = "Std. Error",
+         z.value = "z value",
+         p.value = "Pr(>|z|)")
+
+predictors[,-1] <- round(predictors[,-1],2)
+
+predictors <- data.frame(lapply(predictors, function(x) {
+                  gsub("^0$", "<0.01", x)
+              }))
+
+predictors <- data.frame(lapply(predictors, function(x) {
+                  gsub(":", "*", x)
+              }))
+
+predictors <- data.frame(lapply(predictors, function(x) {
+                  gsub("s_dist", "sound_dist", x)
+              }))
+
+predictors <- data.frame(lapply(predictors, function(x) {
+                  gsub("c_dist", "object_dist", x)
+              }))
+
+print(xtable(predictors, type="latex", caption = "Predictor estimates with standard errors and significance information for a logistic mixed-effects model predicting the accuracy of word learning.", table.placement = "h!"))
+
+```
 

### 2019-08-27 journal/ms.tex
first version journal

@@
 \abstract{
-``Cognitive development is often characterized in term of
+``Cognitive development is often characterized in terms of
 discontinuities, but these discontinuities can sometimes be apparent
@@
 children do encode such contrasts, thus favoring a continuous pattern of
-development. Here we propose a probabilistic model describing how
-development may proceed in a continuous fashion across the lifespan. It
-characterizes developmental change as improvement in the precision of
-perceptual encoding. Our model explained previous findings in the
-literature and provided a new prediction --- the referents' visual
-similarity modulates word leanring accuracy. The models' predictions
-were corroborated by human data we collected from both preschool
-children and adults. The braoder impact of this work is to show that
-computational models, such as ours, can help us explore the extent to
-which episodes of cogntive development that are typically thought of as
-discontinuities may emerge from simpler, continuous mechanisms.''
+development. Here we propose a probabilistic model that represents word
+knowledge in a graded fashion and characterizes developmental change as
+improvement in the precision of this graded knowledge. Our model
+explained previous findings in the literature and provided a new
+prediction --- the referents' visual similarity modulates word learning
+accuracy. The models' predictions were corroborated by human data we
+collected from both preschool children and adults. The broader impact of
+this work is to show that computational models, such as ours, can help
+us explore the extent to which episodes of cognitive development that
+are typically thought of as discontinuities may emerge from simpler,
+continuous mechanisms.''
 
@@
 stage-like. Some discontinuities may be related to how we measure a
-specific skill --- some tasks may not allow us to detect successful
-learning. Other discontinuities may emerge due to statistical
+specific skill. Other discontinuities may emerge due to statistical
 thresholding (e.g., p-value \textless{} 0.05) which can create a
@@
 the lifespan --- may provide a simpler and more transparent account of
-development.
+development (see also McMurray (2007) and Shultz, Schmidt, Buckingham,
+and Mareschal (1995)).
 
@@
 task. First, infants are familiarized with two word-object pairings
-(e.g., lable A with object A and label B with object B). Second, they
+(e.g., label 1 with object 1 and label 2 with object 2). Second, they
 are tested using two types of trials. The control \enquote{same} trial
-consists of a correct pairing (e.g., label A with object A) and the
-\enquote{switch} trial consists of a wrong pairing (e.g., label A with
-object B). If babies have correctly learned the association during the
+consists of a correct pairing (e.g., label 1 with object 1) and the
+\enquote{switch} trial consists of a wrong pairing (e.g., label 1 with
+object 2). If babies have correctly learned the association during the
 familiarization, they are supposed to be surprised by the
@@
 subsequent work. For instance, Yoshida, Fennell, Swingley, and Werker
-(2009) investigated whether failure in the switch task reflects a lack
+(2009) investigated whether failure in the Switch task reflects a lack
 of sound encoding during \emph{familiarization}, or whether it is only
-due to the demands of the \emph{testing} method which does not allow
+due to the nature of the \emph{testing} method which does not allow
 learning below a certain threshold to be detected. They used the same
@@
 \& Marchman, 2006; Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987).
-Using this easier and more precise task, the researcher found evidence
-for learning even in 14-month olds.
+Using this testing method, the researcher found evidence for learning
+even in 14-month olds.
 
@@
 in encoding minimal contrast when learning the meanings. Rather, they
-may be encoding this knowledge in a graded fashion (ses also munakata,
-2001). According to this view, development does not so much involve a
+may be encoding this knowledge in a graded fashion (see also Munakata
+(2001)). According to this view, development does not so much involve a
 qualitative shift (i.e., a sudden emergence of an ability that did not
@@
 This general framework --- in which the precision of word knowledge is
-characterize with the variance of a probability distribution --- can
+characterized with the variance of a probability distribution --- can
 already provide an intuitive way of thinking about several findings. In
 particular, unlike the binary view, the probabilistic view allows for
-the possibility that knowldege can be successful while still being
-noisy. This new understanding can provide an account for the fact that
-children show evidence of learning in some testing condition (Yoshida et
-al., 2009), but not in others (Stager \& Werker, 1997).
+the possibility of word knowledge being both successful and noisy. This
+new understanding can provide an account for the fact that children show
+evidence of learning in some testing condition (e.g., Yoshida et al.,
+2009) but not in others (e.g., Stager \& Werker, 1997) --- depending on
+the precision of the measurement.
 
 In a word-pair learning paradigm, children are supposed to associate one
-label, e.g, \enquote{bih}, with object 1 and a second label, e.g.,
+label, e.g., \enquote{bih}, with object 1 and a second label, e.g.,
 \enquote{dih}, with object 2. Infants may succeed in learning both
-associations. Nevertheless, the precision with which the words are
-encoded can still be large, causing their probability distributions to
-overalp (Figure \ref{fig:illus}, top). The way this knowledge is tested
-can lead to divering results.
-
-Failure in the Switch task (Stager \& Werker, 1997) can be exlained as
-follows. Children are understood to succeed if they reject the wrong
-pairing (e.g., \enquote{bih} with object 2). However, the overlap means
-that children could think of \enquote{bih} as plausible misprononciation
-of \enquote{dih}. They may require a stronger sound mismatch to
-confidently reject the possibility that the wrong label is just an
-acceptable deviation from the tyical pronouciation. In contrast, success
-in the two-alternative choice task (Yoshida et al., 2009) occurs
-precisely becasue children do not have to reject a wrong pairing.
-Instead, the setting allows them to just choose which objects is a
-better match to a given label, thus revealing whether they have a
-prefernce, albeit samll, for the correct pairing.
-
-In addition to explaining behavior in different tasks, the probabilsitic
-understanding also accounts for different behaviors in the same task. In
-particular, when the labels are quite distinct in the pereptual space
-(\enquote{lif} vs. \enquote{neem}), the distributions do not overlap as
-much as in the case of similar-sounding words (Figure \ref{fig:illus},
-left). This fact means that the learners will have a stronger preference
-fot the correct label-object pairings and less tolerance for the wrong
-ones. That said, perceptual distinctiveness can be enhanced even for
+associations. Nevertheless, the variance with which the pair of words
+are encoded can still be large, causing their probability distributions
+to overlap (Figure \ref{fig:illus}, top). The way this (noisy) knowledge
+is probed can lead to different results.
+
+In the Switch task (Stager \& Werker, 1997), children are understood to
+succeed if they reject a wrong association (e.g., \enquote{bih} with
+object 2). However, a large overlap between \enquote{bin} and
+\enquote{din} means that \enquote{bih} is itself a plausible
+mispronunciation of \enquote{dih}. The wrong association may not be
+rejected by children because the speaker could have said \enquote{bih}
+but meant \enquote{dih}. In the two-alternative choice task (Yoshida et
+al., 2009), children do not have to reject the wrong association; they
+only need to show a preference for the correct one. Given a label, e.g.,
+\enquote{bih}, they pick which object is a better match to this label.
+Though it is possible that the speaker said \enquote{bih} and meant
+\enquote{dih}, it is \emph{more} likely that the speaker both said and
+meant \enquote{bih} --- this higher probability leads to a preference
+for the correct object.
+
+In addition to explaining the difference in behavior across the Switch
+and the preferential looking tasks, the probabilistic account explains
+difference in behavior within the same task. In particular, when the
+labels are quite distinct in the perceptual space (\enquote{lif} vs.
+\enquote{neem}), the probabilistic distributions do not overlap as much
+as in the case of similar-sounding words (Figure \ref{fig:illus}, left).
+This fact means that the learners will have less tolerance for the wrong
+association, leading to a successful rejection in the Switch task (as
+was reported by Stager and Werker (1997) and subsequent studies using
+the same paradigm). Further, distinctiveness can be enhanced even for
 minimally different sounds when other cues highlight their difference
@@
 Finally, development can be understood as an increase in the precision
-(i.e., a decrease in the variance) of the probabilistic representations,
-leading to a lower overlap between the similar-sounding words (Figure
-\ref{fig:illus}, right). Importantly, a more precise representation
-still has a non-zero variance --- Learning difficulties can still be
-induced with challenging stimuli or in cognitively demanding situations
-as was demonstrate in adults studies (Pajak et al., 2016; White et al.,
-2013).
+(i.e., a decrease in the variance) of the probabilistic knowledge,
+leading to a lower overlap between the distributions of similar-sounding
+words (Figure \ref{fig:illus}, right). Importantly, a more precise
+representation still has a non-zero variance --- Learning difficulties
+can still be induced with challenging stimuli or in cognitively
+demanding situations as was demonstrated in adults studies (Pajak et
+al., 2016; White et al., 2013).
 
@@
 not been tested before (i.e., the effect of the referents' similarity on
-word learning). The broader impact of this work is to explore the extent
-to which development can be understood as a continuous refinement in
-similar representations across the lifespan.
+word learning). We explore the extent to which the probabilistic account
+allows us to understand development in terms of as a continuous
+refinement in similar representations across the lifespan.
 
 The paper is organized as follows. First, we introduce the model and we
-explain how it allows us to characterize behavior in a word learning
-task which resembles the one used in Stager and Werker (1997) and
-Yoshida et al. (2009). Then we explore the predictions of the model
-through simulating its behavior across different parameter settings.
-Next we quantify the extent to which the model's predictions account for
-human data we collected from both preschool children and adults.
-Finally, we discuss the results in the lights of existing accounts of
-word development.
+explain how it allows us to characterize behavior in a
+word-pair-learning paradigm. Then we explore the predictions of the
+model through simulating its behavior across different parameter
+settings. Next, we quantify the extent to which the model's predictions
+account for human data we collected from both preschool children and
+adults. Finally, we discuss the results in the lights of existing
+accounts of word development.
 
@@
 When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score.
-The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
+The accuracy is higher when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
 \end{figure}
@@
 
-{\centering \includegraphics[width=300px]{figs/model}
+{\centering \includegraphics[width=150px]{figs/model}
 
@@
 
-\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
-
-\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \]
+\begin{equation} \label{eq:object}
+ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) 
+\end{equation}
+
+\begin{center}
+and 
+\end{center}
+
+\begin{equation} \label{eq:sound}
+p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L)
+\end{equation}
 
@@
 labels and that observers have successfully learned these mappings
-during the exposure phase: \[
+during the exposure phase:
+
+\begin{equation}
 P(L_i|C_j) = 
@@
 \end{cases}
-\]
+\end{equation}
 
@@
 
-The learner hears a sound \(s\) and has to decide which object \(o\)
-provides an optimal match to this sound (see Figure \ref{fig:task}). To
-this end, they must compute the probability \(P(o|s)\) for all possible
-objects. This probability can be computed by summing over all possible
-concepts and labels:
-\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
-
-The joint probability \(P(o, C, L, s)\) is obtained by factoring the
-Bayesian network in Figure \ref{fig:model}:
-\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]
-
-which can be transformed using Bayes rule into:
-
-\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \]
-
-Finally, assuming that the concepts' prior probability is uniformly
-distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.},
+In our canonical inference case, the learner hears a sound \(s\) and has
+to decide which object \(o\) provides an optimal match to this sound
+(see Figure \ref{fig:task}). To this end, they must compute the
+probability \(P(o|s)\) for all possible objects. This probability can be
+computed by summing over all possible concepts and labels:
+
+\begin{equation}
+P(o|s)=\sum_{C,L} P(o, C, L| s)  
+\end{equation}
+
+Using the fact that \(P(o,C,L|s) = \frac{P(o,C,L,s)}{P(s)}\) and that
+\(P(s)\) does not depend on \(o\), we arrive at the equation:
+
+\begin{equation}
+P(o|s) \propto \sum_{C,L} P(o, C, L, s) 
+\end{equation}
+
+The joint probability \(P(o,C,L,s)\) is obtained by factoring the
+graphical model in Figure \ref{fig:model}:
+
+\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o)\]
+
+Using Bayes' rule, we can rewrite \(P(C|o)\) in terms of \(P(o|C)\):
+
+\[P(C|o) = \frac{P(o|C)P(C)}{P(o)}\]
+
+By subtituting this term in the expression of the joint distribution
+\(P(o,C,L,S)\) we obtain:
+
+\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C)\]
+
+Finally, assuming that the concepts' prior probability \(P(C)\) is
+uniformly
+distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in our experiment.}
 we obtain the following expression, where all conditional dependencies
@@
 
-\[
-P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
-\]
+\begin{equation} \label{eq:general}
+P(o|s) \propto \sum_{C,L}  P(s|L)P(L|C)P(o|C)
+\end{equation}
 
@@
 introduced by Stager and Werker (1997). We used a modified version of
-the task where the testing method consists in a two-alternative forced
-choice (Yoshida et al., 2009). In this task, participants are first
-exposed to the association between pairs of nonsense words (e.g.,
-\enquote{lif}/\enquote{neem}) and pairs of objects. The word-object
-associations are introduced sequentially. After this exposure phase,
-participants perform a series of test trials. In each of these trials,
-one of the two sounds is uttered (e.g., \enquote{lif}) and participants
-choose the corresponding object from the two alternatives. An overview
-of the task is shown in Figure \ref{fig:task}.
-
-From the general expression (1), we derive three exact analytical
-solutions instantiating different learning assumptions. The first
-solution is derived by assuming that the labels are recovered from
-sounds with a certain level of uncertainty \(\sigma_L\), but that
-concepts are unambiguously recovered from the observed objects, i.e.,
+the task where the testing method consists in a two-alternative
+forced-choice (Yoshida et al., 2009). In this task, participants are
+first exposed to two different word-object pairings (e.g., \enquote{lif}
+- object 1, \enquote{neem} - object 2). The word-object associations are
+introduced sequentially. After this exposure phase, participants perform
+a series of test trials. In each of these trials, one of the two sounds
+is uttered (e.g., \enquote{lif}) and participants choose the
+corresponding object from the two alternatives. An overview of the task
+is shown in Figure \ref{fig:task}.
+
+\subsubsection{Model 1}\label{model-1}
+
+From the general expression \ref{eq:general}, we derive three exact
+analytical solutions instantiating different learning assumptions.
+Recall from expressions \ref{eq:object} and \ref{eq:sound} that
+\(P(o|C)\) and \(P(s|L)\) have parameters \(\sigma_C\) and \(\sigma_L\),
+respectively, that control perceptual uncertainty. The first solution is
+derived by assuming that the labels are recovered from sounds with a
+certain level of uncertainty \(\sigma_L > 0\), but that concepts are
+unambiguously recovered from the observed objects, i.e.,
 \(\sigma_C \rightarrow 0\). This assumption has been made --- whether
 implicitly or explicitly --- by most previous work in this line of
-research. One important implication of this assumption is that only the
-similarity of word sounds modulates success in word learning, not the
-similarity of the referents (as long as these referents are
-differentiated perceptually). This assumption yields the following
-probability function:
-
-\begin{equation}
+research. For example, in Stager and Werker (1997), the objects were
+quite dissimilar. Thus, the assumption that they were easily
+discriminated by infants seems relatively well justified. One important
+implication of this assumption is that only the similarity of word
+sounds modulates success in word learning, not the similarity of the
+referents (as long as these referents are differentiated perceptually).
+This assumption yields the following probability function:
+
+\begin{equation} \label{eq:model1}
 P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
@@
 
+\subsubsection{Model 2}\label{model-2}
+
 The second solution is derived by making the more general assumption
-that both the labels and the concepts are recovered with ambiguity from
-the sounds and objects. We first introduce the simplifying assumption
-that the label-related uncertainty \(\sigma_L\) and the concept-related
+that both the labels and the concepts are recovered with noise from the
+sounds and objects. We first introduce the simplifying assumption that
+the label-related uncertainty \(\sigma_L\) and the concept-related
 uncertainty \(\sigma_C\) are of a similar magnitude, i.e.,
@@
 word learning accuracy in exactly the same way. Furthermore, it allows
-us to study the behavior of the model with minimal free parameters.
-
-\begin{equation}
+us to study the behavior of the model with only one free parameter, an
+important consideration given the small number of datapoints available
+from any given infant experiment.
+
+\begin{equation} \label{eq:model2}
 P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
@@
 
+\subsubsection{Model 3}\label{model-3}
+
 We finally derive the third (and most general) solution which allows
@@
 
-\begin{equation}
+\begin{equation} \label{eq:model3}
 P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
@@
 more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation}
-show some simulations of the accuracy \(P(o_T|s)\) as a function of the
+show simulations of the accuracy \(P(o_T|s)\) as a function of the
 distinctiveness parameters (\(\Delta s\) and \(\Delta o\)) and the
@@
 \(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
-(For clarity, we assume here that \(\sigma\)=\(\sigma_C\)=\(\sigma_L\)).
-Dashed line represents chance.}
+(For simplicity, we use model 2, which assumes that
+\(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
 \end{figure}
@@
   For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
-  when the representational uncertainty \(\sigma\) decreases. This fact
-  may explain development, i.e., younger children have noisier
-  representations (see Swingley, 2007; Yoshida et al., 2009), which
-  leads to lower word recognition accuracy, especially for
-  similar-sounding words.
+  when the representational uncertainty \(\sigma\) decreases. This
+  observation provides a simple model for developmental change. Younger
+  children have noisier representations (see Swingley, 2007; Yoshida et
+  al., 2009), which leads to lower word recognition accuracy, especially
+  for similar-sounding words.
 \item
@@
 Nursery School on Stanford University's campus. An additional \(N=\) 39
-children participated but were removed from analyses because they were
-not above chance on the catch trials due to the challenging nature of
-our procedure (see below). We also report data from \(N=\) 74 adult
-participants tested on Amazon Mechanical Turk. An additional \(N=\) 26
-were tested but removed from analyses because they had low scores on the
-catch trials or because they were familiar with the non-English sound
-stimuli we used in the adult experiment.
+children participated but were removed from analyses (using
+preregistered exclusion criteria) because they were not above chance on
+the catch trials due to the challenging nature of our procedure (see
+below). We also report data from \(N=\) 74 adult participants tested on
+Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed
+from analyses (again, using preregistered exclusion criteria) because
+they had low scores on the catch trials or because they were familiar
+with the non-English sound stimuli we used in the adult experiment.
 
@@
 generate objects in four different categories: \enquote{tree,}
-\enquote{bird,} \enquote{bug,} and \enquote{fish.} These categories are
-supposed to be naturally occurring kinds that might be seen on an alien
+\enquote{bird,} \enquote{bug,} and \enquote{fish.} These categories were
+described to participants as naturally occurring kinds on an alien
 planet. In each category, we generated \emph{different},
-\emph{intermediate} and \emph{similar} pairs by manipulating a
-continuous property controlling features of the category's shape (e.g,
+\emph{intermediate}, and \emph{similar} pairs by manipulating a
+continuous property controlling features of the category's shape (e.g.,
 body stretch or head fatness).
@@
 a 7-point scale. Data are shown in Figure \ref{fig:stim} where we scaled
-responses within the range {[}0,1{]} for each stimulus group. These data
-will be used in all models as a proxy for the perceptual distance
-between the sound pairs (\(\Delta s\)) and the object pairs
-(\(\Delta o\)).
+responses within the range {[}0,1{]} for each stimulus group. We used
+these data in all models as an empirical measurement of the perceptual
+distance between the sound pairs and the object pairs. The use of
+empirical measurement allows us to eliminate \(\Delta s\) and
+\(\Delta s\) as free parameters (see Frank and Goodman (2012) and Xu and
+Tenenbaum (2007) for a similar strategy).
 
@@
 said, this difference in the level of similarity is accounted for in the
-model through using the appropriate distance (Figure \ref{fig:stim}).
+model: We used empirical distance measurement to fill in the appropriate
+values of \(\Delta s\) and \(\Delta o\) for each age group.
 
@@
 participants on a fifth catch condition which was similar in its
-structure to the other ones but was used only to select participants who
-were able to follow the instructions and show minimal learning.
+structure to the other ones but was trivially easy and used only to
+select participants who were able to follow the instructions and show
+minimal learning.
 
@@
 adults used their own computers to complete the same experiment online.
-Participants were tested in a sequence of five conditions: the four
-experimental conditions plus the catch condition. In each condition,
-participants saw a first block of four exposure trials followed by four
-testing trials, and a second block of two exposure trials (for memory
-refreshment) followed by an additional four testing trials. The length
-of this procedure was demanding, especially for children, but we adopted
-a fully within-subjects design based on pilot testing that indicated
-that precision of measurement was critical for testing our experimental
-predictions.
+Participants were tested in a random sequence of five conditions: the
+four experimental conditions plus the catch condition. In each
+condition, participants saw a first block of four exposure trials
+followed by four testing trials, and a second block of two exposure
+trials (for memory refreshment) followed by an additional four testing
+trials. The length of this procedure was demanding, especially for
+children, but we adopted a fully within-subjects design based on pilot
+testing that indicated that precision of measurement was critical for
+testing our experimental predictions.
 
@@
 sequence). We also randomized the on-screen position (left vs.~right) of
-the two pictures on each testing trial.
-
-\subsection{Results}\label{results}
+the two pictures on each testing
+trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}
 
@@
 adults).
-We show both the models' predictions (dashed lines) and the experimental results (solid lines).
-The single-variance model uses one joint fitting parameter for both sound and meaning variances.
-The double-variance model uses two separate fittings parameters for the sound and the meaning variances.
+We show both the models' predictions (dashed lines) and the experimental results (solid lines, same across the three panels).
 Error bars represent 95\% confidence intervals.}\label{fig:allData}
 \end{figure}
+
+\subsection{Results}\label{results}
 
@@
 effects in the regression. For the sound distance, we obtained
-\(\beta =\) 0.52 (\(p\) \textless{} 0.001), replicating previous
+\(\beta =\) 0.68 (\(p\) \textless{} 0.001), replicating previous
 findings that sound distance modulates success in word learning (e.g.,
-Stager \& Werker, 1997). For object distance, we found \(\beta =\) 0.83
-(\(p\) \textless{} 0.001), and this finding confirms the new prediction
-of our model according to which object distance also modulates success
-in word learning. Finally, for the age group, we obtained \(\beta =\)
-0.76 (\(p\) \textless{} 0.001), showing that overall performance
-improves with age.
+Stager \& Werker, 1997).
+
+For object distance, we found \(\beta =\) 0.60 (\(p\) \textless{}
+0.001), and this finding confirms the new prediction of our model,
+according to which, object distance also modulates success in word
+learning. Note, in particular, that increasing the visual similarity of
+the objects makes children succeed in learning the similar-sounding
+words. Finally, for the age group, we obtained \(\beta =\) 0.59 (\(p\)
+\textless{} 0.001), showing that overall performance improves with age.
+The full output of the regression model is shown in the Appendix.
 
@@
 \centering
-\begin{tabular}[t]{>{\bfseries}llrrrlrl}
+\begin{tabular}[t]{>{\bfseries}llrrllll}
 \toprule
@@
 \cmidrule(l{2pt}r{2pt}){5-6} \cmidrule(l{2pt}r{2pt}){7-8}
-Model & Structure & Param. & R\textsuperscript{2} & Sig\textsubscript{L} & Sig\textsubscript{C} & Sig\textsubscript{L} & Sig\textsubscript{C}\\
+Model & Structure & Param. & R\textsuperscript{2} & $\sigma$\textsubscript{L} & $\sigma$\textsubscript{C} & $\sigma$\textsubscript{L} & $\sigma$\textsubscript{C}\\
 \midrule
-model 1 & Sig\textsubscript{L} only & 1 & 0.27 & 1.00 & -- & 0.37 & --\\
-model 2 & Sig\textsubscript{L} = Sig\textsubscript{C} & 1 & 0.95 & 0.60 & 0.6 & 0.15 & 0.15\\
-model 3 & Sig\textsubscript{L} != Sig\textsubscript{C} & 2 & 1.00 & 0.83 & 0.31 & 0.12 & 0.17\\
+model 1 & $\sigma$\textsubscript{L} only & 1 & 0.27 & 1 & -- & 0.37 & --\\
+model 2 & $\sigma$\textsubscript{L} = $\sigma$\textsubscript{C} & 1 & 0.95 & 0.6 & 0.6 & 0.15 & 0.15\\
+model 3 & $\sigma$\textsubscript{L} $\neq$ $\sigma$\textsubscript{C} & 2 & 1.00 & 0.83 & 0.31 & 0.12 & 0.17\\
 \bottomrule
@@
 
-We next fit the three models obtained through expressions (1), (2), and
-(3) to the participants' responses in each age group. The predictions of
-the models are shown \ref{fig:allData} (dashed lines) and the parameter
-estimates (for \(\sigma_L\) and \(\sigma_C\)) as well as models'
-goodness to fit (i.e., measured through \(R^2\)) are presented in Table
-\ref{tab:models}.
+We next fit the three models obtained through expressions
+\ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the
+participants' responses in each age group. The predictions of the models
+are shown \ref{fig:allData}. The parameter estimates (for \(\sigma_L\)
+and \(\sigma_C\)) as well as models' goodness to fit (i.e., measured
+through \(R^2\)) are presented in Table \ref{tab:models}.
 
@@
 has a single, shared uncertainty parameter for both auditory and visual
-modalities still explains almost all the variance in human data,
-suggesting that the explanatory power of the general Model 3 is largely
-due to its structure, rather than its degrees of freedom.
+modalities still explains almost all the variance in human data.
 
 As predicted, the uncertainty parameters were larger for children than
-they were for adults (Table \ref{tab:models}), showing that the
-probabilistic representations become more refined (that is, \(\sigma\)
-becomes smaller) across development. Further, the parameter estimates of
-Model 3 show that this developmental effect is more important for the
-label-specific uncertainty that it is for the concept-specific
-uncertainty.
+they were for adults (Table \ref{tab:models}), showing that word
+knowledge gets more precise with development. Further, the parameter
+estimates of Model 3 show that this developmental effect is larger for
+labels (\(\sigma_L\) varies between 0.83 in children and 0.12 in adults)
+than it is for concepts (\(\sigma_C\) varies between 0.31 in children
+and 0.17 in adults).
 
@@
 showing a discrepancy between children's speech perception abilities and
-their word learning skills. While this fact might seem like a specific
-stage in early development, our model demonstrated, instead, that it can
-be more simply understood in terms of continuous developmental change.
-
-The main assumption of the model was that both word form and referent
-are encoded in a probabilistic fashion. The model provided a
-quantitative instantiation of the continuous development hypothesis
-(Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009). More
-precisely, we showed that developmental changes in word-object mappings
-can be characterized as a continuous refinement in the precision of the
-probabilistic representations.
+their word learning skills. The development of this discrepancy could be
+understood in terms of a discrete change in word representation. But our
+model demonstrates that it can also be parsimoniously described as a
+result of continuous developmental change in the precision of children's
+graded word knowledge. Our model instantiates the continuous development
+hypothesis (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009).
 
@@
 categories and as they gain more experience with the functional role of
-these categories, i.e., contrasting word meaning (Apfelbaum \& McMurray,
-2011; Dietrich, Swingley, \& Werker, 2007; Rost \& McMurray, 2009, 2010;
-Yoshida et al., 2009). On the second account, the precision of sound
-encoding in the switch task improves as a result of the maturation of
-more general resources like the attentional and working memory capacity
-(Hofer \& Levy, 2017; Stager \& Werker, 1997; Werker \& Fennell, 2004).
-Such improvement allows older children and adults to better encode the
-sound details while simultaneously matching these sounds to visual
-objects. These two accounts are complementary and both seem to play a
-role (see Tsui, Byers-Heinlein, \& Fennell, 2019 for a review).
+these categories (Apfelbaum \& McMurray, 2011; Dietrich, Swingley, \&
+Werker, 2007; Rost \& McMurray, 2009, 2010; Yoshida et al., 2009). On
+the second account, the precision of sound encoding in the switch task
+improves as a result of the maturation of more general resources like
+the attentional and working memory capacity (Hofer \& Levy, 2017; Stager
+\& Werker, 1997; Werker \& Fennell, 2004). Such improvement allows older
+children and adults to better encode the sound details while
+simultaneously matching these sounds to visual objects. Indeed, one
+recent meta-analysis of the switch task concluded that both changing
+representation precision and better memory/attention play a role in
+developmental changes (Tsui, Byers-Heinlein, \& Fennell, 2019).
 
@@
 task using their theory called Processing Rich Information from
-Multidimensional Interactive Representations (or PRIMIR) which purports
+Multidimensional Interactive Representations (or PRIMIR) which attempts
 to explain various phenomena in early speech perception and word
@@
 simultaneously (including, for example, the gender of the speaker). The
-lack of attentional selection leads to confusion and then to failure in
+lack of selective attention leads to confusion and then to failure in
 the task.
@@
 act as filters, allowing children to attend selectively to the important
-information. This account is also compatible with our model (as it
-resembles the direct account we discussed above). Developing a better
-attentional strategy (thanks to phoneme) can translate into a reduction
-in the uncertainty about whether a sound contrast signals a change in
-meaning.
+information. This account is also compatible with our model: Developing
+phonemic categories allows learners to better determine when a sound
+contrast signals a change in meaning (i.e., when this contrast straddles
+two categories as in \enquote{bin} vs. \enquote{din}) and when a sound
+contrast does not change word meaning (i.e., when it instantiates a
+variation within the same category). In fact, learning to distinguish
+contrastive vs.~non-contrastive pairs amounts to reducing the overlap
+between the probability distribution of two neighboring words.
 
 While most research focused on the sound representation in analyzing the
-Switch task, this work showed that the visual representation of the
-referent is equally important. Indeed, Model 1 --- which assumes that
-any visually discriminable contrast can be encoded unambiguously as
-separate referents --- failed to explain the data, whereas Model 2 and 3
---- which take into account visual ambiguity --- succeeded. As a
-consequence of this assumption, we found that just like word learning is
-modulated by the phonological similarity of the form, it is also
-modulated by the visual similarity of the semantic referents.
+process of learning similar-sounding words, this work showed that the
+visual representation of the referent is equally important. Indeed,
+Model 1 --- which assumes that any visually discriminable contrast can
+be encoded unambiguously as separate referents --- failed to explain the
+data, whereas Model 2 and 3 --- which take into account visual ambiguity
+--- succeeded. As a consequence of this assumption, we found that just
+like word learning is modulated by the phonological similarity of the
+form, it is also modulated by the visual similarity of the semantic
+referents.
 
@@
 less variance than Model 3 which predicts that these modalities
-influence word learning differently. More precisely, a comparison of the
-variance estimates across age groups shows that uncertainty reduction in
-the visual modality was lower compared to that of the auditory modality
-(Table 1). Perhaps this difference is due to the fact that, in our task,
-the auditory speech had more sources of noise --- that children have to
-deal with --- than the visual input does. The processing of speech
-involved dealing with both perceptual noise and categorical ambiguity
-(due to the fact that the phonemic boundaries are still developing). In
-contrast, the processing of the visual input in our task involved only
-perceptual noise and no category-related uncertainty.
+influence word learning differently. Further, as we stated in the
+results' section, a comparison of the variance estimates across age
+groups showed that uncertainty reduction in the visual modality was
+lower compared to that of the auditory modality (Table 1). Perhaps this
+difference is due to the fact that, in our task, the auditory speech had
+more sources of noise --- that children have to deal with --- than the
+visual input did. The processing of speech involved dealing with both
+perceptual noise and categorical ambiguity (due to the fact that the
+phonemic boundaries are still developing). In contrast, the processing
+of the visual input in our task involved only perceptual noise and no
+category-related uncertainty. A future direction of research is
+independent measurement and comparison of these parameters in children.
 
@@
 development. It suggests that, all things being equal, children may
-prioritize the acquisition of words whose semantic referents are
-visually different, as this allows them to minimize semantic ambiguity.
-It will be interesting for future work to explore whether the results
-that we obtained using visual similarity generalize to richer, more
-conceptual features in the semantic space. This suggestion is, indeed,
-supported by recent work investigating vocabulary development
-(Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore,
-Karuza, Giusti, \& Bassett, 2018)
+learn, first, words whose semantic referents are visually different as
+this allows them to minimize semantic ambiguity. It will be interesting
+for future work to explore whether the results that we obtained using
+visual similarity generalize to richer, more conceptual features in the
+semantic space. In addition, it is important to study how laboratory
+experiment of this sort may explain patterns of word learning in the
+wild (Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018;
+Sizemore, Karuza, Giusti, \& Bassett, 2018).
 
@@
 challenging to obtain such measures with infants. That said, though we
-used data from older children, we still found clear differences compared
-to adults, suggesting that development does not stop at 17 months, but
-continues throughout childhood.
-
-One limitation of the model is that it only accounts for bottom-up,
-similarity-based effects. It does not account for how high-level factors
+used data from older children, we still found clear developmental
+differences with adults, confirming and extending findings that the
+ability to distinguish similar-sounding words continues developing well
+beyond 17 months (Fennell \& Byers-Heinlein, 2014; Hazan \& Barrett,
+2000; Mattock, Polka, Rvachew, \& Krehm, 2010).
+
+One limitation of our models is that they only account for bottom-up,
+similarity-based effects. They do not account for how high-level factors
 such as social and communicative cues can influence learning. For
-example, Fennell and Waxman (2010) highlighted the fact that the Switch
-task introduces novel words in isolation (e.g., \enquote{neem!}) rather
-than within a naming phrase (e.g., \enquote{look at the neem!}). This
-fact may prompt children to interpret these novel words in a
-non-referential way (e.g., an exclamation such as \enquote{Wow!}).
+example, Fennell and Waxman (2010) highlighted the fact that some
+laboratory tasks such as the one used in Stager and Werker (1997)
+introduce novel words in isolation (e.g., \enquote{neem!}) rather than
+within a naming phrase (e.g., \enquote{look at the neem!}). This fact
+may prompt children to interpret these novel words in a non-referential
+way (e.g., an exclamation such as \enquote{Wow!}).
 
@@
 
-\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/networks}}}
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}}
 \vspace{1em}
+
+\section{Appendix}\label{appendix}
+
+We show in Table 2 the output of the regression model we used to analyze
+behavioral data in the experiment.
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rlllll}
+  \hline
+ & Predictor & Estimate & Std.Error & z.value & p.value \\ 
+  \hline
+1 & (Intercept) & 1.06 & 0.21 & 5.02 & $<$0.01 \\ 
+  2 & sound\_dist & 0.68 & 0.14 & 4.72 & $<$0.01 \\ 
+  3 & object\_dist & 0.6 & 0.15 & 3.96 & $<$0.01 \\ 
+  4 & age & 0.59 & 0.16 & 3.64 & $<$0.01 \\ 
+  5 & sound\_dist*object\_dist & 0.36 & 0.14 & 2.56 & 0.01 \\ 
+  6 & sound\_dist*age & 0.37 & 0.13 & 2.83 & $<$0.01 \\ 
+  7 & object\_dist*age & 0.25 & 0.13 & 1.91 & 0.06 \\ 
+  8 & sound\_dist*object\_dist*age & 0.19 & 0.13 & 1.45 & 0.15 \\ 
+   \hline
+\end{tabular}
+\caption{Predictor estimates with standard errors and significance information for a logistic mixed-effects model predicting the accuracy of word learning.} 
+\end{table}
 
@@
 
+\hypertarget{ref-Fennell2014}{}
+Fennell, C., \& Byers-Heinlein, K. (2014). You sound like mommy:
+Bilingual and monolingual infants learn words best from speakers typical
+of their language environments. \emph{International Journal of
+Behavioral Development}, \emph{38}(4).
+
 \hypertarget{ref-fennell2010}{}
@@
 Fourtassi, A., Bian, Y., \& Frank, M. C. (2018). Word learning as
-network growth: A cross-linguistic analysis. In \emph{CogSci}.
+network growth: A cross-linguistic analysis. In \emph{Proceedings of the
+40th annual meeting of the cognitive science society}.
+
+\hypertarget{ref-frank2012}{}
+Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning
+in language games. \emph{Science}, \emph{336}(6084).
 
@@
 
+\hypertarget{ref-hazan2000}{}
+Hazan, V., \& Barrett, S. (2000). The development of phonemic
+categorization in children aged 6--12. \emph{Journal of Phonetics},
+\emph{28}(4).
+
 \hypertarget{ref-hofer2017}{}
@@
 \hypertarget{ref-lewis2013}{}
-Lewis, M., \& Frank, M. (2013). An integrated model of concept learning
-and word-concept mapping. In \emph{Proceedings of the annual meeting of
-the cognitive science society} (Vol. 35).
+Lewis, M., \& Frank, M. C. (2013). An integrated model of concept
+learning and word-concept mapping. In \emph{Proceedings of the annual
+meeting of the cognitive science society} (Vol. 35).
+
+\hypertarget{ref-Mattock2010}{}
+Mattock, K., Polka, L., Rvachew, S., \& Krehm, M. (2010). The first
+steps in word learning are easier when the shoes fit: Comparing
+monolingual and bilingual infants. \emph{Developmental Science},
+\emph{13}(1).
+
+\hypertarget{ref-McMurray2007}{}
+McMurray, B. (2007). Defusing the childhood vocabulary explosion.
+\emph{Science}, \emph{317}(5838).
+
+\hypertarget{ref-Munakata2001}{}
+Munakata, Y. (2001). Graded representations in behavioral dissociations.
+\emph{Trends in Cognitive Sciences}, \emph{5}(7).
 
@@
 
+\hypertarget{ref-shultz1995}{}
+Shultz, T. R., Schmidt, W. C., Buckingham, D., \& Mareschal, D. (1995).
+Modeling cognitive development with a generative connectionist
+algorithm. In T. J. Simon \& G. S. Halford (Eds.), \emph{Developing
+cognitive competence: New approaches to process modeling}. Hillsdale,
+NJ: Lawrence Erlbaum Associates, Inc.
+
 \hypertarget{ref-sizemore2018}{}
@@
 
+\hypertarget{ref-xu2007}{}
+Xu, F., \& Tenenbaum, J. B. (2007). Word learning as bayesian inference.
+\emph{Psychological Review}, \emph{114}(2).
+
 \hypertarget{ref-yeung09}{}

### 2019-09-08 journal/ms_blind.Rmd
journal submission

--- 2019-08-27 journal/ms.Rmd
@@
 
-  Abdellah Fourtassi
-
-  Department of Psychology
-
-  Stanford University
-
-  50 Serra Mall
-
-  Jordan Hall, Building 420
-
-  Stanford, CA 94301
+  None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
 
@@
 
-figsintext        : yes
-figurelist        : no
+figsintext        : no
+figurelist        : yes
 tablelist         : no
@@
 
-Cognitive development is sometimes characterized in terms of a succession of discontinuous stages [@piaget1954].
-Although intuitively appealing, this sort of stage theories can be challenging to integrate with theories of learning, which typically posit that knowledge and skills improve incrementally with experience.
+Cognitive development is often characterized in terms of a succession of discontinuous stages.
+In Piaget's initial conception, these stages cross-cut different aspects of cognition [@piaget1954]; in more modern conceptions, distinct domains are often thought to progress on their own timeline [e.g., @carey2015].
+Although intuitively appealing, this sort of stage theory can be challenging to integrate with theories of learning, which typically posit that knowledge and skills improve incrementally with experience.
 Indeed, one of the central challenges of cognitive development has been to explain transitions between stages which appear to be qualitatively different [@carey2009].
@@
 Some discontinuities may be related to how we measure a specific skill.
-Other discontinuities may emerge due to statistical thresholding (e.g., p-value < 0.05) which can create a spurious dichotomy between success and failure in observing a given behavior.
+Other discontinuities may emerge due to statistical thresholding (e.g., an experimental p-value of $p < .05$ for one age group but not another) which can create a spurious dichotomy between success and failure in observing a given behavior.
 In such cases, positing discontinuous stages is unnecessary.
-Instead, a continuous model --- involving similar representations across the lifespan --- may provide a simpler and more transparent account of development (see also @McMurray2007 and @shultz1995).
+Instead, a continuous model --- involving similar representations across the lifespan --- may provide a simpler and more transparent account of development [cf.
+@McMurray2007; @shultz1995].
 
-We use a case study from word learning literature.
+To explore this point computationally, we use a case study from word learning literature.
 @stager1997 first showed that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
@@
 The control 'same' trial consists of a correct pairing  (e.g., label 1 with object 1) and the 'switch' trial consists of a wrong pairing (e.g., label 1 with object 2).
-If babies have correctly learned the association during the familiarization, they are supposed to be surprised by the 'switch' trial and not by the 'same' trial.
+If babies have correctly learned the association during the habituation, they are supposed to be surprised by the 'switch' trial and not by the 'same' trial.
 The former should thus result in a greater looking time compared to the latter [@werker1998].
@@
 The initial discontinuous interpretation has been challenged by subsequent work.
-For instance, @yoshida2009 investigated whether failure in the Switch task reflects a lack of sound encoding during *familiarization*, or whether it is only due to the nature of the *testing* method which does not allow learning below a certain threshold to be detected.
-They used the same familiarization procedure as @stager1997, but instead of comparing the looking times in 'same' and 'switch' trials, they tested infants using a two-alternative choice task comparing fixations to target and distractor objects [@golinkoff1987; @fernald2006].
-Using this testing method, the researcher found evidence for learning even in 14-month olds.
+For instance, @yoshida2009 investigated whether failure in the Switch task reflects a lack of sound encoding during *habituation*, or whether it is only due to the nature of the *testing* method which does not allow learning below a certain threshold to be detected.
+They used the same habituation procedure as @stager1997, but instead of comparing the looking times in 'same' and 'switch' trials, they tested infants using a two-alternative choice task comparing fixations to target and distractor objects [@golinkoff1987; @fernald2006].
+Using this testing method, researchers found evidence for learning even in 14-month olds.
 
@@
 Some researchers [@swingley2007; @yoshida2009; @pajak2016] proposed that word knowledge may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
-Rather, they may be encoding this knowledge in a graded fashion (see also @Munakata2001).
-According to this view, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy knowledge.
+Rather, they may be encoding this knowledge in a graded fashion (see @Munakata2001 for an detailed discussion of a similar view).
+Thus, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy knowledge.
 
@@
 In the Switch task [@stager1997], children are understood to succeed if they reject a wrong association (e.g., "bih" with object 2).
-However, a large overlap between "bin" and "din" means that "bih" is itself a plausible mispronunciation of "dih".
+However, a large overlap between "bih" and "dih" means that "bih" is itself a plausible mispronunciation of "dih".
 The wrong association may not be rejected by children because the speaker could have said "bih" but meant "dih".
-In the two-alternative choice task [@yoshida2009], children do not have to reject the wrong association; they only need to show a preference for the correct one.
-Given a label, e.g., "bih", they pick which object is a better match to this label.
+In the two-alternative choice task [@yoshida2009], children do not have to reject the wrong association; they only need to show a preference, albeit small, for the correct one.
+Thus, unlike the Switch, this testing method allows us to see subtle evidence of learning even with a large overlap.
+For example, given the label "bih", children are supposed to pick which object is a better match to this label.
 Though it is possible that the speaker said "bih" and meant "dih", it is *more* likely that the speaker both said and meant "bih" --- this higher probability leads to a preference for the correct object.
@@
 
-Finally, development can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic knowledge, leading to a lower overlap between the distributions of similar-sounding words (Figure \@ref(fig:illus), right).
-Importantly, a more precise representation still has a non-zero variance --- Learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adults studies [@white2013; @pajak2016].
+In this framework, developmental change can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic knowledge, leading to a lower overlap between the distributions of similar-sounding words (Figure \@ref(fig:illus), right).
+Importantly, a more precise representation still has a non-zero variance.
+Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adults studies [@white2013; @pajak2016].
 
-## This study
+## The current study
 
@@
 The present work proposes a model of word-pair learning based on the probabilistic account.
-We tested the ability of this model to both *explain* various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to *predict* new learning patterns that have not been tested before (i.e., the effect of the referents' similarity on word learning).
-We explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.
+We tested the ability of this model to both *explain* various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to *predict* new learning patterns that have not been tested before.
+In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting recognition difficulty.
+Although this prediction is intuitive, to our knowledge, it has never been tested.
+Finally, we explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.
 
@@
 Next, we quantify the extent to which the model's predictions account for human data we collected from both preschool children and adults.
-Finally, we discuss the results in the lights of existing accounts of word development.
+Finally, we discuss the results in the light of existing accounts of word development.
 
@@
 
+where $\Delta s = s_2-s_1$.
+
 ### Model 2
@@
 Sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design.
-Two age groups (preschool children and adults) were tested on the same task to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
-The experiment, sample size, exclusion criteria and the model's main predictions were pre-registered.\footnote{https://osf.io/942gv/}
+Two age groups (preschool children and adults) were tested on the same task^[This four-condition within-subject design is relatively novel for preschoolers, but we followed the tablet paradigm [e.g., @frank2016] which allowed us to gather a relatively large number of trials from each child.] to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
+The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
 
@@
 ### Participants
-We report data from $N=$ `r N_good_ch` children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
+
+We report data from $N=$ `r N_good_ch` children ages 4-5 years from a nursery school.
 An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
@@
 We also randomized the on-screen position (left vs.
-right) of the two pictures on each testing trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}
+right) of the two pictures on each testing trial.
 
@@
 Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that overall performance improves with age.
-The full output of the regression model is shown in the Appendix.
+The full output of the regression model is shown in Table 2.
 
@@
 
-While most research focused on the sound representation in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important.
+While most research has focused on sound representation specifically in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important.
 Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded.
@@
 Model 2, which predicts that sound similarity and visual similarity influence word learning accuracy in the same way, explained slightly less variance than Model 3 which predicts that these modalities influence word learning differently.
-Further, as we stated in the results' section, a comparison of the variance estimates across age groups showed that uncertainty reduction in the visual modality was lower compared to that of the auditory modality (Table 1).
+Further, as we stated in the results section, a comparison of the variance estimates across age groups showed that uncertainty reduction in the visual modality was lower compared to that of the auditory modality (Table 1).
 Perhaps this difference is due to the fact that, in our task, the auditory speech had more sources of noise --- that children have to deal with --- than the visual input did.
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}} \vspace{1em}
+\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}} \vspace{1em}
 
-# Appendix
-
-We show in Table 2 the output of the regression model we used to analyze behavioral data in the experiment.
 ```{r xtable, results="asis"}
@@
 
-# Acknowledgements
-This work was supported by a post-doctoral grant from the Fyssen Foundation, NSF #1528526, and NSF #1659585.
-
-# Disclosure statement
-None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
-
 # References

### 2019-09-08 journal/ms_blind.tex
journal submission

--- 2019-08-27 journal/ms.tex
@@
-\documentclass[english,,man,floatsintext]{apa6}
+\documentclass[english,,man]{apa6}
 \usepackage{lmodern}
@@
 
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 \linenumbers
+\usepackage[titles]{tocloft}
+\cftpagenumbersoff{figure}
+\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
+\renewcommand{\cftfigaftersnum}{.\space}
+\setlength{\cftfigindent}{0pt}
+\setlength{\cftafterloftitleskip}{0pt}
+\settowidth{\cftfignumwidth}{Figure 10.\qquad}
 \usepackage{tipa}
@@
 
-\authornote{ Abdellah Fourtassi
-
-Department of Psychology
-
-Stanford University
-
-50 Serra Mall
-
-Jordan Hall, Building 420
-
-Stanford, CA 94301
+\authornote{
+
+None of the authors have any financial interest or a conflict of
+interest regarding this work and this submission.
 
@@
 
-Cognitive development is sometimes characterized in terms of a
-succession of discontinuous stages (Piaget, 1954). Although intuitively
-appealing, this sort of stage theories can be challenging to integrate
-with theories of learning, which typically posit that knowledge and
-skills improve incrementally with experience. Indeed, one of the central
-challenges of cognitive development has been to explain transitions
-between stages which appear to be qualitatively different (Carey, 2009).
+Cognitive development is often characterized in terms of a succession of
+discontinuous stages. In Piaget's initial conception, these stages
+cross-cut different aspects of cognition (Piaget, 1954); in more modern
+conceptions, distinct domains are often thought to progress on their own
+timeline (e.g., Carey, Zaitchik, \& Bascandziev, 2015). Although
+intuitively appealing, this sort of stage theory can be challenging to
+integrate with theories of learning, which typically posit that
+knowledge and skills improve incrementally with experience. Indeed, one
+of the central challenges of cognitive development has been to explain
+transitions between stages which appear to be qualitatively different
+(Carey, 2009).
 
@@
 specific skill. Other discontinuities may emerge due to statistical
-thresholding (e.g., p-value \textless{} 0.05) which can create a
-spurious dichotomy between success and failure in observing a given
-behavior. In such cases, positing discontinuous stages is unnecessary.
-Instead, a continuous model --- involving similar representations across
-the lifespan --- may provide a simpler and more transparent account of
-development (see also McMurray (2007) and Shultz, Schmidt, Buckingham,
-and Mareschal (1995)).
-
-We use a case study from word learning literature. Stager and Werker
-(1997) first showed that children's early ability to distinguish similar
-sounds does not automatically translate into word learning skills. The
-authors measured word learning using an audio-visual habituation Switch
-task. First, infants are familiarized with two word-object pairings
-(e.g., label 1 with object 1 and label 2 with object 2). Second, they
-are tested using two types of trials. The control \enquote{same} trial
-consists of a correct pairing (e.g., label 1 with object 1) and the
-\enquote{switch} trial consists of a wrong pairing (e.g., label 1 with
-object 2). If babies have correctly learned the association during the
-familiarization, they are supposed to be surprised by the
-\enquote{switch} trial and not by the \enquote{same} trial. The former
-should thus result in a greater looking time compared to the latter
-(Werker, Cohen, Lloyd, Casasola, \& Stager, 1998).
+thresholding (e.g., an experimental p-value of \(p < .05\) for one age
+group but not another) which can create a spurious dichotomy between
+success and failure in observing a given behavior. In such cases,
+positing discontinuous stages is unnecessary. Instead, a continuous
+model --- involving similar representations across the lifespan --- may
+provide a simpler and more transparent account of development (cf.
+McMurray, 2007; Shultz, Schmidt, Buckingham, \& Mareschal, 1995).
+
+To explore this point computationally, we use a case study from word
+learning literature. Stager and Werker (1997) first showed that
+children's early ability to distinguish similar sounds does not
+automatically translate into word learning skills. The authors measured
+word learning using an audio-visual habituation Switch task. First,
+infants are familiarized with two word-object pairings (e.g., label 1
+with object 1 and label 2 with object 2). Second, they are tested using
+two types of trials. The control \enquote{same} trial consists of a
+correct pairing (e.g., label 1 with object 1) and the \enquote{switch}
+trial consists of a wrong pairing (e.g., label 1 with object 2). If
+babies have correctly learned the association during the habituation,
+they are supposed to be surprised by the \enquote{switch} trial and not
+by the \enquote{same} trial. The former should thus result in a greater
+looking time compared to the latter (Werker, Cohen, Lloyd, Casasola, \&
+Stager, 1998).
 
@@
 (2009) investigated whether failure in the Switch task reflects a lack
-of sound encoding during \emph{familiarization}, or whether it is only
-due to the nature of the \emph{testing} method which does not allow
-learning below a certain threshold to be detected. They used the same
-familiarization procedure as Stager and Werker (1997), but instead of
-comparing the looking times in \enquote{same} and \enquote{switch}
-trials, they tested infants using a two-alternative choice task
-comparing fixations to target and distractor objects (Fernald, Perfors,
-\& Marchman, 2006; Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987).
-Using this testing method, the researcher found evidence for learning
-even in 14-month olds.
+of sound encoding during \emph{habituation}, or whether it is only due
+to the nature of the \emph{testing} method which does not allow learning
+below a certain threshold to be detected. They used the same habituation
+procedure as Stager and Werker (1997), but instead of comparing the
+looking times in \enquote{same} and \enquote{switch} trials, they tested
+infants using a two-alternative choice task comparing fixations to
+target and distractor objects (Fernald, Perfors, \& Marchman, 2006;
+Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987). Using this testing
+method, researchers found evidence for learning even in 14-month olds.
 
@@
 in encoding minimal contrast when learning the meanings. Rather, they
-may be encoding this knowledge in a graded fashion (see also Munakata
-(2001)). According to this view, development does not so much involve a
-qualitative shift (i.e., a sudden emergence of an ability that did not
-exist before) as much as it consists in the continuous refinement of
-initially noisy knowledge.
+may be encoding this knowledge in a graded fashion (see Munakata (2001)
+for an detailed discussion of a similar view). Thus, development does
+not so much involve a qualitative shift (i.e., a sudden emergence of an
+ability that did not exist before) as much as it consists in the
+continuous refinement of initially noisy knowledge.
 
@@
 succeed if they reject a wrong association (e.g., \enquote{bih} with
-object 2). However, a large overlap between \enquote{bin} and
-\enquote{din} means that \enquote{bih} is itself a plausible
+object 2). However, a large overlap between \enquote{bih} and
+\enquote{dih} means that \enquote{bih} is itself a plausible
 mispronunciation of \enquote{dih}. The wrong association may not be
@@
 al., 2009), children do not have to reject the wrong association; they
-only need to show a preference for the correct one. Given a label, e.g.,
-\enquote{bih}, they pick which object is a better match to this label.
-Though it is possible that the speaker said \enquote{bih} and meant
-\enquote{dih}, it is \emph{more} likely that the speaker both said and
-meant \enquote{bih} --- this higher probability leads to a preference
-for the correct object.
+only need to show a preference, albeit small, for the correct one. Thus,
+unlike the Switch, this testing method allows us to see subtle evidence
+of learning even with a large overlap. For example, given the label
+\enquote{bih}, children are supposed to pick which object is a better
+match to this label. Though it is possible that the speaker said
+\enquote{bih} and meant \enquote{dih}, it is \emph{more} likely that the
+speaker both said and meant \enquote{bih} --- this higher probability
+leads to a preference for the correct object.
 
@@
 
-Finally, development can be understood as an increase in the precision
-(i.e., a decrease in the variance) of the probabilistic knowledge,
-leading to a lower overlap between the distributions of similar-sounding
-words (Figure \ref{fig:illus}, right). Importantly, a more precise
-representation still has a non-zero variance --- Learning difficulties
-can still be induced with challenging stimuli or in cognitively
-demanding situations as was demonstrated in adults studies (Pajak et
-al., 2016; White et al., 2013).
-
-\subsection{This study}\label{this-study}
+In this framework, developmental change can be understood as an increase
+in the precision (i.e., a decrease in the variance) of the probabilistic
+knowledge, leading to a lower overlap between the distributions of
+similar-sounding words (Figure \ref{fig:illus}, right). Importantly, a
+more precise representation still has a non-zero variance. Thus,
+learning difficulties can still be induced with challenging stimuli or
+in cognitively demanding situations as was demonstrated in adults
+studies (Pajak et al., 2016; White et al., 2013).
+
+\subsection{The current study}\label{the-current-study}
 
@@
 different words) and to \emph{predict} new learning patterns that have
-not been tested before (i.e., the effect of the referents' similarity on
-word learning). We explore the extent to which the probabilistic account
-allows us to understand development in terms of as a continuous
-refinement in similar representations across the lifespan.
+not been tested before. In particular, we test the prediction that
+referent similarity (i.e., the confusability of pictures referred to by
+novel words) should play an identical computational role to word form
+similarity in predicting recognition difficulty. Although this
+prediction is intuitive, to our knowledge, it has never been tested.
+Finally, we explore the extent to which the probabilistic account allows
+us to understand development in terms of as a continuous refinement in
+similar representations across the lifespan.
 
@@
 account for human data we collected from both preschool children and
-adults. Finally, we discuss the results in the lights of existing
+adults. Finally, we discuss the results in the light of existing
 accounts of word development.
@@
 
+where \(\Delta s = s_2-s_1\).
+
 \subsubsection{Model 2}\label{model-2}
@@
 \centering
-\includegraphics{ms_files/figure-latex/simulation-1.pdf}
+\includegraphics{ms_blind_files/figure-latex/simulation-1.pdf}
 \caption{\label{fig:simulation}The predicted probability of accurate
@@
 varied simultaneously in a within-subject design. Two age groups
-(preschool children and adults) were tested on the same task to explore
-whether development can be characterized with the uncertainty
+(preschool children and adults) were tested on the same task\footnote{This
+  four-condition within-subject design is relatively novel for
+  preschoolers, but we followed the tablet paradigm (e.g., Frank,
+  Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to
+  gather a relatively large number of trials from each child.} to
+explore whether development can be characterized with the uncertainty
 parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
-exclusion criteria and the model's main predictions were
-pre-registered.\footnote{https://osf.io/942gv/}
+exclusion criteria, and the model's main predictions were
+pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
 
@@
 
-We report data from \(N=\) 63 children ages 4-5 years from the Bing
-Nursery School on Stanford University's campus. An additional \(N=\) 39
-children participated but were removed from analyses (using
-preregistered exclusion criteria) because they were not above chance on
-the catch trials due to the challenging nature of our procedure (see
-below). We also report data from \(N=\) 74 adult participants tested on
-Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed
-from analyses (again, using preregistered exclusion criteria) because
-they had low scores on the catch trials or because they were familiar
-with the non-English sound stimuli we used in the adult experiment.
+We report data from \(N=\) 63 children ages 4-5 years from a nursery
+school. An additional \(N=\) 39 children participated but were removed
+from analyses (using preregistered exclusion criteria) because they were
+not above chance on the catch trials due to the challenging nature of
+our procedure (see below). We also report data from \(N=\) 74 adult
+participants tested on Amazon Mechanical Turk. An additional \(N=\) 26
+were tested but removed from analyses (again, using preregistered
+exclusion criteria) because they had low scores on the catch trials or
+because they were familiar with the non-English sound stimuli we used in
+the adult experiment.
 
@@
 
-{\centering \includegraphics{ms_files/figure-latex/stim-1}
+{\centering \includegraphics{ms_blind_files/figure-latex/stim-1}
 
@@
 sequence). We also randomized the on-screen position (left vs.~right) of
-the two pictures on each testing
-trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}
+the two pictures on each testing trial.
 
@@
 
-{\centering \includegraphics{ms_files/figure-latex/allData-1}
+{\centering \includegraphics{ms_blind_files/figure-latex/allData-1}
 
@@
 \textless{} 0.001), showing that overall performance improves with age.
-The full output of the regression model is shown in the Appendix.
+The full output of the regression model is shown in Table 2.
 
@@
 
-While most research focused on the sound representation in analyzing the
-process of learning similar-sounding words, this work showed that the
-visual representation of the referent is equally important. Indeed,
-Model 1 --- which assumes that any visually discriminable contrast can
-be encoded unambiguously as separate referents --- failed to explain the
-data, whereas Model 2 and 3 --- which take into account visual ambiguity
---- succeeded. As a consequence of this assumption, we found that just
-like word learning is modulated by the phonological similarity of the
-form, it is also modulated by the visual similarity of the semantic
-referents.
+While most research has focused on sound representation specifically in
+analyzing the process of learning similar-sounding words, this work
+showed that the visual representation of the referent is equally
+important. Indeed, Model 1 --- which assumes that any visually
+discriminable contrast can be encoded unambiguously as separate
+referents --- failed to explain the data, whereas Model 2 and 3 ---
+which take into account visual ambiguity --- succeeded. As a consequence
+of this assumption, we found that just like word learning is modulated
+by the phonological similarity of the form, it is also modulated by the
+visual similarity of the semantic referents.
 
@@
 influence word learning differently. Further, as we stated in the
-results' section, a comparison of the variance estimates across age
+results section, a comparison of the variance estimates across age
 groups showed that uncertainty reduction in the visual modality was
@@
 
-\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}}
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}}
 \vspace{1em}
-
-\section{Appendix}\label{appendix}
-
-We show in Table 2 the output of the regression model we used to analyze
-behavioral data in the experiment.
 
@@
 
-\section{Acknowledgements}\label{acknowledgements}
-
-This work was supported by a post-doctoral grant from the Fyssen
-Foundation, NSF \#1528526, and NSF \#1659585.
-
-\section{Disclosure statement}\label{disclosure-statement}
-
-None of the authors have any financial interest or a conflict of
-interest regarding this work and this submission.
-
 \section{References}\label{references}
@@
 
+\hypertarget{ref-carey2015}{}
+Carey, S., Zaitchik, D., \& Bascandziev, I. (2015). Theories of
+development: In dialog with jean piaget. \emph{Developmental Review},
+\emph{38}.
+
 \hypertarget{ref-dautriche2015}{}
@@
 in language games. \emph{Science}, \emph{336}(6084).
+
+\hypertarget{ref-frank2016}{}
+Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M., \& Yurovsky, D.
+(2016). Using tablets to collect data from young children. \emph{Journal
+of Cognition and Development}, \emph{17}(1).
 
@@
 
+\clearpage
+
+\renewcommand{\listfigurename}{Figure captions}
+
+\listoffigures
+
 \end{document}

### 2019-09-09 journal/ms_full.Rmd
create folder experiment

--- 2019-09-08 journal/ms_blind.Rmd
@@
 
-  None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
+  'The experiment, sample size, exclusion criteria, and the model’s main predictions were preregistered at https://osf.io/942gv/'
+
+  'All data and analytic code are available at https://github.com/afourtassi/kidswitch'
+
+  'None of the authors have any financial interest or a conflict of interest regarding this work and this submission.'
 
@@
 
-figsintext        : no
-figurelist        : yes
+figsintext        : yes
+figurelist        : no
 tablelist         : no
 footnotelist      : no
-lineno            : yes
+lineno            : no
 
@@
 Sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design.
-Two age groups (preschool children and adults) were tested on the same task^[This four-condition within-subject design is relatively novel for preschoolers, but we followed the tablet paradigm [e.g., @frank2016] which allowed us to gather a relatively large number of trials from each child.] to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
-The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
+Two age groups (preschool children and adults) were tested on the same task^[This four-condition within-subject design is relatively novel for preschoolers, but the tablet paradigm [@frank2016] allowed us to gather a relatively large number of trials from each child.] to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
+The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{https://osf.io/942gv/}
 
@@
 
-We report data from $N=$ `r N_good_ch` children ages 4-5 years from a nursery school.
+We report data from $N=$ `r N_good_ch` children ages 4-5 years from the Bing Nursery School on Stanford University’s campus.
 An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
@@
 We also randomized the on-screen position (left vs.
-right) of the two pictures on each testing trial.
+right) of the two pictures on each testing trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}
 
@@
 
-\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}} \vspace{1em}
+\vspace{1em} \fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}} \vspace{1em}
+
+# Appendix
+
+We show in Table 2 the output of the regression model we used to analyze behavioral data in the experiment.
 

### 2019-09-09 journal/ms_full.tex
create folder experiment

--- 2019-09-08 journal/ms_blind.tex
@@
-\documentclass[english,,man]{apa6}
+\documentclass[english,,man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
-\usepackage{lineno}
-
-\linenumbers
-\usepackage[titles]{tocloft}
-\cftpagenumbersoff{figure}
-\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
-\renewcommand{\cftfigaftersnum}{.\space}
-\setlength{\cftfigindent}{0pt}
-\setlength{\cftafterloftitleskip}{0pt}
-\settowidth{\cftfignumwidth}{Figure 10.\qquad}
 \usepackage{tipa}
@@
 
-\authornote{
-
-None of the authors have any financial interest or a conflict of
-interest regarding this work and this submission.
+\authornote{ `The experiment, sample size, exclusion criteria,
+and the model's main predictions were preregistered at
+\url{https://osf.io/942gv/}'
+
+`All data and analytic code are available at
+\url{https://github.com/afourtassi/kidswitch}'
+
+`None of the authors have any financial interest or a conflict of
+interest regarding this work and this submission.'
 
@@
 \centering
-\includegraphics{ms_blind_files/figure-latex/simulation-1.pdf}
+\includegraphics{ms_full_files/figure-latex/simulation-1.pdf}
 \caption{\label{fig:simulation}The predicted probability of accurate
@@
   four-condition within-subject design is relatively novel for
-  preschoolers, but we followed the tablet paradigm (e.g., Frank,
-  Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to
-  gather a relatively large number of trials from each child.} to
-explore whether development can be characterized with the uncertainty
-parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
-exclusion criteria, and the model's main predictions were
-pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
+  preschoolers, but the tablet paradigm (Frank, Sugarman, Horowitz,
+  Lewis, \& Yurovsky, 2016) allowed us to gather a relatively large
+  number of trials from each child.} to explore whether development can
+be characterized with the uncertainty parameters, \(\sigma_C\) and
+\(\sigma_L\). The experiment, sample size, exclusion criteria, and the
+model's main predictions were
+pre-registered.\footnote{https://osf.io/942gv/}
 
@@
 
-We report data from \(N=\) 63 children ages 4-5 years from a nursery
-school. An additional \(N=\) 39 children participated but were removed
-from analyses (using preregistered exclusion criteria) because they were
-not above chance on the catch trials due to the challenging nature of
-our procedure (see below). We also report data from \(N=\) 74 adult
-participants tested on Amazon Mechanical Turk. An additional \(N=\) 26
-were tested but removed from analyses (again, using preregistered
-exclusion criteria) because they had low scores on the catch trials or
-because they were familiar with the non-English sound stimuli we used in
-the adult experiment.
+We report data from \(N=\) 63 children ages 4-5 years from the Bing
+Nursery School on Stanford University's campus. An additional \(N=\) 39
+children participated but were removed from analyses (using
+preregistered exclusion criteria) because they were not above chance on
+the catch trials due to the challenging nature of our procedure (see
+below). We also report data from \(N=\) 74 adult participants tested on
+Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed
+from analyses (again, using preregistered exclusion criteria) because
+they had low scores on the catch trials or because they were familiar
+with the non-English sound stimuli we used in the adult experiment.
 
@@
 
-{\centering \includegraphics{ms_blind_files/figure-latex/stim-1}
+{\centering \includegraphics{ms_full_files/figure-latex/stim-1}
 
@@
 sequence). We also randomized the on-screen position (left vs.~right) of
-the two pictures on each testing trial.
+the two pictures on each testing
+trial.\footnote{The experiment can be viewed online at https://tinyurl.com/word-pair-learning-experiment}
 
@@
 
-{\centering \includegraphics{ms_blind_files/figure-latex/allData-1}
+{\centering \includegraphics{ms_full_files/figure-latex/allData-1}
 
@@
 
-\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}}
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at\ \url{https://github.com/afourtassi/kidswitch}}}
 \vspace{1em}
+
+\section{Appendix}\label{appendix}
+
+We show in Table 2 the output of the regression model we used to analyze
+behavioral data in the experiment.
 
@@
 
-\clearpage
-
-\renewcommand{\listfigurename}{Figure captions}
-
-\listoffigures
-
 \end{document}

### 2020-03-20 Analysis/process.Rmd
revisions

@@
 library(ggplot2)
-library(langcog)
+#library(langcog)
 library(ggthemes)
@@
   xlab("Stimuli group")+ ylab("Perceptual distance (experimental)")
+
+```
+
+Stats here
+
+```{r}
+
+#Is the most difficult condition is at chance?
+rand_stat <- d_child_good %>%
+  filter(sound_dist == "similar" & concept_dist == "similar")
+
+myVar <- rand_stat$iscorrect
+k <- sum(myVar)
+n <- length(myVar)
+
+myTest <- binom.test(k,n, 0.5)
+
+rand_plus_stat <- d_child_good %>%
+  filter(sound_dist == "similar" & concept_dist == "different")
+
+myVar <- rand_plus_stat$iscorrect
+k <- sum(myVar)
+n <- length(myVar)
+
+myTest <- binom.test(k,n, 0.5)
+
+both <- d_child_good %>%
+  filter(sound_dist == "similar" & (concept_dist == "similar" || concept_dist == "different"))
+
+data_both <- both %>%
+  mutate(s_dist=ifelse(sound_dist=="similar", -1,1),
+         c_dist=ifelse(concept_dist=="similar", -1, 1))
+
+model_both <- glmer(iscorrect ~ c_dist + 
+                 (c_dist  | ID), 
+               data = data_both, family = binomial())
 
@@
 
-model2_val <- c(confint(fit_children_2), Vr_s_ch, Vr_o_ch, model="2", group = "children") %>%
-  bind_rows(c(confint(fit_adults_2), Vr_s_ad, Vr_o_ad, model="2", group = "adults"))
+#model2_val <- c(confint(fit_children_2), Vr_s_ch, Vr_o_ch, model="2", group = "children") %>%
+#  bind_rows(c(confint(fit_adults_2), Vr_s_ad, Vr_o_ad, model="2", group = "adults"))
 

### 2020-03-20 cogsci/cogsci.Rmd
revisions

@@
 library(ggplot2)
-library(langcog)
+#library(langcog)
 library(boot)
@@
 library(lmtest)
-library(rwebppl)
+#library(rwebppl)
 library(jsonlite)

### 2020-03-20 cogsci/cogsci.tex
revisions

@@
 % cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
+\usepackage{apacite}
+
+% KM added 1/4/18 to allow control of blind submission
 
@@
 
-\section{Introduction}\label{introduction}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
-\section{Model}\label{model}
+\hypertarget{model}{%
+\section{Model}\label{model}}
 
-\subsection{Probabilistic structure}\label{probabilistic-structure}
+\hypertarget{probabilistic-structure}{%
+\subsection{Probabilistic structure}\label{probabilistic-structure}}
 
@@
 
-\subsection{Inference}\label{inference}
+\hypertarget{inference}{%
+\subsection{Inference}\label{inference}}
 
@@
 
+\hypertarget{task-and-model-predictions}{%
 \subsection{Task and model
-predictions}\label{task-and-model-predictions}
+predictions}\label{task-and-model-predictions}}
 
@@
 
-\section{Experiment}\label{experiment}
+\hypertarget{experiment}{%
+\section{Experiment}\label{experiment}}
 
@@
 
-\subsection{Methods}\label{methods}
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
 
-\subsubsection{Participants}\label{participants}
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
 
@@
 
+\hypertarget{stimuli-and-similarity-rating}{%
 \subsubsection{Stimuli and similarity
-rating}\label{stimuli-and-similarity-rating}
+rating}\label{stimuli-and-similarity-rating}}
 
@@
 
-\subsubsection{Design}\label{design}
+\#\#\#Design
 
@@
 
-\subsubsection{Procedure}\label{procedure}
+\hypertarget{procedure}{%
+\subsubsection{Procedure}\label{procedure}}
 
@@
 
-\subsection{Results}\label{results}
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
@@
 \& Tily, 2013). We found main effects for all the fixed effects in the
-regression. For the sound distance, we obtained \(\beta =\) 0.52 (\(p\)
+regression. For the sound distance, we obtained \(\beta =\) 0.68 (\(p\)
 \textless{} 0.001), replicating previous findings. For object distance,
-we found \(\beta =\) 0.83 (\(p\) \textless{} 0.001), and this finding
+we found \(\beta =\) 0.6 (\(p\) \textless{} 0.001), and this finding
 confirms the new prediction of our model. Finally, for the age group, we
-obtained \(\beta =\) 0.76 (\(p\) \textless{} 0.001), showing that
+obtained \(\beta =\) 0.59 (\(p\) \textless{} 0.001), showing that
 performance improves with age.
@@
 
-\section{General Discussion}\label{general-discussion}
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
-\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent
+\setlength{\parindent}{-0.1in} 
+\setlength{\leftskip}{0.125in}
+
+\noindent
 
 \hypertarget{refs}{}
-\hypertarget{ref-barr2013}{}
+\leavevmode\hypertarget{ref-barr2013}{}%
 Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects
@@
 
-\hypertarget{ref-carey2009}{}
+\leavevmode\hypertarget{ref-carey2009}{}%
 Carey, S. (2009). \emph{The origin of concepts}. Oxford University
@@
 
-\hypertarget{ref-dutoit1996}{}
+\leavevmode\hypertarget{ref-dutoit1996}{}%
 Dutoit, T., Pagel, V., Pierret, N., Bataille, F., \& Van der Vrecken, O.
@@
 
-\hypertarget{ref-engelthaler2017}{}
+\leavevmode\hypertarget{ref-engelthaler2017}{}%
 Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word
@@
 
-\hypertarget{ref-fennell2010}{}
+\leavevmode\hypertarget{ref-fennell2010}{}%
 Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow
@@
 
-\hypertarget{ref-hofer2017}{}
+\leavevmode\hypertarget{ref-hofer2017}{}%
 Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken
@@
 
-\hypertarget{ref-lewis2013}{}
+\leavevmode\hypertarget{ref-lewis2013}{}%
 Lewis, M., \& Frank, M. (2013). An integrated model of concept learning
@@
 
-\hypertarget{ref-pajak2016}{}
+\leavevmode\hypertarget{ref-pajak2016}{}%
 Pajak, B., Creel, S., \& Levy, R. (2016). Difficulty in learning
@@
 
-\hypertarget{ref-piaget1954}{}
+\leavevmode\hypertarget{ref-piaget1954}{}%
 Piaget, J. (1954). \emph{The construction of reality in the child}. New
@@
 
-\hypertarget{ref-rost2009}{}
+\leavevmode\hypertarget{ref-rost2009}{}%
 Rost, G., \& McMurray, B. (2009). Speaker variability augments
@@
 
-\hypertarget{ref-sizemore2018}{}
+\leavevmode\hypertarget{ref-sizemore2018}{}%
 Sizemore, A. E., Karuza, E. A., Giusti, C., \& Bassett, D. S. (2018).
@@
 
-\hypertarget{ref-stager1997}{}
+\leavevmode\hypertarget{ref-stager1997}{}%
 Stager, C., \& Werker, J. (1997). Infants listen for more phonetic
@@
 
-\hypertarget{ref-swingley2007}{}
+\leavevmode\hypertarget{ref-swingley2007}{}%
 Swingley, D. (2007). Lexical exposure and word-form encoding in
@@
 
-\hypertarget{ref-thiessen2007}{}
+\leavevmode\hypertarget{ref-thiessen2007}{}%
 Thiessen, E. (2007). The effect of distributional information on
@@
 
-\hypertarget{ref-werker2002}{}
+\leavevmode\hypertarget{ref-werker2002}{}%
 Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants'
@@
 
-\hypertarget{ref-white2013}{}
+\leavevmode\hypertarget{ref-white2013}{}%
 White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show
@@
 
-\hypertarget{ref-wojcik2013}{}
+\leavevmode\hypertarget{ref-wojcik2013}{}%
 Wojcik, E., \& Saffran, J. (2013). The ontogeny of lexical networks:
@@
 
-\hypertarget{ref-yoshida2009}{}
+\leavevmode\hypertarget{ref-yoshida2009}{}%
 Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009).
@@
 
+\bibliographystyle{apacite}
+
 \end{document}

### 2020-03-20 journal/ms_blind.Rmd
revisions

@@
    - \usepackage[sortcites=false,sorting=none]{biblatex}
+   - \usepackage{xcolor}
 
@@
 footnotelist      : no
-lineno            : yes
+lineno            : no
 
@@
 
-#Introduction
+# Introduction
 
@@
 
-The probabilistic account has been put forward to explain patterns of learning and development at the qualitative level.
+The probabilistic account was used before to explain patterns of learning and development at the qualitative level [e.g.,@swingley2007].
 However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.
@@
 However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously.
-In our model, we assume that both labels and concepts are observed with a certain amount of perceptual noise, which we assume, for simplicity, is captured by a normal distribution:
+In our model, we assume that both labels and concepts are categories with possibly overlapping distributions.
+In other words, we allow the model to account for the --- more realistic --- possibility that an instances of a given categories (e.g.,"bin") can be mistaken for an instance of a neighboring category (e.g., "din"), albeit with a smaller probability.
+We assume, for simplicity, that this probability is captured by a normal distribution\footnote{\textcolor{red}{We used a normal distribution to simplify the mathematical derivations.
+This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}}:
 
@@
 Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
-\begin{equation}
+\begin{equation}\label{eq:mapping}
 P(L_i|C_j) = 
@@
 
+From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions.
+
 ### Model 1
-From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions.
-Recall from expressions \ref{eq:object} and \ref{eq:sound} that $P(o|C)$ and $P(s|L)$ have parameters $\sigma_C$ and $\sigma_L$, respectively, that control perceptual uncertainty.
-The first solution is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty $\sigma_L > 0$, but that concepts are unambiguously recovered from the observed objects, i.e., $\sigma_C \rightarrow 0$.
+
+ Recall from expressions \ref{eq:object} and \ref{eq:sound} that $P(o|C)$ and $P(s|L)$ have parameters $\sigma_C$ and $\sigma_L$, respectively, that control for uncertainty.
+The first solution/model is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty $\sigma_L > 0$, but that concepts are unambiguously recovered from the observed objects, i.e., $\sigma_C \rightarrow 0$.
 This assumption has been made --- whether implicitly or explicitly --- by most previous work in this line of research.
@@
 Thus, the assumption that they were easily discriminated by infants seems relatively well justified.
-One important implication of this assumption is that only the similarity of word sounds modulates success in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually).
-This assumption yields the following probability function:
+One important implication of this assumption is that only the similarity of word sounds modulates performance in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually).
+
+This assumption yields the following probability function of choosing the correct object $o_i$ given the correspondding label instance $s_i$, where $i \in \{1,2\}$ (see the Appendix for the full mathematical derivation):
 
 \begin{equation} \label{eq:model1}
-P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
+P(o_i|s_i)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
 \end{equation}
 
-where $\Delta s = s_2-s_1$.
+where $\Delta s = s_2-s_1$ is the perceptual sound distance between the pair of sounds that we refer to as $s_1$ and $s_2$.
+These distances were measured empirically as shown in Figure \@ref(fig:stim).
 
 ### Model 2
+
 The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with noise from the sounds and objects.
@@
 \begin{equation} \label{eq:model2}
-P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
+P(o_i|s_i)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
 \end{equation}
@@
 \begin{equation} \label{eq:model3}
-P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
+P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
 \end{equation}
 
-In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show simulations of the accuracy $P(o_T|s)$ as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the uncertainty parameters $\sigma_L$ and $\sigma_C$.
+In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show simulations of the accuracy $P(o_i|s_i)$ as a function of the distinctiveness parameters ($\Delta s$ and $\Delta o$) and the uncertainty parameters $\sigma_L$ and $\sigma_C$.
 
@@
   geom_hline(yintercept = 0.50, linetype="dashed") +
-  xlab(expression(Delta*"s")) + ylab(expression("P("*o['T']*"| s)")) +
+  xlab(expression(Delta*"s")) + ylab(expression("P("*o['i']*"|"*s['i']*")")) +
   facet_grid(.~obj) +
@@
 The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996].
-We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) *different* pairs: "lif"/"neem" and "zem"/"doof", 2) *intermediate* pairs: "aka"/"ama" and "ada"/"aba", and 3) *similar* non-English pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
+We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) *different* pairs: "lif"/"neem" and "zem"/"doof", 2) *intermediate* pairs: "aka"/"ama" and "ada"/"aba", and 3) *similar* non-English pairs\footnote{For the intermediate/similar pairs, we made the choice of using a VCV (Vowel-Consonant-Vowel) structure in order to emphasize the phonemic difference in the minimal pairs, especially for the non-native contrasts.
+However, as one reviwer rightfully pointed out to us, this structure could influence word leaning performance since it is not common in English.
+Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand.
+However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
+For the simialr pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
+In this respect, we took inspiration from the work of @pajak2016.
+We refer the reader to that paper for a lengthy discussion of the literature on (and implications for) L2 phoneme perception.
 
@@
 
-###Design
+### Design
 
@@
 
-```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=4, fig.height=3, fig.cap = "Distances for both sound and object pairs from an adult norming study.
+```{r stim, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=4, fig.height=3, fig.cap = "Distances for sound and object pairs ($\\Delta s$ and $\\Delta o$, respectively) from an adult norming study.
 Data represent Likert values normalized to [0,1] interval.
@@
 For both objects, visual stimuli were present for the duration of the sound clip (about 800ms).
+During this phase, participant were asked to pay attention and try yo lean the words.
 In the testing trials, participants saw both objects simultaneously and heard only one sound.
@@
 right) of the two pictures on each testing trial.
+The online experiment can be viewed at XXX
 
@@
 
+```{r results='asis'}
+
+#Binomoial test to show that children are not different from chance at the most difficult condition
+rand_stat <- d_child_good %>%
+  filter(sound_dist == "similar" & concept_dist == "similar")
+
+myVar <- rand_stat$iscorrect
+k <- sum(myVar)
+n <- length(myVar)
+
+myTest0 <- binom.test(k,n, 0.5)
+
+rand_plus_stat <- d_child_good %>%
+  filter(sound_dist == "similar" & concept_dist == "different")
+
+myVar <- rand_plus_stat$iscorrect
+k <- sum(myVar)
+n <- length(myVar)
+
+myTest1 <- binom.test(k,n, 0.5)
+
+```
+
 Experimental results are shown in Figure \@ref(fig:allData) (solid lines).
@@
 
-For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model, according to which, object distance also modulates success in word learning.
-Note, in particular, that increasing the visual similarity of the objects makes children succeed in learning the similar-sounding words.
+For object distance, we found $\beta =$ `r c_coef`  ($p$ `r p_val(c_p)`), and this finding confirms the new prediction of our model, according to which, object distance also modulates performance in word learning.
 Finally, for the age group, we obtained  $\beta =$ `r age_coef` ($p$ `r p_val(age_p)`), showing that overall performance improves with age.
 The full output of the regression model is shown in Table 2.
+
+In particular, while children were not different form chance in the most difficult condition when both the sounds and objects are similar .
+Note, however, the differe that the difference between the these two conditions was not itself
 
@@
                    R = c(R2_model1, R2_model2, R2_model3),
-                   sigS_C = c(mod1_ch_val,
-                              mod2_ch_val,
-                              mod3_ch_s_val
+                   sigS_C = c(paste(mod1_ch_val, ' [', mod1_ch_conf1, ', ' , mod1_ch_conf2, ']', sep = ""),
+                              paste(mod2_ch_val, ' [', mod2_ch_conf1, ', ' , mod2_ch_conf2, ']', sep = ""),
+                              paste(mod3_ch_s_val, ' [', mod3_ch_s_conf1, ', ' , mod3_ch_s_conf2, ']', sep = "")
                               ),
                    sigO_C = c('--',
-                              mod2_ch_val,
-                              mod3_ch_o_val
+                              paste(mod2_ch_val, ' [', mod2_ch_conf1, ', ' , mod2_ch_conf2, ']', sep = ""),
+                              paste(mod3_ch_o_val, ' [', mod3_ch_o_conf1, ', ' , mod3_ch_o_conf2, ']', sep = "")
                               ),
-                   sigS_A = c(mod1_ad_val,
-                              mod2_ad_val,
-                              mod3_ad_s_val
+                   sigS_A = c(paste(mod1_ad_val, ' [', mod1_ad_conf1, ', ' , mod1_ad_conf2, ']', sep = ""),
+                              paste(mod2_ad_val, ' [', mod2_ad_conf1, ', ' , mod2_ad_conf2, ']', sep = ""),
+                              paste(mod3_ad_s_val, ' [', mod3_ad_s_conf1, ', ' , mod3_ad_s_conf2, ']', sep = "")
                               ),
                    sigO_A = c('--',
-                              mod2_ad_val,
-                              mod3_ad_o_val
+                              paste(mod2_ad_val, ' [', mod2_ad_conf1, ', ' , mod2_ad_conf2, ']', sep = ""),
+                              paste(mod3_ad_o_val, ' [', mod3_ad_o_conf1, ', ' , mod3_ad_o_conf2, ']', sep = "")
 
@@
       linesep = "", format.args = list(big.mark = ","),
-      caption = "Characteristics and performance of the models used in this study.",
+      caption = "Characteristics and performance of the models used in this study. Value ranges represent 95\\% confidence intervals.",
       col.names = c("Model",  "Structure", "Param.", "R\\textsuperscript{2}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}", "$\\sigma$\\textsubscript{L}", "$\\sigma$\\textsubscript{C}")) %>%
@@
   column_spec(1, bold = TRUE) %>%
-  kable_styling(position = "center")
+  kable_styling(position = "center", latex_options="scale_down")
 
@@
 The parameter estimates (for $\sigma_L$ and $\sigma_C$) as well as models' goodness to fit (i.e., measured through $R^2$) are presented in Table \@ref(tab:models).
+\ Remmeber that, in our model, the fitted uncertainty parameters characterize the learners' general processing skills at a given time in development.
+Thus, they are understood to be the same across all stimuli within a given modality.
 
@@
 
+More precisely, our model used the assumption that the ability to distinguish two stimuli perceptually leads to accurate mapping to two distinct objects, although this mapping can be noisy.
+On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations.
+With this assumption, the model was capable of accurately predicting behavior (including around-chance performance in the case of the most difficult contrasts)\footnote{That is, the case when both the sounds and objects are similar for children.
+Figure 6 shows that the confidence intervals include the chance value of 0.5.}, thus providing a proof of concept for the continuity hypothesis.
+The discontinuity hypothesis  --- which posits the absence of learning and not just retrieval difficulty --- cannot be ruled out by our model, but it is less parsimonious.
+We propose that the continuous hypothesis should be considered as a baseline; discontinuous development should only be posited if it deviates from this baseline.
+
 We find in the literature two broad accounts of development in the Switch task: One that suggests *direct* development of the sound representation and one that hypothesizes *indirect* development of this representation through improvement in general cognitive resources.
-On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011].
+On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011; @werker2005].
 On the second account, the precision of sound encoding in the switch task improves as a result of the maturation of more general resources like the attentional and working memory capacity [@stager1997; @werker2004; @hofer2017].
@@
 
-Our model is compatible with both of these accounts.
-In our work, the probability distributions do not distinguish between the direct and indirect sources of uncertainty --- both are included.
-Indeed, part of the measured uncertainty reflects the learner's degrees of confidence in the phonetic/phonological boundaries (i.e., the direct account) and another part reflects a possible drop in perceptual acuity due to high cognitive load (i.e., the indirect account).
-Note, however, that the model (at least in its current format) is incapable of answering questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.
-
+<!---
 @werker2005 proposed to explain development in the Switch task using their theory called Processing Rich Information from Multidimensional Interactive Representations (or PRIMIR) which attempts to explain various phenomena in early speech perception and word learning within a unified framework.
@@
 The latter act as filters, allowing children to attend selectively to the important information.
-This account is also compatible with our model: Developing phonemic categories allows learners to better determine when a sound contrast signals a change in meaning (i.e., when this contrast straddles two categories as in "bin" vs.
+This account is also compatible with our model: Developing phonemic categories, by definition, means that learners become better at determining when a sound contrast signals a change in meaning (i.e., when this contrast straddles two categories as in "bin" vs.
 "din") and when a sound contrast does not change word meaning (i.e.,  when it instantiates a variation within the same category).
@@
 non-contrastive pairs amounts to reducing the overlap between the probability distribution of two neighboring words.
+--->
+
+In some sense, our model is compatible with both of these accounts.
+Indeed, the model aims at understanding *how* (by contrast to *what*) uncertainty can influence word learning.
+It characterizes and measures uncertainty in a rather global/coarse fashion, without committing to any specific source.
+Thus, it is compatible\footnote{Note the fact that our model is compatible with several previous accounts does not necessarily mean that these accounts are themeselves compatible with one another.} with direct accounts that posit uncertainty primarily stems from noisy phonological representations, and with the indirect account which suggests uncertainty primarily stems from a limitation in the general cognitive resources, hindering precise encoding in memory of subtle sounds under challenging conditions.
+Note that, since our goal was not to distinguish between these accounts, the model (at least in its current format) cannot answer questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.
 
@@
 As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents.
+This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform [@Zhao2019; @fourtassi2019; @yeung09].
+Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see @Zhao2019 for a detailed dsicussion).
+That said, these two questions can be related, albeit indirectly.
+For instance, while we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
 
@@
 
+Our work found, among other things, that children have higher sound/phoneme uncertainty that adults do, but prior work have shown that children have good auditory encoding [@swingley2000; @swingley2002; @swingley2003].
+These two findings are not in contradicton with each other.
+In this work, and as we explained above, the measured sound uncertainty includes various sources.
+One of these sources is perceptual uncertainty, i.e., the ability to perceptually distinguish a sound from other neighboring sounds (e.g., "bin" is perceptually different from "din"), and another source is categorical uncertainty, i.e., the ability to estimate phonological boundaries, e.g., "bin" and "din" straddle a phonological boundary, that is, they signal a change in meaning.
+The fact that children have a higher sound uncertainty than adults do,  does not necessarily mean this higher uncertainty is due to poorer perceptual encoding, only.
+In fact, it is possible that much of the differential in uncertainty (compared to adults) is due to the categorical/phonological dimension which we know undergoes a process of reorganization and refinement across development.
+Thus, our finding that children have higher sound-related uncertainty does not contradict previous work showing children are capable of fine-grained speech perception (see @werker2005 for a similar view).
+
 There are a few limitations to this work.
@@
 We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting).
-Data collection involved presenting participants with several trials across four conditions in a between-subject design.
+Data collection involved presenting participants with several trials across four conditions in a within-subject design.
 It would have been challenging to obtain such measures with infants.
@@
 Computational models, such as the one proposed here, can help us investigate the extent to which such discontinuities emerge due to genuine qualitative changes and the extent to which they reflect the granularity of the researchers' own measurement tools.
+
+# Appendix
+
+Here we provide the full mathematical derivation the models' predictions.
+More specifically, we explain how the general Equation \ref{eq:general} leads to Equations \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} which represent our three Models.
+
+Each of these Models instantiates an approximation of $P(o_i|s_i)$ which is the probability that, given a label instance $s_i$, a participant would choose the correct object $o_i$, as opposed to the incorrect object $o_{j}$, where $i, j \in \{1,2\}$ and $j = 1-i$.
+
+We strat from the general expression of this probability as defined in Equation \ref{eq:general}.
+This expression can be normalized in our special case (i.e., a two-alternative-forced choice task) as follows:
+
+$$P(o_i|s_i) = \frac{\sum_{C,L} P(s_i|L)P(L|C)P(o_i|C)}{\sum_{C,L}  P(s_i|L)P(L|C)P(o_i|C) + \sum_{C,L}  P(s_i|L)P(L|C)P(o_j|C)}.$$
+Using the definition of $P(L|C)$ (given in Equation \ref{eq:mapping}) and the fact that we only have two possible categories in each modality ($L_1, L_2$ and $C_1, C_2$) we obtain:
+
+\begin{equation} \label{eq:special}
+P(o_i|s_i) = \frac{P(s_i|L_i)P(o_i|C_i) + P(s_i|L_j)P(o_i|C_j)}{[P(s_i|L_i)P(o_i|C_i) + P(s_i|L_j)P(o_i|C_j)] + [P(s_i|L_i)P(o_j|C_i) + P(s_i|L_j)P(o_j|C_j)]}
+\end{equation}
+
+In what follows, we compute the explicit expression of each conditional probability in Equation \ref{eq:special}.
+
+$P(s_i | L_i)$ is the probability that the sound $s_i$ was sampled from its correct category $L_i$.
+Using the fact that we assumed in Equation \ref{eq:sound} that this probability follows a normal distribution $\mathcal{N}(\mu_C, \sigma^2_C)$, we have:
+
+$$P(s_i|L_i) = \frac{1}{\sqrt{2\pi\sigma^2_{L_i}}}e^{-\frac{(s_i-\mu_{L_j})^2}{2\sigma^2_{L_i}}}.$$
+
+We use the symplifying assumption that $\sigma_{L_i} = \sigma_L$, an uncertainty common to all labels.
+$\sigma_L$ can be understood as characterizing general speech processing skills (at a given time in development).
+We obtain the following expression:
+
+$$P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{(s_i-\mu_{L_j})^2}{2\sigma^2_L}}.$$
+
+$s_i$ is supposed to be the prototyical instance of $L_i$, that is, $s_i=\mu_{L_j}$, leading to $$P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}}.$$
+
+Similarly, $$P(o_i | C_i) = P(o_j | C_j) = \frac{1}{\sqrt{2\pi\sigma^2_C}}.$$
+
+$P(s_i | L_j)$ is the probability that the sound $s_i$, though a perfect instance of $L_i$, could still be a mispronunced instance of the category $L_j$.
+The value of this probability depends on the extent to which the distributions of the categories $L_i$ and $L_j$ overlap with each other (Figure \@ref(fig:illus)).
+Using the normal distribution, we obtain the following expression: $$P(s_i| L_j) = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{(s_i-s_j)^2}{2\sigma^2_L}} = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{\Delta s^2}{2\sigma^2_L}}.$$
+
+Similarly, $$P(o_i| C_j) = P(o_j| C_i) = \frac{1}{\sqrt{2\pi\sigma^2_C}} e^{-\frac{\Delta o^2}{2\sigma^2_C}} $$
+
+Finally, we substitute all these expresisions in equation \ref{eq:special} above, leading to:
+
+$$P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}$$
+Which is the expression for Model 3 (Equatin \ref{eq:model3}).
+The expression for Model 2 (Equation \ref{eq:model2}) can be deduced from that of Model 3 by positing $\sigma= \sigma_L = \sigma_C$.
+The expression for Model 1 (Equation \ref{eq:model1}) is also derived from Model 3 by taking the limit when $\sigma_C \rightarrow 0$.
 

### 2020-03-20 journal/ms_blind.tex
revisions

@@
             pdftitle={Continuous developmental change explains discontinuities in word learning},
-            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
             pdfkeywords={word learning, cognitive development, computational modeling},
@@
 \setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
@@
 
-  \title{Continuous developmental change explains discontinuities in word
-learning}
-    \author{Abdellah Fourtassi\textsuperscript{1}, Sophie Regan\textsuperscript{1},
-\& Michael C. Frank\textsuperscript{1}}
+  \title{Continuous developmental change explains discontinuities in word learning}
+    \author{true \\ true \\ true}
     \date{}
 
-\shorttitle{Continuous Development of Word Learning}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Department of Psychology, Stanford University}
-\keywords{word learning, cognitive development, computational modeling}
-\usepackage{csquotes}
+% Manuscript styling
 \usepackage{upgreek}
@@
 
+% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
-
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\makeatother
+\shorttitle{Continuous Development of Word Learning}
+\author{Abdellah Fourtassi\textsuperscript{1}, Sophie Regan\textsuperscript{1}, \& Michael C. Frank\textsuperscript{1}}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Psychology, Stanford University}
+\authornote{
+
+None of the authors have any financial interest or a conflict of interest regarding this work and this submission.
+
+Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: afourtas@stanford.edu}
+\keywords{word learning, cognitive development, computational modeling}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
+\usepackage{csquotes}
 \usepackage[titles]{tocloft}
@@
 \usepackage[sortcites=false,sorting=none]{biblatex}
-
-\authornote{
-
-None of the authors have any financial interest or a conflict of
-interest regarding this work and this submission.
-
-Correspondence concerning this article should be addressed to Abdellah
-Fourtassi, Postal address. E-mail:
-\href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}}
+\usepackage{xcolor}
 
 \abstract{
-``Cognitive development is often characterized in terms of
-discontinuities, but these discontinuities can sometimes be apparent
-rather than actual and can arise from continuous developmental change.
-To explore this idea, we use as a case study the finding by Stager and
-Werker (1997) that children's early ability to distinguish similar
-sounds does not automatically translate into word learning skills. Early
-explanations proposed that children may not be able to encode subtle
-phonetic contrasts when learning novel word meanings, thus suggesting a
-discontinuous/stage-like pattern of development. However, later work has
-revealed (e.g., through using more precise testing methods) that
-children do encode such contrasts, thus favoring a continuous pattern of
-development. Here we propose a probabilistic model that represents word
-knowledge in a graded fashion and characterizes developmental change as
-improvement in the precision of this graded knowledge. Our model
-explained previous findings in the literature and provided a new
-prediction --- the referents' visual similarity modulates word learning
-accuracy. The models' predictions were corroborated by human data we
-collected from both preschool children and adults. The broader impact of
-this work is to show that computational models, such as ours, can help
-us explore the extent to which episodes of cognitive development that
-are typically thought of as discontinuities may emerge from simpler,
-continuous mechanisms.''
-
+``Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
+To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
+Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development.
+However, later work has revealed (e.g., through using more precise testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development.
+Here we propose a probabilistic model that represents word knowledge in a graded fashion and characterizes developmental change as improvement in the precision of this graded knowledge.
+Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word learning accuracy.
+The models' predictions were corroborated by human data we collected from both preschool children and adults.
+The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms.''
 }
 
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{proposition}{Proposition}[section]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[section]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[section]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
 \begin{document}
@@
 
-\section{Introduction}\label{introduction}
-
-Cognitive development is often characterized in terms of a succession of
-discontinuous stages. In Piaget's initial conception, these stages
-cross-cut different aspects of cognition (Piaget, 1954); in more modern
-conceptions, distinct domains are often thought to progress on their own
-timeline (e.g., Carey, Zaitchik, \& Bascandziev, 2015). Although
-intuitively appealing, this sort of stage theory can be challenging to
-integrate with theories of learning, which typically posit that
-knowledge and skills improve incrementally with experience. Indeed, one
-of the central challenges of cognitive development has been to explain
-transitions between stages which appear to be qualitatively different
-(Carey, 2009).
-
-Nevertheless, at least in some cases, development may only appear to be
-stage-like. Some discontinuities may be related to how we measure a
-specific skill. Other discontinuities may emerge due to statistical
-thresholding (e.g., an experimental p-value of \(p < .05\) for one age
-group but not another) which can create a spurious dichotomy between
-success and failure in observing a given behavior. In such cases,
-positing discontinuous stages is unnecessary. Instead, a continuous
-model --- involving similar representations across the lifespan --- may
-provide a simpler and more transparent account of development (cf.
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Cognitive development is often characterized in terms of a succession of discontinuous stages.
+In Piaget's initial conception, these stages cross-cut different aspects of cognition (Piaget, 1954); in more modern conceptions, distinct domains are often thought to progress on their own timeline (e.g., Carey, Zaitchik, \& Bascandziev, 2015).
+Although intuitively appealing, this sort of stage theory can be challenging to integrate with theories of learning, which typically posit that knowledge and skills improve incrementally with experience.
+Indeed, one of the central challenges of cognitive development has been to explain transitions between stages which appear to be qualitatively different (Carey, 2009).
+
+Nevertheless, at least in some cases, development may only appear to be stage-like.
+Some discontinuities may be related to how we measure a specific skill.
+Other discontinuities may emerge due to statistical thresholding (e.g., an experimental p-value of \(p < .05\) for one age group but not another) which can create a spurious dichotomy between success and failure in observing a given behavior.
+In such cases, positing discontinuous stages is unnecessary.
+Instead, a continuous model --- involving similar representations across the lifespan --- may provide a simpler and more transparent account of development (cf.
 McMurray, 2007; Shultz, Schmidt, Buckingham, \& Mareschal, 1995).
 
-To explore this point computationally, we use a case study from word
-learning literature. Stager and Werker (1997) first showed that
-children's early ability to distinguish similar sounds does not
-automatically translate into word learning skills. The authors measured
-word learning using an audio-visual habituation Switch task. First,
-infants are familiarized with two word-object pairings (e.g., label 1
-with object 1 and label 2 with object 2). Second, they are tested using
-two types of trials. The control \enquote{same} trial consists of a
-correct pairing (e.g., label 1 with object 1) and the \enquote{switch}
-trial consists of a wrong pairing (e.g., label 1 with object 2). If
-babies have correctly learned the association during the habituation,
-they are supposed to be surprised by the \enquote{switch} trial and not
-by the \enquote{same} trial. The former should thus result in a greater
-looking time compared to the latter (Werker, Cohen, Lloyd, Casasola, \&
-Stager, 1998).
-
-Though infants around 14-month old can distinguish perceptually similar
-sound pairs such as \enquote{dih} and \enquote{bih}, they appear to fail
-in mapping this pair to two different objects in the switch task. This
-failure was initially taken as evidence that 14-month olds do not encode
-subtle sounds during meaning learning (Pater, Stager, \& Werker, 2004;
-Stager \& Werker, 1997). This interpretation suggested a
-discontinuous/stage-like pattern of development whereby younger children
-fail to encode the contrastive phonetic detail, whereas older children,
-around 17 months, typically do (Werker, Fennell, Corcoran, \& Stager,
-2002).
-
-The initial discontinuous interpretation has been challenged by
-subsequent work. For instance, Yoshida, Fennell, Swingley, and Werker
-(2009) investigated whether failure in the Switch task reflects a lack
-of sound encoding during \emph{habituation}, or whether it is only due
-to the nature of the \emph{testing} method which does not allow learning
-below a certain threshold to be detected. They used the same habituation
-procedure as Stager and Werker (1997), but instead of comparing the
-looking times in \enquote{same} and \enquote{switch} trials, they tested
-infants using a two-alternative choice task comparing fixations to
-target and distractor objects (Fernald, Perfors, \& Marchman, 2006;
-Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987). Using this testing
-method, researchers found evidence for learning even in 14-month olds.
-
-Another challenge to the discontinuous account of development came from
-adult studies. If the mismatch between sound discrimination and word
-learning is only a stage in early infancy, then this mismatch should
-disappear by adulthood. Nonetheless, even adults show patterns of
-learning that mirror those shown by 14-month-olds when the sound
-contrasts are more challenging (Pajak, Creel, \& Levy, 2016; White, Yee,
-Blumstein, \& Morgan, 2013).
-
-Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al.,
-2009) proposed that word knowledge may not be encoded in a binary
-fashion, i.e., it is not the case that children either succeed or fail
-in encoding minimal contrast when learning the meanings. Rather, they
-may be encoding this knowledge in a graded fashion (see Munakata (2001)
-for an detailed discussion of a similar view). Thus, development does
-not so much involve a qualitative shift (i.e., a sudden emergence of an
-ability that did not exist before) as much as it consists in the
-continuous refinement of initially noisy knowledge.
+To explore this point computationally, we use a case study from word learning literature.
+Stager \& Werker (1997) first showed that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
+The authors measured word learning using an audio-visual habituation Switch task.
+First, infants are familiarized with two word-object pairings (e.g., label 1 with object 1 and label 2 with object 2).
+Second, they are tested using two types of trials.
+The control \enquote{same} trial consists of a correct pairing (e.g., label 1 with object 1) and the \enquote{switch} trial consists of a wrong pairing (e.g., label 1 with object 2).
+If babies have correctly learned the association during the habituation, they are supposed to be surprised by the \enquote{switch} trial and not by the \enquote{same} trial.
+The former should thus result in a greater looking time compared to the latter (Werker, Cohen, Lloyd, Casasola, \& Stager, 1998).
+
+Though infants around 14-month old can distinguish perceptually similar sound pairs such as \enquote{dih} and \enquote{bih}, they appear to fail in mapping this pair to two different objects in the switch task.
+This failure was initially taken as evidence that 14-month olds do not encode subtle sounds during meaning learning (Pater, Stager, \& Werker, 2004; Stager \& Werker, 1997).
+This interpretation suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children, around 17 months, typically do (Werker, Fennell, Corcoran, \& Stager, 2002).
+
+The initial discontinuous interpretation has been challenged by subsequent work.
+For instance, Yoshida, Fennell, Swingley, \& Werker (2009) investigated whether failure in the Switch task reflects a lack of sound encoding during \emph{habituation}, or whether it is only due to the nature of the \emph{testing} method which does not allow learning below a certain threshold to be detected.
+They used the same habituation procedure as Stager \& Werker (1997), but instead of comparing the looking times in \enquote{same} and \enquote{switch} trials, they tested infants using a two-alternative choice task comparing fixations to target and distractor objects (Fernald, Perfors, \& Marchman, 2006; Golinkoff, Hirsh-Pasek, Cauley, \& Gordon, 1987).
+Using this testing method, researchers found evidence for learning even in 14-month olds.
+
+Another challenge to the discontinuous account of development came from adult studies.
+If the mismatch between sound discrimination and word learning is only a stage in early infancy, then this mismatch should disappear by adulthood.
+Nonetheless, even adults show patterns of learning that mirror those shown by 14-month-olds when the sound contrasts are more challenging (Pajak, Creel, \& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).
+
+Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009) proposed that word knowledge may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
+Rather, they may be encoding this knowledge in a graded fashion (see Munakata (2001) for an detailed discussion of a similar view).
+Thus, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy knowledge.
 
 Many different computational formalisms can represent graded knowledge.
-Here we use probabilistic models, a formalism that allows both easy
-examination of internal representations and quantification of the
-robustness of these representations. Word knowledge can be characterized
-with a probability distribution over sound instances organized in a
-similarity space. The probability is highest at the most typical sound
-instance. It decreases as the instance becomes less typical. The
-precision of word knowledge can be characterized by whether it tolerates
-slightly atypical pronunciations. This tolerance is captured formally by
-the variance of the probability distribution: larger variance indicates
-higher tolerance and lower precision, whereas smaller variance indicates
-lower tolerance and higher precision (for an illustration, see Figure
-\ref{fig:illus} top and right panels).
-
-This general framework --- in which the precision of word knowledge is
-characterized with the variance of a probability distribution --- can
-already provide an intuitive way of thinking about several findings. In
-particular, unlike the binary view, the probabilistic view allows for
-the possibility of word knowledge being both successful and noisy. This
-new understanding can provide an account for the fact that children show
-evidence of learning in some testing condition (e.g., Yoshida et al.,
-2009) but not in others (e.g., Stager \& Werker, 1997) --- depending on
-the precision of the measurement.
-
-In a word-pair learning paradigm, children are supposed to associate one
-label, e.g., \enquote{bih}, with object 1 and a second label, e.g.,
-\enquote{dih}, with object 2. Infants may succeed in learning both
-associations. Nevertheless, the variance with which the pair of words
-are encoded can still be large, causing their probability distributions
-to overlap (Figure \ref{fig:illus}, top). The way this (noisy) knowledge
-is probed can lead to different results.
-
-In the Switch task (Stager \& Werker, 1997), children are understood to
-succeed if they reject a wrong association (e.g., \enquote{bih} with
-object 2). However, a large overlap between \enquote{bih} and
-\enquote{dih} means that \enquote{bih} is itself a plausible
-mispronunciation of \enquote{dih}. The wrong association may not be
-rejected by children because the speaker could have said \enquote{bih}
-but meant \enquote{dih}. In the two-alternative choice task (Yoshida et
-al., 2009), children do not have to reject the wrong association; they
-only need to show a preference, albeit small, for the correct one. Thus,
-unlike the Switch, this testing method allows us to see subtle evidence
-of learning even with a large overlap. For example, given the label
-\enquote{bih}, children are supposed to pick which object is a better
-match to this label. Though it is possible that the speaker said
-\enquote{bih} and meant \enquote{dih}, it is \emph{more} likely that the
-speaker both said and meant \enquote{bih} --- this higher probability
-leads to a preference for the correct object.
-
-In addition to explaining the difference in behavior across the Switch
-and the preferential looking tasks, the probabilistic account explains
-difference in behavior within the same task. In particular, when the
-labels are quite distinct in the perceptual space (\enquote{lif} vs.
-\enquote{neem}), the probabilistic distributions do not overlap as much
-as in the case of similar-sounding words (Figure \ref{fig:illus}, left).
-This fact means that the learners will have less tolerance for the wrong
-association, leading to a successful rejection in the Switch task (as
-was reported by Stager and Werker (1997) and subsequent studies using
-the same paradigm). Further, distinctiveness can be enhanced even for
-minimally different sounds when other cues highlight their difference
-(Dautriche, Swingley, \& Christophe, 2015; Rost \& McMurray, 2009, 2010;
-Thiessen, 2007; Yeung \& Werker, 2009).
-
-In this framework, developmental change can be understood as an increase
-in the precision (i.e., a decrease in the variance) of the probabilistic
-knowledge, leading to a lower overlap between the distributions of
-similar-sounding words (Figure \ref{fig:illus}, right). Importantly, a
-more precise representation still has a non-zero variance. Thus,
-learning difficulties can still be induced with challenging stimuli or
-in cognitively demanding situations as was demonstrated in adults
-studies (Pajak et al., 2016; White et al., 2013).
-
-\subsection{The current study}\label{the-current-study}
-
-The probabilistic account has been put forward to explain patterns of
-learning and development at the qualitative level. However, it is
-crucial to have a precise computational instantiation of this account
-which would help us 1) test this theoretical hypothesis more directly
-and 2) identify the particular parameters that are the locus of
-developmental change. One previous study attempted to provide such a
-computational instantiation (Hofer \& Levy, 2017). However, this
-previous work was designed with the goal of reproducing the results of a
-specific study (Pajak et al., 2016) which focused on explaining the
-mismatch between speech perception and word learning in adults rather
-than on exploring the mechanism of development.
-
-The present work proposes a model of word-pair learning based on the
-probabilistic account. We tested the ability of this model to both
-\emph{explain} various findings in previous experiments in both children
-and adults (e.g., the fact that similar words are harder to learn than
-different words) and to \emph{predict} new learning patterns that have
-not been tested before. In particular, we test the prediction that
-referent similarity (i.e., the confusability of pictures referred to by
-novel words) should play an identical computational role to word form
-similarity in predicting recognition difficulty. Although this
-prediction is intuitive, to our knowledge, it has never been tested.
-Finally, we explore the extent to which the probabilistic account allows
-us to understand development in terms of as a continuous refinement in
-similar representations across the lifespan.
-
-The paper is organized as follows. First, we introduce the model and we
-explain how it allows us to characterize behavior in a
-word-pair-learning paradigm. Then we explore the predictions of the
-model through simulating its behavior across different parameter
-settings. Next, we quantify the extent to which the model's predictions
-account for human data we collected from both preschool children and
-adults. Finally, we discuss the results in the light of existing
-accounts of word development.
+Here we use probabilistic models, a formalism that allows both easy examination of internal representations and quantification of the robustness of these representations.
+Word knowledge can be characterized with a probability distribution over sound instances organized in a similarity space.
+The probability is highest at the most typical sound instance.
+It decreases as the instance becomes less typical.
+The precision of word knowledge can be characterized by whether it tolerates slightly atypical pronunciations.
+This tolerance is captured formally by the variance of the probability distribution: larger variance indicates higher tolerance and lower precision, whereas smaller variance indicates lower tolerance and higher precision (for an illustration, see Figure \ref{fig:illus} top and right panels).
+
+This general framework --- in which the precision of word knowledge is characterized with the variance of a probability distribution --- can already provide an intuitive way of thinking about several findings.
+In particular, unlike the binary view, the probabilistic view allows for the possibility of word knowledge being both successful and noisy.
+This new understanding can provide an account for the fact that children show evidence of learning in some testing condition (e.g., Yoshida et al., 2009) but not in others (e.g., Stager \& Werker, 1997) --- depending on the precision of the measurement.
+
+In a word-pair learning paradigm, children are supposed to associate one label, e.g., \enquote{bih}, with object 1 and a second label, e.g., \enquote{dih}, with object 2.
+Infants may succeed in learning both associations.
+Nevertheless, the variance with which the pair of words are encoded can still be large, causing their probability distributions to overlap (Figure \ref{fig:illus}, top).
+The way this (noisy) knowledge is probed can lead to different results.
+
+In the Switch task (Stager \& Werker, 1997), children are understood to succeed if they reject a wrong association (e.g., \enquote{bih} with object 2).
+However, a large overlap between \enquote{bih} and \enquote{dih} means that \enquote{bih} is itself a plausible mispronunciation of \enquote{dih}.
+The wrong association may not be rejected by children because the speaker could have said \enquote{bih} but meant \enquote{dih}.
+In the two-alternative choice task (Yoshida et al., 2009), children do not have to reject the wrong association; they only need to show a preference, albeit small, for the correct one.
+Thus, unlike the Switch, this testing method allows us to see subtle evidence of learning even with a large overlap.
+For example, given the label \enquote{bih}, children are supposed to pick which object is a better match to this label.
+Though it is possible that the speaker said \enquote{bih} and meant \enquote{dih}, it is \emph{more} likely that the speaker both said and meant \enquote{bih} --- this higher probability leads to a preference for the correct object.
+
+In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains difference in behavior within the same task.
+In particular, when the labels are quite distinct in the perceptual space (\enquote{lif} vs.
+\enquote{neem}), the probabilistic distributions do not overlap as much as in the case of similar-sounding words (Figure \ref{fig:illus}, left).
+This fact means that the learners will have less tolerance for the wrong association, leading to a successful rejection in the Switch task (as was reported by Stager \& Werker (1997) and subsequent studies using the same paradigm).
+Further, distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference (Dautriche, Swingley, \& Christophe, 2015; Rost \& McMurray, 2009, 2010; Thiessen, 2007; Yeung \& Werker, 2009).
+
+In this framework, developmental change can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic knowledge, leading to a lower overlap between the distributions of similar-sounding words (Figure \ref{fig:illus}, right).
+Importantly, a more precise representation still has a non-zero variance.
+Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adults studies (Pajak et al., 2016; White et al., 2013).
+
+\hypertarget{the-current-study}{%
+\subsection{The current study}\label{the-current-study}}
+
+The probabilistic account was used before to explain patterns of learning and development at the qualitative level (e.g., Swingley, 2007).
+However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.
+One previous study attempted to provide such a computational instantiation (Hofer \& Levy, 2017).
+However, this previous work was designed with the goal of reproducing the results of a specific study (Pajak et al., 2016) which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
+
+The present work proposes a model of word-pair learning based on the probabilistic account.
+We tested the ability of this model to both \emph{explain} various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to \emph{predict} new learning patterns that have not been tested before.
+In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting recognition difficulty.
+Although this prediction is intuitive, to our knowledge, it has never been tested.
+Finally, we explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.
+
+The paper is organized as follows.
+First, we introduce the model and we explain how it allows us to characterize behavior in a word-pair-learning paradigm.
+Then we explore the predictions of the model through simulating its behavior across different parameter settings.
+Next, we quantify the extent to which the model's predictions account for human data we collected from both preschool children and adults.
+Finally, we discuss the results in the light of existing accounts of word development.
 
@@
 
-\section{Model}\label{model}
-
-\subsection{Probabilistic structure}\label{probabilistic-structure}
-
-Our model consists of a set of variables describing the general process
-of spoken word recognition in a referential situation. These variables
-are related in a way that reflects the simple generative scenario
-represented graphically in Figure \ref{fig:model}. When a speaker utters
-a sound in the presence of an object, the observer assumes that the
-object \(o\) activated the concept \(C\) in the speaker's mind. The
-concept prompted the corresponding label \(L\). Finally, the label was
-physically instantiated by the sound \(s\).
+\hypertarget{model}{%
+\section{Model}\label{model}}
+
+\hypertarget{probabilistic-structure}{%
+\subsection{Probabilistic structure}\label{probabilistic-structure}}
+
+Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation.
+These variables are related in a way that reflects the simple generative scenario represented graphically in Figure \ref{fig:model}.
+When a speaker utters a sound in the presence of an object, the observer assumes that the object \(o\) activated the concept \(C\) in the speaker's mind.
+The concept prompted the corresponding label \(L\).
+Finally, the label was physically instantiated by the sound \(s\).
 
@@
 
-A similar probabilistic structure was used by Lewis and Frank (2013) to
-model concept learning, and by Hofer and Levy (2017) to model spoken
-word learning. However, the first study assumed that the sounds are
-heard unambiguously, and the second assumed the concepts are observed
-unambiguously. In our model, we assume that both labels and concepts are
-observed with a certain amount of perceptual noise, which we assume, for
-simplicity, is captured by a normal distribution:
+A similar probabilistic structure was used by Lewis \& Frank (2013) to model concept learning, and by Hofer \& Levy (2017) to model spoken word learning.
+However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously.
+In our model, we assume that both labels and concepts are categories with possibly overlapping distributions.
+In other words, we allow the model to account for the --- more realistic --- possibility that an instances of a given categories (e.g.,\enquote{bin}) can be mistaken for an instance of a neighboring category (e.g., \enquote{din}), albeit with a smaller probability.
+We assume, for simplicity, that this probability is captured by a normal distribution\footnote{\textcolor{red}{We used a normal distribution to simplify the mathematical derivations.
+This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}}:
 
@@
 
-Finally, we assume there to be one-to-one mappings between concepts and
-labels and that observers have successfully learned these mappings
-during the exposure phase:
-
-\begin{equation}
+Finally, we assume there to be one-to-one mappings between concepts and labels and that observers have successfully learned these mappings during the exposure phase:
+\begin{equation}\label{eq:mapping}
 P(L_i|C_j) = 
@@
 
-\subsection{Inference}\label{inference}
-
-In our canonical inference case, the learner hears a sound \(s\) and has
-to decide which object \(o\) provides an optimal match to this sound
-(see Figure \ref{fig:task}). To this end, they must compute the
-probability \(P(o|s)\) for all possible objects. This probability can be
-computed by summing over all possible concepts and labels:
+\hypertarget{inference}{%
+\subsection{Inference}\label{inference}}
+
+In our canonical inference case, the learner hears a sound \(s\) and has to decide which object \(o\) provides an optimal match to this sound (see Figure \ref{fig:task}).
+To this end, they must compute the probability \(P(o|s)\) for all possible objects.
+This probability can be computed by summing over all possible concepts and labels:
 
@@
 
-Using the fact that \(P(o,C,L|s) = \frac{P(o,C,L,s)}{P(s)}\) and that
-\(P(s)\) does not depend on \(o\), we arrive at the equation:
+Using the fact that \(P(o,C,L|s) = \frac{P(o,C,L,s)}{P(s)}\) and that \(P(s)\) does not depend on \(o\), we arrive at the equation:
 
@@
 
-The joint probability \(P(o,C,L,s)\) is obtained by factoring the
-graphical model in Figure \ref{fig:model}:
+The joint probability \(P(o,C,L,s)\) is obtained by factoring the graphical model in Figure \ref{fig:model}:
 
@@
 
-By subtituting this term in the expression of the joint distribution
-\(P(o,C,L,S)\) we obtain:
+By subtituting this term in the expression of the joint distribution \(P(o,C,L,S)\) we obtain:
 
@@
 
-Finally, assuming that the concepts' prior probability \(P(C)\) is
-uniformly
-distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in our experiment.}
-we obtain the following expression, where all conditional dependencies
-are now well defined:
+Finally, assuming that the concepts' prior probability \(P(C)\) is uniformly distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in our experiment.} we obtain the following expression, where all conditional dependencies are now well defined:
 
@@
 
-\subsection{Task and model
-predictions}\label{task-and-model-predictions}
+\hypertarget{task-and-model-predictions}{%
+\subsection{Task and model predictions}\label{task-and-model-predictions}}
 
@@
 
-We use the model to predict word learning in a task similar to the one
-introduced by Stager and Werker (1997). We used a modified version of
-the task where the testing method consists in a two-alternative
-forced-choice (Yoshida et al., 2009). In this task, participants are
-first exposed to two different word-object pairings (e.g., \enquote{lif}
-- object 1, \enquote{neem} - object 2). The word-object associations are
-introduced sequentially. After this exposure phase, participants perform
-a series of test trials. In each of these trials, one of the two sounds
-is uttered (e.g., \enquote{lif}) and participants choose the
-corresponding object from the two alternatives. An overview of the task
-is shown in Figure \ref{fig:task}.
-
-\subsubsection{Model 1}\label{model-1}
-
-From the general expression \ref{eq:general}, we derive three exact
-analytical solutions instantiating different learning assumptions.
-Recall from expressions \ref{eq:object} and \ref{eq:sound} that
-\(P(o|C)\) and \(P(s|L)\) have parameters \(\sigma_C\) and \(\sigma_L\),
-respectively, that control perceptual uncertainty. The first solution is
-derived by assuming that the labels are recovered from sounds with a
-certain level of uncertainty \(\sigma_L > 0\), but that concepts are
-unambiguously recovered from the observed objects, i.e.,
-\(\sigma_C \rightarrow 0\). This assumption has been made --- whether
-implicitly or explicitly --- by most previous work in this line of
-research. For example, in Stager and Werker (1997), the objects were
-quite dissimilar. Thus, the assumption that they were easily
-discriminated by infants seems relatively well justified. One important
-implication of this assumption is that only the similarity of word
-sounds modulates success in word learning, not the similarity of the
-referents (as long as these referents are differentiated perceptually).
-This assumption yields the following probability function:
+We use the model to predict word learning in a task similar to the one introduced by Stager \& Werker (1997).
+We used a modified version of the task where the testing method consists in a two-alternative forced-choice (Yoshida et al., 2009).
+In this task, participants are first exposed to two different word-object pairings (e.g., \enquote{lif} - object 1, \enquote{neem} - object 2).
+The word-object associations are introduced sequentially.
+After this exposure phase, participants perform a series of test trials.
+In each of these trials, one of the two sounds is uttered (e.g., \enquote{lif}) and participants choose the corresponding object from the two alternatives.
+An overview of the task is shown in Figure \ref{fig:task}.
+
+From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions.
+
+\hypertarget{model-1}{%
+\subsubsection{Model 1}\label{model-1}}
+
+Recall from expressions \ref{eq:object} and \ref{eq:sound} that \(P(o|C)\) and \(P(s|L)\) have parameters \(\sigma_C\) and \(\sigma_L\), respectively, that control for uncertainty.
+The first solution/model is derived by assuming that the labels are recovered from sounds with a certain level of uncertainty \(\sigma_L > 0\), but that concepts are unambiguously recovered from the observed objects, i.e., \(\sigma_C \rightarrow 0\).
+This assumption has been made --- whether implicitly or explicitly --- by most previous work in this line of research.
+For example, in Stager \& Werker (1997), the objects were quite dissimilar.
+Thus, the assumption that they were easily discriminated by infants seems relatively well justified.
+One important implication of this assumption is that only the similarity of word sounds modulates performance in word learning, not the similarity of the referents (as long as these referents are differentiated perceptually).
+
+This assumption yields the following probability function of choosing the correct object \(o_i\) given the correspondding label instance \(s_i\), where \(i \in \{1,2\}\) (see the Appendix for the full mathematical derivation):
 
 \begin{equation} \label{eq:model1}
-P(o_T|s)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
+P(o_i|s_i)= \frac{1}{1 + e^{-\frac{\Delta s^2}{2\sigma_L^2}}}
 \end{equation}
 
-where \(\Delta s = s_2-s_1\).
-
-\subsubsection{Model 2}\label{model-2}
-
-The second solution is derived by making the more general assumption
-that both the labels and the concepts are recovered with noise from the
-sounds and objects. We first introduce the simplifying assumption that
-the label-related uncertainty \(\sigma_L\) and the concept-related
-uncertainty \(\sigma_C\) are of a similar magnitude, i.e.,
-\(\sigma_C \approx \sigma_L = \sigma\). This assumption makes the
-prediction that the sound similarity and the object similarity impact
-word learning accuracy in exactly the same way. Furthermore, it allows
-us to study the behavior of the model with only one free parameter, an
-important consideration given the small number of datapoints available
-from any given infant experiment.
+where \(\Delta s = s_2-s_1\) is the perceptual sound distance between the pair of sounds that we refer to as \(s_1\) and \(s_2\).
+These distances were measured empirically as shown in Figure \ref{fig:stim}.
+
+\hypertarget{model-2}{%
+\subsubsection{Model 2}\label{model-2}}
+
+The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with noise from the sounds and objects.
+We first introduce the simplifying assumption that the label-related uncertainty \(\sigma_L\) and the concept-related uncertainty \(\sigma_C\) are of a similar magnitude, i.e., \(\sigma_C \approx \sigma_L = \sigma\).
+This assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way.
+Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given infant experiment.
 
 \begin{equation} \label{eq:model2}
-P(o_T|s)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
+P(o_i|s_i)= \frac{1 + e^{- \frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}}{1 + e^{-\frac{\Delta s^2 + \Delta o^2}{2\sigma^2}}+ e^{-\frac{\Delta s^2}{2\sigma^2}} + e^{-\frac{\Delta o^2}{2\sigma^2}}}
 \end{equation}
 
-\subsubsection{Model 3}\label{model-3}
-
-We finally derive the third (and most general) solution which allows
-label- and concept-related uncertainties to vary independently.
+\hypertarget{model-3}{%
+\subsubsection{Model 3}\label{model-3}}
+
+We finally derive the third (and most general) solution which allows label- and concept-related uncertainties to vary independently.
 
 \begin{equation} \label{eq:model3}
-P(o_T|s)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
+P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}
 \end{equation}
 
-In order to understand the predictions of the models (especially the
-more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation}
-show simulations of the accuracy \(P(o_T|s)\) as a function of the
-distinctiveness parameters (\(\Delta s\) and \(\Delta o\)) and the
-uncertainty parameters \(\sigma_L\) and \(\sigma_C\).
-
-\begin{figure}[htbp]
+In order to understand the predictions of the models (especially the more general ones, i.e., Model 2 and 3), Figure \ref{fig:simulation} show simulations of the accuracy \(P(o_i|s_i)\) as a function of the distinctiveness parameters (\(\Delta s\) and \(\Delta o\)) and the uncertainty parameters \(\sigma_L\) and \(\sigma_C\).
+
+\begin{figure}
 \centering
 \includegraphics{ms_blind_files/figure-latex/simulation-1.pdf}
-\caption{\label{fig:simulation}The predicted probability of accurate
-responses in the testing phase as a function of stimuli distinctiveness
-\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
-(For simplicity, we use model 2, which assumes that
-\(\sigma\)=\(\sigma_C\)=\(\sigma_L\)). Dashed line represents chance.}
+\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness \(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\) (For simplicity, we use model 2, which assumes that \(\sigma\)=\(\sigma_C\)=\(\sigma_L\)).
+Dashed line represents chance.}
 \end{figure}
 
-The simulations explain two experimental results from previous studies
-and make one new prediction:
+The simulations explain two experimental results from previous studies and make one new prediction:
 
@@
 \item
-  For fixed values of \(\Delta o\) and \(\sigma\), the probability of
-  accurate responses increases as a function of \(\Delta s\). This
-  pattern accounts for the fact that similar sounds are generally more
-  challenging to learn than different sounds for both children (Stager
-  \& Werker, 1997) and adults (Pajak et al., 2016).
+  For fixed values of \(\Delta o\) and \(\sigma\), the probability of accurate responses increases as a function of \(\Delta s\).
+This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both children (Stager \& Werker, 1997) and adults (Pajak et al., 2016).
 \item
-  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases
-  when the representational uncertainty \(\sigma\) decreases. This
-  observation provides a simple model for developmental change. Younger
-  children have noisier representations (see Swingley, 2007; Yoshida et
-  al., 2009), which leads to lower word recognition accuracy, especially
-  for similar-sounding words.
+  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases when the representational uncertainty \(\sigma\) decreases.
+This observation provides a simple model for developmental change.
+Younger children have noisier representations (see Swingley, 2007; Yoshida et al., 2009), which leads to lower word recognition accuracy, especially for similar-sounding words.
 \item
-  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases
-  with the visual distance between the semantic referents \(\Delta o\).
-  This is a new prediction that our model makes. Previous work studied
-  the effect of several bottom-up and top-down properties in
-  disambiguating similar sounding words (e.g., Fennell \& Waxman, 2010;
-  Rost \& McMurray, 2009; Thiessen, 2007), but to our knowledge, no
-  previous study in the literature tested the effect of the visual
-  distance between the semantic referents.
+  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases with the visual distance between the semantic referents \(\Delta o\).
+This is a new prediction that our model makes.
+Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (e.g., Fennell \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007), but to our knowledge, no previous study in the literature tested the effect of the visual distance between the semantic referents.
 \end{enumerate}
 
-\section{Experiment}\label{experiment}
-
-In this experiment, we tested participants in the word learning task
-introduced above (Figure \ref{fig:task}). More precisely, we explored
-the predictions related to both distinctiveness and precision. Sound
-similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were
-varied simultaneously in a within-subject design. Two age groups
-(preschool children and adults) were tested on the same task\footnote{This
-  four-condition within-subject design is relatively novel for
-  preschoolers, but we followed the tablet paradigm (e.g., Frank,
-  Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to
-  gather a relatively large number of trials from each child.} to
-explore whether development can be characterized with the uncertainty
-parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size,
-exclusion criteria, and the model's main predictions were
-pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
-
-\subsection{Methods}\label{methods}
-
-\subsubsection{Participants}\label{participants}
-
-We report data from \(N=\) 63 children ages 4-5 years from a nursery
-school. An additional \(N=\) 39 children participated but were removed
-from analyses (using preregistered exclusion criteria) because they were
-not above chance on the catch trials due to the challenging nature of
-our procedure (see below). We also report data from \(N=\) 74 adult
-participants tested on Amazon Mechanical Turk. An additional \(N=\) 26
-were tested but removed from analyses (again, using preregistered
-exclusion criteria) because they had low scores on the catch trials or
-because they were familiar with the non-English sound stimuli we used in
-the adult experiment.
-
-\subsubsection{Stimuli and similarity
-rating}\label{stimuli-and-similarity-rating}
-
-The sound stimuli were generated using the MBROLA Speech Synthesizer
-(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
-generated three kinds of nonsense word pairs which varied in their
-degree of perceptual similarity to English speakers: 1) \emph{different}
-pairs: \enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2)
-\emph{intermediate} pairs: \enquote{aka}/\enquote{ama} and
-\enquote{ada}/\enquote{aba}, and 3) \emph{similar} non-English pairs:
-\enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and
-\enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
-
-As for the objects, we used the Dynamic Stimuli javascript
-library\footnote{https://github.com/erindb/stimuli} which allowed us to
-generate objects in four different categories: \enquote{tree,}
-\enquote{bird,} \enquote{bug,} and \enquote{fish.} These categories were
-described to participants as naturally occurring kinds on an alien
-planet. In each category, we generated \emph{different},
-\emph{intermediate}, and \emph{similar} pairs by manipulating a
-continuous property controlling features of the category's shape (e.g.,
-body stretch or head fatness).
-
-In order to validate and quantify our similarity scales, we ran a
-separate survey on Amazon Mechanical Turk where we asked \(N=20\) adults
-participants to evaluate the similarity of each sound and object pair on
-a 7-point scale. Data are shown in Figure \ref{fig:stim} where we scaled
-responses within the range {[}0,1{]} for each stimulus group. We used
-these data in all models as an empirical measurement of the perceptual
-distance between the sound pairs and the object pairs. The use of
-empirical measurement allows us to eliminate \(\Delta s\) and
-\(\Delta s\) as free parameters (see Frank and Goodman (2012) and Xu and
-Tenenbaum (2007) for a similar strategy).
-
-\subsubsection{Design}\label{design}
-
-Each age group saw only two of the three levels of similarity described
-in the previous sub-section: \emph{different} vs. \emph{intermediate}
-for the preschoolers, and \emph{intermediate} vs. \emph{similar} for
-adults. We made this choice in light of pilot studies showing that
-adults were at ceiling with \emph{different} sounds/objects, and
-children were at chance with the \emph{similar} sounds/objects. That
-said, this difference in the level of similarity is accounted for in the
-model: We used empirical distance measurement to fill in the appropriate
-values of \(\Delta s\) and \(\Delta o\) for each age group.
+\hypertarget{experiment}{%
+\section{Experiment}\label{experiment}}
+
+In this experiment, we tested participants in the word learning task introduced above (Figure \ref{fig:task}).
+More precisely, we explored the predictions related to both distinctiveness and precision.
+Sound similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were varied simultaneously in a within-subject design.
+Two age groups (preschool children and adults) were tested on the same task\footnote{This four-condition within-subject design is relatively novel for preschoolers, but we followed the tablet paradigm (e.g., Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to gather a relatively large number of trials from each child.} to explore whether development can be characterized with the uncertainty parameters, \(\sigma_C\) and \(\sigma_L\).
+The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
+
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
+
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
+
+We report data from \(N=\) 63 children ages 4-5 years from a nursery school.
+An additional \(N=\) 39 children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
+We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk.
+An additional \(N=\) 26 were tested but removed from analyses (again, using preregistered exclusion criteria) because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.
+
+\hypertarget{stimuli-and-similarity-rating}{%
+\subsubsection{Stimuli and similarity rating}\label{stimuli-and-similarity-rating}}
+
+The sound stimuli were generated using the MBROLA Speech Synthesizer (Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996).
+We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) \emph{different} pairs: \enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2) \emph{intermediate} pairs: \enquote{aka}/\enquote{ama} and \enquote{ada}/\enquote{aba}, and 3) \emph{similar} non-English pairs\footnote{For the intermediate/similar pairs, we made the choice of using a VCV (Vowel-Consonant-Vowel) structure in order to emphasize the phonemic difference in the minimal pairs, especially for the non-native contrasts.
+However, as one reviwer rightfully pointed out to us, this structure could influence word leaning performance since it is not common in English.
+Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand.
+However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
+For the simialr pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
+In this respect, we took inspiration from the work of Pajak et al.
+(2016).
+We refer the reader to that paper for a lengthy discussion of the literature on (and implications for) L2 phoneme perception.
+
+As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: \enquote{tree,} \enquote{bird,} \enquote{bug,} and \enquote{fish.} These categories were described to participants as naturally occurring kinds on an alien planet.
+In each category, we generated \emph{different}, \emph{intermediate}, and \emph{similar} pairs by manipulating a continuous property controlling features of the category's shape (e.g., body stretch or head fatness).
+
+In order to validate and quantify our similarity scales, we ran a separate survey on Amazon Mechanical Turk where we asked \(N=20\) adults participants to evaluate the similarity of each sound and object pair on a 7-point scale.
+Data are shown in Figure \ref{fig:stim} where we scaled responses within the range {[}0,1{]} for each stimulus group.
+We used these data in all models as an empirical measurement of the perceptual distance between the sound pairs and the object pairs.
+The use of empirical measurement allows us to eliminate \(\Delta s\) and \(\Delta s\) as free parameters (see Frank \& Goodman (2012) and Xu \& Tenenbaum (2007) for a similar strategy).
+
+\hypertarget{design}{%
+\subsubsection{Design}\label{design}}
+
+Each age group saw only two of the three levels of similarity described in the previous sub-section: \emph{different} vs.
+\emph{intermediate} for the preschoolers, and \emph{intermediate} vs.
+\emph{similar} for adults.
+We made this choice in light of pilot studies showing that adults were at ceiling with \emph{different} sounds/objects, and children were at chance with the \emph{similar} sounds/objects.
+That said, this difference in the level of similarity is accounted for in the model: We used empirical distance measurement to fill in the appropriate values of \(\Delta s\) and \(\Delta o\) for each age group.
 
@@
 
-\caption{Distances for both sound and object pairs from an adult norming study.
+\caption{Distances for sound and object pairs ($\Delta s$ and $\Delta o$, respectively) from an adult norming study.
 Data represent Likert values normalized to [0,1] interval.
@@
 
-To maximize our ability to measure subtle stimulus effects, the
-experiment was a 2x2 within-subjects factorial design with four
-conditions: high/low sound similarity crossed with high/low visual
-object similarity. Besides the four conditions, we also tested
-participants on a fifth catch condition which was similar in its
-structure to the other ones but was trivially easy and used only to
-select participants who were able to follow the instructions and show
-minimal learning.
-
-\subsubsection{Procedure}\label{procedure}
-
-Preschoolers were tested at the nursery school using a tablet, whereas
-adults used their own computers to complete the same experiment online.
-Participants were tested in a random sequence of five conditions: the
-four experimental conditions plus the catch condition. In each
-condition, participants saw a first block of four exposure trials
-followed by four testing trials, and a second block of two exposure
-trials (for memory refreshment) followed by an additional four testing
-trials. The length of this procedure was demanding, especially for
-children, but we adopted a fully within-subjects design based on pilot
-testing that indicated that precision of measurement was critical for
-testing our experimental predictions.
-
-In the exposure trials, participants saw two objects associated with
-their corresponding sounds. We presented the first object on the left
-side of the tablet's screen simultaneously with the corresponding sound.
-The second sound-object association followed on the other side of the
-screen after 500ms. For both objects, visual stimuli were present for
-the duration of the sound clip (about 800ms). In the testing trials,
-participants saw both objects simultaneously and heard only one sound.
-They completed the trial by selecting which of the two objects
-corresponded to the sound. The object-sound pairings were randomized
-across participants, as was the order of the conditions (except for the
-catch condition which was always placed in the middle of the testing
-sequence). We also randomized the on-screen position (left vs.~right) of
-the two pictures on each testing trial.
+To maximize our ability to measure subtle stimulus effects, the experiment was a 2x2 within-subjects factorial design with four conditions: high/low sound similarity crossed with high/low visual object similarity.
+Besides the four conditions, we also tested participants on a fifth catch condition which was similar in its structure to the other ones but was trivially easy and used only to select participants who were able to follow the instructions and show minimal learning.
+
+\hypertarget{procedure}{%
+\subsubsection{Procedure}\label{procedure}}
+
+Preschoolers were tested at the nursery school using a tablet, whereas adults used their own computers to complete the same experiment online.
+Participants were tested in a random sequence of five conditions: the four experimental conditions plus the catch condition.
+In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.
+The length of this procedure was demanding, especially for children, but we adopted a fully within-subjects design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.
+
+In the exposure trials, participants saw two objects associated with their corresponding sounds.
+We presented the first object on the left side of the tablet's screen simultaneously with the corresponding sound.
+The second sound-object association followed on the other side of the screen after 500ms.
+For both objects, visual stimuli were present for the duration of the sound clip (about 800ms).
+During this phase, participant were asked to pay attention and try yo lean the words.
+In the testing trials, participants saw both objects simultaneously and heard only one sound.
+They completed the trial by selecting which of the two objects corresponded to the sound.
+The object-sound pairings were randomized across participants, as was the order of the conditions (except for the catch condition which was always placed in the middle of the testing sequence).
+We also randomized the on-screen position (left vs.~right) of the two pictures on each testing trial.
+The online experiment can be viewed at XXX
 
@@
 
-\subsection{Results}\label{results}
-
-Experimental results are shown in Figure \ref{fig:allData} (solid
-lines). We first analyzed the results using a mixed-effects logistic
-regression with sound distance, object distance and age group as fixed
-effects, and with a maximal random effects structure (allowing us to
-take into account the full nested structure of our data) (Barr, Levy,
-Scheepers, \& Tily, 2013). We found main effects for all the fixed
-effects in the regression. For the sound distance, we obtained
-\(\beta =\) 0.68 (\(p\) \textless{} 0.001), replicating previous
-findings that sound distance modulates success in word learning (e.g.,
-Stager \& Werker, 1997).
-
-For object distance, we found \(\beta =\) 0.60 (\(p\) \textless{}
-0.001), and this finding confirms the new prediction of our model,
-according to which, object distance also modulates success in word
-learning. Note, in particular, that increasing the visual similarity of
-the objects makes children succeed in learning the similar-sounding
-words. Finally, for the age group, we obtained \(\beta =\) 0.59 (\(p\)
-\textless{} 0.001), showing that overall performance improves with age.
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+Experimental results are shown in Figure \ref{fig:allData} (solid lines).
+We first analyzed the results using a mixed-effects logistic regression with sound distance, object distance and age group as fixed effects, and with a maximal random effects structure (allowing us to take into account the full nested structure of our data) (Barr, Levy, Scheepers, \& Tily, 2013).
+We found main effects for all the fixed effects in the regression.
+For the sound distance, we obtained \(\beta =\) 0.68 (\(p\) \textless{} 0.001), replicating previous findings that sound distance modulates success in word learning (e.g., Stager \& Werker, 1997).
+
+For object distance, we found \(\beta =\) 0.60 (\(p\) \textless{} 0.001), and this finding confirms the new prediction of our model, according to which, object distance also modulates performance in word learning.
+Finally, for the age group, we obtained \(\beta =\) 0.59 (\(p\) \textless{} 0.001), showing that overall performance improves with age.
 The full output of the regression model is shown in Table 2.
 
+In particular, while children were not different form chance in the most difficult condition when both the sounds and objects are similar .
+Note, however, the differe that the difference between the these two conditions was not itself
+
 \begin{table}
 
-\caption{\label{tab:models}Characteristics and performance of the models used in this study.}
+\caption{\label{tab:models}Characteristics and performance of the models used in this study. Value ranges represent 95\% confidence intervals.}
 \centering
+\resizebox{\linewidth}{!}{
 \begin{tabular}[t]{>{\bfseries}llrrllll}
@@
 \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Children} & \multicolumn{2}{c}{Adults} \\
-\cmidrule(l{2pt}r{2pt}){5-6} \cmidrule(l{2pt}r{2pt}){7-8}
+\cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8}
 Model & Structure & Param. & R\textsuperscript{2} & $\sigma$\textsubscript{L} & $\sigma$\textsubscript{C} & $\sigma$\textsubscript{L} & $\sigma$\textsubscript{C}\\
 \midrule
-model 1 & $\sigma$\textsubscript{L} only & 1 & 0.27 & 1 & -- & 0.37 & --\\
-model 2 & $\sigma$\textsubscript{L} = $\sigma$\textsubscript{C} & 1 & 0.95 & 0.6 & 0.6 & 0.15 & 0.15\\
-model 3 & $\sigma$\textsubscript{L} $\neq$ $\sigma$\textsubscript{C} & 2 & 1.00 & 0.83 & 0.31 & 0.12 & 0.17\\
+model 1 & $\sigma$\textsubscript{L} only & 1 & 0.27 & 1.01 [0.55, 1.47] & -- & 0.37 [0.01, 0.73] & --\\
+model 2 & $\sigma$\textsubscript{L} = $\sigma$\textsubscript{C} & 1 & 0.96 & 0.6 [0.53, 0.67] & 0.6 [0.53, 0.67] & 0.15 [0.12, 0.17] & 0.15 [0.12, 0.17]\\
+model 3 & $\sigma$\textsubscript{L} $\neq$ $\sigma$\textsubscript{C} & 2 & 1.00 & 0.82 [0.69, 0.95] & 0.33 [0.18, 0.48] & 0.12 [0.12, 0.13] & 0.17 [0.16, 0.18]\\
 \bottomrule
-\end{tabular}
+\end{tabular}}
 \end{table}
 
-We next fit the three models obtained through expressions
-\ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the
-participants' responses in each age group. The predictions of the models
-are shown \ref{fig:allData}. The parameter estimates (for \(\sigma_L\)
-and \(\sigma_C\)) as well as models' goodness to fit (i.e., measured
-through \(R^2\)) are presented in Table \ref{tab:models}.
-
-Model 1, which does not take into account ambiguity in recovering
-concepts from observed objects, explains only a small part of the
-variance. In contrast, Model 3, which does take into account this
-ambiguity, accounts for all the variance. Interestingly, Model 2 which
-has a single, shared uncertainty parameter for both auditory and visual
-modalities still explains almost all the variance in human data.
-
-As predicted, the uncertainty parameters were larger for children than
-they were for adults (Table \ref{tab:models}), showing that word
-knowledge gets more precise with development. Further, the parameter
-estimates of Model 3 show that this developmental effect is larger for
-labels (\(\sigma_L\) varies between 0.83 in children and 0.12 in adults)
-than it is for concepts (\(\sigma_C\) varies between 0.31 in children
-and 0.17 in adults).
-
-\section{General Discussion}\label{general-discussion}
-
-This paper explored the idea that some seemingly stage-like patterns in
-cognitive development can be characterized in a continuous fashion. We
-used as a case study the seminal work of Stager and Werker (1997)
-showing a discrepancy between children's speech perception abilities and
-their word learning skills. The development of this discrepancy could be
-understood in terms of a discrete change in word representation. But our
-model demonstrates that it can also be parsimoniously described as a
-result of continuous developmental change in the precision of children's
-graded word knowledge. Our model instantiates the continuous development
-hypothesis (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009).
-
-We find in the literature two broad accounts of development in the
-Switch task: One that suggests \emph{direct} development of the sound
-representation and one that hypothesizes \emph{indirect} development of
-this representation through improvement in general cognitive resources.
-On the first account, the sound representation becomes more precise as
-learners refine the boundaries of their initially ambiguous phonetic
-categories and as they gain more experience with the functional role of
-these categories (Apfelbaum \& McMurray, 2011; Dietrich, Swingley, \&
-Werker, 2007; Rost \& McMurray, 2009, 2010; Yoshida et al., 2009). On
-the second account, the precision of sound encoding in the switch task
-improves as a result of the maturation of more general resources like
-the attentional and working memory capacity (Hofer \& Levy, 2017; Stager
-\& Werker, 1997; Werker \& Fennell, 2004). Such improvement allows older
-children and adults to better encode the sound details while
-simultaneously matching these sounds to visual objects. Indeed, one
-recent meta-analysis of the switch task concluded that both changing
-representation precision and better memory/attention play a role in
-developmental changes (Tsui, Byers-Heinlein, \& Fennell, 2019).
-
-Our model is compatible with both of these accounts. In our work, the
-probability distributions do not distinguish between the direct and
-indirect sources of uncertainty --- both are included. Indeed, part of
-the measured uncertainty reflects the learner's degrees of confidence in
-the phonetic/phonological boundaries (i.e., the direct account) and
-another part reflects a possible drop in perceptual acuity due to high
-cognitive load (i.e., the indirect account). Note, however, that the
-model (at least in its current format) is incapable of answering
-questions about the development of each of these sources of uncertainty
-separately or about their relative contribution to the global
-uncertainty.
-
-Werker and Curtin (2005) proposed to explain development in the Switch
-task using their theory called Processing Rich Information from
-Multidimensional Interactive Representations (or PRIMIR) which attempts
-to explain various phenomena in early speech perception and word
-learning within a unified framework. PRIMIR posits that children
-initially try to attend to various features of the speech signal,
-regardless of whether or not these features are relevant to the task at
-hand. For example, when learning the meaning of similar sounds, infants
-are unsure what detail is most important to identify words (i.e., the
-phonemes), and will instead activate several aspects of the information
-simultaneously (including, for example, the gender of the speaker). The
-lack of selective attention leads to confusion and then to failure in
-the task.
-
-According to PRIMIR, learning similar-sounding words becomes more robust
-over time as children develop abstract phonemic categories. The latter
-act as filters, allowing children to attend selectively to the important
-information. This account is also compatible with our model: Developing
-phonemic categories allows learners to better determine when a sound
-contrast signals a change in meaning (i.e., when this contrast straddles
-two categories as in \enquote{bin} vs. \enquote{din}) and when a sound
-contrast does not change word meaning (i.e., when it instantiates a
-variation within the same category). In fact, learning to distinguish
-contrastive vs.~non-contrastive pairs amounts to reducing the overlap
-between the probability distribution of two neighboring words.
-
-While most research has focused on sound representation specifically in
-analyzing the process of learning similar-sounding words, this work
-showed that the visual representation of the referent is equally
-important. Indeed, Model 1 --- which assumes that any visually
-discriminable contrast can be encoded unambiguously as separate
-referents --- failed to explain the data, whereas Model 2 and 3 ---
-which take into account visual ambiguity --- succeeded. As a consequence
-of this assumption, we found that just like word learning is modulated
-by the phonological similarity of the form, it is also modulated by the
-visual similarity of the semantic referents.
-
-Model 2, which predicts that sound similarity and visual similarity
-influence word learning accuracy in the same way, explained slightly
-less variance than Model 3 which predicts that these modalities
-influence word learning differently. Further, as we stated in the
-results section, a comparison of the variance estimates across age
-groups showed that uncertainty reduction in the visual modality was
-lower compared to that of the auditory modality (Table 1). Perhaps this
-difference is due to the fact that, in our task, the auditory speech had
-more sources of noise --- that children have to deal with --- than the
-visual input did. The processing of speech involved dealing with both
-perceptual noise and categorical ambiguity (due to the fact that the
-phonemic boundaries are still developing). In contrast, the processing
-of the visual input in our task involved only perceptual noise and no
-category-related uncertainty. A future direction of research is
-independent measurement and comparison of these parameters in children.
-
-Our finding that word learning is mediated by the visual similarity of
-the semantic objects has implications for theories of lexical
-development. It suggests that, all things being equal, children may
-learn, first, words whose semantic referents are visually different as
-this allows them to minimize semantic ambiguity. It will be interesting
-for future work to explore whether the results that we obtained using
-visual similarity generalize to richer, more conceptual features in the
-semantic space. In addition, it is important to study how laboratory
-experiment of this sort may explain patterns of word learning in the
-wild (Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018;
-Sizemore, Karuza, Giusti, \& Bassett, 2018).
-
-There are a few limitations to this work. One is that the model was fit
-to data from children at a relatively older age (4-5 years old) than
-what is typically studied in the literature (14-17 month-old). We
-selected this older age group to optimize the number and precision of
-the experimental measures (both are crucial to model fitting). Data
-collection involved presenting participants with several trials across
-four conditions in a between-subject design. It would have been
-challenging to obtain such measures with infants. That said, though we
-used data from older children, we still found clear developmental
-differences with adults, confirming and extending findings that the
-ability to distinguish similar-sounding words continues developing well
-beyond 17 months (Fennell \& Byers-Heinlein, 2014; Hazan \& Barrett,
-2000; Mattock, Polka, Rvachew, \& Krehm, 2010).
-
-One limitation of our models is that they only account for bottom-up,
-similarity-based effects. They do not account for how high-level factors
-such as social and communicative cues can influence learning. For
-example, Fennell and Waxman (2010) highlighted the fact that some
-laboratory tasks such as the one used in Stager and Werker (1997)
-introduce novel words in isolation (e.g., \enquote{neem!}) rather than
-within a naming phrase (e.g., \enquote{look at the neem!}). This fact
-may prompt children to interpret these novel words in a non-referential
-way (e.g., an exclamation such as \enquote{Wow!}).
-
-To conclude, this paper proposes a model that accounts for the
-development of an important aspect of word learning. Our account
-suggests that the developmental data can be explained based on a
-continuous process operating over similar representations across the
-lifespan, suggesting developmental continuity. We used a case from word
-learning as an example, but the same idea might apply to other aspects
-of cognitive development that are typically thought of as stage-like
-(e.g., acquisition of a theory of mind). Computational models, such as
-the one proposed here, can help us investigate the extent to which such
-discontinuities emerge due to genuine qualitative changes and the extent
-to which they reflect the granularity of the researchers' own
-measurement tools.
+We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the participants' responses in each age group.
+The predictions of the models are shown \ref{fig:allData}.
+The parameter estimates (for \(\sigma_L\) and \(\sigma_C\)) as well as models' goodness to fit (i.e., measured through \(R^2\)) are presented in Table \ref{tab:models}.
+~Remmeber that, in our model, the fitted uncertainty parameters characterize the learners' general processing skills at a given time in development.
+Thus, they are understood to be the same across all stimuli within a given modality.
+
+Model 1, which does not take into account ambiguity in recovering concepts from observed objects, explains only a small part of the variance.
+In contrast, Model 3, which does take into account this ambiguity, accounts for all the variance.
+Interestingly, Model 2 which has a single, shared uncertainty parameter for both auditory and visual modalities still explains almost all the variance in human data.
+
+As predicted, the uncertainty parameters were larger for children than they were for adults (Table \ref{tab:models}), showing that word knowledge gets more precise with development.
+Further, the parameter estimates of Model 3 show that this developmental effect is larger for labels (\(\sigma_L\) varies between 0.82 in children and 0.12 in adults) than it is for concepts (\(\sigma_C\) varies between 0.33 in children and 0.17 in adults).
+
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
+
+This paper explored the idea that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion.
+We used as a case study the seminal work of Stager \& Werker (1997) showing a discrepancy between children's speech perception abilities and their word learning skills.
+The development of this discrepancy could be understood in terms of a discrete change in word representation.
+But our model demonstrates that it can also be parsimoniously described as a result of continuous developmental change in the precision of children's graded word knowledge.
+Our model instantiates the continuous development hypothesis (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009).
+
+More precisely, our model used the assumption that the ability to distinguish two stimuli perceptually leads to accurate mapping to two distinct objects, although this mapping can be noisy.
+On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations.
+With this assumption, the model was capable of accurately predicting behavior (including around-chance performance in the case of the most difficult contrasts)\footnote{That is, the case when both the sounds and objects are similar for children.
+Figure 6 shows that the confidence intervals include the chance value of 0.5.}, thus providing a proof of concept for the continuity hypothesis.
+The discontinuity hypothesis --- which posits the absence of learning and not just retrieval difficulty --- cannot be ruled out by our model, but it is less parsimonious.
+We propose that the continuous hypothesis should be considered as a baseline; discontinuous development should only be posited if it deviates from this baseline.
+
+We find in the literature two broad accounts of development in the Switch task: One that suggests \emph{direct} development of the sound representation and one that hypothesizes \emph{indirect} development of this representation through improvement in general cognitive resources.
+On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories (Apfelbaum \& McMurray, 2011; Dietrich, Swingley, \& Werker, 2007; Rost \& McMurray, 2009, 2010; Werker \& Curtin, 2005; Yoshida et al., 2009).
+On the second account, the precision of sound encoding in the switch task improves as a result of the maturation of more general resources like the attentional and working memory capacity (Hofer \& Levy, 2017; Stager \& Werker, 1997; Werker \& Fennell, 2004).
+Such improvement allows older children and adults to better encode the sound details while simultaneously matching these sounds to visual objects.
+Indeed, one recent meta-analysis of the switch task concluded that both changing representation precision and better memory/attention play a role in developmental changes (Tsui, Byers-Heinlein, \& Fennell, 2019).
+
+In some sense, our model is compatible with both of these accounts.
+Indeed, the model aims at understanding \emph{how} (by contrast to \emph{what}) uncertainty can influence word learning.
+It characterizes and measures uncertainty in a rather global/coarse fashion, without committing to any specific source.
+Thus, it is compatible\footnote{Note the fact that our model is compatible with several previous accounts does not necessarily mean that these accounts are themeselves compatible with one another.} with direct accounts that posit uncertainty primarily stems from noisy phonological representations, and with the indirect account which suggests uncertainty primarily stems from a limitation in the general cognitive resources, hindering precise encoding in memory of subtle sounds under challenging conditions.
+Note that, since our goal was not to distinguish between these accounts, the model (at least in its current format) cannot answer questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.
+
+While most research has focused on sound representation specifically in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important.
+Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded.
+As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents.
+This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform (Fourtassi \& Dupoux, 2019; Yeung \& Werker, 2009; Zhao, Packard, McMurray, \& Gupta, 2019).
+Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see Zhao et al.
+(2019) for a detailed dsicussion).
+That said, these two questions can be related, albeit indirectly.
+For instance, while we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
+
+Model 2, which predicts that sound similarity and visual similarity influence word learning accuracy in the same way, explained slightly less variance than Model 3 which predicts that these modalities influence word learning differently.
+Further, as we stated in the results section, a comparison of the variance estimates across age groups showed that uncertainty reduction in the visual modality was lower compared to that of the auditory modality (Table 1).
+Perhaps this difference is due to the fact that, in our task, the auditory speech had more sources of noise --- that children have to deal with --- than the visual input did.
+The processing of speech involved dealing with both perceptual noise and categorical ambiguity (due to the fact that the phonemic boundaries are still developing).
+In contrast, the processing of the visual input in our task involved only perceptual noise and no category-related uncertainty.
+A future direction of research is independent measurement and comparison of these parameters in children.
+
+Our finding that word learning is mediated by the visual similarity of the semantic objects has implications for theories of lexical development.
+It suggests that, all things being equal, children may learn, first, words whose semantic referents are visually different as this allows them to minimize semantic ambiguity.
+It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space.
+In addition, it is important to study how laboratory experiment of this sort may explain patterns of word learning in the wild (Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore, Karuza, Giusti, \& Bassett, 2018).
+
+Our work found, among other things, that children have higher sound/phoneme uncertainty that adults do, but prior work have shown that children have good auditory encoding (Swingley, 2003; Swingley \& Aslin, 2000, 2002).
+These two findings are not in contradicton with each other.
+In this work, and as we explained above, the measured sound uncertainty includes various sources.
+One of these sources is perceptual uncertainty, i.e., the ability to perceptually distinguish a sound from other neighboring sounds (e.g., \enquote{bin} is perceptually different from \enquote{din}), and another source is categorical uncertainty, i.e., the ability to estimate phonological boundaries, e.g., \enquote{bin} and \enquote{din} straddle a phonological boundary, that is, they signal a change in meaning.
+The fact that children have a higher sound uncertainty than adults do, does not necessarily mean this higher uncertainty is due to poorer perceptual encoding, only.
+In fact, it is possible that much of the differential in uncertainty (compared to adults) is due to the categorical/phonological dimension which we know undergoes a process of reorganization and refinement across development.
+Thus, our finding that children have higher sound-related uncertainty does not contradict previous work showing children are capable of fine-grained speech perception (see Werker \& Curtin (2005) for a similar view).
+
+There are a few limitations to this work.
+One is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-17 month-old).
+We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting).
+Data collection involved presenting participants with several trials across four conditions in a within-subject design.
+It would have been challenging to obtain such measures with infants.
+That said, though we used data from older children, we still found clear developmental differences with adults, confirming and extending findings that the ability to distinguish similar-sounding words continues developing well beyond 17 months (Fennell \& Byers-Heinlein, 2014; Hazan \& Barrett, 2000; Mattock, Polka, Rvachew, \& Krehm, 2010).
+
+One limitation of our models is that they only account for bottom-up, similarity-based effects.
+They do not account for how high-level factors such as social and communicative cues can influence learning.
+For example, Fennell \& Waxman (2010) highlighted the fact that some laboratory tasks such as the one used in Stager \& Werker (1997) introduce novel words in isolation (e.g., \enquote{neem!}) rather than within a naming phrase (e.g., \enquote{look at the neem!}).
+This fact may prompt children to interpret these novel words in a non-referential way (e.g., an exclamation such as \enquote{Wow!}).
+
+To conclude, this paper proposes a model that accounts for the development of an important aspect of word learning.
+Our account suggests that the developmental data can be explained based on a continuous process operating over similar representations across the lifespan, suggesting developmental continuity.
+We used a case from word learning as an example, but the same idea might apply to other aspects of cognitive development that are typically thought of as stage-like (e.g., acquisition of a theory of mind).
+Computational models, such as the one proposed here, can help us investigate the extent to which such discontinuities emerge due to genuine qualitative changes and the extent to which they reflect the granularity of the researchers' own measurement tools.
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+Here we provide the full mathematical derivation the models' predictions.
+More specifically, we explain how the general Equation \ref{eq:general} leads to Equations \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} which represent our three Models.
+
+Each of these Models instantiates an approximation of \(P(o_i|s_i)\) which is the probability that, given a label instance \(s_i\), a participant would choose the correct object \(o_i\), as opposed to the incorrect object \(o_{j}\), where \(i, j \in \{1,2\}\) and \(j = 1-i\).
+
+We strat from the general expression of this probability as defined in Equation \ref{eq:general}.
+This expression can be normalized in our special case (i.e., a two-alternative-forced choice task) as follows:
+
+\[P(o_i|s_i) = \frac{\sum_{C,L} P(s_i|L)P(L|C)P(o_i|C)}{\sum_{C,L}  P(s_i|L)P(L|C)P(o_i|C) + \sum_{C,L}  P(s_i|L)P(L|C)P(o_j|C)}.\]
+Using the definition of \(P(L|C)\) (given in Equation \ref{eq:mapping}) and the fact that we only have two possible categories in each modality (\(L_1, L_2\) and \(C_1, C_2\)) we obtain:
+
+\begin{equation} \label{eq:special}
+P(o_i|s_i) = \frac{P(s_i|L_i)P(o_i|C_i) + P(s_i|L_j)P(o_i|C_j)}{[P(s_i|L_i)P(o_i|C_i) + P(s_i|L_j)P(o_i|C_j)] + [P(s_i|L_i)P(o_j|C_i) + P(s_i|L_j)P(o_j|C_j)]}
+\end{equation}
+
+In what follows, we compute the explicit expression of each conditional probability in Equation \ref{eq:special}.
+
+\(P(s_i | L_i)\) is the probability that the sound \(s_i\) was sampled from its correct category \(L_i\).
+Using the fact that we assumed in Equation \ref{eq:sound} that this probability follows a normal distribution \(\mathcal{N}(\mu_C, \sigma^2_C)\), we have:
+
+\[P(s_i|L_i) = \frac{1}{\sqrt{2\pi\sigma^2_{L_i}}}e^{-\frac{(s_i-\mu_{L_j})^2}{2\sigma^2_{L_i}}}.\]
+
+We use the symplifying assumption that \(\sigma_{L_i} = \sigma_L\), an uncertainty common to all labels.
+\(\sigma_L\) can be understood as characterizing general speech processing skills (at a given time in development).
+We obtain the following expression:
+
+\[P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{(s_i-\mu_{L_j})^2}{2\sigma^2_L}}.\]
+
+\(s_i\) is supposed to be the prototyical instance of \(L_i\), that is, \(s_i=\mu_{L_j}\), leading to \[P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}}.\]
+
+Similarly, \[P(o_i | C_i) = P(o_j | C_j) = \frac{1}{\sqrt{2\pi\sigma^2_C}}.\]
+
+\(P(s_i | L_j)\) is the probability that the sound \(s_i\), though a perfect instance of \(L_i\), could still be a mispronunced instance of the category \(L_j\).
+The value of this probability depends on the extent to which the distributions of the categories \(L_i\) and \(L_j\) overlap with each other (Figure \ref{fig:illus}).
+Using the normal distribution, we obtain the following expression: \[P(s_i| L_j) = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{(s_i-s_j)^2}{2\sigma^2_L}} = \frac{1}{\sqrt{2\pi\sigma^2_L}} e^{-\frac{\Delta s^2}{2\sigma^2_L}}.\]
+
+Similarly, \[P(o_i| C_j) = P(o_j| C_i) = \frac{1}{\sqrt{2\pi\sigma^2_C}} e^{-\frac{\Delta o^2}{2\sigma^2_C}} \]
+
+Finally, we substitute all these expresisions in equation \ref{eq:special} above, leading to:
+
+\[P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}\]
+Which is the expression for Model 3 (Equatin \ref{eq:model3}).
+The expression for Model 2 (Equation \ref{eq:model2}) can be deduced from that of Model 3 by positing \(\sigma= \sigma_L = \sigma_C\).
+The expression for Model 1 (Equation \ref{eq:model1}) is also derived from Model 3 by taking the limit when \(\sigma_C \rightarrow 0\).
 
@@
 
-\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}}
-\vspace{1em}
+\fbox{\parbox[b][][c]{14cm}{\centering All data and code for these analyses are available at [Due to the doube-blind review, the link to the github repository is only provided in the full version addressed to the editor]}} \vspace{1em}
 
@@
 
-\section{References}\label{references}
-
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-apfelbaum2011}{}
-Apfelbaum, K. S., \& McMurray, B. (2011). Using variability to guide
-dimensional weighting: Associative mechanisms in early word learning.
-\emph{Cognitive Science}, \emph{35}.
-
-\hypertarget{ref-barr2013}{}
-Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects
-structure for confirmatory hypothesis testing: Keep it maximal.
-\emph{Journal of Memory and Language}, \emph{68}(3).
-
-\hypertarget{ref-carey2009}{}
-Carey, S. (2009). \emph{The origin of concepts}. Oxford University
-Press.
-
-\hypertarget{ref-carey2015}{}
-Carey, S., Zaitchik, D., \& Bascandziev, I. (2015). Theories of
-development: In dialog with jean piaget. \emph{Developmental Review},
-\emph{38}.
-
-\hypertarget{ref-dautriche2015}{}
-Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel
-phonological neighbors: Syntactic category matters. \emph{Cognition},
-\emph{143}.
-
-\hypertarget{ref-dietrich2007}{}
-Dietrich, C., Swingley, D., \& Werker, J. (2007). Native language
-governs interpretation of salient speech sound differences at 18 months.
+\leavevmode\hypertarget{ref-apfelbaum2011}{}%
+Apfelbaum, K. S., \& McMurray, B. (2011). Using variability to guide dimensional weighting: Associative mechanisms in early word learning. \emph{Cognitive Science}, \emph{35}.
+
+\leavevmode\hypertarget{ref-barr2013}{}%
+Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects structure for confirmatory hypothesis testing: Keep it maximal. \emph{Journal of Memory and Language}, \emph{68}(3).
+
+\leavevmode\hypertarget{ref-carey2009}{}%
+Carey, S. (2009). \emph{The origin of concepts}. Oxford University Press.
+
+\leavevmode\hypertarget{ref-carey2015}{}%
+Carey, S., Zaitchik, D., \& Bascandziev, I. (2015). Theories of development: In dialog with jean piaget. \emph{Developmental Review}, \emph{38}.
+
+\leavevmode\hypertarget{ref-dautriche2015}{}%
+Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel phonological neighbors: Syntactic category matters. \emph{Cognition}, \emph{143}.
+
+\leavevmode\hypertarget{ref-dietrich2007}{}%
+Dietrich, C., Swingley, D., \& Werker, J.
+(2007).
+Native language governs interpretation of salient speech sound differences at 18 months.
 \emph{Proceedings of the National Academy of Sciences}, \emph{104}.
 
-\hypertarget{ref-dutoit1996}{}
+\leavevmode\hypertarget{ref-dutoit1996}{}%
 Dutoit, T., Pagel, V., Pierret, N., Bataille, F., \& Van der Vrecken, O.
-(1996). The mbrola project: Towards a set of high quality speech
-synthesizers free of use for non commercial purposes. In
-\emph{Proceedings of ICSLP} (Vol. 3). IEEE.
-
-\hypertarget{ref-engelthaler2017}{}
-Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word
-learning: Network distinctiveness predicts age of acquisition.
-\emph{Cognitive Science}, \emph{41}.
-
-\hypertarget{ref-Fennell2014}{}
-Fennell, C., \& Byers-Heinlein, K. (2014). You sound like mommy:
-Bilingual and monolingual infants learn words best from speakers typical
-of their language environments. \emph{International Journal of
-Behavioral Development}, \emph{38}(4).
-
-\hypertarget{ref-fennell2010}{}
-Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow
-for infant use of phonetic detail in word learning. \emph{Child
-Development}, \emph{81}.
-
-\hypertarget{ref-fernald2006}{}
-Fernald, A., Perfors, A., \& Marchman, V. A. (2006). Picking up speed in
-understanding: Speech processing efficiency and vocabulary growth across
-the 2nd year. \emph{Developmental Psychology}, \emph{42}.
-
-\hypertarget{ref-fourtassi2018}{}
-Fourtassi, A., Bian, Y., \& Frank, M. C. (2018). Word learning as
-network growth: A cross-linguistic analysis. In \emph{Proceedings of the
-40th annual meeting of the cognitive science society}.
-
-\hypertarget{ref-frank2012}{}
-Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning
-in language games. \emph{Science}, \emph{336}(6084).
-
-\hypertarget{ref-frank2016}{}
-Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M., \& Yurovsky, D.
-(2016). Using tablets to collect data from young children. \emph{Journal
-of Cognition and Development}, \emph{17}(1).
-
-\hypertarget{ref-golinkoff1987}{}
-Golinkoff, R. M., Hirsh-Pasek, K., Cauley, K. M., \& Gordon, L. (1987).
-The eyes have it: Lexical and syntactic comprehension in a new paradigm.
-\emph{Journal of Child Language}, \emph{14}.
-
-\hypertarget{ref-hazan2000}{}
-Hazan, V., \& Barrett, S. (2000). The development of phonemic
-categorization in children aged 6--12. \emph{Journal of Phonetics},
-\emph{28}(4).
-
-\hypertarget{ref-hofer2017}{}
-Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken
-Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the
-Cognitive Science Society}.
-
-\hypertarget{ref-lewis2013}{}
-Lewis, M., \& Frank, M. C. (2013). An integrated model of concept
-learning and word-concept mapping. In \emph{Proceedings of the annual
-meeting of the cognitive science society} (Vol. 35).
-
-\hypertarget{ref-Mattock2010}{}
-Mattock, K., Polka, L., Rvachew, S., \& Krehm, M. (2010). The first
-steps in word learning are easier when the shoes fit: Comparing
-monolingual and bilingual infants. \emph{Developmental Science},
-\emph{13}(1).
-
-\hypertarget{ref-McMurray2007}{}
-McMurray, B. (2007). Defusing the childhood vocabulary explosion.
-\emph{Science}, \emph{317}(5838).
-
-\hypertarget{ref-Munakata2001}{}
-Munakata, Y. (2001). Graded representations in behavioral dissociations.
-\emph{Trends in Cognitive Sciences}, \emph{5}(7).
-
-\hypertarget{ref-pajak2016}{}
-Pajak, B., Creel, S., \& Levy, R. (2016). Difficulty in learning
-similar-sounding words: A developmental stage or a general property of
-learning? \emph{Journal of Experimental Psychology: Learning, Memory,
-and Cognition}, \emph{42}(9).
-
-\hypertarget{ref-pater2004}{}
-Pater, J., Stager, C., \& Werker, J. (2004). The perceptual acquisition
-of phonological contrasts. \emph{Language}, \emph{80}.
-
-\hypertarget{ref-piaget1954}{}
-Piaget, J. (1954). \emph{The construction of reality in the child}. New
-York, NY, US: Basic Books.
-
-\hypertarget{ref-rost2009}{}
-Rost, G., \& McMurray, B. (2009). Speaker variability augments
-phonological processing in early word learning. \emph{Developmental
-Science}, \emph{12}.
-
-\hypertarget{ref-rost2010}{}
-Rost, G., \& McMurray, B. (2010). Finding the signal by adding noise:
-The role of noncontrastive phonetic variability in early word learning.
-\emph{Infancy}, \emph{15}.
-
-\hypertarget{ref-shultz1995}{}
-Shultz, T. R., Schmidt, W. C., Buckingham, D., \& Mareschal, D. (1995).
-Modeling cognitive development with a generative connectionist
-algorithm. In T. J. Simon \& G. S. Halford (Eds.), \emph{Developing
-cognitive competence: New approaches to process modeling}. Hillsdale,
-NJ: Lawrence Erlbaum Associates, Inc.
-
-\hypertarget{ref-sizemore2018}{}
-Sizemore, A. E., Karuza, E. A., Giusti, C., \& Bassett, D. S. (2018).
-Knowledge gaps in the early growth of semantic feature networks.
-\emph{Nature Human Behaviour}, \emph{2}(9).
-
-\hypertarget{ref-stager1997}{}
-Stager, C., \& Werker, J. (1997). Infants listen for more phonetic
-detail in speech perception than in word-learning tasks. \emph{Nature},
-\emph{388}(6640).
-
-\hypertarget{ref-swingley2007}{}
-Swingley, D. (2007). Lexical exposure and word-form encoding in
-1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2).
-
-\hypertarget{ref-thiessen2007}{}
-Thiessen, E. (2007). The effect of distributional information on
-children's use of phonemic contrasts. \emph{Journal of Memory and
-Language}, \emph{56}.
-
-\hypertarget{ref-tsui2019}{}
-Tsui, A. S. M., Byers-Heinlein, K., \& Fennell, C. (2019). Associative
-word learning in infancy: A meta-analysis of the switch task.
-\emph{Developmental Psychology}, \emph{55}.
-
-\hypertarget{ref-werker2005}{}
-Werker, J., \& Curtin, S. (2005). PRIMIR: A developmental framework of
-infant speech processing. \emph{Language Learning and Development},
-\emph{1}.
-
-\hypertarget{ref-werker2004}{}
-Werker, J., \& Fennell, C. (2004). Listening to sounds versus listening
-to words: Early steps in word learning. In D. G. Hall \& S. Waxman
-(Eds.), \emph{Weaving a lexicon}. Cambridge: MIT Press.
-
-\hypertarget{ref-werker1998}{}
-Werker, J., Cohen, L. B., Lloyd, V. L., Casasola, M., \& Stager, C.
-(1998). Acquisition of word--object associations by 14-month-old
-infants. \emph{Developmental Psychology}, \emph{34}.
-
-\hypertarget{ref-werker2002}{}
-Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants'
-ability to learn phonetically similar words: Effects of age and
-vocabulary size. \emph{Infancy}, \emph{3}.
-
-\hypertarget{ref-white2013}{}
-White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show
-less sensitivity to phonetic detail in unfamiliar words, too.
-\emph{Journal of Memory and Language}, \emph{68}(4).
-
-\hypertarget{ref-xu2007}{}
-Xu, F., \& Tenenbaum, J. B. (2007). Word learning as bayesian inference.
-\emph{Psychological Review}, \emph{114}(2).
-
-\hypertarget{ref-yeung09}{}
-Yeung, H., \& Werker, J. (2009). Learning words' sounds before learning
-how words sound: 9-month-olds use distinct objects as cues to categorize
-speech information. \emph{Cognition}, \emph{113}.
-
-\hypertarget{ref-yoshida2009}{}
-Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009).
-14-month-olds learn similar-sounding words. \emph{Developmental
-Science}, \emph{12}.
+(1996).
+The mbrola project: Towards a set of high quality speech synthesizers free of use for non commercial purposes.
+In \emph{Proceedings of ICSLP} (Vol.
+3).
+IEEE.
+
+\leavevmode\hypertarget{ref-engelthaler2017}{}%
+Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word learning: Network distinctiveness predicts age of acquisition. \emph{Cognitive Science}, \emph{41}.
+
+\leavevmode\hypertarget{ref-Fennell2014}{}%
+Fennell, C., \& Byers-Heinlein, K.
+(2014).
+You sound like mommy: Bilingual and monolingual infants learn words best from speakers typical of their language environments.
+\emph{International Journal of Behavioral Development}, \emph{38}(4).
+
+\leavevmode\hypertarget{ref-fennell2010}{}%
+Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow for infant use of phonetic detail in word learning. \emph{Child Development}, \emph{81}.
+
+\leavevmode\hypertarget{ref-fernald2006}{}%
+Fernald, A., Perfors, A., \& Marchman, V.
+A.
+(2006).
+Picking up speed in understanding: Speech processing efficiency and vocabulary growth across the 2nd year.
+\emph{Developmental Psychology}, \emph{42}.
+
+\leavevmode\hypertarget{ref-fourtassi2018}{}%
+Fourtassi, A., Bian, Y., \& Frank, M. C. (2018). Word learning as network growth: A cross-linguistic analysis. In \emph{Proceedings of the 40th annual meeting of the cognitive science society}.
+
+\leavevmode\hypertarget{ref-fourtassi2019}{}%
+Fourtassi, A., \& Dupoux, E.
+(2019).
+Phoneme learning is influenced by the taxonomic organization of the semantic referents.
+In \emph{Proceedings of the 41st annual meeting of the cognitive science society}.
+
+\leavevmode\hypertarget{ref-frank2012}{}%
+Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning in language games. \emph{Science}, \emph{336}(6084).
+
+\leavevmode\hypertarget{ref-frank2016}{}%
+Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M., \& Yurovsky, D. (2016). Using tablets to collect data from young children. \emph{Journal of Cognition and Development}, \emph{17}(1).
+
+\leavevmode\hypertarget{ref-golinkoff1987}{}%
+Golinkoff, R. M., Hirsh-Pasek, K., Cauley, K. M., \& Gordon, L. (1987). The eyes have it: Lexical and syntactic comprehension in a new paradigm. \emph{Journal of Child Language}, \emph{14}.
+
+\leavevmode\hypertarget{ref-hazan2000}{}%
+Hazan, V., \& Barrett, S. (2000). The development of phonemic categorization in children aged 6--12. \emph{Journal of Phonetics}, \emph{28}(4).
+
+\leavevmode\hypertarget{ref-hofer2017}{}%
+Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the Cognitive Science Society}.
+
+\leavevmode\hypertarget{ref-lewis2013}{}%
+Lewis, M., \& Frank, M. C. (2013). An integrated model of concept learning and word-concept mapping. In \emph{Proceedings of the annual meeting of the cognitive science society} (Vol. 35).
+
+\leavevmode\hypertarget{ref-Mattock2010}{}%
+Mattock, K., Polka, L., Rvachew, S., \& Krehm, M.
+(2010).
+The first steps in word learning are easier when the shoes fit: Comparing monolingual and bilingual infants.
+\emph{Developmental Science}, \emph{13}(1).
+
+\leavevmode\hypertarget{ref-McMurray2007}{}%
+McMurray, B. (2007). Defusing the childhood vocabulary explosion. \emph{Science}, \emph{317}(5838).
+
+\leavevmode\hypertarget{ref-Munakata2001}{}%
+Munakata, Y. (2001). Graded representations in behavioral dissociations. \emph{Trends in Cognitive Sciences}, \emph{5}(7).
+
+\leavevmode\hypertarget{ref-pajak2016}{}%
+Pajak, B., Creel, S., \& Levy, R.
+(2016).
+Difficulty in learning similar-sounding words: A developmental stage or a general property of learning?
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{42}(9).
+
+\leavevmode\hypertarget{ref-pater2004}{}%
+Pater, J., Stager, C., \& Werker, J. (2004). The perceptual acquisition of phonological contrasts. \emph{Language}, \emph{80}.
+
+\leavevmode\hypertarget{ref-piaget1954}{}%
+Piaget, J. (1954). \emph{The construction of reality in the child}. New York, NY, US: Basic Books.
+
+\leavevmode\hypertarget{ref-rost2009}{}%
+Rost, G., \& McMurray, B. (2009). Speaker variability augments phonological processing in early word learning. \emph{Developmental Science}, \emph{12}.
+
+\leavevmode\hypertarget{ref-rost2010}{}%
+Rost, G., \& McMurray, B. (2010). Finding the signal by adding noise: The role of noncontrastive phonetic variability in early word learning. \emph{Infancy}, \emph{15}.
+
+\leavevmode\hypertarget{ref-shultz1995}{}%
+Shultz, T.
+R., Schmidt, W.
+C., Buckingham, D., \& Mareschal, D.
+(1995).
+Modeling cognitive development with a generative connectionist algorithm.
+In T.
+J.
+Simon \& G.
+S.
+Halford (Eds.), \emph{Developing cognitive competence: New approaches to process modeling}.
+Hillsdale, NJ: Lawrence Erlbaum Associates, Inc.
+
+\leavevmode\hypertarget{ref-sizemore2018}{}%
+Sizemore, A. E., Karuza, E. A., Giusti, C., \& Bassett, D. S. (2018). Knowledge gaps in the early growth of semantic feature networks. \emph{Nature Human Behaviour}, \emph{2}(9).
+
+\leavevmode\hypertarget{ref-stager1997}{}%
+Stager, C., \& Werker, J. (1997). Infants listen for more phonetic detail in speech perception than in word-learning tasks. \emph{Nature}, \emph{388}(6640).
+
+\leavevmode\hypertarget{ref-swingley2003}{}%
+Swingley, D. (2003). Phonetic detail in the developing lexicon. \emph{Language and Speech}, \emph{46}(2-3), 265--294.
+
+\leavevmode\hypertarget{ref-swingley2007}{}%
+Swingley, D. (2007). Lexical exposure and word-form encoding in 1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2).
+
+\leavevmode\hypertarget{ref-swingley2000}{}%
+Swingley, D., \& Aslin, R. N. (2000). Spoken word recognition and lexical representation in very young children. \emph{Cognition}, \emph{76}(2), 147--166.
+
+\leavevmode\hypertarget{ref-swingley2002}{}%
+Swingley, D., \& Aslin, R. N. (2002). Lexical neighborhoods and the word-form representations of 14-month-olds. \emph{Psychological Science}, \emph{13}(5), 480--484.
+
+\leavevmode\hypertarget{ref-thiessen2007}{}%
+Thiessen, E. (2007). The effect of distributional information on children's use of phonemic contrasts. \emph{Journal of Memory and Language}, \emph{56}.
+
+\leavevmode\hypertarget{ref-tsui2019}{}%
+Tsui, A. S. M., Byers-Heinlein, K., \& Fennell, C. (2019). Associative word learning in infancy: A meta-analysis of the switch task. \emph{Developmental Psychology}, \emph{55}.
+
+\leavevmode\hypertarget{ref-werker1998}{}%
+Werker, J., Cohen, L. B., Lloyd, V. L., Casasola, M., \& Stager, C. (1998). Acquisition of word--object associations by 14-month-old infants. \emph{Developmental Psychology}, \emph{34}.
+
+\leavevmode\hypertarget{ref-werker2005}{}%
+Werker, J., \& Curtin, S. (2005). PRIMIR: A developmental framework of infant speech processing. \emph{Language Learning and Development}, \emph{1}.
+
+\leavevmode\hypertarget{ref-werker2004}{}%
+Werker, J., \& Fennell, C. (2004). Listening to sounds versus listening to words: Early steps in word learning. In D. G. Hall \& S. Waxman (Eds.), \emph{Weaving a lexicon}. Cambridge: MIT Press.
+
+\leavevmode\hypertarget{ref-werker2002}{}%
+Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants' ability to learn phonetically similar words: Effects of age and vocabulary size. \emph{Infancy}, \emph{3}.
+
+\leavevmode\hypertarget{ref-white2013}{}%
+White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show less sensitivity to phonetic detail in unfamiliar words, too. \emph{Journal of Memory and Language}, \emph{68}(4).
+
+\leavevmode\hypertarget{ref-xu2007}{}%
+Xu, F., \& Tenenbaum, J. B. (2007). Word learning as bayesian inference. \emph{Psychological Review}, \emph{114}(2).
+
+\leavevmode\hypertarget{ref-yeung09}{}%
+Yeung, H., \& Werker, J. (2009). Learning words' sounds before learning how words sound: 9-month-olds use distinct objects as cues to categorize speech information. \emph{Cognition}, \emph{113}.
+
+\leavevmode\hypertarget{ref-yoshida2009}{}%
+Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009). 14-month-olds learn similar-sounding words. \emph{Developmental Science}, \emph{12}.
+
+\leavevmode\hypertarget{ref-Zhao2019}{}%
+Zhao, L., Packard, S., McMurray, B., \& Gupta, P.
+(2019).
+Similarity of referents influences the learning of phonological word forms: Evidence from concurrent word learning.
+\emph{Cognition}, \emph{190}, 42--60.
+
+\leavevmode\hypertarget{ref-apfelbaum2011}{}%
+Apfelbaum, K. S., \& McMurray, B. (2011). Using variability to guide dimensional weighting: Associative mechanisms in early word learning. \emph{Cognitive Science}, \emph{35}.
+
+\leavevmode\hypertarget{ref-barr2013}{}%
+Barr, D., Levy, R., Scheepers, C., \& Tily, H. (2013). Random effects structure for confirmatory hypothesis testing: Keep it maximal. \emph{Journal of Memory and Language}, \emph{68}(3).
+
+\leavevmode\hypertarget{ref-carey2009}{}%
+Carey, S. (2009). \emph{The origin of concepts}. Oxford University Press.
+
+\leavevmode\hypertarget{ref-carey2015}{}%
+Carey, S., Zaitchik, D., \& Bascandziev, I. (2015). Theories of development: In dialog with jean piaget. \emph{Developmental Review}, \emph{38}.
+
+\leavevmode\hypertarget{ref-dautriche2015}{}%
+Dautriche, I., Swingley, D., \& Christophe, A. (2015). Learning novel phonological neighbors: Syntactic category matters. \emph{Cognition}, \emph{143}.
+
+\leavevmode\hypertarget{ref-dietrich2007}{}%
+Dietrich, C., Swingley, D., \& Werker, J.
+(2007).
+Native language governs interpretation of salient speech sound differences at 18 months.
+\emph{Proceedings of the National Academy of Sciences}, \emph{104}.
+
+\leavevmode\hypertarget{ref-dutoit1996}{}%
+Dutoit, T., Pagel, V., Pierret, N., Bataille, F., \& Van der Vrecken, O.
+(1996).
+The mbrola project: Towards a set of high quality speech synthesizers free of use for non commercial purposes.
+In \emph{Proceedings of ICSLP} (Vol.
+3).
+IEEE.
+
+\leavevmode\hypertarget{ref-engelthaler2017}{}%
+Engelthaler, T., \& Hills, T. T. (2017). Feature biases in early word learning: Network distinctiveness predicts age of acquisition. \emph{Cognitive Science}, \emph{41}.
+
+\leavevmode\hypertarget{ref-Fennell2014}{}%
+Fennell, C., \& Byers-Heinlein, K.
+(2014).
+You sound like mommy: Bilingual and monolingual infants learn words best from speakers typical of their language environments.
+\emph{International Journal of Behavioral Development}, \emph{38}(4).
+
+\leavevmode\hypertarget{ref-fennell2010}{}%
+Fennell, C., \& Waxman, S. (2010). What paradox? Referential cues allow for infant use of phonetic detail in word learning. \emph{Child Development}, \emph{81}.
+
+\leavevmode\hypertarget{ref-fernald2006}{}%
+Fernald, A., Perfors, A., \& Marchman, V.
+A.
+(2006).
+Picking up speed in understanding: Speech processing efficiency and vocabulary growth across the 2nd year.
+\emph{Developmental Psychology}, \emph{42}.
+
+\leavevmode\hypertarget{ref-fourtassi2018}{}%
+Fourtassi, A., Bian, Y., \& Frank, M. C. (2018). Word learning as network growth: A cross-linguistic analysis. In \emph{Proceedings of the 40th annual meeting of the cognitive science society}.
+
+\leavevmode\hypertarget{ref-fourtassi2019}{}%
+Fourtassi, A., \& Dupoux, E.
+(2019).
+Phoneme learning is influenced by the taxonomic organization of the semantic referents.
+In \emph{Proceedings of the 41st annual meeting of the cognitive science society}.
+
+\leavevmode\hypertarget{ref-frank2012}{}%
+Frank, M. C., \& Goodman, N. D. (2012). Predicting pragmatic reasoning in language games. \emph{Science}, \emph{336}(6084).
+
+\leavevmode\hypertarget{ref-frank2016}{}%
+Frank, M. C., Sugarman, E., Horowitz, A. C., Lewis, M., \& Yurovsky, D. (2016). Using tablets to collect data from young children. \emph{Journal of Cognition and Development}, \emph{17}(1).
+
+\leavevmode\hypertarget{ref-golinkoff1987}{}%
+Golinkoff, R. M., Hirsh-Pasek, K., Cauley, K. M., \& Gordon, L. (1987). The eyes have it: Lexical and syntactic comprehension in a new paradigm. \emph{Journal of Child Language}, \emph{14}.
+
+\leavevmode\hypertarget{ref-hazan2000}{}%
+Hazan, V., \& Barrett, S. (2000). The development of phonemic categorization in children aged 6--12. \emph{Journal of Phonetics}, \emph{28}(4).
+
+\leavevmode\hypertarget{ref-hofer2017}{}%
+Hofer, M., \& Levy, R. (2017). Modeling Sources of Uncertainty in Spoken Word Learning. In \emph{Proceedings of the 39th Annual Meeting of the Cognitive Science Society}.
+
+\leavevmode\hypertarget{ref-lewis2013}{}%
+Lewis, M., \& Frank, M. C. (2013). An integrated model of concept learning and word-concept mapping. In \emph{Proceedings of the annual meeting of the cognitive science society} (Vol. 35).
+
+\leavevmode\hypertarget{ref-Mattock2010}{}%
+Mattock, K., Polka, L., Rvachew, S., \& Krehm, M.
+(2010).
+The first steps in word learning are easier when the shoes fit: Comparing monolingual and bilingual infants.
+\emph{Developmental Science}, \emph{13}(1).
+
+\leavevmode\hypertarget{ref-McMurray2007}{}%
+McMurray, B. (2007). Defusing the childhood vocabulary explosion. \emph{Science}, \emph{317}(5838).
+
+\leavevmode\hypertarget{ref-Munakata2001}{}%
+Munakata, Y. (2001). Graded representations in behavioral dissociations. \emph{Trends in Cognitive Sciences}, \emph{5}(7).
+
+\leavevmode\hypertarget{ref-pajak2016}{}%
+Pajak, B., Creel, S., \& Levy, R.
+(2016).
+Difficulty in learning similar-sounding words: A developmental stage or a general property of learning?
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{42}(9).
+
+\leavevmode\hypertarget{ref-pater2004}{}%
+Pater, J., Stager, C., \& Werker, J. (2004). The perceptual acquisition of phonological contrasts. \emph{Language}, \emph{80}.
+
+\leavevmode\hypertarget{ref-piaget1954}{}%
+Piaget, J. (1954). \emph{The construction of reality in the child}. New York, NY, US: Basic Books.
+
+\leavevmode\hypertarget{ref-rost2009}{}%
+Rost, G., \& McMurray, B. (2009). Speaker variability augments phonological processing in early word learning. \emph{Developmental Science}, \emph{12}.
+
+\leavevmode\hypertarget{ref-rost2010}{}%
+Rost, G., \& McMurray, B. (2010). Finding the signal by adding noise: The role of noncontrastive phonetic variability in early word learning. \emph{Infancy}, \emph{15}.
+
+\leavevmode\hypertarget{ref-shultz1995}{}%
+Shultz, T.
+R., Schmidt, W.
+C., Buckingham, D., \& Mareschal, D.
+(1995).
+Modeling cognitive development with a generative connectionist algorithm.
+In T.
+J.
+Simon \& G.
+S.
+Halford (Eds.), \emph{Developing cognitive competence: New approaches to process modeling}.
+Hillsdale, NJ: Lawrence Erlbaum Associates, Inc.
+
+\leavevmode\hypertarget{ref-sizemore2018}{}%
+Sizemore, A. E., Karuza, E. A., Giusti, C., \& Bassett, D. S. (2018). Knowledge gaps in the early growth of semantic feature networks. \emph{Nature Human Behaviour}, \emph{2}(9).
+
+\leavevmode\hypertarget{ref-stager1997}{}%
+Stager, C., \& Werker, J. (1997). Infants listen for more phonetic detail in speech perception than in word-learning tasks. \emph{Nature}, \emph{388}(6640).
+
+\leavevmode\hypertarget{ref-swingley2003}{}%
+Swingley, D. (2003). Phonetic detail in the developing lexicon. \emph{Language and Speech}, \emph{46}(2-3), 265--294.
+
+\leavevmode\hypertarget{ref-swingley2007}{}%
+Swingley, D. (2007). Lexical exposure and word-form encoding in 1.5-year-olds. \emph{Developmental Psychology}, \emph{43}(2).
+
+\leavevmode\hypertarget{ref-swingley2000}{}%
+Swingley, D., \& Aslin, R. N. (2000). Spoken word recognition and lexical representation in very young children. \emph{Cognition}, \emph{76}(2), 147--166.
+
+\leavevmode\hypertarget{ref-swingley2002}{}%
+Swingley, D., \& Aslin, R. N. (2002). Lexical neighborhoods and the word-form representations of 14-month-olds. \emph{Psychological Science}, \emph{13}(5), 480--484.
+
+\leavevmode\hypertarget{ref-thiessen2007}{}%
+Thiessen, E. (2007). The effect of distributional information on children's use of phonemic contrasts. \emph{Journal of Memory and Language}, \emph{56}.
+
+\leavevmode\hypertarget{ref-tsui2019}{}%
+Tsui, A. S. M., Byers-Heinlein, K., \& Fennell, C. (2019). Associative word learning in infancy: A meta-analysis of the switch task. \emph{Developmental Psychology}, \emph{55}.
+
+\leavevmode\hypertarget{ref-werker1998}{}%
+Werker, J., Cohen, L. B., Lloyd, V. L., Casasola, M., \& Stager, C. (1998). Acquisition of word--object associations by 14-month-old infants. \emph{Developmental Psychology}, \emph{34}.
+
+\leavevmode\hypertarget{ref-werker2005}{}%
+Werker, J., \& Curtin, S. (2005). PRIMIR: A developmental framework of infant speech processing. \emph{Language Learning and Development}, \emph{1}.
+
+\leavevmode\hypertarget{ref-werker2004}{}%
+Werker, J., \& Fennell, C. (2004). Listening to sounds versus listening to words: Early steps in word learning. In D. G. Hall \& S. Waxman (Eds.), \emph{Weaving a lexicon}. Cambridge: MIT Press.
+
+\leavevmode\hypertarget{ref-werker2002}{}%
+Werker, J., Fennell, C., Corcoran, K., \& Stager, C. (2002). Infants' ability to learn phonetically similar words: Effects of age and vocabulary size. \emph{Infancy}, \emph{3}.
+
+\leavevmode\hypertarget{ref-white2013}{}%
+White, K., Yee, E., Blumstein, S., \& Morgan, J. (2013). Adults show less sensitivity to phonetic detail in unfamiliar words, too. \emph{Journal of Memory and Language}, \emph{68}(4).
+
+\leavevmode\hypertarget{ref-xu2007}{}%
+Xu, F., \& Tenenbaum, J. B. (2007). Word learning as bayesian inference. \emph{Psychological Review}, \emph{114}(2).
+
+\leavevmode\hypertarget{ref-yeung09}{}%
+Yeung, H., \& Werker, J. (2009). Learning words' sounds before learning how words sound: 9-month-olds use distinct objects as cues to categorize speech information. \emph{Cognition}, \emph{113}.
+
+\leavevmode\hypertarget{ref-yoshida2009}{}%
+Yoshida, K., Fennell, C., Swingley, D., \& Werker, J. (2009). 14-month-olds learn similar-sounding words. \emph{Developmental Science}, \emph{12}.
+
+\leavevmode\hypertarget{ref-Zhao2019}{}%
+Zhao, L., Packard, S., McMurray, B., \& Gupta, P.
+(2019).
+Similarity of referents influences the learning of phonological word forms: Evidence from concurrent word learning.
+\emph{Cognition}, \emph{190}, 42--60.
 
 \clearpage
-
 \renewcommand{\listfigurename}{Figure captions}
 
-\listoffigures
-
 \end{document}

### 2020-03-21 journal/ms_blind.Rmd
more revisions

@@
 Some researchers [@swingley2007; @yoshida2009; @pajak2016] proposed that word knowledge may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
-Rather, they may be encoding this knowledge in a graded fashion (see @Munakata2001 for an detailed discussion of a similar view).
+Rather, they may be encoding this knowledge in a graded fashion (see @Munakata2001 for a detailed discussion of a similar view).
 Thus, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy knowledge.
@@
 Many different computational formalisms can represent graded knowledge.
-Here we use probabilistic models, a formalism that allows both easy examination of internal representations and quantification of the robustness of these representations.
-Word knowledge can be characterized with a probability distribution over sound instances organized in a similarity space.
-The probability is highest at the most typical sound instance.
+Here we use probabilistic models, a formalism that allows both easy examinations of internal representations and quantification of the robustness of these representations.
+For example, wordform knowledge can be characterized by a probability distribution in a similarity space.
+The probability is highest at the most typical sound instance of the word.
 It decreases as the instance becomes less typical.
@@
 In particular, unlike the binary view, the probabilistic view allows for the possibility of word knowledge being both successful and noisy.
-This new understanding can provide an account for the fact that children show evidence of learning in some testing condition [e.g., @yoshida2009] but not in others [e.g., @stager1997] --- depending on the precision of the measurement.
+This new understanding can provide an account for the fact that children show evidence of learning in some testing conditions [e.g., @yoshida2009] but not in others [e.g., @stager1997] --- depending on the precision of the measurement.
 
@@
 
-In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains difference in behavior within the same task.
+In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task.
 In particular, when the labels are quite distinct in the perceptual space ("lif" vs.
@@
 Importantly, a more precise representation still has a non-zero variance.
-Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adults studies [@white2013; @pajak2016].
+Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adult studies [@white2013; @pajak2016].
 
@@
 One previous study attempted to provide such a computational instantiation [@hofer2017].
-However, this previous work was designed with the goal of reproducing the results of a specific study [@pajak2016] which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
+However, this previous work aimed more at reproducing the results of a specific study [@pajak2016] which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
 
-The present work proposes a model of word-pair learning based on the probabilistic account.
+The present work proposes a model of word-pair learning and development based on the probabilistic account.
 We tested the ability of this model to both *explain* various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to *predict* new learning patterns that have not been tested before.
@@
 Next, we quantify the extent to which the model's predictions account for human data we collected from both preschool children and adults.
-Finally, we discuss the results in the light of existing accounts of word development.
+Finally, we discuss the results in light of existing accounts of word development.
 
@@
 However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously.
-In our model, we assume that both labels and concepts are categories with possibly overlapping distributions.
-In other words, we allow the model to account for the --- more realistic --- possibility that an instances of a given categories (e.g.,"bin") can be mistaken for an instance of a neighboring category (e.g., "din"), albeit with a smaller probability.
-We assume, for simplicity, that this probability is captured by a normal distribution\footnote{\textcolor{red}{We used a normal distribution to simplify the mathematical derivations.
-This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}}:
+In our model, we make the --- more realistic --- assumption that both labels and concepts are characterized with distributions and that the distributions of neighboring categories may overlap.
+In other words, we allow the model to account for the possibility that an instance of a given category (e.g.,"bih") can be mistaken for an instance of a neighboring category (e.g., "dih"), albeit with a smaller probability.
+We assume, for simplicity, that this probability is captured by a normal distribution\footnote{We used a normal distribution to simplify the mathematical derivations.
+This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}:
 
@@
 
-Finally, assuming that the concepts' prior probability $P(C)$ is uniformly distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in our experiment.} we obtain the following expression, where all conditional dependencies are now well defined:
+Finally, assuming that the concepts' prior probability $P(C)$ is uniformly distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in the experiment.} we obtain the following expression, where all conditional dependencies are now well defined:
 
@@
 
-From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions.
+From the general expression \ref{eq:general}, we derive three exact analytical solutions instantiating different learning assumptions (see the Appendix for the full mathematical derivation).
 
@@
 
-This assumption yields the following probability function of choosing the correct object $o_i$ given the correspondding label instance $s_i$, where $i \in \{1,2\}$ (see the Appendix for the full mathematical derivation):
+Using this assumption, we can simplify the general Equation \ref{eq:general} of the probability $P(o_i | s_i)$ of choosing the correct object $o_i$ given the correspondding label instance $s_i$:
 
@@
 where $\Delta s = s_2-s_1$ is the perceptual sound distance between the pair of sounds that we refer to as $s_1$ and $s_2$.
-These distances were measured empirically as shown in Figure \@ref(fig:stim).
 
@@
 
-The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with noise from the sounds and objects.
-We first introduce the simplifying assumption that the label-related uncertainty $\sigma_L$ and the concept-related uncertainty $\sigma_C$ are of a similar magnitude, i.e., $\sigma_C \approx \sigma_L = \sigma$.
-This assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way.
-Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given infant experiment.
+The second solution/model is derived from Equation \ref{eq:general} by making the more general assumption that both the labels and the concepts are recovered with uncertainty from the sounds and objects, but we introduce the simplifying assumption that the label-related uncertainty $\sigma_L$ and the concept-related uncertainty $\sigma_C$ are of a similar magnitude, i.e., $\sigma_C \approx \sigma_L = \sigma$.
+This simplifying assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way.
+Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given developmental experiment.
 
@@
 ### Model 3
+
 We finally derive the third (and most general) solution which allows label- and concept-related uncertainties to vary independently.
@@
 We report data from $N=$ `r N_good_ch` children ages 4-5 years from a nursery school.
-An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
-We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk.
-An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses (again, using preregistered exclusion criteria) because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.
+An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group.
+This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers.
+The length of this procedure was demanding for children, but we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk.
+An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.
 
@@
 However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
-For the simialr pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
+For the similar pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
 In this respect, we took inspiration from the work of @pajak2016.
@@
 
-In order to validate and quantify our similarity scales, we ran a separate survey on Amazon Mechanical Turk where we asked $N=20$ adults participants to evaluate the similarity of each sound and object pair on a 7-point scale.
+In order to validate and quantify our similarity scales, we ran a separate survey on Amazon Mechanical Turk where we asked $N=20$ adult participants to evaluate the similarity of each sound and object pair on a 7-point scale.
 Data are shown in Figure \@ref(fig:stim) where we scaled responses within the range [0,1] for each stimulus group.
@@
 For both objects, visual stimuli were present for the duration of the sound clip (about 800ms).
-During this phase, participant were asked to pay attention and try yo lean the words.
+During this phase, participants were asked to pay attention and try yo lean the words.
 In the testing trials, participants saw both objects simultaneously and heard only one sound.
@@
 right) of the two pictures on each testing trial.
-The online experiment can be viewed at XXX
 
@@
 The full output of the regression model is shown in Table 2.
-
-In particular, while children were not different form chance in the most difficult condition when both the sounds and objects are similar .
-Note, however, the differe that the difference between the these two conditions was not itself
 
@@
 
-We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the participants' responses in each age group.
+We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the population's mean responses in each age group, using a Nonlinear Least Squares algorithm.
 The predictions of the models are shown \@ref(fig:allData).
 The parameter estimates (for $\sigma_L$ and $\sigma_C$) as well as models' goodness to fit (i.e., measured through $R^2$) are presented in Table \@ref(tab:models).
-\ Remmeber that, in our model, the fitted uncertainty parameters characterize the learners' general processing skills at a given time in development.
-Thus, they are understood to be the same across all stimuli within a given modality.
 
@@
 # General Discussion
-
 This paper explored the idea that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion.
@@
 
-More precisely, our model used the assumption that the ability to distinguish two stimuli perceptually leads to accurate mapping to two distinct objects, although this mapping can be noisy.
+More precisely, our model used the assumption that the ability to distinguish two sounds perceptually leads to an accurate mapping of these sounds with two distinct objects, although this mapping can be noisy.
 On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations.
@@
 
-We find in the literature two broad accounts of development in the Switch task: One that suggests *direct* development of the sound representation and one that hypothesizes *indirect* development of this representation through improvement in general cognitive resources.
+We find in the literature two broad accounts of development in the ability to learn the meanings of similar-sounding words: One that suggests *direct* development of the sound representation and one that hypothesizes *indirect* development of this representation through improvement in general cognitive resources.
 On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories [@yoshida2009; @dietrich2007; @rost2009; @rost2010; @apfelbaum2011; @werker2005].
@@
 
-In some sense, our model is compatible with both of these accounts.
-Indeed, the model aims at understanding *how* (by contrast to *what*) uncertainty can influence word learning.
+Our model is compatible with both of these accounts.
+Indeed, the model aims at understanding *how* uncertainty can influence word learning.
 It characterizes and measures uncertainty in a rather global/coarse fashion, without committing to any specific source.
-Thus, it is compatible\footnote{Note the fact that our model is compatible with several previous accounts does not necessarily mean that these accounts are themeselves compatible with one another.} with direct accounts that posit uncertainty primarily stems from noisy phonological representations, and with the indirect account which suggests uncertainty primarily stems from a limitation in the general cognitive resources, hindering precise encoding in memory of subtle sounds under challenging conditions.
+Thus, it is compatible\footnote{The fact that our model is compatible with several previous accounts does not necessarily mean that these accounts are themselves compatible with one another.} with direct accounts that posit uncertainty primarily stems from noisy phonological representations, and with the indirect account which suggests uncertainty primarily stems from a limitation in the general cognitive resources, hindering precise encoding in memory of subtle sounds under challenging conditions.
 Note that, since our goal was not to distinguish between these accounts, the model (at least in its current format) cannot answer questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.
@@
 This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform [@Zhao2019; @fourtassi2019; @yeung09].
-Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see @Zhao2019 for a detailed dsicussion).
-That said, these two questions can be related, albeit indirectly.
-For instance, while we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
+Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see @Zhao2019 for a detailed discussion).
+While we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
 
@@
 
-Our work found, among other things, that children have higher sound/phoneme uncertainty that adults do, but prior work have shown that children have good auditory encoding [@swingley2000; @swingley2002; @swingley2003].
+Our work found, among other things, that children have higher sound/phoneme uncertainty than adults do, but prior work have shown that children have good auditory encoding [@swingley2000; @swingley2002; @swingley2003].
 These two findings are not in contradicton with each other.
@@
 # Appendix
+Here we provide the full mathematical derivation of the models' predictions.
 
-Here we provide the full mathematical derivation the models' predictions.
-More specifically, we explain how the general Equation \ref{eq:general} leads to Equations \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} which represent our three Models.
+ More specifically, we explain how the general Equation \ref{eq:general} leads to Equations \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} which represent our three models.
+Each of these models instantiates an approximation of $P(o_i|s_i)$ which is the probability that, given a label instance $s_i$, a participant would choose the correct object $o_i$, as opposed to the incorrect object $o_{j}$, where $i, j \in \{1,2\}$ and $j = 1-i$.
 
-Each of these Models instantiates an approximation of $P(o_i|s_i)$ which is the probability that, given a label instance $s_i$, a participant would choose the correct object $o_i$, as opposed to the incorrect object $o_{j}$, where $i, j \in \{1,2\}$ and $j = 1-i$.
-
-We strat from the general expression of this probability as defined in Equation \ref{eq:general}.
+We start with the general expression of this probability as defined in Equation \ref{eq:general}.
 This expression can be normalized in our special case (i.e., a two-alternative-forced choice task) as follows:
@@
 $$P(o_i|s_i) = \frac{\sum_{C,L} P(s_i|L)P(L|C)P(o_i|C)}{\sum_{C,L}  P(s_i|L)P(L|C)P(o_i|C) + \sum_{C,L}  P(s_i|L)P(L|C)P(o_j|C)}.$$
-Using the definition of $P(L|C)$ (given in Equation \ref{eq:mapping}) and the fact that we only have two possible categories in each modality ($L_1, L_2$ and $C_1, C_2$) we obtain:
+Using the definition of $P(L|C)$ (given in Equation \ref{eq:mapping}) and the fact that there are two categories in each modality ($L_1, L_2$ and $C_1, C_2$) we obtain:
 
@@
 In what follows, we compute the explicit expression of each conditional probability in Equation \ref{eq:special}.
-
 $P(s_i | L_i)$ is the probability that the sound $s_i$ was sampled from its correct category $L_i$.
-Using the fact that we assumed in Equation \ref{eq:sound} that this probability follows a normal distribution $\mathcal{N}(\mu_C, \sigma^2_C)$, we have:
+This probability follows a normal distribution $\mathcal{N}(\mu_C, \sigma^2_C)$ (Equation \ref{eq:sound}), thus:
 
@@
 
-We use the symplifying assumption that $\sigma_{L_i} = \sigma_L$, an uncertainty common to all labels.
+We use the simplifying assumption that $\sigma_{L_i} = \sigma_L$, an uncertainty common to all labels.
 $\sigma_L$ can be understood as characterizing general speech processing skills (at a given time in development).
@@
 
-$s_i$ is supposed to be the prototyical instance of $L_i$, that is, $s_i=\mu_{L_j}$, leading to $$P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}}.$$
+$s_i$ is supposed to be the prototypical instance of $L_i$, that is, $s_i=\mu_{L_j}$, leading to $$P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}}.$$
 
@@
 
-$P(s_i | L_j)$ is the probability that the sound $s_i$, though a perfect instance of $L_i$, could still be a mispronunced instance of the category $L_j$.
+$P(s_i | L_j)$ is the probability that the sound $s_i$, though a perfect instance of $L_i$, could still be a mispronounced instance of the category $L_j$.
 The value of this probability depends on the extent to which the distributions of the categories $L_i$ and $L_j$ overlap with each other (Figure \@ref(fig:illus)).
@@
 
-Finally, we substitute all these expresisions in equation \ref{eq:special} above, leading to:
+Finally, we substitute all these expressions in equation \ref{eq:special} above, leading to:
 
 $$P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}$$
-Which is the expression for Model 3 (Equatin \ref{eq:model3}).
+Which is the expression for Model 3 (Equation \ref{eq:model3}).
 The expression for Model 2 (Equation \ref{eq:model2}) can be deduced from that of Model 3 by positing $\sigma= \sigma_L = \sigma_C$.

### 2020-03-21 journal/ms_blind.tex
more revisions

@@
 Some researchers (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009) proposed that word knowledge may not be encoded in a binary fashion, i.e., it is not the case that children either succeed or fail in encoding minimal contrast when learning the meanings.
-Rather, they may be encoding this knowledge in a graded fashion (see Munakata (2001) for an detailed discussion of a similar view).
+Rather, they may be encoding this knowledge in a graded fashion (see Munakata (2001) for a detailed discussion of a similar view).
 Thus, development does not so much involve a qualitative shift (i.e., a sudden emergence of an ability that did not exist before) as much as it consists in the continuous refinement of initially noisy knowledge.
@@
 In particular, unlike the binary view, the probabilistic view allows for the possibility of word knowledge being both successful and noisy.
-This new understanding can provide an account for the fact that children show evidence of learning in some testing condition (e.g., Yoshida et al., 2009) but not in others (e.g., Stager \& Werker, 1997) --- depending on the precision of the measurement.
+This new understanding can provide an account for the fact that children show evidence of learning in some testing conditions (e.g., Yoshida et al., 2009) but not in others (e.g., Stager \& Werker, 1997) --- depending on the precision of the measurement.
 
@@
 
-In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains difference in behavior within the same task.
+In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task.
 In particular, when the labels are quite distinct in the perceptual space (\enquote{lif} vs.
@@
 Importantly, a more precise representation still has a non-zero variance.
-Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adults studies (Pajak et al., 2016; White et al., 2013).
+Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adult studies (Pajak et al., 2016; White et al., 2013).
 
@@
 One previous study attempted to provide such a computational instantiation (Hofer \& Levy, 2017).
-However, this previous work was designed with the goal of reproducing the results of a specific study (Pajak et al., 2016) which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
-
-The present work proposes a model of word-pair learning based on the probabilistic account.
+However, this previous work aimed more at reproducing the results of a specific study (Pajak et al., 2016) which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
+
+The present work proposes a model of word-pair learning and development based on the probabilistic account.
 We tested the ability of this model to both \emph{explain} various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to \emph{predict} new learning patterns that have not been tested before.
@@
 However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously.
-In our model, we assume that both labels and concepts are categories with possibly overlapping distributions.
-In other words, we allow the model to account for the --- more realistic --- possibility that an instances of a given categories (e.g.,\enquote{bin}) can be mistaken for an instance of a neighboring category (e.g., \enquote{din}), albeit with a smaller probability.
-We assume, for simplicity, that this probability is captured by a normal distribution\footnote{\textcolor{red}{We used a normal distribution to simplify the mathematical derivations.
-This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}}:
+In our model, we make the --- more realistic --- assumption that both labels and concepts are characterized with distributions and that the distributions of neighboring categories may overlap.
+In other words, we allow the model to account for the possibility that an instance of a given category (e.g.,\enquote{bih}) can be mistaken for an instance of a neighboring category (e.g., \enquote{dih}), albeit with a smaller probability.
+We assume, for simplicity, that this probability is captured by a normal distribution\footnote{We used a normal distribution to simplify the mathematical derivations.
+This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}:
 
@@
 
-Finally, assuming that the concepts' prior probability \(P(C)\) is uniformly distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in our experiment.} we obtain the following expression, where all conditional dependencies are now well defined:
+Finally, assuming that the concepts' prior probability \(P(C)\) is uniformly distributed,\footnote{This is a reasonable assumption in our particular case given the similarity of the concept pairs used in each naming situation in the experiment.} we obtain the following expression, where all conditional dependencies are now well defined:
 
@@
 
-This assumption yields the following probability function of choosing the correct object \(o_i\) given the correspondding label instance \(s_i\), where \(i \in \{1,2\}\) (see the Appendix for the full mathematical derivation):
+Using this assumption, we can simplify the general Equation \ref{eq:general} of the probability \(P(o_i | s_i)\) of choosing the correct object \(o_i\) given the correspondding label instance \(s_i\):
 
@@
 where \(\Delta s = s_2-s_1\) is the perceptual sound distance between the pair of sounds that we refer to as \(s_1\) and \(s_2\).
-These distances were measured empirically as shown in Figure \ref{fig:stim}.
 
@@
 
-The second solution is derived by making the more general assumption that both the labels and the concepts are recovered with noise from the sounds and objects.
-We first introduce the simplifying assumption that the label-related uncertainty \(\sigma_L\) and the concept-related uncertainty \(\sigma_C\) are of a similar magnitude, i.e., \(\sigma_C \approx \sigma_L = \sigma\).
-This assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way.
-Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given infant experiment.
+The second solution/model is derived from Equation \ref{eq:general} by making the more general assumption that both the labels and the concepts are recovered with uncertainty from the sounds and objects, but we introduce the simplifying assumption that the label-related uncertainty \(\sigma_L\) and the concept-related uncertainty \(\sigma_C\) are of a similar magnitude, i.e., \(\sigma_C \approx \sigma_L = \sigma\).
+This simplifying assumption makes the prediction that the sound similarity and the object similarity impact word learning accuracy in exactly the same way.
+Furthermore, it allows us to study the behavior of the model with only one free parameter, an important consideration given the small number of datapoints available from any given developmental experiment.
 
@@
 We report data from \(N=\) 63 children ages 4-5 years from a nursery school.
-An additional \(N=\) 39 children participated but were removed from analyses (using preregistered exclusion criteria) because they were not above chance on the catch trials due to the challenging nature of our procedure (see below).
-We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk.
-An additional \(N=\) 26 were tested but removed from analyses (again, using preregistered exclusion criteria) because they had low scores on the catch trials or because they were familiar with the non-English sound stimuli we used in the adult experiment.
+An additional \(N=\) 39 children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group.
+This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers.
+The length of this procedure was demanding for children, but we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk.
+An additional \(N=\) 26 were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.
 
@@
 However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
-For the simialr pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
+For the similar pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
 In this respect, we took inspiration from the work of Pajak et al.
@@
 
-In order to validate and quantify our similarity scales, we ran a separate survey on Amazon Mechanical Turk where we asked \(N=20\) adults participants to evaluate the similarity of each sound and object pair on a 7-point scale.
+In order to validate and quantify our similarity scales, we ran a separate survey on Amazon Mechanical Turk where we asked \(N=20\) adult participants to evaluate the similarity of each sound and object pair on a 7-point scale.
 Data are shown in Figure \ref{fig:stim} where we scaled responses within the range {[}0,1{]} for each stimulus group.
@@
 We also randomized the on-screen position (left vs.~right) of the two pictures on each testing trial.
-The online experiment can be viewed at XXX
 
@@
 
-We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the participants' responses in each age group.
+We next fit the three models obtained through expressions \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} to the population's mean responses in each age group, using a Nonlinear Least Squares algorithm.
 The predictions of the models are shown \ref{fig:allData}.
 The parameter estimates (for \(\sigma_L\) and \(\sigma_C\)) as well as models' goodness to fit (i.e., measured through \(R^2\)) are presented in Table \ref{tab:models}.
-~Remmeber that, in our model, the fitted uncertainty parameters characterize the learners' general processing skills at a given time in development.
-Thus, they are understood to be the same across all stimuli within a given modality.
 
@@
 
-We find in the literature two broad accounts of development in the Switch task: One that suggests \emph{direct} development of the sound representation and one that hypothesizes \emph{indirect} development of this representation through improvement in general cognitive resources.
+We find in the literature two broad accounts of development in the ability to learn the meanings of similar-sounding words: One that suggests \emph{direct} development of the sound representation and one that hypothesizes \emph{indirect} development of this representation through improvement in general cognitive resources.
 On the first account, the sound representation becomes more precise as learners refine the boundaries of their initially ambiguous phonetic categories and as they gain more experience with the functional role of these categories (Apfelbaum \& McMurray, 2011; Dietrich, Swingley, \& Werker, 2007; Rost \& McMurray, 2009, 2010; Werker \& Curtin, 2005; Yoshida et al., 2009).
@@
 
-In some sense, our model is compatible with both of these accounts.
-Indeed, the model aims at understanding \emph{how} (by contrast to \emph{what}) uncertainty can influence word learning.
+Our model is compatible with both of these accounts.
+Indeed, the model aims at understanding \emph{how} uncertainty can influence word learning.
 It characterizes and measures uncertainty in a rather global/coarse fashion, without committing to any specific source.
-Thus, it is compatible\footnote{Note the fact that our model is compatible with several previous accounts does not necessarily mean that these accounts are themeselves compatible with one another.} with direct accounts that posit uncertainty primarily stems from noisy phonological representations, and with the indirect account which suggests uncertainty primarily stems from a limitation in the general cognitive resources, hindering precise encoding in memory of subtle sounds under challenging conditions.
+Thus, it is compatible\footnote{The fact that our model is compatible with several previous accounts does not necessarily mean that these accounts are themselves compatible with one another.} with direct accounts that posit uncertainty primarily stems from noisy phonological representations, and with the indirect account which suggests uncertainty primarily stems from a limitation in the general cognitive resources, hindering precise encoding in memory of subtle sounds under challenging conditions.
 Note that, since our goal was not to distinguish between these accounts, the model (at least in its current format) cannot answer questions about the development of each of these sources of uncertainty separately or about their relative contribution to the global uncertainty.
@@
 Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see Zhao et al.
-(2019) for a detailed dsicussion).
-That said, these two questions can be related, albeit indirectly.
-For instance, while we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
+(2019) for a detailed discussion).
+While we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
 
@@
 
-Our work found, among other things, that children have higher sound/phoneme uncertainty that adults do, but prior work have shown that children have good auditory encoding (Swingley, 2003; Swingley \& Aslin, 2000, 2002).
+Our work found, among other things, that children have higher sound/phoneme uncertainty than adults do, but prior work have shown that children have good auditory encoding (Swingley, 2003; Swingley \& Aslin, 2000, 2002).
 These two findings are not in contradicton with each other.
@@
 
-Here we provide the full mathematical derivation the models' predictions.
-More specifically, we explain how the general Equation \ref{eq:general} leads to Equations \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} which represent our three Models.
-
-Each of these Models instantiates an approximation of \(P(o_i|s_i)\) which is the probability that, given a label instance \(s_i\), a participant would choose the correct object \(o_i\), as opposed to the incorrect object \(o_{j}\), where \(i, j \in \{1,2\}\) and \(j = 1-i\).
-
-We strat from the general expression of this probability as defined in Equation \ref{eq:general}.
+Here we provide the full mathematical derivation of the models' predictions.
+
+More specifically, we explain how the general Equation \ref{eq:general} leads to Equations \ref{eq:model1}, \ref{eq:model2}, and \ref{eq:model3} which represent our three models.
+Each of these models instantiates an approximation of \(P(o_i|s_i)\) which is the probability that, given a label instance \(s_i\), a participant would choose the correct object \(o_i\), as opposed to the incorrect object \(o_{j}\), where \(i, j \in \{1,2\}\) and \(j = 1-i\).
+
+We start with the general expression of this probability as defined in Equation \ref{eq:general}.
 This expression can be normalized in our special case (i.e., a two-alternative-forced choice task) as follows:
@@
 \[P(o_i|s_i) = \frac{\sum_{C,L} P(s_i|L)P(L|C)P(o_i|C)}{\sum_{C,L}  P(s_i|L)P(L|C)P(o_i|C) + \sum_{C,L}  P(s_i|L)P(L|C)P(o_j|C)}.\]
-Using the definition of \(P(L|C)\) (given in Equation \ref{eq:mapping}) and the fact that we only have two possible categories in each modality (\(L_1, L_2\) and \(C_1, C_2\)) we obtain:
+Using the definition of \(P(L|C)\) (given in Equation \ref{eq:mapping}) and the fact that there are two categories in each modality (\(L_1, L_2\) and \(C_1, C_2\)) we obtain:
 
@@
 In what follows, we compute the explicit expression of each conditional probability in Equation \ref{eq:special}.
-
 \(P(s_i | L_i)\) is the probability that the sound \(s_i\) was sampled from its correct category \(L_i\).
-Using the fact that we assumed in Equation \ref{eq:sound} that this probability follows a normal distribution \(\mathcal{N}(\mu_C, \sigma^2_C)\), we have:
+This probability follows a normal distribution \(\mathcal{N}(\mu_C, \sigma^2_C)\) (Equation \ref{eq:sound}), thus:
 
@@
 
-We use the symplifying assumption that \(\sigma_{L_i} = \sigma_L\), an uncertainty common to all labels.
+We use the simplifying assumption that \(\sigma_{L_i} = \sigma_L\), an uncertainty common to all labels.
 \(\sigma_L\) can be understood as characterizing general speech processing skills (at a given time in development).
@@
 
-\(s_i\) is supposed to be the prototyical instance of \(L_i\), that is, \(s_i=\mu_{L_j}\), leading to \[P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}}.\]
+\(s_i\) is supposed to be the prototypical instance of \(L_i\), that is, \(s_i=\mu_{L_j}\), leading to \[P(s_i | L_i) = \frac{1}{\sqrt{2\pi\sigma^2_L}}.\]
 
@@
 
-\(P(s_i | L_j)\) is the probability that the sound \(s_i\), though a perfect instance of \(L_i\), could still be a mispronunced instance of the category \(L_j\).
+\(P(s_i | L_j)\) is the probability that the sound \(s_i\), though a perfect instance of \(L_i\), could still be a mispronounced instance of the category \(L_j\).
 The value of this probability depends on the extent to which the distributions of the categories \(L_i\) and \(L_j\) overlap with each other (Figure \ref{fig:illus}).
@@
 
-Finally, we substitute all these expresisions in equation \ref{eq:special} above, leading to:
+Finally, we substitute all these expressions in equation \ref{eq:special} above, leading to:
 
 \[P(o_i|s_i)= \frac{1 + e^{- (\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}}{1 + e^{-(\frac{\Delta s^2}{2\sigma_L^2}+ \frac{\Delta o^2}{2\sigma_C^2})}+ e^{-\frac{\Delta s^2}{2\sigma_L^2}} + e^{-\frac{\Delta o^2}{2\sigma_C^2}}}\]
-Which is the expression for Model 3 (Equatin \ref{eq:model3}).
+Which is the expression for Model 3 (Equation \ref{eq:model3}).
 The expression for Model 2 (Equation \ref{eq:model2}) can be deduced from that of Model 3 by positing \(\sigma= \sigma_L = \sigma_C\).

### 2020-03-21 journal/ms_blind.Rmd
more revisions

@@
 An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group.
-This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers.
-The length of this procedure was demanding for children, but we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk.
+This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers, and which was demanding for children.
+As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk.
 An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.

### 2020-03-21 journal/ms_blind.tex
more revisions

@@
 An additional \(N=\) 39 children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group.
-This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers.
-The length of this procedure was demanding for children, but we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk.
+This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers, and which was demanding for children.
+As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk.
 An additional \(N=\) 26 were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.

### 2020-03-24 journal/ms_blind.Rmd
more revisions

@@
 
- "Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
+ Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
 To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
@@
 Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word learning accuracy.
-The models' predictions were corroborated by human data we collected from both preschool children and adults.
-The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms."
+The models' predictions were corroborated by human data collected from both preschool children and adults.
+The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms.
 
@@
 Here we use probabilistic models, a formalism that allows both easy examinations of internal representations and quantification of the robustness of these representations.
-For example, wordform knowledge can be characterized by a probability distribution in a similarity space.
+Our goal here is an exploration at the highest level of abstraction, in which we attempt to characterize the computational constraints that might lead to a particular behavior [@marr1982].
+We characterize word knowledge by a probability distribution in a similarity space.
 The probability is highest at the most typical sound instance of the word.
@@
 
-In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task.
+In addition to providing a potential explanation of the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task.
 In particular, when the labels are quite distinct in the perceptual space ("lif" vs.
@@
 Importantly, a more precise representation still has a non-zero variance.
-Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adult studies [@white2013; @pajak2016].
+Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations, as has been demonstrated in adult studies [@white2013; @pajak2016].
 
@@
 
-The probabilistic account was used before to explain patterns of learning and development at the qualitative level [e.g.,@swingley2007].
-However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.
+A probabilistic account has been described before to explain patterns of learning and development at the qualitative level [e.g.,@swingley2007].
+However, it is crucial to have a precise computational instantiation of this account which can help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.
 One previous study attempted to provide such a computational instantiation [@hofer2017].
-However, this previous work aimed more at reproducing the results of a specific study [@pajak2016] which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
+However, this previous work aimed more at reproducing the results of a specific study [@pajak2016], which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
 
-The present work proposes a model of word-pair learning and development based on the probabilistic account.
+The present work proposes a model of developmental change in word-pair learning based on the probabilistic account.
 We tested the ability of this model to both *explain* various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to *predict* new learning patterns that have not been tested before.
-In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting recognition difficulty.
-Although this prediction is intuitive, to our knowledge, it has never been tested.
+In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting word recognition difficulty.
+Previous work in this line of research has studied the effect of several bottom-up and top-down properties on improving learning [e.g., @fennell2010; @rost2009; @thiessen2007] but the effect of the referent similarity remains to be tested.
+While some researchers studied this effect on wordform learning [@Zhao2019; @fourtassi2019; @yeung09], to our knowledge, the effect on children's word-object mapping has not been investigated before.
 Finally, we explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.
@@
 We assume, for simplicity, that this probability is captured by a normal distribution\footnote{We used a normal distribution to simplify the mathematical derivations.
-This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}:
+This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall see in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}:
 
@@
 3) For fixed values of $\Delta s$ and $\sigma$, accuracy increases with the visual distance between the semantic referents $\Delta o$.
-This is a new prediction that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words [e.g., @fennell2010; @rost2009; @thiessen2007], but to our knowledge, no previous study in the literature tested the effect of the visual distance between the semantic referents.
+
+<!--This is a new prediction that our model makes.
+Previous work studied the effect of several bottom-up and top-down properties on word meaning learning [e.g., @fennell2010; @rost2009; @thiessen2007] and the effect of , but to our knowledge, no previous study in the literature tested the effect of the visual distance between the semantic referents.
+-->
 
@@
 Sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simultaneously in a within-subject design.
-Two age groups (preschool children and adults) were tested on the same task^[This four-condition within-subject design is relatively novel for preschoolers, but we followed the tablet paradigm [e.g., @frank2016] which allowed us to gather a relatively large number of trials from each child.] to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
+Two age groups (preschool children and adults) were tested on the same task^[This four-condition within-subject design is somewhat unusual for preschoolers, but we followed the tablet paradigm [e.g., @frank2016] which allowed us to gather a relatively large number of trials from each child.] to explore whether development can be characterized with the uncertainty parameters, $\sigma_C$ and $\sigma_L$.
 The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
@@
 An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group.
-This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers, and which was demanding for children.
+This is partly due to our adoption of a 2x2 fully within-subject design, which was demanding for children.
 As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk.
@@
 Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand.
-However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
+However, this was not the case; word learning accuracy was correctly predicted based on perceptual similarity alone.}: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).
 For the similar pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
@@
 # General Discussion
+
 This paper explored the idea that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion.
@@
 But our model demonstrates that it can also be parsimoniously described as a result of continuous developmental change in the precision of children's graded word knowledge.
-Our model instantiates the continuous development hypothesis [@swingley2007; @yoshida2009; @pajak2016].
+Our model thus provides a computational instantiation and test of the continuous development hypothesis proposed in previous work [@swingley2007; @yoshida2009; @pajak2016].
 
-More precisely, our model used the assumption that the ability to distinguish two sounds perceptually leads to an accurate mapping of these sounds with two distinct objects, although this mapping can be noisy.
+Our model used the assumption that the ability to distinguish two sounds perceptually leads to an accurate mapping of these sounds with two distinct objects, although this mapping can be noisy.
 On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations.
@@
 Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see @Zhao2019 for a detailed discussion).
-While we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
+While we did not model the process of phonological development per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
 
@@
 It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space.
-In addition, it is important to study how laboratory experiment of this sort may explain patterns of word learning in the wild [@engelthaler2017; @sizemore2018; @fourtassi2018].
+In addition, it is important to study how laboratory experiments of this sort may explain patterns of word learning in the wild [@engelthaler2017; @sizemore2018; @fourtassi2018].
 
 Our work found, among other things, that children have higher sound/phoneme uncertainty than adults do, but prior work have shown that children have good auditory encoding [@swingley2000; @swingley2002; @swingley2003].
-These two findings are not in contradicton with each other.
+These two findings are not in conflict with each other.
 In this work, and as we explained above, the measured sound uncertainty includes various sources.
 One of these sources is perceptual uncertainty, i.e., the ability to perceptually distinguish a sound from other neighboring sounds (e.g., "bin" is perceptually different from "din"), and another source is categorical uncertainty, i.e., the ability to estimate phonological boundaries, e.g., "bin" and "din" straddle a phonological boundary, that is, they signal a change in meaning.
-The fact that children have a higher sound uncertainty than adults do,  does not necessarily mean this higher uncertainty is due to poorer perceptual encoding, only.
+The fact that children have a higher sound uncertainty than adults do,  does not necessarily mean this higher uncertainty is due to poorer perceptual encoding only.
 In fact, it is possible that much of the differential in uncertainty (compared to adults) is due to the categorical/phonological dimension which we know undergoes a process of reorganization and refinement across development.
@@
 
-There are a few limitations to this work.
+There are a number of limitations to this work.
 One is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-17 month-old).

### 2020-03-24 journal/ms_blind.tex
more revisions

@@
 \abstract{
-``Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
+Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change.
 To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills.
@@
 Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word learning accuracy.
-The models' predictions were corroborated by human data we collected from both preschool children and adults.
-The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms.''
+The models' predictions were corroborated by human data collected from both preschool children and adults.
+The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms.
 }
@@
 Here we use probabilistic models, a formalism that allows both easy examinations of internal representations and quantification of the robustness of these representations.
-For example, wordform knowledge can be characterized by a probability distribution in a similarity space.
+Our goal here is an exploration at the highest level of abstraction, in which we attempt to characterize the computational constraints that might lead to a particular behavior (Marr, 1982).
+We characterize word knowledge by a probability distribution in a similarity space.
 The probability is highest at the most typical sound instance of the word.
@@
 
-In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task.
+In addition to providing a potential explanation of the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task.
 In particular, when the labels are quite distinct in the perceptual space (\enquote{lif} vs.
@@
 Importantly, a more precise representation still has a non-zero variance.
-Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adult studies (Pajak et al., 2016; White et al., 2013).
+Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations, as has been demonstrated in adult studies (Pajak et al., 2016; White et al., 2013).
 
@@
 
-The probabilistic account was used before to explain patterns of learning and development at the qualitative level (e.g., Swingley, 2007).
-However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.
+A probabilistic account has been described before to explain patterns of learning and development at the qualitative level (e.g., Swingley, 2007).
+However, it is crucial to have a precise computational instantiation of this account which can help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change.
 One previous study attempted to provide such a computational instantiation (Hofer \& Levy, 2017).
-However, this previous work aimed more at reproducing the results of a specific study (Pajak et al., 2016) which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
-
-The present work proposes a model of word-pair learning and development based on the probabilistic account.
+However, this previous work aimed more at reproducing the results of a specific study (Pajak et al., 2016), which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.
+
+The present work proposes a model of developmental change in word-pair learning based on the probabilistic account.
 We tested the ability of this model to both \emph{explain} various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to \emph{predict} new learning patterns that have not been tested before.
-In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting recognition difficulty.
-Although this prediction is intuitive, to our knowledge, it has never been tested.
+In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting word recognition difficulty.
+Previous work in this line of research has studied the effect of several bottom-up and top-down properties on improving learning (e.g., Fennell \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007) but the effect of the referent similarity remains to be tested.
+While some researchers studied this effect on wordform learning (Fourtassi \& Dupoux, 2019; Yeung \& Werker, 2009; Zhao, Packard, McMurray, \& Gupta, 2019), to our knowledge, the effect on children's word-object mapping has not been investigated before.
 Finally, we explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.
@@
   For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases with the visual distance between the semantic referents \(\Delta o\).
-This is a new prediction that our model makes.
-Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (e.g., Fennell \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007), but to our knowledge, no previous study in the literature tested the effect of the visual distance between the semantic referents.
 \end{enumerate}
@@
 Sound similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were varied simultaneously in a within-subject design.
-Two age groups (preschool children and adults) were tested on the same task\footnote{This four-condition within-subject design is relatively novel for preschoolers, but we followed the tablet paradigm (e.g., Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to gather a relatively large number of trials from each child.} to explore whether development can be characterized with the uncertainty parameters, \(\sigma_C\) and \(\sigma_L\).
+Two age groups (preschool children and adults) were tested on the same task\footnote{This four-condition within-subject design is somewhat unusual for preschoolers, but we followed the tablet paradigm (e.g., Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to gather a relatively large number of trials from each child.} to explore whether development can be characterized with the uncertainty parameters, \(\sigma_C\) and \(\sigma_L\).
 The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}
@@
 An additional \(N=\) 39 children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group.
-This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers, and which was demanding for children.
+This is partly due to our adoption of a 2x2 fully within-subject design, which was demanding for children.
 As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk.
@@
 Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand.
-However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
+However, this was not the case; word learning accuracy was correctly predicted based on perceptual similarity alone.}: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).
 For the similar pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults.
@@
 But our model demonstrates that it can also be parsimoniously described as a result of continuous developmental change in the precision of children's graded word knowledge.
-Our model instantiates the continuous development hypothesis (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009).
-
-More precisely, our model used the assumption that the ability to distinguish two sounds perceptually leads to an accurate mapping of these sounds with two distinct objects, although this mapping can be noisy.
+Our model thus provides a computational instantiation and test of the continuous development hypothesis proposed in previous work (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009).
+
+Our model used the assumption that the ability to distinguish two sounds perceptually leads to an accurate mapping of these sounds with two distinct objects, although this mapping can be noisy.
 On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations.
@@
 As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents.
-This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform (Fourtassi \& Dupoux, 2019; Yeung \& Werker, 2009; Zhao, Packard, McMurray, \& Gupta, 2019).
+This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform (Fourtassi \& Dupoux, 2019; Yeung \& Werker, 2009; Zhao et al., 2019).
 Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see Zhao et al.
 (2019) for a detailed discussion).
-While we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
+While we did not model the process of phonological development per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.
 
@@
 It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space.
-In addition, it is important to study how laboratory experiment of this sort may explain patterns of word learning in the wild (Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore, Karuza, Giusti, \& Bassett, 2018).
+In addition, it is important to study how laboratory experiments of this sort may explain patterns of word learning in the wild (Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore, Karuza, Giusti, \& Bassett, 2018).
 
 Our work found, among other things, that children have higher sound/phoneme uncertainty than adults do, but prior work have shown that children have good auditory encoding (Swingley, 2003; Swingley \& Aslin, 2000, 2002).
-These two findings are not in contradicton with each other.
+These two findings are not in conflict with each other.
 In this work, and as we explained above, the measured sound uncertainty includes various sources.
 One of these sources is perceptual uncertainty, i.e., the ability to perceptually distinguish a sound from other neighboring sounds (e.g., \enquote{bin} is perceptually different from \enquote{din}), and another source is categorical uncertainty, i.e., the ability to estimate phonological boundaries, e.g., \enquote{bin} and \enquote{din} straddle a phonological boundary, that is, they signal a change in meaning.
-The fact that children have a higher sound uncertainty than adults do, does not necessarily mean this higher uncertainty is due to poorer perceptual encoding, only.
+The fact that children have a higher sound uncertainty than adults do, does not necessarily mean this higher uncertainty is due to poorer perceptual encoding only.
 In fact, it is possible that much of the differential in uncertainty (compared to adults) is due to the categorical/phonological dimension which we know undergoes a process of reorganization and refinement across development.
@@
 
+\leavevmode\hypertarget{ref-marr1982}{}%
+Marr, D. (1982). \emph{Vision}. WH Freeman.
+
 \leavevmode\hypertarget{ref-Mattock2010}{}%
